### 2018-07-18 writing/thesis/chapters/conclusion.tex
Setup latex template.

\chapter{Conclusion}
Conclusion here.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:

### 2018-07-18 writing/thesis/pages/acknowledgements.tex
Setup latex template.

\thispagestyle{empty}

% \vspace*{20mm}

% \begin{center}
% %{\usekomafont{section} Acknowledgments}
% \end{center}

% \vspace{10mm}

\renewcommand{\dictumwidth}{\textwidth}
\setchapterpreamble{\dictum[Booktitle]{
    Quote!
}}
%\addcontentsline{toc}{chapter}{Acknowledgments}
\chapter{Acknowledgments}
\vspace{1em}

Acknowledgements here.
\cleardoublepage{}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:

### 2018-07-18 writing/thesis/chapters/methods.tex
Setup latex template.
Add Euler and NS-Equations.
Further work on equation typesetting.

--- 2018-07-18 writing/thesis/chapters/conclusion.tex
@@
-\chapter{Conclusion}
-Conclusion here.
+\chapter{Methods}
+Methods here.\todo{Organize into chapters!}
+
+% TODO: Extract to settings.tex
+\newcommand{\Qrho}{\ensuremath{\rho}}
+\newcommand{\Qj}{\ensuremath{\rho \bm{v}}}
+%\newcommand{\Qv}{\ensuremath{\Qrho^{-1} \Qj}}
+\newcommand{\Qv}{\ensuremath{\bm{v}}}
+\newcommand{\QE}{\ensuremath{\rho E}}
+\newcommand{\stressT}{\ensuremath{\bm{\sigma}}}
+\newcommand{\pressure}{\ensuremath{p}}
+\newcommand{\maxConvEigen}{\ensuremath{\vert \lambda_c^{\text{max}} \vert}}
+\newcommand{\maxViscEigen}{\ensuremath{\vert \lambda_v^{\text{max}} \vert}}
+
+\section{Conservative Form}
+Standard (hyperbolic) form of conservation law
+\begin{equation}
+  \label{eq:conservation-law}
+ \frac{\partial}{\partial_t}  Q + \nabla \cdot F(Q) = S(\bm{x}, t, Q)
+\end{equation}
+extend to:
+\begin{equation}
+  \label{eq:conservation-law}
+ \frac{\partial}{\partial_t}  Q + \nabla \cdot F(Q, \nabla Q) = S(\bm{x}, t, Q)
+\end{equation}
+
+\section{Compressible Euler}
+Vector of conserved quantities:
+\begin{equation}
+  \label{eq:conserved-variables}
+ Q = \left( \Qrho, \Qj, \QE \right) 
+\end{equation}
+
+\newcommand{\eulerFlux}{%
+  \begin{pmatrix}
+    \Qj \\
+    \Qv  \otimes \Qj + \pressure \bm{I}  \\
+    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure)
+  }
+Flux:
+\begin{equation}
+  F(Q) = \eulerFlux
+  \end{pmatrix}
+\end{equation}
+\begin{equation}
+  \pressure = (\gamma - 1) \left(\QE - 0.5 \left(\Qv \cdot \Qj \right) \right)
+\end{equation}
+
+\section{Compressible Navier Stokes}
+Following~\cite{dumbser2010arbitrary} by \citeauthor{dumbser2010arbitrary}.
+
+Flux:
+\begin{equation}
+  F(Q, \nabla Q) = 
+  \begin{pmatrix}
+    \Qj \\
+    \Qv  \otimes \Qj + \bm{I} \pressure + \stressT (Q, \nabla Q)  \\
+    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure + \stressT (Q, \nabla Q)) - \kappa \nabla T
+  \end{pmatrix}
+\end{equation}
+
+With:
+Pressure \pressure
+\begin{equation}
+  \pressure = (\gamma - 1) \left(\QE - 0.5 \left(\Qv \cdot \Qj \right) \right)
+\end{equation}
+
+Temperature $T$
+\begin{equation}
+ \frac{\pressure}{\Qrho} = RT
+\end{equation}
+
+Heat conduction coefficient $\kappa$
+\begin{equation}
+  \label{eq:heat-conduction-coeff}
+  \kappa = \frac{\mu \gamma}{\Pr} \frac{1}{\gamma - 1} R
+\end{equation}
+with $R$ gas constant and $Pr$ Prandtl number
+
+Sutherland's viscosity law:
+\begin{equation}
+  \label{eq:sutherland}
+ \mu(T)  = \mu_0 {\left(\frac{T}{T_0}  \right)}^{\beta} \frac{T_0 + C}{T + C}
+\end{equation}
+with \(\beta = 1.5\), \(C = \text{const.}\), reference temperature $T_0$ and reference viscosity $\mu_=$.
+Equal to
+\begin{align}
+  \lambda &= \frac{\mu_0 (T_0 + C)}{T_0^\beta} \\
+  \mu(T) &= \lambda \frac{T^\beta}{T + C},
+\end{align}
+where $\lambda$ is constant for a given fluid.
+
+stress tensor
+\begin{equation}
+  \label{eq:stress-tensor}
+  \stressT(Q, \nabla Q) = \left(\nicefrac{2}{3} \mu \nabla \cdot \Qv \right) -
+  \mu \left( \nabla (\Qv) + \nabla ( \Qv )^\intercal \right)
+\end{equation}
+
+Max eigenvalue of convective part \maxConvEigen\,i.e.\ of $\left( \partial \bm{F}/\partial \bm{Q}\right) \cdot \bm{n}$,
+and viscous part \maxViscEigen\, i.e.\ of $\left( \partial \bm{F}/\partial \left( \nabla \bm{Q} \cdot \bm{n} \right)\right) \cdot \bm{n}$
+is
+\begin{align}
+  \maxConvEigen \vert  &= \Vert \Qv \Vert + c\\
+  \maxViscEigen \vert &= \max \left( \frac{4}{3} \frac{\mu}{\Qrho}
+                                       , \frac{\gamma \mu}{\Pr \Qrho} \right)
+\end{align}
+with speed of sound $c = \sqrt{\gamma R T }$
+
+Maximum timestep (\textsc{cfl})
+\begin{equation}
+ \Delta t = \frac{\text{CFL}}{2N + 1} \, \frac{h}{\maxConvEigen + 2 \maxViscEigen \frac{2N+1}{h}}
+\end{equation}
+with $N$ polynomial order and $h$ characteristic length scale of elements
+
+Numerical flux:
+\begin{equation}
+  \label{eq:rusanov-flux}
+  G(q_h^-, \nabla q_h^-; g_h^+, \nabla q_h^+) \cdot \bm{n} =
+  \frac{1}{2} \left(
+    F(q_h^+, \nabla q_h^+) +
+    F(q_h^-, \nabla q_h^-)
+  \right) -
+  \frac{1}{2} s_\text{max} (q_h^+ - q_h^-)
+\end{equation}
+with
+\begin{equation}
+  \label{eq:parabolic-penalty}
+  s_\text{max}  = \max \left(
+\vert \lambda_c(q_h^-) \vert, \, \vert \lambda_c(q_h^+)
+\right) +
+2 \eta \max \left(
+\vert \lambda_v(q_h^-) \vert, \, \vert \lambda_v(q_h^+)
+\right)
+\end{equation}
+and
+\begin{equation}
+  \eta = \frac{N+1}{h}
+\end{equation}
 

### 2018-07-19 deploy.sh
Add deploy script.

@@ -1,0 +1,27 @@
+#!/bin/bash
+
+set -o errexit -o nounset
+
+if [ "$TRAVIS_BRANCH" != "master" ]
+then
+  echo "This commit was made against the $TRAVIS_BRANCH and not the master! No deploy!"
+  exit 0
+fi
+
+rev=$(git rev-parse --short HEAD)
+
+cd writing/thesis/build
+
+git init
+git config user.name "Lukas Krenz"
+git config user.email "lukas@krenz.land"
+
+git remote add upstream "https://$GH_TOKEN@github.com/cloudSuperComputing.git"
+git fetch upstream
+git reset upstream/pdf
+
+touch main.pdf
+
+git add -A .
+git commit -m "rebuild pages at ${rev}"
+git push -q upstream HEAD:pdf

### 2018-07-20 deploy.sh
Fix deploy.sh.

@@ -16,7 +16,7 @@ git init
 git config user.name "Lukas Krenz"
 git config user.email "lukas@krenz.land"
 
-git remote add upstream "https://$GH_TOKEN@github.com/cloudSuperComputing.git"
+git remote add upstream "https://$GH_TOKEN@github.com/krenzland/cloudSuperComputing.git"
 git fetch upstream
 git reset upstream/pdf
 

### 2018-07-20 deploy.sh
Ignore build files for deploying.
Only add main.pdf for now.

@@ -22,6 +22,6 @@ git reset upstream/pdf
 
 touch main.pdf
 
-git add -A .
+git add main.pdf
 git commit -m "rebuild pages at ${rev}"
 git push -q upstream HEAD:pdf

### 2018-10-14 writing/slides/kick_off.tex
Add first draft of slides.

\documentclass{beamer}
\usetheme{metropolis} % Use metropolis theme
\usepackage{lmodern}

\renewcommand{\footnoterule}{%
  \hspace{2cm}
  \kern -3pt
  \hrule width \textwidth height 1pt
  \kern 2pt
}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[autostyle, english = british]{csquotes}
\usepackage[british]{babel}
\usepackage{todonotes}
\usepackage[%
  backend=biber,
  doi=false,
  url=false,
  isbn=false,
  eprint=false,
  style=verbose,
  citestyle=verbose,
  hyperref=true,
  maxnames=99,
  minnames=1,
  maxbibnames=99,
  firstinits,
  uniquename=init]{biblatex}
%\DeclareFieldFormat[inproceedings, article]{pages}{}%
%\DeclareFieldFormat[inproceedings]{organization}{}%
  % ignore some field for citations
\DeclareSourcemap{
  \maps[datatype=bibtex, overwrite]{
    \map{
      \step[fieldset=edition, null]
      \step[fieldset=publisher, null]
      \step[fieldset=pages, null]
      \step[fieldset=organization, null]
    }
  }
}

\addbibresource{../bibliography.bib}

\let\oldfootnotesize\footnotesize
\renewcommand*{\footnotesize}{\oldfootnotesize\fontsize{6}{6}}

\usepackage{caption}
\usepackage{xpatch}
\usepackage{xcolor}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{mathtools} % for \mathclap
\usepackage{varioref}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage[noabbrev]{cleveref}
\newcommand{\creflastconjunction}{, and\nobreakspace} % use Oxford comma
\usepackage{todonotes}
\usepackage{multimedia}

\graphicspath{{../figures/}}
\newcommand{\Qrho}{\ensuremath{\rho}}
\newcommand{\Qj}{\ensuremath{\rho \bm{v}}}
%\newcommand{\Qv}{\ensuremath{\Qrho^{-1} \Qj}}
\newcommand{\Qv}{\ensuremath{\bm{v}}}
\newcommand{\QE}{\ensuremath{\rho E}}
\newcommand{\stressT}{\ensuremath{\bm{\sigma}}}
\newcommand{\pressure}{\ensuremath{p}}
\newcommand{\maxConvEigen}{\ensuremath{\vert \lambda_c^{\text{max}} \vert}}
\newcommand{\maxViscEigen}{\ensuremath{\vert \lambda_v^{\text{max}} \vert}}

\newcommand{\cn}{\footnote{\enquote{TODO: Citation.}, 2017, \textbf{Conference}, \textit{Author 1, Author 2, Author 3, Author 4} }}

\title{Cloud Supercomputing with the ExaHyPE-Engine\\Master Thesis Kick-Off}
\author{Lukas Krenz\\Adviser: Leonhard Rannabauer\\Superviser: Prof.\ Dr.\ Michael Bader}
\date{October 18, 2018} 
\institute{\textsc{tum}, Chair for Scientific Computing}

\begin{document}
\maketitle
\begin{frame}{Rising Bubble: Hydrostatic Equilibrium\footfullcite{robert1993bubble}}
  \begin{columns}
    \begin{column}[t]{0.5\textwidth}
      \begin{itemize}
      \item 
  Air is in hydrostatic equilibrium:

  Gravitational force and pressure-gradient force are exactly balanced.

  \item Constant potential temperature (temperature normalized by pressure) with slightly warmer bubble.

  \end{itemize}
    \end{column}~%
    \begin{column}[t]{0.5\textwidth}
      \begin{figure}[h]
\includegraphics[width=1.0\textwidth]{hydrostatic_density}
\caption{Density in equilibrium}
\end{figure}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Rising Bubble: Simulation}
   \begin{figure}[h]
    \centering
    \movie[width=0.9735\textwidth, height=0.55\textwidth, autostart,, loop, poster]{}{bubbles_order1.ogv}
    \caption{Rising bubble scenario}
  \end{figure}
\end{frame}

\begin{frame}{The ADER-DG Approach\footfullcite{dumbser2008unified}}
  Solve hyperbolic conservation laws of the form
\begin{equation}
  \label{eq:conservation-law}
 \frac{\partial}{\partial_t}  Q + \nabla \cdot F(Q) = S(\bm{x}, t, Q)
\end{equation}
with $Q$ vector of conserved variables, $\bm{x}$ position, $t$ time,  $\nabla \cdot F(Q)$ divergence of flux and $S(\bm{x}, t, Q)$ source term.

Discontinous Galerkin (DG) divides domain into disjoint elements, approximates solutions by discontinous polynomials.
Elements are connected by solving the Riemann problem.

ADER-Approach uses space-time polynomials for time integration instead of Runge-Kutta procedures.

Implemented in the PDE-Framework ExaHyPe.
\end{frame}

\begin{frame}{The Navier-Stokes Equations}
  Vector of conserved quantities:
\begin{equation}
  \label{eq:conserved-variables}
 Q = \left( \Qrho, \Qj, \QE \right) 
\end{equation}
With $\Qrho$ density of fluid, $\Qj$ velocity density and $\QE$ energy density.

Flux:
\begin{equation}
  F(Q, \nabla Q) = 
  \begin{pmatrix}
    \Qj \\
    \Qv  \otimes \Qj + \bm{I} \pressure + \textcolor{orange}{\stressT (Q, \nabla Q)}  \\
    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure + \textcolor{orange}{\stressT (Q, \nabla Q))} -
    \textcolor{orange}{\kappa \nabla T}
  \end{pmatrix}
\end{equation}

$T$ temperature, $\pressure$ pressure,
$\textcolor{orange}{\stressT}$ stress tensor, $\textcolor{orange}{\kappa \nabla T}$ heat diffusion term
\end{frame}

\begin{frame}{Problem: Not hyperbolic}
  DG solves equations of the form (e.g.\ Euler):
  \begin{equation}
  \label{eq:conservation-law}
 \frac{\partial}{\partial_t}  Q + \nabla \cdot F(Q) = S(\bm{x}, t, Q)
\end{equation}

We have:
\begin{equation}
  \label{eq:conservation-law}
 \frac{\partial}{\partial_t}  Q + \nabla \cdot F(Q, \textcolor{orange}{\nabla Q}) = S(\bm{x}, t, Q)
\end{equation}

Solution:
Change numerical flux (Riemann solver), time step size (CFL-Condition) and boundary conditions to allow diffusive terms\footfullcite{dumbser2010arbitrary}.

\alert{No explicit discretization} of gradient $\nabla Q$.
\end{frame}

\begin{frame}{Current status}
  \begin{block}{Working}
  \begin{itemize}
  \item Numerical scheme
  \item Cloud scenario
  \end{itemize}
  \end{block}

  \begin{block}{Goals}
  \begin{itemize}
  \item Fix convergence
  \item Finite Volume Limiting\footfullcite{dumbser2016simple}
  \item Adaptive Grids
  \item Coupling of Navier-Stokes with other PDE (e.g.\ simple advection equation) by solving Riemann problem at boundary
  \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Current status of Convergence-Tests}
  \begin{figure}[h]
    \centering
   \includegraphics[width=0.8\textwidth]{{l2_error}}
    \caption{Mesh-Size vs $L_2$ error }
    \label{fig:l2-error}
  \end{figure}
\end{frame}

\begin{frame}{Summary}
  \begin{block}{Main Objectives}
  \begin{itemize}
  \item Dynamics of clouds can be simulated by Navier-Stokes equations.
  \item ADER-DG can be used to simulate Navier-Stokes equations.
  \item The ExaHyPE-Engine provides an efficient, scalable implementation of ADER-DG scheme. 
  \end{itemize}
  \end{block}

  \begin{block}{Bonus Objectives}
    \begin{itemize}
    \item All extensions to engine (diffusive fluxes, coupling) useful for other user of ExaHyPE
    \item First use of ExaHyPE-Engine for metrological simulations
    \end{itemize}

  \end{block}
\end{frame}

\end{document}

### 2018-10-17 writing/slides/kick_off.tex
Improve slides using bold text.

@@
 
-  Gravitational force and pressure-gradient force are exactly balanced.
+  Gravitational force and pressure-gradient force are \textbf{exactly balanced}.
 
@@
 \begin{frame}{The ADER-DG Approach\footfullcite{dumbser2008unified}}
-  Solve hyperbolic conservation laws of the form
+  Solve \textbf{hyperbolic conservation laws} of the form
 \begin{equation}
@@
 
-Discontinous Galerkin (DG) divides domain into disjoint elements, approximates solutions by discontinous polynomials.
+\textbf{Discontinuous Galerkin} (\textsc{DG}) divides domain into disjoint elements, approximates solutions by piecewise-polynomials.
 Elements are connected by solving the Riemann problem.
 
-ADER-Approach uses space-time polynomials for time integration instead of Runge-Kutta procedures.
+\textbf{ADER}-Approach uses space-time polynomials for time integration instead of Runge-Kutta procedures.
 
-Implemented in the PDE-Framework ExaHyPe.
+Implemented in the PDE-Framework \textbf{ExaHyPE}.
 \end{frame}
@@
 \begin{equation}
-  F(Q, \nabla Q) = 
+  F(Q, \textcolor{orange}{\nabla Q}) = 
   \begin{pmatrix}
@@
 
-Solution:
-Change numerical flux (Riemann solver), time step size (CFL-Condition) and boundary conditions to allow diffusive terms\footfullcite{dumbser2010arbitrary}.
+\textbf{Solution}:
+Modify numerical flux (Riemann solver), time step size (CFL-Condition) and boundary conditions to \textbf{allow diffusive terms}\footfullcite{dumbser2010arbitrary}.
 
@@
   \item Fix convergence
+  \item Adaptive Grids
   \item Finite Volume Limiting\footfullcite{dumbser2016simple}
-  \item Adaptive Grids
   \item Coupling of Navier-Stokes with other PDE (e.g.\ simple advection equation) by solving Riemann problem at boundary
@@
 
-\begin{frame}{Current status of Convergence-Tests}
-  \begin{figure}[h]
-    \centering
-   \includegraphics[width=0.8\textwidth]{{l2_error}}
-    \caption{Mesh-Size vs $L_2$ error }
-    \label{fig:l2-error}
-  \end{figure}
-\end{frame}
+% \begin{frame}{Current status of Convergence-Tests}
+%   \begin{figure}[h]
+%     \centering
+%    \includegraphics[width=0.8\textwidth]{{l2_error}}
+%     \caption{Mesh-Size vs $L_2$ error }
+%     \label{fig:l2-error}
+%   \end{figure}
+% \end{frame}
 
@@
   \begin{itemize}
-  \item Dynamics of clouds can be simulated by Navier-Stokes equations.
-  \item ADER-DG can be used to simulate Navier-Stokes equations.
-  \item The ExaHyPE-Engine provides an efficient, scalable implementation of ADER-DG scheme. 
+  \item \textbf{Navier-Stokes equations} can describe dynamics of clouds.
+  \item \textbf{ADER-DG} can be used to discretize Navier-Stokes equations.
+  \item The \textbf{ExaHyPE-Engine} provides an efficient, scalable implementation of ADER-DG scheme. 
   \end{itemize}
@@
     \begin{itemize}
-    \item All extensions to engine (diffusive fluxes, coupling) useful for other user of ExaHyPE
-    \item First use of ExaHyPE-Engine for metrological simulations
+    \item All extensions to engine (diffusive fluxes, coupling) useful for other user of ExaHyPE.
+    \item First use of ExaHyPE-Engine for simulation of clouds.
     \end{itemize}

### 2018-10-18 writing/slides/kick_off.tex
Revise kick off slides, final(?) revision.
Also add conv. plot.
Add final (really?) version of slides.

@@
 \title{Cloud Supercomputing with the ExaHyPE-Engine\\Master Thesis Kick-Off}
-\author{Lukas Krenz\\Adviser: Leonhard Rannabauer\\Superviser: Prof.\ Dr.\ Michael Bader}
+\author{Lukas Krenz\\Adviser: Leonhard Rannabauer\\Supervisor: Prof.\ Dr.\ Michael Bader}
 \date{October 18, 2018} 
@@
 
-Implemented in the PDE-Framework \textbf{ExaHyPE}.
+Implemented in the \textsc{PDE}-Framework \textbf{ExaHyPE}.
 \end{frame}
@@
     \Qv  \otimes \Qj + \bm{I} \pressure + \textcolor{orange}{\stressT (Q, \nabla Q)}  \\
-    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure + \textcolor{orange}{\stressT (Q, \nabla Q))} -
+    \Qv \cdot \left(\bm{I} \QE + \bm{I} \pressure + \textcolor{orange}{\stressT (Q, \nabla Q)} \right) -
     \textcolor{orange}{\kappa \nabla T}
@@
 \begin{frame}{Problem: Not hyperbolic}
-  DG solves equations of the form (e.g.\ Euler):
+  \textsc{DG} solves equations of the form (e.g.\ Euler):
   \begin{equation}
@@
 \textbf{Solution}:
-Modify numerical flux (Riemann solver), time step size (CFL-Condition) and boundary conditions to \textbf{allow diffusive terms}\footfullcite{dumbser2010arbitrary}.
+Modify numerical flux (Riemann solver), time step size (\textsc{cfl}-Condition) and boundary conditions to \textbf{allow diffusive terms}\footfullcite{dumbser2010arbitrary}.
 
@@
   \item Fix convergence
-  \item Adaptive Grids
+  \item Adaptive Mesh Refinement
   \item Finite Volume Limiting\footfullcite{dumbser2016simple}
@@
 
-% \begin{frame}{Current status of Convergence-Tests}
-%   \begin{figure}[h]
-%     \centering
-%    \includegraphics[width=0.8\textwidth]{{l2_error}}
-%     \caption{Mesh-Size vs $L_2$ error }
-%     \label{fig:l2-error}
-%   \end{figure}
-% \end{frame}
+\begin{frame}{Current status of Convergence-Tests}
+  \begin{figure}[h]
+    \centering
+   \includegraphics[width=0.8\textwidth]{{l2_error}}
+    \caption{Mesh-Size vs $L_2$ error }
+    \label{fig:l2-error}
+  \end{figure}
+\end{frame}
 
@@
     \begin{itemize}
-    \item All extensions to engine (diffusive fluxes, coupling) useful for other user of ExaHyPE.
-    \item First use of ExaHyPE-Engine for simulation of clouds.
+    \item All \textbf{extensions} to engine (diffusive fluxes, coupling) useful for \textbf{other users} of ExaHyPE.
+    \item First use of ExaHyPE-Engine for \textbf{simulation of clouds}.
     \end{itemize}

### 2018-10-21 writing/thesis/chapters/methods.tex
Write a bit more about scenarios.

@@
 \begin{equation}
+  \label{eq:temperature}
  \frac{\pressure}{\Qrho} = RT
@@
 
+\section{Scenarios}
+\label{sec:scenarios}
+
+\subsection{Clouds}
+Air is initially at rest and in hydrostractic balance
+\begin{equation}
+  \label{eq:hydrostatic-balance}
+ \pdv{p (z)}{z} = -\rho(z) g.
+\end{equation}
+Inserting \cref{eq:temperature} leads to the \textsc{ode}
+\begin{equation}
+  \pdv{p(z)}{z} = - \frac{p(z)}{RT} g,
+\end{equation}
+which can be solved by seperation of variables.
+This results in the equation
+\begin{equation}
+  \label{eq:bubble-pressure}
+  p(z) = c \exp \left( - \frac{gz}{RT} \right),
+\end{equation}
+where the constant of integration $c$ can be found by considering the case
+\begin{equation}
+  p(0) = c.
+\end{equation}
+
+The scenario is described in terms of potential temperature $\theta$
+\begin{equation}
+  \theta = T \frac{p_0}{p}^{R/c_p},
+\end{equation}
+where $p_o = \SI{10e5}{\Pa}$ is the reference pressure.
+Solving for $T$ leads to
+\begin{equation}
+  T = \theta (\frac{p}{p_0})^{R/c_p}.
+\end{equation}
+
+Note: Above approach leads to wrong atmosphere, rather do (with constant potential temperature):
+Equation of state with potential temperature:
+\begin{equation}
+  \label{eq:eos}
+\Qrho(z) = \frac{p_{0}^{\frac{c_{p} - c_{v}}{c_{p}}} p^{\frac{c_{v}}{c_{p}}}{\left (z \right )}}{R \theta}
+\end{equation}
+Hydrostatic equilibrium with potential temperature:
+\begin{equation}
+  \label{eq:hydrostatic-balance-potT}
+  \frac{d}{d z} p{\left (z \right )} = - \frac{g p_{0}^{\frac{R}{c_{p}}} p^{\frac{1}{\gamma}}{\left (z \right )}}{R \theta}
+\end{equation}
+Solution for pressure with initial condition of $p(0) = p_0$:
+% \begin{equation*}
+% p = \left(\frac{R \gamma \theta \left(\gamma^{\frac{\gamma}{\gamma - 1}} p_{0}\right)^{\frac{\gamma - 1}{\gamma}} - R \theta \left(\gamma^{\frac{\gamma}{\gamma - 1}} p_{0}\right)^{\frac{\gamma - 1}{\gamma}} - g \gamma p_{0}^{\frac{R}{c_{p}}} z \left(\gamma - 1\right) + g p_{0}^{\frac{R}{c_{p}}} z \left(\gamma - 1\right)}{R \gamma \theta \left(\gamma - 1\right)}\right)^{\frac{\gamma}{\gamma - 1}}
+% \end{equation*}
+\begin{equation}
+p(z) =  \left(C - \frac{C}{\gamma} - \frac{g p_{0}^{\frac{R}{c_{p}}} z}{R \theta} + \frac{g p_{0}^{\frac{R}{c_{p}}} z}{R \gamma \theta}\right)^{\frac{\gamma}{\gamma - 1}},
+\end{equation}
+with constant of integration
+\begin{equation}
+  \label{eq:hydrostatic-balance-constant}
+ C = \frac{\left(\gamma^{\frac{\gamma}{\gamma - 1}} p_{0}\right)^{\frac{\gamma - 1}{\gamma}}}{\gamma - 1},
+\end{equation}
+which can be obtained by setting $p(0) = p_0$.
+
+\section{Convergence}
+We first define the $L_p$ norms for $p > 0$ by
+% notation: https://en.wikipedia.org/wiki/Lp_space#Lp_spaces
+\begin{equation}
+  \label{eq:Lp-nrom}
+  \Vert f(x) \Vert = \left( \int_K \vert f(x) \vert^p d\mu  \right)^{1/p}.
+\end{equation}
+We start by a known analytical solution $f(x)$ and compare it to our approximation $\hat{f}(x)$.
+Let $Q$ and $\hat{Q}$ denote the analytical and approximate solution at node.
+We start by computing the point-wise error, and compute the cell-wise error from this.
+Observe that for our broken space $\Omega$
+\begin{equation}
+  \label{eq:lp-norm-broken}
+ \Vert f(x) \Vert = \sum_{K \in \Omega} \Vert f_K(x) \Vert_p.
+\end{equation}
+
+We are now ready to integrate the error for each cell.
+The output contains the position and conserved variables of each point.
+Each cell consists of $(N + 1)^d$ nodes, each associated with a quadrature weight $w_i$.
+The quadrature weights are associated with the reference cuboid.
+We thus need to map our element to the reference element, before we can compute the integral.
+
+Let $V$ denote the volume (or area) of each cell.
+For example, in three dimensions $V = \Delta x \, \Delta y \, \Delta z$.
+The final result is then
+\begin{equation}
+  \Vert f_K(x) \Vert = \left( V \sum_{\bm{i}} \vert f(\bm{x}_{\bm{i}}) \vert^p w_{{\bm{i}}}  \right)^{1/p},
+\end{equation}
+where we used the mapping to the reference triangle (integration by substitution).
+
+Following~\cite{dumbser2010arbitrary}, the scenario can be described in primitive variables by setting
+\begin{align}
+  \pressure &= \pressure_0 \cos( \bm{k} \bm{x} - \omega t ) + \pressure_b, \\
+  \Qrho &= \Qrho_0 \sin (\bm{k} \bm{x} - \omega t) + \Qrho_b, \\
+  \Qv &= \bm{v_0} \sin(\bm{k} \bm{x} - \omega t).
+\end{align}
+We set the constants to \( \left(  \pressure_0 = 0.1, \pressure_b = \gamma^{-1}, \Qrho_0 = 0.5, \Qrho_b = 1, 
+\bm{v_0} = 0.25 {(1,1)}^\intercal, \bm{k} = \pi/5 {(1,1)}^\intercal \right) \).
+
+We derive a source term by inserting this solution into the \textsc{pde} using the symbolic math toolkit \textit{SymPy}.
+
 %%% Local Variables:

### 2018-10-31 writing/thesis/chapters/methods.tex
Flesh out description of NS-Eq, start DG-sec.

@@
 % TODO: Extract to settings.tex
-\newcommand{\Qrho}{\ensuremath{\rho}}
-\newcommand{\Qj}{\ensuremath{\rho \bm{v}}}
+\newcommand{\Qrho}{\rho}
+\newcommand{\Qj}{\rho \bm{v}}
 %\newcommand{\Qv}{\ensuremath{\Qrho^{-1} \Qj}}
-\newcommand{\Qv}{\ensuremath{\bm{v}}}
-\newcommand{\QE}{\ensuremath{\rho E}}
-\newcommand{\stressT}{\ensuremath{\bm{\sigma}}}
-\newcommand{\pressure}{\ensuremath{p}}
-\newcommand{\maxConvEigen}{\ensuremath{\vert \lambda_c^{\text{max}} \vert}}
-\newcommand{\maxViscEigen}{\ensuremath{\vert \lambda_v^{\text{max}} \vert}}
+\newcommand{\Qv}{\bm{v}}
+\newcommand{\QE}{\rho E}
+\newcommand{\stressT}{\bm{\sigma}}
+\newcommand{\pressure}{p}
+\newcommand{\maxConvEigen}{\vert \lambda_c^{\text{max}} \vert}
+\newcommand{\maxViscEigen}{\vert \lambda_v^{\text{max}} \vert}
+
+\newcommand{\domain}{\Omega}
+\newcommand{\broken}{\domain}
+\newcommand{\cell}[1][i]{C_{#1}}
+\newcommand{\boundary}{\partial \domain}
+\newcommand{\sbasis}[1]{\Phi_{#1}}
+\newcommand{\testfunction}[1]{\Phi_{#1}}
 
@@
   \label{eq:conservation-law}
- \frac{\partial}{\partial_t}  Q + \nabla \cdot F(Q) = S(\bm{x}, t, Q)
+ \frac{\partial}{\partial_t}  Q + \div \cdot F(Q) = S(\bm{x}, t, Q)
 \end{equation}
@@
 \begin{equation}
-  \label{eq:conservation-law}
- \frac{\partial}{\partial_t}  Q + \nabla \cdot F(Q, \nabla Q) = S(\bm{x}, t, Q)
+  \label{eq:conservation-law-gradient}
+ \frac{\partial}{\partial_t}  Q + \div \cdot F(Q, \grad Q) = S(\bm{x}, t, Q)
 \end{equation}
+
+\section{The ADER-DG Method}
+\label{sec:ader-dg}
+We describe the arbitrary derivative discontinous Galerkin (ADER-DG) method in this chapter.
+
+We discuss the solution of a hyperbolic conservation law \cref{eq:conservation-law} with domain $\domain$ and boundary $boundary$.
+In the discontinous Galerkin (DG) framework, we approximate this solution in the space
+\begin{equation}
+  \label{eq:dg-space}
+  \broken = \bigcup_i \cell
+\end{equation}
+of disjoint quadrilateral cells $\cell$.
+Note that we do not distinguish between the approximation space and the domain, the use should be clear given its surrounding context.
+In the following we make use of the Einstein summation convention where summation over repeated indexes is implied.
+
+Inside each cell $\cell$ we represent the solution in terms of the basis function 
+\begin{equation}
+  \label{eq:cell-approx}
+  u(\bm{x}, t^n)_{|\cell[i]} = \hat{u}^n_{i,l} \sbasis{l}{\bm{x}},
+\end{equation}
+where $l$ is a multi-index, containing one index per spatial dimension.
+\todo{dofs $\hat{u}$. local solution, etc.}
+For example, $(l = (l_1, l_2))$ for the two dimensional case.
+This polynomial is interpolating, i.e.\ \ldots\todo{interpolating?}.
+This choice of basis (called \textit{nodal} basis) allows us to easily compute integrals over cells using Gaussian quadrature.
+In detail, we use a the Lagrange interpolation polynomials.
+
+We now describe the derivation of the \textsc{ader-dg} method.
+This scheme is a predictor-corrector method.
+We first compute a local solution of the cell in the predictor step and then connect with the neighbors in the corrector step.
+In the following we first describe the corrector step as it follows directly from the \textsc{pde}.
+The predictor is derived shortly after.
+
+\sidetitle{Corrector}
+First, we multiply the system \cref{eq:conservation-law} by a test function $\testfunction{i}$ and integrate over the space-time volume $(\cell \times [t^n, t^{n+1}])$.
+We arrive at the so called weak formulation of the \textsc{pde} 
+\newcommand{\intdt}[1]{\int_{t^n}^{t^{n+1}} #1 \dd{t}}
+\newcommand{\intdcell}[1]{\int_{\cell} #1 \dd{\bm{x}}}
+\newcommand{\intdcellb}[1]{\int_{\partial{} \cell} #1 \dd{S}} % TODO: define boundary of cell
+\begin{equation}
+  \label{eq:weak-pde}
+\intdt{\intdcell{
+\testfunction{k} \pdv{\bm{Q}}{t}
+}}
++
+\intdt{\intdcell{
+    \testfunction{k} \left( \div{F(Q, \gradient{Q})} \right)
+}}
+=
+\intdt{\intdcell{
+    \testfunction{k} S(Q, \bm{x}, t)
+}}
+\end{equation}
+\todo{Include gradient everywhere!}
+\todo{Double check the following description}
+\newcommand{\stpredictor}[1]{\bm{q}_{#1}}
+We now replace the solution $\bm{Q}$ with so called spacetime-predictor $\stpredictor{h}(\bm{x},t)$ into the weak form and write it as a polynomial using the representation of \cref{eq:cell-approx}.
+Integrate first by parts in time (note basis here not defined over time), flux divergence by parts in space.
+\begin{align}
+\begin{split}
+\label{eq:corrector}
+\left(
+\intdcell{
+  \testfunction{k} \sbasis{l}
+}
+\right)
+\left(\intdt{\intdcellb{
+\text{dofs boundary time}
+}}\right)
+&+\\
+\left(\intdt{\intdcell{
+\text{Riemann}
+}}\right)
+-
+\left(\intdt{\intdcell{
+\text{Flux}
+}}\right)
+&=
+\left(\intdt{\intdcell{
+  \text{Source}
+}}\right)
+\end{split}
+\end{align}
+The first term motivates an orthogonal basis as this leads to a diagonal mass matrix.
+
+\sidetitle{Predictor}
+To derive the predictor, we again take an approximation of our solution in a nodal basis, but now consider polynomials that are defined both in space and time.
+\begin{equation}
+  \ldots
+\end{equation}
+We know multiply the conservation law again by a test function (of the same function space as the basis) and arrive at the weak formulation
+\begin{equation}
+  \label{eq:weak-pde-space-time}
+ \ldots
+\end{equation}
+Similar to the derivation of the corrector, we again integrate the first term by parts in time and the flux divergence in space.
+This time we do not use the Riemann solver for the flux boundary term but rather use the discrete solution at time $t$.
+Note that this neglects the interaction with neighbouring cells; this is corrected in the corrector step.
+
+\begin{equation}
+  \label{eq:space-time-predictor}
+  \ldots
+\end{equation}
+Inserting \cref{eq:cell-approx-space-time} results in a local systems of equations that can be solved in a fixed point iteration scheme.
+For details and proof of convergence for the linear case, see (todo).
+Write about initial guess (we use naive one anyway, right?)
+
+\sidetitle{Boundary extrapolation and stuff}
+Extrapolate unknowns to boundary, convert from our basis to basis on faces.
+Then Riemann solver
+and so on
+
+\sidetitle{Full Scheme}
+Maybe write algorithm?
+
+\todo{Actually write this section\ldots}
 
@@
 
-Flux:
+The full compressible Navier Stokes equations with heat transfer can be described by
 \begin{equation}
@@
     \Qv \cdot (\bm{I} \QE + \bm{I} \pressure + \stressT (Q, \nabla Q)) - \kappa \nabla T
-  \end{pmatrix}
+  \end{pmatrix},
 \end{equation}
+where $\pressure$, $\stressT$ and $(\kappa \nabla T)$ denote the pressure, stress tensor and heat flux respectively.
+Temperature is denoted by $T$.
 
-With:
-Pressure \pressure
+We use the equation of state of an ideal gas
 \begin{equation}
-  \pressure = (\gamma - 1) \left(\QE - 0.5 \left(\Qv \cdot \Qj \right) \right)
+  \pressure = (\gamma - 1) \left(\QE - 0.5 \left(\Qv \cdot \Qj \right) \right).
 \end{equation}
-
-Temperature $T$
+The temperature $T$ relates to pressure and density by the ideal gas law
 \begin{equation}
   \label{eq:temperature}
- \frac{\pressure}{\Qrho} = RT
+ \frac{\pressure}{\Qrho} = RT,
 \end{equation}
+where $R$ is the specific gas constant.
+
+\todo{Write more text about constants, cite idolikecfd or sth}
+\begin{align}
+  c_v &= \frac{1}{\gamma - 1} R \\
+  c_p &= \frac{\gamma}{\gamma - 1} R\\
+  R &= c_p - c_v\\
+  \gamma &= \frac{c_p}{c_v}
+\end{align}
 
@@
 \end{equation}
-with $R$ gas constant and $Pr$ Prandtl number
+with $R$ gas constant and $\Pr$ Prandtl number
 
-Sutherland's viscosity law:
-\begin{equation}
-  \label{eq:sutherland}
- \mu(T)  = \mu_0 {\left(\frac{T}{T_0}  \right)}^{\beta} \frac{T_0 + C}{T + C}
-\end{equation}
-with \(\beta = 1.5\), \(C = \text{const.}\), reference temperature $T_0$ and reference viscosity $\mu_=$.
-Equal to
-\begin{align}
-  \lambda &= \frac{\mu_0 (T_0 + C)}{T_0^\beta} \\
-  \mu(T) &= \lambda \frac{T^\beta}{T + C},
-\end{align}
-where $\lambda$ is constant for a given fluid.
+% Sutherland's viscosity law:
+% \begin{equation}
+%   \label{eq:sutherland}
+%  \mu(T)  = \mu_0 {\left(\frac{T}{T_0}  \right)}^{\beta} \frac{T_0 + C}{T + C}
+% \end{equation}
+% with \(\beta = 1.5\), \(C = \text{const.}\), reference temperature $T_0$ and reference viscosity $\mu_=$.
+% Equal to
+% \begin{align}
+%   \lambda &= \frac{\mu_0 (T_0 + C)}{T_0^\beta} \\
+%   \mu(T) &= \lambda \frac{T^\beta}{T + C},
+% \end{align}
+% where $\lambda$ is constant for a given fluid.
 
-stress tensor
+The viscous effects are modeled by the stress tensor
 \begin{equation}
@@
   \stressT(Q, \nabla Q) = \left(\nicefrac{2}{3} \mu \nabla \cdot \Qv \right) -
-  \mu \left( \nabla (\Qv) + \nabla ( \Qv )^\intercal \right)
+  \mu \left( \nabla (\Qv) + \nabla ( \Qv )^\intercal \right).
 \end{equation}
 
-Max eigenvalue of convective part \maxConvEigen\,i.e.\ of $\left( \partial \bm{F}/\partial \bm{Q}\right) \cdot \bm{n}$,
-and viscous part \maxViscEigen\, i.e.\ of $\left( \partial \bm{F}/\partial \left( \nabla \bm{Q} \cdot \bm{n} \right)\right) \cdot \bm{n}$
+\subsection{Boundary conditions}
+To close the system we need to impose boundary conditions.
+
+For some scenarios we use Cauchy boundary conditions.
+In most cases, we would like to impose periodic boundary conditions, due to the inner workings of ExaHyPE this is not possible.
+Instead we use the analytical solution of our problems at the boundary, imposing both value and gradients of the conservative variables.
+Note that this leads to an error when our problem does not posses an exact analytical solution.
+This is the case for test cases that are analytical solutions to the incompressible Navier Stokes equations but do not satisfy the compressible equation set.
+
+As a physical boundary condition we limit ourselves to the no-slip boundary condition, where we assume that the fluid has a velocity of zero near the wall.
+\todo{Check if this is the correct physical description!}
+We enfore this by setting
+\begin{align}
+  \Qrho^o &= \Qrho^i, \\
+  \Qj^o &= -\Qj^i, \\
+  \QE^0 &= \QE^i,\\
+  {(\nabla Q)}^o &= {(\nabla Q)}^i,
+\end{align}
+where a superscript of $o$ and $i$ denotes the values outside and inside of the boundary respectively.
+
+\subsection{Diffusive Flux stuff}
+Max eigenvalue of convective part $\maxConvEigen$,i.e.\ of $\left( \partial \bm{F}/\partial \bm{Q}\right) \cdot \bm{n}$,
+and viscous part $maxViscEigen$, i.e.\ of $\left( \partial \bm{F}/\partial \left( \nabla \bm{Q} \cdot \bm{n} \right)\right) \cdot \bm{n}$
 is

### 2018-11-14 writing/thesis/chapters/methods.tex
Rewrite section about cloud scenarios.

@@
 \newcommand{\QE}{\rho E}
+\newcommand{\potT}{\theta}
+\newcommand{\backgroundPotT}{\overline{\theta}}
+\newcommand{\pertubationPotT}{\theta'}
 \newcommand{\stressT}{\bm{\sigma}}
@@
 \begin{equation}
+  \label{eq:eos}
   \pressure = (\gamma - 1) \left(\QE - 0.5 \left(\Qv \cdot \Qj \right) \right).
 \end{equation}
+
 The temperature $T$ relates to pressure and density by the ideal gas law
@@
 
-\section{Scenarios}
-\label{sec:scenarios}
+\section{Scenarios}\label{sec:scenarios}
 
 \subsection{Clouds}
-Air is initially at rest and in hydrostractic balance
+The scenario is described in terms of potential temperature $\potT$
 \begin{equation}
-  \label{eq:hydrostatic-balance}
- \pdv{p (z)}{z} = -\rho(z) g.
-\end{equation}
-Inserting \cref{eq:temperature} leads to the \textsc{ode}
-\begin{equation}
-  \pdv{p(z)}{z} = - \frac{p(z)}{RT} g,
-\end{equation}
-which can be solved by seperation of variables.
-This results in the equation
-\begin{equation}
-  \label{eq:bubble-pressure}
-  p(z) = c \exp \left( - \frac{gz}{RT} \right),
-\end{equation}
-where the constant of integration $c$ can be found by considering the case
-\begin{equation}
-  p(0) = c.
-\end{equation}
-
-The scenario is described in terms of potential temperature $\theta$
-\begin{equation}
-  \theta = T \frac{p_0}{p}^{R/c_p},
+  \potT = T \frac{p_0}{p}^{R/c_p},
 \end{equation}
@@
 \begin{equation}
-  T = \theta (\frac{p}{p_0})^{R/c_p}.
+  \label{eq:potTToT}
+  T = \potT (\frac{p}{p_0})^{R/c_p}.
+\end{equation}
+To allow for an easier description of the initial conditions we split the $\potT$ into a background state $\backgroundPotT$ and a pertubation $\pertubationPotT$
+\begin{equation}
+  \label{eq:potT-split}
+  \potT = \backgroundPotT + \pertubationPotT.
 \end{equation}
 
-Note: Above approach leads to wrong atmosphere, rather do (with constant potential temperature):
-Equation of state with potential temperature:
+The initial conditions for pressure and density can be computed directly from the \textsc{pde} once few assumptions have been given.
+We assume that $\backgroundPotT$ is constant over the entire domain.
+Inserting the definition of potential temperature, given by \cref{eq:potTToT}, into the equation of state (see \cref{eq:eos}) leads us to
 \begin{equation}
-  \label{eq:eos}
-\Qrho(z) = \frac{p_{0}^{\frac{c_{p} - c_{v}}{c_{p}}} p^{\frac{c_{v}}{c_{p}}}{\left (z \right )}}{R \theta}
+  \label{eq:eos-potT}
+\Qrho(z) = \frac{p_{0}^{\frac{R}{c_{p}}} p^{\frac{1}{\gamma}}{\left (z \right )}}{R \backgroundPotT}.
 \end{equation}
-Hydrostatic equilibrium with potential temperature:
+Flow in hydrostatic equilibrium can now be described by the ordinary differential equation(\textsc{ode})
+\begin{align}
+  \label{eq:hydrostatic-balance-potT}
+  \frac{d}{d z} p{\left (z \right )} &= -g \Qrho(z)
+                                     = 
+        - \frac{g p_{0}^{\frac{R}{c_{p}}} p^{\frac{1}{\gamma}}{\left (z \right )}}{R \backgroundPotT}\\
+  p{\left (0 \right )} &= p_0
+\end{align}
+where we use the reference pressure $p_0$ as the pressure on ground level.
+This \textsc{ode} can be now simply solved by separation of variables.
+After simplifying, we arrive at the initial condition for pressure
 \begin{equation}
-  \label{eq:hydrostatic-balance-potT}
-  \frac{d}{d z} p{\left (z \right )} = - \frac{g p_{0}^{\frac{R}{c_{p}}} p^{\frac{1}{\gamma}}{\left (z \right )}}{R \theta}
+p(z) = \left(\left(1 - \frac{1}{\gamma}\right) \left(C - \frac{g p_{0}^{\frac{R}{c_{p}}} z}{R \backgroundPotT}\right)\right)^{\frac{c_{p}}{R}},
 \end{equation}
-Solution for pressure with initial condition of $p(0) = p_0$:
-% \begin{equation*}
-% p = \left(\frac{R \gamma \theta \left(\gamma^{\frac{\gamma}{\gamma - 1}} p_{0}\right)^{\frac{\gamma - 1}{\gamma}} - R \theta \left(\gamma^{\frac{\gamma}{\gamma - 1}} p_{0}\right)^{\frac{\gamma - 1}{\gamma}} - g \gamma p_{0}^{\frac{R}{c_{p}}} z \left(\gamma - 1\right) + g p_{0}^{\frac{R}{c_{p}}} z \left(\gamma - 1\right)}{R \gamma \theta \left(\gamma - 1\right)}\right)^{\frac{\gamma}{\gamma - 1}}
-% \end{equation*}
-\begin{equation}
-p(z) =  \left(C - \frac{C}{\gamma} - \frac{g p_{0}^{\frac{R}{c_{p}}} z}{R \theta} + \frac{g p_{0}^{\frac{R}{c_{p}}} z}{R \gamma \theta}\right)^{\frac{\gamma}{\gamma - 1}},
-\end{equation}
-with constant of integration
+with a constant of integration
 \begin{equation}
   \label{eq:hydrostatic-balance-constant}
- C = \frac{\left(\gamma^{\frac{\gamma}{\gamma - 1}} p_{0}\right)^{\frac{\gamma - 1}{\gamma}}}{\gamma - 1},
+ C = \frac{c_{p} p_{0}^{\frac{R}{c_{p}}}}{R}.
 \end{equation}
-which can be obtained by setting $p(0) = p_0$.
+
+We now compute the pertubated potential temperature $\potT$ and use \cref{eq:potTToT} to convert it to temperature.
+We then evaluate the density $\Qrho(\bm{x})$ with \cref{eq:temperature}.
+The energy can be computed by inserting the previously computed pressure into the equation of state~(\ref{eq:eos}).
 

### 2018-11-14 writing/thesis/chapters/introduction.tex
Setup latex template.
Rewrite scenarios, add structure, references, etc.

--- 2018-07-18 writing/thesis/chapters/conclusion.tex
@@
-\chapter{Conclusion}
-Conclusion here.
+\chapter{Introduction}
+We make the following contributions:
+
+\begin{itemize}
+\item We implement an \textsc{ader-dg} scheme for the compressible Navier-Stokes equations.
+\item We compare different mesh refinement strategies and evaluate their computational efficiency.
+\item We investigate the ability of our scheme to simulate classical fluid mechanics test scenarios correctly.
+\item We describe the simulation of flows with a background state that is in hydrostatic equilibrium.
+  This is useful for problems in atmospheric flow and for problems in meterology.
+  Furthermore, we evaluate our discretization for these scenarios.
+\end{itemize}
 

### 2018-11-14 writing/thesis/chapters/methods.tex
Rewrite scenarios, add structure, references, etc.

@@
-\chapter{Methods}
-Methods here.\todo{Organize into chapters!}
-
 % TODO: Extract to settings.tex
@@
 
+\chapter{An ADER-DG scheme for the Navier-Stokes Equations}
 \section{Conservative Form}
@@
   \label{eq:conservation-law}
- \frac{\partial}{\partial_t}  Q + \div \cdot F(Q) = S(\bm{x}, t, Q)
+ \frac{\partial}{\partial_t}  Q + \div F(Q) = S(\bm{x}, t, Q)
 \end{equation}
@@
   \label{eq:conservation-law-gradient}
- \frac{\partial}{\partial_t}  Q + \div \cdot F(Q, \grad Q) = S(\bm{x}, t, Q)
+ \frac{\partial}{\partial_t}  Q + \div F(Q, \grad Q) = S(\bm{x}, t, Q)
 \end{equation}
@@
 We describe the arbitrary derivative discontinous Galerkin (ADER-DG) method in this chapter.
+See: \cite{dumbser2018efficient}
 
@@
 where $l$ is a multi-index, containing one index per spatial dimension.
-\todo{dofs $\hat{u}$. local solution, etc.}
+\todo{dofs $\hat{u}$, local solution, etc.}
 For example, $(l = (l_1, l_2))$ for the two dimensional case.
@@
 
-\section{Compressible Euler}
+\section{Compressible Navier Stokes}
+Following~\cite{dumbser2010arbitrary} by \citeauthor{dumbser2010arbitrary}.
+
 Vector of conserved quantities:
@@
 \end{equation}
-
-\newcommand{\eulerFlux}{%
-  \begin{pmatrix}
-    \Qj \\
-    \Qv  \otimes \Qj + \pressure \bm{I}  \\
-    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure)
-  }
-Flux:
-\begin{equation}
-  F(Q) = \eulerFlux
-  \end{pmatrix}
-\end{equation}
-\begin{equation}
-  \pressure = (\gamma - 1) \left(\QE - 0.5 \left(\Qv \cdot \Qj \right) \right)
-\end{equation}
-
-\section{Compressible Navier Stokes}
-Following~\cite{dumbser2010arbitrary} by \citeauthor{dumbser2010arbitrary}.
 
@@
 \begin{align}
+  \begin{split}
   c_v &= \frac{1}{\gamma - 1} R \\
@@
   \gamma &= \frac{c_p}{c_v}
+  \end{split}
 \end{align}
@@
 
-\subsection{Boundary conditions}
+\section{Boundary conditions}
 To close the system we need to impose boundary conditions.
@@
 \begin{align}
+  \label{eq:no-slip}
+  \begin{split}
   \Qrho^o &= \Qrho^i, \\
@@
   {(\nabla Q)}^o &= {(\nabla Q)}^i,
+  \end{split}
 \end{align}
@@
 
-\subsection{Diffusive Flux stuff}
+\section{Diffusive Flux stuff}
 Max eigenvalue of convective part $\maxConvEigen$,i.e.\ of $\left( \partial \bm{F}/\partial \bm{Q}\right) \cdot \bm{n}$,
@@
 
-\section{Scenarios}\label{sec:scenarios}
-
-\subsection{Clouds}
-The scenario is described in terms of potential temperature $\potT$
-\begin{equation}
-  \potT = T \frac{p_0}{p}^{R/c_p},
-\end{equation}
-where $p_o = \SI{10e5}{\Pa}$ is the reference pressure.
-Solving for $T$ leads to
-\begin{equation}
-  \label{eq:potTToT}
-  T = \potT (\frac{p}{p_0})^{R/c_p}.
-\end{equation}
-To allow for an easier description of the initial conditions we split the $\potT$ into a background state $\backgroundPotT$ and a pertubation $\pertubationPotT$
-\begin{equation}
-  \label{eq:potT-split}
-  \potT = \backgroundPotT + \pertubationPotT.
-\end{equation}
-
-The initial conditions for pressure and density can be computed directly from the \textsc{pde} once few assumptions have been given.
-We assume that $\backgroundPotT$ is constant over the entire domain.
-Inserting the definition of potential temperature, given by \cref{eq:potTToT}, into the equation of state (see \cref{eq:eos}) leads us to
-\begin{equation}
-  \label{eq:eos-potT}
-\Qrho(z) = \frac{p_{0}^{\frac{R}{c_{p}}} p^{\frac{1}{\gamma}}{\left (z \right )}}{R \backgroundPotT}.
-\end{equation}
-Flow in hydrostatic equilibrium can now be described by the ordinary differential equation(\textsc{ode})
-\begin{align}
-  \label{eq:hydrostatic-balance-potT}
-  \frac{d}{d z} p{\left (z \right )} &= -g \Qrho(z)
-                                     = 
-        - \frac{g p_{0}^{\frac{R}{c_{p}}} p^{\frac{1}{\gamma}}{\left (z \right )}}{R \backgroundPotT}\\
-  p{\left (0 \right )} &= p_0
-\end{align}
-where we use the reference pressure $p_0$ as the pressure on ground level.
-This \textsc{ode} can be now simply solved by separation of variables.
-After simplifying, we arrive at the initial condition for pressure
-\begin{equation}
-p(z) = \left(\left(1 - \frac{1}{\gamma}\right) \left(C - \frac{g p_{0}^{\frac{R}{c_{p}}} z}{R \backgroundPotT}\right)\right)^{\frac{c_{p}}{R}},
-\end{equation}
-with a constant of integration
-\begin{equation}
-  \label{eq:hydrostatic-balance-constant}
- C = \frac{c_{p} p_{0}^{\frac{R}{c_{p}}}}{R}.
-\end{equation}
-
-We now compute the pertubated potential temperature $\potT$ and use \cref{eq:potTToT} to convert it to temperature.
-We then evaluate the density $\Qrho(\bm{x})$ with \cref{eq:temperature}.
-The energy can be computed by inserting the previously computed pressure into the equation of state~(\ref{eq:eos}).
-
-\section{Convergence}
+\chapter{Scenarios}\label{sec:scenarios}
+\section{Numerical Convergence Test}
 We first define the $L_p$ norms for $p > 0$ by
@@
 
-We derive a source term by inserting this solution into the \textsc{pde} using the symbolic math toolkit \textit{SymPy}.
+We derive a source term by inserting this solution into the \textsc{pde} by using the symbolic math toolkit \textit{SymPy}.
+This procedure is called method of manufactured solutions~\cite{salari2000code}.
+
+\section{Classical Scenarios}
+
+\subsection{The first Stokes Problem}
+\cite{dumbser2010arbitrary}
+\subsection{Taylor-Green Vortex}
+\cite{dumbser2016high}
+
+\section{Atmospheric Scenarios}
+The scenario is described in terms of potential temperature $\potT$
+\begin{equation}
+  \potT = T \frac{p_0}{p}^{R/c_p},
+\end{equation}
+where $p_o = \SI{10e5}{\Pa}$ is the reference pressure.
+Solving for $T$ leads to
+\begin{equation}
+  \label{eq:potTToT}
+  T = \potT (\frac{p}{p_0})^{R/c_p}.
+\end{equation}
+To allow for an easier description of the initial conditions we split the $\potT$ into a background state $\backgroundPotT$ and a pertubation $\pertubationPotT$
+\begin{equation}
+  \label{eq:potT-split}
+  \potT = \backgroundPotT + \pertubationPotT.
+\end{equation}
+
+The initial conditions for pressure and density can be computed directly from the \textsc{pde} once few assumptions have been given.
+We assume that $\backgroundPotT$ is constant over the entire domain.
+Inserting the definition of potential temperature, given by \cref{eq:potTToT}, into the equation of state (see \cref{eq:eos}) leads us to
+\begin{equation}
+  \pressure(z) = \Qrho(z) R {\left( \backgroundPotT \frac{p}{p_0}\right)}^{R/c_p},
+\end{equation}
+which we solve for $p(z)$.
+After some algebra and simplifying, we arrive at
+\begin{equation}
+ p(z) = p_0 \left( \frac{R \backgroundPotT \rho(z)}{p_0} \right)^{\gamma},
+\end{equation}
+or equivalently
+\begin{equation}
+  \label{eq:eos-potT}
+\Qrho(z) = \frac{p_{0}^{\frac{R}{c_{p}}} p^{\frac{1}{\gamma}}{\left (z \right )}}{R \backgroundPotT}.
+\end{equation}
+We want to consider flow in hydrostatic equilibrium, i.e.\ flow where the force originating from the pressure-gradient is exactly balanced by gravitation.
+Inserting this assumption in the momentum equation in $z$-direction and using \cref{eq:eos} once again, we arrive at the ordinary differential equation (\textsc{ode})
+\begin{align}
+  \label{eq:hydrostatic-balance-potT}
+  \begin{split}
+  \frac{d}{d z} p{\left (z \right )} &= -g \Qrho(z)
+                                     = 
+        - \frac{g p_{0}^{\frac{R}{c_{p}}} p^{\frac{1}{\gamma}}{\left (z \right )}}{R \backgroundPotT}\\
+  p{\left (0 \right )} &= p_0
+  \end{split}
+\end{align}
+where we use the reference pressure $p_0$ as the pressure on ground level.
+This \textsc{ode} can be now simply solved by separation of variables.
+After simplifying, we arrive at the initial condition for pressure
+\begin{align}
+  \label{eq:hydrostatic-background-pressure}
+p(z) &= \left(\left(1 - \frac{1}{\gamma}\right) \left(C - \frac{g p_{0}^{\frac{R}{c_{p}}} z}{R \backgroundPotT}\right)\right)^{\frac{c_{p}}{R}},\\
+\shortintertext{with constant of integration}
+ C &= \frac{c_{p} p_{0}^{\frac{R}{c_{p}}}}{R}.
+\end{align}
+
+We now compute the pertubated potential temperature $\potT$ and use \cref{eq:potTToT} to convert it to temperature.
+We then evaluate the density $\Qrho(\bm{x})$ with \cref{eq:temperature}.
+The energy can be computed by inserting the previously computed pressure into the equation of state~(\ref{eq:eos}).
+
+This leaves us with one problem:
+The adiabatic no-slip boundary conditions defined by~\vref{eq:no-slip} are no longer valid.
+Concretely, we need to impose a viscous heat flux to ensure that the atmosphere stays in hydrostatic balance~\cite{giraldo2008study}
+\todo{Flux correct? Fix notation}
+\begin{equation}
+  \label{eq:atmosphere-bc}
+  F^\text{visc} = \kappa \pdv{\overline{T}}{z} =
+\frac{R \overline{\theta} \left(\frac{\overline{p}{\left (z \right )}}{p_{0}}\right)^{\frac{R}{c_{p}}} \frac{d}{d z} \overline{p}{\left (z \right )}}{c_{p} \overline{p}{\left (z \right )}}.
+\end{equation}
+The background pressure can be reconstructed by \cref{eq:hydrostatic-background-pressure}, its derivative is given by \cref{eq:hydrostatic-balance-potT}.
+
+\subsection{Robert's smooth bubble}
+\cite{robert1993bubble}
+\subsection{Density current}
+\cite{straka1993numerical}
 

### 2018-11-21 writing/thesis/chapters/methods.tex
Further work on ADER-DG, NS, AMR

@@
 \newcommand{\maxViscEigen}{\vert \lambda_v^{\text{max}} \vert}
+\newcommand{\Riemann}{\operatorname{Riemann}}
 
@@
 \newcommand{\testfunction}[1]{\Phi_{#1}}
+\newcommand{\normal}{\bm{n}}
+\newcommand{\source}{\bm{S}}
 
@@
 \right)
-\left(\intdt{\intdcellb{
-\text{dofs boundary time}
+(\bm{u^{n+1} - u^{n}})
++
+\left(\intdt{\intdcell{
+      \testfunction{k} \Riemann(\bm{q}^-, \bm{q}^+) \cdot \normal
 }}\right)
-&+\\
+&-\\
 \left(\intdt{\intdcell{
-\text{Riemann}
-}}\right)
--
-\left(\intdt{\intdcell{
-\text{Flux}
+    \gradient{\testfunction{k}} \cdot  F(\bm{q})
 }}\right)
@@
 \left(\intdt{\intdcell{
-  \text{Source}
+      \testfunction{k} \source(\bm{q})
 }}\right)
@@
 
+\sidetitle{Diffusive Flux stuff}
+Numerical flux:
+\begin{equation}
+  \label{eq:rusanov-flux}
+  \Riemann(q_h^-, \nabla q_h^-; g_h^+, \nabla q_h^+) \cdot \bm{n} =
+  \frac{1}{2} \left(
+    F(q_h^+, \nabla q_h^+) +
+    F(q_h^-, \nabla q_h^-)
+  \right) -
+  \frac{1}{2} s_\text{max} (q_h^+ - q_h^-)
+\end{equation}
+with
+\begin{equation}
+  \label{eq:parabolic-penalty}
+  s_\text{max}  = \max \left(
+\vert \lambda_c(q_h^-) \vert, \, \vert \lambda_c(q_h^+)
+\right) +
+2 \eta \max \left(
+\vert \lambda_v(q_h^-) \vert, \, \vert \lambda_v(q_h^+)
+\right)
+\end{equation}
+and
+\begin{equation}
+  \eta = \frac{2N+1}{h \sqrt{\frac{1}{2} \pi}}
+\end{equation}
+
+Maximum timestep (\textsc{cfl})
+\begin{equation}
+ \Delta t \leq  \text{CFL} \, \frac{\alpha(N) \, h}{\maxConvEigen + 2 \maxViscEigen \frac{2N+1}{h}}
+\end{equation}
+with $N$ polynomial order and $h$ characteristic length scale of elements~\cite{dumbser2010arbitrary,gassner2008discontinuous}.
+The constant $\alpha(N) \leq \frac{1}{2N+1}$ is obtained from von Neumann analysis on a simple model problem and depends on the approximation order~\cite{dumbser2008unified}.
+
 \section{Compressible Navier Stokes}
-Following~\cite{dumbser2010arbitrary} by \citeauthor{dumbser2010arbitrary}.
+Fluid motion can be described by the compressible Navier Stokes equations.
+We follow the description in~\cite{dumbser2010arbitrary}.
 
-Vector of conserved quantities:
+The vector of conserved quantities is given by
 \begin{equation}
   \label{eq:conserved-variables}
- Q = \left( \Qrho, \Qj, \QE \right) 
+ Q = \left( \Qrho, \Qj, \QE \right).
 \end{equation}
-
-The full compressible Navier Stokes equations with heat transfer can be described by
+The flux by
 \begin{equation}
@@
 
-We use the equation of state of an ideal gas
+We close the system with the equation of state of an ideal gas
 \begin{equation}
@@
 \end{equation}
-
 The temperature $T$ relates to pressure and density by the ideal gas law
@@
 
-\todo{Write more text about constants, cite idolikecfd or sth}
+We further introduce the ratio of specific heats $\gamma$ and the heat fraction for constant volume $c_v$ and constant volume $c_r$.
+These constants are all fluid dependent and relate to each other by
 \begin{align}
@@
   R &= c_p - c_v\\
-  \gamma &= \frac{c_p}{c_v}
+  \gamma &= \frac{c_p}{c_v}.
   \end{split}
 \end{align}
+\todo{Cite sth!}
 
-Heat conduction coefficient $\kappa$
+We can finally define the heat conduction coefficient $\kappa$
 \begin{equation}
@@
 \end{equation}
-with $R$ gas constant and $\Pr$ Prandtl number
+where Prandtl number $\text{Pr}$ again depends on the fluid.
 
@@
 \end{equation}
+
+Max eigenvalue of convective part $\maxConvEigen$,i.e.\ of $\left( \partial \bm{F}/\partial \bm{Q}\right) \cdot \bm{n}$,
+and viscous part $maxViscEigen$, i.e.\ of $\left( \partial \bm{F}/\partial \left( \nabla \bm{Q} \cdot \bm{n} \right)\right) \cdot \bm{n}$
+is
+\begin{align}
+  \maxConvEigen \vert  &= \Vert \Qv \Vert + c\\
+  \maxViscEigen \vert &= \max \left( \frac{4}{3} \frac{\mu}{\Qrho}
+                                       , \frac{\gamma \mu}{\Pr \Qrho} \right)
+\end{align}
+with speed of sound $c = \sqrt{\gamma R T }$
 
@@
 
-\section{Diffusive Flux stuff}
-Max eigenvalue of convective part $\maxConvEigen$,i.e.\ of $\left( \partial \bm{F}/\partial \bm{Q}\right) \cdot \bm{n}$,
-and viscous part $maxViscEigen$, i.e.\ of $\left( \partial \bm{F}/\partial \left( \nabla \bm{Q} \cdot \bm{n} \right)\right) \cdot \bm{n}$
-is
-\begin{align}
-  \maxConvEigen \vert  &= \Vert \Qv \Vert + c\\
-  \maxViscEigen \vert &= \max \left( \frac{4}{3} \frac{\mu}{\Qrho}
-                                       , \frac{\gamma \mu}{\Pr \Qrho} \right)
-\end{align}
-with speed of sound $c = \sqrt{\gamma R T }$
+\section{Adaptive Mesh Refinement}
+\label{sec:amr}
+We use adaptive mesh refinement (\textsc{amr}).
 
-Maximum timestep (\textsc{cfl})
+Use total variation (\textsc{tv}) given by
 \begin{equation}
- \Delta t = \frac{\text{CFL}}{2N + 1} \, \frac{h}{\maxConvEigen + 2 \maxViscEigen \frac{2N+1}{h}}
+  \label{eq:tv}
+  \operatorname{TV}\left( f \right) =
+\intdcell{ \vert \gradient{f} \vert }
 \end{equation}
-with $N$ polynomial order and $h$ characteristic length scale of elements
 
-Numerical flux:
-\begin{equation}
-  \label{eq:rusanov-flux}
-  G(q_h^-, \nabla q_h^-; g_h^+, \nabla q_h^+) \cdot \bm{n} =
-  \frac{1}{2} \left(
-    F(q_h^+, \nabla q_h^+) +
-    F(q_h^-, \nabla q_h^-)
-  \right) -
-  \frac{1}{2} s_\text{max} (q_h^+ - q_h^-)
-\end{equation}
-with
-\begin{equation}
-  \label{eq:parabolic-penalty}
-  s_\text{max}  = \max \left(
-\vert \lambda_c(q_h^-) \vert, \, \vert \lambda_c(q_h^+)
-\right) +
-2 \eta \max \left(
-\vert \lambda_v(q_h^-) \vert, \, \vert \lambda_v(q_h^+)
-\right)
-\end{equation}
-and
-\begin{equation}
-  \eta = \frac{N+1}{h}
-\end{equation}
+We introduce parallel reduce.
+
+Reduce mean/std by~\cite{chan1982updating}
+
+Criterion with threshold.
+Justify by Chebychev's inequality?
 
@@
 
-We derive a source term by inserting this solution into the \textsc{pde} by using the symbolic math toolkit \textit{SymPy}.
+We derive a source term by inserting this solution into the \textsc{pde} by using the symbolic math toolkit \textit{Sage}.
 This procedure is called method of manufactured solutions~\cite{salari2000code}.

### 2018-11-21 writing/thesis/pages/abstract.tex
Setup latex template.
Further work on ADER-DG, NS, AMR

--- 2018-07-18 writing/thesis/chapters/conclusion.tex
@@
-\chapter{Conclusion}
-Conclusion here.
+\chapter{\abstractname}
+This thesis is concerned with the simulation of clouds with the ExaHyPE framework.
+ExaHyPE is an engine for hyperbolic PDEs that uses the ADER-DG scheme.
+
+We use the compressible Navier-Stokes (NS) equations with heat conduction to describe the dynamics of clouds.
+Due to the diffusive components, the NS-Equations are not hyperbolic.
+We thus need to modify parts of the numerical scheme.
 

### 2018-12-03 deploy.sh
Try amending last commit on travis.

@@ -23,5 +23,5 @@ git reset upstream/pdf
 touch main.pdf
 
 git add main.pdf
-git commit -m "rebuild pages at ${rev}"
-git push -q upstream HEAD:pdf
+git commit --amend -m "rebuild pages at ${rev}"
+git push --force-with-lease -q upstream HEAD:pdf

### 2018-12-03 writing/thesis/chapters/methods.tex
Split into chapters, some additional work.

@@
 % TODO: Extract to settings.tex
+
+% Variables and other equation stuff
+\newcommand{\Q}{\bm{Q}}
+\newcommand{\gradQ}{\gradient{\Q}}
 \newcommand{\Qrho}{\rho}
 \newcommand{\Qj}{\rho \bm{v}}
-%\newcommand{\Qv}{\ensuremath{\Qrho^{-1} \Qj}}
 \newcommand{\Qv}{\bm{v}}
 \newcommand{\QE}{\rho E}
+\newcommand{\QZZ}{Z} % TODO: Name?
+\newcommand{\QZ}{\rho \QZZ}
 \newcommand{\potT}{\theta}
@@
 
+% Stuff for numerics
 \newcommand{\domain}{\Omega}
@@
 \newcommand{\normal}{\bm{n}}
+
+% Equation parts
+\newcommand{\flux}{F}
+\newcommand{\viscFlux}{\flux^{v}}
+\newcommand{\hyperFlux}{\flux^{h}}
 \newcommand{\source}{\bm{S}}
+
+% Integrals
+\newcommand{\intdt}[1]{\int_{t^n}^{t^{n+1}} #1 \dd{t}}
+\newcommand{\intdcell}[1]{\int_{\cell} #1 \dd{\bm{x}}}
+\newcommand{\intdcellb}[1]{\int_{\partial{} \cell} #1 \dd{S}} % TODO: define boundary of cell
 
@@
   \label{eq:conservation-law}
- \frac{\partial}{\partial_t}  Q + \div F(Q) = S(\bm{x}, t, Q)
+ \frac{\partial}{\partial_t}  \Q + \div \flux(\Q) = \source(\bm{x}, t, \Q)
 \end{equation}
@@
   \label{eq:conservation-law-gradient}
- \frac{\partial}{\partial_t}  Q + \div F(Q, \grad Q) = S(\bm{x}, t, Q)
+ \frac{\partial}{\partial_t}  \Q + \div \flux(\Q, \gradQ) = \source(\bm{x}, t, \Q)
 \end{equation}
@@
 We arrive at the so called weak formulation of the \textsc{pde} 
-\newcommand{\intdt}[1]{\int_{t^n}^{t^{n+1}} #1 \dd{t}}
-\newcommand{\intdcell}[1]{\int_{\cell} #1 \dd{\bm{x}}}
-\newcommand{\intdcellb}[1]{\int_{\partial{} \cell} #1 \dd{S}} % TODO: define boundary of cell
 \begin{equation}
@@
 Fluid motion can be described by the compressible Navier Stokes equations.
-We follow the description in~\cite{dumbser2010arbitrary}.
+We follow the description in~\cite{dumbser2010arbitrary} for the Navier Stokes part.
+The coupling with the advection-diffusion-reaction equations follows~\cite{hidalgo2011ader}.
 
@@
   \label{eq:conserved-variables}
- Q = \left( \Qrho, \Qj, \QE \right).
+ \Q = \left( \Qrho, \Qj, \QE \QZ \right).
 \end{equation}
-The flux by
+where $\Qrho$ is the density, $\Qj$ is the momentum, $\QE$ the energy density and $\QZ$ is the mass fraction of the chemical reactant.
+
+We split the flux into a hyperbolic part $\hyperFlux(\Q)$ and an viscous flux $\viscFlux(\gradQ)$
 \begin{equation}
-  F(Q, \nabla Q) = 
+  \label{eq:flux}
+  \flux(\Q, \gradQ) = \hyperFlux(\Q) + \viscFlux(\Q, \gradQ)
+\end{equation}
+
+The hyperbolic flux is given by
+\begin{equation}
+  \label{eq:hyper-flux}
+  \hyperFlux(\Q) = 
   \begin{pmatrix}
     \Qj \\
-    \Qv  \otimes \Qj + \bm{I} \pressure + \stressT (Q, \nabla Q)  \\
-    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure + \stressT (Q, \nabla Q)) - \kappa \nabla T
+    \Qv  \otimes \Qj + \bm{I} \pressure  \\
+    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure) \\
+    \Qj \QZZ
   \end{pmatrix},
 \end{equation}
+which are the Euler equations coupled with an advection equation.
+\newcommand{\diffCoeff}{\varepsilon}
+The viscous flux is
+\begin{equation}
+  \label{eq:visc-flux}
+  \viscFlux(\Q, \gradQ) = 
+  \begin{pmatrix}
+    -\diffCoeff \gradient{\Qrho}\\
+    \stressT (\Q, \gradQ)  \\
+    \Qv \cdot \stressT (\Q, \gradQ) - \kappa \gradient{T}\\
+    -\diffCoeff \gradient{\QZ}
+  \end{pmatrix},
+\end{equation}
+
+% \begin{equation}
+%   F(Q, \nabla Q) = 
+%   \begin{pmatrix}
+%     \Qj \\
+%     \Qv  \otimes \Qj + \bm{I} \pressure + \stressT (Q, \nabla Q)  \\
+%     \Qv \cdot (\bm{I} \QE + \bm{I} \pressure + \stressT (Q, \nabla Q)) - \kappa \nabla T
+%   \end{pmatrix},
+% \end{equation}
 where $\pressure$, $\stressT$ and $(\kappa \nabla T)$ denote the pressure, stress tensor and heat flux respectively.
@@
   \label{eq:eos}
-  \pressure = (\gamma - 1) \left(\QE - 0.5 \left(\Qv \cdot \Qj \right) \right).
+  \pressure = (\gamma - 1) \left(\QE - \frac{1}{2} \left(\Qv \cdot \Qj \right)  - q_0 \QZ \right).
 \end{equation}
+%The term $\q_0 \QZ$ corresponds to the chemical energy.
 The temperature $T$ relates to pressure and density by the ideal gas law
@@
 Max eigenvalue of convective part $\maxConvEigen$,i.e.\ of $\left( \partial \bm{F}/\partial \bm{Q}\right) \cdot \bm{n}$,
-and viscous part $maxViscEigen$, i.e.\ of $\left( \partial \bm{F}/\partial \left( \nabla \bm{Q} \cdot \bm{n} \right)\right) \cdot \bm{n}$
+and viscous part $\maxViscEigen$, i.e.\ of $\left( \partial \bm{F}/\partial \left( \nabla \bm{Q} \cdot \bm{n} \right)\right) \cdot \bm{n}$
 is
@@
 
-\chapter{Scenarios}\label{sec:scenarios}
-\section{Numerical Convergence Test}
-We first define the $L_p$ norms for $p > 0$ by
-% notation: https://en.wikipedia.org/wiki/Lp_space#Lp_spaces
-\begin{equation}
-  \label{eq:Lp-nrom}
-  \Vert f(x) \Vert = \left( \int_K \vert f(x) \vert^p d\mu  \right)^{1/p}.
-\end{equation}
-We start by a known analytical solution $f(x)$ and compare it to our approximation $\hat{f}(x)$.
-Let $Q$ and $\hat{Q}$ denote the analytical and approximate solution at node.
-We start by computing the point-wise error, and compute the cell-wise error from this.
-Observe that for our broken space $\Omega$
-\begin{equation}
-  \label{eq:lp-norm-broken}
- \Vert f(x) \Vert = \sum_{K \in \Omega} \Vert f_K(x) \Vert_p.
-\end{equation}
-
-We are now ready to integrate the error for each cell.
-The output contains the position and conserved variables of each point.
-Each cell consists of $(N + 1)^d$ nodes, each associated with a quadrature weight $w_i$.
-The quadrature weights are associated with the reference cuboid.
-We thus need to map our element to the reference element, before we can compute the integral.
-
-Let $V$ denote the volume (or area) of each cell.
-For example, in three dimensions $V = \Delta x \, \Delta y \, \Delta z$.
-The final result is then
-\begin{equation}
-  \Vert f_K(x) \Vert = \left( V \sum_{\bm{i}} \vert f(\bm{x}_{\bm{i}}) \vert^p w_{{\bm{i}}}  \right)^{1/p},
-\end{equation}
-where we used the mapping to the reference triangle (integration by substitution).
-
-Following~\cite{dumbser2010arbitrary}, the scenario can be described in primitive variables by setting
-\begin{align}
-  \pressure &= \pressure_0 \cos( \bm{k} \bm{x} - \omega t ) + \pressure_b, \\
-  \Qrho &= \Qrho_0 \sin (\bm{k} \bm{x} - \omega t) + \Qrho_b, \\
-  \Qv &= \bm{v_0} \sin(\bm{k} \bm{x} - \omega t).
-\end{align}
-We set the constants to \( \left(  \pressure_0 = 0.1, \pressure_b = \gamma^{-1}, \Qrho_0 = 0.5, \Qrho_b = 1, 
-\bm{v_0} = 0.25 {(1,1)}^\intercal, \bm{k} = \pi/5 {(1,1)}^\intercal \right) \).
-
-We derive a source term by inserting this solution into the \textsc{pde} by using the symbolic math toolkit \textit{Sage}.
-This procedure is called method of manufactured solutions~\cite{salari2000code}.
-
-\section{Classical Scenarios}
-
-\subsection{The first Stokes Problem}
-\cite{dumbser2010arbitrary}
-\subsection{Taylor-Green Vortex}
-\cite{dumbser2016high}
-
-\section{Atmospheric Scenarios}
-The scenario is described in terms of potential temperature $\potT$
-\begin{equation}
-  \potT = T \frac{p_0}{p}^{R/c_p},
-\end{equation}
-where $p_o = \SI{10e5}{\Pa}$ is the reference pressure.
-Solving for $T$ leads to
-\begin{equation}
-  \label{eq:potTToT}
-  T = \potT (\frac{p}{p_0})^{R/c_p}.
-\end{equation}
-To allow for an easier description of the initial conditions we split the $\potT$ into a background state $\backgroundPotT$ and a pertubation $\pertubationPotT$
-\begin{equation}
-  \label{eq:potT-split}
-  \potT = \backgroundPotT + \pertubationPotT.
-\end{equation}
-
-The initial conditions for pressure and density can be computed directly from the \textsc{pde} once few assumptions have been given.
-We assume that $\backgroundPotT$ is constant over the entire domain.
-Inserting the definition of potential temperature, given by \cref{eq:potTToT}, into the equation of state (see \cref{eq:eos}) leads us to
-\begin{equation}
-  \pressure(z) = \Qrho(z) R {\left( \backgroundPotT \frac{p}{p_0}\right)}^{R/c_p},
-\end{equation}
-which we solve for $p(z)$.
-After some algebra and simplifying, we arrive at
-\begin{equation}
- p(z) = p_0 \left( \frac{R \backgroundPotT \rho(z)}{p_0} \right)^{\gamma},
-\end{equation}
-or equivalently
-\begin{equation}
-  \label{eq:eos-potT}
-\Qrho(z) = \frac{p_{0}^{\frac{R}{c_{p}}} p^{\frac{1}{\gamma}}{\left (z \right )}}{R \backgroundPotT}.
-\end{equation}
-We want to consider flow in hydrostatic equilibrium, i.e.\ flow where the force originating from the pressure-gradient is exactly balanced by gravitation.
-Inserting this assumption in the momentum equation in $z$-direction and using \cref{eq:eos} once again, we arrive at the ordinary differential equation (\textsc{ode})
-\begin{align}
-  \label{eq:hydrostatic-balance-potT}
-  \begin{split}
-  \frac{d}{d z} p{\left (z \right )} &= -g \Qrho(z)
-                                     = 
-        - \frac{g p_{0}^{\frac{R}{c_{p}}} p^{\frac{1}{\gamma}}{\left (z \right )}}{R \backgroundPotT}\\
-  p{\left (0 \right )} &= p_0
-  \end{split}
-\end{align}
-where we use the reference pressure $p_0$ as the pressure on ground level.
-This \textsc{ode} can be now simply solved by separation of variables.
-After simplifying, we arrive at the initial condition for pressure
-\begin{align}
-  \label{eq:hydrostatic-background-pressure}
-p(z) &= \left(\left(1 - \frac{1}{\gamma}\right) \left(C - \frac{g p_{0}^{\frac{R}{c_{p}}} z}{R \backgroundPotT}\right)\right)^{\frac{c_{p}}{R}},\\
-\shortintertext{with constant of integration}
- C &= \frac{c_{p} p_{0}^{\frac{R}{c_{p}}}}{R}.
-\end{align}
-
-We now compute the pertubated potential temperature $\potT$ and use \cref{eq:potTToT} to convert it to temperature.
-We then evaluate the density $\Qrho(\bm{x})$ with \cref{eq:temperature}.
-The energy can be computed by inserting the previously computed pressure into the equation of state~(\ref{eq:eos}).
-
-This leaves us with one problem:
-The adiabatic no-slip boundary conditions defined by~\vref{eq:no-slip} are no longer valid.
-Concretely, we need to impose a viscous heat flux to ensure that the atmosphere stays in hydrostatic balance~\cite{giraldo2008study}
-\todo{Flux correct? Fix notation}
-\begin{equation}
-  \label{eq:atmosphere-bc}
-  F^\text{visc} = \kappa \pdv{\overline{T}}{z} =
-\frac{R \overline{\theta} \left(\frac{\overline{p}{\left (z \right )}}{p_{0}}\right)^{\frac{R}{c_{p}}} \frac{d}{d z} \overline{p}{\left (z \right )}}{c_{p} \overline{p}{\left (z \right )}}.
-\end{equation}
-The background pressure can be reconstructed by \cref{eq:hydrostatic-background-pressure}, its derivative is given by \cref{eq:hydrostatic-balance-potT}.
-
-\subsection{Robert's smooth bubble}
-\cite{robert1993bubble}
-\subsection{Density current}
-\cite{straka1993numerical}
-
 %%% Local Variables:

### 2018-12-03 writing/thesis/chapters/results.tex
Split into chapters, some additional work.

\chapter{Results}
\section{Convergence Test}
\section{Accurate CFD}
\section{Accurate Clouds}
\section{AMR Efficiency}
\section{Reactive Euler \textit{\&} Navier Stokes}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:

### 2018-12-03 writing/thesis/chapters/scenarios.tex
Split into chapters, some additional work.

\chapter{Scenarios}\label{sec:scenarios}
\section{Numerical Convergence Test}
We first define the $L_p$ norms for $p > 0$ by
% notation: https://en.wikipedia.org/wiki/Lp_space#Lp_spaces
\begin{equation}
  \label{eq:Lp-nrom}
  \Vert f(x) \Vert = \left( \int_K \vert f(x) \vert^p d\mu  \right)^{1/p}.
\end{equation}
We start by a known analytical solution $f(x)$ and compare it to our approximation $\hat{f}(x)$.
Let $Q$ and $\hat{Q}$ denote the analytical and approximate solution at node.
We start by computing the point-wise error, and compute the cell-wise error from this.
Observe that for our broken space $\Omega$
\begin{equation}
  \label{eq:lp-norm-broken}
 \Vert f(x) \Vert = \sum_{K \in \Omega} \Vert f_K(x) \Vert_p.
\end{equation}

We are now ready to integrate the error for each cell.
The output contains the position and conserved variables of each point.
Each cell consists of $(N + 1)^d$ nodes, each associated with a quadrature weight $w_i$.
The quadrature weights are associated with the reference cuboid.
We thus need to map our element to the reference element, before we can compute the integral.

Let $V$ denote the volume (or area) of each cell.
For example, in three dimensions $V = \Delta x \, \Delta y \, \Delta z$.
The final result is then
\begin{equation}
  \Vert f_K(x) \Vert = \left( V \sum_{\bm{i}} \vert f(\bm{x}_{\bm{i}}) \vert^p w_{{\bm{i}}}  \right)^{1/p},
\end{equation}
where we used the mapping to the reference triangle (integration by substitution).

Following~\cite{dumbser2010arbitrary}, the scenario can be described in primitive variables by setting
\begin{align}
  \pressure &= \pressure_0 \cos( \bm{k} \bm{x} - \omega t ) + \pressure_b, \\
  \Qrho &= \Qrho_0 \sin (\bm{k} \bm{x} - \omega t) + \Qrho_b, \\
  \Qv &= \bm{v_0} \sin(\bm{k} \bm{x} - \omega t).
\end{align}
We set the constants to \( \left(  \pressure_0 = 0.1, \pressure_b = \gamma^{-1}, \Qrho_0 = 0.5, \Qrho_b = 1, 
\bm{v_0} = 0.25 {(1,1)}^\intercal, \bm{k} = \pi/5 {(1,1)}^\intercal \right) \).

We derive a source term by inserting this solution into the \textsc{pde} by using the symbolic math toolkit \textit{Sage}~\cite{sagemath}.
This procedure is called method of manufactured solutions~\cite{salari2000code}.

\section{Classical Scenarios}

\subsection{The first Stokes Problem}
\cite{dumbser2010arbitrary}
\subsection{Taylor-Green Vortex}
\begin{align}
  \begin{split}
  \Qv(\bm{x}, t) &= \exp(-2 \mu t)
  \begin{pmatrix}
    \phantom{-}\sin(x) cos(y) \\
- \cos(x) sin(y) 
    \end{pmatrix} \\
  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \frac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C
  \end{split}
\end{align}
\todo{Constants!}
$C = 100/\gamma$ \cite{dumbser2016high}

\section{Atmospheric Scenarios}
The scenario is described in terms of potential temperature $\potT$
\begin{equation}
  \potT = T \frac{p_0}{p}^{R/c_p},
\end{equation}
where $p_o = \SI{10e5}{\Pa}$ is the reference pressure.
Solving for $T$ leads to
\begin{equation}
  \label{eq:potTToT}
  T = \potT (\frac{p}{p_0})^{R/c_p}.
\end{equation}
To allow for an easier description of the initial conditions we split the $\potT$ into a background state $\backgroundPotT$ and a pertubation $\pertubationPotT$
\begin{equation}
  \label{eq:potT-split}
  \potT = \backgroundPotT + \pertubationPotT.
\end{equation}

The initial conditions for pressure and density can be computed directly from the \textsc{pde} once few assumptions have been given.
We assume that $\backgroundPotT$ is constant over the entire domain.
Inserting the definition of potential temperature, given by \cref{eq:potTToT}, into the equation of state (see \cref{eq:eos}) leads us to
\begin{equation}
  \pressure(z) = \Qrho(z) R {\left( \backgroundPotT \frac{p}{p_0}\right)}^{R/c_p},
\end{equation}
which we solve for $p(z)$.
After some algebra and simplifying, we arrive at
\begin{equation}
 p(z) = p_0 \left( \frac{R \backgroundPotT \rho(z)}{p_0} \right)^{\gamma},
\end{equation}
or equivalently
\begin{equation}
  \label{eq:eos-potT}
\Qrho(z) = \frac{p_{0}^{\frac{R}{c_{p}}} p^{\frac{1}{\gamma}}{\left (z \right )}}{R \backgroundPotT}.
\end{equation}
We want to consider flow in hydrostatic equilibrium, i.e.\ flow where the force originating from the pressure-gradient is exactly balanced by gravitation.
Inserting this assumption in the momentum equation in $z$-direction and using \cref{eq:eos} once again, we arrive at the ordinary differential equation (\textsc{ode})
\begin{align}
  \label{eq:hydrostatic-balance-potT}
  \begin{split}
  \frac{d}{d z} p{\left (z \right )} &= -g \Qrho(z)
                                     = 
        - \frac{g p_{0}^{\frac{R}{c_{p}}} p^{\frac{1}{\gamma}}{\left (z \right )}}{R \backgroundPotT}\\
  p{\left (0 \right )} &= p_0
  \end{split}
\end{align}
where we use the reference pressure $p_0$ as the pressure on ground level.
This \textsc{ode} can be now simply solved by separation of variables.
After simplifying, we arrive at the initial condition for pressure
\begin{align}
  \label{eq:hydrostatic-background-pressure}
p(z) &= \left(\left(1 - \frac{1}{\gamma}\right) \left(C - \frac{g p_{0}^{\frac{R}{c_{p}}} z}{R \backgroundPotT}\right)\right)^{\frac{c_{p}}{R}},\\
\shortintertext{with constant of integration}
 C &= \frac{c_{p} p_{0}^{\frac{R}{c_{p}}}}{R}.
\end{align}

We now compute the pertubated potential temperature $\potT$ and use \cref{eq:potTToT} to convert it to temperature.
We then evaluate the density $\Qrho(\bm{x})$ with \cref{eq:temperature}.
The energy can be computed by inserting the previously computed pressure into the equation of state~(\ref{eq:eos}).

This leaves us with one problem:
The adiabatic no-slip boundary conditions defined by~\vref{eq:no-slip} are no longer valid.
Concretely, we need to impose a viscous heat flux to ensure that the atmosphere stays in hydrostatic balance~\cite{giraldo2008study}
\todo{Flux correct? Fix notation}
\begin{equation}
  \label{eq:atmosphere-bc}
  F^\text{visc} = \kappa \pdv{\overline{T}}{z} =
\frac{R \overline{\theta} \left(\frac{\overline{p}{\left (z \right )}}{p_{0}}\right)^{\frac{R}{c_{p}}} \frac{d}{d z} \overline{p}{\left (z \right )}}{c_{p} \overline{p}{\left (z \right )}}.
\end{equation}
The background pressure can be reconstructed by \cref{eq:hydrostatic-background-pressure}, its derivative is given by \cref{eq:hydrostatic-balance-potT}.

\subsection{Robert's smooth bubble}
\cite{robert1993bubble}
\subsection{Density current}
\cite{straka1993numerical}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:

### 2018-12-08 writing/thesis/chapters/implementation.tex
Some more work.

--- 2018-12-03 writing/thesis/chapters/scenarios.tex
@@
-\chapter{Scenarios}\label{sec:scenarios}
-\section{Numerical Convergence Test}
-We first define the $L_p$ norms for $p > 0$ by
-% notation: https://en.wikipedia.org/wiki/Lp_space#Lp_spaces
-\begin{equation}
-  \label{eq:Lp-nrom}
-  \Vert f(x) \Vert = \left( \int_K \vert f(x) \vert^p d\mu  \right)^{1/p}.
-\end{equation}
-We start by a known analytical solution $f(x)$ and compare it to our approximation $\hat{f}(x)$.
-Let $Q$ and $\hat{Q}$ denote the analytical and approximate solution at node.
-We start by computing the point-wise error, and compute the cell-wise error from this.
-Observe that for our broken space $\Omega$
-\begin{equation}
-  \label{eq:lp-norm-broken}
- \Vert f(x) \Vert = \sum_{K \in \Omega} \Vert f_K(x) \Vert_p.
-\end{equation}
+\chapter{Implementation}\label{chap:implementation}
+\todo{Write this chapter!}
 
-We are now ready to integrate the error for each cell.
-The output contains the position and conserved variables of each point.
-Each cell consists of $(N + 1)^d$ nodes, each associated with a quadrature weight $w_i$.
-The quadrature weights are associated with the reference cuboid.
-We thus need to map our element to the reference element, before we can compute the integral.
-
-Let $V$ denote the volume (or area) of each cell.
-For example, in three dimensions $V = \Delta x \, \Delta y \, \Delta z$.
-The final result is then
-\begin{equation}
-  \Vert f_K(x) \Vert = \left( V \sum_{\bm{i}} \vert f(\bm{x}_{\bm{i}}) \vert^p w_{{\bm{i}}}  \right)^{1/p},
-\end{equation}
-where we used the mapping to the reference triangle (integration by substitution).
-
-Following~\cite{dumbser2010arbitrary}, the scenario can be described in primitive variables by setting
-\begin{align}
-  \pressure &= \pressure_0 \cos( \bm{k} \bm{x} - \omega t ) + \pressure_b, \\
-  \Qrho &= \Qrho_0 \sin (\bm{k} \bm{x} - \omega t) + \Qrho_b, \\
-  \Qv &= \bm{v_0} \sin(\bm{k} \bm{x} - \omega t).
-\end{align}
-We set the constants to \( \left(  \pressure_0 = 0.1, \pressure_b = \gamma^{-1}, \Qrho_0 = 0.5, \Qrho_b = 1, 
-\bm{v_0} = 0.25 {(1,1)}^\intercal, \bm{k} = \pi/5 {(1,1)}^\intercal \right) \).
-
-We derive a source term by inserting this solution into the \textsc{pde} by using the symbolic math toolkit \textit{Sage}~\cite{sagemath}.
-This procedure is called method of manufactured solutions~\cite{salari2000code}.
-
-\section{Classical Scenarios}
-
-\subsection{The first Stokes Problem}
-\cite{dumbser2010arbitrary}
-\subsection{Taylor-Green Vortex}
-\begin{align}
-  \begin{split}
-  \Qv(\bm{x}, t) &= \exp(-2 \mu t)
-  \begin{pmatrix}
-    \phantom{-}\sin(x) cos(y) \\
-- \cos(x) sin(y) 
-    \end{pmatrix} \\
-  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \frac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C
-  \end{split}
-\end{align}
-\todo{Constants!}
-$C = 100/\gamma$ \cite{dumbser2016high}
-
-\section{Atmospheric Scenarios}
-The scenario is described in terms of potential temperature $\potT$
-\begin{equation}
-  \potT = T \frac{p_0}{p}^{R/c_p},
-\end{equation}
-where $p_o = \SI{10e5}{\Pa}$ is the reference pressure.
-Solving for $T$ leads to
-\begin{equation}
-  \label{eq:potTToT}
-  T = \potT (\frac{p}{p_0})^{R/c_p}.
-\end{equation}
-To allow for an easier description of the initial conditions we split the $\potT$ into a background state $\backgroundPotT$ and a pertubation $\pertubationPotT$
-\begin{equation}
-  \label{eq:potT-split}
-  \potT = \backgroundPotT + \pertubationPotT.
-\end{equation}
-
-The initial conditions for pressure and density can be computed directly from the \textsc{pde} once few assumptions have been given.
-We assume that $\backgroundPotT$ is constant over the entire domain.
-Inserting the definition of potential temperature, given by \cref{eq:potTToT}, into the equation of state (see \cref{eq:eos}) leads us to
-\begin{equation}
-  \pressure(z) = \Qrho(z) R {\left( \backgroundPotT \frac{p}{p_0}\right)}^{R/c_p},
-\end{equation}
-which we solve for $p(z)$.
-After some algebra and simplifying, we arrive at
-\begin{equation}
- p(z) = p_0 \left( \frac{R \backgroundPotT \rho(z)}{p_0} \right)^{\gamma},
-\end{equation}
-or equivalently
-\begin{equation}
-  \label{eq:eos-potT}
-\Qrho(z) = \frac{p_{0}^{\frac{R}{c_{p}}} p^{\frac{1}{\gamma}}{\left (z \right )}}{R \backgroundPotT}.
-\end{equation}
-We want to consider flow in hydrostatic equilibrium, i.e.\ flow where the force originating from the pressure-gradient is exactly balanced by gravitation.
-Inserting this assumption in the momentum equation in $z$-direction and using \cref{eq:eos} once again, we arrive at the ordinary differential equation (\textsc{ode})
-\begin{align}
-  \label{eq:hydrostatic-balance-potT}
-  \begin{split}
-  \frac{d}{d z} p{\left (z \right )} &= -g \Qrho(z)
-                                     = 
-        - \frac{g p_{0}^{\frac{R}{c_{p}}} p^{\frac{1}{\gamma}}{\left (z \right )}}{R \backgroundPotT}\\
-  p{\left (0 \right )} &= p_0
-  \end{split}
-\end{align}
-where we use the reference pressure $p_0$ as the pressure on ground level.
-This \textsc{ode} can be now simply solved by separation of variables.
-After simplifying, we arrive at the initial condition for pressure
-\begin{align}
-  \label{eq:hydrostatic-background-pressure}
-p(z) &= \left(\left(1 - \frac{1}{\gamma}\right) \left(C - \frac{g p_{0}^{\frac{R}{c_{p}}} z}{R \backgroundPotT}\right)\right)^{\frac{c_{p}}{R}},\\
-\shortintertext{with constant of integration}
- C &= \frac{c_{p} p_{0}^{\frac{R}{c_{p}}}}{R}.
-\end{align}
-
-We now compute the pertubated potential temperature $\potT$ and use \cref{eq:potTToT} to convert it to temperature.
-We then evaluate the density $\Qrho(\bm{x})$ with \cref{eq:temperature}.
-The energy can be computed by inserting the previously computed pressure into the equation of state~(\ref{eq:eos}).
-
-This leaves us with one problem:
-The adiabatic no-slip boundary conditions defined by~\vref{eq:no-slip} are no longer valid.
-Concretely, we need to impose a viscous heat flux to ensure that the atmosphere stays in hydrostatic balance~\cite{giraldo2008study}
-\todo{Flux correct? Fix notation}
-\begin{equation}
-  \label{eq:atmosphere-bc}
-  F^\text{visc} = \kappa \pdv{\overline{T}}{z} =
-\frac{R \overline{\theta} \left(\frac{\overline{p}{\left (z \right )}}{p_{0}}\right)^{\frac{R}{c_{p}}} \frac{d}{d z} \overline{p}{\left (z \right )}}{c_{p} \overline{p}{\left (z \right )}}.
-\end{equation}
-The background pressure can be reconstructed by \cref{eq:hydrostatic-background-pressure}, its derivative is given by \cref{eq:hydrostatic-balance-potT}.
-
-\subsection{Robert's smooth bubble}
-\cite{robert1993bubble}
-\subsection{Density current}
-\cite{straka1993numerical}
 %%% Local Variables:

### 2018-12-08 writing/thesis/chapters/methods.tex
Some more work.

@@
 \newcommand{\sbasis}[1]{\Phi_{#1}}
+\newcommand{\stbasis}[1]{\Phi_{#1}}
 \newcommand{\testfunction}[1]{\Phi_{#1}}
@@
 
-\chapter{An ADER-DG scheme for the Navier-Stokes Equations}
+\chapter{An ADER-DG scheme for the Navier-Stokes Equations}\label{chap:methods}
 \section{Conservative Form}
@@
   \label{eq:cell-approx}
-  u(\bm{x}, t^n)_{|\cell[i]} = \hat{u}^n_{i,l} \sbasis{l}{\bm{x}},
+  u(\bm{x}, t^n)_{|\cell[i]} = \hat{u}^n_{i,l} \sbasis{l}(\bm{x}),
 \end{equation}
@@
 
+\newcommand{\dsol}{\bm{u}}
+\newcommand{\stpredictor}[1][h]{\bm{q}_{#1}}
 \sidetitle{Corrector}
@@
 \intdt{\intdcell{
-\testfunction{k} \pdv{\bm{Q}}{t}
+\testfunction{k} \pdv{\Q}{t}
 }}
@@
 \intdt{\intdcell{
-    \testfunction{k} \left( \div{F(Q, \gradient{Q})} \right)
+    \testfunction{k} \left( \div{F(\Q, \gradQ} \right)
 }}
@@
 \intdt{\intdcell{
-    \testfunction{k} S(Q, \bm{x}, t)
+    \testfunction{k} S(\Q, \bm{x}, t)
 }}
@@
 \todo{Double check the following description}
-\newcommand{\stpredictor}[1]{\bm{q}_{#1}}
-We now replace the solution $\bm{Q}$ with so called spacetime-predictor $\stpredictor{h}(\bm{x},t)$ into the weak form and write it as a polynomial using the representation of \cref{eq:cell-approx}.
+We now replace the solution $\bm{Q}$ with so called spacetime-predictor $\stpredictor (\bm{x},t)$ into the weak form and write it as a polynomial using the representation of \cref{eq:cell-approx}.
 Integrate first by parts in time (note basis here not defined over time), flux divergence by parts in space.
@@
 (\bm{u^{n+1} - u^{n}})
-+
+&+
 \left(\intdt{\intdcell{
-      \testfunction{k} \Riemann(\bm{q}^-, \bm{q}^+) \cdot \normal
+      \testfunction{k} \Riemann(\stpredictor^-, \stpredictor^+) \cdot \normal
 }}\right)
-&-\\
+-\\
 \left(\intdt{\intdcell{
-    \gradient{\testfunction{k}} \cdot  F(\bm{q})
+    \gradient{\testfunction{k}} \cdot  \flux(\stpredictor)
 }}\right)
@@
 \left(\intdt{\intdcell{
-      \testfunction{k} \source(\bm{q})
+      \testfunction{k} \source(\stpredictor)
 }}\right)
@@
 \sidetitle{Predictor}
-To derive the predictor, we again take an approximation of our solution in a nodal basis, but now consider polynomials that are defined both in space and time.
+To derive the predictor, we again take an approximation of our solution in a nodal basis, but now consider polynomials that are defined both in space and time
 \begin{equation}
-  \ldots
+  \label{eq:cell-approx-time}
+  q(\bm{x}, t^n)_{|\cell[i]} = \hat{u}^n_{i,l} \stbasis{l}(\bm{x}, t).
 \end{equation}
-We know multiply the conservation law again by a test function (of the same function space as the basis) and arrive at the weak formulation
-\begin{equation}
-  \label{eq:weak-pde-space-time}
- \ldots
+We now multiply the conservation law again by a test function (of the same function space as the basis) and arrive at the weak formulation
+\begin{equation}\label{eq:weak-pde-space-time}
+\intdt{\intdcell{
+    \testfunction{k}(\bm{x}, t)
+    \pdv{\stpredictor}{t}
+}}
++
+\intdt{\intdcell{
+    \testfunction{k}{\bm{x}, t}
+    \left(
+      \divergence{\flux(\stpredictor)}
+    \right)
+}}
+=
+\intdt{\intdcell{
+  \testfunction{k} \source(\stpredictor)
+}}.
 \end{equation}
@@
 Note that this neglects the interaction with neighbouring cells; this is corrected in the corrector step.
+\todo{Replace $\bm{x}$ with a macro some other letter. Is also coordinate!}
 
@@
   \label{eq:space-time-predictor}
-  \ldots
+0
+  + \ldots
 \end{equation}
@@
 
-\section{Compressible Navier Stokes}
+\section{Reactive Compressible Navier Stokes Equations}
 Fluid motion can be described by the compressible Navier Stokes equations.
 We follow the description in~\cite{dumbser2010arbitrary} for the Navier Stokes part.
-The coupling with the advection-diffusion-reaction equations follows~\cite{hidalgo2011ader}.
+The coupling with the advection-diffusion-reaction equation follows~\cite{hidalgo2011ader}.
 
@@
   \label{eq:conserved-variables}
- \Q = \left( \Qrho, \Qj, \QE \QZ \right).
+ \Q = \left( \Qrho, \Qj, \QE, \QZ \right).
 \end{equation}
@@
 
-The hyperbolic flux is given by
-\begin{equation}
-  \label{eq:hyper-flux}
-  \hyperFlux(\Q) = 
+\newcommand{\diffCoeff}{\varepsilon}
+\newcommand{\hyperFluxDef}{
   \begin{pmatrix}
@@
     \Qj \QZZ
-  \end{pmatrix},
-\end{equation}
-which are the Euler equations coupled with an advection equation.
-\newcommand{\diffCoeff}{\varepsilon}
-The viscous flux is
-\begin{equation}
-  \label{eq:visc-flux}
-  \viscFlux(\Q, \gradQ) = 
+  \end{pmatrix}
+}
+
+\newcommand{\viscFluxDef}{
   \begin{pmatrix}
@@
      -\diffCoeff \gradient{\QZ}
-  \end{pmatrix},
+   \end{pmatrix}
+}
+
+The hyperbolic flux is given by
+\begin{equation}
+  \label{eq:hyper-flux}
+  \hyperFlux(\Q) = \hyperFluxDef,
+\end{equation}
+which are the Euler equations coupled with an advection equation.
+The viscous flux is
+\begin{equation}
+  \label{eq:visc-flux}
+  \viscFlux(\Q, \gradQ) = \viscFluxDef.
 \end{equation}
 
-% \begin{equation}
-%   F(Q, \nabla Q) = 
-%   \begin{pmatrix}
-%     \Qj \\
-%     \Qv  \otimes \Qj + \bm{I} \pressure + \stressT (Q, \nabla Q)  \\
-%     \Qv \cdot (\bm{I} \QE + \bm{I} \pressure + \stressT (Q, \nabla Q)) - \kappa \nabla T
-%   \end{pmatrix},
-% \end{equation}
+Complete \textsc{pde}:
+\begin{equation}
+  \pdv{}{t}
+  \underbrace{
+  \begin{pmatrix}
+    \Qrho\\
+    \Qj\\
+    \QE\\
+    \QZ
+    \end{pmatrix}}_{\Q}
+  + 
+  \divergence{
+  \left(
+   \underbrace{\hyperFluxDef}_{\hyperFlux(\Q)}
++
+\underbrace{\viscFluxDef}_{\viscFlux(\Q, \gradQ)}
+  \right)}
+ =
+  \underbrace{
+  \begin{pmatrix}
+    S_{\Qrho\phantom{\Qrho}}\\
+    S_{\Qj}\\
+    S_{\QE}\\
+    S_{\QZ}
+    \end{pmatrix}}_{\source(\Q, \bm{x}, t)}
+\quad
+ \begin{array}{l}
+ \text{mass cons.} \\
+ \text{momentum cons.} \\
+ \text{energy cons.} \\
+ \text{cont.\ gas} 
+\end{array}
+\end{equation}
+
 where $\pressure$, $\stressT$ and $(\kappa \nabla T)$ denote the pressure, stress tensor and heat flux respectively.
@@
 \end{equation}
-%The term $\q_0 \QZ$ corresponds to the chemical energy.
+The term $q_0 \QZ$ corresponds to the chemical energy, where $q_0$ is the heat release.
 The temperature $T$ relates to pressure and density by the ideal gas law
@@
 \begin{align}
+  \label{eq:fluid-constants}
   \begin{split}
@@
 \todo{Cite sth!}
-
 We can finally define the heat conduction coefficient $\kappa$
@@
   \label{eq:stress-tensor}
-  \stressT(Q, \nabla Q) = \left(\nicefrac{2}{3} \mu \nabla \cdot \Qv \right) -
+  \stressT(Q, \nabla Q) = \left(\frac{2}{3} \mu \nabla \cdot \Qv \right) -
   \mu \left( \nabla (\Qv) + \nabla ( \Qv )^\intercal \right).
@@
 
-\section{Adaptive Mesh Refinement}
-\label{sec:amr}
+\section{Adaptive Mesh Refinement \textit{\&} Finite Volume Limiting}\label{sec:grid}
+Grid, spacefilling curve, and so on.
+
+\subsection{Adaptive Mesh Refinement}\label{sec:amr}
 We use adaptive mesh refinement (\textsc{amr}).
 
-Use total variation (\textsc{tv}) given by
+We use the total variation (\textsc{tv}) over an arbitrary indicator variable given by
 \begin{equation}
   \label{eq:tv}
-  \operatorname{TV}\left( f \right) =
-\intdcell{ \vert \gradient{f} \vert }
+  \operatorname{TV}\left[ f(\bm{x}] \right] =
+\Vert \left(\intdcell{ \vert \gradient{f \left( \bm{x} \right)} \vert } \right) \Vert_1
 \end{equation}
@@
 Justify by Chebychev's inequality?
+\todo{Cite this!}
+This criterion can be justified by Chebychev's inequality, which states that
+\begin{equation}
+  \label{eq:chebychev}
+  \mathbb{P}(\vert X - \mu \vert \geq c \sigma) \leq \frac{1}{c^2}
+\end{equation}
+for an arbitrary distribution with mean $\mu$ and standard deviation $\sigma$ probability $\mathbb{P}$.
+
+\subsection{Limiting}\label{sec:limiting}
+Higher order \textsc{dg} methods cannot cope with discontinuous solutions.
+Even worse, in the case of non-linear fluxes, discontinuities can appear even from smooth initial data.
+A classical way of dealing with this problem is the usage of so called limiters.
+The idea is to smooth out steep gradients and thus eliminate discontinuities.\todo{It doesnt work like this exactly..}
+
+A relatively recent way of dealing with this problem is the finite volume subcell limiter.
+Our discussion follows the one in~\cite{dumbser2016simple}.
+This limiting is an a posteriori limiting, which means that we first evaluate a timestep with an unlimited \textsc{ader-dg} method and then check, whether our solution is \enquote{correct}.
+In our case, we check whether the solution is a valid floating point number.
+We also check whether it is physically admissible.
+In our case we use the criterion
+\begin{equation}
+  \label{eq:limiting-physical}
+  \operatorname{is-admissible}(\Q) =
+  \begin{cases}
+    \text{true} & \Qrho > 0 \land \QE > 0 \\
+    \text{false} & \text{otherwise}.
+  \end{cases}
+\end{equation}
+\todo{Mention dmp if I end up using it.}
 

### 2018-12-08 writing/thesis/chapters/results.tex
Some more work.

@@
-\chapter{Results}
+\chapter{Results}\label{chap:results}
 \section{Convergence Test}
+Before computing the error we first need to define the $L_p$ norms for a $p > 0$ by
+% notation: https://en.wikipedia.org/wiki/Lp_space#Lp_spaces
+\begin{equation}
+  \label{eq:Lp-nrom}
+  \Vert f(x) \Vert = \left( \int_K \vert f(x) \vert^p d\mu  \right)^{1/p}.
+\end{equation}
+We start by a known analytical solution $f(x)$ and compare it to our approximation $\hat{f}(x)$.
+Let $Q$ and $\hat{Q}$ denote the analytical and approximate solution at node.
+We start by computing the point-wise error, and compute the cell-wise error from this.
+Observe that for our broken space $\Omega$
+\begin{equation}
+  \label{eq:lp-norm-broken}
+ \Vert f(x) \Vert = \sum_{K \in \Omega} \Vert f_K(x) \Vert_p.
+\end{equation}
+
+We are now ready to integrate the error for each cell.
+The output contains the position and conserved variables of each point.
+Each cell consists of $(N + 1)^d$ nodes, each associated with a quadrature weight $w_i$.
+The quadrature weights are associated with the reference cuboid.
+We thus need to map our element to the reference element, before we can compute the integral.
+
+Let $V$ denote the volume (or area) of each cell.
+For example, in three dimensions $V = \Delta x \, \Delta y \, \Delta z$.
+The final result is then
+\begin{equation}
+  \Vert f_K(x) \Vert = \left( V \sum_{\bm{i}} \vert f(\bm{x}_{\bm{i}}) \vert^p w_{{\bm{i}}}  \right)^{1/p},
+\end{equation}
+where we used the mapping to the reference triangle (integration by substitution).
+
 \section{Accurate CFD}

### 2018-12-08 writing/thesis/chapters/scenarios.tex
Some more work.

@@
 \chapter{Scenarios}\label{sec:scenarios}
+Unless otherwise noted, we use the constants
+\begin{align}
+\begin{split}
+  \gamma &= 1.4, \\
+  \Pr &= 0.7, \\
+  c_v &= 1.0
+\end{split}
+\end{align}
+The other constants follow from the definition of \cref{eq:fluid-constants}.
+
+We describe some scenarios in terms of the primitive variables $(\Qrho, \Qv, \pressure)$, these can be converted to the conservative variables by the definition of momentum and the definition of energy.
 \section{Numerical Convergence Test}
-We first define the $L_p$ norms for $p > 0$ by
-% notation: https://en.wikipedia.org/wiki/Lp_space#Lp_spaces
-\begin{equation}
-  \label{eq:Lp-nrom}
-  \Vert f(x) \Vert = \left( \int_K \vert f(x) \vert^p d\mu  \right)^{1/p}.
-\end{equation}
-We start by a known analytical solution $f(x)$ and compare it to our approximation $\hat{f}(x)$.
-Let $Q$ and $\hat{Q}$ denote the analytical and approximate solution at node.
-We start by computing the point-wise error, and compute the cell-wise error from this.
-Observe that for our broken space $\Omega$
-\begin{equation}
-  \label{eq:lp-norm-broken}
- \Vert f(x) \Vert = \sum_{K \in \Omega} \Vert f_K(x) \Vert_p.
-\end{equation}
-
-We are now ready to integrate the error for each cell.
-The output contains the position and conserved variables of each point.
-Each cell consists of $(N + 1)^d$ nodes, each associated with a quadrature weight $w_i$.
-The quadrature weights are associated with the reference cuboid.
-We thus need to map our element to the reference element, before we can compute the integral.
-
-Let $V$ denote the volume (or area) of each cell.
-For example, in three dimensions $V = \Delta x \, \Delta y \, \Delta z$.
-The final result is then
-\begin{equation}
-  \Vert f_K(x) \Vert = \left( V \sum_{\bm{i}} \vert f(\bm{x}_{\bm{i}}) \vert^p w_{{\bm{i}}}  \right)^{1/p},
-\end{equation}
-where we used the mapping to the reference triangle (integration by substitution).
-
 Following~\cite{dumbser2010arbitrary}, the scenario can be described in primitive variables by setting
 \begin{align}
-  \pressure &= \pressure_0 \cos( \bm{k} \bm{x} - \omega t ) + \pressure_b, \\
-  \Qrho &= \Qrho_0 \sin (\bm{k} \bm{x} - \omega t) + \Qrho_b, \\
-  \Qv &= \bm{v_0} \sin(\bm{k} \bm{x} - \omega t).
+\begin{split}
+  \pressure(\bm{x}, t) &= \pressure_0 \cos( \bm{k} \bm{x} - \omega t ) + \pressure_b, \\
+  \Qrho(\bm{x}, t) &= \Qrho_0 \sin (\bm{k} \bm{x} - \omega t) + \Qrho_b, \\
+  \Qv(\bm{x}, t) &= \bm{v_0} \sin(\bm{k} \bm{x} - \omega t).
+\end{split}
 \end{align}
@@
 \section{Classical Scenarios}
+In addition to the convergence test, we use standard \textsc{cfd} scenarios to evaluate our simulations.
 
@@
 \begin{align}
+  \label{eq:taylor-green}
   \begin{split}
+  \Qrho(\bm{x}, t) &= 1\\
   \Qv(\bm{x}, t) &= \exp(-2 \mu t)
@@
 $C = 100/\gamma$ \cite{dumbser2016high}
+
+As initial conditions we use \cref{eq:taylor-green} at time $(t = 0)$ and as boundary conditions we impose the solution and the corresponding gradients.
+Note that this solution is not exactly correct, as it assumes an incompressible flow.
+Due to the low mach number a compressible flow approaches this solution.
 

### 2018-12-09 writing/thesis/chapters/scenarios.tex
Add CJ-detonation wave scenario.

@@
 \subsection{The first Stokes Problem}
+\todo{Do I actually want to include this? Bit boring scenario}
 \cite{dumbser2010arbitrary}
@@
 Due to the low mach number a compressible flow approaches this solution.
+
+\subsection{Radialsymmetric CJ Detonation Wave}
+We investigate the radialsymmetric CJ detonation wave scenario from~\cite{helzel2000modified}.
+This scenario for the reactive Euler-equations is set up in a 2D box of size $[-0.5, 0.5] \times [-0.5, 0.5]$.
+Inside a circle of radius $0.3$ we have totally unburnt gas, outside of this circle we have burned gas.
+Let $\alpha =  \operatorname{atan2}(y,x)$ be the angle in polar coordinates.
+We use the initial conditions
+\begin{align}
+  \begin{split}
+  \Qrho_u &= 0.887565\\
+  \Qv_u &= -0.577350
+  \begin{pmatrix}
+     \cos (\alpha)\\
+     \sin (\alpha)
+  \end{pmatrix} \\
+  \pressure_u &= 0.191709 \\
+  \QZZ_u &= 1
+  \end{split}
+\intertext{for the burnt gas and}
+\begin{split}
+  \Qrho_b &= 1.4\\
+  \Qv_b &= 0\\
+  \pressure_b &= 1 \\
+  \QZZ_b &= 0
+  \end{split}
+\end{align}
+for the unburnt gas.
 

### 2018-12-10 writing/thesis/chapters/methods.tex
Fix limiter condition.
Fix some errors in description of dg problem.

@@
 \newcommand{\pressure}{p}
-\newcommand{\maxConvEigen}{\vert \lambda_c^{\text{max}} \vert}
-\newcommand{\maxViscEigen}{\vert \lambda_v^{\text{max}} \vert}
+\newcommand{\maxConvEigen}[1][]{
+  \vert%
+  \lambda_c^{\text{max}}
+  \notblank{#1}{\left(#1\right)}{}
+  \vert%
+}
+\newcommand{\maxViscEigen}[1][]{
+  \vert%
+  \lambda_v^{\text{max}}
+  \notblank{#1}{\left(#1\right)}{}
+  \vert%
+}
 \newcommand{\Riemann}{\operatorname{Riemann}}
@@
 
-\newcommand{\dsol}{\bm{u}}
+\newcommand{\dsol}[1][h]{\bm{u}_{#1}}
 \newcommand{\stpredictor}[1][h]{\bm{q}_{#1}}
@@
 \begin{equation}
-  \label{eq:cell-approx-time}
+  \label{eq:cell-approx-space-time}
   q(\bm{x}, t^n)_{|\cell[i]} = \hat{u}^n_{i,l} \stbasis{l}(\bm{x}, t).
@@
 \intdt{\intdcell{
-    \testfunction{k}{\bm{x}, t}
+    \testfunction{k}(\bm{x}, t)
     \left(
@@
 
-\begin{equation}
-  \label{eq:space-time-predictor}
-0
-  + \ldots
-\end{equation}
+\begin{align}\label{eq:space-time-predictor}
+\begin{split}
+\intdcell{
+  \testfunction{k} (\bm{x}, t^{n+1}) \stpredictor(\bm{x}. t^{n+1})
+}
+&-
+\intdt{\intdcell{
+    \pdv{}{d} \testfunction{k}(\bm{x}, t) \stpredictor(\bm{x}, t)
+}}
+-
+\intdcell{
+  \testfunction{k}(\bm{x},t^n) \dsol(\bm{x}, t^n)
+} = \\
+\intdt{\intdcell{
+    \testfunction{k}(\bm{x},t) \divergence{\flux(\stpredictor)}
+}}
+&+
+\intdt{\intdcell{
+    \testfunction{k}(\bm{x}, t) \source(\stpredictor)
+}}
+\end{split}
+\end{align}
 Inserting \cref{eq:cell-approx-space-time} results in a local systems of equations that can be solved in a fixed point iteration scheme.
-For details and proof of convergence for the linear case, see (todo).
-Write about initial guess (we use naive one anyway, right?)
+\todo{Inital guess correct? Maybe cite sth?}
+As initial value for the space-time-predictor we use the solution of the timestep before.
+\todo{Maybe collect into matrices and show scheme?}
+For details and proof of convergence for the linear case, see~\cite{dumbser2008unified}.
 
 \sidetitle{Boundary extrapolation and stuff}
+\todo{Explain that stpredictor and fluxes are saved and extrapolated to boundary.
+This is important because we extrapolate the gradient as well!}
 Extrapolate unknowns to boundary, convert from our basis to basis on faces.
@@
 
-\sidetitle{Diffusive Flux stuff}
-Numerical flux:
+\sidetitle{Riemann solver \textit{\&} timestep}
+As a Riemann solver we use a simple Rusanov-flux that is adapted for diffusive problems
 \begin{equation}
@@
   \right) -
-  \frac{1}{2} s_\text{max} (q_h^+ - q_h^-)
+  \frac{1}{2} s_\text{max} (q_h^+ - q_h^-),
 \end{equation}
-with
+with a penalty term
 \begin{equation}
@@
   s_\text{max}  = \max \left(
-\vert \lambda_c(q_h^-) \vert, \, \vert \lambda_c(q_h^+)
+\maxConvEigen[q_h^-], \, \maxConvEigen[q_h^+]
 \right) +
 2 \eta \max \left(
-\vert \lambda_v(q_h^-) \vert, \, \vert \lambda_v(q_h^+)
+\maxViscEigen[q_h^-], \, \maxViscEigen[q_h^+]
 \right)
@@
 \begin{equation}
-  \eta = \frac{2N+1}{h \sqrt{\frac{1}{2} \pi}}
+  \eta = \frac{2N+1}{h \sqrt{\frac{1}{2} \pi}}.
 \end{equation}
+In this equation, $N$ is the polynomial order and $h$ is the side-length of an element.
+The penalty term depends on the maximal absolute eigenvalues $\lambda_c$ and $\lambda_v$ \todo{
+Eigenvalues of jacobian (in normal direction), maximal eigenvalues.}.
+Max eigenvalue of convective part $\maxConvEigen$,i.e.\ of $\left( \partial \bm{F}/\partial \bm{Q}\right) \cdot \bm{n}$,
+and viscous part $\maxViscEigen$, i.e.\ of $\left( \partial \bm{F}/\partial \left( \nabla \bm{Q} \cdot \bm{n} \right)\right) \cdot \bm{n}$.
 
-Maximum timestep (\textsc{cfl})
+This Riemann solver was first published in~\cite{gassner2008discontinuous} and used for an \textsc{ader-dg} scheme in~\cite{dumbser2010arbitrary}.
+The timestep is restriced to a so-called \textsc{cfl}-type penalty
 \begin{equation}
@@
 with $N$ polynomial order and $h$ characteristic length scale of elements~\cite{dumbser2010arbitrary,gassner2008discontinuous}.
-The constant $\alpha(N) \leq \frac{1}{2N+1}$ is obtained from von Neumann analysis on a simple model problem and depends on the approximation order~\cite{dumbser2008unified}.
+The constant $\alpha(N) \leq {\left( 2N+1  \right)}^{-1}$ is obtained from von Neumann analysis on a simple model problem and depends on the approximation order~\cite{dumbser2008unified}.
+We use a value of $0.7$ for the constant $\text{CFL}$.
+\todo{Describe CFL-cond.\ for multiple dimensions!}
 
@@
 We follow the description in~\cite{dumbser2010arbitrary} for the Navier Stokes part.
-The coupling with the advection-diffusion-reaction equation follows~\cite{hidalgo2011ader}.
+The coupling with the advection-diffusion-reaction equation follows~\cite{hidalgo2011ader} which describes this equation set for the one-dimensional case.
 
@@
   \label{eq:conserved-variables}
- \Q = \left( \Qrho, \Qj, \QE, \QZ \right).
+ \Q = \left( \Qrho, \Qj, \QE, \QZ \right),
 \end{equation}
@@
   \label{eq:flux}
-  \flux(\Q, \gradQ) = \hyperFlux(\Q) + \viscFlux(\Q, \gradQ)
+  \flux(\Q, \gradQ) = \hyperFlux(\Q) + \viscFlux(\Q, \gradQ).
 \end{equation}
@@
 \begin{equation}
+ \begin{array}{l}
+ \text{mass cons.} \\
+ \text{momentum cons.} \\
+ \text{energy cons.} \\
+ \text{cont.\ gas} 
+\end{array}
+:
+\quad
   \pdv{}{t}
@@
     \end{pmatrix}}_{\source(\Q, \bm{x}, t)}
-\quad
- \begin{array}{l}
- \text{mass cons.} \\
- \text{momentum cons.} \\
- \text{energy cons.} \\
- \text{cont.\ gas} 
-\end{array}
 \end{equation}
@@
   \begin{cases}
-    \text{true} & \Qrho > 0 \land \QE > 0 \\
+    \text{true} & \Qrho > 0 \land \pressure > 0 \land \QZ > 0\\
     \text{false} & \text{otherwise}.
@@
 \end{equation}
+The positivity of the pressure implies positivity of energy.
 \todo{Mention dmp if I end up using it.}

### 2018-12-10 writing/thesis/chapters/methods.tex
Add more stuff.

@@
 \newcommand{\normal}{\bm{n}}
+\newcommand{\dsol}[1][h]{\bm{u}_{#1}}
+\newcommand{\stpredictor}[1][h]{\bm{q}_{#1}}
 
@@
 
-\newcommand{\dsol}[1][h]{\bm{u}_{#1}}
-\newcommand{\stpredictor}[1][h]{\bm{q}_{#1}}
+\begin{algorithm}[H]
+  \begin{algorithmic}
+    \Let{$\stpredictor$}{Initial guess}
+    \Let{$F_h$}{$\flux(\Q, \gradQ)$}
+    \Let{$\stpredictor$}{Solve \cref{eq:space-time-predictor} using $F_h, \Q, \gradQ$}
+    \Let{$\left( \hat{F_h}, \hat{\Q}, \hat{\gradQ}, \hat{\stpredictor} \right)$}
+        {Extrapolate to boundary using \cref{eq:boundary-extrapolation}}
+    \Let{update}{Use \cref{eq:corrector} with boundary extrapolated values (fluxes of neighbors)}
+  \end{algorithmic}
+  \caption{The \textsc{ader-dg} algorithm for one cell.}
+\end{algorithm}
+
 \sidetitle{Corrector}
@@
 This is important because we extrapolate the gradient as well!}
-Extrapolate unknowns to boundary, convert from our basis to basis on faces.
-Then Riemann solver
-and so on
-
-\sidetitle{Full Scheme}
-Maybe write algorithm?
-
-\todo{Actually write this section\ldots}
+Extrapolate unknowns to boundary, convert from our basis to basis on faces and so on
 
@@
 In this equation, $N$ is the polynomial order and $h$ is the side-length of an element.
-The penalty term depends on the maximal absolute eigenvalues $\lambda_c$ and $\lambda_v$ \todo{
-Eigenvalues of jacobian (in normal direction), maximal eigenvalues.}.
-Max eigenvalue of convective part $\maxConvEigen$,i.e.\ of $\left( \partial \bm{F}/\partial \bm{Q}\right) \cdot \bm{n}$,
-and viscous part $\maxViscEigen$, i.e.\ of $\left( \partial \bm{F}/\partial \left( \nabla \bm{Q} \cdot \bm{n} \right)\right) \cdot \bm{n}$.
+The penalty term depends on the maximal absolute eigenvalues of both the convective and viscous part of the equations
+\begin{align}
+  \begin{split}
+    \maxConvEigen &= \left( \partial \bm{F}/\partial \bm{Q}\right) \cdot \normal,\\
+    \maxViscEigen &= \left( \partial \bm{F}/\partial \left( \nabla \bm{Q} \cdot \normal \right)\right) \cdot \normal,
+  \end{split}
+\end{align}
+in direction of the normal vector $\normal$ to the cell face.
 
@@
 \end{equation}
+where $\pressure$, $\stressT$ and $(\kappa \nabla T)$ denote the pressure, stress tensor and heat flux respectively.
+Temperature is denoted by $T$.
 
-Complete \textsc{pde}:
+Putting everything together, our complete \textsc{pde} is a conservation law of the form of \cref{eq:conservation-law-gradient}
 \begin{equation}
@@
 
-where $\pressure$, $\stressT$ and $(\kappa \nabla T)$ denote the pressure, stress tensor and heat flux respectively.
-Temperature is denoted by $T$.
-
-We close the system with the equation of state of an ideal gas
+We close the system with the equation of state of an ideal reacting gas
 \begin{equation}
@@
   \label{eq:heat-conduction-coeff}
-  \kappa = \frac{\mu \gamma}{\Pr} \frac{1}{\gamma - 1} R
+  \kappa = \frac{\mu \gamma}{\Pr} \frac{1}{\gamma - 1} R = \frac{\mu \gamma}{\Pr} c_v
 \end{equation}
-where Prandtl number $\text{Pr}$ again depends on the fluid.
+where Prandtl number $\Pr$ again depends on the fluid.
 
@@
   \label{eq:stress-tensor}
-  \stressT(Q, \nabla Q) = \left(\frac{2}{3} \mu \nabla \cdot \Qv \right) -
-  \mu \left( \nabla (\Qv) + \nabla ( \Qv )^\intercal \right).
+  \stressT(Q, \nabla Q) =
+  \mu
+  \left(
+  \left(\nicefrac{2}{3} \divergence{\Qv} \right) -
+  \left( \gradient{\Qv} + \gradient{\Qv}^\intercal \right)
+  \right).
 \end{equation}
 
-Max eigenvalue of convective part $\maxConvEigen$,i.e.\ of $\left( \partial \bm{F}/\partial \bm{Q}\right) \cdot \bm{n}$,
-and viscous part $\maxViscEigen$, i.e.\ of $\left( \partial \bm{F}/\partial \left( \nabla \bm{Q} \cdot \bm{n} \right)\right) \cdot \bm{n}$
-is
+The maximal eigenvalues for convective and viscous part are
 \begin{align}
   \maxConvEigen \vert  &= \Vert \Qv \Vert + c\\
-  \maxViscEigen \vert &= \max \left( \frac{4}{3} \frac{\mu}{\Qrho}
-                                       , \frac{\gamma \mu}{\Pr \Qrho} \right)
+  \maxViscEigen \vert &= \max \left( \frac{4}{3} \frac{\mu}{\Qrho},
+                        \frac{\gamma \mu}{\Pr \Qrho},
+                        \diffCoeff \right)
 \end{align}
-with speed of sound $c = \sqrt{\gamma R T }$
+with speed of sound $c = \sqrt{\gamma R T }$.
 
@@
 
-We introduce parallel reduce.
+\newcommand{\gobs}{\operatorname{G}}
+\newcommand{\mean}{\mu}
+\newcommand{\std}{\sigma}
+\newcommand{\variance}{\std^2}
+\newcommand{\gobsCount}{n}
+We want to compute the mean and the variance over all grid cells by performing only pairwise merge operations.
+This allows us to minimize communication over nodes and allows for a simple implementation.
+The simplest way to compute this would be by using the textbook definitions of mean and variance of a random variable $X$
+\newcommand{\expectation}{\mathbb{E}}
+\begin{align}
+  \begin{split}
+    \mu [X] &= \expectation \left[ X \right]\\
+    \variance [X] &= \expectation \left[ X^2 \right] - \expectation \left[ X \right]^2.
+  \end{split}
+\end{align}
+The reduction for the variance is numerically unstable when the variance is orders of magnitudes smaller than the mean as this can lead to catastrophic cancellations.
+We thus compute the mean and variance with the parallel algorithm of~\cite{chan1982updating}.
+To do this, we need to store three variables per computation unit:
+the mean, the variance and the number of processed elements.
+We collect these items in the vector $\gobs = (\mean, \variance, \gobsCount)$
+We can then merge two pairs of observed variables by \cref{alg:merge-variance}.
 
-Reduce mean/std by~\cite{chan1982updating}
-
-Criterion with threshold.
-Justify by Chebychev's inequality?
-\todo{Cite this!}
+\begin{algorithm}[ht]
+  \begin{algorithmic}
+% TODO: Special cases 
+\Function{reduce-variance}{$\gobs_0, \gobs_1$}
+\If{$\gobsCount_0 = 0$}
+  \State\Return{$\mean_1, \variance_1, \gobsCount_1$}
+\EndIf\
+\If{$\gobsCount_1 = 0$}
+  \State\Return{$\mean_0, \variance_0, \gobsCount_0$}
+\EndIf\
+  \Let{$\Delta$}{$\mean_1 - \mean_0$}  
+  \Let{$\gobsCount_\Sigma$}{$\gobsCount_0 + \gobsCount_1$}
+  \Let{$m_a$}{$\variance_0 (\gobsCount_0 - 1)$}
+  \Let{$m_b$}{$\variance_1 (\gobsCount_1 - 1)$}
+  \Let{$m_\Sigma$}{$\nicefrac{m_a + m_b + (\Delta^2 \gobsCount_0 \gobsCount_1)}{\gobsCount_\Sigma}$}
+  \Let{$\mean_\Sigma$}{$\mean_0  \gobsCount_0 + \mean_1 \gobsCount_1$}
+  \State\Return{$
+    \nicefrac{\mean_\Sigma}{\gobsCount_\Sigma},
+    \nicefrac{m_\text{total}}{\gobsCount_\Sigma - 1},
+    \gobsCount_\Sigma
+    $}
+\EndFunction\
+  \end{algorithmic}
+  \caption{\label{alg:merge-variance}
+    Merging two sets of reduced mean and variance~\cite{chan1982updating}}
+\end{algorithm}
+We then use a threshold criterion
+\todo{Cite Chebychev, add concrete form of threshold.}
 This criterion can be justified by Chebychev's inequality, which states that

### 2018-12-10 writing/thesis/chapters/results.tex
Add more stuff.

--- 2018-12-03 writing/thesis/chapters/results.tex
@@
-\chapter{Results}
+\chapter{Results}\label{chap:results}
 \section{Convergence Test}
+\newcommand{\error}{\operatorname{Total-Error}}
+Before computing the error we first need to define the $L_p$ norms for a $p > 0$ by
+% notation: https://en.wikipedia.org/wiki/Lp_space#Lp_spaces
+\begin{equation}
+  \label{eq:Lp-nrom}
+  \Vert f(x) \Vert_p = \left( \int_K \vert f(x) \vert^p d\mu  \right)^{1/p}.
+\end{equation}
+We are interested in the total error which we define as the norm of the difference between an analytical solution $f(\bm{x}, t)$ and our approximation $\hat{f}(\bm{x}, t)$.
+The error at a time $t$ is thus defined as
+\begin{equation}
+  \label{eq:error}
+  \error(t,p) = \Vert f(\bm{x}, t) - \hat{f}(\bm{x}, t) \Vert_p.
+\end{equation}
+
+We first observe that for our approximation space $\broken$ we can split up the error as a sum over all cells
+\begin{equation}
+  \label{eq:lp-norm-broken}
+ %\Vert f(\bm{x}) \Vert = \sum_{\cell[] \in \broken} \Vert f_{\cell[]} (\bm{x}) \Vert_p,
+  \error(t,p) = \sum_{\cell[] \in \broken} \error_{\cell[]}(t,p)
+\end{equation}
+where $\error_{\cell[]}$ is the error in the cell $\cell[]$.
+
+\todo{Describe how to integrate the error for cells, and effect of volume}
+% We are now ready to integrate the error for each cell.
+% The output contains the position and conserved variables of each point.
+% Each cell consists of $(N + 1)^d$ nodes, each associated with a quadrature weight $w_i$.
+% The quadrature weights are associated with the reference cuboid.
+% We thus need to map our element to the reference element, before we can compute the integral.
+
+% Let $V$ denote the volume (or area) of each cell.
+% For example, in two dimensions $V = \Delta x \, \Delta y$.
+% The final result is then
+% \begin{equation}
+%   \Vert f_K(x) \Vert = \left( V \sum_{\bm{i}} \vert f(\bm{x}_{\bm{i}}) \vert^p w_{{\bm{i}}}  \right)^{1/p},
+% \end{equation}
+% where we used the mapping to the reference triangle (integration by substitution).
+
+For the limiting case of $p \to \infty$ we use the maximum point-wise error.
+
 \section{Accurate CFD}

### 2018-12-10 writing/thesis/chapters/scenarios.tex
Add more stuff.

@@
 
-\subsection{The first Stokes Problem}
-\todo{Do I actually want to include this? Bit boring scenario}
-\cite{dumbser2010arbitrary}
+% \subsection{The first Stokes Problem}
+% \todo{Do I actually want to include this? Bit boring scenario}
+% \cite{dumbser2010arbitrary}
+
 \subsection{Taylor-Green Vortex}
@@
 Due to the low mach number a compressible flow approaches this solution.
+
+\subsection{Lid-Driven Cavity Flow}
+The lid-driven cavity flow is a very simple testing scenario for the Navier-Stokes equations.
+We use a constant pressure of (what exactly) and a constant density $(\Qrho = 1.0)$ for the entire domain.
+The flow is then driven entirely by the boundary conditions.
+They consist in four no-slip walls where the upper wall has a constant velocity $\Qv = (1.0, 0)$.
+This scenario is surprisingly difficult for an \textsc{ader-dg} scheme as the boundary conditions lead to a discontinuity at the top left corner.
+There, the velocity of the wall is piece-wise constant.
+Therefore, this scenario is a good choice to test the stability of the finite volume limiter.
+
+\subsection{ABC-Flow}
+We use theArnold–Beltrami–Childress (\textsc{abc}) flow as a simple example of a three-dimensional scenario~\cite{tavelli2016staggered}.
+This scenario has, unlike the three-dimensional version of the Taylor-Green vortex, at least for the incompressible case an analytical solution
+\begin{align}
+  \label{eq:abc-flow}
+  \begin{split}
+  \Qrho(\bm{x}, t) &= 1\\
+  \Qv(\bm{x}, t) &= \phantom{-} \exp(-1\mu t)
+  \begin{pmatrix}
+    \sin(z) + \cos(y)\\
+    \sin(x) + \cos(z)\\
+    \sin(y) + \cos(x)
+  \end{pmatrix} \\
+  \pressure(\bm{x}, t) &= -\exp(-2 \mu t) \, \left(\cos(x)\sin(y) + \sin(x)\cos(z) + \sin(z)\cos(y)\right)
+  + C
+  \end{split}
+\end{align}
+Thus, we can simulate this without periodic boundary conditions.
+\todo{Analytical solution!}
 

### 2018-12-11 writing/thesis/chapters/results.tex
Add preliminary table of convergence orders.

@@
 \section{Convergence Test}
+\begin{table}[htb]
+  \centering
+\caption{Numerical order of convergence of ADER-DG method}%
+\label{tab:convergence-order}
+\begin{tabular}{@{}lS[table-format=1.2]S[table-format=1.2]S[table-format=1.2]@{}}
+\toprule
+{Order} & {L1} & {L2} & {LInf}\\ \midrule
+1 & 2.03 & 2.00 & 1.92\\
+2 & 2.56 & 2.55 & 2.56\\
+3 & 3.44 & 3.41 & 3.42\\
+4 & 4.27 & 4.27 & 4.33\\
+5 & 5.36 & 5.32 & 5.26\\
+6 & 5.38 & 5.35 & 5.17\\
+\bottomrule
+\end{tabular}
+\end{table}
 \newcommand{\error}{\operatorname{Total-Error}}
+
 Before computing the error we first need to define the $L_p$ norms for a $p > 0$ by
@@
 \todo{Describe how to integrate the error for cells, and effect of volume}
-% We are now ready to integrate the error for each cell.
-% The output contains the position and conserved variables of each point.
-% Each cell consists of $(N + 1)^d$ nodes, each associated with a quadrature weight $w_i$.
-% The quadrature weights are associated with the reference cuboid.
-% We thus need to map our element to the reference element, before we can compute the integral.
-
-% Let $V$ denote the volume (or area) of each cell.
-% For example, in two dimensions $V = \Delta x \, \Delta y$.
-% The final result is then
-% \begin{equation}
-%   \Vert f_K(x) \Vert = \left( V \sum_{\bm{i}} \vert f(\bm{x}_{\bm{i}}) \vert^p w_{{\bm{i}}}  \right)^{1/p},
-% \end{equation}
-% where we used the mapping to the reference triangle (integration by substitution).
+We evaluate the cell-wise error with Gaussian quadrature.
+ \begin{equation}
+   \Vert f_K(x) \Vert_p = \left( V \sum_{\bm{i}} \vert f(\bm{x}_i, t) - \hat{f}(\bm{x}_i, t) \vert^p w_{{\bm{i}}}  \right)^{1/p},
+ \end{equation}
+where $V = \Delta x \Delta y$ is the volume of each two-dimensional cell.
+The sum runs over all quadrature nodes $x_i$ with weights $w_i$.
+We use ten nodes.
 

### 2018-12-11 writing/thesis/chapters/methods.tex
Begin describing MUSCL.

@@
 
+% Names of methods or so
+\newcommand{\muscl}{\textsc{muscl}-Hancock}
+\newcommand{\dg}{\textsc{dg}}
+\newcommand{\ader}{\textsc{ader}}
+\newcommand{\aderdg}{\textsc{ader-dg}}
+\newcommand{\amr}{\textsc{amr}}
+
 \chapter{An ADER-DG scheme for the Navier-Stokes Equations}\label{chap:methods}
+This chapter describes the numerical and physical background that is needed to simulate reacting fluids with good accuracy.
+We start with a description of the arbitrary high order derivatives (\ader) discontinuous Galerkin (\dg) method with a focus on equations that contain both advective and diffusive terms.
+We then seque into a short description of the \muscl\ scheme, a second order finite volume scheme.
+This discussion of the discretization enables us to talk about the equation set in sufficient detail.
+
+We conclude this chapter by a description of adaptive mesh refinement (\amr) and finite volume limiting, which combines both numerical methods to achieve a stable, high-order method.
+
 \section{Conservative Form}
@@
 
-\section{The ADER-DG Method}
-\label{sec:ader-dg}
+\section{The ADER-DG Method}\label{sec:ader-dg}
 We describe the arbitrary derivative discontinous Galerkin (ADER-DG) method in this chapter.
@@
 
-\section{Reactive Compressible Navier Stokes Equations}
+\section{MUSCL-Hancock Finite Volume Scheme}\label{sec:muscl}
+\newcommand{\cellAvg}[1][i,j]{U_{#1}}
+\newcommand{\sign}{\operatorname{sign}}
+\newcommand{\minmod}{\operatorname{minmod}}
+\newcommand{\slope}[2][i,j]{s^{#2}_{#1}}
+\newcommand{\gradCellAvg}[1][i,j]{\gradient{\cellAvg[#1]}}
+\newcommand{\fluxX}{\flux_x}
+\newcommand{\fluxY}{\flux_y}
+We discussed a modern, high-order \textsc{DG} method in the previous chapter.
+While this scheme is efficient, it can become unstable, especially in case of discontinuities.
+A simple alternative is a finite volume scheme.
+We use the \muscl\ method, our discussion and notation follows the one in~\cite{toro2013riemann}.
+Similar to~\cite{toro2013riemann} we only describe the two-dimensional case, an extension to three dimensions is straigthforward.
+\todo{Source term!}
+
+In contrast to the previous \dg\ scheme, we now only store cell averages instead of a full polynomial solution per cell.
+We achieve higher order then by a reconstruction of a linear function.
+Let $\cellAvg$ denote the averages per cell at spatial coordinates $i,j$.
+
+\sidetitle{Boundary Extrapolated Values}
+We first compute the slope of the linear function connecting the cells.
+This is done by assuming a linear function per cell.
+\todo{Explain concrete limiter!}
+\todo{Cite minmod limiter. Is this correct? It's the one used}
+We use the minmod slope-limiter
+\begin{equation}
+  \label{eq:minmod}
+  \operatorname{minmod}(a, b) =
+  \begin{cases}
+    0.0 & \sign(a) \neq \sign(b) \\
+      a & \vert a \vert < \vert b \vert \\
+      b & \text{otherwise}
+  \end{cases}
+\end{equation}
+to avoid unphyiscally steep gradients and stabilize the system.
+This function then be used to compute the slopes
+\begin{align}\label{eq:slopes}
+  \begin{split}
+   \slope{x} &=  \Delta x \minmod \left( \cellAvg[i+1,j] - \cellAvg[i,j], \, \cellAvg[i,j] - \cellAvg[i-1, j] \right),\\ 
+   \slope{y} &=  \Delta y \minmod \left( \cellAvg[i,j+1] - \cellAvg[i,j], \, \cellAvg[i,j] - \cellAvg[i, j-1] \right),
+   \end{split}
+\end{align}
+where $\Delta x$ and $\Delta y$ are the inverse cell sizes in $x$ and $y$ direction respectively.
+
+We then use the slope to reconstruct the value of the boundary.
+In the following $\cellAvg^{\pm x}$ is the average of the left ($+$) or right ($-$) cell boundary.
+Similar, $\cellAvg^{\pm y}$ is the value at the top/bottom cell boundary.
+These so called boundary extrapolated values are given by
+\newcommand{\extrapolatedCellAvg}[3][i,j]{\cellAvg[#1]^{#3 #2} = \cellAvg #3 \frac{1}{2} \slope{#2}}
+\begin{equation}
+\begin{alignedat}{2}
+& \extrapolatedCellAvg{x}{-} , \qquad && \extrapolatedCellAvg{x}{+}, \\
+& \extrapolatedCellAvg{y}{-} , \qquad && \extrapolatedCellAvg{y}{+}.
+\end{alignedat}
+\end{equation}
+We also use the slopes defined in \cref{eq:slopes} to estimate the gradient of $\Q$ in each cell by the block matrix\todo{Notation!}
+\begin{equation}
+  \label{eq:muscl-gradient}
+  \gradCellAvg = \left( \slope{x} \bigg\rvert \slope{y} \right),
+\end{equation}
+which is of course an abuse of notation insofar as it is not the gradient of the constant cell value but rather of the linear reconstruction.
+\sidetitle{Time Evolution}
+To achieve second order in time, we evolve the boundary extrapolated values in time by
+\todo{Correct index for gradient of cell average}
+\todo{Actually compare with implementation. Currently gradient is ignored here!}
+\todo{Describe splliting of $\flux$ into $\fluxX, \fluxY$}
+\newcommand{\evolvedCellAvg}[2][i,j]{\hat{U}_{#1}^{#2}}
+\begin{equation}\label{eq:muscl-time-evolution}
+  \begin{split}
+  \forall_{k \in [-x, +x, -y, +y]}:  \hat{U}_{ij}^k = \cellAvg^k &+
+  \frac{\Delta t}{2 \Delta x} \left[ \fluxX(\cellAvg^{-x}, \gradCellAvg) - \fluxX(\cellAvg^{+x}, \gradCellAvg) \right] \\&+
+  \frac{\Delta t}{2 \Delta y} \left[ \fluxY(\cellAvg^{-y}, \gradCellAvg) - \fluxY(\cellAvg^{+y}, \gradCellAvg) \right].
+  \end{split}
+\end{equation}
+
+Finally, the update can be described by\todo{Double check update}
+\begin{align}
+  \begin{split}
+    \cellAvg (t^{n+1}) &= \cellAvg (t^n)
+    \\ &+
+  \frac{\Delta t}{\Delta x}
+    \Riemann \left(
+      \evolvedCellAvg[i-1,j]{+x}, \gradCellAvg[i-1,j]; \ %
+      \evolvedCellAvg[i,j\phantom{-1}]{-x}, \gradCellAvg[i,j\phantom{-1}]
+    \right)
+    \\ &-
+  \frac{\Delta t}{\Delta x}
+    \Riemann \left(
+      \evolvedCellAvg[i,j\phantom{+1}]{+x}, \gradCellAvg[i,j\phantom{+1}]; \ %
+      \evolvedCellAvg[i+1,j]{-x}, \gradCellAvg[i+1,j]
+    \right)
+    \\ &+
+  \frac{\Delta t}{\Delta y}
+    \Riemann \left(
+      \evolvedCellAvg[i,j-1]{+y}, \gradCellAvg[i,j-1]; \ %
+      \evolvedCellAvg[i,j\phantom{-1}]{-y}, \gradCellAvg[i,j\phantom{-1}]
+    \right)
+    \\ &-
+  \frac{\Delta t}{\Delta y}
+    \Riemann \left(
+      \evolvedCellAvg[i,j\phantom{+1}]{+y}, \gradCellAvg[i,j\phantom{+1}]; \ %
+      \evolvedCellAvg[i,j+1]{-y}, \gradCellAvg[i,j+1]
+    \right)    
+  \end{split}
+\end{align}
+
+\section{Reactive Compressible Navier Stokes Equations}\label{sec:navier-stokes}
 Fluid motion can be described by the compressible Navier Stokes equations.
@@
 
-\section{Boundary conditions}
+\subsection{Boundary conditions}
 To close the system we need to impose boundary conditions.

### 2018-12-14 writing/thesis/chapters/results.tex
Add small paragraph about convergence results.

@@
 \toprule
-{Order} & {L1} & {L2} & {LInf}\\ \midrule
+{Order} & {$L_1$} & {$L_2$} & {$L_\infty$}\\ \midrule
 1 & 2.03 & 2.00 & 1.92\\
@@
 
+We compute the error for the manufactured-solution scenario (\cref{sec:manufactured-solution}).
+Looking at the plot for the $L_2$ error (refer to plot here) shows that our method converges for all tested polynomial orders.
+\todo{Preliminary results used here!}
+
+To compute the numerical order of convergence, we perform a linear regression of the logarithm of the error vs.\ the logarithm of the meshsize.
+The size of the slope is then the convergence order.
+We can see (\cref{tab:convergence-order}) that our numerical convergence rate increases with the polynomial order.
+We do not achieve the optimal theoretical order of convergence of $N+1$.
+In~\cite{dumbser2010arbitrary}, which use a similar numerical method and the same scenario, but a different grid, \citeauthor{dumbser2010arbitrary} achieves the optimal order for most polynomial orders.
+Some \textsc{dg}-methods of odd order only achieve a numerical convergence order of $N+\nicefrac{1}{2}$.
+
 \section{Accurate CFD}

### 2018-12-14 writing/thesis/chapters/scenarios.tex
Add constants for some scenarios.

@@
 We describe some scenarios in terms of the primitive variables $(\Qrho, \Qv, \pressure)$, these can be converted to the conservative variables by the definition of momentum and the definition of energy.
-\section{Numerical Convergence Test}
+\section{A Manufactured Solution}\label{sec:manufactured-solution}
 Following~\cite{dumbser2010arbitrary}, the scenario can be described in primitive variables by setting
@@
 \subsection{ABC-Flow}
-We use theArnold–Beltrami–Childress (\textsc{abc}) flow as a simple example of a three-dimensional scenario~\cite{tavelli2016staggered}.
+We use the Arnold–Beltrami–Childress (\textsc{abc}) flow as a simple example of a three-dimensional scenario~\cite{tavelli2016staggered}.
 This scenario has, unlike the three-dimensional version of the Taylor-Green vortex, at least for the incompressible case an analytical solution
@@
 for the unburnt gas.
+
+Similar to~\cite{helzel2000modified}, we use the constants
+\begin{align}
+  \begin{split}
+  \gamma &= 1.4, \\
+  \Pr &= 0.7, \\
+  c_v &= 2.5, \\
+  c_p &= 3.5, \\
+  R &= 1.0.
+  \end{split}
+\end{align}
 
@@
 
+We use the following set of fluid dependent constants for these scenarios
+\begin{align}
+  \begin{split}
+    \gamma &= 1, \\
+    \Pr &=  0.71, \\
+    R &= 287.058, \\
+    p_0 &= 10000,
+  \end{split}
+\end{align}
+the other constants are evaluated following \cref{eq:fluid-constants}.
+
 \subsection{Robert's smooth bubble}

### 2018-12-14 writing/thesis/chapters/methods.tex
Improve methods chapter slightly.

@@
 \newcommand{\amr}{\textsc{amr}}
+\newcommand{\pde}{\textsc{pde}}
 
@@
 
-\section{Conservative Form}
-Standard (hyperbolic) form of conservation law
+\section{The ADER-DG Method}\label{sec:ader-dg}
+We describe the arbitrary derivative discontinous Galerkin (\aderdg) method in this chapter.
+Our description of the main method follows~\cite{dumbser2008unified,dumbser2010arbitrary,dumbser2018efficient}, our notation follows primarily~\cite{dumbser2018efficient}.
+We discuss the approximation of systems of partial differential equations (\pde) of the form
+\begin{equation}
+  \label{eq:conservation-law-gradient}
+ \frac{\partial}{\partial_t}  \Q + \div \flux(\Q, \gradQ) = \source(\bm{x}, t, \Q),
+\end{equation}
+which in contrast to hyperbolic conservation laws of the form
 \begin{equation}
@@
 \end{equation}
-extend to:
-\begin{equation}
-  \label{eq:conservation-law-gradient}
- \frac{\partial}{\partial_t}  \Q + \div \flux(\Q, \gradQ) = \source(\bm{x}, t, \Q)
-\end{equation}
+contain the gradient $\gradQ$ of the so called vector of conservative variables $\Q$~\cite{dumbser2010arbitrary}.
+There are therefore not hyperbolic but rather parabolic or elliptic.
 
-\section{The ADER-DG Method}\label{sec:ader-dg}
-We describe the arbitrary derivative discontinous Galerkin (ADER-DG) method in this chapter.
-See: \cite{dumbser2018efficient}
-
-We discuss the solution of a hyperbolic conservation law \cref{eq:conservation-law} with domain $\domain$ and boundary $boundary$.
-In the discontinous Galerkin (DG) framework, we approximate this solution in the space
+We discuss the solution of a hyperbolic conservation law \cref{eq:conservation-law} with domain $\domain$ and boundary $\boundary$.
+Let $\domain$ and $\boundary$ denote our two- or three-dimensional computational domain and its boundary.
+In our implementation of the discontinous Galerkin (\dg) framework, we approximate this solution in the space
 \begin{equation}
@@
 of disjoint quadrilateral cells $\cell$.
-Note that we do not distinguish between the approximation space and the domain, the use should be clear given its surrounding context.
+Note that we do not distinguish between the broken approximation space and the domain, the use should be clear given its surrounding context.
 In the following we make use of the Einstein summation convention where summation over repeated indexes is implied.
@@
 We first compute a local solution of the cell in the predictor step and then connect with the neighbors in the corrector step.
-In the following we first describe the corrector step as it follows directly from the \textsc{pde}.
+In the following we first describe the corrector step as it follows directly from the \pde.
 The predictor is derived shortly after.
@@
 First, we multiply the system \cref{eq:conservation-law} by a test function $\testfunction{i}$ and integrate over the space-time volume $(\cell \times [t^n, t^{n+1}])$.
-We arrive at the so called weak formulation of the \textsc{pde} 
+We arrive at the so called weak formulation of the \pde\
 \begin{equation}
@@
 \left(\intdt{\intdcell{
-    \gradient{\testfunction{k}} \cdot  \flux(\stpredictor)
+    \gradient{\testfunction{k}} \cdot  \flux(\stpredictor, \gradient{\stpredictor}) % todo correct gradient?
 }}\right)
@@
     \left(
-      \divergence{\flux(\stpredictor)}
+      \divergence{\flux(\stpredictor, \gradient{\stpredictor})}
     \right)
@@
 This time we do not use the Riemann solver for the flux boundary term but rather use the discrete solution at time $t$.
-Note that this neglects the interaction with neighbouring cells; this is corrected in the corrector step.
+Note that this neglects the interaction with neighbouring cells; we account for this in the corrector step.
 \todo{Replace $\bm{x}$ with a macro some other letter. Is also coordinate!}
@@
 \intdcell{
-  \testfunction{k} (\bm{x}, t^{n+1}) \stpredictor(\bm{x}. t^{n+1})
+  \testfunction{k} (\bm{x}, t^{n+1}) \stpredictor(\bm{x}, t^{n+1})
 }
@@
 \intdt{\intdcell{
-    \pdv{}{d} \testfunction{k}(\bm{x}, t) \stpredictor(\bm{x}, t)
+    \pdv{}{t} \testfunction{k}(\bm{x}, t) \stpredictor(\bm{x}, t)
 }}
@@
 \intdt{\intdcell{
-    \testfunction{k}(\bm{x},t) \divergence{\flux(\stpredictor)}
+    \testfunction{k}(\bm{x},t) \divergence{\flux(\stpredictor, \gradient{\stpredictor})}
 }}
@@
 The timestep is restriced to a so-called \textsc{cfl}-type penalty
-\begin{equation}
+\begin{equation}\label{eq:cfl-aderdg}
  \Delta t \leq  \text{CFL} \, \frac{\alpha(N) \, h}{\maxConvEigen + 2 \maxViscEigen \frac{2N+1}{h}}
@@
 
+We again use the Rusanov-type Riemann solver~\cref{eq:rusanov-flux}.
+The timestep is subject to a penalty of the form
+\begin{equation}\label{eq:cfl-muscl}
+ \Delta t \leq  \text{CFL} \, \frac{h}{\maxConvEigen + 2 \maxViscEigen \frac{1}{h}},
+\end{equation}
+with a constant value of CFL that is typically close to $0.7$.
+
 \section{Reactive Compressible Navier Stokes Equations}\label{sec:navier-stokes}
@@
 
-Putting everything together, our complete \textsc{pde} is a conservation law of the form of \cref{eq:conservation-law-gradient}
+Putting everything together, our complete \pde\ is a conservation law of the form of \cref{eq:conservation-law-gradient}
 \begin{equation}
@@
   \begin{cases}
-    \text{true} & \Qrho > 0 \land \pressure > 0 \land \QZ > 0\\
+    \text{true} & \Qrho > 0 \land \pressure > 0 \land \left(0 \leq \QZ \leq 1 \right)\\
     \text{false} & \text{otherwise}.
@@
 
+If a solution violates our criteria, we subdivide the infringing cell into $N_2 = 2N + 1$ subcells.
+This results in the remarkable properties, that we first do not loose any spatial resolution and secondly that we can use the same timestep size for both methods.
+This can be seen easily by noticing the similar form of \cref{eq:cfl-aderdg} and \cref{eq:cfl-muscl}.
+
 %%% Local Variables:

### 2018-12-16 writing/thesis/chapters/scenarios.tex
Add constants and details to atmospheric scenarios.

@@
 This \textsc{ode} can be now simply solved by separation of variables.
-After simplifying, we arrive at the initial condition for pressure
+We then obtain after simplifying the solution
 \begin{align}
@@
 
-We now compute the pertubated potential temperature $\potT$ and use \cref{eq:potTToT} to convert it to temperature.
-We then evaluate the density $\Qrho(\bm{x})$ with \cref{eq:temperature}.
-The energy can be computed by inserting the previously computed pressure into the equation of state~(\ref{eq:eos}).
+We can now compute the initial conditions for a scenario where the background potential energy is in hydrostatic equilbrium with a pertubation that is not in equilbrium.
+We first compute the background pressure with background potential temperature $\backgroundPotT = \text{const.}$ using \cref{eq:hydrostatic-background-pressure}.
+Next, we compute the pertubated potential temperature $\potT$ and use \cref{eq:potTToT} to convert it to temperature.
+The density $\Qrho(\bm{x})$ can now be evaluated with \cref{eq:temperature}.
+Finally, we compute the energy by inserting pressure and density into the equation of state~(\ref{eq:eos}).
 
@@
 
-\subsection{Robert's smooth bubble}
-\cite{robert1993bubble}
+\subsection{Two Bubbles}
+As a simple test case we consider a scenario where we have one large warm air bubble in the middle, and a small cold bubble on the top.
+This scenario was first published by \citeauthor{robert1993bubble}~\cite{robert1993bubble}.
+We use a domain of $\SI{1}{\km} \times \SI{1}{\km}$.
+The initial conditions of the scenario are given by a pertubation of a hydrostatic equlibrium.
+We use a background potential temperature of $\backgroundPotT = 300$.
+
+Let
+\begin{equation}
+  \label{eq:radius}
+  r^2 = (x - x_0)^2 + (z - z_0)^2
+\end{equation}
+denote the difference between spatial positions $x,z$ and the center of a bubble $x_c, z_c$.
+The pertubation is given by the function
+\begin{equation}
+  \label{eq:bubbles-pertubation}
+  \pertubationPotT =
+  \begin{cases}
+    A & r \leq a \\
+    A \exp \left( - (r-a)^2/s^2 \right) & r > a,
+    \end{cases}
+\end{equation}
+where $A$ denotes the maximal pertubation, $a$ is the size of the bubble and $s$ is the decay rate.
+We have two bubbles, with the values
+\begin{equation}
+  \label{eq:bubbles-values}
+\begin{alignedat}{6}
+  & \text{warm:} \qquad && A = 0.5 \quad&& a = \SI{150}{\m} \quad&& s = \SI{50}{\m} \quad&& x_c = \SI{500}{\m} \quad&& z_c = \SI{300}{\m},\\
+  & \text{cold:} \qquad && A = -0.15 \quad&& a = \SI{0}{\m} \quad&& s = \SI{50}{\m} \quad&& x_c = \SI{560}{\m} \quad&& z_c = \SI{640}{\m}.
+  \end{alignedat}
+\end{equation}
+
+Similar to~\cite{muller2010adaptive}, we use a constant viscosity of $\mu = 0.1$ to regularize the solution.
+
 \subsection{Density current}
-\cite{straka1993numerical}
+A similar scenario is the density current~\cite{straka1993numerical} by \citeauthor{straka1993numerical}.
+In this scenario we only have one cold bubble.
+We use the same procedure as before to compute the initial conditions, again with $\backgroundPotT = 300$ but with a pertubation of the form
+\begin{align}
+  \label{eq:cos-pertubation}
+  \pertubationPotT &= \begin{cases}
+    \nicefrac{A}{2} \left[ 1 + \cos(\pi r) \right] & r \leq a \\
+    0 & r > a
+    \end{cases}
+\intertext{with}        
+        r^2 &=  \left( \frac{x - x_c}{x_r} \right)^2 + \left( \frac{z -z_c}{z_r} \right)^2
+\end{align}
+and constants
+\begin{equation}\label{eq:density-bubble}
+  A = -15 \quad a = \SI{1}{\m} \quad x_r = \SI{4000}{\m} \quad z_r = \SI{2000}{\m} \quad x_c = \SI{0}{\m} \quad z_c = \SI{3000}{\m}.
+\end{equation}
+Similar to~\cite{giraldo2008study} we use a constant viscosity of $\mu = 75$.
+
 %%% Local Variables:

### 2018-12-17 writing/thesis/chapters/methods.tex
Add reference mapping to DG, begin workin on matrix notation.
It's a mess.

@@
 \newcommand{\intdcell}[1]{\int_{\cell} #1 \dd{\bm{x}}}
+\newcommand{\intdrefcell}[1]{\int_{\cell} #1 \dd{\hat{\bm{x}}}}
 \newcommand{\intdcellb}[1]{\int_{\partial{} \cell} #1 \dd{S}} % TODO: define boundary of cell
+\newcommand{\intdrefcellb}[1]{\int_{\partial{} \cell} #1 \hat{\dd{S}}} % TODO: define boundary of cell
 
@@
 
-\sidetitle{Corrector}
-First, we multiply the system \cref{eq:conservation-law} by a test function $\testfunction{i}$ and integrate over the space-time volume $(\cell \times [t^n, t^{n+1}])$.
-We arrive at the so called weak formulation of the \pde\
+\sidetitle{Reference Cell}
+\newcommand{\mapping}{\mathcal{M}}
+\newcommand{\volume}{V}
+For reasons of computational efficiency, we describe the scheme in terms of a reference cell.
+We use the quad cell $\cell = [0, 1]^D$\todo{check if $[0,1]$ detontes correct interval}.
+The mapping, which takes a point on the reference cell with coordinates $\hat{\bm{x}}$ and returns a point $\bm{x}$ on a cell with center and widths $(\Delta x, \Delta y, \Delta z)$, is given by
 \begin{equation}
-  \label{eq:weak-pde}
-\intdt{\intdcell{
-\testfunction{k} \pdv{\Q}{t}
-}}
-+
-\intdt{\intdcell{
-    \testfunction{k} \left( \div{F(\Q, \gradQ} \right)
-}}
+  \hat{x} = \mapping (\bm{x}) =
+  \operatorname{cell-center}(\cell) +
+\begin{pmatrix}
+\Delta x && \\
+&\Delta y & \\
+&&\Delta z&
+\end{pmatrix}
+ % \operatorname{diag}(\Delta x, \Delta y, \Delta z)
+  \begin{pmatrix}
+    x - 0.5\\
+    y - 0.5\\
+    z - 0.5
+  \end{pmatrix}.
+\end{equation}
+We also define the inverse mapping $\mapping^{-1}$.
+This can be used to define a function $f(\bm{x})$ acting on a point $\bm{x}$ of a regular cell in term of a function $\hat{f}(\bm{x})$ that acts on a point of the reference cell by considering
+\begin{equation}
+  \label{eq:function-ref-cell}
+  f(\bm{x}) = f\left( \mapping^{-1}(\bm{x}) \right) = \hat{f}(\hat{\bm{x}}).
+\end{equation}
+
+The determinant of $\mapping$ is simply the volume $V$ of the cell
+\begin{equation}
+  \label{eq:determinant-mapping}
+  \volume = \operatorname{det}(\operatorname{Jacobian}\mapping) = \Delta x \, \Delta y \,\Delta z.
+\end{equation}
+This is useful for evaluating derivatives by the chain rule and, similarly, integrals by substitution.
+For example, we can evaluate a volume integral by
+\begin{equation}
+  \label{eq:integration-by-substitution}
+  \intdcell{
+f(\bm{x})
+  }
   =
-\intdt{\intdcell{
-    \testfunction{k} S(\Q, \bm{x}, t)
-}}
+\volume \intdrefcell{
+    \hat{f}(\hat{\bm{x}})
+  }
 \end{equation}
-\todo{Include gradient everywhere!}
-\todo{Double check the following description}
-We now replace the solution $\bm{Q}$ with so called spacetime-predictor $\stpredictor (\bm{x},t)$ into the weak form and write it as a polynomial using the representation of \cref{eq:cell-approx}.
-Integrate first by parts in time (note basis here not defined over time), flux divergence by parts in space.
-\begin{align}
-\begin{split}
-\label{eq:corrector}
-\left(
-\intdcell{
-  \testfunction{k} \sbasis{l}
-}
-\right)
-(\bm{u^{n+1} - u^{n}})
-&+
-\left(\intdt{\intdcell{
-      \testfunction{k} \Riemann(\stpredictor^-, \stpredictor^+) \cdot \normal
-}}\right)
--\\
-\left(\intdt{\intdcell{
-    \gradient{\testfunction{k}} \cdot  \flux(\stpredictor, \gradient{\stpredictor}) % todo correct gradient?
-}}\right)
-&=
-\left(\intdt{\intdcell{
-      \testfunction{k} \source(\stpredictor)
-}}\right)
-\end{split}
-\end{align}
-The first term motivates an orthogonal basis as this leads to a diagonal mass matrix.
+
+\todo{Maybe show this.}
 
@@
 As initial value for the space-time-predictor we use the solution of the timestep before.
-\todo{Maybe collect into matrices and show scheme?}
+\todo{Collect into matrices and show scheme?}
+To show the computational efficiency of our scheme, we follow the approach of~\cite{dumbser2008unified} and collect our integrals into matrices.
+\begin{equation}
+  \label{eq:predictor-matrices}
+  \begin{alignedat}{2}
+& A = \intdt{\intdcell{
+    \testfunction{k} \pdv{t} \stbasis{l}
+}}
+\qquad&& B \\
+& A
+\qquad&& B
+\end{alignedat}
+\end{equation}
 For details and proof of convergence for the linear case, see~\cite{dumbser2008unified}.
@@
 Extrapolate unknowns to boundary, convert from our basis to basis on faces and so on
+
+\sidetitle{Corrector}
+First, we multiply the system \cref{eq:conservation-law} by a test function $\testfunction{i}$ and integrate over the space-time volume $(\cell \times [t^n, t^{n+1}])$.
+We arrive at the so called weak formulation of the \pde\
+\begin{equation}
+  \label{eq:weak-pde}
+\intdt{\intdcell{
+\testfunction{k} \pdv{\Q}{t}
+}}
++
+\intdt{\intdcell{
+    \testfunction{k} \left( \div{F(\Q, \gradQ} \right)
+}}
+=
+\intdt{\intdcell{
+    \testfunction{k} S(\Q, \bm{x}, t)
+}}
+\end{equation}
+\todo{Include gradient everywhere!}
+\todo{Double check the following description}
+We now replace the solution $\bm{Q}$ with so called spacetime-predictor $\stpredictor (\bm{x},t)$ into the weak form and write it as a polynomial using the representation of \cref{eq:cell-approx}.
+Integrate first by parts in time (note basis here not defined over time), flux divergence by parts in space.
+\newcommand{\massMatrixDef}{\intdcell{
+  \testfunction{k} \sbasis{l}
+}}
+\begin{align}
+\begin{split}
+\label{eq:corrector}
+\left(
+\massMatrixDef
+\right)
+(\bm{u^{n+1} - u^{n}})
+&+
+\left(\intdt{\intdcell{
+      \testfunction{k} \Riemann(\stpredictor^-, \stpredictor^+) \cdot \normal
+}}\right)
+-\\
+\left(\intdt{\intdcell{
+    \gradient{\testfunction{k}} \cdot  \flux(\stpredictor, \gradient{\stpredictor}) % todo correct gradient?
+}}\right)
+&=
+\left(\intdt{\intdcell{
+      \testfunction{k} \source(\stpredictor)
+}}\right)
+\end{split}
+\end{align}
+The first term is our mass matrix with entries
+\newcommand{\massMatrix}[1][]{\bm{M}_{#1}}
+\newcommand{\quadWeight}[1][i]{w_{#1}}
+\begin{equation}
+  \label{eq:mass-matrix}
+  \massMatrix[kl] = \massMatrixDef = \volume \underbrace{\quadWeight[k] \delta_{kl}}_{\text{diagonal}}
+\end{equation}
+which is diagonal and thus convenient to invert.
+\newcommand{\sumbasis}{\sum_i^{(N + 1)^d - 1}}
+We can then insert the definition of our basis function into our equation and arrive at
+\begin{align}
+  \massMatrix \left( \dsol^{t+1} - \dsol^{t} \right) &=
+  \Delta t \left( \bm{a} - \bm{b} + \bm{s} \right) 
+  \intertext{with}
+\begin{split}
+  a &= \sumbasis \\
+  b &= \sumbasis \\
+  s &= \sumbasis.
+\end{split}
+\end{align}
+We can solve this for the new unknows $\bm{u}^{n+1}$
+\begin{align}\label{eq:update-predictor}
+\begin{split}
+  \bm{u}^{n+1} &= \bm{u}^{n} + \Delta t (\operatorname{update}) \\
+  \operatorname{update} &= \massMatrix^{-1} \left( \bm{a} - \bm{b} + \bm{s} \right)
+\end{split}
+\end{align}
+which is clearly of the form of a one-step scheme.
 
@@
 \begin{align}
+  \begin{split}
   \maxConvEigen \vert  &= \Vert \Qv \Vert + c\\
@@
                         \diffCoeff \right)
+  \end{split}
 \end{align}
@@
 We use the total variation (\textsc{tv}) over an arbitrary indicator variable given by
+\newcommand{\tv}{\operatorname{TV}}
 \begin{equation}
   \label{eq:tv}
-  \operatorname{TV}\left[ f(\bm{x}] \right] =
+  \tv \left[ f(\bm{x}] \right] =
 \Vert \left(\intdcell{ \vert \gradient{f \left( \bm{x} \right)} \vert } \right) \Vert_1
 \end{equation}
+This integral can be evaluated efficiently using \cref{eq:integration-by-substitution}.
+\todo{Gradient on reference cell, Gaussian quad., inline}
+\todo{Definition for FV schemes (maybe just mapping to DG-Cells)}
 
@@
 We collect these items in the vector $\gobs = (\mean, \variance, \gobsCount)$
-We can then merge two pairs of observed variables by \cref{alg:merge-variance}.
+We can then merge two pairs of observed variables (\cref{alg:merge-variance}).
 
@@
 \end{algorithm}
-We then use a threshold criterion
 \todo{Cite Chebychev, add concrete form of threshold.}
-This criterion can be justified by Chebychev's inequality, which states that
+Chebychev's inequality
 \begin{equation}
   \label{eq:chebychev}
-  \mathbb{P}(\vert X - \mu \vert \geq c \sigma) \leq \frac{1}{c^2}
+  \mathbb{P}(\vert X - \mu \vert \geq c \sigma) \leq \frac{1}{c^2},
 \end{equation}
-for an arbitrary distribution with mean $\mu$ and standard deviation $\sigma$ probability $\mathbb{P}$.
+with probability $\mathbb{P}$,
+holds for an arbitrary distribution with mean $\mu$ and standard deviation $\sigma$ probability $\mathbb{P}$.
+This motivates the following refinement criterion
+\begin{equation}
+  \label{eq:refinement-criterion}
+  \operatorname{evaluate-refinement}(\Q, \mu, \sigma) =
+  \begin{cases}
+    \text{refine} & \text{if } \tv(\Q) \geq \mu + T_r \sigma \\
+    \text{delete} & \text{if } \tv(\Q) \leq \mu + T_r \sigma \\
+    \text{keep} & \text{otherwise}
+    \end{cases}
+\end{equation}
+which refines when a cell has a significantly higher standard deviation.
+In this equation, the constants $T_r$ and $T_d$ can be used to tailor the trade-off between the quality of approximation and computational cost.
+They can be chosen freely, as long $T_d < T_r$ holds.
+Chebychev's inequality then guarantees that only a subset is marked for refinement.
+Note that even though this inequality provides only a loose bound.
+If one would be willing to assume a distribution of the indicator variable, tighter bounds can be derived.
 
@@
 
-If a solution violates our criteria, we subdivide the infringing cell into $N_2 = 2N + 1$ subcells.
-This results in the remarkable properties, that we first do not loose any spatial resolution and secondly that we can use the same timestep size for both methods.
-This can be seen easily by noticing the similar form of \cref{eq:cfl-aderdg} and \cref{eq:cfl-muscl}.
+If a solution violates our criteria, we recompute the timestep using a limited finite volume method.
+In our case we use the \muscl{}-method (\cref{sec:muscl}).
+The recomputation starts by subdividing the infringing cell into $N_2 = 2N + 1$ subcells.
+This number of subcells has the advantage that we do not loose spatial resolution.
+We can see this easily by noticing the similar form of \cref{eq:cfl-aderdg} and \cref{eq:cfl-muscl}.
+
+For the sake of brevity, we omit technical details.
+We refer the interested reader to~\cite{dumbser2016simple}.
 

### 2018-12-17 writing/thesis/chapters/results.tex
Add reference mapping to DG, begin workin on matrix notation.
It's a mess.

@@
 \todo{Describe how to integrate the error for cells, and effect of volume}
-We evaluate the cell-wise error with Gaussian quadrature.
+We evaluate the cell-wise error with Gaussian quadrature using \cref{eq:integration-by-substitution}
  \begin{equation}

### 2018-12-19 writing/thesis/chapters/methods.tex
Changes.

@@
 \newcommand{\hyperFlux}{\flux^{h}}
-\newcommand{\source}{\bm{S}}
+%\newcommand{\source}{\bm{S}}
+\newcommand{\source}[1][]{
+  \notblank{#1}{
+S_{#1}
+}{
+\bm{S}
+}
+}
 
@@
 
+% Yet to be sorted
+\newcommand{\quadWeight}[1][i]{w_{#1}}
+
 \chapter{An ADER-DG scheme for the Navier-Stokes Equations}\label{chap:methods}
@@
 We conclude this chapter by a description of adaptive mesh refinement (\amr) and finite volume limiting, which combines both numerical methods to achieve a stable, high-order method.
+
+\section{Reactive Compressible Navier Stokes Equations}\label{sec:navier-stokes}
+\newcommand{\diffCoeff}{\varepsilon}
+\newcommand{\hyperFluxDef}{
+  \begin{pmatrix}
+    \Qj \\
+    \Qv  \otimes \Qj + \bm{I} \pressure  \\
+    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure) \\
+    \Qj \QZZ
+  \end{pmatrix}
+}
+
+\newcommand{\viscFluxDef}{
+  \begin{pmatrix}
+     -\diffCoeff \gradient{\Qrho}\\
+     \stressT (\Q, \gradQ)  \\
+     \Qv \cdot \stressT (\Q, \gradQ) - \kappa \gradient{T}\\
+     -\diffCoeff \gradient{\QZ}
+   \end{pmatrix}
+}
+
+Fluid motion can be described by the compressible Navier Stokes equations.
+We follow the description in~\cite{dumbser2010arbitrary} for the Navier Stokes part.
+The coupling with the advection-diffusion-reaction equation follows~\cite{hidalgo2011ader} which describes this equation set for the one-dimensional case.
+We solve the \pde\ in the conversative form \pcref{eq:conservation-law-gradient}\todo{Dont reference to following chapter!}
+\begin{equation}
+ \begin{array}{l}
+ \text{mass cons.} \\
+ \text{momentum cons.} \\
+ \text{energy cons.} \\
+ \text{cont.\ gas} 
+\end{array}
+:
+\quad
+  \pdv{}{t}
+  \underbrace{
+  \begin{pmatrix}
+    \Qrho\\
+    \Qj\\
+    \QE\\
+    \QZ
+    \end{pmatrix}}_{\Q}
+  +
+  \divergence{
+  \underbrace{
+  \left(
+   \underbrace{\hyperFluxDef}_{\hyperFlux(\Q)}
++
+\underbrace{\viscFluxDef}_{\viscFlux(\Q, \gradQ)}
+  \right)}_{\flux(\Q, \gradQ)}}
+ =
+  \underbrace{
+  \begin{pmatrix}
+    \source[\Qrho\phantom{\Qrho}]\\
+    \source[\Qj]\\
+    \source[\QE]\\
+    \source[\QZ]
+    \end{pmatrix}}_{\source(\Q, \bm{x}, t)}
+\end{equation}
+which describes the time evolution of variables $\Q$ with respect to a flux $\flux(\Q, \gradQ)$ and a source $\source(\Q)$.
+The vector of conserved quantities is given by
+\begin{equation}
+  \label{eq:conserved-variables}
+ \Q = \left( \Qrho, \Qj, \QE, \QZ \right),
+\end{equation}
+where $\Qrho$ is the density, $\Qj$ is the two or three-dimensional momentum, $\QE$ the energy density and $\QZ$ is the mass fraction of the chemical reactant.
+The chemical reactant in our case is unburnt gas.
+The rows of the equation are the conservation of mass, the conservation of momentum, the conservation of energy and the continuity of the reactant.
+We split the flux into a hyperbolic $\hyperFlux(\Q)$ and a viscous part$\viscFlux(\gradQ)$
+
+\begin{equation}
+  \label{eq:flux}
+  \flux(\Q, \gradQ) = \hyperFlux(\Q) + \viscFlux(\Q, \gradQ).
+\end{equation}
+The hyperbolic flux is given by
+\begin{equation}
+  \label{eq:hyper-flux}
+  \hyperFlux(\Q) = \hyperFluxDef,
+\end{equation}
+which are the Euler equations coupled with an advection equation.
+In this equation $\bm{a} \otimes \bm{b} = \bm{a} \bm{b}^\intercal$ is the Kronecker or outer product of two vectors $\bm{a}$ and $\bm{b}$.
+The pressure $\pressure$ is given by the caloric equation of state of an ideal reacting gas
+\begin{equation}
+  \label{eq:eos}
+  \pressure = (\gamma - 1) \left(\QE - \frac{1}{2} \left(\Qv \cdot \Qj \right)  - q_0 \QZ \right).
+\end{equation}
+The term $q_0 \QZ$ is the chemical energy with the heat release $q_0$.
+The pressure is related to the temperature $T$ by the thermic ideal gas law
+\begin{equation}
+  \label{eq:temperature}
+ \frac{\pressure}{\Qrho} = RT,
+\end{equation}
+where $R$ is the specific gas constant of a fluid.
+
+The viscous flux is
+\begin{equation}
+  \label{eq:visc-flux}
+  \viscFlux(\Q, \gradQ) = \viscFluxDef.
+\end{equation}
+where $\stressT$ and $(\kappa \nabla T)$ denote the stress tensor and heat flux respectively.
+The viscous effects of the fluid are modeled by the stress tensor
+\begin{equation}
+  \label{eq:stress-tensor}
+  \stressT(Q, \nabla Q) =
+  \mu
+  \left(
+  \left(\nicefrac{2}{3} \divergence{\Qv} \right) -
+  \left( \gradient{\Qv} + \gradient{\Qv}^\intercal \right)
+  \right).
+\end{equation}
+
+We further introduce the ratio of specific heats $\gamma$ and the heat fraction for constant volume $c_v$ and constant volume $c_r$.
+These constants are all fluid dependent and relate to each other and the gas constant by
+\begin{align}
+  \label{eq:fluid-constants}
+  \begin{split}
+  c_v &= \frac{1}{\gamma - 1} R \\
+  c_p &= \frac{\gamma}{\gamma - 1} R\\
+  R &= c_p - c_v\\
+  \gamma &= \frac{c_p}{c_v}.
+  \end{split}
+\end{align}
+\todo{Cite sth for this!}
+We can then compute the heat conduction coefficient
+\begin{equation}
+  \label{eq:heat-conduction-coeff}
+  \kappa = \frac{\mu \gamma}{\Pr} \frac{1}{\gamma - 1} R = \frac{\mu \gamma}{\Pr} c_v,
+\end{equation}
+where the Prandtl number $\Pr$ depends on the fluid.
+% Sutherland's viscosity law:
+% \begin{equation}
+%   \label{eq:sutherland}
+%  \mu(T)  = \mu_0 {\left(\frac{T}{T_0}  \right)}^{\beta} \frac{T_0 + C}{T + C}
+% \end{equation}
+% with \(\beta = 1.5\), \(C = \text{const.}\), reference temperature $T_0$ and reference viscosity $\mu_=$.
+% Equal to
+% \begin{align}
+%   \lambda &= \frac{\mu_0 (T_0 + C)}{T_0^\beta} \\
+%   \mu(T) &= \lambda \frac{T^\beta}{T + C},
+% \end{align}
+% where $\lambda$ is constant for a given fluid.
+
+The maximal absolute eigenvalues for convective and viscous part in direction of a normal vector $\normal$ are
+\begin{align}
+  \begin{split}
+    \maxConvEigen &= \left( \partial \bm{F}/\partial \bm{Q}\right) \cdot \normal = \vert \Qv_{\normal} \vert + c,\\
+    \maxViscEigen &= \left( \partial \bm{F}/\partial \left( \nabla \bm{Q} \cdot \normal \right)\right) \cdot \normal =
+    \max \left( \frac{4}{3} \frac{\mu}{\Qrho},
+                        \frac{\gamma \mu}{\Pr \Qrho},
+                        \diffCoeff \right)
+  \end{split}
+\end{align}
+with velocity in direction of the normal $\Qv_{\normal}$ and speed of sound $c = \sqrt{\gamma R T }$.
+
+We also support two different kind of (optional) source terms.
+\todo{Either include gravity in pressure or add source term for energy.}
+The first source term is gravity, given by
+\begin{equation}\label{eq:source-gravity}
+  \source[\Qj] = - g \bm{k} \cdot \Qj,
+\end{equation}
+where $g = 9.81$ and $\bm{k}$ is a unit vector pointing in $z$-direction.
+
+\newcommand{\reactionTimescale}{\tau}
+\newcommand{\reactionTemperature}{T_{\text{ign}}}
+The chemical reactive source term is
+\begin{equation}\label{eq:source-reaction}
+  \source[\QZ] = - K(T) \QZ.
+\end{equation}
+We use the very simple reaction model
+\begin{equation}\label{eq:reaction-model}
+\begin{cases}
+  - \frac{1}{\reactionTimescale} & T > \reactionTemperature\\
+  0 & \text{otherwise}
+\end{cases}  
+\end{equation}
+where $\reactionTimescale$ is the timescale of the reaction and $\reactionTemperature$ is the activation temperature.
+
+\subsection{Boundary conditions}
+To close the system we need to impose boundary conditions.
+
+For some scenarios we use Cauchy boundary conditions.
+In most cases, we would like to impose periodic boundary conditions, due to the inner workings of ExaHyPE this is not possible.
+Instead we use the analytical solution of our problems at the boundary, imposing both value and gradients of the conservative variables.
+Note that this leads to an error when our problem does not posses an exact analytical solution.
+This is the case for test cases that are analytical solutions to the incompressible Navier Stokes equations but do not satisfy the compressible equation set.
+
+As a physical boundary condition we limit ourselves to the no-slip boundary condition, where we assume that the fluid has a velocity of zero near the wall.
+\todo{Check if this is the correct physical description!}
+We enfore this by setting
+\begin{align}
+  \label{eq:no-slip}
+  \begin{split}
+  \Qrho^o &= \Qrho^i, \\
+  \Qj^o &= -\Qj^i, \\
+  \QE^0 &= \QE^i,\\
+  {(\nabla Q)}^o &= {(\nabla Q)}^i,
+  \end{split}
+\end{align}
+where a superscript of $o$ and $i$ denotes the values outside and inside of the boundary respectively.
 
@@
 
-Inside each cell $\cell$ we represent the solution in terms of the basis function 
-\begin{equation}
-  \label{eq:cell-approx}
-  u(\bm{x}, t^n)_{|\cell[i]} = \hat{u}^n_{i,l} \sbasis{l}(\bm{x}),
-\end{equation}
-where $l$ is a multi-index, containing one index per spatial dimension.
-\todo{dofs $\hat{u}$, local solution, etc.}
-For example, $(l = (l_1, l_2))$ for the two dimensional case.
-This polynomial is interpolating, i.e.\ \ldots\todo{interpolating?}.
-This choice of basis (called \textit{nodal} basis) allows us to easily compute integrals over cells using Gaussian quadrature.
-In detail, we use a the Lagrange interpolation polynomials.
+% Inside each cell $\cell$ we represent the solution in terms of the basis function 
+% \begin{equation}
+%   \label{eq:cell-approx}
+%   u(\bm{x}, t^n)_{|\cell[i]} = \hat{u}^n_{i,l} \sbasis{l}(\bm{x}),
+% \end{equation}
+% where $l$ is a multi-index, containing one index per spatial dimension.
+% \todo{dofs $\hat{u}$, local solution, etc.}
+% For example, $(l = (l_1, l_2))$ for the two dimensional case.
+% This polynomial is interpolating, i.e.\ \ldots\todo{interpolating?}.
+% This choice of basis (called \textit{nodal} basis) allows us to easily compute integrals over cells using Gaussian quadrature.
+% In detail, we use a the Lagrange interpolation polynomials.
 
@@
 This scheme is a predictor-corrector method.
-We first compute a local solution of the cell in the predictor step and then connect with the neighbors in the corrector step.
-In the following we first describe the corrector step as it follows directly from the \pde.
-The predictor is derived shortly after.
+We first compute a local time evolution of each cell in a predictor step and then add the influence of the neighbors in the corrector step.
+$\ldots$
 
-\begin{algorithm}[H]
-  \begin{algorithmic}
-    \Let{$\stpredictor$}{Initial guess}
-    \Let{$F_h$}{$\flux(\Q, \gradQ)$}
-    \Let{$\stpredictor$}{Solve \cref{eq:space-time-predictor} using $F_h, \Q, \gradQ$}
-    \Let{$\left( \hat{F_h}, \hat{\Q}, \hat{\gradQ}, \hat{\stpredictor} \right)$}
-        {Extrapolate to boundary using \cref{eq:boundary-extrapolation}}
-    \Let{update}{Use \cref{eq:corrector} with boundary extrapolated values (fluxes of neighbors)}
-  \end{algorithmic}
-  \caption{The \textsc{ader-dg} algorithm for one cell.}
-\end{algorithm}
+% \begin{algorithm}[H]
+%   \begin{algorithmic}
+%     \Let{$\stpredictor$}{Initial guess}
+%     \Let{$F_h$}{$\flux(\Q, \gradQ)$}
+%     \Let{$\stpredictor$}{Solve \cref{eq:space-time-predictor} using $F_h, \Q, \gradQ$}
+%     \Let{$\left( \hat{F_h}, \hat{\Q}, \hat{\gradQ}, \hat{\stpredictor} \right)$}
+%         {Extrapolate to boundary using \cref{eq:boundary-extrapolation}}
+%     \Let{update}{Use \cref{eq:corrector} with boundary extrapolated values (fluxes of neighbors)}
+%   \end{algorithmic}
+%   \caption{The \textsc{ader-dg} algorithm for one cell.}
+% \end{algorithm}
 
@@
 
-\todo{Maybe show this.}
+\sidetitle{Basis Functions}
+\newcommand{\lagrange}[1][i]{L_{#1}}
+We define basis functions on the reference cell.
+We use Langrange polynomials that are defined in the one-dimensional case by
+\begin{equation}
+  \label{eq:lagrange-basis}
+  \lagrange(x) = \prod_{i \neq j}^N \frac{x - x_j}{x_i - x_j}.
+\end{equation}
+We can then represent functions as a sum over the support points $x_j$
+\begin{equation}
+  \label{eq:langrange-expansion-1d}
+  f(x) = \sum_{i = 0}^N f(x_i) \lagrange[i](x) = f(x_i) \lagrange[i](x),
+\end{equation}
+where we used the Einstein summation convention where summation over repeated indices is implied.
+The support points $x_i$ are chosen such that they coincide with the nodes of the Gauss-Legendre quadrature which we can use to evaluate integrals
+\begin{equation}
+  \label{eq:quadrature-1d}
+  \int_0^1 f(x) \dd{x} = \sum_n^N \quadWeight[n] f(x_n),
+\end{equation}
+where $x_n$ is a quadrature point with weight $\quadWeight[n]$.
+The basis functions are similarly defined in $d$ dimensions by considering nodes that are the tensor-products of $d$ one-dimensional Gauss-Legendre quadrature.
+To simplify notation, we order the polynomials by a linearised index, a $d$-dimensional function is then approximated by
+\begin{equation}
+  \label{eq:lagrange-expansion}
+  f(\bm{x}) = \sum_{i = 0}^{N^d} f(\bm{x}_i) \lagrange[i](\bm{x}) = f(\bm{x}_i) \lagrange[i](\bm{x}).
+\end{equation}
+Similarly to the one-dimensional case, we can evaluate integrals by
+\begin{align}
+  \label{eq:quadrature}
+  \int_0^1 f(\bm{x}) \dd{\bm{x}} &= \sum_n^{(N+1)^D - 1} \quadWeight[n] f(\bm{x}_n) \\
+  \intertext{with}
+  \quadWeight[n] &= \prod_{i}^{d} \quadWeight[i].
+\end{align}
+\todo{Fix notation, especially multi-dimensional integral.}
+\todo{Check number of total polynomials.}
+% TODO: Quadrature
+
+Two important properties of this family of polynomials are
+  \begin{alignat}{10}
+    \label{eq:basis-interpolating}
+&& \text{Interpolating:} \qquad & \lagrange[i] (x_j) &= \delta_{ij}\\
+\label{eq:basis-orthogonality}
+&& \text{Orthogonality:} \qquad & \ldots &= \ldots
+    \end{alignat}
 
 \sidetitle{Predictor}
-To derive the predictor, we again take an approximation of our solution in a nodal basis, but now consider polynomials that are defined both in space and time
+To derive the predictor, we take an approximation of our solution in a nodal basis that is defined both in space and time
 \begin{equation}
@@
 \end{equation}
-We now multiply the conservation law again by a test function (of the same function space as the basis) and arrive at the weak formulation
+Furthermore we assume that all quantities are given in this represantation.
+We now multiply the conservation law by a test function (of the same function space as the basis) and arrive at the weak formulation
 \begin{equation}\label{eq:weak-pde-space-time}
@@
 \end{equation}
-Similar to the derivation of the corrector, we again integrate the first term by parts in time and the flux divergence in space.
-This time we do not use the Riemann solver for the flux boundary term but rather use the discrete solution at time $t$.
-Note that this neglects the interaction with neighbouring cells; we account for this in the corrector step.
+We integrate the first term by parts in time and the flux divergence in space.
+Here we do not use the Riemann solver for the flux boundary term but rather use the discrete solution at time $t$.
+Note that this neglects the interaction with neighbouring cells, we account for this in the corrector step.
 \todo{Replace $\bm{x}$ with a macro some other letter. Is also coordinate!}
-
 \begin{align}\label{eq:space-time-predictor}
@@
 \end{align}
-Inserting \cref{eq:cell-approx-space-time} results in a local systems of equations that can be solved in a fixed point iteration scheme.
+Inserting \cref{eq:cell-approx-space-time} results in a local systems of equations that can be by a fixed point iteration scheme.
 \todo{Inital guess correct? Maybe cite sth?}
@@
 \todo{Collect into matrices and show scheme?}
-To show the computational efficiency of our scheme, we follow the approach of~\cite{dumbser2008unified} and collect our integrals into matrices.
-\begin{equation}
+To show the computational efficiency of our scheme, we follow the approach of~\cite{dumbser2008unified} and collect our integrals into matrices\todo{Source is Dominics \aderdg-document.}.
+
+\newcommand{\pleft}{\bm{L}}
+\newcommand{\prightsol}{\bm{r}}
+\newcommand{\prightpred}{\bm{w}}
+\begin{align}
   \label{eq:predictor-matrices}
-  \begin{alignedat}{2}
-& A = \intdt{\intdcell{
-    \testfunction{k} \pdv{t} \stbasis{l}
-}}
-\qquad&& B \\
-& A
-\qquad&& B
-\end{alignedat}
-\end{equation}
+  \pleft &= \ldots \\
+  \prightsol &= \ldots \\
+  \prightpred &= \ldots
+\end{align}
+Using these matrices, we can solve for the space-time-predictor with the iterative scheme
+\begin{align}
+  \label{eq:predictor-iterative}
+  \pleft \stpredictor &= \prightsol (\dsol) - \prightpred(\stpredictor) \\
+ \stpredictor &= \pleft^{-1} \left( \prightsol (\dsol) - \prightpred(\stpredictor) \right).
+\end{align}
 For details and proof of convergence for the linear case, see~\cite{dumbser2008unified}.
+
+We then prepare the space-time-predictor for use in the corrector step.
+Due to the linearity of the Riemann solver, we can exchange time and space integration and thus only need to consider the Riemann problem for time-averaged quantities.
+We can compute this for the space-time-predictor by
+\begin{align}
+  \ldots = \ldots,
+\end{align}
+the procedure is similar for all other quantities (Q, gradQ, fluxes).
+
+Finally, we extrapolate all quantities to the boundary.
+This is needed for the Riemann solver and for the reconstruction of boundary values.
+We achieve this by
+\begin{align}
+  \label{eq:boundary-extrapolation}
+  \ldots = \ldots.
+\end{align}
 
@@
 \sidetitle{Corrector}
-First, we multiply the system \cref{eq:conservation-law} by a test function $\testfunction{i}$ and integrate over the space-time volume $(\cell \times [t^n, t^{n+1}])$.
-We arrive at the so called weak formulation of the \pde\
+First, we multiply the system \cref{eq:conservation-law-gradient} by a test function $\testfunction{i}$ and integrate over the space-time volume $(\cell \times [t^n, t^{n+1}])$.
+Note that the testfunctions
+\begin{equation}
+  \label{eq:cell-approx-space}
+  q(\bm{x})_{|\cell[i]} = \hat{u}^n_{i,l} \stbasis{l}(\bm{x}).
+\end{equation}
+
+here do not depend on time but only on the spatial dimensions.
+We arrive yet again at the weak formulation of the \pde\
 \begin{equation}
@@
     \testfunction{k} S(\Q, \bm{x}, t)
-}}
+}}.
 \end{equation}
@@
 \todo{Double check the following description}
-We now replace the solution $\bm{Q}$ with so called spacetime-predictor $\stpredictor (\bm{x},t)$ into the weak form and write it as a polynomial using the representation of \cref{eq:cell-approx}.
+We now replace the solution $\bm{Q}$ with the spacetime-predictor $\stpredictor (\bm{x},t)$ and write it as a polynomial using the representation of \cref{eq:cell-approx}.
 Integrate first by parts in time (note basis here not defined over time), flux divergence by parts in space.
@@
 \newcommand{\massMatrix}[1][]{\bm{M}_{#1}}
-\newcommand{\quadWeight}[1][i]{w_{#1}}
 \begin{equation}
@@
 \end{equation}
-which is diagonal and thus convenient to invert.
+which is diagonal thanks to the orthogonal basis \pcref{eq:basis-orthogonality} and thus trivial to invert.
 \newcommand{\sumbasis}{\sum_i^{(N + 1)^d - 1}}
@@
 \end{equation}
-We also use the slopes defined in \cref{eq:slopes} to estimate the gradient of $\Q$ in each cell by the block matrix\todo{Notation!}
+We also use the slopes defined in \cref{eq:slopes} to estimate the gradient of $\cellAvg$ in each cell by the block matrix\todo{Notation!}
 \begin{equation}
@@
 \end{equation}
-which is of course an abuse of notation insofar as it is not the gradient of the constant cell value but rather of the linear reconstruction.
+which is of course an abuse of notation insofar as it is not the gradient of the constant cell value but rather of the linear reconstruction \pcref{eq:slopes}.
 \sidetitle{Time Evolution}
@@
 with a constant value of CFL that is typically close to $0.7$.
-
-\section{Reactive Compressible Navier Stokes Equations}\label{sec:navier-stokes}
-Fluid motion can be described by the compressible Navier Stokes equations.
-We follow the description in~\cite{dumbser2010arbitrary} for the Navier Stokes part.
-The coupling with the advection-diffusion-reaction equation follows~\cite{hidalgo2011ader} which describes this equation set for the one-dimensional case.
-
-The vector of conserved quantities is given by
-\begin{equation}
-  \label{eq:conserved-variables}
- \Q = \left( \Qrho, \Qj, \QE, \QZ \right),
-\end{equation}
-where $\Qrho$ is the density, $\Qj$ is the momentum, $\QE$ the energy density and $\QZ$ is the mass fraction of the chemical reactant.
-
-We split the flux into a hyperbolic part $\hyperFlux(\Q)$ and an viscous flux $\viscFlux(\gradQ)$
-\begin{equation}
-  \label{eq:flux}
-  \flux(\Q, \gradQ) = \hyperFlux(\Q) + \viscFlux(\Q, \gradQ).
-\end{equation}
-
-\newcommand{\diffCoeff}{\varepsilon}
-\newcommand{\hyperFluxDef}{
-  \begin{pmatrix}
-    \Qj \\
-    \Qv  \otimes \Qj + \bm{I} \pressure  \\
-    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure) \\
-    \Qj \QZZ
-  \end{pmatrix}
-}
-
-\newcommand{\viscFluxDef}{
-  \begin{pmatrix}
-     -\diffCoeff \gradient{\Qrho}\\
-     \stressT (\Q, \gradQ)  \\
-     \Qv \cdot \stressT (\Q, \gradQ) - \kappa \gradient{T}\\
-     -\diffCoeff \gradient{\QZ}
-   \end{pmatrix}
-}
-
-The hyperbolic flux is given by
-\begin{equation}
-  \label{eq:hyper-flux}
-  \hyperFlux(\Q) = \hyperFluxDef,
-\end{equation}
-which are the Euler equations coupled with an advection equation.
-The viscous flux is
-\begin{equation}
-  \label{eq:visc-flux}
-  \viscFlux(\Q, \gradQ) = \viscFluxDef.
-\end{equation}
-where $\pressure$, $\stressT$ and $(\kappa \nabla T)$ denote the pressure, stress tensor and heat flux respectively.
-Temperature is denoted by $T$.
-
-Putting everything together, our complete \pde\ is a conservation law of the form of \cref{eq:conservation-law-gradient}
-\begin{equation}
- \begin{array}{l}
- \text{mass cons.} \\
- \text{momentum cons.} \\
- \text{energy cons.} \\
- \text{cont.\ gas} 
-\end{array}
-:
-\quad
-  \pdv{}{t}
-  \underbrace{
-  \begin{pmatrix}
-    \Qrho\\
-    \Qj\\
-    \QE\\
-    \QZ
-    \end{pmatrix}}_{\Q}
-  + 
-  \divergence{
-  \left(
-   \underbrace{\hyperFluxDef}_{\hyperFlux(\Q)}
-+
-\underbrace{\viscFluxDef}_{\viscFlux(\Q, \gradQ)}
-  \right)}
- =
-  \underbrace{
-  \begin{pmatrix}
-    S_{\Qrho\phantom{\Qrho}}\\
-    S_{\Qj}\\
-    S_{\QE}\\
-    S_{\QZ}
-    \end{pmatrix}}_{\source(\Q, \bm{x}, t)}
-\end{equation}
-
-We close the system with the equation of state of an ideal reacting gas
-\begin{equation}
-  \label{eq:eos}
-  \pressure = (\gamma - 1) \left(\QE - \frac{1}{2} \left(\Qv \cdot \Qj \right)  - q_0 \QZ \right).
-\end{equation}
-The term $q_0 \QZ$ corresponds to the chemical energy, where $q_0$ is the heat release.
-The temperature $T$ relates to pressure and density by the ideal gas law
-\begin{equation}
-  \label{eq:temperature}
- \frac{\pressure}{\Qrho} = RT,
-\end{equation}
-where $R$ is the specific gas constant.
-
-We further introduce the ratio of specific heats $\gamma$ and the heat fraction for constant volume $c_v$ and constant volume $c_r$.
-These constants are all fluid dependent and relate to each other by
-\begin{align}
-  \label{eq:fluid-constants}
-  \begin{split}
-  c_v &= \frac{1}{\gamma - 1} R \\
-  c_p &= \frac{\gamma}{\gamma - 1} R\\
-  R &= c_p - c_v\\
-  \gamma &= \frac{c_p}{c_v}.
-  \end{split}
-\end{align}
-\todo{Cite sth!}
-We can finally define the heat conduction coefficient $\kappa$
-\begin{equation}
-  \label{eq:heat-conduction-coeff}
-  \kappa = \frac{\mu \gamma}{\Pr} \frac{1}{\gamma - 1} R = \frac{\mu \gamma}{\Pr} c_v
-\end{equation}
-where Prandtl number $\Pr$ again depends on the fluid.
-
-% Sutherland's viscosity law:
-% \begin{equation}
-%   \label{eq:sutherland}
-%  \mu(T)  = \mu_0 {\left(\frac{T}{T_0}  \right)}^{\beta} \frac{T_0 + C}{T + C}
-% \end{equation}
-% with \(\beta = 1.5\), \(C = \text{const.}\), reference temperature $T_0$ and reference viscosity $\mu_=$.
-% Equal to
-% \begin{align}
-%   \lambda &= \frac{\mu_0 (T_0 + C)}{T_0^\beta} \\
-%   \mu(T) &= \lambda \frac{T^\beta}{T + C},
-% \end{align}
-% where $\lambda$ is constant for a given fluid.
-
-The viscous effects are modeled by the stress tensor
-\begin{equation}
-  \label{eq:stress-tensor}
-  \stressT(Q, \nabla Q) =
-  \mu
-  \left(
-  \left(\nicefrac{2}{3} \divergence{\Qv} \right) -
-  \left( \gradient{\Qv} + \gradient{\Qv}^\intercal \right)
-  \right).
-\end{equation}
-
-The maximal eigenvalues for convective and viscous part are
-\begin{align}
-  \begin{split}
-  \maxConvEigen \vert  &= \Vert \Qv \Vert + c\\
-  \maxViscEigen \vert &= \max \left( \frac{4}{3} \frac{\mu}{\Qrho},
-                        \frac{\gamma \mu}{\Pr \Qrho},
-                        \diffCoeff \right)
-  \end{split}
-\end{align}
-with speed of sound $c = \sqrt{\gamma R T }$.
-
-\subsection{Boundary conditions}
-To close the system we need to impose boundary conditions.
-
-For some scenarios we use Cauchy boundary conditions.
-In most cases, we would like to impose periodic boundary conditions, due to the inner workings of ExaHyPE this is not possible.
-Instead we use the analytical solution of our problems at the boundary, imposing both value and gradients of the conservative variables.
-Note that this leads to an error when our problem does not posses an exact analytical solution.
-This is the case for test cases that are analytical solutions to the incompressible Navier Stokes equations but do not satisfy the compressible equation set.
-
-As a physical boundary condition we limit ourselves to the no-slip boundary condition, where we assume that the fluid has a velocity of zero near the wall.
-\todo{Check if this is the correct physical description!}
-We enfore this by setting
-\begin{align}
-  \label{eq:no-slip}
-  \begin{split}
-  \Qrho^o &= \Qrho^i, \\
-  \Qj^o &= -\Qj^i, \\
-  \QE^0 &= \QE^i,\\
-  {(\nabla Q)}^o &= {(\nabla Q)}^i,
-  \end{split}
-\end{align}
-where a superscript of $o$ and $i$ denotes the values outside and inside of the boundary respectively.
 
@@
   \begin{cases}
-    \text{true} & \Qrho > 0 \land \pressure > 0 \land \left(0 \leq \QZ \leq 1 \right)\\
+    \text{true} & \Qrho > 0 \land \pressure > 0 \land \QZZ > 0 \\
     \text{false} & \text{otherwise}.

### 2018-12-20 writing/thesis/chapters/introduction.tex
Further work on ADER-DG, NS, AMR
Some more work.
Change stuff.

@@
-\chapter{Introduction}
+\chapter{Introduction}\label{chap:introduction}
 We make the following contributions:
-
 \begin{itemize}
-\item We implement an \textsc{ader-dg} scheme for the compressible Navier-Stokes equations.
+\item We implement an \textsc{ader-dg} and \textsc{muscl}-scheme for the compressible Navier-Stokes equations.
+\item We describe a coupling of the compressible Navier-Stokes equations with an advection-diffusion-reaction term for two dimensional problems.
 \item We compare different mesh refinement strategies and evaluate their computational efficiency.

### 2018-12-20 writing/thesis/chapters/methods.tex
Change stuff.

@@
 \newcommand{\boundary}{\partial \domain}
-\newcommand{\sbasis}[1]{\Phi_{#1}}
-\newcommand{\stbasis}[1]{\Phi_{#1}}
-\newcommand{\testfunction}[1]{\Phi_{#1}}
+\newcommand{\sbasis}[1][]{\Phi_{#1}}
+\newcommand{\stbasis}[1][]{\Theta_{#1}}
+\newcommand{\sbasisRef}[1][]{\hat{\sbasis[#1]}}
+\newcommand{\stbasisRef}[1][]{\hat{\stbasis[#1]}}
+\newcommand{\stestfunction}[1]{\sbasis[#1]}
+\newcommand{\sttestfunction}[1]{\stbasis[#1]}
 \newcommand{\normal}{\bm{n}}
@@
 The mapping, which takes a point on the reference cell with coordinates $\hat{\bm{x}}$ and returns a point $\bm{x}$ on a cell with center and widths $(\Delta x, \Delta y, \Delta z)$, is given by
-\begin{equation}
+\begin{equation}\label{eq:space-mapping}
   \hat{x} = \mapping (\bm{x}) =
@@
 \end{equation}
+
 We also define the inverse mapping $\mapping^{-1}$.
@@
 
-The determinant of $\mapping$ is simply the volume $V$ of the cell
+Similar to this, we define a mapping that maps a point in time to the reference time $\in (0,1)$
+\todo{Fix this/remove}
+\newcommand{\timeMapping}{\mathcal{T}}
+\begin{equation}
+  \label{eq:time-mapping}
+  \hat{t} = \timeMapping(t) = t_0 + (\Delta t) t,
+\end{equation}
+where $\Delta t$ is timestep of a cell and $t_0$ is the beginning of its time interval.
+
+The Jacobian determinant of $\mapping$ is simply the volume $V$ of the cell
 \begin{equation}
   \label{eq:determinant-mapping}
-  \volume = \operatorname{det}(\operatorname{Jacobian}\mapping) = \Delta x \, \Delta y \,\Delta z.
+  \volume = \operatorname{det}(\operatorname{Jacobian}\mapping) = \Delta x \, \Delta y \,\Delta z,
 \end{equation}
+the Jacobian determinant of $\timeMapping$ is $\Delta t$.
 This is useful for evaluating derivatives by the chain rule and, similarly, integrals by substitution.
@@
 \end{equation}
-
 \sidetitle{Basis Functions}
+\newcommand{\lagrangeRef}[1][i]{\hat{L}_{#1}}
 \newcommand{\lagrange}[1][i]{L_{#1}}
-We define basis functions on the reference cell.
+The next step is the definition of basis functions for the reference cell.
 We use Langrange polynomials that are defined in the one-dimensional case by
@@
   \label{eq:lagrange-basis}
-  \lagrange(x) = \prod_{i \neq j}^N \frac{x - x_j}{x_i - x_j}.
+  \lagrangeRef(x) = \prod_{i \neq j}^N \frac{x - x_j}{x_i - x_j}.
 \end{equation}
@@
   \label{eq:langrange-expansion-1d}
-  f(x) = \sum_{i = 0}^N f(x_i) \lagrange[i](x) = f(x_i) \lagrange[i](x),
+  f(x) = \sum_{i = 0}^N f(x_i) \lagrangeRef[i](x) = f(x_i) \lagrangeRef[i](x),
 \end{equation}
@@
   \label{eq:lagrange-expansion}
-  f(\bm{x}) = \sum_{i = 0}^{N^d} f(\bm{x}_i) \lagrange[i](\bm{x}) = f(\bm{x}_i) \lagrange[i](\bm{x}).
+  f(\bm{x}) = \sum_{i = 0}^{N^d} f(\bm{x}_i) \lagrangeRef[i](\bm{x}) = f(\bm{x}_i) \lagrangeRef[i](\bm{x}).
 \end{equation}
@@
   \label{eq:quadrature}
-  \int_0^1 f(\bm{x}) \dd{\bm{x}} &= \sum_n^{(N+1)^D - 1} \quadWeight[n] f(\bm{x}_n) \\
+  \underbrace{\int_0^1 \cdots \int_0^1}_{D \text{ times}} f(\bm{x}) \dd{\bm{x}} &= \sum_n^{(N+1)^D - 1} \quadWeight[n] f(\bm{x}_n) \\
   \intertext{with}
@@
     \label{eq:basis-interpolating}
-&& \text{Interpolating:} \qquad & \lagrange[i] (x_j) &= \delta_{ij}\\
+&& \text{Interpolating:} \qquad & \lagrangeRef[i] (x_j) &= \delta_{ij}\\
 \label{eq:basis-orthogonality}
-&& \text{Orthogonality:} \qquad & \ldots &= \ldots
+&& \text{Orthogonality:} \qquad &
+\int_0^1 \cdots \int_0^1 \lagrangeRef[j](\hat{\bm(x)} \lagrangeRef[j]{\hat{\bm{x}}}) \dd{\hat{\bm{x}}}  &= \quadWeight[i] \delta_{ij}
     \end{alignat}
+
+We will later need basis functions over a space-cell 
+\begin{align}\label{eq:space-basis}
+  \begin{split}
+  \sbasisRef(\hat{\bm{x}}) &= \sum_i^{(N+1)^D - 1} \lagrange[i] (x_i)\\
+  \sbasis(\bm{x}) &= \sbasisRef \left( \mapping(\bm{x}) \right)
+  \end{split}
+\end{align}
+where $\sbasisRef$ denotes the basis function on the reference cell.
+Similar we define a basis for a space-time element defined by $(0, 1)^D \times (t^n, t^{n+1})$
+\begin{align}\label{eq:space-time-basis}
+  \begin{split}
+  \stbasisRef(\hat{\bm{x}}, \hat{t}) &= \sum_j^{N} \sum_i^{(N+1)^D - 1} \lagrange[j](x_j) \lagrange[i] (x_i)\\
+  \stbasis (\bm{x}, t) &= \stbasisRef \left( \mapping(\bm{x}), \timeMapping(t) \right)
+  \end{split}
+\end{align}
 
@@
 \intdt{\intdcell{
-    \testfunction{k}(\bm{x}, t)
+    \sttestfunction{k}(\bm{x}, t)
     \pdv{\stpredictor}{t}
@@
 \intdt{\intdcell{
-    \testfunction{k}(\bm{x}, t)
+    \sttestfunction{k}(\bm{x}, t)
     \left(
@@
 \intdt{\intdcell{
-  \testfunction{k} \source(\stpredictor)
+  \sttestfunction{k} \source(\stpredictor)
 }}.
@@
 \intdcell{
-  \testfunction{k} (\bm{x}, t^{n+1}) \stpredictor(\bm{x}, t^{n+1})
+  \sttestfunction{k} (\bm{x}, t^{n+1}) \stpredictor(\bm{x}, t^{n+1})
 }
@@
 \intdt{\intdcell{
-    \pdv{}{t} \testfunction{k}(\bm{x}, t) \stpredictor(\bm{x}, t)
+    \pdv{}{t} \sttestfunction{k}(\bm{x}, t) \stpredictor(\bm{x}, t)
 }}
@@
 \intdcell{
-  \testfunction{k}(\bm{x},t^n) \dsol(\bm{x}, t^n)
+  \sttestfunction{k}(\bm{x},t^n) \dsol(\bm{x}, t^n)
 } = \\
 \intdt{\intdcell{
-    \testfunction{k}(\bm{x},t) \divergence{\flux(\stpredictor, \gradient{\stpredictor})}
+    \sttestfunction{k}(\bm{x},t) \divergence{\flux(\stpredictor, \gradient{\stpredictor})}
 }}
@@
 \intdt{\intdcell{
-    \testfunction{k}(\bm{x}, t) \source(\stpredictor)
+    \sttestfunction{k}(\bm{x}, t) \source(\stpredictor)
 }}
@@
 \sidetitle{Corrector}
-First, we multiply the system \cref{eq:conservation-law-gradient} by a test function $\testfunction{i}$ and integrate over the space-time volume $(\cell \times [t^n, t^{n+1}])$.
+First, we multiply the system \cref{eq:conservation-law-gradient} by a test function $\stestfunction{i}$ and integrate over the space-time volume $(\cell \times [t^n, t^{n+1}])$.
 Note that the testfunctions
@@
   \label{eq:cell-approx-space}
-  q(\bm{x})_{|\cell[i]} = \hat{u}^n_{i,l} \stbasis{l}(\bm{x}).
+  q(\bm{x})_{|\cell[i]} = \hat{u}^n_{i,l} \sbasis{l}(\bm{x}).
 \end{equation}
@@
 \intdt{\intdcell{
-\testfunction{k} \pdv{\Q}{t}
+\stestfunction{k} \pdv{\Q}{t}
 }}
@@
 \intdt{\intdcell{
-    \testfunction{k} \left( \div{F(\Q, \gradQ} \right)
+    \stestfunction{k} \left( \div{F(\Q, \gradQ } \right)
 }}
@@
 \intdt{\intdcell{
-    \testfunction{k} S(\Q, \bm{x}, t)
+    \stestfunction{k} S(\Q, \bm{x}, t)
 }}.
@@
 \newcommand{\massMatrixDef}{\intdcell{
-  \testfunction{k} \sbasis{l}
+  \stestfunction{k} \sbasis[l]
 }}
@@
 \left(\intdt{\intdcell{
-      \testfunction{k} \Riemann(\stpredictor^-, \stpredictor^+) \cdot \normal
+      \stestfunction{k} \Riemann(\stpredictor^-, \stpredictor^+) \cdot \normal
 }}\right)
@@
 \left(\intdt{\intdcell{
-    \gradient{\testfunction{k}} \cdot  \flux(\stpredictor, \gradient{\stpredictor}) % todo correct gradient?
+    \gradient{\stestfunction{k}} \cdot  \flux(\stpredictor, \gradient{\stpredictor}) % todo correct gradient?
 }}\right)
@@
 \left(\intdt{\intdcell{
-      \testfunction{k} \source(\stpredictor)
+      \stestfunction{k} \source(\stpredictor)
 }}\right)
@@
 \begin{split}
-  a &= \sumbasis \\
-  b &= \sumbasis \\
-  s &= \sumbasis.
+  a &= \sumbasis F_n \intdcell{
+\sbasis[n] \gradient{\sbasis[n]}
+  } \\
+  b &= \ldots \\
+  s_n &= \sumbasis \intdcell{
+s \sbasis[n]
+  }.
 \end{split}
@@
 
-We use the total variation (\textsc{tv}) over an arbitrary indicator variable given by
+Let $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ be a function that maps the discrete solution of a cell to an arbitrary indicator variable.
+Furthermore, we assume that $\bm{f}$ is expanded in the space-basis as in \cref{eq:cell-approx-space}.
+Then the total variation (\textsc{tv}) of this function is defined by
 \newcommand{\tv}{\operatorname{TV}}
@@
   \tv \left[ f(\bm{x}] \right] =
-\Vert \left(\intdcell{ \vert \gradient{f \left( \bm{x} \right)} \vert } \right) \Vert_1
+\left(\intdcell{ \vert \gradient{f \left( \bm{x} \right)} \vert } \right).
 \end{equation}
-This integral can be evaluated efficiently using \cref{eq:integration-by-substitution}.
+This integral can be evaluated efficiently on the reference cell \pcref{eq:space-mapping,eq:cell-approx-space} with Gaussian quadrature \pcref{eq:quadrature}.
+
 \todo{Gradient on reference cell, Gaussian quad., inline}
 \todo{Definition for FV schemes (maybe just mapping to DG-Cells)}
-
 \newcommand{\gobs}{\operatorname{G}}

### 2018-12-26 writing/thesis/chapters/implementation.tex
Add first draft of implementation chapter.

@@
+\newcommand{\softwareName}[1]{\textit{#1}}
+\newcommand{\exahype}{\softwareName{ExaHyPE}}
+\newcommand{\peano}{\softwareName{Peano}}
+\newcommand{\className}[1]{\texttt{#1}}
+\newcommand{\funName}[1]{\textsf{#1}}
+\newcommand{\fileName}[1]{\textbf{#1}}
+\newcommand{\varName}[1]{\enquote{#1}}
+
+\newcommand{\cpp}{C\texttt{++}}
+\newcommand{\tbb}{\textsc{tbb}}
+\newcommand{\mpi}{\textsc{mpi}}
+
 \chapter{Implementation}\label{chap:implementation}
-\todo{Write this chapter!}
+This chapter is organized as follows:
+We first give a short overview of the general structure of the \exahype{} code and then describe the changes done over the course of this project.
+\exahype{} implements an \aderdg{} solver with \muscl{} limiting and \textsc{amr}, as described in \cref{chap:methods}.
+It uses \softwareName{Intel® Threading Building Blocks} (\tbb{}) for node-level parallelism and the \softwareName{Message Passing Interface} (\mpi{}) for intra-node parallelism. 
+In the following we define a \enquote{user} as someone who implements the logic of a \pde{} but does not change the implementation of \exahype{} itself.
+This is in contrast with a \enquote{developer} whose scope is the entirety of the source code.
+The goal of our implementation is that all new features should be accesible to users, not only developers.
+
+\section{ExaHyPE}
+\exahype\ is based on the space-filling-curves library \peano~\cite{weinzierl2011}.
+The workflow from the perspective of a user is
+\begin{itemize}
+\item Generate glue-code using a \softwareName{Python}-based Toolkit that inserts parameters into templates.\todo{Jinja? Or sth else?}
+  The parameters are configured in a setting file.
+  The user can configure the number of dimensions, numerical order and type of solver (\aderdg{}, \muscl, or limiting-\aderdg).
+  Depending on the solver type, a different implementation is generated.
+  In case of a limiting solver, a finite-volume and a \dg\ implementation is generated.
+  An implementation consists of
+  \begin{itemize}
+  \item An \className{AbstractSolver} that is a subclass of \className{FiniteVolumesSolver}, \className{ADERDGSolver} or \className{LimitingADERDGSolver}.
+    The solver types all have a shared superclass \className{Solver} which describes a common interface.
+  \item A class that inherits from the aforementioned abstract class that needs to be used to implement the program logic.
+  \end{itemize}
+
+\item The user then needs to modify the generated glue code.
+  The \pde{} is specified in the methods \funName{flux} and \funName{eigenvalues}.
+  We describe the grid refinement criterion in \funName{refinementCriterion} and the limiting criterion in \funName{isPhysicallyAdmissible}
+  To close the system, the user needs to prescribe initial and boundary conditions with \funName{adjustPointSolution}, \funName{boundaryConditions} and \funName{boundaryValues}.
+  The methods \funName{boundaryConditions} first calls \funName{boundaryValues} and then solves the Riemann-problem at the boundary.
+  In many cases it thus suffices to only override the latter method.
+\item Finally, the user can specify more options such as mesh size and spacing, simulation time, parallelization options, plotters, and optimization parameters.
+ After compiling the program, it can be run with the setting file as first and only parameter.
+\end{itemize}
+
+From the perspective of a developer, the situation is more complicated.
+We will thus only give the necessary minimum of information that is needed to understand the modifications conducted by us.
+\exahype{} is structured as a \peano{} project and follows the basic structure:
+\begin{itemize}
+\item A runner iterates through the grid and calls an adapter for so-called events.
+  An example for an event is entering a cell, for example.
+\item An adapter calls one or multiple mappings.
+\item A mapping then performs the actual program logic.
+  For our purposes, we only need to consider the mappings (with corresponding adapters):
+  \begin{itemize}
+  \item \className{FinalizeMeshRefinement}
+  \item \className{FusedTimeStep}
+  \end{itemize}
+\item Often, a mapping calls a method defined in \className{Solver}.
+  These implementation can differ between different solvers.
+\end{itemize}
+Furthermore, the degrees of freedom and some meta-information are stored each cell in a heap data-structure.
+The information for each cell is defined in the file \fileName{ADERDGCellDescrition.def} for the \dg{}-solver.
+Similar files exists for the finite volume solver but are not relevant for us.
+These files are converted to \cpp{} files by the software \softwareName{DaStGen}~\cite{bungartz2008dastgen}.
+
+\section{Implementing numerics}
+We needed to modify the existing implementation of the numerics to be able to solve problems with diffusive fluxes.
+These changes are:
+\begin{itemize}
+\item Modifying the space-time-predictor (defined in file \fileName{spaceTimePredictorNonlinear.cpph}).
+  \begin{itemize}
+  \item In the function \funName{aderPicardLoopNonlinear} we pass the gradient of the conserved variables to the \funName{flux} method.
+    We also return the time-average of the gradient.
+   \item In the function \funName{aderExtrapolatorNonlinear} we also compute the extrapolated gradient.
+    \item In the function \funName{spaceTimePredictorNonlinear} we also return the extrapolated gradient.
+  \end{itemize}
+\item Storing the extrapolated gradient for each cell for use in the boundary conditions.
+\item Using the gradient for the computation of the boundary conditions.
+  They are defined in the file \fileName{boundaryConditions.cpph}.
+\item Adding the diffusive penalty terms for Riemann solver (\fileName{riemannSolverNonlinear.cpph}) and \textsc{cfl}-condition (\fileName{stableTimeStepSize.cpph}).
+\item Computing the gradient for the \muscl{} scheme (\fileName{musclhancock.cpph}) and passing it to the flux (\fileName{rusanov.cpph}).
+\end{itemize}
+Furthermore, we needed to change the templates for the glue code and needed to modify some function signatures to accompany the other changes.
+
+\section{Implementing Global Observables}
+\newcommand{\ngobs}{N^{\text{gobs}}}
+The implementation of the global observables is quite simple.
+
+We use three functions that need to be defined by the user and adher to the interface
+\begin{itemize}
+\item The function \funName{resetGlobalObservables} takes no arguments and returns a vector of size $\ngobs$.
+  This vector should be the identity of the reduction, i.e.\ a value $a$ with the property that $\operatorname{reduce}(a, b) = b$.
+  \todo{Is this right?}
+\item The function \funName{mapGlobalObservables} that takes the degrees of freedoms of a cell and its cell size and returns a vector of size $\ngobs$.
+  This vector should be the observables that correspond to the cell.
+\item The function \funName{reduceGlobalObservables} updates the current partially reduced vector of global observables \varName{reducedGlobalObservables} with another vector of partially reduced observables \varName{curGlobalObservables}.
+\end{itemize}
+We then compute the observables by \cref{alg:reduce-gobs}
+\begin{algorithm}[htb]
+  \begin{algorithmic}
+    \Let{observables}{\Call{resetGlobalObservables}{}}
+    \For{$\text{cell} \in \text{cells}$}
+    \Let{curObservables}{\Call{mapGlobalObservables}{$Q_\text{cell}, \Delta x_\text{cell}$}}
+    \Let{observables}{\Call{reduceGlobalObservables}{observables, curObservables}}
+    \EndFor{}
+    \State\Return{observables}
+  \end{algorithmic}
+  \caption{\label{alg:reduce-gobs}Reducing global observables}
+\end{algorithm}
+This results in a simple, yet powerful interface, which can be used to implement all reductions that can be done in a pair-wise manner.
+Examples are computing the minimum, maximum, sum, mean and variance.
+
+For the variance of the total variation, we store the partial mean, variance, and count as global observables.
+\todo{Use Q, TV macro here!}
+The vector $(-1, -1, 0)$ is then the base-case for the iteration (\funName{resetGlobalObservables}).
+The method \funName{mapGlobalObservables} is defined to return $\left( \operatorname{TV} \left[ f(\bm{Q}) \right], 0, 1 \right)$, where $f(\bm{Q})$ returns an arbitary indicator value per cell.
+Finally, \funName{reduceGlobalObservables} is implemented exactly as described in \cref{alg:merge-variance}.
+
+For the actual implementation we follow \cref{alg:reduce-gobs} but include nodal and intra-nodal parallelization in the following way:
+\begin{itemize}
+\item Add vectors \varName{\_globalObservables} and \varName{\_nextGlobalObservables} to all solvers.
+  The former stores the observables of the previous timestep, the latter the ones of the current timestep.
+  We can thus use the old observables for mesh refinement and compute a new reduction concurrently.
+  Before the first timestep, we reset both current and next observables.
+  At the beginning of each timestep, we overwrite the previous timestep data with the current data, and reset \varName{\_nextGlobalObservables} with \funName{resetGlobalObservables}.
+  This is done in the methods \funName{startNewTimeStep}, \funName{startNewTimeStepFused}, \funName{updateTimeStepSizesFused}, \funName{updateTimeStepSizes}.
+\item Reduce global observables in solver with method \funName{reduceGlobalObservables} that takes \varName{cellInfo} and \varName{solverNumber}.
+  The cell information stores pointers to the cell data for all solvers.
+  We implement this method for all solvers.
+  This has the advantage that we have a shared interface for all solver types.
+\item Reduce global observables per node in the mappings \className{FinaliseMashRefinement}, \className{FusedTimeStep}, \className{UpdateAndReduce}.
+  \begin{itemize}
+  \item We initialize the observables in the method \funName{beginIteration} with \funName{resetGlobalObservables}. 
+  \item We reduce the observables in \funName{leaveCell} by calling the solver method \funName{reduceGlobalObservables} with the \varName{cellInfo} of the current cell as argument.
+    For the mapping \className{UpdateAndReduce} this is done in the method \funName{enterCell} instead.
+  \item If we use \tbb{}, we merge the partially reduced observables in \funName{mergeWithWorkerThread} with \funName{reduceGlobalObservables} with two vectors as arguments.
+    This is not necessary for the mapping \className{FinaliseMeshRefinement}.
+   \item We update the global observables of the solver in the method \funName{endIteration}.
+  \end{itemize}
+\item If we use \mpi{}, we also need to reduce the observables over all ranks.
+  \exahype{} already reduces the timestep size, we extend these already existing \mpi{} messages to also include the global observables.
+  For this, we changed the following methods\todo{Next and current?!} of the \dg{}-solver:
+  \begin{itemize}
+  \item \funName{compileMessageForMaster} and \funName{sendDataToMaster} to send data from the workers to the master rank.
+  \item \funName{mergeWithWorkerData} to merge the received worker data with the current master data. 
+  \item \funName{compileMessageForWorker} and \funName{sendDateToWorker} to send the reduced data from the master to the workers.
+  \item \funName{mergeWithMasterData} to overwrite the current data of the workers with the reductions from the previous timestep.
+  \end{itemize}
+  This reduction is not supported for the limiting and finite volumes solver.\todo{Support for limiting?}
+  Together with the aforementioned resetting of the observables, this again corresponds to \cref{alg:reduce-gobs}.
+\end{itemize}
 

### 2018-12-30 writing/thesis/chapters/methods.tex
Add first draft of implementation chapter.
Replace density current with cosine bubble.

@@
 
-% Names of methods or so
-\newcommand{\muscl}{\textsc{muscl}-Hancock}
-\newcommand{\dg}{\textsc{dg}}
-\newcommand{\ader}{\textsc{ader}}
-\newcommand{\aderdg}{\textsc{ader-dg}}
-\newcommand{\amr}{\textsc{amr}}
-\newcommand{\pde}{\textsc{pde}}
-
 % Yet to be sorted
@@
 The coupling with the advection-diffusion-reaction equation follows~\cite{hidalgo2011ader} which describes this equation set for the one-dimensional case.
+In the following, we will denote the spatial coordinates as $\bm{x} = \left( x,z \right)$ and $\bm{x} = \left( x,y,z \right)$ for the two and three-dimensional case respectively.
+The variable $t$ corresponds to the currenty (physical) time.
 We solve the \pde\ in the conversative form \pcref{eq:conservation-law-gradient}\todo{Dont reference to following chapter!}
@@
 The chemical reactant in our case is unburnt gas.
+
 The rows of the equation are the conservation of mass, the conservation of momentum, the conservation of energy and the continuity of the reactant.
@@
 In this equation $\bm{a} \otimes \bm{b} = \bm{a} \bm{b}^\intercal$ is the Kronecker or outer product of two vectors $\bm{a}$ and $\bm{b}$.
-The pressure $\pressure$ is given by the caloric equation of state of an ideal reacting gas
+The pressure $\pressure$ is given by the caloric equation of state of an ideal reacting gas\todo{Geopot height correct?}
 \begin{equation}
   \label{eq:eos}
-  \pressure = (\gamma - 1) \left(\QE - \frac{1}{2} \left(\Qv \cdot \Qj \right)  - q_0 \QZ \right).
+  \pressure = (\gamma - 1) \left(\QE - \frac{1}{2} \left(\Qv \cdot \Qj \right)  - q_0 \QZ - gz \right).
 \end{equation}
-The term $q_0 \QZ$ is the chemical energy with the heat release $q_0$.
+The term $q_0 \QZ$ is the chemical energy with the heat release $q_0$, the term $gz$ is the geopotential height.
 The pressure is related to the temperature $T$ by the thermic ideal gas law
@@
 
+\sidetitle{Cauchy}
 For some scenarios we use Cauchy boundary conditions.
-In most cases, we would like to impose periodic boundary conditions, due to the inner workings of ExaHyPE this is not possible.
+In most cases, we would like to impose periodic boundary conditions, due to the inner workings of \exahype{} this is not possible.
 Instead we use the analytical solution of our problems at the boundary, imposing both value and gradients of the conservative variables.
@@
 
-As a physical boundary condition we limit ourselves to the no-slip boundary condition, where we assume that the fluid has a velocity of zero near the wall.
+As a physical boundary condition we limit ourselves to wall boundary condition
+
+\sidetitle{No-Slip}
+A standard wall boundary condition for viscous fluid is the no-slip condition, where we assume that the fluid has a velocity of zero near the wall.
 \todo{Check if this is the correct physical description!}
@@
 
+\sidetitle{Free-Slip}
+Similarly to the no-slip condition, we define the free-slip condition
+\begin{equation}
+  \label{eq:free-slip}
+  \Qj^o_d = \begin{cases}
+    -\Qj^i_d & d = \text{normal} \\
+    \Qj^i_d & \text{otherwise}
+    \end{cases}
+\end{equation}
+where only the velocity in normal direction is zero after the Riemann solver.
+The other variables are extrapolated in the same manner as in \cref{eq:no-slip}.
+
+We manually set the energy component of the numerical flux to zero for both no- and free-slip conditions.
 \section{The ADER-DG Method}\label{sec:ader-dg}
@@
 \section{Adaptive Mesh Refinement \textit{\&} Finite Volume Limiting}\label{sec:grid}
-Grid, spacefilling curve, and so on.
+\todo{Grid, spacefilling curve, and so on.}
+This section is concerned with two different but related concepts:%
+adaptive mesh refinement \amr{} and finite volume limiting.
+Both have in common that they change the structure of the grid.
+Instead of a regular grid where each cell has the same size, we now have different cell sizes.
 
 \subsection{Adaptive Mesh Refinement}\label{sec:amr}
-We use adaptive mesh refinement (\textsc{amr}).
+The goal of \amr{} is increasing the computational efficiency by using a higher spatial resolution in areas of interest.
+A simple example for this would be using finer mesh cells for the simulation of a wave, while using a low resolution for areas where the wave does not pass through.
+Of course, the difficult part is defining areas of interest.
+We use a global, gradient based refinement strategy.
+We first describe the computation of our indicator variable and then describe a simple way how one can detect outliers.
 
 Let $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ be a function that maps the discrete solution of a cell to an arbitrary indicator variable.
-Furthermore, we assume that $\bm{f}$ is expanded in the space-basis as in \cref{eq:cell-approx-space}.
-Then the total variation (\textsc{tv}) of this function is defined by
+Furthermore, we assume that $\bm{f}$ is expanded in the space-basis \pcref{eq:cell-approx-space}.
+Then the total variation (\textsc{tv}) of this function is defined by\todo{Cite sth for this?}
 \newcommand{\tv}{\operatorname{TV}}
@@
   \tv \left[ f(\bm{x}] \right] =
-\left(\intdcell{ \vert \gradient{f \left( \bm{x} \right)} \vert } \right).
+\int_{\domain} \vert \gradient{f \left( \bm{x} \right)} \vert.
 \end{equation}
 This integral can be evaluated efficiently on the reference cell \pcref{eq:space-mapping,eq:cell-approx-space} with Gaussian quadrature \pcref{eq:quadrature}.
+In the following, we divide this total variation by the volume of each cell, i.e.\ we use the volume of the corresponding reference cells as criterion.
 
@@
 \newcommand{\gobsCount}{n}
-We want to compute the mean and the variance over all grid cells by performing only pairwise merge operations.
-This allows us to minimize communication over nodes and allows for a simple implementation.
-The simplest way to compute this would be by using the textbook definitions of mean and variance of a random variable $X$
+A simple way of determining outliers is by how many standard deviations it differs from the mean value.
+We thus want to compute the mean and variance over all grid cells.
+To minimize intranodal communications and to simplify the implementation, we do this by performing only pairwise merge operations.
+The simplest way to compute this would be by using the textbook definitions of mean $\mean$ and variance $\variance$ of a random variable $X$
 \newcommand{\expectation}{\mathbb{E}}
@@
   \begin{split}
-    \mu [X] &= \expectation \left[ X \right]\\
+    \mean [X] &= \expectation \left[ X \right]\\
     \variance [X] &= \expectation \left[ X^2 \right] - \expectation \left[ X \right]^2.
@@
 \end{align}
-The reduction for the variance is numerically unstable when the variance is orders of magnitudes smaller than the mean as this can lead to catastrophic cancellations.
+The naive algorithm is numerically unstable when the variance is orders of magnitudes smaller than the mean as this can lead to catastrophic cancellations.
 We thus compute the mean and variance with the parallel algorithm of~\cite{chan1982updating}.
@@
 We collect these items in the vector $\gobs = (\mean, \variance, \gobsCount)$
-We can then merge two pairs of observed variables (\cref{alg:merge-variance}).
+We can then merge two pairs of observed variables with \cref{alg:merge-variance}.
+This algorithm computes an estimate of the population variance using Bessel's correction, i.e.\ it returns the sample variance times $\nicefrac{n}{n-1}$.
+In our case, the compute the variance over all grid cells.
+Because of this, we multiply the estimate of \cref{alg:merge-variance} with $\nicefrac{n-1}{n}$ to undo the correction.
 
@@
 In this equation, the constants $T_r$ and $T_d$ can be used to tailor the trade-off between the quality of approximation and computational cost.
-They can be chosen freely, as long $T_d < T_r$ holds.
+They can be chosen freely, as long as $T_d < T_r$ holds.
 Chebychev's inequality then guarantees that only a subset is marked for refinement.
-Note that even though this inequality provides only a loose bound.
+Note that this inequality provides only a loose bound.
 If one would be willing to assume a distribution of the indicator variable, tighter bounds can be derived.
@@
 Even worse, in the case of non-linear fluxes, discontinuities can appear even from smooth initial data.
+In addition, oscillations stemming from the high-order polynomical approximation can lead to wrong or unphyiscal data.
+This is called the Gibbs phenomenon.
 A classical way of dealing with this problem is the usage of so called limiters.
-The idea is to smooth out steep gradients and thus eliminate discontinuities.\todo{It doesnt work like this exactly..}
+The idea is to smooth out steep gradients and thus eliminate discontinuities.\todo{It doesnt work like this exactly. Cite DG book}
 
@@
 In our case we use the \muscl{}-method (\cref{sec:muscl}).
-The recomputation starts by subdividing the infringing cell into $N_2 = 2N + 1$ subcells.
+The recomputation starts by subdividing the infringing cell into $N_s = 2N + 1$ subcells\todo{Show picture!}.
 This number of subcells has the advantage that we do not loose spatial resolution.
-We can see this easily by noticing the similar form of \cref{eq:cfl-aderdg} and \cref{eq:cfl-muscl}.
+Similarly, we can use the same timestep size for both cell types.
+The reason for this is that the \textsc{cfl}-conditions for both schemes \pcref{eq:cfl-aderdg,eq:cfl-muscl} coincide for our choice of $N_s$.
 

### 2018-12-30 writing/thesis/chapters/scenarios.tex
Fix dimensions for CJ detonation wave scenario.
Replace density current with cosine bubble.

@@
 We investigate the radialsymmetric CJ detonation wave scenario from~\cite{helzel2000modified}.
-This scenario for the reactive Euler-equations is set up in a 2D box of size $[-0.5, 0.5] \times [-0.5, 0.5]$.
+This scenario for the reactive Euler-equations is set up in a 2D box of size $[-1, 1] \times [-1, 1]$ surrounded by free-slip walls~\pcref{eq:free-slip}.
 Inside a circle of radius $0.3$ we have totally unburnt gas, outside of this circle we have burned gas.
@@
 \end{align}
+\todo{What about viscous effects?}
 
@@
 \end{align}
-where we use the reference pressure $p_0$ as the pressure on ground level.
+where we use the reference pressure $p_0$ as the pressure on ground level\todo{Refer to hydrostatic balance eq.\ in methods chapter!\cref{eq:hydrostatic-balance}}.
 This \textsc{ode} can be now simply solved by separation of variables.
@@
 
-\subsection{Density current}
-A similar scenario is the density current~\cite{straka1993numerical} by \citeauthor{straka1993numerical}.
-In this scenario we only have one cold bubble.
+\subsection{Cosine Bubble}
+A similar scenario is the cosine bubble as described in~\cite{giraldo2008study}.
+In this scenario the flow is driven by one warm bubble.
 We use the same procedure as before to compute the initial conditions, again with $\backgroundPotT = 300$ but with a pertubation of the form
@@
     \end{cases}
-\intertext{with}        
-        r^2 &=  \left( \frac{x - x_c}{x_r} \right)^2 + \left( \frac{z -z_c}{z_r} \right)^2
-\end{align}
-and constants
+\end{align},
+where $r$ again is the radius to the center~\pcref{eq:radius} and constants
 \begin{equation}\label{eq:density-bubble}
-  A = -15 \quad a = \SI{1}{\m} \quad x_r = \SI{4000}{\m} \quad z_r = \SI{2000}{\m} \quad x_c = \SI{0}{\m} \quad z_c = \SI{3000}{\m}.
+  A = 0.5 \quad a = \SI{250}{\m} \quad x_c = \SI{500}{\m} \quad z_c = \SI{350}{\m}.
 \end{equation}
-Similar to~\cite{giraldo2008study} we use a constant viscosity of $\mu = 75$.
+Similar to the previous scenario, we use a constant viscosity of $\mu = 0.1$\todo{Are we? Check~\cite{giraldo2008study}!}.
 

### 2018-12-30 writing/thesis/chapters/results.tex
Update convergence.

@@
 1 & 2.03 & 2.00 & 1.92\\
-2 & 2.56 & 2.55 & 2.56\\
-3 & 3.44 & 3.41 & 3.42\\
-4 & 4.27 & 4.27 & 4.33\\
-5 & 5.36 & 5.32 & 5.26\\
-6 & 5.38 & 5.35 & 5.17\\
+2 & 2.56 & 2.55 & 2.55\\
+3 & 3.43 & 3.40 & 3.44\\
+4 & 4.44 & 4.44 & 4.67\\
+5 & 5.37 & 5.34 & 5.28\\
+6 & 5.43 & 5.42 & 5.30\\
 \bottomrule
@@
 \end{table}
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics{thesis_convergence}
+  \caption{$L_2$-Error vs.\ Grid Size}
+  \label{fig:convergence-l2-error}
+\end{figure}
+
 \newcommand{\error}{\operatorname{Total-Error}}
@@
 \section{AMR Efficiency}
+To show the effectiveness of the \amr{}, we compare the time to solution of a simulation using \amr{} and another simulation with a fully refined mesh.
+In detail, we compare
+\begin{description}
+\item[AMR] We use a coarse mesh with just $9 \times 9$ cells.
+  Each cell can be refined up to three times.
+  That is, the cells have sidelengths of roughly $\left( \SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.35}{\m} \right)$.
+  As refinement thresholds we use $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$ in \cref{eq:refinement-criterion}.
+\item[Fine] We use a uniform grid where all cells have a sidelength corresponding to the finest mesh of the \amr{}-test case.
+  In addition, we disable the reduction of global observables.
+\end{description}
+We use an \aderdg{}-method of order $4$ and thus have a minimal effective resolution of ca.\ $\SI{3.09}{\m}$.
+
+To ensure a fair comparison, we ran both configurations with the same optimisation option.
+
+We use a single node of the Haswell-nodes of the Supermuc (Phase 2).
+The node has two xxx \textsc{cpu}s with 28 cores each.
+We use the \tbb{} parallelisation of \exahype{}.
+To find a reasonable parameter for the number of background threads, we ran a grid search.
+We ran three \arm{} testcases for a simulation time of $\SI{1}{\min}$.
+The best median performance was achieved by only using two background threads!
+
 \section{Reactive Euler \textit{\&} Navier Stokes}

### 2018-12-30 writing/thesis/chapters/methods.tex
Describe splitting of pressure and density.

@@
 \begin{equation}
+ \label{eq:equation-set} 
  \begin{array}{l}
@@
 where $g = 9.81$ and $\bm{k}$ is a unit vector pointing in $z$-direction.
+
+\newcommand{\backgroundPressure}{\overline{\pressure}}
+\newcommand{\backgroundRho}{\overline{\Qrho}}
+Some of our scenarios can be described as a pertubation of a background state that is in hydrostatic balance
+\begin{equation}
+  \label{eq:hydrostatic-balance}
+  \pdv{}{z} \backgroundPressure{\left (z \right )} = -g \backgroundRho(z),
+\end{equation}
+where $\backgroundPressure$ and $\backgroundRho$ is the background pressure and density.
+We now focus on the following part of the momentum equation (neglecting viscous effects) of \cref{eq:equation-set}
+\begin{equation}
+  \label{eq:momentum-equation}
+  \pdv{\Qj}{t}+ \divergence{
+    \Qv \cdot \left( \bm{I} \QE + \bm{I} \pressure \right)
+  }
+  =
+  -g \bm{k} \cdot \Qrho
+\end{equation}.
+The background state \cref{eq:hydrostatic-balance} leads to large values and can diminish other parts of the flux due to numerical instabilities~\cite{muller2010adaptive}.
+We can now split the pressure as $\pressure = \backgroundPressure(z) + \pressure' (\bm{x}, t)$ and the density as $\Qrho = \backgroundRho(z) + \Qrho'(\bm{x}, t)$.
+Inserting this splitting, the definition of divergence into \cref{eq:momentum-equation} allows us to apply \cref{eq:hydrostatic-balance}.
+Furthermore, the background states have zero derivatives in all directions but in $z$.
+We arrive at 
+\begin{equation}
+  \label{eq:momentum-equation}
+  \pdv{\Qj}{t}+ \divergence \left(
+    \Qv \cdot \left( \bm{I} \QE + \bm{I} \pressure' \right)
+   \right)
+  =
+  -g \bm{k} \Qrho'.
+\end{equation}.
+We thus cancel parts of the flux with parts of the source term.
+Note that the time derivative of the background density also vanishes.
+We do not use this to simplify the implementation of the gradient computation.
+This form of the equation is similar to equation set 3 of~\cite{giraldo2008study} but without splitting the energy.
 

### 2019-01-02 writing/thesis/chapters/methods.tex
Add second optional argument to basis macros.
Advance theory chapter.

@@
 \newcommand{\broken}{\domain}
-\newcommand{\cell}[1][i]{C_{#1}}
+\newcommand{\cell}[1][]{C_{#1}}
 \newcommand{\boundary}{\partial \domain}
-\newcommand{\sbasis}[1][]{\Phi_{#1}}
-\newcommand{\stbasis}[1][]{\Theta_{#1}}
-\newcommand{\sbasisRef}[1][]{\hat{\sbasis[#1]}}
-\newcommand{\stbasisRef}[1][]{\hat{\stbasis[#1]}}
-\newcommand{\stestfunction}[1]{\sbasis[#1]}
-\newcommand{\sttestfunction}[1]{\stbasis[#1]}
+\NewDocumentCommand{\sbasis}{ O{} O{} }{\phi^{#1}_{#2}}
+\NewDocumentCommand{\stbasis}{ O{} O{} }{ \Theta^{#1}_{#2}}
+\NewDocumentCommand{\sbasisRef}{ O{} O{} }{\hat{\sbasis[#1][#2]}}
+\NewDocumentCommand{\stbasisRef}{ O{} O{} }{\hat{\stbasis[#1][#2]}}
+%\newcommand{\stestfunction}[1]{\sbasis[#1]}
+\NewDocumentCommand{\stestfunction}{ O{} O{} }{\sbasis[#1][#2]}
+\NewDocumentCommand{\sttestfunction}{ O{} O{} }{\stbasis[#1][#2]}
 \newcommand{\normal}{\bm{n}}
@@
 This chapter describes the numerical and physical background that is needed to simulate reacting fluids with good accuracy.
+We start with a description 
 We start with a description of the arbitrary high order derivatives (\ader) discontinuous Galerkin (\dg) method with a focus on equations that contain both advective and diffusive terms.
 We then seque into a short description of the \muscl\ scheme, a second order finite volume scheme.
-This discussion of the discretization enables us to talk about the equation set in sufficient detail.
 
@@
 where $\sbasisRef$ denotes the basis function on the reference cell.
-Similar we define a basis for a space-time element defined by $(0, 1)^D \times (t^n, t^{n+1})$
+Similarly, we define a basis for a space-time element defined by $(0, 1)^D \times (t^n, t^{n+1})$
 \begin{align}\label{eq:space-time-basis}
@@
   \label{eq:cell-approx-space-time}
-  q(\bm{x}, t^n)_{|\cell[i]} = \hat{u}^n_{i,l} \stbasis{l}(\bm{x}, t).
+  q(\bm{x}, t^n)_{|\cell[i]} = \hat{u}^n_{i,l} \stbasis[][l](\bm{x}, t).
 \end{equation}
@@
 Here we do not use the Riemann solver for the flux boundary term but rather use the discrete solution at time $t$.
-Note that this neglects the interaction with neighbouring cells, we account for this in the corrector step.
-\todo{Replace $\bm{x}$ with a macro some other letter. Is also coordinate!}
+This corresponds to upwinding in time~\cite{dumbser2008unified}.
+Note that this neglects the interaction with neighbouring cells.
+We account for this in the corrector step.
 \begin{align}\label{eq:space-time-predictor}
@@
 }}
--
+= \\
 \intdcell{
   \sttestfunction{k}(\bm{x},t^n) \dsol(\bm{x}, t^n)
-} = \\
+}
+&+
 \intdt{\intdcell{
@@
 }}
-&+
++
 \intdt{\intdcell{
@@
   \label{eq:predictor-matrices}
-  \pleft &= \ldots \\
-  \prightsol &= \ldots \\
-  \prightpred &= \ldots
+  \pleft^{\cell}_{(n v l), (n' v' l')} &=
+\intdcell{
+  \sttestfunction[\cell][v,l,n](1) \stbasis[\cell][v,l', n']
+}
+-
+\intdt{\intdcell{
+  \left( \pdv{}{t} \sttestfunction[\cell][v,l,n] (t) \right) \stbasis[\cell][v,l',n']
+}}                             
+\\
+\prightsol^{\cell}_{v, l,n} &=
+\intdcell{
+  \sttestfunction[\cell][v,l,n] (0) \sbasis[\cell][v,n'] \dsol[v,n']^{\cell}
+}
++
+\intdt{\intdcell{
+  \sttestfunction[\cell][v,l,n] \stbasis[\cell][v,l',n'](t) S_{v,l',n'}(\stpredictor[]^{\cell, i})
+}}                             
+  \\
+\prightpred^{\cell}_{v,l,n} &= 
+F^{k}_{v,l',n'}
+\intdt{\intdcell{
+  \left( \gradient{\sttestfunction[\cell][v,l,n]} \right) \stbasis[\cell][v,l',n'](t) S_{v,l',n'}(\stpredictor[]^{\cell, i})
+}}
 \end{align}
@@
   \label{eq:predictor-iterative}
-  \pleft \stpredictor &= \prightsol (\dsol) - \prightpred(\stpredictor) \\
- \stpredictor &= \pleft^{-1} \left( \prightsol (\dsol) - \prightpred(\stpredictor) \right).
+  \pleft \stpredictor[]^{\cell, i+1} &= \prightsol (\dsol) - \prightpred(\stpredictor[]^{\cell, i}) \\
+ \stpredictor[]^{\cell, i+1} &= \pleft^{-1} \left( \prightsol (\dsol) - \prightpred(\stpredictor[]^{\cell, i}) \right).
 \end{align}
@@
 
+\sidetitle{Preparing for corrector}
 We then prepare the space-time-predictor for use in the corrector step.
 Due to the linearity of the Riemann solver, we can exchange time and space integration and thus only need to consider the Riemann problem for time-averaged quantities.
-We can compute this for the space-time-predictor by
-\begin{align}
-  \ldots = \ldots,
-\end{align}
-the procedure is similar for all other quantities (Q, gradQ, fluxes).
-
-Finally, we extrapolate all quantities to the boundary.
+% We can compute this for the space-time-predictor by
+% \begin{align}
+%   \ldots = \ldots,
+% \end{align}
+% the procedure is similar for all other quantities (Q, gradQ, fluxes).
+We then extrapolate all quantities to the boundary.
 This is needed for the Riemann solver and for the reconstruction of boundary values.
-We achieve this by
-\begin{align}
-  \label{eq:boundary-extrapolation}
-  \ldots = \ldots.
-\end{align}
-
-\sidetitle{Boundary extrapolation and stuff}
-\todo{Explain that stpredictor and fluxes are saved and extrapolated to boundary.
-This is important because we extrapolate the gradient as well!}
-Extrapolate unknowns to boundary, convert from our basis to basis on faces and so on
+We accomplish this by evaluating the function at the degrees of freedom on the boundary.
+Thanks to the interpolating property of the nodal basis~\pcref{eq:basis-interpolating}, this reduces to a change of basis which can be precomputed on the reference element.
+We compute time-averaged and boundary extrapolated versions of the space-time-predictor, the degrees of freedom and their gradient, and the fluxes.
 
 \sidetitle{Corrector}
-First, we multiply the system \cref{eq:conservation-law-gradient} by a test function $\stestfunction{i}$ and integrate over the space-time volume $(\cell \times [t^n, t^{n+1}])$.
-Note that the testfunctions
+The final step of the \aderdg{}-scheme is the corrector.
+For this step, we write the approximation of a function $q$ in a cell as
 \begin{equation}
   \label{eq:cell-approx-space}
-  q(\bm{x})_{|\cell[i]} = \hat{u}^n_{i,l} \sbasis{l}(\bm{x}).
-\end{equation}
-
-here do not depend on time but only on the spatial dimensions.
+  q(\bm{x})_{|\cell[i]} = \hat{u}^n_{i,l} \sbasis{l}(\bm{x}),
+\end{equation}
+where the basis, unlike in \cref{eq:cell-approx-time}, does not depend on the time.
+We then multiply the system \cref{eq:conservation-law-gradient} by a test function $\stestfunction{i}$ and integrate over the space-time volume $(\cell \times [t^n, t^{n+1}])$.
 We arrive yet again at the weak formulation of the \pde\
@@
 \newcommand{\massMatrixDef}{\intdcell{
-  \stestfunction{k} \sbasis[l]
+  \stestfunction[\cell][k] \sbasis[\cell][l]
 }}
@@
 &+
-\left(\intdt{\intdcell{
-      \stestfunction{k} \Riemann(\stpredictor^-, \stpredictor^+) \cdot \normal
+\left(\intdt{\intdcellb{
+      \stestfunction[k] \Riemann(\stpredictor^-, \stpredictor^+) \cdot \normal
 }}\right)
@@
 \left(\intdt{\intdcell{
-    \gradient{\stestfunction{k}} \cdot  \flux(\stpredictor, \gradient{\stpredictor}) % todo correct gradient?
+    \gradient{\stestfunction[k]} \cdot  \flux(\stpredictor, \gradient{\stpredictor}) % todo correct gradient?
 }}\right)
@@
 \left(\intdt{\intdcell{
-      \stestfunction{k} \source(\stpredictor)
+      \stestfunction[k] \source(\stpredictor)
 }}\right)
@@
 \end{equation}
-which is diagonal thanks to the orthogonal basis \pcref{eq:basis-orthogonality} and thus trivial to invert.
-\newcommand{\sumbasis}{\sum_i^{(N + 1)^d - 1}}
+which is, due to the orthogonal basis \pcref{eq:basis-orthogonality}, diagonal and thus trivial to invert.
+\newcommand{\basisSize}{(N+1)^d - 1}
+\newcommand{\sumbasis}{\sum_i^{\basisSize}}
 We can then insert the definition of our basis function into our equation and arrive at
@@
 \begin{split}
-  a &= \sumbasis F_n \intdcell{
-\sbasis[n] \gradient{\sbasis[n]}
-  } \\
+a^{\cell}_{v,n} &= F^{\cell}_{n'} \intdt{\intdcell{
+  \sbasis[\cell][v,n'] \gradient{\sbasis[\cell][v,n]}(t)
+}}
+\\
 b &= \ldots \\
-  s_n &= \sumbasis \intdcell{
-s \sbasis[n]
-  }.
-\end{split}
-\end{align}
+s^{\cell}_n &=
+\intdcell{
+  S^{\cell}_v \sbasis[\cell][v,n]
+}
+,
+\end{split}
+\end{align}
+where we evaluated the time-integrals by using the fact that our quantities are time-averaged.
 We can solve this for the new unknows $\bm{u}^{n+1}$
@@
 \end{equation}
+Note that we do not need to consider neighboring cells for this step.
 
@@
       \evolvedCellAvg[i,j+1]{-y}, \gradCellAvg[i,j+1]
-    \right)    
+    \right).
   \end{split}
@@
 In our case, the compute the variance over all grid cells.
-Because of this, we multiply the estimate of \cref{alg:merge-variance} with $\nicefrac{n-1}{n}$ to undo the correction.
+\todo{Std is still slightly biased!}
+Because of this, we multiply the estimate of \cref{alg:merge-variance} with $\nicefrac{n-1}{n}$ to undo the correction.\todo{Is this actually correct?
+Doesn't bessel's correction come from the dofs ``used for the mean?''.
+(Doesnt really matter anyway.)}
 
@@
 \end{algorithm}
-\todo{Cite Chebychev, add concrete form of threshold.}
 Chebychev's inequality
@@
 with probability $\mathbb{P}$,
-holds for an arbitrary distribution with mean $\mu$ and standard deviation $\sigma$ probability $\mathbb{P}$.
+holds for an arbitrary distribution with mean $\mu$ and standard deviation $\sigma$ probability $\mathbb{P}$~\cite{wasserman2004all}.
 This motivates the following refinement criterion
@@
   \begin{cases}
-    \text{refine} & \text{if } \tv(\Q) \geq \mu + T_r \sigma \\
-    \text{delete} & \text{if } \tv(\Q) \leq \mu + T_r \sigma \\
+    \text{refine} & \text{if } \tv(\Q) \geq \mu + T_\text{refine} \sigma \\
+    \text{delete} & \text{if } \tv(\Q) \leq \mu + T_\text{delete} \sigma \\
     \text{keep} & \text{otherwise}
@@
 In addition, oscillations stemming from the high-order polynomical approximation can lead to wrong or unphyiscal data.
-This is called the Gibbs phenomenon.
+This is called Gibbs phenomenon.
 A classical way of dealing with this problem is the usage of so called limiters.
-The idea is to smooth out steep gradients and thus eliminate discontinuities.\todo{It doesnt work like this exactly. Cite DG book}
+The idea is to smooth out steep gradients and thus eliminate discontinuities~\cite{hesthaven2008nodal}.\todo{It doesnt work like this exactly.}
 
@@
 In our case we use the \muscl{}-method (\cref{sec:muscl}).
-The recomputation starts by subdividing the infringing cell into $N_s = 2N + 1$ subcells\todo{Show picture!}.
+The recomputation starts by subdividing the infringing cell into $N_s = 2N + 1$ subcells.
 This number of subcells has the advantage that we do not loose spatial resolution.
@@
 
+\begin{figure}[htb]
+  \centering
+  \includegraphics[scale=0.7]{thesis_aderdg_subcell_grid}
+  \caption{\label{fig:limiting-subcells}Conversion from \dg{}-dofs to fv-dofs. Image taken from~\cite{dumbser2018conformal}. }
+\end{figure}
+\todo{Cite source for subcells~\pcref{fig:limiting-subcells}. See guidebook. NOTE THAT IT IS MODIFIED. Also: Fix size, currently font is too small}
 For the sake of brevity, we omit technical details.

### 2019-01-02 writing/thesis/chapters/results.tex
Add some plans for further results.

@@
 \section{Accurate CFD}
+Show:
+\begin{itemize}
+\item Taylor-Green High Order
+\item ABC Medium Order
+\end{itemize}
 \section{Accurate Clouds}
-\section{AMR Efficiency}
+\begin{itemize}
+\item Cosine Bubble
+\item Two Bubbles
+\end{itemize}
+\section{Time-to-solution: AMR vs Static Mesh}
 To show the effectiveness of the \amr{}, we compare the time to solution of a simulation using \amr{} and another simulation with a fully refined mesh.
@@
 We use a single node of the Haswell-nodes of the Supermuc (Phase 2).
-The node has two xxx \textsc{cpu}s with 28 cores each.
+The node has two xxx\todo{name cpus} \textsc{cpu}s with 28 cores each.
+Both \textsc{cpu}s currently run on \SI{1.8}{\GHz}
 We use the \tbb{} parallelisation of \exahype{}.
 To find a reasonable parameter for the number of background threads, we ran a grid search.
-We ran three \arm{} testcases for a simulation time of $\SI{1}{\min}$.
-The best median performance was achieved by only using two background threads!
+We ran three \amr{} testcases for a simulation time of \SI{1}{\min}.
+\todo{Noisy, show results}
+The best median performance was achieved by using seven background threads.
 
 \section{Reactive Euler \textit{\&} Navier Stokes}
-
+\begin{itemize}
+\item With viscous effects
+\item Without viscous effects  
+\end{itemize}
 %%% Local Variables:

### 2019-01-03 writing/thesis/chapters/methods.tex
Add unbiased estimate of variance and citation for sample std bias.

@@
     \mean [X] &= \expectation \left[ X \right]\\
-    \variance [X] &= \expectation \left[ X^2 \right] - \expectation \left[ X \right]^2.
-  \end{split}
-\end{align}
+    \variance [X] &= \frac{n}{n-1} \expectation \left[ X^2 \right] - \expectation \left[ X \right]^2.
+  \end{split}
+\end{align}
+\todo{Bessel's correction here!}
+The variance is corrected for bias by the so-called Bessel's correction~\cite{holtzman1950unbiased}.
 The naive algorithm is numerically unstable when the variance is orders of magnitudes smaller than the mean as this can lead to catastrophic cancellations.
@@
 In our case, the compute the variance over all grid cells.
-\todo{Std is still slightly biased!}
-Because of this, we multiply the estimate of \cref{alg:merge-variance} with $\nicefrac{n-1}{n}$ to undo the correction.\todo{Is this actually correct?
-Doesn't bessel's correction come from the dofs ``used for the mean?''.
-(Doesnt really matter anyway.)}
-
+We then use
+\begin{equation}
+  \label{eq:sample-std}
+ \sigma = \sqrt{\variance[X]} 
+\end{equation}
+as sample standard deviaton.
+Note, that this estimate is biased; an unbiased estimate for general distributions does not exist~\cite{holtzman1950unbiased}.
+\todo{Do we actually care about the bias?}
 \begin{algorithm}[ht]

### 2019-01-05 writing/thesis/chapters/implementation.tex
Move macros to settings.
Second draft of implementation chapter.

@@
-\newcommand{\softwareName}[1]{\textit{#1}}
-\newcommand{\exahype}{\softwareName{ExaHyPE}}
-\newcommand{\peano}{\softwareName{Peano}}
-\newcommand{\className}[1]{\texttt{#1}}
-\newcommand{\funName}[1]{\textsf{#1}}
-\newcommand{\fileName}[1]{\textbf{#1}}
-\newcommand{\varName}[1]{\enquote{#1}}
-
-\newcommand{\cpp}{C\texttt{++}}
-\newcommand{\tbb}{\textsc{tbb}}
-\newcommand{\mpi}{\textsc{mpi}}
-
 \chapter{Implementation}\label{chap:implementation}
@@
 \exahype{} implements an \aderdg{} solver with \muscl{} limiting and \textsc{amr}, as described in \cref{chap:methods}.
-It uses \softwareName{Intel® Threading Building Blocks} (\tbb{}) for node-level parallelism and the \softwareName{Message Passing Interface} (\mpi{}) for intra-node parallelism. 
+It uses \softwareName{Intel® Threading Building Blocks} (\tbb{}) for shared memory parallelism and the \softwareName{Message Passing Interface} (\mpi{}) for distributed memory parallelism. 
 In the following we define a \enquote{user} as someone who implements the logic of a \pde{} but does not change the implementation of \exahype{} itself.
 This is in contrast with a \enquote{developer} whose scope is the entirety of the source code.
-The goal of our implementation is that all new features should be accesible to users, not only developers.
+The goal of our implementation is that all new features should be accesible to users as well.
 
@@
     The solver types all have a shared superclass \className{Solver} which describes a common interface.
-  \item A class that inherits from the aforementioned abstract class that needs to be used to implement the program logic.
+  \item A class that inherits from the aforementioned abstract class that implements the \pde{} logic.
   \end{itemize}
 
-\item The user then needs to modify the generated glue code.
+\item The user then needs to modify the generated \className{Solver} class.
   The \pde{} is specified in the methods \funName{flux} and \funName{eigenvalues}.
-  We describe the grid refinement criterion in \funName{refinementCriterion} and the limiting criterion in \funName{isPhysicallyAdmissible}
+  We implement the grid refinement criterion in \funName{refinementCriterion} and the limiting criterion in \funName{isPhysicallyAdmissible}.
   To close the system, the user needs to prescribe initial and boundary conditions with \funName{adjustPointSolution}, \funName{boundaryConditions} and \funName{boundaryValues}.
@@
 \begin{itemize}
-\item A runner iterates through the grid and calls an adapter for so-called events.
-  An example for an event is entering a cell, for example.
+\item A runner iterates over the grid and calls an adapter for so-called events.
+  An example for an event is entering a cell.
 \item An adapter calls one or multiple mappings.
@@
   These implementation can differ between different solvers.
+\item The actual numerical logic is outsourced to kernels.
 \end{itemize}
-Furthermore, the degrees of freedom and some meta-information are stored each cell in a heap data-structure.
-The information for each cell is defined in the file \fileName{ADERDGCellDescrition.def} for the \dg{}-solver.
+Furthermore, the degrees of freedom and some meta-information are stored for each cell in a heap data-structure.
+The information for each \dg{}-cell is defined in the file \fileName{ADERDGCellDescrition.def}.
 Similar files exists for the finite volume solver but are not relevant for us.
@@
 \section{Implementing numerics}
-We needed to modify the existing implementation of the numerics to be able to solve problems with diffusive fluxes.
+We needed to modify the existing implementation of the mappings, solvers and kernels to be able to solve problems with diffusive fluxes.
 These changes are:
@@
   \begin{itemize}
-  \item In the function \funName{aderPicardLoopNonlinear} we pass the gradient of the conserved variables to the \funName{flux} method.
-    We also return the time-average of the gradient.
-   \item In the function \funName{aderExtrapolatorNonlinear} we also compute the extrapolated gradient.
+  \item The function \funName{aderPicardLoopNonlinear} implements the space-time-predictor loop \pcref{eq:predictor-iterative}.
+    We pass the gradient of the conserved variables to the \funName{flux} method of the \className{Solver}.
+    Because we need the time-average of the gradient later, we return it.
+   \item In the function \funName{aderExtrapolatorNonlinear}, which implements the boundary extrapolation, we also compute the extrapolated gradient.
     \item In the function \funName{spaceTimePredictorNonlinear} we also return the extrapolated gradient.
   \end{itemize}
-\item Storing the extrapolated gradient for each cell for use in the boundary conditions.
+\item Storing the extrapolated and time-averaged gradient for each cell for use in the boundary conditions and the corrector step.
 \item Using the gradient for the computation of the boundary conditions.
   They are defined in the file \fileName{boundaryConditions.cpph}.
-\item Adding the diffusive penalty terms for Riemann solver (\fileName{riemannSolverNonlinear.cpph}) and \textsc{cfl}-condition (\fileName{stableTimeStepSize.cpph}).
+\item Adding the diffusive penalty terms for the Riemann solver (\fileName{riemannSolverNonlinear.cpph}) and \textsc{cfl}-condition (\fileName{stableTimeStepSize.cpph}).
+  This corresponds to \cref{eq:rusanov-flux,eq:cfl-aderdg}.
 \item Computing the gradient for the \muscl{} scheme (\fileName{musclhancock.cpph}) and passing it to the flux (\fileName{rusanov.cpph}).
@@
 The implementation of the global observables is quite simple.
-
-We use three functions that need to be defined by the user and adher to the interface
+We use three functions that need to be defined by the user.
+They adhere to the interface:
 \begin{itemize}
+\item The function \funName{mapGlobalObservables} computes for a cell the observables from its degrees of freedoms and cell size.
+  It returns a vector of size $\ngobs$.
+\item The function \funName{reduceGlobalObservables} updates the current partially reduced vector of global observables \varName{reducedGlobalObservables} with another vector of partially reduced observables \varName{curGlobalObservables}.
 \item The function \funName{resetGlobalObservables} takes no arguments and returns a vector of size $\ngobs$.
-  This vector should be the identity of the reduction, i.e.\ a value $a$ with the property that $\operatorname{reduce}(a, b) = b$.
-  \todo{Is this right?}
-\item The function \funName{mapGlobalObservables} that takes the degrees of freedoms of a cell and its cell size and returns a vector of size $\ngobs$.
-  This vector should be the observables that correspond to the cell.
-\item The function \funName{reduceGlobalObservables} updates the current partially reduced vector of global observables \varName{reducedGlobalObservables} with another vector of partially reduced observables \varName{curGlobalObservables}.
+  This vector should be the identity of the reduction, i.e.\ a value $a$ with the property that for all $b$ $\funName{reduce}(a, b) = b$.
 \end{itemize}
@@
     \For{$\text{cell} \in \text{cells}$}
-    \Let{curObservables}{\Call{mapGlobalObservables}{$Q_\text{cell}, \Delta x_\text{cell}$}}
+    \Let{curObservables}{\Call{mapGlobalObservables}{$Q_\text{cell}, \Delta \bm{x}_\text{cell}$}}
     \Let{observables}{\Call{reduceGlobalObservables}{observables, curObservables}}
@@
 \end{algorithm}
-This results in a simple, yet powerful interface, which can be used to implement all reductions that can be done in a pair-wise manner.
+This results in a simple, yet powerful interface, which can be used to implement all reductions that can be performed in a pair-wise manner.
 Examples are computing the minimum, maximum, sum, mean and variance.
 
-For the variance of the total variation, we store the partial mean, variance, and count as global observables.
-\todo{Use Q, TV macro here!}
-The vector $(-1, -1, 0)$ is then the base-case for the iteration (\funName{resetGlobalObservables}).
+For the variance of the total variation, we store the partial mean, sample variance, and count as global observables.
+\todo{Use Q, TV macro here! Same for algorithm for cell.}
+The vector $(-1, -1, 0)$ is then the base-case for the iteration~\pcref{alg:reduce-gobs} and is thus returned by the function \funName{resetGlobalObservables}.
 The method \funName{mapGlobalObservables} is defined to return $\left( \operatorname{TV} \left[ f(\bm{Q}) \right], 0, 1 \right)$, where $f(\bm{Q})$ returns an arbitary indicator value per cell.
@@
 
-For the actual implementation we follow \cref{alg:reduce-gobs} but include nodal and intra-nodal parallelization in the following way:
+For the actual implementation, we follow \cref{alg:reduce-gobs} but include distributed and shared memory parallelization in the following way:
 \begin{itemize}
@@
   Before the first timestep, we reset both current and next observables.
-  At the beginning of each timestep, we overwrite the previous timestep data with the current data, and reset \varName{\_nextGlobalObservables} with \funName{resetGlobalObservables}.
+  At the beginning of each timestep, we overwrite the previous data with the current data, and reset \varName{\_nextGlobalObservables} with \funName{resetGlobalObservables}.
   This is done in the methods \funName{startNewTimeStep}, \funName{startNewTimeStepFused}, \funName{updateTimeStepSizesFused}, \funName{updateTimeStepSizes}.
-\item Reduce global observables in solver with method \funName{reduceGlobalObservables} that takes \varName{cellInfo} and \varName{solverNumber}.
+\item Reduce global observables in solver with method \funName{reduceGlobalObservables} that takes the \varName{cellInfo} and \varName{solverNumber}.
+  The solver number is always 0 because we only use one solver at a given time.
   The cell information stores pointers to the cell data for all solvers.
@@
   This has the advantage that we have a shared interface for all solver types.
-\item Reduce global observables per node in the mappings \className{FinaliseMashRefinement}, \className{FusedTimeStep}, \className{UpdateAndReduce}.
+\item Reduce global observables per node in the mappings \className{FinaliseMeshRefinement}, \className{FusedTimeStep}, \className{UpdateAndReduce}.
   \begin{itemize}
@@
     For the mapping \className{UpdateAndReduce} this is done in the method \funName{enterCell} instead.
-  \item If we use \tbb{}, we merge the partially reduced observables in \funName{mergeWithWorkerThread} with \funName{reduceGlobalObservables} with two vectors as arguments.
+  \item If we use \tbb{}, we merge the partially reduced observables in \funName{mergeWithWorkerThread} with \funName{reduceGlobalObservables} using the current reduced observables and the partially reduced observables from the worker.
     This is not necessary for the mapping \className{FinaliseMeshRefinement}.
-   \item We update the global observables of the solver in the method \funName{endIteration}.
+   \item We update the global observables of the solver in the method \funName{endIteration}, which call the method \funName{updateG}.
   \end{itemize}
 \item If we use \mpi{}, we also need to reduce the observables over all ranks.
-  \exahype{} already reduces the timestep size, we extend these already existing \mpi{} messages to also include the global observables.
+  \exahype{} already reduces the timestep size, we extend these already existing \mpi{} messages to also include the global observables \varName{_globalObservables}.
   For this, we changed the following methods\todo{Next and current?!} of the \dg{}-solver:
@@
   \end{itemize}
-  This reduction is not supported for the limiting and finite volumes solver.\todo{Support for limiting?}
+  The solvers update the variable \varName{_nextGlobalObservables} during the \mpi{}-reduction.
   Together with the aforementioned resetting of the observables, this again corresponds to \cref{alg:reduce-gobs}.
 \end{itemize}
+The global observables interface is defined for all solvers, the \mpi{}-reduction only for the \aderdg{}-solver.
 

### 2019-01-07 writing/thesis/chapters/implementation.tex
Escape underscores (fix compilation on travis).

@@
 \item If we use \mpi{}, we also need to reduce the observables over all ranks.
-  \exahype{} already reduces the timestep size, we extend these already existing \mpi{} messages to also include the global observables \varName{_globalObservables}.
+  \exahype{} already reduces the timestep size, we extend these already existing \mpi{} messages to also include the global observables \varName{\_globalObservables}.
   For this, we changed the following methods\todo{Next and current?!} of the \dg{}-solver:
@@
   \end{itemize}
-  The solvers update the variable \varName{_nextGlobalObservables} during the \mpi{}-reduction.
+  The solvers update the variable \varName{\_nextGlobalObservables} during the \mpi{}-reduction.
   Together with the aforementioned resetting of the observables, this again corresponds to \cref{alg:reduce-gobs}.

### 2019-01-07 writing/thesis/chapters/methods.tex
More work on methods chapter.

@@
 \NewDocumentCommand{\stbasis}{ O{} O{} }{ \Theta^{#1}_{#2}}
-\NewDocumentCommand{\sbasisRef}{ O{} O{} }{\hat{\sbasis[#1][#2]}}
-\NewDocumentCommand{\stbasisRef}{ O{} O{} }{\hat{\stbasis[#1][#2]}}
+\NewDocumentCommand{\sbasisRef}{ O{} O{} }{\hat{\phi}^{#1}_{#2}} %{\hat{\sbasis[#1][#2]}}
+\NewDocumentCommand{\stbasisRef}{ O{} O{} }{\hat{\Theta}^{#1}_{#2}} %{\hat{\stbasis[#1][#2]}}
 %\newcommand{\stestfunction}[1]{\sbasis[#1]}
@@
 \newcommand{\dsol}[1][h]{\bm{u}_{#1}}
-\newcommand{\stpredictor}[1][h]{\bm{q}_{#1}}
+\NewDocumentCommand{\stpredictor}{ O{} O{} }{\overline{\bm{q}}^{#1}_{#2}}
+\NewDocumentCommand{\spredictor}{ O{} O{} }{\bm{q}^{#1}_{#2}}
 
@@
 % Integrals
-\newcommand{\intdt}[1]{\int_{t^n}^{t^{n+1}} #1 \dd{t}}
+\newcommand{\curTime}{t^n}
+\newcommand{\nextTime}{t^{n+1}}
+\newcommand{\intdt}[1]{\int_{\curTime}^{\nextTime} #1 \dd{t}}
 \newcommand{\intdcell}[1]{\int_{\cell} #1 \dd{\bm{x}}}
@@
 \newcommand{\quadWeight}[1][i]{w_{#1}}
+\newcommand{\quadNode}[1][i]{n_{#1}}
+\newcommand{\sbasisSize}{(N+1)^\dimensions}
+\newcommand{\stbasisSize}{(N+1)^{\dimensions+1}}
 
@@
 \begin{equation}
-  \label{eq:momentum-equation}
+  \label{eq:momentum-equation-split}
   \pdv{\Qj}{t}+ \divergence \left(
@@
 \sidetitle{Cauchy}
-For some scenarios we use Cauchy boundary conditions.
+For some scenarios we use Cauchy boundary conditions, i.e.\ we prescribe both $\Q$ and $\gradQ$ at the boundary.
 In most cases, we would like to impose periodic boundary conditions, due to the inner workings of \exahype{} this is not possible.
@@
 \section{The ADER-DG Method}\label{sec:ader-dg}
+\newcommand{\NVar}{N^{\text{var}}}
+\newcommand{\dimensions}{d}
+\newcommand{\mapping}{\mathcal{M}}
+\newcommand{\volume}{V}
+\newcommand{\cellCenter}{\operatorname{cell-center}}
 We describe the arbitrary derivative discontinous Galerkin (\aderdg) method in this chapter.
 Our description of the main method follows~\cite{dumbser2008unified,dumbser2010arbitrary,dumbser2018efficient}, our notation follows primarily~\cite{dumbser2018efficient}.
+Let $\NVar$ be the number of variables and $\dimensions$ the number of spatial dimensions.
 We discuss the approximation of systems of partial differential equations (\pde) of the form
@@
 \end{equation}
-contain the gradient $\gradQ$ of the so called vector of conservative variables $\Q$~\cite{dumbser2010arbitrary}.
-There are therefore not hyperbolic but rather parabolic or elliptic.
-
-We discuss the solution of a hyperbolic conservation law \cref{eq:conservation-law} with domain $\domain$ and boundary $\boundary$.
-Let $\domain$ and $\boundary$ denote our two- or three-dimensional computational domain and its boundary.
+contain the gradient $\gradQ \in \mathbb{R}^{\NVar \times \dimensions}$ of the so called vector of conservative variables $\Q \in \mathbb{R}^{\NVar}$~\cite{dumbser2010arbitrary}.
+They are therefore not hyperbolic but rather parabolic or elliptic.
+
+We discuss the solution of a conservation law \cref{eq:conservation-law-gradient} with two or three dimensional domain $\domain$ and boundary $\boundary$.
 In our implementation of the discontinous Galerkin (\dg) framework, we approximate this solution in the space
@@
   \label{eq:dg-space}
-  \broken = \bigcup_i \cell
+  \broken = \bigcup_k \cell[k]
 \end{equation}
@@
 Note that we do not distinguish between the broken approximation space and the domain, the use should be clear given its surrounding context.
-In the following we make use of the Einstein summation convention where summation over repeated indexes is implied.
-
+For each cell we denote its center by $\cellCenter{\cell}$ and its size by $\Delta x, \Delta y$ and $\Delta z$.
+%In the following we make use of the Einstein summation convention where summation over repeated indexes is implied.
 % Inside each cell $\cell$ we represent the solution in terms of the basis function 
@@
 
-We now describe the derivation of the \textsc{ader-dg} method.
-This scheme is a predictor-corrector method.
+The \aderdg{}-scheme is a predictor-corrector method.
 We first compute a local time evolution of each cell in a predictor step and then add the influence of the neighbors in the corrector step.
-$\ldots$
-
 % \begin{algorithm}[H]
@@
 \sidetitle{Reference Cell}
-\newcommand{\mapping}{\mathcal{M}}
-\newcommand{\volume}{V}
 For reasons of computational efficiency, we describe the scheme in terms of a reference cell.
-We use the quad cell $\cell = [0, 1]^D$\todo{check if $[0,1]$ detontes correct interval}.
-The mapping, which takes a point on the reference cell with coordinates $\hat{\bm{x}}$ and returns a point $\bm{x}$ on a cell with center and widths $(\Delta x, \Delta y, \Delta z)$, is given by
+We use the quad cell $\hat{\cell} = [0, 1]^\dimensions$ as space reference cell.\todo{check if $[0,1]$ detontes correct interval}.
+The mapping, which takes a point on a grid cell with coordinates $\bm{x}$ and returns the corresponding point $\hat{\bm{x}}$ on the reference cell
 \begin{equation}\label{eq:space-mapping}
   \hat{x} = \mapping (\bm{x}) =
-  \operatorname{cell-center}(\cell) +
+  \cellCenter(\cell) +
 \begin{pmatrix}
@@
 \end{pmatrix}
- % \operatorname{diag}(\Delta x, \Delta y, \Delta z)
   \begin{pmatrix}
@@
 \end{equation}
-
 We also define the inverse mapping $\mapping^{-1}$.
-This can be used to define a function $f(\bm{x})$ acting on a point $\bm{x}$ of a regular cell in term of a function $\hat{f}(\bm{x})$ that acts on a point of the reference cell by considering
+This can be used to define a function $f(\bm{x})$ acting on a point $\bm{x}$ of a regular cell in terms of a function $\hat{f}(\bm{x})$ that acts on the corresponding point of the reference cell by the relation
 \begin{equation}
@@
 
-Similar to this, we define a mapping that maps a point in time to the reference time $\in (0,1)$
-\todo{Fix this/remove}
+Similar to this, we define a mapping that maps a point in time to the reference time $\hat{t} \in (0,1)$
 \newcommand{\timeMapping}{\mathcal{T}}
@@
 where $\Delta t$ is timestep of a cell and $t_0$ is the beginning of its time interval.
+The space-time reference cell is then $\hat{\cell} = [0,1]^{D+1}$
 
@@
 \sidetitle{Basis Functions}
-\newcommand{\lagrangeRef}[1][i]{\hat{L}_{#1}}
-\newcommand{\lagrange}[1][i]{L_{#1}}
+\newcommand{\lagrange}[1][i]{\varphi_{#1}}
+\newcommand{\lagrangeRef}[1][i]{\hat{\varphi}_{#1}}
 The next step is the definition of basis functions for the reference cell.
@@
 \end{equation}
-where we used the Einstein summation convention where summation over repeated indices is implied.
+where we used the Einstein summation convention where summation over repeated indices is implied\todo{Remove this sentence, or sentence before introducing einstein summation!}.
 The support points $x_i$ are chosen such that they coincide with the nodes of the Gauss-Legendre quadrature which we can use to evaluate integrals
@@
 where $x_n$ is a quadrature point with weight $\quadWeight[n]$.
-The basis functions are similarly defined in $d$ dimensions by considering nodes that are the tensor-products of $d$ one-dimensional Gauss-Legendre quadrature.
+
+The basis functions are similarly defined in $d$-dimensions by considering nodes that are the tensor-products of $d$ one-dimensional Gauss-Legendre quadrature.
 To simplify notation, we order the polynomials by a linearised index, a $d$-dimensional function is then approximated by
@@
   \label{eq:lagrange-expansion}
-  f(\bm{x}) = \sum_{i = 0}^{N^d} f(\bm{x}_i) \lagrangeRef[i](\bm{x}) = f(\bm{x}_i) \lagrangeRef[i](\bm{x}).
+  f(\bm{x}) = \sum_{i = 0}^{(N+1)^\dimensions - 1} f(\bm{x}_i) \lagrangeRef[i](\bm{x}) = f(\bm{x}_i) \lagrangeRef[i](\bm{x}).
 \end{equation}
@@
   \label{eq:quadrature}
-  \underbrace{\int_0^1 \cdots \int_0^1}_{D \text{ times}} f(\bm{x}) \dd{\bm{x}} &= \sum_n^{(N+1)^D - 1} \quadWeight[n] f(\bm{x}_n) \\
+  \underbrace{\int_0^1 \cdots \int_0^1}_{\dimensions \text{ times}} f(\bm{x}) \dd{\bm{x}} &= \sum_n^{(N+1)^D - 1} \quadWeight[n] f(\bm{x}_n) \\
   \intertext{with}
@@
     \label{eq:basis-interpolating}
-&& \text{Interpolating:} \qquad & \lagrangeRef[i] (x_j) &= \delta_{ij}\\
+&& \text{Interpolating:} \qquad && \lagrangeRef[i] (\quadNode[i]) &= \delta_{ij}\\
 \label{eq:basis-orthogonality}
-&& \text{Orthogonality:} \qquad &
-\int_0^1 \cdots \int_0^1 \lagrangeRef[j](\hat{\bm(x)} \lagrangeRef[j]{\hat{\bm{x}}}) \dd{\hat{\bm{x}}}  &= \quadWeight[i] \delta_{ij}
+&& \text{Orthogonality:} \qquad &&
+\underbrace{\int_0^1 \cdots \int_0^1}_{d \,\text{times}}
+\lagrangeRef[i] \left( \hat{\bm{x}} \right)
+\lagrangeRef[j] \left( \hat{\bm{x}} \right) \dd{\hat{\bm{x}}}
+&= \quadWeight[i] \delta_{ij}
     \end{alignat}
@@
 We will later need basis functions over a space-cell
+$v = 0, \ldots, \NVar, n = 0, \ldots, (N+1)^{\dimensions} - 1, l=0,\ldots,N$
 \begin{align}\label{eq:space-basis}
   \begin{split}
-  \sbasisRef(\hat{\bm{x}}) &= \sum_i^{(N+1)^D - 1} \lagrange[i] (x_i)\\
-  \sbasis(\bm{x}) &= \sbasisRef \left( \mapping(\bm{x}) \right)
+  \sbasisRef[][n] (\hat{\bm{x}}) &= \lagrange[n] (x)\\
+  \sbasis[][n] (\bm{x}) &= \sbasisRef[][n] \left( \mapping(\bm{x}) \right)
   \end{split}
@@
 where $\sbasisRef$ denotes the basis function on the reference cell.
-Similarly, we define a basis for a space-time element defined by $(0, 1)^D \times (t^n, t^{n+1})$
+Similarly, we define a basis for a space-time element defined over $(0, 1)^D \times (t^n, t^{n+1})$
 \begin{align}\label{eq:space-time-basis}
   \begin{split}
-  \stbasisRef(\hat{\bm{x}}, \hat{t}) &= \sum_j^{N} \sum_i^{(N+1)^D - 1} \lagrange[j](x_j) \lagrange[i] (x_i)\\
-  \stbasis (\bm{x}, t) &= \stbasisRef \left( \mapping(\bm{x}), \timeMapping(t) \right)
-  \end{split}
-\end{align}
+  \stbasisRef[][l,n](\hat{\bm{x}}, \hat{t}) &= \lagrange[l](t) \sbasis[][n] (x) = \lagrange[l](t) \lagrange[n](x)\\
+  \stbasis[][l,n] (\bm{x}, t) &= \stbasisRef \left( \mapping(\bm{x}), \timeMapping(t) \right)
+  \end{split}
+\end{align}
+Outside of elements, we define the basis functions to be equal to 0.
+\todo{Bold x, bold t?}
+\todo{Variables in basis, tensor product?}
 
 \sidetitle{Predictor}
-To derive the predictor, we take an approximation of our solution in a nodal basis that is defined both in space and time
-\begin{equation}
-  \label{eq:cell-approx-space-time}
-  q(\bm{x}, t^n)_{|\cell[i]} = \hat{u}^n_{i,l} \stbasis[][l](\bm{x}, t).
-\end{equation}
-Furthermore we assume that all quantities are given in this represantation.
-We now multiply the conservation law by a test function (of the same function space as the basis) and arrive at the weak formulation
+We are now ready to derive the predictor.
+Let $t^n$ be the current simulation time and $t^{n+1} = t^n + \Delta t$ the time at the end of a timestep\todo{Explain in basis functions sec}.
+We first multiply the conservation law by a test function of the same function space as the basis, integrate over a space-time-element $\cell$ and replace the vector of conservative variables $\Q$ with the space-time predictor $\stpredictor[\cell]$
 \begin{equation}\label{eq:weak-pde-space-time}
 \intdt{\intdcell{
-    \sttestfunction{k}(\bm{x}, t)
+    \sttestfunction[\cell](\bm{x}, t)
     \pdv{\stpredictor}{t}
@@
 \intdt{\intdcell{
-    \sttestfunction{k}(\bm{x}, t)
+    \sttestfunction[\cell](\bm{x}, t)
     \left(
@@
 \intdt{\intdcell{
-  \sttestfunction{k} \source(\stpredictor)
+  \sttestfunction[\cell] \source(\stpredictor)
 }}.
 \end{equation}
+
 We integrate the first term by parts in time and the flux divergence in space.
-Here we do not use the Riemann solver for the flux boundary term but rather use the discrete solution at time $t$.
+Here we do not use the Riemann solver for the flux boundary term but rather use the discrete solution at time $t$\todo{Insert in equation!}.
 This corresponds to upwinding in time~\cite{dumbser2008unified}.
@@
 \intdcell{
-  \sttestfunction{k} (\bm{x}, t^{n+1}) \stpredictor(\bm{x}, t^{n+1})
+  \sttestfunction[\cell][k] (\bm{x}, t^{n+1}) \stpredictor(\bm{x}, t^{n+1})
 }
@@
 \intdt{\intdcell{
-    \pdv{}{t} \sttestfunction{k}(\bm{x}, t) \stpredictor(\bm{x}, t)
+    \pdv{}{t} \sttestfunction[\cell][k] (\bm{x}, t) \stpredictor(\bm{x}, t)
 }}
@@
 \intdcell{
-  \sttestfunction{k}(\bm{x},t^n) \dsol(\bm{x}, t^n)
+  \sttestfunction[\cell][k] (\bm{x},t^n) \stpredictor(\bm{x}, t^n)
 }
@@
 \intdt{\intdcell{
-    \sttestfunction{k}(\bm{x},t) \divergence{\flux(\stpredictor, \gradient{\stpredictor})}
+    \sttestfunction[\cell][k] (\bm{x},t) \divergence{\flux(\stpredictor, \gradient{\stpredictor})}
 }}
@@
 \intdt{\intdcell{
-    \sttestfunction{k}(\bm{x}, t) \source(\stpredictor)
+    \sttestfunction[\cell][k] (\bm{x}, t) \source(\stpredictor)
 }}
@@
 \end{align}
+\NewDocumentCommand{\stpredictorCoeff}{ O{} O{} }{\underline{\overline{q}}^{#1}_{#2}}
+\NewDocumentCommand{\stflux}{ O{} O{} }{\overline{F}^{#1}_{#2}}
+\NewDocumentCommand{\stfluxCoeff}{ O{} O{} }{\underline{\overline{F}}^{#1}_{#2}}
+\NewDocumentCommand{\stsource}{ O{} O{} }{\overline{S}^{#1}_{#2}}
+\NewDocumentCommand{\stsourceCoeff}{ O{} O{} }{\underline{\overline{S}}^{#1}_{#2}}
+\NewDocumentCommand{\spred}{ O{} O{} }{u^{#1}_{#2}}
+\NewDocumentCommand{\ssolCoeff}{ O{} O{} }{\underline{u}^{#1}_{#2}}
+\NewDocumentCommand{\sflux}{ O{} O{} }{F^{#1}_{#2}}
+\NewDocumentCommand{\sfluxCoeff}{ O{} O{} }{\underline{F}^{#1}_{#2}}
+\NewDocumentCommand{\ssource}{ O{} O{} }{S^{#1}_{#2}}
+\NewDocumentCommand{\ssourceCoeff}{ O{} O{} }{\underline{S}^{#1}_{#2}}
+All quantities can be expanded in the space-time basis.
+For example, the expansion of space-time predictor can be written as
+\begin{equation}
+  \label{eq:cell-approx-space-time}
+  \stpredictor[\cell] (\bm{x}, t) = \stpredictorCoeff[\cell][v,l,n] \stbasis[\cell][v,l,n](\bm{x}, t).
+\end{equation}
+We denote the space-time flux as $\stflux$ and the space-time source as $\stsource$ with coefficient vectors $\stfluxCoeff$ and $\stsourceCoeff$.
+This is a part where we notice the computational advantage of the nodal approach:
+The coefficients correspond to the quantity evaluated at the basis node!
+
 Inserting \cref{eq:cell-approx-space-time} results in a local systems of equations that can be by a fixed point iteration scheme.
-\todo{Inital guess correct? Maybe cite sth?}
-As initial value for the space-time-predictor we use the solution of the timestep before.
-\todo{Collect into matrices and show scheme?}
 To show the computational efficiency of our scheme, we follow the approach of~\cite{dumbser2008unified} and collect our integrals into matrices\todo{Source is Dominics \aderdg-document.}.
-
+Henceforth, we drop the cell index for all quantities.
+For the space-time predictor, we introduce an iteration counter $i$.
+To close the iterative scheme, we set the initial value for the space-time predictor as
+\begin{equation}
+  \label{eq:initial-guess}
+ \stpredictorCoeff[i](t=0) = \ssolCoeff[i]
+\end{equation}
+which corresponds to a stationary guess\todo{This is an expansion only in space!}.
 \newcommand{\pleft}{\bm{L}}
@@
 \newcommand{\prightpred}{\bm{w}}
+We arrive at the matrices
+\begin{equation}
+  \label{eq:matrices}
+  \pleft \in \mathbb{R}^{\NVar \stbasisSize \times \NVar \stbasisSize}, \quad
+  \prightsol \in \mathbb{R}^{\NVar \stbasisSize}, \quad
+  \prightpred \in \mathbb{R}^{\NVar \stbasisSize}
+\end{equation}
+with entries
 \begin{align}
   \label{eq:predictor-matrices}
-  \pleft^{\cell}_{(n v l), (n' v' l')} &=
+\begin{split}
+  \pleft_{(n v l), (n' v l')} &=
 \intdcell{
-  \sttestfunction[\cell][v,l,n](1) \stbasis[\cell][v,l', n']
-}
--
-\intdt{\intdcell{
-  \left( \pdv{}{t} \sttestfunction[\cell][v,l,n] (t) \right) \stbasis[\cell][v,l',n']
+  \sttestfunction[][v,l,n](\nextTime) \  \stbasis[][v,l', n'](\nextTime)
+}
+\\&-
+\intdt{\intdcell{
+  \left( \pdv{}{t} \sttestfunction[][v,l,n] (t) \right) \stbasis[][v,l',n'] (t)
 }}
+\end{split}
 \\
-\prightsol^{\cell}_{v, l,n} &=
+\begin{split}
+\prightsol_{v, l,n} (\stpredictor) =&
 \intdcell{
-  \sttestfunction[\cell][v,l,n] (0) \sbasis[\cell][v,n'] \dsol[v,n']^{\cell}
-}
-+
-\intdt{\intdcell{
-  \sttestfunction[\cell][v,l,n] \stbasis[\cell][v,l',n'](t) S_{v,l',n'}(\stpredictor[]^{\cell, i})
+  \sttestfunction[][v,l,n] (t) \sbasis[][v,n'] \ssolCoeff[][v,n']
+}
+\\&+
+\intdt{\intdcell{
+  \sttestfunction[][v,l,n] (t) \stbasis[][v,l',n'](t) S_{v,l',n'}(\stpredictor[i])
 }}                             
+\end{split}
   \\
-\prightpred^{\cell}_{v,l,n} &= 
-F^{k}_{v,l',n'}
-\intdt{\intdcell{
-  \left( \gradient{\sttestfunction[\cell][v,l,n]} \right) \stbasis[\cell][v,l',n'](t) S_{v,l',n'}(\stpredictor[]^{\cell, i})
+\prightpred_{v,l,n} (\stpredictor) &=
+\stfluxCoeff[][v,l',n'] (\stpredictor)
+\intdt{\intdcell{
+  \left( \gradient{\sttestfunction[][v,l,n]} \right) \stbasis[][v,l',n'](t)
 }}
 \end{align}
+Note here that $\prightpred$ is constant during a interation step.
 Using these matrices, we can solve for the space-time-predictor with the iterative scheme
@@
   \label{eq:predictor-iterative}
-  \pleft \stpredictor[]^{\cell, i+1} &= \prightsol (\dsol) - \prightpred(\stpredictor[]^{\cell, i}) \\
- \stpredictor[]^{\cell, i+1} &= \pleft^{-1} \left( \prightsol (\dsol) - \prightpred(\stpredictor[]^{\cell, i}) \right).
+  \pleft \stpredictorCoeff[i+1] &= \prightsol (\dsol) - \prightpred(\stpredictorCoeff[i]) \\
+ \stpredictorCoeff[i+1] &= \pleft^{-1} \left( \prightsol (\dsol) - \prightpred(\stpredictorCoeff[i]) \right).
 \end{align}
@@
 This is needed for the Riemann solver and for the reconstruction of boundary values.
-We accomplish this by evaluating the function at the degrees of freedom on the boundary.
+We accomplish this by evaluating the function at the degrees of freedom on the boundary.\todo{Details}
 Thanks to the interpolating property of the nodal basis~\pcref{eq:basis-interpolating}, this reduces to a change of basis which can be precomputed on the reference element.
@@
 \end{equation}
-where the basis, unlike in \cref{eq:cell-approx-time}, does not depend on the time.
+where the basis, unlike in \cref{eq:cell-approx-space-time}, does not depend on the time.
 We then multiply the system \cref{eq:conservation-law-gradient} by a test function $\stestfunction{i}$ and integrate over the space-time volume $(\cell \times [t^n, t^{n+1}])$.
@@
 \todo{Double check the following description}
-We now replace the solution $\bm{Q}$ with the spacetime-predictor $\stpredictor (\bm{x},t)$ and write it as a polynomial using the representation of \cref{eq:cell-approx}.
+We now replace the solution $\bm{Q}$ with the spacetime-predictor $\stpredictor (\bm{x},t)$ and write it as a polynomial using the representation of \cref{eq:cell-approx-space,eq:cell-approx-space-time}\todo{Not all quantities are defined over time}.
 Integrate first by parts in time (note basis here not defined over time), flux divergence by parts in space.
 \newcommand{\massMatrixDef}{\intdcell{
-  \stestfunction[\cell][k] \sbasis[\cell][l]
+  \stestfunction[][n] \sbasis[][n']
 }}
+\todo{Fix following equation, sum only needed due to expansion of dsol}
 \begin{align}
@@
 \label{eq:corrector}
+\sum_{n' = 0}{\stbasisSize}
 \left(
@@
 \left(\intdt{\intdcellb{
-      \stestfunction[k] \Riemann(\stpredictor^-, \stpredictor^+) \cdot \normal
+      \stestfunction[][n] \Riemann(\stpredictor[-], \stpredictor[+]) \cdot \normal
 }}\right)
@@
 \left(\intdt{\intdcell{
-    \gradient{\stestfunction[k]} \cdot  \flux(\stpredictor, \gradient{\stpredictor}) % todo correct gradient?
+    \gradient{\stestfunction[k]} \cdot  \flux(\spredictor, \gradient{\spredictor}) % todo correct gradient?
 }}\right)
@@
 \left(\intdt{\intdcell{
-      \stestfunction[k] \source(\stpredictor)
+      \stestfunction[k] \source(\spredictor)
 }}\right)
@@
 \begin{align}
-  \massMatrix \left( \dsol^{t+1} - \dsol^{t} \right) &=
+  \massMatrix \left( \ssolCoeff[t+1] - \ssolCoeff[t] \right) &=
   \Delta t \left( \bm{a} - \bm{b} + \bm{s} \right) 
@@
 \begin{split}
-a^{\cell}_{v,n} &= F^{\cell}_{n'} \intdt{\intdcell{
-  \sbasis[\cell][v,n'] \gradient{\sbasis[\cell][v,n]}(t)
-}}
+a_{v,n} &= \sfluxCoeff[][n'] \intdcell{
+  \sbasis[][v,n'] \gradient{\sbasis[][v,n]}(t)
+}
 \\
 b &= \ldots \\
-s^{\cell}_n &=
-\intdcell{
-  S^{\cell}_v \sbasis[\cell][v,n]
+s_n &=
+\ssourceCoeff[][v,n'] \intdcell{
+  \sbasis[][v,n] \sbasis[][v,n']
 }
@@
 This Riemann solver was first published in~\cite{gassner2008discontinuous} and used for an \textsc{ader-dg} scheme in~\cite{dumbser2010arbitrary}.
-The timestep is restriced to a so-called \textsc{cfl}-type penalty
+The timestep per dimension $d$ is restriced to a so-called \textsc{cfl}-type penalty
 \begin{equation}\label{eq:cfl-aderdg}
- \Delta t \leq  \text{CFL} \, \frac{\alpha(N) \, h}{\maxConvEigen + 2 \maxViscEigen \frac{2N+1}{h}}
-\end{equation}
-with $N$ polynomial order and $h$ characteristic length scale of elements~\cite{dumbser2010arbitrary,gassner2008discontinuous}.
+ %\Delta t \leq  \text{CFL} \, \frac{\alpha(N) \, h}{\maxConvEigen + 2 \maxViscEigen \frac{1}{\alpha(N) h}}
+ \Delta t \leq  \text{CFL} \, \alpha(N) \, h \sum_{i=0}^{\dimensions-1} \frac{1}{\maxConvEigen + 2 \maxViscEigen \frac{1}{\alpha(N) h}}
+\end{equation}
+with $N$ polynomial order and $h$ side length of the cell~\cite{dumbser2010arbitrary,gassner2008discontinuous}.
+\todo{Paper only describe 1d, explain evaluation of eigenvalues in direction $i$}
+The eigenvalues are evaluated for the flux Jacobian in direction $i$.
 The constant $\alpha(N) \leq {\left( 2N+1  \right)}^{-1}$ is obtained from von Neumann analysis on a simple model problem and depends on the approximation order~\cite{dumbser2008unified}.
+We use this constant for both hyperbolic and diffusive penalty terms to ensure stability.
+For a more detailed and rigoruous stability analysis of the Riemann solver, see~\cite{gassner2008discontinuous}\todo{Is this the correct paper, or is this in the other part of the series?}.
 We use a value of $0.7$ for the constant $\text{CFL}$.
-\todo{Describe CFL-cond.\ for multiple dimensions!}
 
@@
 \newcommand{\fluxY}{\flux_y}
-We discussed a modern, high-order \textsc{DG} method in the previous chapter.
+We discussed a modern, high-order \dg{} method in the previous chapter.
 While this scheme is efficient, it can become unstable, especially in case of discontinuities.
 A simple alternative is a finite volume scheme.
-We use the \muscl\ method, our discussion and notation follows the one in~\cite{toro2013riemann}.
-Similar to~\cite{toro2013riemann} we only describe the two-dimensional case, an extension to three dimensions is straigthforward.
+We use the \muscl{} method\todo{Cite original paper (van Leer)}, our discussion and notation follows the one in~\cite{toro2009riemann}.
+Similar to~\cite{toro2009riemann} we only describe the two-dimensional case, an extension to three dimensions is straigthforward.
 \todo{Source term!}
 
-In contrast to the previous \dg\ scheme, we now only store cell averages instead of a full polynomial solution per cell.
+In contrast to the previous \dg{} scheme, we now only store cell averages instead of a full polynomial solution per cell.
 We achieve higher order then by a reconstruction of a linear function.
@@
 This is done by assuming a linear function per cell.
-\todo{Explain concrete limiter!}
-\todo{Cite minmod limiter. Is this correct? It's the one used}
 We use the minmod slope-limiter
@@
 \end{equation}
-to avoid unphyiscally steep gradients and stabilize the system.
+to avoid unphyiscally steep gradients and stabilize the system~\cite{leVeque2002finite}.
 This function then be used to compute the slopes
@@
 \newcommand{\gobsCount}{n}
+\newcommand{\sampleVariance}{\overline{\variance}}
 A simple way of determining outliers is by how many standard deviations it differs from the mean value.
@@
 To minimize intranodal communications and to simplify the implementation, we do this by performing only pairwise merge operations.
-The simplest way to compute this would be by using the textbook definitions of mean $\mean$ and variance $\variance$ of a random variable $X$
+The simplest way to compute this would be by using the textbook definitions of (population) mean $\mean$ and variance $\variance$ of a random variable $X$
 \newcommand{\expectation}{\mathbb{E}}
@@
     \mean [X] &= \expectation \left[ X \right]\\
-    \variance [X] &= \frac{n}{n-1} \expectation \left[ X^2 \right] - \expectation \left[ X \right]^2.
-  \end{split}
-\end{align}
-\todo{Bessel's correction here!}
-The variance is corrected for bias by the so-called Bessel's correction~\cite{holtzman1950unbiased}.
+    \variance [X] &= \expectation \left[ X^2 \right] - \expectation \left[ X \right]^2.
+  \end{split}
+\end{align}
 The naive algorithm is numerically unstable when the variance is orders of magnitudes smaller than the mean as this can lead to catastrophic cancellations.
@@
 To do this, we need to store three variables per computation unit:
-the mean, the variance and the number of processed elements.
-We collect these items in the vector $\gobs = (\mean, \variance, \gobsCount)$
-We can then merge two pairs of observed variables with \cref{alg:merge-variance}.
+the mean $\mean$, the current sample variance $\sampleVariance$ and the number of processed elements $n$.
+We collect these items in the vector $\gobs = (\mean, \sampleVariance, \gobsCount)$
+We can then merge a pair of observed variables with \cref{alg:merge-variance}.
 This algorithm computes an estimate of the population variance using Bessel's correction, i.e.\ it returns the sample variance times $\nicefrac{n}{n-1}$.
 In our case, the compute the variance over all grid cells.
-We then use
+This is why we compute the population standard deviation by
 \begin{equation}
   \label{eq:sample-std}
- \sigma = \sqrt{\variance[X]} 
-\end{equation}
-as sample standard deviaton.
-Note, that this estimate is biased; an unbiased estimate for general distributions does not exist~\cite{holtzman1950unbiased}.
-\todo{Do we actually care about the bias?}
+ \sigma = \sqrt{ \frac{n-1}{n} \sampleVariance}.
+\end{equation}
 \begin{algorithm}[ht]
@@
 with probability $\mathbb{P}$,
-holds for an arbitrary distribution with mean $\mu$ and standard deviation $\sigma$ probability $\mathbb{P}$~\cite{wasserman2004all}.
+holds for an arbitrary distribution with mean $\mu$ and standard deviation $\sigma$~\cite{wasserman2004all}.
 This motivates the following refinement criterion
@@
 \end{equation}
-which refines when a cell has a significantly higher standard deviation.
+which refines a cell when its total variations differs by a multiple of the standard deviation.
 In this equation, the constants $T_r$ and $T_d$ can be used to tailor the trade-off between the quality of approximation and computational cost.

### 2019-01-07 writing/thesis/chapters/results.tex
Small fix?

@@
 The node has two xxx\todo{name cpus} \textsc{cpu}s with 28 cores each.
-Both \textsc{cpu}s currently run on \SI{1.8}{\GHz}
+Both \textsc{cpu}s currently run on $\SI{1.8}{\GHz}$.
 We use the \tbb{} parallelisation of \exahype{}.
 To find a reasonable parameter for the number of background threads, we ran a grid search.
-We ran three \amr{} testcases for a simulation time of \SI{1}{\min}.
+We ran three \amr{} testcases for a simulation time of $\SI{1}{\min}$.
 \todo{Noisy, show results}
-The best median performance was achieved by using seven background threads.
+The best median performance was achieved by using six background threads.
 

### 2019-01-07 deploy.sh
Remove out of source build temporarily.
Currently broken, not sure why.

@@ -10,6 +10,7 @@ fi
 
 rev=$(git rev-parse --short HEAD)
 
+cp writing/thesis/main.pdf writing/thesis/build/
 cd writing/thesis/build
 
 git init

### 2019-01-08 writing/thesis/chapters/methods.tex
Some proof changes.

@@
 \newcommand{\boundary}{\partial \domain}
+\newcommand{\lagrange}[1][i]{\varphi_{#1}}
+\newcommand{\lagrangeRef}[1][i]{\hat{\varphi}_{#1}}
 \NewDocumentCommand{\sbasis}{ O{} O{} }{\phi^{#1}_{#2}}
@@
 \newcommand{\dsol}[1][h]{\bm{u}_{#1}}
+
+% Space-time dofs
 \NewDocumentCommand{\stpredictor}{ O{} O{} }{\overline{\bm{q}}^{#1}_{#2}}
+\NewDocumentCommand{\stpredictorCoeff}{ O{} O{} }{\underline{\overline{q}}^{#1}_{#2}}
+
+\NewDocumentCommand{\stflux}{ O{} O{} }{\overline{F}^{#1}_{#2}}
+\NewDocumentCommand{\stfluxCoeff}{ O{} O{} }{\underline{\overline{F}}^{#1}_{#2}}
+
+\NewDocumentCommand{\stsource}{ O{} O{} }{\overline{S}^{#1}_{#2}}
+\NewDocumentCommand{\stsourceCoeff}{ O{} O{} }{\underline{\overline{S}}^{#1}_{#2}}
+
+\NewDocumentCommand{\ssol}{ O{} O{} }{u^{#1}_{#2}}
+\NewDocumentCommand{\ssolCoeff}{ O{} O{} }{\underline{u}^{#1}_{#2}}
+
+\NewDocumentCommand{\sflux}{ O{} O{} }{F^{#1}_{#2}}
+\NewDocumentCommand{\sfluxCoeff}{ O{} O{} }{\underline{F}^{#1}_{#2}}
+
+% Space dofs
 \NewDocumentCommand{\spredictor}{ O{} O{} }{\bm{q}^{#1}_{#2}}
+\NewDocumentCommand{\spredictorCoeff}{ O{} O{} }{\underline{q}^{#1}_{#2}}
+
+\NewDocumentCommand{\ssource}{ O{} O{} }{S^{#1}_{#2}}
+\NewDocumentCommand{\ssourceCoeff}{ O{} O{} }{\underline{S}^{#1}_{#2}}
 
@@
 \sidetitle{Basis Functions}
-\newcommand{\lagrange}[1][i]{\varphi_{#1}}
-\newcommand{\lagrangeRef}[1][i]{\hat{\varphi}_{#1}}
 The next step is the definition of basis functions for the reference cell.
-We use Langrange polynomials that are defined in the one-dimensional case by
-\begin{equation}
+We use Langrange polynomials that are defined in the one-dimensional case for the reference interval $(0,1)$ by
+\begin{align}
   \label{eq:lagrange-basis}
-  \lagrangeRef(x) = \prod_{i \neq j}^N \frac{x - x_j}{x_i - x_j}.
-\end{equation}
-We can then represent functions as a sum over the support points $x_j$
+    \lagrangeRef(x) = \prod_{i \neq n}^N \frac{x - {\quadNode{j}}}{x_i - \quadNode[j]},
+\end{align}
+We can then approximate functions as a sum over the support points $\quadNode[j]$
 \begin{equation}
@@
 where we used the Einstein summation convention where summation over repeated indices is implied\todo{Remove this sentence, or sentence before introducing einstein summation!}.
-The support points $x_i$ are chosen such that they coincide with the nodes of the Gauss-Legendre quadrature which we can use to evaluate integrals
+The support points $\quadNode[n]$ are chosen such that they coincide with the nodes of the Gauss-Legendre quadrature of order $N+1$ which we can use to evaluate integrals
 \begin{equation}
   \label{eq:quadrature-1d}
-  \int_0^1 f(x) \dd{x} = \sum_n^N \quadWeight[n] f(x_n),
-\end{equation}
-where $x_n$ is a quadrature point with weight $\quadWeight[n]$.
-
-The basis functions are similarly defined in $d$-dimensions by considering nodes that are the tensor-products of $d$ one-dimensional Gauss-Legendre quadrature.
-To simplify notation, we order the polynomials by a linearised index, a $d$-dimensional function is then approximated by
+  \int_0^1 f(x) \dd{x} = \sum_n^{N+1} \quadWeight[n] f(x_n),
+\end{equation}
+where $\quadNode[n]$ is a quadrature point with corresponding weight $\quadWeight[n]$.
+
+The basis functions are similarly defined in $\dimensions$-dimensions by considering nodes that are the tensor-products of $d$ one-dimensional Gauss-Legendre quadrature.
+To simplify notation, we order the polynomials
+\begin{equation}
+  \label{eq:basis-space}
+  \sbasisRef[][n] (\bm{x}) = \prod_{i=0}^{\dimensions} \lagrangeRef[n] (x_i)
+\end{equation}
+by a linearised index, a $d$-dimensional function is then approximated by
 \begin{equation}
   \label{eq:lagrange-expansion}
-  f(\bm{x}) = \sum_{i = 0}^{(N+1)^\dimensions - 1} f(\bm{x}_i) \lagrangeRef[i](\bm{x}) = f(\bm{x}_i) \lagrangeRef[i](\bm{x}).
+  f(\bm{x}) = \sum_{i = 0}^{\sbasisSize} f(\bm{x}_i) \lagrangeRef[i](\bm{x}) = f(\bm{x}_i) \lagrangeRef[i](\bm{x}).
 \end{equation}
@@
   \label{eq:quadrature}
-  \underbrace{\int_0^1 \cdots \int_0^1}_{\dimensions \text{ times}} f(\bm{x}) \dd{\bm{x}} &= \sum_n^{(N+1)^D - 1} \quadWeight[n] f(\bm{x}_n) \\
+  \underbrace{\int_0^1 \cdots \int_0^1}_{\dimensions \text{ times}} f(\bm{x}) \dd{\bm{x}} &= \sum_n^{\sbasisSize} \quadWeight[n] f(\quadNode[n]) \\
   \intertext{with}
@@
 \todo{Fix notation, especially multi-dimensional integral.}
-\todo{Check number of total polynomials.}
 % TODO: Quadrature
@@
     \end{alignat}
-
-We will later need basis functions over a space-cell
-$v = 0, \ldots, \NVar, n = 0, \ldots, (N+1)^{\dimensions} - 1, l=0,\ldots,N$
+\todo{Fix this for multiple integrals!}
+
+We define the basis functions over a space-cell with an index $n = 0, \ldots, \sbasisSize$
 \begin{align}\label{eq:space-basis}
   \begin{split}
-  \sbasisRef[][n] (\hat{\bm{x}}) &= \lagrange[n] (x)\\
   \sbasis[][n] (\bm{x}) &= \sbasisRef[][n] \left( \mapping(\bm{x}) \right)
@@
 where $\sbasisRef$ denotes the basis function on the reference cell.
-Similarly, we define a basis for a space-time element defined over $(0, 1)^D \times (t^n, t^{n+1})$
+Similarly, we define a basis for a space-time reference element defined over $(0, 1)^D \times (0, 1)$
 \begin{align}\label{eq:space-time-basis}
@@
 \end{align}
+where the first index $l = 0, \ldots, N$ runs over times.
 Outside of elements, we define the basis functions to be equal to 0.
-\todo{Bold x, bold t?}
-\todo{Variables in basis, tensor product?}
+
+We introduce an additional index $v = (0, \ldots, \NVar - 1)$ that corresponds to a variable.
+The complete basis functions are then defined by
+\begin{align}
+  \stbasis[][v,l,n] (\bm{x},t)= \bm{I} \otimes \stbasis[][l,n] (\bm{x}, t)
+\end{align}
+with the identity matrix $\bm{I} \in \mathbb{R}^{\NVar}$\todo{Write out definition for space-time basis+both reference basis funcs}.
 
@@
 \end{align}
-\NewDocumentCommand{\stpredictorCoeff}{ O{} O{} }{\underline{\overline{q}}^{#1}_{#2}}
-\NewDocumentCommand{\stflux}{ O{} O{} }{\overline{F}^{#1}_{#2}}
-\NewDocumentCommand{\stfluxCoeff}{ O{} O{} }{\underline{\overline{F}}^{#1}_{#2}}
-\NewDocumentCommand{\stsource}{ O{} O{} }{\overline{S}^{#1}_{#2}}
-\NewDocumentCommand{\stsourceCoeff}{ O{} O{} }{\underline{\overline{S}}^{#1}_{#2}}
-\NewDocumentCommand{\spred}{ O{} O{} }{u^{#1}_{#2}}
-\NewDocumentCommand{\ssolCoeff}{ O{} O{} }{\underline{u}^{#1}_{#2}}
-\NewDocumentCommand{\sflux}{ O{} O{} }{F^{#1}_{#2}}
-\NewDocumentCommand{\sfluxCoeff}{ O{} O{} }{\underline{F}^{#1}_{#2}}
-\NewDocumentCommand{\ssource}{ O{} O{} }{S^{#1}_{#2}}
-\NewDocumentCommand{\ssourceCoeff}{ O{} O{} }{\underline{S}^{#1}_{#2}}
 All quantities can be expanded in the space-time basis.
@@
 The coefficients correspond to the quantity evaluated at the basis node!
+Similarly, we define the space degrees of freedoms by an expansion in the space basis, for example for the space-predictor
+\begin{equation}
+  \label{eq:cell-approx-space}
+  \spredictor[\cell] (\bm{x}) = \spredictorCoeff[\cell][v,n] \sbasis[\cell][v,n] (\bm{x}),
+\end{equation}
+where the basis, unlike in \cref{eq:cell-approx-space-time}, does not depend on the time\todo{Maybe move to averaging in time?}.
 
@@
   \label{eq:initial-guess}
- \stpredictorCoeff[i](t=0) = \ssolCoeff[i]
+\forall l: \quad \stpredictorCoeff[i][v,l,n] = \ssolCoeff[v,n]
 \end{equation}
@@
 \begin{split}
-\prightsol_{v, l,n} (\stpredictor) =&
+\prightsol_{v, l,n} (\ssol) =&
 \intdcell{
@@
   \label{eq:predictor-iterative}
-  \pleft \stpredictorCoeff[i+1] &= \prightsol (\dsol) - \prightpred(\stpredictorCoeff[i]) \\
- \stpredictorCoeff[i+1] &= \pleft^{-1} \left( \prightsol (\dsol) - \prightpred(\stpredictorCoeff[i]) \right).
-\end{align}
-For details and proof of convergence for the linear case, see~\cite{dumbser2008unified}.
+  \pleft \stpredictorCoeff[i+1] &= \prightsol (\ssol) - \prightpred(\stpredictorCoeff[i]) \\
+ \stpredictorCoeff[i+1] &= \pleft^{-1} \left( \prightsol (\ssol) - \prightpred(\stpredictorCoeff[i]) \right).
+\end{align}
+For details and proof of convergence for case of linear \pde{}s, see~\cite{dumbser2008unified}.
 
@@
 The final step of the \aderdg{}-scheme is the corrector.
-For this step, we write the approximation of a function $q$ in a cell as
-\begin{equation}
-  \label{eq:cell-approx-space}
-  q(\bm{x})_{|\cell[i]} = \hat{u}^n_{i,l} \sbasis{l}(\bm{x}),
-\end{equation}
-where the basis, unlike in \cref{eq:cell-approx-space-time}, does not depend on the time.
 We then multiply the system \cref{eq:conservation-law-gradient} by a test function $\stestfunction{i}$ and integrate over the space-time volume $(\cell \times [t^n, t^{n+1}])$.
@@
 \intdt{\intdcell{
-\stestfunction{k} \pdv{\Q}{t}
+\stestfunction[][v,n] \pdv{\Q}{t}
 }}
@@
 \intdt{\intdcell{
-    \stestfunction{k} \left( \div{F(\Q, \gradQ } \right)
+    \stestfunction[][v,n] \left( \div{F(\Q, \gradQ } \right)
 }}
@@
 \intdt{\intdcell{
-    \stestfunction{k} S(\Q, \bm{x}, t)
+    \stestfunction[][v,n] S(\Q, \bm{x}, t)
 }}.
@@
 We now replace the solution $\bm{Q}$ with the spacetime-predictor $\stpredictor (\bm{x},t)$ and write it as a polynomial using the representation of \cref{eq:cell-approx-space,eq:cell-approx-space-time}\todo{Not all quantities are defined over time}.
-Integrate first by parts in time (note basis here not defined over time), flux divergence by parts in space.
+The first part can be integrated by parts in time with the convenient result that only the boundary terms remain because the basis is constant in time.
+We then integrate the flux divergence by parts in space and insert the Riemann solver to connect with the neighbouring elements.
+Finally, we need to solve
 \newcommand{\massMatrixDef}{\intdcell{
-  \stestfunction[][n] \sbasis[][n']
+  \stestfunction[][v,n] \sbasis[][v,n']
 }}
@@
 \label{eq:corrector}
-\sum_{n' = 0}{\stbasisSize}
+% \sum_{n' = 0}^{\stbasisSize}
 \left(
@@
 \right)
-(\bm{u^{n+1} - u^{n}})
+(\ssolCoeff[t^{n+1}][v,n'] - \ssolCoeff[t^n][v,n'])
 &+
 \left(\intdt{\intdcellb{
-      \stestfunction[][n] \Riemann(\stpredictor[-], \stpredictor[+]) \cdot \normal
+      \stestfunction[][v,n] \Riemann(\spredictor[-], \spredictor[+]) \cdot \normal
 }}\right)
@@
 \left(\intdt{\intdcell{
-    \gradient{\stestfunction[k]} \cdot  \flux(\spredictor, \gradient{\spredictor}) % todo correct gradient?
+    \gradient{\stestfunction[v,n][k]} \cdot  \flux(\spredictor, \gradient{\spredictor}) % todo correct gradient?
 }}\right)
@@
 \left(\intdt{\intdcell{
-      \stestfunction[k] \source(\spredictor)
+      \stestfunction[v,n][k] \source(\spredictor)
 }}\right)
@@
 \end{align}
-The first term is our mass matrix with entries
+for the coefficients $\ssolCoeff[\nextTime][v,n]$ of the new solution.
+Here $\spredictor[\pm]$ are the boundary extrapolated space-predictors.
+Again, the computational effort can be vastly reduced, by collecting the integrals in matrices and precomputing as much as possible.
+The first term is thed mass matrix with entries
 \newcommand{\massMatrix}[1][]{\bm{M}_{#1}}
@@
   \label{eq:mass-matrix}
-  \massMatrix[kl] = \massMatrixDef = \volume \underbrace{\quadWeight[k] \delta_{kl}}_{\text{diagonal}}
+  \massMatrix[n n'] = \massMatrixDef = \volume \underbrace{\quadWeight[n] \delta_{n n'}}_{\text{diagonal}}
 \end{equation}
@@
   \intertext{with}
-\begin{split}
 a_{v,n} &= \sfluxCoeff[][n'] \intdcell{
@@
 \\
-b &= \ldots \\
+\label{eq:corrector-surface}
+b_{v,n} &= \intdcellb{
+    \stestfunction[][v,n] \Riemann(\spredictor[-], \spredictor[+]) \cdot \normal
+} \\
 s_n &=
@@
 ,
-\end{split}
 \end{align}
 where we evaluated the time-integrals by using the fact that our quantities are time-averaged.
-We can solve this for the new unknows $\bm{u}^{n+1}$
+The surface integral \pcref{eq:corrector-surface} can be evaluated by summing over the contributions of the faces of each cell, which are computed by integrating the extrapolated space predictor with Gaussian quadrature.
+We can solve \cref{eq:corrector} for the new unknows $\bm{u}^{n+1}$
 \begin{align}\label{eq:update-predictor}
@@
 \end{equation}
-We also use the slopes defined in \cref{eq:slopes} to estimate the gradient of $\cellAvg$ in each cell by the block matrix\todo{Notation!}
+We also use the slopes defined in \cref{eq:slopes} to estimate the gradient of $\cellAvg$ in each cell by the block matrix
 \begin{equation}
@@
 To achieve second order in time, we evolve the boundary extrapolated values in time by
-\todo{Correct index for gradient of cell average}
-\todo{Actually compare with implementation. Currently gradient is ignored here!}
-\todo{Describe splliting of $\flux$ into $\fluxX, \fluxY$}
 \newcommand{\evolvedCellAvg}[2][i,j]{\hat{U}_{#1}^{#2}}
@@
   \begin{split}
-  \forall_{k \in [-x, +x, -y, +y]}:  \hat{U}_{ij}^k = \cellAvg^k &+
+  \forall (k \in \{-x, +x, -y, +y \} ): \quad  \hat{U}_{ij}^k = \cellAvg^k &+
   \frac{\Delta t}{2 \Delta x} \left[ \fluxX(\cellAvg^{-x}, \gradCellAvg) - \fluxX(\cellAvg^{+x}, \gradCellAvg) \right] \\&+
-  \frac{\Delta t}{2 \Delta y} \left[ \fluxY(\cellAvg^{-y}, \gradCellAvg) - \fluxY(\cellAvg^{+y}, \gradCellAvg) \right].
-  \end{split}
-\end{equation}
+  \frac{\Delta t}{2 \Delta y} \left[ \fluxY(\cellAvg^{-y}, \gradCellAvg) - \fluxY(\cellAvg^{+y}, \gradCellAvg) \right],
+  \end{split}
+\end{equation}
+where $\fluxX$ and $\fluxY$ denote the $x$ and $y$ part of the flux respectively.
 Note that we do not need to consider neighboring cells for this step.
@@
 This section is concerned with two different but related concepts:%
-adaptive mesh refinement \amr{} and finite volume limiting.
+finite volume limiting and adaptive mesh refinement (\amr{}).
 Both have in common that they change the structure of the grid.
@@
 
+\subsection{Limiting}\label{sec:limiting}
+Higher order \textsc{dg} methods cannot cope with discontinuous solutions.
+Even worse, in the case of non-linear fluxes, discontinuities can appear even from smooth initial data.
+In addition, oscillations stemming from the high-order polynomical approximation can lead to wrong or unphyiscal data.
+This is called Gibbs phenomenon.
+A classical way of dealing with this problem is the usage of so called limiters.
+The idea is to smooth out steep gradients and thus eliminate discontinuities~\cite{hesthaven2008nodal}.\todo{It doesnt work like this exactly.}
+
+A relatively recent way of dealing with this problem is the finite volume subcell limiter.
+Our discussion follows the one in~\cite{dumbser2016simple}.
+This limiting is an a posteriori limiting, which means that we first evaluate a timestep with an unlimited \textsc{ader-dg} method and then check, whether our solution is \enquote{correct}.
+In our case, we check whether the solution is a valid floating point number.
+We also check whether it is physically admissible with the criterion\todo{Do I actually check for pos.\ of Z?}
+\begin{equation}
+  \label{eq:limiting-physical}
+  \operatorname{is-admissible}(\Q) =
+  \begin{cases}
+    \text{true} & \Qrho > 0 \land \pressure > 0 \land \QZZ > 0 \\
+    \text{false} & \text{otherwise}.
+  \end{cases}
+\end{equation}
+The positivity of the pressure implies positivity of energy.
+\todo{Mention dmp if I end up using it.}
+
+If a solution violates our criterion, we recompute the last timestep for the offending cells with a limited finite volume method.
+In our case we use the \muscl{}-method (\cref{sec:muscl}).
+The recomputation starts by subdividing the infringing cell into $N_s = 2N + 1$ subcells.
+This number of subcells has the advantage that we do not loose spatial resolution and that we can use the same timestep size for both cell types.
+The reason for this is that the \textsc{cfl}-conditions for both schemes \pcref{eq:cfl-aderdg,eq:cfl-muscl} coincide for our choice of $N_s$.
+\begin{figure}[htb]
+  \centering
+  \includegraphics[scale=0.7]{thesis_aderdg_subcell_grid}
+  \caption{\label{fig:limiting-subcells}Conversion from \dg{}-dofs to fv-dofs. Image taken from~\cite{dumbser2018conformal}. }
+\end{figure}
+\todo{Cite source for subcells~\pcref{fig:limiting-subcells}. See guidebook. NOTE THAT IT IS MODIFIED. Also: Fix size, currently font is too small}
+
+\Cref{fig:limiting-subcells} depicts the mapping from \dg{}-cells to finite volume subcells.
+For the sake of brevity, we omit technical details and refer the interested reader to~\cite{dumbser2016simple}.
+
 \subsection{Adaptive Mesh Refinement}\label{sec:amr}
-The goal of \amr{} is increasing the computational efficiency by using a higher spatial resolution in areas of interest.
+The goal of \amr{} is to increase the computational efficiency by using a coarse spatial resolution in areas with low information content and a higher resolution in areas of interest.
 A simple example for this would be using finer mesh cells for the simulation of a wave, while using a low resolution for areas where the wave does not pass through.
@@
   \label{eq:tv}
-  \tv \left[ f(\bm{x}] \right] =
-\int_{\domain} \vert \gradient{f \left( \bm{x} \right)} \vert.
-\end{equation}
+  \tv \left[ f(\bm{x}) \right] =
+  \Vert
+\intdcell{ \vert \gradient{f \left( \bm{x} \right)} \vert }
+\Vert_1
+,
+\end{equation}
+for each cell.
+The operator $\Vert \cdot \Vert_1$ denotes the discrete $l_1$ norm in this equation.
 This integral can be evaluated efficiently on the reference cell \pcref{eq:space-mapping,eq:cell-approx-space} with Gaussian quadrature \pcref{eq:quadrature}.
-In the following, we divide this total variation by the volume of each cell, i.e.\ we use the volume of the corresponding reference cells as criterion.
-
-\todo{Gradient on reference cell, Gaussian quad., inline}
+
 \todo{Definition for FV schemes (maybe just mapping to DG-Cells)}
@@
 \newcommand{\sampleVariance}{\overline{\variance}}
-A simple way of determining outliers is by how many standard deviations it differs from the mean value.
+A simple way of determining outliers is by how many standard deviations a value differs from the mean value.
 We thus want to compute the mean and variance over all grid cells.
-To minimize intranodal communications and to simplify the implementation, we do this by performing only pairwise merge operations.
-The simplest way to compute this would be by using the textbook definitions of (population) mean $\mean$ and variance $\variance$ of a random variable $X$
+For computational efficiency and to simplify the implementation, we do this by performing only pairwise merge operations.
+The simplest way to compute is by the textbook definitions of mean $\mean$ and population variance $\variance$ of a random variable $X$
 \newcommand{\expectation}{\mathbb{E}}
@@
   \begin{split}
-    \mean [X] &= \expectation \left[ X \right]\\
-    \variance [X] &= \expectation \left[ X^2 \right] - \expectation \left[ X \right]^2.
-  \end{split}
-\end{align}
-The naive algorithm is numerically unstable when the variance is orders of magnitudes smaller than the mean as this can lead to catastrophic cancellations.
+    \mean [X] &= \expectation \left[ X \right],\\
+    \variance [X] &= \expectation \left[ X^2 \right] - \expectation \left[ X \right]^2,
+  \end{split}
+\end{align}
+where $\expectation \left[ X \right]$ denotes the expectation of a random variable $X$.
+The naive algorithm is numerically unstable when the variance is orders of magnitudes smaller than the mean, as this can lead to catastrophic cancellations.
 We thus compute the mean and variance with the parallel algorithm of~\cite{chan1982updating}.
@@
 the mean $\mean$, the current sample variance $\sampleVariance$ and the number of processed elements $n$.
-We collect these items in the vector $\gobs = (\mean, \sampleVariance, \gobsCount)$
+We collect these items in the vector $\gobs = (\mean, \sampleVariance, \gobsCount)$.
 We can then merge a pair of observed variables with \cref{alg:merge-variance}.
@@
 \end{equation}
-with probability $\mathbb{P}$,
-holds for an arbitrary distribution with mean $\mu$ and standard deviation $\sigma$~\cite{wasserman2004all}.
+where $\mathbb{P}$ is the probability of an event,
+holds for arbitrary distributions with mean $\mu$ and standard deviation $\sigma$~\cite{wasserman2004all}.
 This motivates the following refinement criterion
@@
     \text{refine} & \text{if } \tv(\Q) \geq \mu + T_\text{refine} \sigma \\
-    \text{delete} & \text{if } \tv(\Q) \leq \mu + T_\text{delete} \sigma \\
+    \text{delete} & \text{if } \tv(\Q) < \mu + T_\text{delete} \sigma \\
     \text{keep} & \text{otherwise}
@@
 which refines a cell when its total variations differs by a multiple of the standard deviation.
-In this equation, the constants $T_r$ and $T_d$ can be used to tailor the trade-off between the quality of approximation and computational cost.
-They can be chosen freely, as long as $T_d < T_r$ holds.
-Chebychev's inequality then guarantees that only a subset is marked for refinement.
+In this equation, the constants $T_\text{refine}$ and $T_\text{delete}$ can be used to tailor the trade-off between the quality of approximation and computational cost.
+They can be chosen freely, as long as $T_\text{refine} < T_\text{delete}$.
+Chebychev's inequality~\pcref{eq:chebychev} then guarantees that only a subset of cells is marked for refinement.
 Note that this inequality provides only a loose bound.
-If one would be willing to assume a distribution of the indicator variable, tighter bounds can be derived.
-
-\subsection{Limiting}\label{sec:limiting}
-Higher order \textsc{dg} methods cannot cope with discontinuous solutions.
-Even worse, in the case of non-linear fluxes, discontinuities can appear even from smooth initial data.
-In addition, oscillations stemming from the high-order polynomical approximation can lead to wrong or unphyiscal data.
-This is called Gibbs phenomenon.
-A classical way of dealing with this problem is the usage of so called limiters.
-The idea is to smooth out steep gradients and thus eliminate discontinuities~\cite{hesthaven2008nodal}.\todo{It doesnt work like this exactly.}
-
-A relatively recent way of dealing with this problem is the finite volume subcell limiter.
-Our discussion follows the one in~\cite{dumbser2016simple}.
-This limiting is an a posteriori limiting, which means that we first evaluate a timestep with an unlimited \textsc{ader-dg} method and then check, whether our solution is \enquote{correct}.
-In our case, we check whether the solution is a valid floating point number.
-We also check whether it is physically admissible.
-In our case we use the criterion
-\begin{equation}
-  \label{eq:limiting-physical}
-  \operatorname{is-admissible}(\Q) =
-  \begin{cases}
-    \text{true} & \Qrho > 0 \land \pressure > 0 \land \QZZ > 0 \\
-    \text{false} & \text{otherwise}.
-  \end{cases}
-\end{equation}
-The positivity of the pressure implies positivity of energy.
-\todo{Mention dmp if I end up using it.}
-
-If a solution violates our criteria, we recompute the timestep using a limited finite volume method.
-In our case we use the \muscl{}-method (\cref{sec:muscl}).
-The recomputation starts by subdividing the infringing cell into $N_s = 2N + 1$ subcells.
-This number of subcells has the advantage that we do not loose spatial resolution.
-Similarly, we can use the same timestep size for both cell types.
-The reason for this is that the \textsc{cfl}-conditions for both schemes \pcref{eq:cfl-aderdg,eq:cfl-muscl} coincide for our choice of $N_s$.
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[scale=0.7]{thesis_aderdg_subcell_grid}
-  \caption{\label{fig:limiting-subcells}Conversion from \dg{}-dofs to fv-dofs. Image taken from~\cite{dumbser2018conformal}. }
-\end{figure}
-\todo{Cite source for subcells~\pcref{fig:limiting-subcells}. See guidebook. NOTE THAT IT IS MODIFIED. Also: Fix size, currently font is too small}
-For the sake of brevity, we omit technical details.
-We refer the interested reader to~\cite{dumbser2016simple}.
+If one would be willing to assume a distribution of the indicator variable, tighter bounds can be derived~\cite{wasserman2004all}.
 

### 2019-01-08 writing/thesis/chapters/results.tex
Some proof changes.

@@
   \includegraphics{thesis_convergence}
-  \caption{$L_2$-Error vs.\ Grid Size}
+  \caption{$L_2$-Error vs.\ Grid Size.
+    The dashed lines are the optimal order of convergence $N+1$.
+  The line is estimated by using the constant part of a linear regression fit and the ideal order as slope.}
   \label{fig:convergence-l2-error}
@@
 where $V = \Delta x \Delta y$ is the volume of each two-dimensional cell.
+\todo{Use quadNodes, quadWeights and volume macro}
 The sum runs over all quadrature nodes $x_i$ with weights $w_i$.
-We use ten nodes.
+We use ten nodes for all orders and evaluate our solution for all nodes.
+In this way we ensure a fair comparision.
 

### 2019-01-11 writing/thesis/chapters/methods.tex
Update methods.

@@
 
-% Stuff for numerics
+% Domain
 \newcommand{\domain}{\Omega}
+\newcommand{\boundary}{\partial \domain}
 \newcommand{\broken}{\domain}
+
+% Cells
 \newcommand{\cell}[1][]{C_{#1}}
-\newcommand{\boundary}{\partial \domain}
+\newcommand{\refCell}[1][]{\hat{C}_{#1}}
+\newcommand{\cellb}{\partial{} \cell}
+\newcommand{\refCellb}{\partial{} \refCell}
+
+% Basis functions
 \newcommand{\lagrange}[1][i]{\varphi_{#1}}
@@
 \NewDocumentCommand{\sbasis}{ O{} O{} }{\phi^{#1}_{#2}}
-\NewDocumentCommand{\stbasis}{ O{} O{} }{ \Theta^{#1}_{#2}}
 \NewDocumentCommand{\sbasisRef}{ O{} O{} }{\hat{\phi}^{#1}_{#2}} %{\hat{\sbasis[#1][#2]}}
-\NewDocumentCommand{\stbasisRef}{ O{} O{} }{\hat{\Theta}^{#1}_{#2}} %{\hat{\stbasis[#1][#2]}}
+\NewDocumentCommand{\stbasis}{ O{} O{} }{ \psi^{#1}_{#2}}
+\NewDocumentCommand{\stbasisRef}{ O{} O{} }{\hat{\psi}^{#1}_{#2}} %{\hat{\stbasis[#1][#2]}}
 %\newcommand{\stestfunction}[1]{\sbasis[#1]}
@@
 \NewDocumentCommand{\sttestfunction}{ O{} O{} }{\stbasis[#1][#2]}
-\newcommand{\normal}{\bm{n}}
-\newcommand{\dsol}[1][h]{\bm{u}_{#1}}
 
@@
 
+% \NewDocumentCommand{\stsol}{ O{} O{} }{\overline{u}^{#1}_{#2}}
+% \NewDocumentCommand{\stsol}{ O{} O{} }{\underline{\overline{u}}^{#1}_{#2}}
+
 \NewDocumentCommand{\stsource}{ O{} O{} }{\overline{S}^{#1}_{#2}}
 \NewDocumentCommand{\stsourceCoeff}{ O{} O{} }{\underline{\overline{S}}^{#1}_{#2}}
-
-\NewDocumentCommand{\ssol}{ O{} O{} }{u^{#1}_{#2}}
-\NewDocumentCommand{\ssolCoeff}{ O{} O{} }{\underline{u}^{#1}_{#2}}
-
-\NewDocumentCommand{\sflux}{ O{} O{} }{F^{#1}_{#2}}
-\NewDocumentCommand{\sfluxCoeff}{ O{} O{} }{\underline{F}^{#1}_{#2}}
 
@@
 \NewDocumentCommand{\ssourceCoeff}{ O{} O{} }{\underline{S}^{#1}_{#2}}
+
+\NewDocumentCommand{\ssol}{ O{} O{} }{u^{#1}_{#2}}
+\NewDocumentCommand{\ssolCoeff}{ O{} O{} }{\underline{u}^{#1}_{#2}}
+
+\NewDocumentCommand{\sflux}{ O{} O{} }{F^{#1}_{#2}}
+\NewDocumentCommand{\sfluxCoeff}{ O{} O{} }{\underline{F}^{#1}_{#2}}
 
@@
 % Integrals
-\newcommand{\curTime}{t^n}
-\newcommand{\nextTime}{t^{n+1}}
+\newcommand{\curTime}{t^k}
+\newcommand{\nextTime}{t^{k+1}}
 \newcommand{\intdt}[1]{\int_{\curTime}^{\nextTime} #1 \dd{t}}
 \newcommand{\intdcell}[1]{\int_{\cell} #1 \dd{\bm{x}}}
-\newcommand{\intdrefcell}[1]{\int_{\cell} #1 \dd{\hat{\bm{x}}}}
-\newcommand{\intdcellb}[1]{\int_{\partial{} \cell} #1 \dd{S}} % TODO: define boundary of cell
-\newcommand{\intdrefcellb}[1]{\int_{\partial{} \cell} #1 \hat{\dd{S}}} % TODO: define boundary of cell
+\newcommand{\intdrefcell}[1]{\int_{\refCell} #1 \dd{\hat{\bm{x}}}}
+\newcommand{\intdcellb}[1]{\int_{\cellb} #1 \dd{S}} % TODO: define boundary of cell
+\newcommand{\intdrefcellb}[1]{\int_{\refCellb} #1 \hat{\dd{S}}} % TODO: define boundary of cell
 
@@
 \newcommand{\quadWeight}[1][i]{w_{#1}}
-\newcommand{\quadNode}[1][i]{n_{#1}}
+\newcommand{\quadNode}[1][i]{\hat{x}_{#1}}
+\newcommand{\quadNodeNd}[1][i]{\hat{\bm{x}}_{#1}}
 \newcommand{\sbasisSize}{(N+1)^\dimensions}
 \newcommand{\stbasisSize}{(N+1)^{\dimensions+1}}
+\newcommand{\normal}{\bm{n}}
+
+\newcommand{\pleft}{\bm{L}}
+\newcommand{\prightsol}{\bm{r}}
+\newcommand{\prightpred}{\bm{w}}
 
@@
 This chapter describes the numerical and physical background that is needed to simulate reacting fluids with good accuracy.
-We start with a description 
-We start with a description of the arbitrary high order derivatives (\ader) discontinuous Galerkin (\dg) method with a focus on equations that contain both advective and diffusive terms.
-We then seque into a short description of the \muscl\ scheme, a second order finite volume scheme.
-
-We conclude this chapter by a description of adaptive mesh refinement (\amr) and finite volume limiting, which combines both numerical methods to achieve a stable, high-order method.
+We start with a description of the arbitrary high order derivatives (\ader{}) discontinuous Galerkin (\dg{}) method with a focus on equations that contain both advective and diffusive terms.
+We then seque into a short description of the \muscl{} scheme which is a second order finite volume scheme.
+
+We conclude this chapter by a description of finite volume limiting and adaptive mesh refinement (\amr{}).
+The limiting combines both numerical methods to achieve a stable, high-order method and the \amr{} allows us to perform high quality simulations with a smaller computational cost.
 
@@
 }
-
 \newcommand{\viscFluxDef}{
@@
 }
-
 Fluid motion can be described by the compressible Navier Stokes equations.
@@
 In the following, we will denote the spatial coordinates as $\bm{x} = \left( x,z \right)$ and $\bm{x} = \left( x,y,z \right)$ for the two and three-dimensional case respectively.
-The variable $t$ corresponds to the currenty (physical) time.
-We solve the \pde\ in the conversative form \pcref{eq:conservation-law-gradient}\todo{Dont reference to following chapter!}
+The variable $t$ corresponds to the current physical time.
+We solve the \pde{} in the conservative form% \pcref{eq:conservation-law-gradient}
 \begin{equation}
@@
 
-The rows of the equation are the conservation of mass, the conservation of momentum, the conservation of energy and the continuity of the reactant.
-We split the flux into a hyperbolic $\hyperFlux(\Q)$ and a viscous part$\viscFlux(\gradQ)$
-
+The rows of the equation are the conservation of mass, the conservation of momentum, the conservation of energy and the continuity equation of the reactant.
+We split the flux into a hyperbolic $\hyperFlux(\Q)$ and a viscous part $\viscFlux(\Q, \gradQ)$
 \begin{equation}
@@
 In this equation $\bm{a} \otimes \bm{b} = \bm{a} \bm{b}^\intercal$ is the Kronecker or outer product of two vectors $\bm{a}$ and $\bm{b}$.
-The pressure $\pressure$ is given by the caloric equation of state of an ideal reacting gas\todo{Geopot height correct?}
+The pressure $\pressure$ is given by the caloric equation of state of an ideal reacting gas
 \begin{equation}
@@
 
-We also support two different kind of (optional) source terms.
-\todo{Either include gravity in pressure or add source term for energy.}
+We also support two different kind of optional source terms.
 The first source term is gravity, given by
@@
 \end{equation}
-where $g = 9.81$ and $\bm{k}$ is a unit vector pointing in $z$-direction.
+where $g = 9.81$ and $\bm{k}$ is a unit vector pointing in $z$-direction\todo{Discuss $g$ either in pressure or scenario.}.
 
@@
 \newcommand{\backgroundRho}{\overline{\Qrho}}
-Some of our scenarios can be described as a pertubation of a background state that is in hydrostatic balance
+Some of our scenarios can be described as a pertubation of a background state that is initially in hydrostatic balance
 \begin{equation}
@@
   =
-  -g \bm{k} \cdot \Qrho
-\end{equation}.
-The background state \cref{eq:hydrostatic-balance} leads to large values and can diminish other parts of the flux due to numerical instabilities~\cite{muller2010adaptive}.
-We can now split the pressure as $\pressure = \backgroundPressure(z) + \pressure' (\bm{x}, t)$ and the density as $\Qrho = \backgroundRho(z) + \Qrho'(\bm{x}, t)$.
-Inserting this splitting, the definition of divergence into \cref{eq:momentum-equation} allows us to apply \cref{eq:hydrostatic-balance}.
+  -g \bm{k} \cdot \Qrho.
+\end{equation}
+The background state \cref{eq:hydrostatic-balance} can be comparitively large and can thus diminish other parts of the flux due to numerical instabilities~\cite{muller2010adaptive}.
+To avoid this, we split the pressure as $\pressure = \backgroundPressure(z) + \pressure' (\bm{x}, t)$ and the density as $\Qrho = \backgroundRho(z) + \Qrho'(\bm{x}, t)$.
+Inserting this splitting and the definition of divergence into \cref{eq:momentum-equation} allows us to apply \cref{eq:hydrostatic-balance}.
 Furthermore, the background states have zero derivatives in all directions but in $z$.
@@
 Note that the time derivative of the background density also vanishes.
-We do not use this to simplify the implementation of the gradient computation.
-This form of the equation is similar to equation set 3 of~\cite{giraldo2008study} but without splitting the energy.
+This form of the equation is inspired by equation set 3 of~\cite{giraldo2008study}.
+They additionally use a splitting of the energy and use the pertubations directly as conservative variables.
+%We do not use this to simplify the implementation of gradients.
 
@@
 \end{equation}
-We use the very simple reaction model
+We use the simple reaction model
 \begin{equation}\label{eq:reaction-model}
@@
 \end{equation}
-where $\reactionTimescale$ is the timescale of the reaction and $\reactionTemperature$ is the activation temperature.
+where $\reactionTimescale$ is the timescale of the reaction and $\reactionTemperature$ is the activation temperature~\cite{hidalgo2011ader,helzel2000modified}.
 
 \subsection{Boundary conditions}
-To close the system we need to impose boundary conditions.
+To close the system we need to impose boundary conditions.\todo{Adapt this chapter to implementation!}
 
@@
 Our description of the main method follows~\cite{dumbser2008unified,dumbser2010arbitrary,dumbser2018efficient}, our notation follows primarily~\cite{dumbser2018efficient}.
-Let $\NVar$ be the number of variables and $\dimensions$ the number of spatial dimensions.
+Let $\NVar$ be the number of variables, $\dimensions$ the number of spatial dimensions and $N > 0$ the order of the method.
 We discuss the approximation of systems of partial differential equations (\pde) of the form
@@
 For each cell we denote its center by $\cellCenter{\cell}$ and its size by $\Delta x, \Delta y$ and $\Delta z$.
-%In the following we make use of the Einstein summation convention where summation over repeated indexes is implied.
-% Inside each cell $\cell$ we represent the solution in terms of the basis function 
-% \begin{equation}
-%   \label{eq:cell-approx}
-%   u(\bm{x}, t^n)_{|\cell[i]} = \hat{u}^n_{i,l} \sbasis{l}(\bm{x}),
-% \end{equation}
-% where $l$ is a multi-index, containing one index per spatial dimension.
-% \todo{dofs $\hat{u}$, local solution, etc.}
-% For example, $(l = (l_1, l_2))$ for the two dimensional case.
-% This polynomial is interpolating, i.e.\ \ldots\todo{interpolating?}.
-% This choice of basis (called \textit{nodal} basis) allows us to easily compute integrals over cells using Gaussian quadrature.
-% In detail, we use a the Lagrange interpolation polynomials.
 
@@
 For reasons of computational efficiency, we describe the scheme in terms of a reference cell.
-We use the quad cell $\hat{\cell} = [0, 1]^\dimensions$ as space reference cell.\todo{check if $[0,1]$ detontes correct interval}.
-The mapping, which takes a point on a grid cell with coordinates $\bm{x}$ and returns the corresponding point $\hat{\bm{x}}$ on the reference cell
+We use the quad cell $\hat{\cell} = (0, 1)^\dimensions$ as space reference cell.
+The mapping, which takes a point on the reference cell with coordinates $\hat{\bm{x}}$ and and returns a the coordinates $\bm{x}$ in a grid cell $\cell$ is
 \begin{equation}\label{eq:space-mapping}
-  \hat{x} = \mapping (\bm{x}) =
+  \bm{x} = \mapping (\hat{\bm{x}}) =
   \cellCenter(\cell) +
@@
   \begin{pmatrix}
-    x - 0.5\\
-    y - 0.5\\
-    z - 0.5
+    \hat{x} - 0.5\\
+    \hat{y} - 0.5\\
+    \hat{z} - 0.5
   \end{pmatrix}.
 \end{equation}
-We also define the inverse mapping $\mapping^{-1}$.
-This can be used to define a function $f(\bm{x})$ acting on a point $\bm{x}$ of a regular cell in terms of a function $\hat{f}(\bm{x})$ that acts on the corresponding point of the reference cell by the relation
+The inverse mapping $\mapping^{-1}$ can be used to define a function $f(\bm{x})$ acting on a point $\hat{\bm{x}}$ of a regular cell in terms of a function $\hat{f}(\bm{x})$ that acts on the corresponding point of the reference cell by the relation
 \begin{equation}
@@
 
-Similar to this, we define a mapping that maps a point in time to the reference time $\hat{t} \in (0,1)$
+Similar to this, we define a mapping that maps a reference time point $\hat t$ to simulation time $t$
 \newcommand{\timeMapping}{\mathcal{T}}
@@
   \label{eq:time-mapping}
-  \hat{t} = \timeMapping(t) = t_0 + (\Delta t) t,
-\end{equation}
-where $\Delta t$ is timestep of a cell and $t_0$ is the beginning of its time interval.
-The space-time reference cell is then $\hat{\cell} = [0,1]^{D+1}$
+  t = \timeMapping(\hat{t}) = \curTime + (\Delta t) \hat{t},
+\end{equation}
+where the reference time interval is $[0,1]$ and the time interval of a cell is $[\curTime, \nextTime]$.
+The time at the beginning of a timestep is thus denoted by $\curTime$, the time at the end of a step is denoted by $\nextTime = \curTime + \Delta t$ with timestep size $\Delta t$.
 
@@
 This is useful for evaluating derivatives by the chain rule and, similarly, integrals by substitution.
-For example, we can evaluate a volume integral by
+For example, we can evaluate a volume integral over a cell by
 \begin{equation}
@@
 \sidetitle{Basis Functions}
-The next step is the definition of basis functions for the reference cell.
+The next step is the definition of basis functions for our cells.
 We use Langrange polynomials that are defined in the one-dimensional case for the reference interval $(0,1)$ by
@@
   \label{eq:lagrange-basis}
-    \lagrangeRef(x) = \prod_{i \neq n}^N \frac{x - {\quadNode{j}}}{x_i - \quadNode[j]},
+    \lagrangeRef(x) = \prod_{i >0, j>0, i \neq n}^N \frac{x - {\quadNode[j]}}{x_i - \quadNode[j]},
 \end{align}
@@
 \end{equation}
-where we used the Einstein summation convention where summation over repeated indices is implied\todo{Remove this sentence, or sentence before introducing einstein summation!}.
-The support points $\quadNode[n]$ are chosen such that they coincide with the nodes of the Gauss-Legendre quadrature of order $N+1$ which we can use to evaluate integrals
+where we used the Einstein summation convention which implies summation over repeated free indices.
+This convention is used from here on.
+The support points $\quadNode[i]$ are chosen such that they coincide with the nodes of the Gauss-Legendre quadrature of order $N+1$ which we can use to evaluate integrals
 \begin{equation}
   \label{eq:quadrature-1d}
-  \int_0^1 f(x) \dd{x} = \sum_n^{N+1} \quadWeight[n] f(x_n),
-\end{equation}
-where $\quadNode[n]$ is a quadrature point with corresponding weight $\quadWeight[n]$.
+  \int_0^1 f(\hat{x}) \dd{\hat{x}} = \sum_{i=0}^{N} \quadWeight[i] f(\quadNode[i]),
+\end{equation}
+where $\quadWeight[i]$ is the quadrature weight corresponding to the node $\quadNode[i]$.
 
 The basis functions are similarly defined in $\dimensions$-dimensions by considering nodes that are the tensor-products of $d$ one-dimensional Gauss-Legendre quadrature.
-To simplify notation, we order the polynomials
+They are indexed by a multi-index $n = (n_1, \ldots, n_\dimensions)$
 \begin{equation}
   \label{eq:basis-space}
-  \sbasisRef[][n] (\bm{x}) = \prod_{i=0}^{\dimensions} \lagrangeRef[n] (x_i)
-\end{equation}
-by a linearised index, a $d$-dimensional function is then approximated by
+  \sbasisRef[][n] (\bm{x}) = \prod_{i=0}^{\dimensions} \lagrangeRef[n_i] (x_i)
+\end{equation}
+that is linearised such that $n = (0, \ldots, \sbasisSize)$.
+A $d$-dimensional function is then approximated by
 \begin{equation}
   \label{eq:lagrange-expansion}
-  f(\bm{x}) = \sum_{i = 0}^{\sbasisSize} f(\bm{x}_i) \lagrangeRef[i](\bm{x}) = f(\bm{x}_i) \lagrangeRef[i](\bm{x}).
+  f(\bm{x}) = \sum_{i = 0}^{\sbasisSize - 1} f(\bm{x}_i) \lagrangeRef[i](\bm{x}) = f(\bm{x}_i) \lagrangeRef[i](\bm{x}).
 \end{equation}
@@
   \label{eq:quadrature}
-  \underbrace{\int_0^1 \cdots \int_0^1}_{\dimensions \text{ times}} f(\bm{x}) \dd{\bm{x}} &= \sum_n^{\sbasisSize} \quadWeight[n] f(\quadNode[n]) \\
+  \underbrace{\int_0^1 \cdots \int_0^1}_{\dimensions \text{ times}} f(\hat{\bm{x}}) \dd{\hat{\bm{x}}} &=
+ \sum_{n=0}^{\sbasisSize-1} \quadWeight[n] f(\quadNodeNd[n]) \\
   \intertext{with}
-  \quadWeight[n] &= \prod_{i}^{d} \quadWeight[i].
-\end{align}
-\todo{Fix notation, especially multi-dimensional integral.}
-% TODO: Quadrature
+  \quadWeight[n] &= \prod_{i}^{d} \quadWeight[n_i],
+\end{align}
+where the quadrature weights $\quadWeight[n]$ are the product of all relevant one-dimensional quadrature weights, using the aforementioned (linearized) multi-index $n$.
+\todo{Should be correct. Is there a way to avoid this index hell, esp.\ multi-index?}
 
@@
     \label{eq:basis-interpolating}
-&& \text{Interpolating:} \qquad && \lagrangeRef[i] (\quadNode[i]) &= \delta_{ij}\\
+&& \text{Interpolating:} \qquad && \lagrangeRef[i] (\quadNode[j]) &= \delta_{ij},\\
+&& \qquad && \sbasisRef[][n] (\quadNodeNd[m]) &= \delta_{nm}, \notag\\
 \label{eq:basis-orthogonality}
-&& \text{Orthogonality:} \qquad &&
+&& \text{Orthogonality:} \qquad && \int_0^1 \lagrangeRef[i](x) \lagrangeRef[j](x) \dd{\hat{x}} &= \quadWeight[i] \delta_{ij},\\
+&& \qquad &&
 \underbrace{\int_0^1 \cdots \int_0^1}_{d \,\text{times}}
-\lagrangeRef[i] \left( \hat{\bm{x}} \right)
-\lagrangeRef[j] \left( \hat{\bm{x}} \right) \dd{\hat{\bm{x}}}
-&= \quadWeight[i] \delta_{ij}
+\sbasisRef[][n] \left( \hat{\bm{x}} \right)
+\sbasisRef[][m] \left( \hat{\bm{x}} \right) \dd{\hat{\bm{x}}}
+&= \quadWeight[n] \delta_{nm}, \notag
     \end{alignat}
+    where we make use of the Kronecker delta
+\begin{equation}
+      \label{eq:kronecker-delta}
+      \delta_{ij} =
+      \begin{cases}
+        1 & \text{if } i = j\\
+        0 & \text{otherwise}
+      \end{cases}.
+\end{equation}
 \todo{Fix this for multiple integrals!}
 
-We define the basis functions over a space-cell with an index $n = 0, \ldots, \sbasisSize$
+We define the basis functions over a space-cell with an index $n = 0, \ldots, \sbasisSize - 1$
 \begin{align}\label{eq:space-basis}
@@
 where $\sbasisRef$ denotes the basis function on the reference cell.
-Similarly, we define a basis for a space-time reference element defined over $(0, 1)^D \times (0, 1)$
+
+In addition to the space cells, we also introduce space-time cells $\cell \times [\curTime, \nextTime]$ with reference cell $(0,1)^\dimensions \times  [0,1]$.
+A basis for these cells is given by
 \begin{align}\label{eq:space-time-basis}
   \begin{split}
-  \stbasisRef[][l,n](\hat{\bm{x}}, \hat{t}) &= \lagrange[l](t) \sbasis[][n] (x) = \lagrange[l](t) \lagrange[n](x)\\
+  \stbasisRef[][l,n](\hat{\bm{x}}, \hat{t}) &= \lagrange[l](t) \sbasis[][n] (x)\\
   \stbasis[][l,n] (\bm{x}, t) &= \stbasisRef \left( \mapping(\bm{x}), \timeMapping(t) \right)
@@
 \begin{align}
-  \stbasis[][v,l,n] (\bm{x},t)= \bm{I} \otimes \stbasis[][l,n] (\bm{x}, t)
-\end{align}
-with the identity matrix $\bm{I} \in \mathbb{R}^{\NVar}$\todo{Write out definition for space-time basis+both reference basis funcs}.
+  \stbasis[][v,n,l] (\bm{x},t)= \bm{I} \otimes \stbasis[][n,l] (\bm{x}, t)
+\end{align}
+with the identity matrix $\bm{I} \in \mathbb{R}^{\NVar}$\todo{Write out definition for space-time basis+both reference basis funcs. Explain kronecker delta, maybe when first used in pde chapter}.
+
+\sidetitle{Expansion of quantities}
+All quantities can be expanded in the space-time basis.
+For example, the expansion of space-time predictor $\stpredictor[\cell]$ can be written as
+\begin{equation}
+  \label{eq:cell-approx-space-time}
+  \stpredictor[\cell] (\bm{x}, t) = \stpredictorCoeff[\cell][v',l',n'] \stbasis[\cell][v',l',n'](\bm{x}, t).
+\end{equation}
+We denote the space-time flux as $\stflux$ and the space-time source as $\stsource$ with coefficient vectors $\stfluxCoeff$ and $\stsourceCoeff$.
+Similarly, we define the space degrees of freedoms by an expansion in the space basis, for example for the space predictor
+\begin{equation}
+  \label{eq:cell-approx-space}
+  \spredictor[\cell] (\bm{x}) = \spredictorCoeff[\cell][v',n'] \sbasis[\cell][v',n'] (\bm{x}),
+\end{equation}
+where the basis, unlike in \cref{eq:cell-approx-space-time}, does not depend on the time.
+We need the space-expansion for the predictor $\spredictor$, the discrete solution $\ssol$, the source $\ssource$ and the flux $\sflux$,
+with coefficients $\spredictorCoeff, \ssolCoeff, \ssourceCoeff$ and $\sfluxCoeff$ respectively.
+The indices are in range of $v' = (0, \ldots, \NVar - 1)$, $n' = (0, \ldots, \sbasisSize - 1)$ and $l' = ( 0, \ldots, N)$.
+
+Here, the computational advantage of the nodal approach is evident:
+The coefficients correspond to the quantity evaluated at the basis node, due to the interpolation property~\pcref{eq:basis-interpolating}.
 
@@
 We are now ready to derive the predictor.
-Let $t^n$ be the current simulation time and $t^{n+1} = t^n + \Delta t$ the time at the end of a timestep\todo{Explain in basis functions sec}.
-We first multiply the conservation law by a test function of the same function space as the basis, integrate over a space-time-element $\cell$ and replace the vector of conservative variables $\Q$ with the space-time predictor $\stpredictor[\cell]$
+We first multiply the conservation law by a test function of the same function space as the basis, integrate over a space-time-element $\cell$ and replace all terms with the discrete approximations.
+In particular, we replace the vector of conservative variables $\Q$ with the space-time predictor $\stpredictor[\cell]$.
 \begin{equation}\label{eq:weak-pde-space-time}
 \intdt{\intdcell{
-    \sttestfunction[\cell](\bm{x}, t)
+    \sttestfunction[\cell][v,l,n](\bm{x}, t)
     \pdv{\stpredictor}{t}
@@
 \intdt{\intdcell{
-    \sttestfunction[\cell](\bm{x}, t)
+    \sttestfunction[\cell][v,l,n](\bm{x}, t)
     \left(
-      \divergence{\flux(\stpredictor, \gradient{\stpredictor})}
+      \divergence{\stflux(\stpredictor, \gradient{\stpredictor})}
     \right)
@@
 \intdt{\intdcell{
-  \sttestfunction[\cell] \source(\stpredictor)
-}}.
-\end{equation}
-
-We integrate the first term by parts in time and the flux divergence in space.
-Here we do not use the Riemann solver for the flux boundary term but rather use the discrete solution at time $t$\todo{Insert in equation!}.
+  \sttestfunction[\cell][v,l,n] \stsource(\bm{x}, t, \stpredictor)
+}},
+\end{equation}
+where the indices $v = (0, \ldots, \NVar-1)$, $n = (0, \ldots, \sbasisSize - 1)$ and $l = (0, \ldots, N)$ run over the variables, space and time.
+
+Henceforth, we drop the cell index for all quantities and the spatial argument for the basis and test functions.
+We integrate the first term of \cref{eq:weak-pde-space-time} by parts in time and the flux divergence in space.
+Here we do not use the Riemann solver for the flux boundary term but rather use the known discrete solution at time $t$.
 This corresponds to upwinding in time~\cite{dumbser2008unified}.
 Note that this neglects the interaction with neighbouring cells.
-We account for this in the corrector step.
+The cell-local scheme is then
 \begin{align}\label{eq:space-time-predictor}
@@
 \intdcell{
-  \sttestfunction[\cell][k] (\bm{x}, t^{n+1}) \stpredictor(\bm{x}, t^{n+1})
+  \sttestfunction[][v,l,n] (\nextTime) \stpredictor(\nextTime)
 }
@@
 \intdt{\intdcell{
-    \pdv{}{t} \sttestfunction[\cell][k] (\bm{x}, t) \stpredictor(\bm{x}, t)
+    \pdv{}{t} \sttestfunction[][v,l,n] (t) \stpredictor(t)
 }}
@@
 \intdcell{
-  \sttestfunction[\cell][k] (\bm{x},t^n) \stpredictor(\bm{x}, t^n)
+  \sttestfunction[][v,l,n] (\curTime) \ssol (\curTime)
 }
@@
 \intdt{\intdcell{
-    \sttestfunction[\cell][k] (\bm{x},t) \divergence{\flux(\stpredictor, \gradient{\stpredictor})}
+    \sttestfunction[][v,l,n] (t) \divergence{\stflux(\stpredictor, \gradient{\stpredictor})}
 }}
@@
 \intdt{\intdcell{
-    \sttestfunction[\cell][k] (\bm{x}, t) \source(\stpredictor)
-}}
-\end{split}
-\end{align}
-All quantities can be expanded in the space-time basis.
-For example, the expansion of space-time predictor can be written as
-\begin{equation}
-  \label{eq:cell-approx-space-time}
-  \stpredictor[\cell] (\bm{x}, t) = \stpredictorCoeff[\cell][v,l,n] \stbasis[\cell][v,l,n](\bm{x}, t).
-\end{equation}
-We denote the space-time flux as $\stflux$ and the space-time source as $\stsource$ with coefficient vectors $\stfluxCoeff$ and $\stsourceCoeff$.
-This is a part where we notice the computational advantage of the nodal approach:
-The coefficients correspond to the quantity evaluated at the basis node!
-Similarly, we define the space degrees of freedoms by an expansion in the space basis, for example for the space-predictor
-\begin{equation}
-  \label{eq:cell-approx-space}
-  \spredictor[\cell] (\bm{x}) = \spredictorCoeff[\cell][v,n] \sbasis[\cell][v,n] (\bm{x}),
-\end{equation}
-where the basis, unlike in \cref{eq:cell-approx-space-time}, does not depend on the time\todo{Maybe move to averaging in time?}.
-
-Inserting \cref{eq:cell-approx-space-time} results in a local systems of equations that can be by a fixed point iteration scheme.
-To show the computational efficiency of our scheme, we follow the approach of~\cite{dumbser2008unified} and collect our integrals into matrices\todo{Source is Dominics \aderdg-document.}.
-Henceforth, we drop the cell index for all quantities.
+    \sttestfunction[][v,l,n] (t) \stsource(\stpredictor)
+}}.
+\end{split}
+\end{align}
+
+Using the expansions in space and time~\pcref{eq:cell-approx-space,eq:cell-approx-space-time} results in a local systems of equations that can be solved by a fixed-point iteration scheme.
 For the space-time predictor, we introduce an iteration counter $i$.
@@
 \end{equation}
-which corresponds to a stationary guess\todo{This is an expansion only in space!}.
-\newcommand{\pleft}{\bm{L}}
-\newcommand{\prightsol}{\bm{r}}
-\newcommand{\prightpred}{\bm{w}}
-We arrive at the matrices
+which corresponds to a stationary initial guess~\cite{dumbser2008unified}.
+For an overview of possible initial guesses, see~\cite{dumbser2018efficient}.
+
+To show the computational efficiency of our scheme, we follow the approach of~\cite{dumbser2008unified} and collect our integrals into matrices\todo{Maybe mention that they are actually unrolled tensors?\\Source here is Dominics \aderdg{}-document.}.
+We arrive at the cell-local scheme
+\begin{align}
+  \label{eq:predictor-iterative}
+  \pleft \stpredictorCoeff[i+1] &= \prightsol (\ssol) - \prightpred(\stpredictorCoeff[i]) \\
+ \stpredictorCoeff[i+1] &= \pleft^{-1} \left( \prightsol (\ssol) - \prightpred(\stpredictorCoeff[i]) \right).
+\end{align}
+where we introduced the matrices
 \begin{equation}
@@
 \begin{split}
-  \pleft_{(n v l), (n' v l')} &=
+  \pleft_{(v l n), (v l' n')} &=
 \intdcell{
-  \sttestfunction[][v,l,n](\nextTime) \  \stbasis[][v,l', n'](\nextTime)
+  \sttestfunction[][v,l,n](\nextTime) \  \stbasis[][v,l',n'](\nextTime)
 }
@@
 \begin{split}
-\prightsol_{v, l,n} (\ssol) =&
+\prightsol_{v,l,n} (\ssol) &=
 \intdcell{
@@
 \intdt{\intdcell{
-  \sttestfunction[][v,l,n] (t) \stbasis[][v,l',n'](t) S_{v,l',n'}(\stpredictor[i])
+  \sttestfunction[][v,l,n] (t) \stbasis[][v,l',n'](t) \stsourceCoeff[][v,l',n'](\stpredictor[i])
 }}                             
@@
 Note here that $\prightpred$ is constant during a interation step.
-Using these matrices, we can solve for the space-time-predictor with the iterative scheme
-\begin{align}
-  \label{eq:predictor-iterative}
-  \pleft \stpredictorCoeff[i+1] &= \prightsol (\ssol) - \prightpred(\stpredictorCoeff[i]) \\
- \stpredictorCoeff[i+1] &= \pleft^{-1} \left( \prightsol (\ssol) - \prightpred(\stpredictorCoeff[i]) \right).
-\end{align}
+In practice, we precompute all integrals that contain only basis functions and their derivatives for the reference cell.
+The computation of the integrals for general space-tiem cells can then be done by \cref{eq:integration-by-substitution}.
 For details and proof of convergence for case of linear \pde{}s, see~\cite{dumbser2008unified}.
@@
 \sidetitle{Preparing for corrector}
-We then prepare the space-time-predictor for use in the corrector step.
-Due to the linearity of the Riemann solver, we can exchange time and space integration and thus only need to consider the Riemann problem for time-averaged quantities.
-% We can compute this for the space-time-predictor by
-% \begin{align}
-%   \ldots = \ldots,
-% \end{align}
-% the procedure is similar for all other quantities (Q, gradQ, fluxes).
-We then extrapolate all quantities to the boundary.
-This is needed for the Riemann solver and for the reconstruction of boundary values.
-We accomplish this by evaluating the function at the degrees of freedom on the boundary.\todo{Details}
-Thanks to the interpolating property of the nodal basis~\pcref{eq:basis-interpolating}, this reduces to a change of basis which can be precomputed on the reference element.
-We compute time-averaged and boundary extrapolated versions of the space-time-predictor, the degrees of freedom and their gradient, and the fluxes.
+It is useful to precompute time-averaged versions of our quantities.
+For example, this can be done for the space-time predictor by
+\begin{align}\label{eq:time-average}
+  \begin{split}
+  \spredictor (\bm{x}) &= \frac{1}{\Delta t} \intdt{
+\stpredictor(\bm{x}, t),
+  } \\
+\spredictor[][v,n] (\bm{x}) &= \stpredictorCoeff[][v,l,n] \quadWeight[l].
+  \end{split}
+\end{align}
+We then extrapolate the space predictor and its gradient, and the fluxes to the boundary.
+In our case we have a $\dimensions - 1$ dimensional basis for all $2 \dimensions$ faces.
+We accomplish this by evaluating the function at the degrees of freedom at the boundary.
+Due to the interpolating property of the nodal basis~\pcref{eq:basis-interpolating}, this reduces to a change of basis which can be precomputed on the reference element.
+We use the extrapolated values later for the Riemann solver and for the reconstruction of boundary values.
 
@@
 The final step of the \aderdg{}-scheme is the corrector.
-We then multiply the system \cref{eq:conservation-law-gradient} by a test function $\stestfunction{i}$ and integrate over the space-time volume $(\cell \times [t^n, t^{n+1}])$.
-We arrive yet again at the weak formulation of the \pde\
+We multiply the system \cref{eq:conservation-law-gradient} by a space test function $\stestfunction$ and integrate over the space-time control volume.
+This results, yet again, at the weak formulation of the \pde{}
 \begin{equation}
@@
 \end{equation}
-\todo{Include gradient everywhere!}
-\todo{Double check the following description}
-We now replace the solution $\bm{Q}$ with the spacetime-predictor $\stpredictor (\bm{x},t)$ and write it as a polynomial using the representation of \cref{eq:cell-approx-space,eq:cell-approx-space-time}\todo{Not all quantities are defined over time}.
+We now insert our discrete approximations and apply the basis expansions \cref{eq:cell-approx-space,eq:cell-approx-space-time} to the space-time predictor.
 The first part can be integrated by parts in time with the convenient result that only the boundary terms remain because the basis is constant in time.
@@
 }}
-\todo{Fix following equation, sum only needed due to expansion of dsol}
 \begin{align}
@@
 \label{eq:corrector}
-% \sum_{n' = 0}^{\stbasisSize}
 \left(
@@
 \left(\intdt{\intdcellb{
-      \stestfunction[][v,n] \Riemann(\spredictor[-], \spredictor[+]) \cdot \normal
+      \stestfunction[][v,n] \Riemann(\stpredictor[-], \gradient{\stpredictor[-]}; \stpredictor[+], \gradient{\stpredictor[+]}) \cdot \normal
 }}\right)
@@
 \left(\intdt{\intdcell{
-    \gradient{\stestfunction[v,n][k]} \cdot  \flux(\spredictor, \gradient{\spredictor}) % todo correct gradient?
+    \gradient{\stestfunction[][v,n]} \cdot  \stflux(\spredictor, \gradient{\spredictor})
 }}\right)
@@
 \left(\intdt{\intdcell{
-      \stestfunction[v,n][k] \source(\spredictor)
+      \stestfunction[][v,n] \stsource(\spredictor)
 }}\right)
@@
 for the coefficients $\ssolCoeff[\nextTime][v,n]$ of the new solution.
-Here $\spredictor[\pm]$ are the boundary extrapolated space-predictors.
-Again, the computational effort can be vastly reduced, by collecting the integrals in matrices and precomputing as much as possible.
-The first term is thed mass matrix with entries
+Here the superscripts $\pm$ denotes values that are extrapolated to the boundaries.
+Again, the computational effort can be vastly reduced by collecting the integrals into matrices and precomputing as much as possible.
+The first term is the mass tensor with entries
 \newcommand{\massMatrix}[1][]{\bm{M}_{#1}}
@@
   \label{eq:mass-matrix}
-  \massMatrix[n n'] = \massMatrixDef = \volume \underbrace{\quadWeight[n] \delta_{n n'}}_{\text{diagonal}}
-\end{equation}
-which is, due to the orthogonal basis \pcref{eq:basis-orthogonality}, diagonal and thus trivial to invert.
-\newcommand{\basisSize}{(N+1)^d - 1}
-\newcommand{\sumbasis}{\sum_i^{\basisSize}}
+  \massMatrix[v n n'] = \massMatrixDef = \volume \underbrace{\quadWeight[n] \delta_{n n'}}_{\text{diagonal}}
+\end{equation}
+which is, due to the orthogonal basis \pcref{eq:basis-orthogonality}, diagonal for each variable $v$ and thus trivial to invert.
 We can then insert the definition of our basis function into our equation and arrive at
@@
 b_{v,n} &= \intdcellb{
-    \stestfunction[][v,n] \Riemann(\spredictor[-], \spredictor[+]) \cdot \normal
+    \stestfunction[][v,n] \Riemann \left( \spredictor[-], \gradient{\spredictor[-]}, \gradient{\spredictor[+]} \right) \cdot \normal
 } \\
-s_n &=
+s_{v,n} &=
 \ssourceCoeff[][v,n'] \intdcell{
@@
 \end{align}
-where we evaluated the time-integrals by using the fact that our quantities are time-averaged.
+where we evaluated the time-integrals by \cref{eq:integration-by-substitution}.
+All quantities are now time-averaged~\pcref{eq:time-average} and are represented in the space basis~\pcref{eq:cell-approx-space}.
+Note that we evaluate the Riemann problem for the time-averaged space-predictor.
+This is justified by the linearity of our numerical flux~\cite{dumbser2008unified,dumbser2010arbitrary}.
 The surface integral \pcref{eq:corrector-surface} can be evaluated by summing over the contributions of the faces of each cell, which are computed by integrating the extrapolated space predictor with Gaussian quadrature.
-We can solve \cref{eq:corrector} for the new unknows $\bm{u}^{n+1}$
+Finally, we can solve \cref{eq:corrector} for the new unknows $\ssolCoeff[k+1]$
 \begin{align}\label{eq:update-predictor}
 \begin{split}
-  \bm{u}^{n+1} &= \bm{u}^{n} + \Delta t (\operatorname{update}) \\
-  \operatorname{update} &= \massMatrix^{-1} \left( \bm{a} - \bm{b} + \bm{s} \right)
+  %\bm{u}^{n+1}
+  \ssolCoeff[k+1][v]
+  &= \ssolCoeff[k][v] + \Delta t (\operatorname{update}) \\
+  \operatorname{update} &= \massMatrix[v]^{-1} \left( \bm{a}_v - \bm{b}_v + \bm{s}_v \right)
 \end{split}
@@
 \end{equation}
-In this equation, $N$ is the polynomial order and $h$ is the side-length of an element.
+In this equation $h$ is the side-length of an element.
 The penalty term depends on the maximal absolute eigenvalues of both the convective and viscous part of the equations
@@
 This Riemann solver was first published in~\cite{gassner2008discontinuous} and used for an \textsc{ader-dg} scheme in~\cite{dumbser2010arbitrary}.
+\todo{Paper only describe 1d}
 The timestep per dimension $d$ is restriced to a so-called \textsc{cfl}-type penalty
@@
  %\Delta t \leq  \text{CFL} \, \frac{\alpha(N) \, h}{\maxConvEigen + 2 \maxViscEigen \frac{1}{\alpha(N) h}}
- \Delta t \leq  \text{CFL} \, \alpha(N) \, h \sum_{i=0}^{\dimensions-1} \frac{1}{\maxConvEigen + 2 \maxViscEigen \frac{1}{\alpha(N) h}}
-\end{equation}
-with $N$ polynomial order and $h$ side length of the cell~\cite{dumbser2010arbitrary,gassner2008discontinuous}.
-\todo{Paper only describe 1d, explain evaluation of eigenvalues in direction $i$}
-The eigenvalues are evaluated for the flux Jacobian in direction $i$.
+ \Delta t \leq  \text{CFL} \, \alpha(N) \, h \sum_{i=0}^{\dimensions-1} \frac{1}{\maxConvEigen + 2 \maxViscEigen \frac{1}{\alpha(N) h}},
+\end{equation}
+where the eigenvalues are evaluated for the flux Jacobian in direction $i$~\cite{dumbser2010arbitrary,gassner2008discontinuous}..
 The constant $\alpha(N) \leq {\left( 2N+1  \right)}^{-1}$ is obtained from von Neumann analysis on a simple model problem and depends on the approximation order~\cite{dumbser2008unified}.
@@
 A simple alternative is a finite volume scheme.
-We use the \muscl{} method\todo{Cite original paper (van Leer)}, our discussion and notation follows the one in~\cite{toro2009riemann}.
+We use the \muscl{} method\todo{Cite original paper (van Leer)}.
+Our discussion and notation follows the one in~\cite{toro2009riemann}.
 Similar to~\cite{toro2009riemann} we only describe the two-dimensional case, an extension to three dimensions is straigthforward.
@@
 
-In contrast to the previous \dg{} scheme, we now only store cell averages instead of a full polynomial solution per cell.
-We achieve higher order then by a reconstruction of a linear function.
+In contrast to the previous \dg{} scheme, we now only store averages instead of a full polynomial solution for each cell.
+We achieve higher order then by reconstructing a linear function from a cell and its neighbours.
 Let $\cellAvg$ denote the averages per cell at spatial coordinates $i,j$.
@@
 We first compute the slope of the linear function connecting the cells.
-This is done by assuming a linear function per cell.
 We use the minmod slope-limiter
@@
 \end{equation}
-to avoid unphyiscally steep gradients and stabilize the system~\cite{leVeque2002finite}.
-This function then be used to compute the slopes
+to avoid unphyiscally steep gradients and to stabilize the system~\cite{leVeque2002finite}.
+This function can be used to compute the slopes
 \begin{align}\label{eq:slopes}
@@
 
-We then use the slope to reconstruct the value of the boundary.
-In the following $\cellAvg^{\pm x}$ is the average of the left ($+$) or right ($-$) cell boundary.
+We use the slope to reconstruct the value at the boundary.
+In the following, $\cellAvg^{\pm x}$ is the average of the left ($+$) or right ($-$) cell boundary.
 Similar, $\cellAvg^{\pm y}$ is the value at the top/bottom cell boundary.
@@
 \sidetitle{Time Evolution}
-To achieve second order in time, we evolve the boundary extrapolated values in time by
+To achieve second order in time, we evolve the boundary extrapolated values
 \newcommand{\evolvedCellAvg}[2][i,j]{\hat{U}_{#1}^{#2}}
@@
 \end{align}
+This results in a scheme that has an order of convergence of two for both space and time.
 
@@
 \section{Adaptive Mesh Refinement \textit{\&} Finite Volume Limiting}\label{sec:grid}
-\todo{Grid, spacefilling curve, and so on.}
-This section is concerned with two different but related concepts:%
+This section is concerned with two different but related concepts:
 finite volume limiting and adaptive mesh refinement (\amr{}).
@@
 A classical way of dealing with this problem is the usage of so called limiters.
-The idea is to smooth out steep gradients and thus eliminate discontinuities~\cite{hesthaven2008nodal}.\todo{It doesnt work like this exactly.}
+The idea is to smooth out steep gradients and thus lessen the effect of discontinuities~\cite{hesthaven2008nodal}.
 
@@
 Our discussion follows the one in~\cite{dumbser2016simple}.
-This limiting is an a posteriori limiting, which means that we first evaluate a timestep with an unlimited \textsc{ader-dg} method and then check, whether our solution is \enquote{correct}.
-In our case, we check whether the solution is a valid floating point number.
+This limiting is an a posteriori limiting, which means that we first evaluate a timestep with an unlimited \aderdg{}-method and then check, whether our solution is \enquote{correct}.
+In our case, we check whether the solution is a finite floating point number.
 We also check whether it is physically admissible with the criterion\todo{Do I actually check for pos.\ of Z?}
@@
 The recomputation starts by subdividing the infringing cell into $N_s = 2N + 1$ subcells.
-This number of subcells has the advantage that we do not loose spatial resolution and that we can use the same timestep size for both cell types.
+This number of subcells has the advantage that we do not lose spatial resolution and that we can use the same timestep size for both cell types.
 The reason for this is that the \textsc{cfl}-conditions for both schemes \pcref{eq:cfl-aderdg,eq:cfl-muscl} coincide for our choice of $N_s$.

### 2019-01-11 writing/thesis/pages/abstract.tex
Change stuff.
Update methods.

@@
 
-We use the compressible Navier-Stokes (NS) equations with heat conduction to describe the dynamics of clouds.
+We use the compressible Navier-Stokes (NS) equations with heat conduction to simulate the dynamics of clouds.
 Due to the diffusive components, the NS-Equations are not hyperbolic.
 We thus need to modify parts of the numerical scheme.
+
+Furthermore, we extend the equation set to the reactive compressible Navier-Stokes equations which include a source term that models chemical reactions.
 

### 2019-01-11 writing/thesis/chapters/results.tex
Final results for convergence test.
Add TTS AMR vs noAMR.

@@
 3 & 3.43 & 3.40 & 3.44\\
-4 & 4.44 & 4.44 & 4.67\\
-5 & 5.37 & 5.34 & 5.28\\
-6 & 5.43 & 5.42 & 5.30\\
+4 & 4.27 & 4.27 & 4.36\\
+5 & 5.00 & 5.02 & 5.08\\
+6 & 4.46 & 4.50 & 4.65\\
 \bottomrule
@@
   \centering
-  \includegraphics{thesis_convergence}
+  \includegraphics[trim=0.2cm 0.3cm 0.2cm 1.0cm, clip]{thesis_convergence}
   \caption{$L_2$-Error vs.\ Grid Size.
@@
 
+Both methods show similar results.
+The \amr{}-method took \SI{98654.1}{\s} (\SI{1}{\day} \SI{3}{\hour} \SI{24}{\minute} \SI{14}{\s})
+while the fully refined grid took \SI{169071}{\s} (\SI{1}{\day} \SI{22}{\hour} \SI{57}{\minute} \SI{51}{\s}).
+
+no \amr{}:
+\begin{verbatim}
+ 169071       info         memoryUsage    =1390 MB
+ 169071       info         number of mesh refinements      = 0
+ 169071       info         number of local recomputations  = 0
+ 169071       info         number of predictor reruns      = 1
+ 169071       info         || adapter name       || iterations   || total CPU time [t]=s         || average CPU time/g
+rid sweep [t]=s    || total real time [t]=s        || average real time/grid sweep [t]=s  || CPU time properties  || r
+eal time properties 
+ 169071       info         | MeshRefinement      |  5    |  12.58        |  2.516        |  0.593972     |  0.118794 
+    |  (2.516,#5,eps=0,max=10.48(value #1),min=0.05(value #0),+316.534%,-98.0127%,std-deviation=3.98956) [not a valid 
+averaged value yet]   |  (0.118794,#5,eps=0,max=0.420273(value #1),min=0.0371888(value #3),+253.782%,-68.6948%,std-dev
+iation=0.150842) [not a valid averaged value yet]
+ 169071       info         | FinaliseMeshRefinement      |  1    |  0.52         |  0.52         |  0.0232477    |  0.
+0232477    |  (0.52,#1,eps=0,max=0.52(value #0),min=0.52(value #0),+0%,-0%,std-deviation=3.27826e-09) [not a valid ave
+raged value yet]     |  (0.0232477,#1,eps=0,max=0.0232477(value #0),min=0.0232477(value #0),+0%,-0%,std-deviation=1.82
+031e-10) [not a valid averaged value yet]
+ 169071       info         | InitialPrediction   |  2    |  0.68         |  0.34         |  0.0334988    |  0.0167494 
+   |  (0.34,#2,eps=0,max=0.53(value #0),min=0.15(value #1),+55.8824%,-55.8824%,std-deviation=0.19) [not a valid averag
+ed value yet]        |  (0.0167494,#2,eps=0,max=0.0236651(value #0),min=0.0098337(value #1),+41.2893%,-41.2893%,std-de
+viation=0.00691571) [not a valid averaged value yet]
+ 169071       info         | FusedTimeStep       |  1428594      |  4.50835e+06          |  3.15579      |  168823 
+      |  0.118174     |  (3.15579,#1.42859e+06,eps=0,max=9.74(value #1409698),min=0.25(value #1119695),+208.639%,-92.0
+781%,std-deviation=2.72931) [not a valid averaged value yet]    |  (0.118174,#1.42859e+06,eps=0,max=0.590513(value #12
+19442),min=0.011952(value #584763),+399.697%,-89.8861%,std-deviation=0.099553) [not a valid averaged value yet]
+ 169071       info         | PredictionRerun     |  2    |  7.49         |  3.745        |  0.271615     |  0.135807 
+    |  (3.745,#2,eps=0,max=7.07(value #0),min=0.42(value #1),+88.785%,-88.785%,std-deviation=3.325) [not a valid avera
+ged value yet]        |  (0.135807,#2,eps=0,max=0.257506(value #0),min=0.0141086(value #1),+89.6113%,-89.6113%,std-dev
+iation=0.121699) [not a valid averaged value yet]
+ 169071       info         | BroadcastAndDropNeighbourMessages   |  1    |  5.92         |  5.92         |  0.216065 
+    |  0.216065     |  (5.92,#1,eps=0,max=5.92(value #0),min=5.92(value #0),+0%,-0%,std-deviation=2.67624e-08) [not a 
+valid averaged value yet]     |  (0.216065,#1,eps=0,max=0.216065(value #0),min=0.216065(value #0),+0%,-0%,std-deviatio
+n=9.81246e-10) [not a valid averaged value yet]
+\end{verbatim}
+
+\amr{}:
+\begin{verbatim}
+98654.1      info         memoryUsage    =1543 MB
+ 98654.2      info         number of mesh refinements      = 368
+ 98654.2      info         number of local recomputations  = 0
+ 98654.2      info         number of predictor reruns      = 151
+ 98654.2      info         || adapter name       || iterations   || total CPU time [t]=s         || average CPU time/g
+rid sweep [t]=s    || total real time [t]=s        || average real time/grid sweep [t]=s  || CPU time properties  || r
+eal time properties 
+ 98654.2      info         | MeshRefinement      |  5411         |  6546.45      |  1.20984      |  259.067      |  0.
+0478779    |  (1.20984,#5411,eps=0,max=2.1(value #5358),min=0.01(value #0),+73.5765%,-99.1734%,std-deviation=0.219178)
+ [not a valid averaged value yet]    |  (0.0478779,#5411,eps=0,max=0.0876097(value #3782),min=0.00762901(value #5),+82
+.9857%,-84.0657%,std-deviation=0.00892198) [not a valid averaged value yet]
+ 98654.2      info         | FinaliseMeshRefinement      |  1    |  0.13         |  0.13         |  0.00693282   |  0.
+00693282   |  (0.13,#1,eps=0,max=0.13(value #0),min=0.13(value #0),+0%,-0%,std-deviation=0) [not a valid averaged valu
+e yet]       |  (0.00693282,#1,eps=0,max=0.00693282(value #0),min=0.00693282(value #0),+0%,-0%,std-deviation=0) [not a
+ valid averaged value yet]
+ 98654.2      info         | FinaliseMeshRefinementOrLocalRollback       |  368          |  461.67       |  1.25454 
+     |  18.1743      |  0.0493866    |  (1.25454,#368,eps=0,max=1.83(value #341),min=0.67(value #0),+45.8704%,-46.5939
+%,std-deviation=0.171853) [not a valid averaged value yet]     |  (0.0493866,#368,eps=0,max=0.0706977(value #356),min=
+0.0267934(value #0),+43.1517%,-45.7475%,std-deviation=0.00629674) [not a valid averaged value yet]
+ 98654.2      info         | InitialPrediction   |  2    |  0.13         |  0.065        |  0.00881638   |  0.00440819
+   |  (0.065,#2,eps=0,max=0.07(value #0),min=0.06(value #1),+7.69231%,-7.69231%,std-deviation=0.005) [not a valid aver
+aged value yet]      |  (0.00440819,#2,eps=0,max=0.00483773(value #0),min=0.00397865(value #1),+9.74412%,-9.74412%,std
+-deviation=0.00042954) [not a valid averaged value yet]
+ 98654.2      info         | FusedTimeStep       |  1427510      |  2.54517e+06          |  1.78294      |  98033.6 
+     |  0.0686745    |  (1.78294,#1.42751e+06,eps=0,max=5.73(value #1227908),min=0.12(value #1),+221.379%,-93.2696%,st
+d-deviation=1.05159) [not a valid averaged value yet]          |  (0.0686745,#1.42751e+06,eps=0,max=0.43664(value #141
+3800),min=0.00461528(value #1),+535.811%,-93.2795%,std-deviation=0.0435888) [not a valid averaged value yet]
+ 98654.2      info         | PredictionRerun     |  302          |  403.06       |  1.33464      |  14.4881      |  0.
+0479739    |  (1.33464,#302,eps=0,max=3.26(value #240),min=0.44(value #91),+144.261%,-67.0322%,std-deviation=0.626498)
+ [not a valid averaged value yet]    |  (0.0479739,#302,eps=0,max=0.120633(value #240),min=0.0160126(value #91),+151.4
+57%,-66.6222%,std-deviation=0.0225233) [not a valid averaged value yet]
+ 98654.2      info         | BroadcastAndDropNeighbourMessages   |  369          |  518.67       |  1.40561      |  20
+.2393      |  0.0548491    |  (1.40561,#369,eps=0,max=2.56(value #349),min=0.01(value #44),+82.1274%,-99.2886%,std-dev
+iation=0.459906) [not a valid averaged value yet]    |  (0.0548491,#369,eps=0,max=0.0997589(value #349),min=0.0119344(
+value #2),+81.8789%,-78.2413%,std-deviation=0.0156193) [not a valid averaged value yet]
+ 98654.2      info         | RefinementStatusSpreading   |  1104         |  827.71       |  0.749737     |  33.2389 
+     |  0.0301077    |  (0.749737,#1104,eps=0,max=1.2(value #876),min=0.08(value #0),+60.0561%,-89.3296%,std-deviation
+=0.140828) [not a valid averaged value yet]    |  (0.0301077,#1104,eps=0,max=0.0453832(value #876),min=0.00512179(valu
+e #2),+50.7362%,-82.9884%,std-deviation=0.00527307) [not a valid averaged value yet]
+ 98654.2      info         | PredictionOrLocalRecomputation      |  736          |  498.68       |  0.677554     |  19
+.437       |  0.0264089    |  (0.677554,#736,eps=0,max=1.56(value #658),min=0.39(value #0),+130.24%,-42.44%,std-deviat
+ion=0.18267) [not a valid averaged value yet]        |  (0.0264089,#736,eps=0,max=0.112702(value #658),min=0.0157451(v
+alue #3),+326.758%,-40.3797%,std-deviation=0.00979503) [not a valid averaged value yet]
+\end{verbatim}
+
 \section{Reactive Euler \textit{\&} Navier Stokes}

### 2019-01-13 writing/thesis/chapters/conclusion.tex
Some more work.
Begin work on introduction/conclusion.

@@
-\chapter{Conclusion}
+\chapter{Conclusion}\label{chap:conclusion}
 Conclusion here.
 
+lkjl:
+\begin{itemize}
+\item We showed in \cref{sec:results-convergence} that our scheme converges for all considered orders for the Navier-Stokes equations.
+\item cfd-scenarios competitive results
+\item clouds accurate simulated
+\item The results of \cref{sec:results-tts-amr} showed, that our \amr{}-criterion is able to save a significant portion of the computational effort compared to a uniformly fine grid.
+  It is able to do this without degrading the quality of the solution, even for a scenario that contains small-scale details.
+\item Chemical reactions and limiter work for non-stiff detonations.
+\end{itemize}
+
+Future work:
+\begin{itemize}
+\item Improvement of boundary conditions for muscl
+\item Due to the \textsc{cfl}-condition,the timestep of our \aderdg{}-scheme scales quadratically with the number of grid cells.
+  Even though our \amr{}-criterion is able to reduce the number of needed cells drastically, we could get another large improvement by utilizing local, instead of global timestepping.
+\item Our implementation of the \textsc{cj}-detonation wave cannot handle realistic detonations because we do not have an implementation of stiff source terms.
+\end{itemize}
 %%% Local Variables:

### 2019-01-13 writing/thesis/chapters/introduction.tex
Begin work on introduction/conclusion.

--- 2018-11-14 writing/thesis/chapters/introduction.tex
@@
-\chapter{Introduction}
+\chapter{Introduction}\label{chap:introduction}
 We make the following contributions:
-
 \begin{itemize}
-\item We implement an \textsc{ader-dg} scheme for the compressible Navier-Stokes equations.
-\item We compare different mesh refinement strategies and evaluate their computational efficiency.
+\item In \cref{sec:navier-stokes}, we describe a coupling of the compressible Navier-Stokes equations with an advection-diffusion-reaction term for two dimensional problems.
+\item We describe an \textsc{ader-dg} (\cref{sec:ader-dg}) and \textsc{muscl}-scheme (\cref{sec:muscl}) for problems with diffusive terms.
+  In addition, we describe a combination of both methods in \cref{sec:limiting}, where we use the \textsc{muscl}-scheme in cases where the \textsc{ader-dg}-method is unstable.
+\item In \cref{sec:amr}, we introduce a mesh refinement methods that checks, whether the local cell is an outlier.
+  As indicator function we use the total variation of the discrete solution and as outlier detection we use the mean and standard variance of this function.
+  We evaluate the performance of this method using a time-to-solution test.
 \item We investigate the ability of our scheme to simulate classical fluid mechanics test scenarios correctly.
+  For this we use a convergence test with a manufactured solution, the Taylor-Green vortex (2d) and the ABC-Flow (3d).
 \item We describe the simulation of flows with a background state that is in hydrostatic equilibrium.
   This is useful for problems in atmospheric flow and for problems in meterology.
-  Furthermore, we evaluate our discretization for these scenarios.
+  Furthermore, we evaluate our discretization for these scenarios using two scenarios that simulate rising bubbles.
+\item We show that our method is capable of simulating CJ-detonation waves that are a shock which originates from a chemical reaction.
 \end{itemize}

### 2019-01-13 writing/thesis/chapters/scenarios.tex
Final results for convergence test.
Fix some parameters for scenarios and write some stuff.

@@
 \chapter{Scenarios}\label{sec:scenarios}
+\todo{Write test here to introduce the chapter!}
 Unless otherwise noted, we use the constants
@@
 We describe some scenarios in terms of the primitive variables $(\Qrho, \Qv, \pressure)$, these can be converted to the conservative variables by the definition of momentum and the definition of energy.
+
+\begin{table}[htb]
+  \centering
+\caption{Overview of scenarios}%
+\label{tab:scenarios}
+\begin{tabular}{@{}lrrrr@{}}
+\toprule
+{Name} & {Analytic Solution} & {Gravity} & {Coupling} & {Limiting}\\ \midrule
+Manufactured Solution & \cmark{} & \xmark{} & \xmark{} & \xmark{} \\
+Taylor-Green Vortex & \cmark{} & \xmark{} & \xmark{} & \xmark{} \\
+\textsc{ABC}-Flow & \cmark{} & \xmark{} & \xmark{} & \xmark{} \\
+\textsc{CJ}-Detonation & \xmark{} & \xmark{} & \cmark{} & \cmark{} \\
+Two Bubbles & \xmark{} & \cmark{} & \xmark{} & \xmark{} \\
+Cosine Bubble & \xmark{} & \cmark{} & \xmark{} & \xmark{} \\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \section{A Manufactured Solution}\label{sec:manufactured-solution}
@@
 
-\subsection{Taylor-Green Vortex}
+\sidetitle{Taylor-Green Vortex}
+%\subsection{Taylor-Green Vortex}
+An interesting testing scenario is the Taylor-Green Vortex, which exhibits a complicated flow from a simple initial condition.
+It is an analytic solution for the incompressible Navier-Stokes equations which agree relatively well with our equation set at low Mach numbers.
+We can thus use it to evaluate the performance of our solver.
+The solution is
 \begin{align}
@@
 \end{align}
-\todo{Constants!}
-$C = 100/\gamma$ \cite{dumbser2016high}
+where $C = 100/\gamma$ is a constant that governs the speed of sound and thus the Mach number~\cite{dumbser2016high}.
 
 As initial conditions we use \cref{eq:taylor-green} at time $(t = 0)$ and as boundary conditions we impose the solution and the corresponding gradients.
-Note that this solution is not exactly correct, as it assumes an incompressible flow.
-Due to the low mach number a compressible flow approaches this solution.
 
-\subsection{Lid-Driven Cavity Flow}
-The lid-driven cavity flow is a very simple testing scenario for the Navier-Stokes equations.
-We use a constant pressure of (what exactly) and a constant density $(\Qrho = 1.0)$ for the entire domain.
-The flow is then driven entirely by the boundary conditions.
+\sidetitle{Lid-Driven Cavity Flow}
+%\subsection{Lid-Driven Cavity Flow}
+The lid-driven cavity flow is another very simple testing scenario for the Navier-Stokes equations.
+The flow is driven entirely by the boundary conditions.
 They consist in four no-slip walls where the upper wall has a constant velocity $\Qv = (1.0, 0)$.
-This scenario is surprisingly difficult for an \textsc{ader-dg} scheme as the boundary conditions lead to a discontinuity at the top left corner.
-There, the velocity of the wall is piece-wise constant.
-Therefore, this scenario is a good choice to test the stability of the finite volume limiter.
+We want to simulate a flow with a Mach number of $M = 0.1$ and a Reynolds number of $\text{Re} = 100$.
+This leads us to an initial conditions of
+\begin{align}
+  \label{eq:taylor-green}
+  \begin{split}
+  \Qrho(\bm{x}) &= 1\\
+  \Qv(\bm{x}) &=  \bm{0}\\
+  \pressure(\bm{x}) &= \frac{100}{\gamma}.
+  \end{split}
+\end{align}
+% Mach = u/speed of sound
+% c^2 = gamma p
+% p = (u/M)^2 / gamma
+This scenario is surprisingly difficult for an \textsc{ader-dg} scheme as the boundary conditions can lead to a discontinuity at the corners, because the wall speed is discontinuous.
+Therefore, this scenario is a good choice to test the stability of our limited scheme.
 
-\subsection{ABC-Flow}
+\sidetitle{ABC-Flow}
+%\subsection{ABC-Flow}
 We use the Arnold–Beltrami–Childress (\textsc{abc}) flow as a simple example of a three-dimensional scenario~\cite{tavelli2016staggered}.
@@
 \end{align}
-Thus, we can simulate this without periodic boundary conditions.
 \todo{Analytical solution!}
+\todo{What is $c = 100 / \gamma$? Smaller value should be possible.}
 
-\subsection{Radialsymmetric CJ Detonation Wave}
+\sidetitle{Radialsymmetric CJ Detonation Wave}
+%\subsection{Radialsymmetric CJ Detonation Wave}
 We investigate the radialsymmetric CJ detonation wave scenario from~\cite{helzel2000modified}.
-This scenario for the reactive Euler-equations is set up in a 2D box of size $[-1, 1] \times [-1, 1]$ surrounded by free-slip walls~\pcref{eq:free-slip}.
+This scenario for the reactive Euler-equations is set up in a 2D box of size $[-1, 1] \times [-1, 1]$ surrounded by no-slip walls~\pcref{eq:no-slip}.
 Inside a circle of radius $0.3$ we have totally unburnt gas, outside of this circle we have burned gas.
@@
 We use the initial conditions
-\begin{align}
-  \begin{split}
-  \Qrho_u &= 0.887565\\
-  \Qv_u &= -0.577350
+\begin{equation}
+\begin{alignedat}{6}
+  & \Qrho_u &&= 0.887565 \qquad& \Qrho_b &= 1.4\\
+  & \Qv_u &&= -0.577350
   \begin{pmatrix}
@@
      \sin (\alpha)
-  \end{pmatrix} \\
-  \pressure_u &= 0.191709 \\
-  \QZZ_u &= 1
-  \end{split}
-\intertext{for the burnt gas and}
-\begin{split}
-  \Qrho_b &= 1.4\\
-  \Qv_b &= 0\\
-  \pressure_b &= 1 \\
-  \QZZ_b &= 0
-  \end{split}
-\end{align}
-for the unburnt gas.
+   \end{pmatrix}  \qquad& \Qv_b  &=
+   \begin{pmatrix}
+     0 \\
+     0
+   \end{pmatrix}\\
+   & \pressure_u &&=0.191709 \qquad& \pressure_b &= 1\\
+   & \QZZ_u &&= 1 \quad& \QZZ_b &= 0
+  \end{alignedat}
+\end{equation}
+where a subscript of $u$ and $b$ denotes the unburnt and burnt state respectively.
 
@@
   \gamma &= 1.4, \\
-  \Pr &= 0.7, \\
+  \Pr &= 0.75, \\
   c_v &= 2.5, \\
@@
 \end{align}
-\todo{What about viscous effects?}
+The Prandtl number is inspired from the viscous scenarios of~\cite{hidalgo2011ader}.
 
 \section{Atmospheric Scenarios}
-The scenario is described in terms of potential temperature $\potT$
+The following scenarios are all described in terms of a pertubation of a balanced atmosphere.
+This balanced atmosphere is called hydrostatic balance and is described by \cref{eq:hydrostatic-balance}.
+Before we are able to describe individual scenarios, we first need to describe how we can initialize the background atmosphere.
+
+For this, the potential temperature $\potT$
 \begin{equation}
@@
 \end{equation}
-where $p_o = \SI{10e5}{\Pa}$ is the reference pressure.
+is useful.
+The constant $p_o = \SI{10e5}{\Pa}$ is the reference pressure,.
 Solving for $T$ leads to
@@
 
+\sidetitle{Hydrostatic Wall}
 This leaves us with one problem:
-The adiabatic no-slip boundary conditions defined by~\vref{eq:no-slip} are no longer valid.
+The adiabatic free-slip boundary conditions defined by~\vref{eq:free-slip} are no longer valid.
 Concretely, we need to impose a viscous heat flux to ensure that the atmosphere stays in hydrostatic balance~\cite{giraldo2008study}
-\todo{Flux correct? Fix notation}
+\todo{Flux correct? Use viscFlux macro and energy subscript. Also only in z direction!}
 \begin{equation}
@@
   F^\text{visc} = \kappa \pdv{\overline{T}}{z} =
-\frac{R \overline{\theta} \left(\frac{\overline{p}{\left (z \right )}}{p_{0}}\right)^{\frac{R}{c_{p}}} \frac{d}{d z} \overline{p}{\left (z \right )}}{c_{p} \overline{p}{\left (z \right )}}.
+\kappa \frac{R \overline{\theta} \left(\frac{\overline{p}{\left (z \right )}}{p_{0}}\right)^{\frac{R}{c_{p}}} \frac{d}{d z} \overline{p}{\left (z \right )}}{c_{p} \overline{p}{\left (z \right )}}.
 \end{equation}
 The background pressure can be reconstructed by \cref{eq:hydrostatic-background-pressure}, its derivative is given by \cref{eq:hydrostatic-balance-potT}.
+We set the other parts of the viscous flux to zero.
 
@@
 
-\subsection{Two Bubbles}
+\sidetitle{Two Bubbles}
+%\subsection{Two Bubbles}
 As a simple test case we consider a scenario where we have one large warm air bubble in the middle, and a small cold bubble on the top.
@@
 
-\subsection{Cosine Bubble}
+\sidetitle{Cosine Bubble}
+%\subsection{Cosine Bubble}
 A similar scenario is the cosine bubble as described in~\cite{giraldo2008study}.

### 2019-01-13 writing/thesis/chapters/results.tex
Begin work on results.

--- 2019-01-08 writing/thesis/chapters/results.tex
@@
 \chapter{Results}\label{chap:results}
-\section{Convergence Test}
+\section{Convergence Test}\label{sec:results-convergence}
 \begin{table}[htb]
@@
 \item Taylor-Green High Order
+  LIC, Plot v/p ana vs.\ real
 \item ABC Medium Order
+  Plot p ana.\ vs real
+\item Lid-Driven Cavity
+  Show LIC, maybe plot over x?
 \end{itemize}
+
+\sidetitle{Taylor-Green Vortex}
+We use an \aderdg{}-scheme of order 5 with a mesh of size $27 \times 27$ cells to simulate the Taylor-Green Vortex.
+The simulation ran for \SI{10}{\s}.
+Our solution results in the expected streamlines (figure xx).
+Furthermore, we compare our results with the analytical solution for the incrompressible case.
+We achieve a small error (figure xx) for both pressure and velocity.
+The small errors are expected and not only stem from numerical inaccuracies but primarily from the fact that we simulate a compressible fluid.
+Note that the error is small over the entire domain, and not only close to the boundary, where we impose the analytical solution.
+Overall, we notice a very good agreement with the results of~\cite{dumbser2016high} and the analytical solution.
+
+\sidetitle{ABC Flow}
+We use an \aderdg{}-scheme of order 2 with a mesh consisting of $27 \times 27 \times 27$ cells to simulate the \textsc{abc}-flow.
+We run the simulation for \SI{1}{\s}.
+Figure xxx shows two slices of the simulation, figure xxx compares our numerical approximation of the pressure to the analytical solution.
+Again, our solution agrees with the analytical solution.
+
+\sidetitle{Lid-Driven Cavity}
+We use a \muscl{}-limited \aderdg{}-scheme of order 3 with a mesh of size $27 \times 27$ for the Lid-Driven Cavity.
+The streamlines agree with the expected solution but have two additional, smaller vortices in the bottom corners.
+They do not appear in DUMBER but do appear in OTHERSOLUTION.
+Additionally, we show a slice of the velocity in figure XXX, which also agrees with the solution of XXX.
+Surprisingly, the limiter was not activated at all.
+We noticed that we need the limiter when decreasing the speed of sound. 
+The results for this scenario also agree with comparable reference solutions~\cite{ghia1982high}.
+
 \section{Accurate Clouds}
@@
 \end{itemize}
-\section{Time-to-solution: AMR vs Static Mesh}
+Show bubbles, mention they look similar
+\section{Time-to-solution: AMR vs Static Mesh}\label{sec:results-tts-amr}
 To show the effectiveness of the \amr{}, we compare the time to solution of a simulation using \amr{} and another simulation with a fully refined mesh.
@@
 \begin{description}
-\item[AMR] We use a coarse mesh with just $9 \times 9$ cells.
+\item[AMR] We use a coarse mesh with just $27 \times 27$ cells.
   Each cell can be refined up to three times.
-  That is, the cells have sidelengths of roughly $\left( \SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.35}{\m} \right)$.
+  That is, the cells have sidelengths of roughly $\left(\SI{37.04}{\m}, \SI{12.35}{\m} \right)$.
   As refinement thresholds we use $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$ in \cref{eq:refinement-criterion}.
@@
 \end{description}
-We use an \aderdg{}-method of order $4$ and thus have a minimal effective resolution of ca.\ $\SI{3.09}{\m}$.
+Note, that while our \amr{} criterion is able to cope with an additional, coarser level, the current implementation in \exahype{} is unstable for this scenario.
+This is why we only report an \amr{} run with one level of dynamic refinement.
 
-To ensure a fair comparison, we ran both configurations with the same optimisation option.
+For both settings, we use an \aderdg{}-method of order $4$ and thus have a minimal effective resolution of ca.\ $\SI{3.09}{\m}$.
 
 We use a single node of the Haswell-nodes of the Supermuc (Phase 2).
-The node has two xxx\todo{name cpus} \textsc{cpu}s with 28 cores each.
+The node has two Intel® Haswell Xeon Processor E5-2697 v3 \textsc{cpu}s with 14 cores each.
 Both \textsc{cpu}s currently run on $\SI{1.8}{\GHz}$.
@@
 
+To ensure a fair comparison, we ran both configurations with the same optimisation options:
+\begin{verbatim}
+"architecture": "hsw",
+"shared_memory": {
+    "cores": 28,
+    "background_job_consumers": 6,
+    "properties_file": "sharedmemory.properties",
+    "autotuning_strategy": "dummy"
+},
+"optimisation": {
+    "fuse_algorithmic_steps": true,
+    "fuse_algorithmic_steps_factor": 0.99,
+    "spawn_predictor_as_background_thread": true,
+    "spawn_amr_background_threads": true,
+    "spawn_update_as_background_thread": true
+}
+\end{verbatim}
+for the time-to-solution test.
+For this we ran the simulation without plotters.
+The \amr{}-method took \SI{98654.1}{\s} (\SI{1}{\day} \SI{3}{\hour} \SI{24}{\minute} \SI{14}{\s})
+while the fully refined grid took \SI{169071}{\s} (\SI{1}{\day} \SI{22}{\hour} \SI{57}{\minute} \SI{51}{\s}).
+In other words, the latter method took over 71\% longer.
+
 \section{Reactive Euler \textit{\&} Navier Stokes}
+As a final benchmark, we use the reactive Navier-Stokes equations.
+We use a limiting \aderdg{}-scheme with an order of 3 and a meshsize of $81 \times 81$.
+For some runs, we use the \textsc{cmp}\todo{Refer to dmp equation (and include it)} with the following settings:
+\begin{verbatim}
+"limiter": {
+    "dmp_observables": 3,
+    "dmp_relaxation_parameter": 0.05,
+    "dmp_difference_scaling": 1e-3,
+    "helper_layers": 1
+}
+\end{verbatim}
+We use $\Qrho, \pressure$ and $\QZZ$ as \textsc{dmp} variables.
+The results for runs with and without \textsc{dmp} can be seen in figure XXX.
+Note, that oscillations diminish the results but are healed by the \textsc{dmp}-criterion.
+This scenario shows the differences between the viscous Navier-Stokes equations and the Euler equations clearly:
+The viscous effects smooth out the otherwise sharp curves.
+
+It is difficult to compare these results with our references, because they both use different settings.
+In constrast to~\cite{helzel2000modified} we use a non-stiff source term and viscous effects, \cite{hidalgo2011ader} includes viscosity but is limited to one-dimensional scenarios.
+We can see that our simulation captures the overall behaviour of the reaction similar to~\cite{helzel2000modified} while the viscous effects show the same tendency as the results from~\cite{hidalgo2011ader}.
+
+Plots-TODO:
 \begin{itemize}
-\item With viscous effects
-\item Without viscous effects  
+\item 2D: Mass fraction
+\item 2D: Pressure + Limiter
+\item 1D: Line plot pressure
+\item 1D: Line plot mass fraction
 \end{itemize}
+
 %%% Local Variables:

### 2019-01-14 writing/thesis/chapters/methods.tex
Fix typo in surface integral term of corrector.
Some more work on results, mostly plots.
Plots will be added soon, are not final yet.

@@
 b_{v,n} &= \intdcellb{
-    \stestfunction[][v,n] \Riemann \left( \spredictor[-], \gradient{\spredictor[-]}, \gradient{\spredictor[+]} \right) \cdot \normal
+    \stestfunction[][v,n] \Riemann \left( \spredictor[-], \gradient{\spredictor[-]}; \spredictor[+], \gradient{\spredictor[+]} \right) \cdot \normal
 } \\
@@
 The positivity of the pressure implies positivity of energy.
-\todo{Mention dmp if I end up using it.}
+
+\todo{Reread dmp description, fix formulas.}
+To combat the Gibbs phenomenon, we can make use of the discrete maximum principle (\textsc{dmp}).
+This criterion marks cells as troubled that have a numerical solution that is significantly higher or lower than the solutions of its neighbours.
+\begin{align}
+\min (u(y, t^{\curTime})) - \delta &\leq u^*(y, t^{\nextTime}) \leq \max (u(y, t^{\curTime})) + \delta
+%
+%
+\intertext{with tolerance}
+\delta &= \max \left(
+  \varepsilon_0, \varepsilon \left(
+         \max(u(y,t^{\curTime})) -
+         \min(u(y,t^{\curTime}))
+  \right)
+  \right)
+\end{align}
+The parameters $\varepsilon$ and $\varepsilon_0$ can be set freely.
+The former is controls by which factor the local jump can differ from its neighbourhood, the latter is needed for zero jumps~\cite{dumbser2016simple}.
+Note that this criterion is suspectible for false positives, this is especially a problem in the presence of a source term.
+\todo{Mention problems with source term?}
 
@@
   \includegraphics[scale=0.7]{thesis_aderdg_subcell_grid}
-  \caption{\label{fig:limiting-subcells}Conversion from \dg{}-dofs to fv-dofs. Image taken from~\cite{dumbser2018conformal}. }
+  \caption{\label{fig:limiting-subcells}Conversion from \dg{} degrees of freedoms to finite volume degree of freedoms. Image taken from~\cite{dumbser2018conformal}. }
 \end{figure}

### 2019-01-14 writing/thesis/chapters/results.tex
Some more work on results, mostly plots.
Plots will be added soon, are not final yet.

@@
 \chapter{Results}\label{chap:results}
-\section{Convergence Test}\label{sec:results-convergence}
-\begin{table}[htb]
-  \centering
-\caption{Numerical order of convergence of ADER-DG method}%
-\label{tab:convergence-order}
-\begin{tabular}{@{}lS[table-format=1.2]S[table-format=1.2]S[table-format=1.2]@{}}
-\toprule
-{Order} & {$L_1$} & {$L_2$} & {$L_\infty$}\\ \midrule
-1 & 2.03 & 2.00 & 1.92\\
-2 & 2.56 & 2.55 & 2.55\\
-3 & 3.43 & 3.40 & 3.44\\
-4 & 4.27 & 4.27 & 4.36\\
-5 & 5.00 & 5.02 & 5.08\\
-6 & 4.46 & 4.50 & 4.65\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[trim=0.2cm 0.3cm 0.2cm 1.0cm, clip]{thesis_convergence}
-  \caption{$L_2$-Error vs.\ Grid Size.
-    The dashed lines are the optimal order of convergence $N+1$.
-  The line is estimated by using the constant part of a linear regression fit and the ideal order as slope.}
-  \label{fig:convergence-l2-error}
-\end{figure}
+We discussed various scenarios in the previous chapter.
+In this chapter, we use them to gauge the quality of our numerical scheme.
+We start with a convergence test, followed by two standard testing scenarios.
+Next, we simulate two different cloud scenarios and check, whether our \amr{} criterion is useful.
 
 \newcommand{\error}{\operatorname{Total-Error}}
+\section{Convergence Test}\label{sec:results-convergence}
+For the convergence test, we run our manufactured solution scenario~(\cref{sec:manufactured-solution}) for all orders 1 to 6 and for number of cells $3^2, 9^2, 27^2$ and $81^2 $.
 
@@
 
-We first observe that for our approximation space $\broken$ we can split up the error as a sum over all cells
-\begin{equation}
-  \label{eq:lp-norm-broken}
- %\Vert f(\bm{x}) \Vert = \sum_{\cell[] \in \broken} \Vert f_{\cell[]} (\bm{x}) \Vert_p,
-  \error(t,p) = \sum_{\cell[] \in \broken} \error_{\cell[]}(t,p)
-\end{equation}
-where $\error_{\cell[]}$ is the error in the cell $\cell[]$.
-
+We first observe that for our approximation space $\broken$ we can split up the error as a sum over all cells.
+% \begin{equation}
+%   \label{eq:lp-norm-broken}
+%  %\Vert f(\bm{x}) \Vert = \sum_{\cell[] \in \broken} \Vert f_{\cell[]} (\bm{x}) \Vert_p,
+%   \error(t,p) = \sum_{\cell[] \in \broken} \error_{\cell[]}(t,p)
+% \end{equation}
+% where $\error_{\cell[]}$ is the error in the cell $\cell[]$.
 \todo{Describe how to integrate the error for cells, and effect of volume}
@@
  \begin{equation}
-   \Vert f_K(x) \Vert_p = \left( V \sum_{\bm{i}} \vert f(\bm{x}_i, t) - \hat{f}(\bm{x}_i, t) \vert^p w_{{\bm{i}}}  \right)^{1/p},
+%   \Vert f(\bm{x}, t) - \hat{f}(\bm{x}, t) \Vert_p^p =
+   \error(t,p) = 
+   \left( \sum_{\cell[i] \in \broken}
+    \left( V \sum_{\bm{j}} \vert f^{\cell[i]}(\bm{x}_j, t) - \hat{f}^{\cell{i}}(\bm{x}_j, t) \vert^p w_{{\bm{j}}} \right) \right)^{1/p}.
  \end{equation}
-where $V = \Delta x \Delta y$ is the volume of each two-dimensional cell.
-\todo{Use quadNodes, quadWeights and volume macro}
-The sum runs over all quadrature nodes $x_i$ with weights $w_i$.
-We use ten nodes for all orders and evaluate our solution for all nodes.
-In this way we ensure a fair comparision.
+Here, a superscript of $\cell[j]$ denotes the restriction of the function to a grid cell.
+\todo{Use quad node macro here!}
+To increase the quality of the error computation, we evaluate both analytical and approximate solution at the quadrature nodes of a scheme with 10 quadrature nodes $x_j$ with weights $w_j$.
+We then use these nodes to compute the approximation error per cell.
 
-For the limiting case of $p \to \infty$ we use the maximum point-wise error.
+For the limiting case of $p \to \infty$ we use the maximum point-wise error over all nodal points.
 
-We compute the error for the manufactured-solution scenario (\cref{sec:manufactured-solution}).
-Looking at the plot for the $L_2$ error (refer to plot here) shows that our method converges for all tested polynomial orders.
-\todo{Preliminary results used here!}
+\begin{figure}[htb]
+  \centering
+  \includegraphics[trim=0.2cm 0.3cm 0.2cm 1.0cm, clip]{thesis_convergence}
+  \caption{$L_2$-Error vs.\ Grid Size.
+    The dashed lines are the optimal order of convergence $N+1$.
+  The line is estimated by using the constant part of a linear regression fit and the ideal order as slope.}
+  \label{fig:convergence-l2-error}
+\end{figure}
+
+\begin{table}[htb]
+  \centering
+\caption{Numerical order of convergence of ADER-DG method}%
+\label{tab:convergence-order}
+\begin{tabular}{@{}lS[table-format=1.2]S[table-format=1.2]S[table-format=1.2]@{}}
+\toprule
+{Polynomial Order $N$} & {$L_1$} & {$L_2$} & {$L_\infty$}\\ \midrule
+1 & 2.03 & 2.00 & 1.92\\
+2 & 2.56 & 2.55 & 2.55\\
+3 & 3.43 & 3.40 & 3.44\\
+4 & 4.27 & 4.27 & 4.36\\
+5 & 5.00 & 5.02 & 5.08\\
+6 & 4.46 & 4.50 & 4.65\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 The size of the slope is then the convergence order.
-We can see (\cref{tab:convergence-order}) that our numerical convergence rate increases with the polynomial order.
-We do not achieve the optimal theoretical order of convergence of $N+1$.
+Looking at the plot for the $L_2$ error~(\cref{fig:convergence-l2-error}) shows that our method converges for all tested polynomial orders.
+Note that the error for the finest grid with order 6 is worse than the error for order 5.
+For all other meshsizes and orders, a higher order indicates a smaller error.
+If we compare our errors with the optimal order of convergence, we notice that while order 1 exhibits the theoretical order of convergence of 2, larger polynomial orders lead to diminishing returns.
+
+The same is true for other error norms (\cref{tab:convergence-order}).
+This means, that we in general do not achieve the optimal theoretical order of convergence.
 In~\cite{dumbser2010arbitrary}, which use a similar numerical method and the same scenario, but a different grid, \citeauthor{dumbser2010arbitrary} achieves the optimal order for most polynomial orders.
@@
 The simulation ran for \SI{10}{\s}.
-Our solution results in the expected streamlines (figure xx).
+Our solution results in the expected streamlines (\cref{fig:taylor-green-streamlines}).
 Furthermore, we compare our results with the analytical solution for the incrompressible case.
-We achieve a small error (figure xx) for both pressure and velocity.
+We achieve a small error~(\cref{fig:taylor-green-result}) for both pressure and velocity.
 The small errors are expected and not only stem from numerical inaccuracies but primarily from the fact that we simulate a compressible fluid.
 Note that the error is small over the entire domain, and not only close to the boundary, where we impose the analytical solution.
-Overall, we notice a very good agreement with the results of~\cite{dumbser2016high} and the analytical solution.
+Overall, we notice a very good agreement with both the results of~\cite{dumbser2016high} and the analytical solution.
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=0.5\textwidth]{thesis_taylor_green_stream}
+  \caption{Streamlines for Taylor-Green vortex}
+  \label{fig:taylor-green-streamlines}
+\end{figure}
+
+\begin{figure}[htb]
+  \centering
+  \begin{subfigure}[t]{0.5\textwidth}
+    \centering
+    \includegraphics{thesis_taylor_green_vel}
+    \caption{Position vs.\ velocity}
+  \end{subfigure}~%
+  \begin{subfigure}[t]{0.5\textwidth}
+    \centering
+    \includegraphics{thesis_taylor_green_pressure}
+    \caption{Position vs.\ pressure}
+  \end{subfigure}
+  \caption{\label{fig:taylor-green-result}%
+    Comparison of Taylor-Green simulation with analytical solution.
+    The former is represented by the scatter plot, the latter by the gray line.
+    Note that we only show every 5th point.}
+\end{figure}
 
@@
 Again, our solution agrees with the analytical solution.
+\todo{Velocity?}
 
 \sidetitle{Lid-Driven Cavity}
+\begin{figure}[htb]
+  \centering
+  \begin{subfigure}[t]{0.4\textwidth}
+    \centering
+    \includegraphics[width=1.2\textwidth]{thesis_lid_driven_cavity_stream}
+    \caption{\label{fig:lid-driven-cavity-streamlines}%
+      Streamlines of the cavity flow.}
+  \end{subfigure}~%
+  \begin{subfigure}[t]{0.7\textwidth}
+    \centering
+    \includegraphics{thesis_lid_driven_cavity}
+    \caption{\label{fig:lid-driven-cavity-result}%
+      Plot of velocity slices. Lines are our soulution, scatter plot shows reference solution~\cite{ghia1982high}.}
+  \end{subfigure}
+
+  \caption{Lid-Driven Cavity solution at $t=\SI{30}{\s}$}
+  \label{fig:lid-driven-cavity}
+\end{figure}
+
 We use a \muscl{}-limited \aderdg{}-scheme of order 3 with a mesh of size $27 \times 27$ for the Lid-Driven Cavity.
-The streamlines agree with the expected solution but have two additional, smaller vortices in the bottom corners.
-They do not appear in DUMBER but do appear in OTHERSOLUTION.
-Additionally, we show a slice of the velocity in figure XXX, which also agrees with the solution of XXX.
+The streamlines~(\cref{fig:lid-driven-cavity-streamlines}) agree with the expected solution but have two additional, smaller vortices in the bottom corners.
+They do not appear in~\cite{dumbser2010arbitrary} but do appear in~\cite{ghia1982high}.
+Additionally, we show the velocity along both axes in \cref{fig:lid-driven-cavity-result}.
+They too agree with the reference solution of~\cite{ghia1982high}.
+
 Surprisingly, the limiter was not activated at all.
 We noticed that we need the limiter when decreasing the speed of sound.
-The results for this scenario also agree with comparable reference solutions~\cite{ghia1982high}.
 
@@
 \end{itemize}
-Show bubbles, mention they look similar
+The cosine bubble scenario$\ldots$
+
+\sidetitle{Two Bubbles}
+We ran the second scenario with the same \amr{} settings as the first one.
+The results in (\cref{fig:results-two-bubbles}) are comparable to the reference solution~\cite{muller2010adaptive} for the first seven minutes\todo{Recreate contour plots with amr version!}.
+Note that the final plot at \SI{7}{\min} looks different in our simulation.
+A possible source for this is that we use a different equation set than~\cite{muller2010adaptive}.
+While we use a general purpose set with small modifications for atmospheric flows, they use a equation set that is fully focussed on this scenario.
+Furthermore, we use the full Navier-Stokes viscous fluxes instead of an approximation.
+
+\begin{figure}[p]
+  \vspace*{-4.5cm}
+  \thisfloatpagestyle{empty}
+  \centering
+  \begin{subfigure}{1\textwidth}
+    \centering
+    \includegraphics{thesis_two_bubbles_contour_collage.pdf}
+  \end{subfigure}
+  % \begin{subfigure}[t]{0.5\textwidth}
+  %   \centering
+  %   \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.8cm, clip]{thesis_two_bubbles_contour_t0}
+  % \end{subfigure}~%
+  % \begin{subfigure}[t]{0.5\textwidth}
+  %   \centering
+  %   \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.8cm, clip]{thesis_two_bubbles_contour_t240}
+  % \end{subfigure}
+  % \begin{subfigure}[t]{0.5\textwidth}
+  %   \centering
+  %   \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.8cm, clip]{thesis_two_bubbles_contour_t420}
+  % \end{subfigure}~%
+  % \begin{subfigure}[t]{0.5\textwidth}
+  %   \centering
+  %   \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.8cm, clip]{thesis_two_bubbles_contour_t600}
+  % \end{subfigure}
+  \vspace*{1cm}
+  \begin{subfigure}[t]{1\textwidth}
+    \centering
+    \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.0cm, clip, scale=1.2]{giraldo_results_two_bubbles}
+  \end{subfigure}
+  \caption{\label{fig:results-two-bubbles}%
+    Results for two bubble scenario.
+    On the top is our, the bottom plots are taken from~\cite{muller2010adaptive}.
+  Contour values for potential temperature pertubation are $-0.05, 0.05, 0.1, \ldots 0.45$.
+}
+\end{figure}
+
 \section{Time-to-solution: AMR vs Static Mesh}\label{sec:results-tts-amr}
@@
 
+\begin{figure}[htb]
+  \centering
+  \begin{subfigure}[t]{0.3\textwidth}
+    \centering
+    \includegraphics{thesis_detonation_euler_nodmp_pressure}
+    \caption{Pressure, Euler, no \textsc{dmp}}
+  \end{subfigure}~%
+  \begin{subfigure}[t]{0.3\textwidth}
+    \centering
+    \includegraphics{thesis_detonation_euler_dmp_pressure}
+    \caption{Pressure, Euler, \textsc{dmp}}
+  \end{subfigure}~%
+  \begin{subfigure}[t]{0.3\textwidth}
+    \centering
+    \includegraphics{thesis_detonation_ns_pressure}
+    \caption{Pressure, \textsc{NS}, no \textsc{dmp}}
+  \end{subfigure}
+
+  \begin{subfigure}[t]{0.3\textwidth}
+    \centering
+    \includegraphics{thesis_detonation_euler_nodmp_Z}
+    \caption{$Z$, Euler, no \textsc{dmp}}
+  \end{subfigure}~%
+  \begin{subfigure}[t]{0.3\textwidth}
+    \centering
+    \includegraphics{thesis_detonation_euler_dmp_Z}
+    \caption{$Z$, Euler, \textsc{dmp}}
+  \end{subfigure}~%
+  \begin{subfigure}[t]{0.3\textwidth}
+    \centering
+    \includegraphics{thesis_detonation_ns_Z}
+    \caption{$Z$, \textsc{NS}, no \textsc{dmp}}
+  \end{subfigure}
+
+  \caption{\label{fig:detonation-line-plots}%
+    Slices along the $x$-axis for our three configurations.
+    We only show one half of the slice because the scenario is symmetric.
+  }
+\end{figure}
+
 %%% Local Variables:

### 2019-01-15 writing/thesis/chapters/conclusion.tex
Update everything.

--- 2018-07-18 writing/thesis/chapters/conclusion.tex
@@
-\chapter{Conclusion}
-Conclusion here.
+\chapter{Conclusion}\label{chap:conclusion}
+We implemented a \muscl{}-limited \aderdg{}-scheme with \amr{} for the reactive Navier Stokes equations in this thesis.
+We showed that the scheme works and is capable of simulation different scenarios:\todo{Reference sections of results. Reference theory chapter. Reference implementation.}
+\begin{itemize}
+\item We showed in \cref{sec:results-convergence} that our scheme converges for all considered orders for the Navier-Stokes equations.
+\item We evaluated our method for standard \textsc{cfd} scenarios and achieved competitive results for all considered scenarios.
+  This is true for two-dimensional scenarios (Taylor-Green, Lid-Driven Cavity) and for the three-dimensional \textsc{abc}-flow.
+\item Furthermore, our method allows us to simulate flows in hydrostatic equilibrium correctly.
+\item The results of \cref{sec:results-tts-amr} showed that our \amr{}-criterion is able to save a significant portion of the computational effort compared to a uniform fine grid.
+  It is able to do this without degrading the quality of the solution, even for a scenario that contains small-scale details.
+\item Chemical reactions and limiter work for non-stiff detonations.
+\end{itemize}
+
+Of course, there are some things than can be improved and which need further work, such as:
+\begin{itemize}
+\item The current treatment of the boundary conditions is not stable for every scenarios.
+  Especially the viscous walls for the \muscl{}-method are not correct, due to limitations of \exahype{}.
+\item Due to the \textsc{cfl}-condition~\pcref{eq:cfl-aderdg,eq:cfl-muscl}, the timestep of our \aderdg{}-scheme scales quadratically with the number of grid cells.
+  Even though our \amr{}-criterion is able to reduce the number of needed cells drastically, we could get another large improvement by utilizing local timestepping.
+\item Our implementation of the \textsc{cj}-detonation wave cannot handle realistic detonations because we do not have an implementation of stiff source terms.
+  An implementation of this is straight-forward but includes changes to the space-time predictor and its initial guess, and also to the \muscl{}-scheme.
+\end{itemize}
 

### 2019-01-15 writing/thesis/chapters/introduction.tex
Update everything.

@@
 \chapter{Introduction}\label{chap:introduction}
+\todo{General boilerplate introduction (short), mention exahype}
+
 We make the following contributions:
@@
 \item In \cref{sec:navier-stokes}, we describe a coupling of the compressible Navier-Stokes equations with an advection-diffusion-reaction term for two dimensional problems.
-\item We describe an \textsc{ader-dg} (\cref{sec:ader-dg}) and \textsc{muscl}-scheme (\cref{sec:muscl}) for problems with diffusive terms.
-  In addition, we describe a combination of both methods in \cref{sec:limiting}, where we use the \textsc{muscl}-scheme in cases where the \textsc{ader-dg}-method is unstable.
+\item We describe an \aderdg{} (\cref{sec:ader-dg}) and \muscl{}-scheme (\cref{sec:muscl}) for problems with diffusive terms.
+  In addition, we describe a combination of both methods in \cref{sec:limiting}, where we use the \muscl{}-scheme in cases where the \aderdg{}-method is unstable.
 \item In \cref{sec:amr}, we introduce a mesh refinement methods that checks, whether the local cell is an outlier.
@@
 \item We investigate the ability of our scheme to simulate classical fluid mechanics test scenarios correctly.
-  For this we use a convergence test with a manufactured solution, the Taylor-Green vortex (2d) and the ABC-Flow (3d).
+  For this we use a convergence test with a manufactured solution, the Taylor-Green vortex ($2D$) and the \textsc{abc}-Flow ($3D$).
 \item We describe the simulation of flows with a background state that is in hydrostatic equilibrium.
@@
   Furthermore, we evaluate our discretization for these scenarios using two scenarios that simulate rising bubbles.
-\item We show that our method is capable of simulating CJ-detonation waves that are a shock which originates from a chemical reaction.
+\item We evaluate the simulation of a \textsc{cj}-detonation wave that are a shock which originates from a chemical reaction.
 \end{itemize}

### 2019-01-15 writing/thesis/chapters/methods.tex
Update everything.

@@
 % TODO: Extract to settings.tex
-
-% Variables and other equation stuff
-\newcommand{\Q}{\bm{Q}}
-\newcommand{\gradQ}{\gradient{\Q}}
-\newcommand{\Qrho}{\rho}
-\newcommand{\Qj}{\rho \bm{v}}
-\newcommand{\Qv}{\bm{v}}
-\newcommand{\QE}{\rho E}
-\newcommand{\QZZ}{Z} % TODO: Name?
-\newcommand{\QZ}{\rho \QZZ}
-\newcommand{\potT}{\theta}
-\newcommand{\backgroundPotT}{\overline{\theta}}
-\newcommand{\pertubationPotT}{\theta'}
-\newcommand{\stressT}{\bm{\sigma}}
-\newcommand{\pressure}{p}
-\newcommand{\maxConvEigen}[1][]{
-  \vert%
-  \lambda_c^{\text{max}}
-  \notblank{#1}{\left(#1\right)}{}
-  \vert%
-}
-\newcommand{\maxViscEigen}[1][]{
-  \vert%
-  \lambda_v^{\text{max}}
-  \notblank{#1}{\left(#1\right)}{}
-  \vert%
-}
-\newcommand{\Riemann}{\operatorname{Riemann}}
-
-% Domain
-\newcommand{\domain}{\Omega}
-\newcommand{\boundary}{\partial \domain}
-\newcommand{\broken}{\domain}
-
-% Cells
-\newcommand{\cell}[1][]{C_{#1}}
-\newcommand{\refCell}[1][]{\hat{C}_{#1}}
-\newcommand{\cellb}{\partial{} \cell}
-\newcommand{\refCellb}{\partial{} \refCell}
-
-% Basis functions
-\newcommand{\lagrange}[1][i]{\varphi_{#1}}
-\newcommand{\lagrangeRef}[1][i]{\hat{\varphi}_{#1}}
-\NewDocumentCommand{\sbasis}{ O{} O{} }{\phi^{#1}_{#2}}
-\NewDocumentCommand{\sbasisRef}{ O{} O{} }{\hat{\phi}^{#1}_{#2}} %{\hat{\sbasis[#1][#2]}}
-\NewDocumentCommand{\stbasis}{ O{} O{} }{ \psi^{#1}_{#2}}
-\NewDocumentCommand{\stbasisRef}{ O{} O{} }{\hat{\psi}^{#1}_{#2}} %{\hat{\stbasis[#1][#2]}}
-%\newcommand{\stestfunction}[1]{\sbasis[#1]}
-\NewDocumentCommand{\stestfunction}{ O{} O{} }{\sbasis[#1][#2]}
-\NewDocumentCommand{\sttestfunction}{ O{} O{} }{\stbasis[#1][#2]}
-
-% Space-time dofs
-\NewDocumentCommand{\stpredictor}{ O{} O{} }{\overline{\bm{q}}^{#1}_{#2}}
-\NewDocumentCommand{\stpredictorCoeff}{ O{} O{} }{\underline{\overline{q}}^{#1}_{#2}}
-
-\NewDocumentCommand{\stflux}{ O{} O{} }{\overline{F}^{#1}_{#2}}
-\NewDocumentCommand{\stfluxCoeff}{ O{} O{} }{\underline{\overline{F}}^{#1}_{#2}}
-
-% \NewDocumentCommand{\stsol}{ O{} O{} }{\overline{u}^{#1}_{#2}}
-% \NewDocumentCommand{\stsol}{ O{} O{} }{\underline{\overline{u}}^{#1}_{#2}}
-
-\NewDocumentCommand{\stsource}{ O{} O{} }{\overline{S}^{#1}_{#2}}
-\NewDocumentCommand{\stsourceCoeff}{ O{} O{} }{\underline{\overline{S}}^{#1}_{#2}}
-
-% Space dofs
-\NewDocumentCommand{\spredictor}{ O{} O{} }{\bm{q}^{#1}_{#2}}
-\NewDocumentCommand{\spredictorCoeff}{ O{} O{} }{\underline{q}^{#1}_{#2}}
-
-\NewDocumentCommand{\ssource}{ O{} O{} }{S^{#1}_{#2}}
-\NewDocumentCommand{\ssourceCoeff}{ O{} O{} }{\underline{S}^{#1}_{#2}}
-
-\NewDocumentCommand{\ssol}{ O{} O{} }{u^{#1}_{#2}}
-\NewDocumentCommand{\ssolCoeff}{ O{} O{} }{\underline{u}^{#1}_{#2}}
-
-\NewDocumentCommand{\sflux}{ O{} O{} }{F^{#1}_{#2}}
-\NewDocumentCommand{\sfluxCoeff}{ O{} O{} }{\underline{F}^{#1}_{#2}}
-
-% Equation parts
-\newcommand{\flux}{F}
-\newcommand{\viscFlux}{\flux^{v}}
-\newcommand{\hyperFlux}{\flux^{h}}
-%\newcommand{\source}{\bm{S}}
-\newcommand{\source}[1][]{
-  \notblank{#1}{
-S_{#1}
-}{
-\bm{S}
-}
-}
-
-% Integrals
-\newcommand{\curTime}{t^k}
-\newcommand{\nextTime}{t^{k+1}}
-\newcommand{\intdt}[1]{\int_{\curTime}^{\nextTime} #1 \dd{t}}
-\newcommand{\intdcell}[1]{\int_{\cell} #1 \dd{\bm{x}}}
-\newcommand{\intdrefcell}[1]{\int_{\refCell} #1 \dd{\hat{\bm{x}}}}
-\newcommand{\intdcellb}[1]{\int_{\cellb} #1 \dd{S}} % TODO: define boundary of cell
-\newcommand{\intdrefcellb}[1]{\int_{\refCellb} #1 \hat{\dd{S}}} % TODO: define boundary of cell
-
-% Yet to be sorted
-\newcommand{\quadWeight}[1][i]{w_{#1}}
-\newcommand{\quadNode}[1][i]{\hat{x}_{#1}}
-\newcommand{\quadNodeNd}[1][i]{\hat{\bm{x}}_{#1}}
-\newcommand{\sbasisSize}{(N+1)^\dimensions}
-\newcommand{\stbasisSize}{(N+1)^{\dimensions+1}}
-\newcommand{\normal}{\bm{n}}
-
-\newcommand{\pleft}{\bm{L}}
-\newcommand{\prightsol}{\bm{r}}
-\newcommand{\prightpred}{\bm{w}}
 
@@
 
-We conclude this chapter by a description of finite volume limiting and adaptive mesh refinement (\amr{}).
+e conclude this chapter by a description of finite volume limiting and adaptive mesh refinement (\amr{}).
 The limiting combines both numerical methods to achieve a stable, high-order method and the \amr{} allows us to perform high quality simulations with a smaller computational cost.
@@
 }
+
 Fluid motion can be described by the compressible Navier Stokes equations.
@@
 
-\newcommand{\reactionTimescale}{\tau}
-\newcommand{\reactionTemperature}{T_{\text{ign}}}
 The chemical reactive source term is
@@
 where $\reactionTimescale$ is the timescale of the reaction and $\reactionTemperature$ is the activation temperature~\cite{hidalgo2011ader,helzel2000modified}.
-
 \subsection{Boundary conditions}
@@
   \QE^0 &= \QE^i,\\
-  {(\nabla Q)}^o &= {(\nabla Q)}^i,
+  {(\nabla Q)}^o &= {(\nabla Q^o)},
   \end{split}
@@
 We then integrate the flux divergence by parts in space and insert the Riemann solver to connect with the neighbouring elements.
-Finally, we need to solve
+Finally, we need to solve\todo{Fix notation, is tensor not matrix}
 \newcommand{\massMatrixDef}{\intdcell{
@@
 \section{MUSCL-Hancock Finite Volume Scheme}\label{sec:muscl}
+\todo{Mention dubious treatment of viscous boundary terms. Or later in exahype chapter.}
 \newcommand{\cellAvg}[1][i,j]{U_{#1}}
@@
 This criterion marks cells as troubled that have a numerical solution that is significantly higher or lower than the solutions of its neighbours.
-\begin{align}
+\begin{align}\label{eq:limiting-dmp}
 \min (u(y, t^{\curTime})) - \delta &\leq u^*(y, t^{\nextTime}) \leq \max (u(y, t^{\curTime})) + \delta

### 2019-01-15 writing/thesis/chapters/results.tex
Update everything.

@@
 We first observe that for our approximation space $\broken$ we can split up the error as a sum over all cells.
-% \begin{equation}
-%   \label{eq:lp-norm-broken}
-%  %\Vert f(\bm{x}) \Vert = \sum_{\cell[] \in \broken} \Vert f_{\cell[]} (\bm{x}) \Vert_p,
-%   \error(t,p) = \sum_{\cell[] \in \broken} \error_{\cell[]}(t,p)
-% \end{equation}
-% where $\error_{\cell[]}$ is the error in the cell $\cell[]$.
-\todo{Describe how to integrate the error for cells, and effect of volume}
 We evaluate the cell-wise error with Gaussian quadrature using \cref{eq:integration-by-substitution}
@@
    \left( \sum_{\cell[i] \in \broken}
-    \left( V \sum_{\bm{j}} \vert f^{\cell[i]}(\bm{x}_j, t) - \hat{f}^{\cell{i}}(\bm{x}_j, t) \vert^p w_{{\bm{j}}} \right) \right)^{1/p}.
+    \left( V \sum_{\bm{j}} \vert f^{\cell[i]}(\quadNode[j], t) - \hat{f}^{\cell{i}}(\quadNode[j], t) \vert^p \quadWeight[j] \right) \right)^{1/p}.
  \end{equation}
 Here, a superscript of $\cell[j]$ denotes the restriction of the function to a grid cell.
-\todo{Use quad node macro here!}
-To increase the quality of the error computation, we evaluate both analytical and approximate solution at the quadrature nodes of a scheme with 10 quadrature nodes $x_j$ with weights $w_j$.
+To increase the quality of the error computation, we evaluate both analytical and approximate solution at the quadrature nodes of a scheme with 10 quadrature nodes $\quadNode[j]$ with weights $\quadWeight[j]$.
 We then use these nodes to compute the approximation error per cell.
 
-For the limiting case of $p \to \infty$ we use the maximum point-wise error over all nodal points.
+For the limiting case of $p \to \infty$ we use the maximum of the point-wise error over all nodal points.
 
@@
     The dashed lines are the optimal order of convergence $N+1$.
-  The line is estimated by using the constant part of a linear regression fit and the ideal order as slope.}
+  The line is estimated by a linear regression fit and and setting the slope to the ideal order.}
   \label{fig:convergence-l2-error}
@@
 The same is true for other error norms (\cref{tab:convergence-order}).
-This means, that we in general do not achieve the optimal theoretical order of convergence.
+This means, that we do not achieve the optimal theoretical order of convergence in general.
 In~\cite{dumbser2010arbitrary}, which use a similar numerical method and the same scenario, but a different grid, \citeauthor{dumbser2010arbitrary} achieves the optimal order for most polynomial orders.
-Some \textsc{dg}-methods of odd order only achieve a numerical convergence order of $N+\nicefrac{1}{2}$.
+Some \textsc{dg}-methods of odd order only achieve a numerical convergence order of $N+\nicefrac{1}{2}$\todo{Odd polynomial order or convergence order?}.
 
 \section{Accurate CFD}
-Show:
-\begin{itemize}
-\item Taylor-Green High Order
-  LIC, Plot v/p ana vs.\ real
-\item ABC Medium Order
-  Plot p ana.\ vs real
-\item Lid-Driven Cavity
-  Show LIC, maybe plot over x?
-\end{itemize}
+After we established that our scheme converges, we evaluate it using standard \textsc{cfd} testing scenarios that either have an analytical solution or for which we have a reference solution.
+% Show:
+% \begin{itemize}
+% \item Taylor-Green High Order
+%   LIC, Plot v/p ana vs.\ real
+% \item ABC Medium Order
+%   Plot p ana.\ vs real
+% \item Lid-Driven Cavity
+%   Show LIC, maybe plot over x?
+% \end{itemize}
 
 \sidetitle{Taylor-Green Vortex}
-We use an \aderdg{}-scheme of order 5 with a mesh of size $27 \times 27$ cells to simulate the Taylor-Green Vortex.
+We used an \aderdg{}-scheme of order 5 with a mesh of size $27 \times 27$ cells to simulate the Taylor-Green Vortex.
 The simulation ran for \SI{10}{\s}.
-Our solution results in the expected streamlines (\cref{fig:taylor-green-streamlines}).
+Our solution resulted in the expected streamlines (\cref{fig:taylor-green-streamlines}).
 Furthermore, we compare our results with the analytical solution for the incrompressible case.
@@
 Note that the error is small over the entire domain, and not only close to the boundary, where we impose the analytical solution.
-Overall, we notice a very good agreement with both the results of~\cite{dumbser2016high} and the analytical solution.
+Overall, we notice a very good agreement with both the analytical solution and the results of~\cite{dumbser2016high}.
 
@@
 \sidetitle{ABC Flow}
-We use an \aderdg{}-scheme of order 2 with a mesh consisting of $27 \times 27 \times 27$ cells to simulate the \textsc{abc}-flow.
-We run the simulation for \SI{1}{\s}.
-Figure xxx shows two slices of the simulation, figure xxx compares our numerical approximation of the pressure to the analytical solution.
-Again, our solution agrees with the analytical solution.
-\todo{Velocity?}
+\begin{figure}[htb]
+  \centering
+  \includegraphics{thesis_abc_flow_pressure}
+  \caption{\label{fig:abc-result}%
+  Pressure for the \textsc{abc}-flow.
+  Each column represents a one-dimensional slice, all other coordinates are held constant at their median value.
+  We compare the analytical solution (gray line) with our approximation (scatter plot).
+  We only show every 4th point.}
+\end{figure}
+We used an \aderdg{}-scheme of order 2 with a mesh consisting of $27 \times 27 \times 27$ cells to simulate the \textsc{abc}-flow.
+We ran the simulation for \SI{1}{\s}.
+Our solution for the pressure shows an excellent agreement~(\cref{fig:abc-result}) with the analytical solution.
+We thus shows that our implementation can also handle three-dimensional scenarios.
 
@@
 \end{figure}
-
-We use a \muscl{}-limited \aderdg{}-scheme of order 3 with a mesh of size $27 \times 27$ for the Lid-Driven Cavity.
-The streamlines~(\cref{fig:lid-driven-cavity-streamlines}) agree with the expected solution but have two additional, smaller vortices in the bottom corners.
-They do not appear in~\cite{dumbser2010arbitrary} but do appear in~\cite{ghia1982high}.
+We used a \muscl{}-limited \aderdg{}-scheme of order 3 with a mesh of size $27 \times 27$ for the Lid-Driven Cavity.
+The streamlines~(\cref{fig:lid-driven-cavity-streamlines}) agree with the expected solution but have two smaller, secondary vortices in the bottom corners.
+They do not appear in the plots of~\cite{dumbser2010arbitrary} but do appear in~\cite{ghia1982high}.
 Additionally, we show the velocity along both axes in \cref{fig:lid-driven-cavity-result}.
@@
 Surprisingly, the limiter was not activated at all.
-We noticed that we need the limiter when decreasing the speed of sound.
+We noticed that we need the limiter when we use a lower speed of sound and thus a flow with larger Mach number.
 
 \section{Accurate Clouds}
-\begin{itemize}
-\item Cosine Bubble
-\item Two Bubbles
-\end{itemize}
-The cosine bubble scenario$\ldots$
+We discussed the capabilities of our scheme regarding standard \textsc{cfd} testing scenario.
+In this section, we consider our bubble scenarios.
+\sidetitle{Cosine Bubble}
+\begin{figure}[htb]
+  \centering
+  \begin{subfigure}[t]{0.5\textwidth}
+    \centering
+    \includegraphics[scale=1.0]{thesis_cosine_bubble_contour_t700}
+    \caption{\label{fig:cosine-bubble-contour-ours}%
+      Our result}
+  \end{subfigure}~%
+  \begin{subfigure}[t]{0.5\textwidth}
+    \centering
+    \includegraphics{giraldo_results_cosine_bubble}
+    \caption{\label{fig:cosine-bubble-contour-giraldo}%
+      Figure taken from~\cite{giraldo2008study}, resolution of \SI{20}{\m}, $N = 10$, \dg{}, modified Navier-Stokes} %poly order
+  \end{subfigure}
+  \caption{\label{fig:cosine-bubble-contour}%
+    Contours for the cosine bubble results.
+    Contours are $-0.05, -0.025, \ldots 0.525$, excluding zero.
+  }
+\end{figure}
+We ran our first scenario, the cosine bubble, with an \aderdg{}-scheme of order 4 and the adaptive mesh criterion \cref{eq:refinement-criterion} with thresholds of $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$.
+Our coarsest level has $3^3$ cells, our finest level has $3^4$ cells.
+We thus have a resolution of ca.\ \SI{37.037}{\m} up to \SI{12.3457}{\m}.
+
+The coarse structure of our simulation~(\cref{fig:cosine-bubble-contour-ours}) agree with the reference solution~(\cref{fig:cosine-bubble-contour-giraldo} of~\cite{giraldo2008study} but the fine details differ.
+In contrast to us, they use a scheme of polynomial order 10 and a uniform spatial resolution of \SI{20}{\m}.
+Furthermore, we use a physical viscosity of $0.1$, which explains why we have fewer spurious details while using a lower order.
+This becomes more clear, by comparing the potential temperature pertubation.
+Our solution has a smooth distribution inside the cloud~(\cref{fig:cosine-bubble-potT-ours}) while the results of~\cite{giraldo2008study} show sharp peaks~(\cref{fig:cosine-bubble-potT-giraldo}).
+In addition, our solution does not contain negative values for the pertubation.
+Despite the different parameters, the maximum pertubation and its position matches for both results.
+
+\begin{figure}[htb]
+  \centering
+  \begin{subfigure}[t]{0.5\textwidth}
+    \centering
+    \includegraphics{thesis_cosine_bubble_pertubation}
+    \caption{\label{fig:cosine-bubble-potT-ours}%
+      Our result}
+  \end{subfigure}~%
+  \begin{subfigure}[t]{0.5\textwidth}
+    \centering
+    \includegraphics{giraldo_results_cosine_bubble_pertubation}
+    \caption{\label{fig:cosine-bubble-potT-giraldo}%
+      Figure taken from~\cite{giraldo2008study}, resolution of \SI{20}{\m}, $N = 10$, \dg{}3 uses modified Navier-Stokes} %poly order
+  \end{subfigure}
+  \caption{\label{fig:cosine-bubble-potT}%
+    $z$ vs.\ pertubation of potential temperature for the cosine bubble scenario at $t=\SI{700}{\s}$.
+  }
+\end{figure}
 
@@
 We ran the second scenario with the same \amr{} settings as the first one.
-The results in (\cref{fig:results-two-bubbles}) are comparable to the reference solution~\cite{muller2010adaptive} for the first seven minutes\todo{Recreate contour plots with amr version!}.
+The results in (\cref{fig:two-bubbles-contour}) are comparable to the reference solution~\cite{muller2010adaptive} for the first seven minutes.
 Note that the final plot at \SI{7}{\min} looks different in our simulation.
@@
   \end{subfigure}
-  % \begin{subfigure}[t]{0.5\textwidth}
-  %   \centering
-  %   \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.8cm, clip]{thesis_two_bubbles_contour_t0}
-  % \end{subfigure}~%
-  % \begin{subfigure}[t]{0.5\textwidth}
-  %   \centering
-  %   \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.8cm, clip]{thesis_two_bubbles_contour_t240}
-  % \end{subfigure}
-  % \begin{subfigure}[t]{0.5\textwidth}
-  %   \centering
-  %   \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.8cm, clip]{thesis_two_bubbles_contour_t420}
-  % \end{subfigure}~%
-  % \begin{subfigure}[t]{0.5\textwidth}
-  %   \centering
-  %   \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.8cm, clip]{thesis_two_bubbles_contour_t600}
-  % \end{subfigure}
   \vspace*{1cm}
@@
   \end{subfigure}
-  \caption{\label{fig:results-two-bubbles}%
+  \caption{\label{fig:two-bubbles-contour}%
     Results for two bubble scenario.
@@
 
-\section{Time-to-solution: AMR vs Static Mesh}\label{sec:results-tts-amr}
-To show the effectiveness of the \amr{}, we compare the time to solution of a simulation using \amr{} and another simulation with a fully refined mesh.
-In detail, we compare
+\section{AMR vs Static Mesh}\label{sec:results-tts-amr}
+To show the effectiveness of the \amr{} criterion, we compare the two settings:
 \begin{description}
@@
   As refinement thresholds we use $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$ in \cref{eq:refinement-criterion}.
+  \todo{Maybe not restate here?}
+  They are the exact same settings that we used for the bubble scenarios in the previous section.
 \item[Fine] We use a uniform grid where all cells have a sidelength corresponding to the finest mesh of the \amr{}-test case.
@@
 
-For both settings, we use an \aderdg{}-method of order $4$ and thus have a minimal effective resolution of ca.\ $\SI{3.09}{\m}$.
+\begin{figure}[htb]
+  \centering
+  \includegraphics{thesis_two_bubbles_contour_t600_noamr} 
+  \caption{\label{fig:two-bubbles-noamr-contour}%
+    Two bubbles run with fully refined mesh}
+\end{figure}
+For both settings, we used an \aderdg{}-method of order $4$ and thus have a minimal effective resolution of ca.\ $\SI{3.09}{\m}$.
+The final result for the run with the fully refined mesh (\cref{fig:two-bubbles-noamr-contour}) looks identical to the \amr{} results (\cref{fig:two-bubbles-contour}) shown in the previous section.
 
-We use a single node of the Haswell-nodes of the Supermuc (Phase 2).
-The node has two Intel® Haswell Xeon Processor E5-2697 v3 \textsc{cpu}s with 14 cores each.
-Both \textsc{cpu}s currently run on $\SI{1.8}{\GHz}$.
-We use the \tbb{} parallelisation of \exahype{}.
-To find a reasonable parameter for the number of background threads, we ran a grid search.
-We ran three \amr{} testcases for a simulation time of $\SI{1}{\min}$.
-\todo{Noisy, show results}
-The best median performance was achieved by using six background threads.
-
+\sidetitle{Time to solution test}
+We now want to compare the time to solution for both settings.
 To ensure a fair comparison, we ran both configurations with the same optimisation options:
@@
 \end{verbatim}
-for the time-to-solution test.
-For this we ran the simulation without plotters.
+We ran the simulation without plotters to focus on the performance of the numerics and the mesh refinement routines.
+
+We used a single node of the Haswell-nodes of the Supermuc (Phase 2).
+The node has two Intel® Haswell Xeon Processor E5-2697 v3 \textsc{cpu}s with 14 cores each.
+Both \textsc{cpu}s ran at a frequency of $\SI{1.8}{\GHz}$.
+
+We solely used the \tbb{} parallelisation of \exahype{}.
+To find a reasonable parameter for the number of background job consumers, we ran a grid search.
+We ran three \amr{} testcases for a simulation time of $\SI{1}{\min}$.
+The testcases were identical in setting to the aforementioned \amr{} run, but with two levels of refinement.
+\todo{Is a plot necessary here?}
+The best median performance was achieved by using six background threads.
+Note that the results were noisy and it is unclear whether the chosen number of background threads is optimal.
+
 The \amr{}-method took \SI{98654.1}{\s} (\SI{1}{\day} \SI{3}{\hour} \SI{24}{\minute} \SI{14}{\s})
@@
 
+To summarise, our \amr{} criterion saves a significant amount of computational effort while preserving the fine details of a fully refined grid.
 \section{Reactive Euler \textit{\&} Navier Stokes}
-As a final benchmark, we use the reactive Navier-Stokes equations.
-We use a limiting \aderdg{}-scheme with an order of 3 and a meshsize of $81 \times 81$.
-For some runs, we use the \textsc{cmp}\todo{Refer to dmp equation (and include it)} with the following settings:
+As a final benchmark, we used the reactive Navier-Stokes equations.
+We used a limiting \aderdg{}-scheme with an order of 3.
+For runs without viscosity we used a meshsize of $81 \times 81$, for the runs with a viscosity of $\mu = 0.01$ we used a coarser mesh consisting in $27 \times 27$ cells.
+We chose the smaller grid because our boundary conditions become unstable for finer grids.
+A reason for this might be the fact that we are unable to prescribe the gradient at the boundary in the \muscl{} implementation of \exahype{}.
+For some runs, we used the \textsc{dmp} settings
 \begin{verbatim}
@@
 \end{verbatim}
+where the \texttt{dmp\_relaxation\_parameter} refers to $\varepsilon_0$ and \texttt{dmp\_difference\_scaling} refers to $\varepsilon$ in \cref{eq:limiting-dmp}.
+The large value of $\varepsilon_0$ is necessary, as otherwise the full domain is refined.
 We use $\Qrho, \pressure$ and $\QZZ$ as \textsc{dmp} variables.
-The results for runs with and without \textsc{dmp} can be seen in figure XXX.
-Note, that oscillations diminish the results but are healed by the \textsc{dmp}-criterion.
-This scenario shows the differences between the viscous Navier-Stokes equations and the Euler equations clearly:
-The viscous effects smooth out the otherwise sharp curves.
-
-It is difficult to compare these results with our references, because they both use different settings.
-In constrast to~\cite{helzel2000modified} we use a non-stiff source term and viscous effects, \cite{hidalgo2011ader} includes viscosity but is limited to one-dimensional scenarios.
-We can see that our simulation captures the overall behaviour of the reaction similar to~\cite{helzel2000modified} while the viscous effects show the same tendency as the results from~\cite{hidalgo2011ader}.
-
-Plots-TODO:
-\begin{itemize}
-\item 2D: Mass fraction
-\item 2D: Pressure + Limiter
-\item 1D: Line plot pressure
-\item 1D: Line plot mass fraction
-\end{itemize}
-
-\begin{figure}[htb]
+\begin{figure}[tb]
   \centering
@@
 \end{figure}
+The results for runs with and without \textsc{dmp} can be seen in \cref{fig:detonation-line-plots}.
+Note, that oscillations appeared for the Euler equations unless we use the \textsc{dmp}-criterion.
+This is not the case for the Navier Stokes equations.
+This scenario shows the differences between the viscous Navier-Stokes equations and the Euler equations clearly:
+The viscous effects smooth out the otherwise sharp curves.
+
+Furthermore, they have the effect that fewer cells are limited~(\cref{fig:detonation-pressure-contour}).\todo{This is limiter status $\geq$ 3!}
+Note that the limiter activation are not symmetric which is unexpected for a radial-symmetric scenario.
+The contours for pressure and mass fraction look similar for all considered settings.
+
+It is difficult to compare these results with our references, because they both use different settings.
+In constrast to~\cite{helzel2000modified} we use a non-stiff source term and viscous effects,~\cite{hidalgo2011ader} includes viscosity but is limited to one-dimensional scenarios.
+We can see that our simulation captures the overall behaviour of the reaction similar to~\cite{helzel2000modified} while the viscous effects have a similar smoothing effect as in~\cite{hidalgo2011ader}.
+
+\begin{figure}[htb]
+  \centering
+  \begin{subfigure}[t]{1.0\textwidth}
+    \centering
+  \includegraphics[trim=0.0cm 2.0cm 0.0cm 2.6cm, clip]{thesis_detonation_contour_pressure_collage} 
+  \caption{Contour is $p = 0.5$}
+  \end{subfigure}
+  \begin{subfigure}[t]{1.0\textwidth}
+    \centering
+  \includegraphics[trim=0.0cm 2.0cm 0.0cm 2.6cm, clip]{thesis_detonation_contour_Z_collage} 
+  \caption{Contour is $Z = 0.5$}
+  \end{subfigure}
+  \caption{\label{fig:detonation-pressure-contour}%
+    Contour plots for the detonation scenario at $t=0.4$.
+    From left to right: Euler without \textsc{dmp}, Euler with \textsc{dmp}, Navier Stokes without \textsc{dmp}.
+    Red color indicates that a cell is limited.
+  }
+\end{figure}
 

### 2019-01-15 writing/thesis/chapters/scenarios.tex
Some more work on results, mostly plots.
Plots will be added soon, are not final yet.
Update everything.

@@
 \chapter{Scenarios}\label{sec:scenarios}
-\todo{Write test here to introduce the chapter!}
+\todo{Write text here to introduce the chapter!}
 Unless otherwise noted, we use the constants
@@
 As initial conditions we use \cref{eq:taylor-green} at time $(t = 0)$ and as boundary conditions we impose the solution and the corresponding gradients.
+We use a viscosity of $\mu = 0.1$.
 
@@
 We use the Arnold–Beltrami–Childress (\textsc{abc}) flow as a simple example of a three-dimensional scenario~\cite{tavelli2016staggered}.
-This scenario has, unlike the three-dimensional version of the Taylor-Green vortex, at least for the incompressible case an analytical solution
+This scenario has, unlike the three-dimensional version of the Taylor-Green vortex, an analytical solution at least for the incompressible case.
+Unlike the three-dimensional Taylor-Green vortex, the \textsc{abc}-flow has the analytical solution
 \begin{align}
@@
 \end{align}
-\todo{Analytical solution!}
-\todo{What is $c = 100 / \gamma$? Smaller value should be possible.}
+in the incompressible limit.
+Here, $C = \nicefrac{100}{\gamma}$ is an arbitrary constant.
+We use a viscosity of $\mu = 0.01$.
 
 \sidetitle{Radialsymmetric CJ Detonation Wave}
-%\subsection{Radialsymmetric CJ Detonation Wave}
 We investigate the radialsymmetric CJ detonation wave scenario from~\cite{helzel2000modified}.
-This scenario for the reactive Euler-equations is set up in a 2D box of size $[-1, 1] \times [-1, 1]$ surrounded by no-slip walls~\pcref{eq:no-slip}.
+This scenario for the reactive Navier Stokes equations is set up in a 2D box of size $[-1, 1] \times [-1, 1]$ surrounded by no-slip walls~\pcref{eq:no-slip}.
+We use the reactive source term~\pcref{eq:source-reaction,eq:reaction-model} and set the characteristic timescale to the non-stiff case $\reactionTimescale = 0.1$ and the threshold temperature to $\reactionTemperature = 0.26$.
 Inside a circle of radius $0.3$ we have totally unburnt gas, outside of this circle we have burned gas.
@@
 where a subscript of $u$ and $b$ denotes the unburnt and burnt state respectively.
+Note that this scenario is radialsymmetric.
 
@@
 The Prandtl number is inspired from the viscous scenarios of~\cite{hidalgo2011ader}.
+We consider this scenario inviscid case and for a viscosity of $\mu = 0.01$.
 
@@
 where we use the reference pressure $p_0$ as the pressure on ground level\todo{Refer to hydrostatic balance eq.\ in methods chapter!\cref{eq:hydrostatic-balance}}.
-This \textsc{ode} can be now simply solved by separation of variables.
-We then obtain after simplifying the solution
+This \textsc{ode} can be solved by separation of variables.
+After simplifying, we obtain
 \begin{align}
@@
 Finally, we compute the energy by inserting pressure and density into the equation of state~(\ref{eq:eos}).
+
+\begin{figure}[tb]
+  \centering
+  \includegraphics{thesis_hydrostatic_equilibrium}
+  \caption{\label{fig:hydrostatic-p}%
+    Hydrostatic background pressure for constants \cref{eq:atmosphere-constants}}
+\end{figure}
 
@@
 We use the following set of fluid dependent constants for these scenarios
-\begin{align}
+\begin{align}\label{eq:atmosphere-constants}
   \begin{split}
-    \gamma &= 1, \\
+    \gamma &= 1.4, \\
     \Pr &=  0.71, \\
@@
 the other constants are evaluated following \cref{eq:fluid-constants}.
+The background pressure for these constants is depicted in \cref{fig:hydrostatic-p}.
 
@@
   \pertubationPotT &= \begin{cases}
-    \nicefrac{A}{2} \left[ 1 + \cos(\pi r) \right] & r \leq a \\
-    0 & r > a
+    \nicefrac{A}{2} \left[ 1 + \cos(\pi r) \right] & r \leq a, \\
+    0 & r > a,
     \end{cases}
-\end{align},
+\end{align}
 where $r$ again is the radius to the center~\pcref{eq:radius} and constants
@@
 \end{equation}
-Similar to the previous scenario, we use a constant viscosity of $\mu = 0.1$\todo{Are we? Check~\cite{giraldo2008study}!}.
+Similar to the previous scenario, we use a constant viscosity of $\mu = 0.1$.
 

### 2019-01-17 writing/thesis/chapters/methods.tex
Cite muscl, remove matrices from aderdg description.
Matrices not necessary here, source of potential errors.

@@
  \label{eq:equation-set} 
- \begin{array}{l}
- \text{mass cons.} \\
- \text{momentum cons.} \\
- \text{energy cons.} \\
- \text{cont.\ gas} 
-\end{array}
-:
+%  \begin{array}{l}
+%  \text{mass cons.} \\
+%  \text{momentum cons.} \\
+%  \text{energy cons.} \\
+%  \text{cont.\ gas} 
+% \end{array}
+% :
 \quad
@@
 where $\Qrho$ is the density, $\Qj$ is the two or three-dimensional momentum, $\QE$ the energy density and $\QZ$ is the mass fraction of the chemical reactant.
-The chemical reactant in our case is unburnt gas.
+In our case, the chemical reactant is unburnt gas.
+The first row is the conservation of mass, the second is the conservation of momentum, the third is the conservation of energy and the fourth is the continuity of the gas.
 
@@
 where $\reactionTimescale$ is the timescale of the reaction and $\reactionTemperature$ is the activation temperature~\cite{hidalgo2011ader,helzel2000modified}.
-\subsection{Boundary conditions}
+
+\sidetitle{Boundary conditions}
 To close the system we need to impose boundary conditions.\todo{Adapt this chapter to implementation!}
 
-\sidetitle{Cauchy}
+%\sidetitle{Cauchy}
 For some scenarios we use Cauchy boundary conditions, i.e.\ we prescribe both $\Q$ and $\gradQ$ at the boundary.
@@
 
-\sidetitle{No-Slip}
+%\sidetitle{No-Slip}
 A standard wall boundary condition for viscous fluid is the no-slip condition, where we assume that the fluid has a velocity of zero near the wall.
@@
 
-\sidetitle{Free-Slip}
+%\sidetitle{Free-Slip}
 Similarly to the no-slip condition, we define the free-slip condition
@@
 \intdcell{
-  \sttestfunction[][v,l,n] (\nextTime) \stpredictor(\nextTime)
+  \sttestfunction[][v,l,n] (\nextTime) \stpredictor[i+1](\nextTime)
 }
@@
 \intdt{\intdcell{
-    \pdv{}{t} \sttestfunction[][v,l,n] (t) \stpredictor(t)
+    \pdv{}{t} \sttestfunction[][v,l,n] (t) \stpredictor[i+1](t)
 }}
@@
 \intdt{\intdcell{
-    \sttestfunction[][v,l,n] (t) \divergence{\stflux(\stpredictor, \gradient{\stpredictor})}
+    \sttestfunction[][v,l,n] (t) \divergence{\stflux(\stpredictor[i], \gradient{\stpredictor[i]})}
 }}
@@
 \intdt{\intdcell{
-    \sttestfunction[][v,l,n] (t) \stsource(\stpredictor)
+    \sttestfunction[][v,l,n] (t) \stsource(\stpredictor[i])
 }}.
@@
 \end{align}
-
+Here, we introduced the iteration counter $i$ as a subscript for the space-time predictor.
 Using the expansions in space and time~\pcref{eq:cell-approx-space,eq:cell-approx-space-time} results in a local systems of equations that can be solved by a fixed-point iteration scheme.
-For the space-time predictor, we introduce an iteration counter $i$.
 To close the iterative scheme, we set the initial value for the space-time predictor as
@@
   \label{eq:initial-guess}
-\forall l: \quad \stpredictorCoeff[i][v,l,n] = \ssolCoeff[v,n]
+\quad \stpredictorCoeff[0][v,l,n] = \ssolCoeff[][v,n]
 \end{equation}
@@
 
-To show the computational efficiency of our scheme, we follow the approach of~\cite{dumbser2008unified} and collect our integrals into matrices\todo{Maybe mention that they are actually unrolled tensors?\\Source here is Dominics \aderdg{}-document.}.
-We arrive at the cell-local scheme
-\begin{align}
-  \label{eq:predictor-iterative}
-  \pleft \stpredictorCoeff[i+1] &= \prightsol (\ssol) - \prightpred(\stpredictorCoeff[i]) \\
- \stpredictorCoeff[i+1] &= \pleft^{-1} \left( \prightsol (\ssol) - \prightpred(\stpredictorCoeff[i]) \right).
-\end{align}
-where we introduced the matrices
-\begin{equation}
-  \label{eq:matrices}
-  \pleft \in \mathbb{R}^{\NVar \stbasisSize \times \NVar \stbasisSize}, \quad
-  \prightsol \in \mathbb{R}^{\NVar \stbasisSize}, \quad
-  \prightpred \in \mathbb{R}^{\NVar \stbasisSize}
-\end{equation}
-with entries
-\begin{align}
-  \label{eq:predictor-matrices}
-\begin{split}
-  \pleft_{(v l n), (v l' n')} &=
-\intdcell{
-  \sttestfunction[][v,l,n](\nextTime) \  \stbasis[][v,l',n'](\nextTime)
-}
-\\&-
-\intdt{\intdcell{
-  \left( \pdv{}{t} \sttestfunction[][v,l,n] (t) \right) \stbasis[][v,l',n'] (t)
-}}
-\end{split}
-\\
-\begin{split}
-\prightsol_{v,l,n} (\ssol) &=
-\intdcell{
-  \sttestfunction[][v,l,n] (t) \sbasis[][v,n'] \ssolCoeff[][v,n']
-}
-\\&+
-\intdt{\intdcell{
-  \sttestfunction[][v,l,n] (t) \stbasis[][v,l',n'](t) \stsourceCoeff[][v,l',n'](\stpredictor[i])
-}}                             
-\end{split}
-  \\
-\prightpred_{v,l,n} (\stpredictor) &=
-\stfluxCoeff[][v,l',n'] (\stpredictor)
-\intdt{\intdcell{
-  \left( \gradient{\sttestfunction[][v,l,n]} \right) \stbasis[][v,l',n'](t)
-}}
-\end{align}
-Note here that $\prightpred$ is constant during a interation step.
+% To show the computational efficiency of our scheme, we follow the approach of~\cite{dumbser2008unified} and collect our integrals into matrices\todo{Maybe mention that they are actually unrolled tensors?\\Source here is Dominics \aderdg{}-document.}.
+% We arrive at the cell-local scheme
+% \begin{align}
+%    \label{eq:predictor-iterative}
+%    \pleft \stpredictorCoeff[i+1] &= \prightsol (\ssol) - \prightpred(\stpredictorCoeff[i]) \\
+%   \stpredictorCoeff[i+1] &= \pleft^{-1} \left( \prightsol (\ssol) - \prightpred(\stpredictorCoeff[i]) \right).
+%  \end{align}
+% where we introduced the matrices
+% \begin{equation}
+%   \label{eq:matrices}
+%   \pleft \in \mathbb{R}^{\NVar \stbasisSize \times \NVar \stbasisSize}, \quad
+%   \prightsol \in \mathbb{R}^{\NVar \stbasisSize}, \quad
+%   \prightpred \in \mathbb{R}^{\NVar \stbasisSize}
+% \end{equation}
+% with entries
+% \begin{align}
+%   \label{eq:predictor-matrices}
+% \begin{split}
+%   \pleft_{(v l n), (v l' n')} &=
+% \intdcell{
+%   \sttestfunction[][v,l,n](\nextTime) \  \stbasis[][v,l',n'](\nextTime)
+% }
+% \\&-
+% \intdt{\intdcell{
+%   \left( \pdv{}{t} \sttestfunction[][v,l,n] (t) \right) \stbasis[][v,l',n'] (t)
+% }}
+% \end{split}
+% \\
+% \begin{split}
+% \prightsol_{v,l,n} (\ssol) &=
+% \intdcell{
+%   \sttestfunction[][v,l,n] (t) \sbasis[][v,n'] \ssolCoeff[][v,n']
+% }
+% \\&+
+% \intdt{\intdcell{
+%   \sttestfunction[][v,l,n] (t) \stbasis[][v,l',n'](t) \stsourceCoeff[][v,l',n'](\stpredictor[i])
+% }}                             
+% \end{split}
+%   \\
+% \prightpred_{v,l,n} (\stpredictor) &=
+% \stfluxCoeff[][v,l',n'] (\stpredictor)
+% \intdt{\intdcell{
+%   \left( \gradient{\sttestfunction[][v,l,n]} \right) \stbasis[][v,l',n'](t)
+% }}
+% \end{align}
+% Note here that $\prightpred$ is constant during a interation step.
 In practice, we precompute all integrals that contain only basis functions and their derivatives for the reference cell.
@@
 \sidetitle{Preparing for corrector}
-It is useful to precompute time-averaged versions of our quantities.
+It is useful to compute time-averaged versions of our quantities directly after the predictor.
 For example, this can be done for the space-time predictor by
@@
 We multiply the system \cref{eq:conservation-law-gradient} by a space test function $\stestfunction$ and integrate over the space-time control volume.
-This results, yet again, at the weak formulation of the \pde{}
+This results, yet again, in the weak formulation of the \pde{}
 \begin{equation}
@@
 \end{equation}
-We now insert our discrete approximations and apply the basis expansions \cref{eq:cell-approx-space,eq:cell-approx-space-time} to the space-time predictor.
+We now insert our discrete approximations and apply the basis expansions~\pcref{eq:cell-approx-space,eq:cell-approx-space-time} to the space-time predictor.
 The first part can be integrated by parts in time with the convenient result that only the boundary terms remain because the basis is constant in time.
@@
 \right)
-(\ssolCoeff[t^{n+1}][v,n'] - \ssolCoeff[t^n][v,n'])
+(\ssolCoeff[\nextTime][v,n'] - \ssolCoeff[\curTime][v,n'])
 &+
@@
 Again, the computational effort can be vastly reduced by collecting the integrals into matrices and precomputing as much as possible.
-The first term is the mass tensor with entries
-\newcommand{\massMatrix}[1][]{\bm{M}_{#1}}
-\begin{equation}
-  \label{eq:mass-matrix}
-  \massMatrix[v n n'] = \massMatrixDef = \volume \underbrace{\quadWeight[n] \delta_{n n'}}_{\text{diagonal}}
-\end{equation}
-which is, due to the orthogonal basis \pcref{eq:basis-orthogonality}, diagonal for each variable $v$ and thus trivial to invert.
-We can then insert the definition of our basis function into our equation and arrive at
-\begin{align}
-  \massMatrix \left( \ssolCoeff[t+1] - \ssolCoeff[t] \right) &=
-  \Delta t \left( \bm{a} - \bm{b} + \bm{s} \right) 
-  \intertext{with}
-a_{v,n} &= \sfluxCoeff[][n'] \intdcell{
-  \sbasis[][v,n'] \gradient{\sbasis[][v,n]}(t)
-}
-\\
-\label{eq:corrector-surface}
-b_{v,n} &= \intdcellb{
-    \stestfunction[][v,n] \Riemann \left( \spredictor[-], \gradient{\spredictor[-]}; \spredictor[+], \gradient{\spredictor[+]} \right) \cdot \normal
-} \\
-s_{v,n} &=
-\ssourceCoeff[][v,n'] \intdcell{
-  \sbasis[][v,n] \sbasis[][v,n']
-}
-,
-\end{align}
-where we evaluated the time-integrals by \cref{eq:integration-by-substitution}.
-All quantities are now time-averaged~\pcref{eq:time-average} and are represented in the space basis~\pcref{eq:cell-approx-space}.
-Note that we evaluate the Riemann problem for the time-averaged space-predictor.
+Using the orthogonality of the basis functions~\pcref{eq:basis-orthogonality} on the first term, it becomes clear that the correction is a simple, explicit computation.
+% The first term is the mass tensor with entries
+% \newcommand{\massMatrix}[1][]{\bm{M}_{#1}}
+% \begin{equation}
+%   \label{eq:mass-matrix}
+%   \massMatrix[v n n'] = \massMatrixDef = \volume \underbrace{\quadWeight[n] \delta_{n n'}}_{\text{diagonal}}
+% \end{equation}
+% which is, due to the orthogonal basis \pcref{eq:basis-orthogonality}, diagonal for each variable $v$ and thus trivial to invert.
+% We can then insert the definition of our basis function into our equation and arrive at
+% \begin{align}
+%   \massMatrix \left( \ssolCoeff[t+1] - \ssolCoeff[t] \right) &=
+%   \Delta t \left( \bm{a} - \bm{b} + \bm{s} \right) 
+%   \intertext{with}
+% a_{v,n} &= \sfluxCoeff[][n'] \intdcell{
+%   \sbasis[][v,n'] \gradient{\sbasis[][v,n]}(t)
+% }
+% \\
+% \label{eq:corrector-surface}
+% b_{v,n} &= \intdcellb{
+%     \stestfunction[][v,n] \Riemann \left( \spredictor[-], \gradient{\spredictor[-]}; \spredictor[+], \gradient{\spredictor[+]} \right) \cdot \normal
+% } \\
+% s_{v,n} &=
+% \ssourceCoeff[][v,n'] \intdcell{
+%   \sbasis[][v,n] \sbasis[][v,n']
+% }
+% ,
+% \end{align}
+% where we evaluated the time-integrals by \cref{eq:integration-by-substitution}.
+% All quantities are now time-averaged~\pcref{eq:time-average} and are represented in the space basis~\pcref{eq:cell-approx-space}.
+Note that we evaluate the Riemann problem for the time-averaged space-predictor in our implementation.
 This is justified by the linearity of our numerical flux~\cite{dumbser2008unified,dumbser2010arbitrary}.
-The surface integral \pcref{eq:corrector-surface} can be evaluated by summing over the contributions of the faces of each cell, which are computed by integrating the extrapolated space predictor with Gaussian quadrature.
-Finally, we can solve \cref{eq:corrector} for the new unknows $\ssolCoeff[k+1]$
-\begin{align}\label{eq:update-predictor}
-\begin{split}
-  %\bm{u}^{n+1}
-  \ssolCoeff[k+1][v]
-  &= \ssolCoeff[k][v] + \Delta t (\operatorname{update}) \\
-  \operatorname{update} &= \massMatrix[v]^{-1} \left( \bm{a}_v - \bm{b}_v + \bm{s}_v \right)
-\end{split}
-\end{align}
-which is clearly of the form of a one-step scheme.
+% The surface integral \pcref{eq:corrector-surface} can be evaluated by summing over the contributions of the faces of each cell, which are computed by integrating the extrapolated space predictor with Gaussian quadrature.
+% Finally, we can solve \cref{eq:corrector} for the new unknows $\ssolCoeff[k+1]$
+% \begin{align}\label{eq:update-predictor}
+% \begin{split}
+%   %\bm{u}^{n+1}
+%   \ssolCoeff[k+1][v]
+%   &= \ssolCoeff[k][v] + \Delta t (\operatorname{update}) \\
+%   \operatorname{update} &= \massMatrix[v]^{-1} \left( \bm{a}_v - \bm{b}_v + \bm{s}_v \right)
+% \end{split}
+% \end{align}
+% which is clearly of the form of a one-step scheme.
 
@@
 A simple alternative is a finite volume scheme.
-We use the \muscl{} method\todo{Cite original paper (van Leer)}.
+We use the \muscl{} method\cite{vanLeer1979towards}.
 Our discussion and notation follows the one in~\cite{toro2009riemann}.
@@
 Furthermore, we assume that $\bm{f}$ is expanded in the space-basis \pcref{eq:cell-approx-space}.
-Then the total variation (\textsc{tv}) of this function is defined by\todo{Cite sth for this?}
+The total variation (\textsc{tv}) of this function is defined by
 \newcommand{\tv}{\operatorname{TV}}
@@
 \Vert_1
-,
 \end{equation}

### 2019-01-18 writing/thesis/chapters/conclusion.tex
Changes.

@@
 \item We showed in \cref{sec:results-convergence} that our scheme converges for all considered orders for the Navier-Stokes equations.
-\item We evaluated our method for standard \textsc{cfd} scenarios and achieved competitive results for all considered scenarios.
-  This is true for two-dimensional scenarios (Taylor-Green, Lid-Driven Cavity) and for the three-dimensional \textsc{abc}-flow.
+\item We evaluated our method for standard \textsc{cfd} scenarios and achieved competitive results for all used scenarios.
+  This is true for both two-dimensional scenarios (Taylor-Green, Lid-Driven Cavity) and for the three-dimensional \textsc{abc}-flow.
 \item Furthermore, our method allows us to simulate flows in hydrostatic equilibrium correctly.
@@
   Especially the viscous walls for the \muscl{}-method are not correct, due to limitations of \exahype{}.
-\item Due to the \textsc{cfl}-condition~\pcref{eq:cfl-aderdg,eq:cfl-muscl}, the timestep of our \aderdg{}-scheme scales quadratically with the number of grid cells.
+\item Due to the \textsc{cfl}-condition~\pcref{eq:cfl-aderdg,eq:cfl-muscl}, the number of timesteps of our \aderdg{}-scheme scales quadratically with the number of grid cells.
   Even though our \amr{}-criterion is able to reduce the number of needed cells drastically, we could get another large improvement by utilizing local timestepping.

### 2019-01-18 writing/thesis/chapters/implementation.tex
Changes.

@@
 \begin{itemize}
-\item Generate glue-code using a \softwareName{Python}-based Toolkit that inserts parameters into templates.\todo{Jinja? Or sth else?}
+\item Generate glue-code using a \softwareName{Python}-based Toolkit that inserts parameters into templates.
   The parameters are configured in a setting file.
@@
   \begin{itemize}
-  \item The function \funName{aderPicardLoopNonlinear} implements the space-time-predictor loop \pcref{eq:predictor-iterative}.
+  \item The function \funName{aderPicardLoopNonlinear} implements the space-time-predictor loop \pcref{eq:space-time-predictor}.
     We pass the gradient of the conserved variables to the \funName{flux} method of the \className{Solver}.
@@
     \For{$\text{cell} \in \text{cells}$}
-    \Let{curObservables}{\Call{mapGlobalObservables}{$Q_\text{cell}, \Delta \bm{x}_\text{cell}$}}
+    \Let{curObservables}{\Call{mapGlobalObservables}{$\Q_\text{cell}, \Delta \bm{x}_\text{cell}$}}
     \Let{observables}{\Call{reduceGlobalObservables}{observables, curObservables}}
@@
 For the variance of the total variation, we store the partial mean, sample variance, and count as global observables.
-\todo{Use Q, TV macro here! Same for algorithm for cell.}
 The vector $(-1, -1, 0)$ is then the base-case for the iteration~\pcref{alg:reduce-gobs} and is thus returned by the function \funName{resetGlobalObservables}.
-The method \funName{mapGlobalObservables} is defined to return $\left( \operatorname{TV} \left[ f(\bm{Q}) \right], 0, 1 \right)$, where $f(\bm{Q})$ returns an arbitary indicator value per cell.
+The method \funName{mapGlobalObservables} is defined to return $\left( \tv \left[ f(\Q) \right], 0, 1 \right)$, where $f(\Q)$ returns an arbitary indicator value per cell.
 Finally, \funName{reduceGlobalObservables} is implemented exactly as described in \cref{alg:merge-variance}.
@@
   \exahype{} already reduces the timestep size, we extend these already existing \mpi{} messages to also include the global observables \varName{\_globalObservables}.
-  For this, we changed the following methods\todo{Next and current?!} of the \dg{}-solver:
+  For this, we changed the following methods of the \dg{}-solver:
   \begin{itemize}

### 2019-01-18 writing/thesis/chapters/introduction.tex
Changes.

--- 2018-12-20 writing/thesis/chapters/introduction.tex
@@
 \chapter{Introduction}\label{chap:introduction}
+\sidetitle{Climate modeling}
+Simulations are an important part of weather and climate forecasts.
+Both types of forecasts are difficult problems that are not only limited by poor conditioning but also by lack of computational power.
+Especially in a time, where the realization of exascale supercomputers is imminent, scalable numericals model become more and more important.
+Current climate and weather models are not ready for the exascale era~\cite{schulthess2018reflecting}.
+While~\cite{schulthess2018reflecting} proposes the goal of a spatial resolution of $\SI{1}{\kilo\meter}$, simulations with resolution that is an order of magnitude coarser is the current state of the art.
+
+Of course, a finer grid is not useful, if the computational effort is too large.
+Thus, they also propose a compute rate of one simulated years per wall-clock day.
+An example of a recent supercomputing effort in this domain~\cite{fuhrer2018near} achieved a performance of 0.043 simulated years per wall-clock day with a resolution of $\SI{930}{\m}$ for a near-global simulation on the Piz Daint supercomputer.
+They used a \textsc{cosmo}-model which is based on a finite-difference approach.
+
+\sidetitle{Discontinuous Galerkin}
+The discontinuous Galerkin methods are an exciting numerical method as they are relatively easy to scale.
+In addition, they can be of high order and can perform local grid refinement~\cite{hesthaven2008nodal}.
+These advantages are only some reasons why they have been investigated for weather and climate modeling~\cite{muller2010adaptive,giraldo2008study}.
+Recently, the \ader{} discontinuous Galerkin method has been proposed by~\cite{dumbser2008unified}.
+This method is scalable and of arbitrary order in both time and space.
+With an appropiate limiter, it is also stable, even in the vicinity of discontinuities~\cite{dumbser2016simple}.
+It is thus a promising candidate for a numerical scheme for the exascale era.
+
+The goal of this thesis is to evaluate the \aderdg{} method for testing scenarios, which have been devised as benchmark examples for weather prediction~\cite{robert1993bubble,giraldo2008study}.
+We implement this with the \exahype{}-engine, which is \enquote{An Exascale Hyperbolic \pde{} Engine}.
+
 We make the following contributions:
 \begin{itemize}
-\item We implement an \textsc{ader-dg} and \textsc{muscl}-scheme for the compressible Navier-Stokes equations.
-\item We describe a coupling of the compressible Navier-Stokes equations with an advection-diffusion-reaction term for two dimensional problems.
-\item We compare different mesh refinement strategies and evaluate their computational efficiency.
-\item We investigate the ability of our scheme to simulate classical fluid mechanics test scenarios correctly.
-\item We describe the simulation of flows with a background state that is in hydrostatic equilibrium.
-  This is useful for problems in atmospheric flow and for problems in meterology.
-  Furthermore, we evaluate our discretization for these scenarios.
+\item In \cref{sec:navier-stokes}, we describe a coupling of the compressible Navier-Stokes equations for two and three dimensional problems.
+Furthermore, we adapt the equation set for scenarios with gravity.
+In addition, we present a coupling with an advection-reaction term.
+\item We describe an \aderdg{} (\cref{sec:ader-dg}) and \muscl{}-scheme (\cref{sec:muscl}) for problems with diffusive terms.
+  Moreover, we describe a combination of both methods in \cref{sec:limiting}, where we use the \muscl{}-scheme in cases where the \aderdg{}-method is unstable.
+\item In \cref{sec:amr}, we introduce an adaptive mesh refinement (\amr{}) method that checks, whether the local cell is an outlier.
+  As indicator function we use the total variation of the discrete solution and as outlier detection we use the mean and standard variance of this function.
+\item In \cref{chap:implementation} we show how we implemented our proposed method using the \exahype{}-engine.
+\item We present seven different scenarios in \cref{chap:scenarios}.
+\item We check the performance of our method in~\cref{chap:results}.
+  \begin{itemize}
+  \item In \cref{sec:results-convergence}, we perform a convergence test.
+  \item In~\cref{sec:cfd} we investigate the ability of our scheme to simulate classical fluid mechanics (\textsc{cfd}) test scenarios correctly.
+  \item We evaluate the simulation quality of atmospheric flows in \cref{sec:results-cloud}.
+  \item For these scenarios, we perform a time-to-solution test for our \amr{} strategy (\cref{sec:results-tts-amr}).
+  \item Finally, we evaluate the implementation of the reactive terms in \cref{sec:results-reactive}.
+\end{itemize}
 \end{itemize}

### 2019-01-18 writing/thesis/chapters/methods.tex
Changes.

@@
-% TODO: Extract to settings.tex
+% TODO: Extract to settings
+\newcommand{\cellAvg}[1][i,j]{U_{#1}}
+\newcommand{\sign}{\operatorname{sign}}
+\newcommand{\minmod}{\operatorname{minmod}}
+\newcommand{\slope}[2][i,j]{s^{#2}_{#1}}
+\newcommand{\gradCellAvg}[1][i,j]{\gradient{\cellAvg[#1]}}
+\newcommand{\fluxX}{\flux_x}
+\newcommand{\fluxY}{\flux_y}
 
@@
   \begin{pmatrix}
-     -\diffCoeff \gradient{\Qrho}\\
+    0\\
      \stressT (\Q, \gradQ)  \\
      \Qv \cdot \stressT (\Q, \gradQ) - \kappa \gradient{T}\\
-     -\diffCoeff \gradient{\QZ}
+     0\\
    \end{pmatrix}
@@
 
-The rows of the equation are the conservation of mass, the conservation of momentum, the conservation of energy and the continuity equation of the reactant.
+The rows of \cref{eq:equation-set} are the conservation of mass, the conservation of momentum, the conservation of energy and the continuity equation of the reactant.
 We split the flux into a hyperbolic $\hyperFlux(\Q)$ and a viscous part $\viscFlux(\Q, \gradQ)$
@@
   \label{eq:temperature}
- \frac{\pressure}{\Qrho} = RT,
+  \pressure = \Qrho R T
 \end{equation}
@@
 We further introduce the ratio of specific heats $\gamma$ and the heat fraction for constant volume $c_v$ and constant volume $c_r$.
-These constants are all fluid dependent and relate to each other and the gas constant by
+These constants are all fluid dependent and relate to each other~\cite{dumbser2010arbitrary} and the gas constant by
 \begin{align}
@@
 \end{align}
-\todo{Cite sth for this!}
 We can then compute the heat conduction coefficient
@@
 where the Prandtl number $\Pr$ depends on the fluid.
-% Sutherland's viscosity law:
-% \begin{equation}
-%   \label{eq:sutherland}
-%  \mu(T)  = \mu_0 {\left(\frac{T}{T_0}  \right)}^{\beta} \frac{T_0 + C}{T + C}
-% \end{equation}
-% with \(\beta = 1.5\), \(C = \text{const.}\), reference temperature $T_0$ and reference viscosity $\mu_=$.
-% Equal to
-% \begin{align}
-%   \lambda &= \frac{\mu_0 (T_0 + C)}{T_0^\beta} \\
-%   \mu(T) &= \lambda \frac{T^\beta}{T + C},
-% \end{align}
-% where $\lambda$ is constant for a given fluid.
-
-The maximal absolute eigenvalues for convective and viscous part in direction of a normal vector $\normal$ are
+The temperature gradient $\gradient{T}$ in terms of the conservative variables can be found in \cref{chap:appendix-pde}.
+
+The maximal absolute eigenvalues for the normal Jacobians of both convective and viscous part in direction of a normal vector $\normal$ are
 \begin{align}
   \begin{split}
-    \maxConvEigen &= \left( \partial \bm{F}/\partial \bm{Q}\right) \cdot \normal = \vert \Qv_{\normal} \vert + c,\\
-    \maxViscEigen &= \left( \partial \bm{F}/\partial \left( \nabla \bm{Q} \cdot \normal \right)\right) \cdot \normal =
-    \max \left( \frac{4}{3} \frac{\mu}{\Qrho},
-                        \frac{\gamma \mu}{\Pr \Qrho},
-                        \diffCoeff \right)
+    \maxConvEigen &=  \vert \Qv_{\normal} \vert + c,\\
+    \maxViscEigen &= \max \left( \frac{4}{3} \frac{\mu}{\Qrho},
+                        \frac{\gamma \mu}{\Pr \Qrho}\right)
   \end{split}
@@
 with velocity in direction of the normal $\Qv_{\normal}$ and speed of sound $c = \sqrt{\gamma R T }$.
+The Jacobians of both fluxes can be found in \cref{chap:appendix-pde}.
 
@@
 %\sidetitle{No-Slip}
-A standard wall boundary condition for viscous fluid is the no-slip condition, where we assume that the fluid has a velocity of zero near the wall.
-\todo{Check if this is the correct physical description!}
+A standard wall boundary condition for viscous fluid is the no-slip condition, where we assume that when the fluid is close to a wall, it has a velocity of zero relative to the wall.
 We enfore this by setting
@@
 where the quadrature weights $\quadWeight[n]$ are the product of all relevant one-dimensional quadrature weights, using the aforementioned (linearized) multi-index $n$.
-\todo{Should be correct. Is there a way to avoid this index hell, esp.\ multi-index?}
 
@@
 \label{eq:basis-orthogonality}
-&& \text{Orthogonality:} \qquad && \int_0^1 \lagrangeRef[i](x) \lagrangeRef[j](x) \dd{\hat{x}} &= \quadWeight[i] \delta_{ij},\\
+&& \text{Orthogonality:} \qquad && \int_0^1 \lagrangeRef[i](\quadNode[i]) \lagrangeRef[j](\quadNode[j]) \dd{\quadNode[j]} &= \quadWeight[i] \delta_{ij},\\
 && \qquad &&
@@
 \end{equation}
-\todo{Fix this for multiple integrals!}
 
@@
 We then integrate the flux divergence by parts in space and insert the Riemann solver to connect with the neighbouring elements.
-Finally, we need to solve\todo{Fix notation, is tensor not matrix}
+Finally, we need to solve
 \newcommand{\massMatrixDef}{\intdcell{
@@
   \label{eq:rusanov-flux}
-  \Riemann(q_h^-, \nabla q_h^-; g_h^+, \nabla q_h^+) \cdot \bm{n} =
+  \Riemann(\Q^-, \gradQ^-; \Q^+, \gradQ^+) \cdot \normal =
   \frac{1}{2} \left(
-    F(q_h^+, \nabla q_h^+) +
-    F(q_h^-, \nabla q_h^-)
+    \flux(\Q^+, \gradQ^+) +
+    \flux(\Q^-, \gradQ^-)
   \right) -
-  \frac{1}{2} s_\text{max} (q_h^+ - q_h^-),
+  \frac{1}{2} s_\text{max} (\Q^+ - \Q^-),
 \end{equation}
@@
   s_\text{max}  = \max \left(
-\maxConvEigen[q_h^-], \, \maxConvEigen[q_h^+]
+\maxConvEigen[\Q^-], \, \maxConvEigen[\Q^+]
 \right) +
 2 \eta \max \left(
-\maxViscEigen[q_h^-], \, \maxViscEigen[q_h^+]
+\maxViscEigen[\Q^-], \, \maxViscEigen[\Q^+]
 \right)
@@
 \end{equation}
-In this equation $h$ is the side-length of an element.
-The penalty term depends on the maximal absolute eigenvalues of both the convective and viscous part of the equations
+In this equation $h$ is the side-length of an element and a superscript of $\pm$ denotes the state of the right or left side.
+The penalty term depends on the maximal absolute eigenvalues of the Jacobian matrices in normal direction of both convective and viscous fluxes
 \begin{align}
   \begin{split}
-    \maxConvEigen &= \left( \partial \bm{F}/\partial \bm{Q}\right) \cdot \normal,\\
-    \maxViscEigen &= \left( \partial \bm{F}/\partial \left( \nabla \bm{Q} \cdot \normal \right)\right) \cdot \normal,
+    \maxConvEigen &= \max \quad \operatorname{eigenvalues} \left( \pdv{\flux}{\Q} \cdot \normal  \right),\\
+    \maxViscEigen &= \max \quad \operatorname{eigenvalues} \left( \pdv{\flux}{\left( \gradQ \cdot \normal \right)} \cdot \normal \right),
   \end{split}
@@
 This Riemann solver was first published in~\cite{gassner2008discontinuous} and used for an \textsc{ader-dg} scheme in~\cite{dumbser2010arbitrary}.
-\todo{Paper only describe 1d}
+\todo{Should i mention paper only describe for 1D?}
 The timestep per dimension $d$ is restriced to a so-called \textsc{cfl}-type penalty
@@
  %\Delta t \leq  \text{CFL} \, \frac{\alpha(N) \, h}{\maxConvEigen + 2 \maxViscEigen \frac{1}{\alpha(N) h}}
- \Delta t \leq  \text{CFL} \, \alpha(N) \, h \sum_{i=0}^{\dimensions-1} \frac{1}{\maxConvEigen + 2 \maxViscEigen \frac{1}{\alpha(N) h}},
-\end{equation}
-where the eigenvalues are evaluated for the flux Jacobian in direction $i$~\cite{dumbser2010arbitrary,gassner2008discontinuous}..
+ \Delta t \leq  \text{CFL} \, \alpha(N) \, h \sum_{i=1}^{\dimensions} \frac{1}{\maxConvEigen + 2 \maxViscEigen \frac{1}{\alpha(N) h}},
+\end{equation}
+where the eigenvalues are evaluated for the flux Jacobian in direction $i$~\cite{dumbser2010arbitrary,gassner2008discontinuous}.
 The constant $\alpha(N) \leq {\left( 2N+1  \right)}^{-1}$ is obtained from von Neumann analysis on a simple model problem and depends on the approximation order~\cite{dumbser2008unified}.
 We use this constant for both hyperbolic and diffusive penalty terms to ensure stability.
-For a more detailed and rigoruous stability analysis of the Riemann solver, see~\cite{gassner2008discontinuous}\todo{Is this the correct paper, or is this in the other part of the series?}.
+For a more detailed and rigoruous stability analysis of the Riemann solver, see~\cite{gassner2008discontinuous}.
 We use a value of $0.7$ for the constant $\text{CFL}$.
@@
 \section{MUSCL-Hancock Finite Volume Scheme}\label{sec:muscl}
-\todo{Mention dubious treatment of viscous boundary terms. Or later in exahype chapter.}
-\newcommand{\cellAvg}[1][i,j]{U_{#1}}
-\newcommand{\sign}{\operatorname{sign}}
-\newcommand{\minmod}{\operatorname{minmod}}
-\newcommand{\slope}[2][i,j]{s^{#2}_{#1}}
-\newcommand{\gradCellAvg}[1][i,j]{\gradient{\cellAvg[#1]}}
-\newcommand{\fluxX}{\flux_x}
-\newcommand{\fluxY}{\flux_y}
 We discussed a modern, high-order \dg{} method in the previous chapter.
@@
 Our discussion and notation follows the one in~\cite{toro2009riemann}.
-Similar to~\cite{toro2009riemann} we only describe the two-dimensional case, an extension to three dimensions is straigthforward.
-\todo{Source term!}
+Similar to~\cite{toro2009riemann} we only describe the two-dimensional case without source terms, an extension to three dimensions is straigthforward.
 
@@
 
-Finally, the update can be described by\todo{Double check update}
+Finally, the update can be described by
 \begin{align}
@@
 This results in a scheme that has an order of convergence of two for both space and time.
-
-We again use the Rusanov-type Riemann solver~\cref{eq:rusanov-flux}.
+\todo{Is this enough detail?}
+We tread the source term by a simple splitting scheme.
+The interested reader is referred to the discussions in~\cite{leVeque2002finite,toro2009riemann}.
+
+We again use the Rusanov-type Riemann solver~\pcref{eq:rusanov-flux}.
 The timestep is subject to a penalty of the form
@@
 \end{equation}
-with a constant value of CFL that is typically close to $0.7$.
+with a constant value of $\text{CFL} = 0.9$.
+
+For reasons of simplicity, we only prescribe the solution at the boundary and then estimate the gradient with \cref{eq:muscl-gradient}.
+This has the effect that the scheme becomes unstable in the case of strong viscous effect next to the boundaries.
 
@@
 In our case, we check whether the solution is a finite floating point number.
-We also check whether it is physically admissible with the criterion\todo{Do I actually check for pos.\ of Z?}
+We also check whether it is physically admissible with the criterion
 \begin{equation}
@@
   \begin{cases}
-    \text{true} & \Qrho > 0 \land \pressure > 0 \land \QZZ > 0 \\
+    \text{true} & \Qrho > 0 \land \pressure > 0 \land \QZZ \geq 0 \\
     \text{false} & \text{otherwise}.
@@
 
-\todo{Reread dmp description, fix formulas.}
-To combat the Gibbs phenomenon, we can make use of the discrete maximum principle (\textsc{dmp}).
-This criterion marks cells as troubled that have a numerical solution that is significantly higher or lower than the solutions of its neighbours.
+To combat the Gibbs phenomenon, we can make use of the discrete maximum principle (\textsc{dmp})~\cite{dumbser2016simple}.
+This criterion marks cells as troubled that have a numerical solution that is significantly higher or lower than the solutions of its neighbors, which are denoted by the set $\mathcal{N}$.
+Here, a cell is defined to be its own neighbor.
+We check for each cell $\cell[i]$ whether
 \begin{align}\label{eq:limiting-dmp}
-\min (u(y, t^{\curTime})) - \delta &\leq u^*(y, t^{\nextTime}) \leq \max (u(y, t^{\curTime})) + \delta
-%
-%
+\forall \bm{x} \in \cell[i]:  &\min_{\bm{y} \in \mathcal{N}_i} \left( \ssol[\curTime](\bm{y}, \curTime) \right) - \delta \leq \ssol[\nextTime](\bm{x}, \nextTime)
+  \leq \max_{\bm{y} \in \mathcal{N}_i} \left( \ssol(\bm{y}, \curTime) \right) + \delta
 \intertext{with tolerance}
@@
   \varepsilon_0, \varepsilon \left(
-         \max(u(y,t^{\curTime})) -
-         \min(u(y,t^{\curTime}))
+         \max_{\bm{y} \in \mathcal{N}} \left( \ssol[\curTime](\bm{x},\curTime) \right) -
+         \min_{\bm{y} \in \mathcal{N}}\left( \ssol[\curTime](\bm{x},\curTime) \right)
   \right)
@@
 \end{align}
+holds.
 The parameters $\varepsilon$ and $\varepsilon_0$ can be set freely.
-The former is controls by which factor the local jump can differ from its neighbourhood, the latter is needed for zero jumps~\cite{dumbser2016simple}.
-Note that this criterion is suspectible for false positives, this is especially a problem in the presence of a source term.
-\todo{Mention problems with source term?}
-
-If a solution violates our criterion, we recompute the last timestep for the offending cells with a limited finite volume method.
+The former controls by which factor the local jump can differ from its neighbourhood, the latter is needed for zero jumps~\cite{dumbser2016simple}.
+Note that this criterion is only a heuristic and is suspectible to false positives.
+
+If a solution violates any of our criterions, we recompute the last timestep for the offending cells with a limited finite volume method.
 In our case we use the \muscl{}-method (\cref{sec:muscl}).
@@
 \end{figure}
-\todo{Cite source for subcells~\pcref{fig:limiting-subcells}. See guidebook. NOTE THAT IT IS MODIFIED. Also: Fix size, currently font is too small}
+\todo{Cite source for subcells~\pcref{fig:limiting-subcells}. See guidebook. NOTE THAT IT IS MODIFIED. Also: Fix size, currently font is a ziny bit too small}
 
@@
 The total variation (\textsc{tv}) of this function is defined by
-\newcommand{\tv}{\operatorname{TV}}
 \begin{equation}
@@
 
-\todo{Definition for FV schemes (maybe just mapping to DG-Cells)}
 \newcommand{\gobs}{\operatorname{G}}
@@
   \begin{algorithmic}
-% TODO: Special cases 
 \Function{reduce-variance}{$\gobs_0, \gobs_1$}

### 2019-01-18 writing/thesis/chapters/results.tex
Changes.

@@
 In this chapter, we use them to gauge the quality of our numerical scheme.
-We start with a convergence test, followed by two standard testing scenarios.
-Next, we simulate two different cloud scenarios and check, whether our \amr{} criterion is useful.
+We start with a convergence test, followed by three standard testing scenarios.
+Next, we simulate two different cloud scenarios and check whether our \amr{} criterion is useful.
 
@@
 
-\section{Accurate CFD}
+\section{Accurate CFD}\label{sec:cfd}
 After we established that our scheme converges, we evaluate it using standard \textsc{cfd} testing scenarios that either have an analytical solution or for which we have a reference solution.
@@
 
-\section{Accurate Clouds}
+\section{Accurate Clouds}\label{sec:results-cloud}
 We discussed the capabilities of our scheme regarding standard \textsc{cfd} testing scenario.
@@
 
+% \begin{figure}[p]
+%   \vspace*{-4.5cm}
+%   \thisfloatpagestyle{empty}
+%   \centering
+%   \begin{subfigure}{1\textwidth}
+%     \centering
+%     \includegraphics{thesis_two_bubbles_contour_collage.pdf}
+%   \end{subfigure}
+%   \vspace*{1cm}
+%   \begin{subfigure}[t]{1\textwidth}
+%     \centering
+%     \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.0cm, clip, scale=1.2]{giraldo_results_two_bubbles}
+%   \end{subfigure}
+%   \caption{\label{fig:two-bubbles-contour}%
+%     Results for two bubble scenario.
+%     On the top is our, the bottom plots are taken from~\cite{muller2010adaptive}.
+%   Contour values for potential temperature pertubation are $-0.05, 0.05, 0.1, \ldots 0.45$.
+% }
+% \end{figure}
 \begin{figure}[p]
-  \vspace*{-4.5cm}
   \thisfloatpagestyle{empty}
   \centering
-  \begin{subfigure}{1\textwidth}
+  \begin{subfigure}[t]{0.5\textwidth}
     \centering
-    \includegraphics{thesis_two_bubbles_contour_collage.pdf}
-  \end{subfigure}
-  \vspace*{1cm}
-  \begin{subfigure}[t]{1\textwidth}
+  \includegraphics[trim={0cm 0cm 6cm 0cm},clip]{thesis_two_bubbles_contour_collage_comparison} 
+  \caption{Our \amr{} solution.}
+  \end{subfigure}~%
+  \begin{subfigure}[t]{0.5\textwidth}
     \centering
-    \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.0cm, clip, scale=1.2]{giraldo_results_two_bubbles}
+  % Without z axis on right \includegraphics[trim={8.16cm 0cm 0cm 0cm},clip]{thesis_two_bubbles_contour_collage_comparison} 
+  \includegraphics[trim={7.4cm 0cm 0cm 0cm},clip]{thesis_two_bubbles_contour_collage_comparison} 
+  \caption{Reference solution from~\cite{muller2010adaptive}.}
   \end{subfigure}
   \caption{\label{fig:two-bubbles-contour}%
-    Results for two bubble scenario.
-    On the top is our, the bottom plots are taken from~\cite{muller2010adaptive}.
+     Contours of the potential temperature for two bubble scenario.
+     On the left is our solution, the right plots are taken from~\cite{muller2010adaptive}.
+     We modified the arrangement of the reference plots and the placement of its axes. 
    Contour values for potential temperature pertubation are $-0.05, 0.05, 0.1, \ldots 0.45$.
@@
 The final result for the run with the fully refined mesh (\cref{fig:two-bubbles-noamr-contour}) looks identical to the \amr{} results (\cref{fig:two-bubbles-contour}) shown in the previous section.
+Note that the \amr{} criterion manages to track the bubble correctly~(\cref{fig:two-bubbles-amr-grid}) and is introduces only small errors~(\cref{fig:two-bubbles-amr-error})\todo{Increase font size a bit more}.
+
+\begin{figure}[htb]
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{thesis_two_bubbles_amr_grid} 
+    \caption{\label{fig:two-bubbles-amr-grid}%
+      Potential temperature of \amr{} solution.}
+\end{subfigure}\qquad%
+\begin{subfigure}[t]{0.45\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{thesis_two_bubbles_amr_error} 
+    \caption{\label{fig:two-bubbles-amr-error}%
+      Potential temperature of fully refined solution minus \amr{} solution.}
+\end{subfigure}
+
+  \caption{%
+    \amr{}-grid at $t = \SI{700}{\s}$ for the two bubbles scenario.}
+\end{figure}
 
@@
 "architecture": "hsw",
-"shared_memory": {
+"shared_memory":
+
     "cores": 28,
@@
 The testcases were identical in setting to the aforementioned \amr{} run, but with two levels of refinement.
-\todo{Is a plot necessary here?}
 The best median performance was achieved by using six background threads.
@@
 
-To summarise, our \amr{} criterion saves a significant amount of computational effort while preserving the fine details of a fully refined grid.
-\section{Reactive Euler \textit{\&} Navier Stokes}
+To summarise, our \amr{} criterion saved a significant amount of computational effort while preserving the fine details of a fully refined grid.
+\section{Reactive Euler \textit{\&} Navier Stokes}\label{sec:results-reactive}
 As a final benchmark, we used the reactive Navier-Stokes equations.
@@
   \end{subfigure}
-
   \caption{\label{fig:detonation-line-plots}%
@@
 
-Furthermore, they have the effect that fewer cells are limited~(\cref{fig:detonation-pressure-contour}).\todo{This is limiter status $\geq$ 3!}
+Furthermore, they have the effect that fewer cells are limited~(\cref{fig:detonation-pressure-contour}).
 Note that the limiter activation are not symmetric which is unexpected for a radial-symmetric scenario.
@@
 In constrast to~\cite{helzel2000modified} we use a non-stiff source term and viscous effects,~\cite{hidalgo2011ader} includes viscosity but is limited to one-dimensional scenarios.
-We can see that our simulation captures the overall behaviour of the reaction similar to~\cite{helzel2000modified} while the viscous effects have a similar smoothing effect as in~\cite{hidalgo2011ader}.
+Comparing with \cref{fig:detonation-contour-reference} we can see that our simulation captures the overall behaviour of the reaction similar to the stiff simulations of~\cite{helzel2000modified}.
+The viscous effects have a similar smoothing effect as in~\cite{hidalgo2011ader}.
 
@@
 
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.33\textwidth]{leveque_detonation_mass_fraction}
+    \caption{\label{fig:detonation-contour-reference}Reference solution for mass fraction with stiff source.
+      Image taken from~\cite{helzel2000modified}.}
+\end{figure}
+
 %%% Local Variables:

### 2019-01-18 writing/thesis/chapters/scenarios.tex
Changes.

@@
-\chapter{Scenarios}\label{sec:scenarios}
-\todo{Write text here to introduce the chapter!}
-Unless otherwise noted, we use the constants
-\begin{align}
-\begin{split}
-  \gamma &= 1.4, \\
-  \Pr &= 0.7, \\
-  c_v &= 1.0
-\end{split}
-\end{align}
-The other constants follow from the definition of \cref{eq:fluid-constants}.
-
-We describe some scenarios in terms of the primitive variables $(\Qrho, \Qv, \pressure)$, these can be converted to the conservative variables by the definition of momentum and the definition of energy.
-
+\chapter{Scenarios}\label{chap:scenarios}
 \begin{table}[htb]
@@
 {Name} & {Analytic Solution} & {Gravity} & {Coupling} & {Limiting}\\ \midrule
-Manufactured Solution & \cmark{} & \xmark{} & \xmark{} & \xmark{} \\
-Taylor-Green Vortex & \cmark{} & \xmark{} & \xmark{} & \xmark{} \\
-\textsc{ABC}-Flow & \cmark{} & \xmark{} & \xmark{} & \xmark{} \\
-\textsc{CJ}-Detonation & \xmark{} & \xmark{} & \cmark{} & \cmark{} \\
-Two Bubbles & \xmark{} & \cmark{} & \xmark{} & \xmark{} \\
-Cosine Bubble & \xmark{} & \cmark{} & \xmark{} & \xmark{} \\
+Manufactured Solution~\cite{dumbser2010arbitrary} & \cmark{} & \xmark{} & \xmark{} & \xmark{} \\
+Taylor-Green Vortex~\cite{dumbser2016high} & \cmark{} & \xmark{} & \xmark{} & \xmark{} \\
+Lid Driven Cavity~\cite{fambri2017space} & \cmark{} & \xmark{} & \xmark{} & \cmark{} \\
+\textsc{ABC}-Flow~\cite{tavelli2016staggered} & \cmark{} & \xmark{} & \xmark{} & \xmark{} \\
+Two Bubbles~\cite{robert1993bubble,muller2010adaptive} & \xmark{} & \cmark{} & \xmark{} & \xmark{} \\
+Cosine Bubble~\cite{giraldo2008study} & \xmark{} & \cmark{} & \xmark{} & \xmark{} \\
+\textsc{CJ}-Detonation~\cite{helzel2000modified,hidalgo2011ader} & \xmark{} & \xmark{} & \cmark{} & \cmark{} \\
 \bottomrule
 \end{tabular}
-\end{table}
+\end{table}%
+In this chapter, we introduce various scenarios that we will later use to to evalute the performance of our method.
+\Cref{tab:scenarios} shows an overview of our scenarios.
+They all have a different focus:
+\begin{itemize}
+\item The manufactured solution is an exact solution for our equation set and can be thus used to reliably evaluate the quality of our implementation.
+\item The Taylor-Green vortex, the \textsc{abc}-flow and the lid-driven cavity flow are standard \textsc{cfd} testing scenarios for which we have a reference result.
+\item The bubble scenarios are simple examples for flows over a realistic background atmosphere.  
+\item The \textsc{cj}-detonation wave uses the reactive advection term to model a detonation.
+\end{itemize}
+
+Unless otherwise noted, we use the constants
+\begin{equation}
+  \gamma = 1.4, \quad \Pr = 0.7, \quad c_v = 1.0.
+\end{equation}
+The other constants follow from the definition of \cref{eq:fluid-constants}.
+
+We describe some scenarios in terms of the primitive variables $(\Qrho, \Qv, \pressure)$, these can be converted to the conservative variables by the definition of momentum and the definition of energy.
 
 \section{A Manufactured Solution}\label{sec:manufactured-solution}
-Following~\cite{dumbser2010arbitrary}, the scenario can be described in primitive variables by setting
-\begin{align}
+The compressible Navier Stokes equations have no interesting exact solution.
+This is why we follow the method of manufactured solutions~\cite{salari2000code} and create our own.
+Following~\cite{dumbser2010arbitrary}, we assume the solution in primitive variables
+\begin{align}\label{eq:manufactured-solution}
 \begin{split}
@@
 \end{align}
-We set the constants to \( \left(  \pressure_0 = 0.1, \pressure_b = \gamma^{-1}, \Qrho_0 = 0.5, \Qrho_b = 1, 
-\bm{v_0} = 0.25 {(1,1)}^\intercal, \bm{k} = \pi/5 {(1,1)}^\intercal \right) \).
+We set the constants
+\begin{equation}
+\begin{alignedat}{6}
+  & \pressure_u &&= \nicefrac{1}{10}, \qquad& \pressure_b &= \nicefrac{1}{\gamma}, \\
+  & \Qrho_0 &&= \nicefrac{1}{2}, \qquad& \Qrho_b &= 1, \\
+  & \bm{v_0} &&= \nicefrac{1}{4},
+  \begin{pmatrix}
+    1 \\
+    1
+  \end{pmatrix},
+  \qquad& \bm{k} &= \nicefrac{\pi}{5}
+  \begin{pmatrix}
+    1\\
+    1
+  \end{pmatrix},\\
+  & \omega &&= 2 \pi.
+  \end{alignedat}
+\end{equation}
+We derive a source term by inserting this solution into the \textsc{pde}~\pcref{eq:equation-set} by using the symbolic math toolkit \textit{Sage}~\cite{sagemath}.
+Our computation of the source term can be found at XXX\todo{Cite github repository with notebook!}.
+\Cref{eq:manufactured-solution} then solves our \pde{} combined with the derived source exactly.
 
-We derive a source term by inserting this solution into the \textsc{pde} by using the symbolic math toolkit \textit{Sage}~\cite{sagemath}.
-This procedure is called method of manufactured solutions~\cite{salari2000code}.
+Note that we only consider the compressible Navier Stokes equations here, without the reactive advection equation.
 
@@
 
-% \subsection{The first Stokes Problem}
-% \todo{Do I actually want to include this? Bit boring scenario}
-% \cite{dumbser2010arbitrary}
-
 \sidetitle{Taylor-Green Vortex}
@@
 An interesting testing scenario is the Taylor-Green Vortex, which exhibits a complicated flow from a simple initial condition.
-It is an analytic solution for the incompressible Navier-Stokes equations which agree relatively well with our equation set at low Mach numbers.
+It is an analytic solution for the incompressible Navier-Stokes equations which agrees relatively well with our equation set at low Mach numbers.
 We can thus use it to evaluate the performance of our solver.
@@
   \begin{pmatrix}
-    \phantom{-}\sin(x) cos(y) \\
-- \cos(x) sin(y) 
+    \phantom{-}\sin(x) \cos(y) \\
+- \cos(x) \sin(y) 
     \end{pmatrix} \\
-  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \frac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C
+  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \nicefrac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C
   \end{split}
@@
 %\subsection{Lid-Driven Cavity Flow}
-The lid-driven cavity flow is another very simple testing scenario for the Navier-Stokes equations.
+The lid-driven cavity flow is another simple testing scenario for the Navier-Stokes equations.
 The flow is driven entirely by the boundary conditions.
 They consist in four no-slip walls where the upper wall has a constant velocity $\Qv = (1.0, 0)$.
-We want to simulate a flow with a Mach number of $M = 0.1$ and a Reynolds number of $\text{Re} = 100$.
-This leads us to an initial conditions of
+We want to simulate a flow with a Mach number of $M = 0.1$ and a Reynolds number of $\text{Re} = 100$~\cite{fambri2017space}.
+This leads us to the constant initial conditions of
 \begin{align}
-  \label{eq:taylor-green}
+  \label{eq:lid-driven-cavity}
   \begin{split}
@@
 
-\sidetitle{Radialsymmetric CJ Detonation Wave}
+\sidetitle{CJ Detonation Wave}
 We investigate the radialsymmetric CJ detonation wave scenario from~\cite{helzel2000modified}.
@@
 Similar to~\cite{helzel2000modified}, we use the constants
-\begin{align}
-  \begin{split}
-  \gamma &= 1.4, \\
-  \Pr &= 0.75, \\
-  c_v &= 2.5, \\
-  c_p &= 3.5, \\
-  R &= 1.0.
-  \end{split}
-\end{align}
+\begin{equation}
+  \gamma = 1.4 ,\qquad \Pr = 0.75, \qquad c_v = 2.5 ,\qquad c_p = 3.5 ,\qquad R = 1.0.
+\end{equation}
 The Prandtl number is inspired from the viscous scenarios of~\cite{hidalgo2011ader}.
-We consider this scenario inviscid case and for a viscosity of $\mu = 0.01$.
+We consider this scenario for the inviscid case and also for a viscosity of $\mu = 0.01$.
 
@@
 We assume that $\backgroundPotT$ is constant over the entire domain.
-Inserting the definition of potential temperature, given by \cref{eq:potTToT}, into the equation of state (see \cref{eq:eos}) leads us to
+Inserting the definition of potential temperature, given by \cref{eq:potTToT}, into the equation of state~\pcref{eq:eos} leads us to
 \begin{equation}
@@
 \end{align}
-where we use the reference pressure $p_0$ as the pressure on ground level\todo{Refer to hydrostatic balance eq.\ in methods chapter!\cref{eq:hydrostatic-balance}}.
-This \textsc{ode} can be solved by separation of variables.
+where we use the reference pressure $p_0$ as the pressure on ground level.
+This \textsc{ode} is the hydrostatic equilibrium (similar to \cref{eq:hydrostatic-balance}) in terms of the potential temperature and can be solved by seperation of variables.
 After simplifying, we obtain
@@
 Concretely, we need to impose a viscous heat flux to ensure that the atmosphere stays in hydrostatic balance~\cite{giraldo2008study}
-\todo{Flux correct? Use viscFlux macro and energy subscript. Also only in z direction!}
 \begin{equation}
   \label{eq:atmosphere-bc}
-  F^\text{visc} = \kappa \pdv{\overline{T}}{z} =
+  \viscFlux_{\QE} = \kappa \pdv{\overline{T}}{z} =
 \kappa \frac{R \overline{\theta} \left(\frac{\overline{p}{\left (z \right )}}{p_{0}}\right)^{\frac{R}{c_{p}}} \frac{d}{d z} \overline{p}{\left (z \right )}}{c_{p} \overline{p}{\left (z \right )}}.
@@
 
+All scenarios use the gravitational source term~\pcref{eq:source-gravity} and the splitting of density and pressure~\pcref{eq:momentum-equation-split}.
 We use the following set of fluid dependent constants for these scenarios
-\begin{align}\label{eq:atmosphere-constants}
-  \begin{split}
-    \gamma &= 1.4, \\
-    \Pr &=  0.71, \\
-    R &= 287.058, \\
-    p_0 &= 10000,
-  \end{split}
-\end{align}
-the other constants are evaluated following \cref{eq:fluid-constants}.
+\begin{equation}\label{eq:atmosphere-constants}
+    \gamma = 1.4 ,\qquad \Pr =  0.71 ,\qquad R = 287.058 ,\qquad p_0 = 10000,
+\end{equation}
+the other constants are evaluated according to \cref{eq:fluid-constants}.
 The background pressure for these constants is depicted in \cref{fig:hydrostatic-p}.

### 2019-01-20 writing/thesis/chapters/conclusion.tex
Changes.

--- 2019-01-15 writing/thesis/chapters/conclusion.tex
@@
 \item We showed in \cref{sec:results-convergence} that our scheme converges for all considered orders for the Navier-Stokes equations.
-\item We evaluated our method for standard \textsc{cfd} scenarios and achieved competitive results for all considered scenarios.
-  This is true for two-dimensional scenarios (Taylor-Green, Lid-Driven Cavity) and for the three-dimensional \textsc{abc}-flow.
-\item Furthermore, our method allows us to simulate flows in hydrostatic equilibrium correctly.
+\item We evaluated our method for standard \textsc{cfd} scenarios~(\cref{sec:cfd}) and achieved competitive results for all used scenarios.
+  This is true for both two-dimensional scenarios (Taylor-Green and Lid-Driven Cavity) and for the three-dimensional \textsc{abc}-flow.
+\item Furthermore, our method allows us to simulate flows in hydrostatic equilibrium correctly (see \cref{sec:results-cloud}).
 \item The results of \cref{sec:results-tts-amr} showed that our \amr{}-criterion is able to save a significant portion of the computational effort compared to a uniform fine grid.
   It is able to do this without degrading the quality of the solution, even for a scenario that contains small-scale details.
-\item Chemical reactions and limiter work for non-stiff detonations.
+\item Our results of \cref{sec:results-reactive} show that our implementation is capable of simulating chemical reactions with a limited scheme, at least for a source term that is not stiff.
 \end{itemize}
 
-Of course, there are some things than can be improved and which need further work, such as:
+Of course, there are some things that can be improved and which need further work, such as:
 \begin{itemize}
-\item The current treatment of the boundary conditions is not stable for every scenarios.
+\item The current treatment of the boundary conditions is not stable for some scenarios.
   Especially the viscous walls for the \muscl{}-method are not correct, due to limitations of \exahype{}.
-\item Due to the \textsc{cfl}-condition~\pcref{eq:cfl-aderdg,eq:cfl-muscl}, the timestep of our \aderdg{}-scheme scales quadratically with the number of grid cells.
+\item The\textsc{cfl}-condition~\pcref{eq:cfl-aderdg,eq:cfl-muscl} has the effect that our method needs a large number of timesteps.
   Even though our \amr{}-criterion is able to reduce the number of needed cells drastically, we could get another large improvement by utilizing local timestepping.

### 2019-01-20 writing/thesis/chapters/implementation.tex
Changes.

@@
 \section{ExaHyPE}
-\exahype\ is based on the space-filling-curves library \peano~\cite{weinzierl2011}.
-The workflow from the perspective of a user is
+\exahype{} is based on the space-filling-curves library \peano~\cite{weinzierl2011}.
+The workflow from the perspective of a user is:
 \begin{itemize}
@@
   They are defined in the file \fileName{boundaryConditions.cpph}.
-\item Adding the diffusive penalty terms for the Riemann solver (\fileName{riemannSolverNonlinear.cpph}) and \textsc{cfl}-condition (\fileName{stableTimeStepSize.cpph}).
+\item Adding the diffusive penalty terms for the Riemann solver\\(\fileName{riemannSolverNonlinear.cpph}) and \textsc{cfl}-condition (\fileName{stableTimeStepSize.cpph}).
   This corresponds to \cref{eq:rusanov-flux,eq:cfl-aderdg}.
@@
 \begin{itemize}
-\item The function \funName{mapGlobalObservables} computes for a cell the observables from its degrees of freedoms and cell size.
+\item The function \funName{mapGlobalObservables} computes the observables for a cell from its degrees of freedoms and its size.
   It returns a vector of size $\ngobs$.
@@
 \begin{itemize}
-\item Add vectors \varName{\_globalObservables} and \varName{\_nextGlobalObservables} to all solvers.
+\item Adding vectors \varName{\_globalObservables} and \varName{\_nextGlobalObservables} to all solvers.
   The former stores the observables of the previous timestep, the latter the ones of the current timestep.
-  We can thus use the old observables for mesh refinement and compute a new reduction concurrently.
+  We can thus use the old observables for mesh refinement and compute a new reduction at the same time.
   Before the first timestep, we reset both current and next observables.
   At the beginning of each timestep, we overwrite the previous data with the current data, and reset \varName{\_nextGlobalObservables} with \funName{resetGlobalObservables}.
-  This is done in the methods \funName{startNewTimeStep}, \funName{startNewTimeStepFused}, \funName{updateTimeStepSizesFused}, \funName{updateTimeStepSizes}.
-\item Reduce global observables in solver with method \funName{reduceGlobalObservables} that takes the \varName{cellInfo} and \varName{solverNumber}.
+  This is done in the methods \funName{startNewTimeStep}, \funName{startNewTimeStepFused}, \funName{updateTimeStepSizesFused} and \funName{updateTimeStepSizes}.
+\item Reducing global observables in solver with method \funName{reduceGlobalObservables} that takes a \varName{cellInfo} and a \varName{solverNumber}.
   The solver number is always 0 because we only use one solver at a given time.
-  The cell information stores pointers to the cell data for all solvers.
+  The cell information stores pointers to the degrees of freedoms.
   We implement this method for all solvers.
   This has the advantage that we have a shared interface for all solver types.
-\item Reduce global observables per node in the mappings \className{FinaliseMeshRefinement}, \className{FusedTimeStep}, \className{UpdateAndReduce}.
+\item Reducing global observables per node in the mappings \className{FinaliseMeshRefinement}, \className{FusedTimeStep} and \className{UpdateAndReduce}.
   \begin{itemize}
@@
     This is not necessary for the mapping \className{FinaliseMeshRefinement}.
-   \item We update the global observables of the solver in the method \funName{endIteration}, which call the method \funName{updateG}.
+   \item We update the global observables of the solver in the method \funName{endIteration}, which calls the method \funName{updateGlobalObservables}.
   \end{itemize}
-\item If we use \mpi{}, we also need to reduce the observables over all ranks.
-  \exahype{} already reduces the timestep size, we extend these already existing \mpi{} messages to also include the global observables \varName{\_globalObservables}.
+\item Reducing the observables over all ranks, if using \mpi{}.
+  \exahype{} already reduces the timestep size.
+  We extend these already existing \mpi{} messages to also include the global observables \varName{\_globalObservables}.
   For this, we changed the following methods of the \dg{}-solver:
@@
   The solvers update the variable \varName{\_nextGlobalObservables} during the \mpi{}-reduction.
-  Together with the aforementioned resetting of the observables, this again corresponds to \cref{alg:reduce-gobs}.
+  This again corresponds to \cref{alg:reduce-gobs} together with the aforementioned resetting of the observables, 
 \end{itemize}

### 2019-01-20 writing/thesis/chapters/introduction.tex
Changes.

@@
 Simulations are an important part of weather and climate forecasts.
-Both types of forecasts are difficult problems that are not only limited by poor conditioning but also by lack of computational power.
+Both types of forecasts are difficult problems that are limited by a lack of computational power.
 Especially in a time, where the realization of exascale supercomputers is imminent, scalable numericals model become more and more important.
 Current climate and weather models are not ready for the exascale era~\cite{schulthess2018reflecting}.
-While~\cite{schulthess2018reflecting} proposes the goal of a spatial resolution of $\SI{1}{\kilo\meter}$, simulations with resolution that is an order of magnitude coarser is the current state of the art.
+While~\cite{schulthess2018reflecting} proposes a spatial resolution of $\SI{1}{\kilo\meter}$ as a goal, current state of the art simulations operate on a resolution that is an order of magnitude coarser.
 
-Of course, a finer grid is not useful, if the computational effort is too large.
+Of course, a finer grid is not useful if the computational effort is too large.
 Thus, they also propose a compute rate of one simulated years per wall-clock day.
@@
 \sidetitle{Discontinuous Galerkin}
-The discontinuous Galerkin methods are an exciting numerical method as they are relatively easy to scale.
+The discontinuous Galerkin (\dg{}) methods are an exciting numerical method as they are relatively easy to scale.
 In addition, they can be of high order and can perform local grid refinement~\cite{hesthaven2008nodal}.
 These advantages are only some reasons why they have been investigated for weather and climate modeling~\cite{muller2010adaptive,giraldo2008study}.
-Recently, the \ader{} discontinuous Galerkin method has been proposed by~\cite{dumbser2008unified}.
+Recently, \ader{} discontinuous Galerkin methods has been proposed, for example in~\cite{dumbser2008unified}.
 This method is scalable and of arbitrary order in both time and space.
@@
 
-The goal of this thesis is to evaluate the \aderdg{} method for testing scenarios, which have been devised as benchmark examples for weather prediction~\cite{robert1993bubble,giraldo2008study}.
+The goal of this thesis is to evaluate the \aderdg{} method for testing scenarios, which have been devised as benchmark examples for meteorological applications~\cite{robert1993bubble,giraldo2008study}.
 We implement this with the \exahype{}-engine, which is \enquote{An Exascale Hyperbolic \pde{} Engine}.
@@
   Moreover, we describe a combination of both methods in \cref{sec:limiting}, where we use the \muscl{}-scheme in cases where the \aderdg{}-method is unstable.
-\item In \cref{sec:amr}, we introduce an adaptive mesh refinement (\amr{}) method that checks, whether the local cell is an outlier.
+\item In \cref{sec:amr}, we introduce an adaptive mesh refinement (\amr{}) method that checks, whether a local cell is an outlier.
   As indicator function we use the total variation of the discrete solution and as outlier detection we use the mean and standard variance of this function.
 \item In \cref{chap:implementation} we show how we implemented our proposed method using the \exahype{}-engine.
-\item We present seven different scenarios in \cref{chap:scenarios}.
-\item We check the performance of our method in~\cref{chap:results}.
+\item We present seven scenarios that stem from different domains in \cref{chap:scenarios}.
+\item We check the performance of our proposed method in~\cref{chap:results}.
   \begin{itemize}
-  \item In \cref{sec:results-convergence}, we perform a convergence test.
+  \item In \cref{sec:results-convergence} we perform a convergence test.
   \item In~\cref{sec:cfd} we investigate the ability of our scheme to simulate classical fluid mechanics (\textsc{cfd}) test scenarios correctly.

### 2019-01-20 writing/thesis/chapters/methods.tex
Changes.

@@
 % TODO: Extract to settings
-\newcommand{\cellAvg}[1][i,j]{U_{#1}}
-\newcommand{\sign}{\operatorname{sign}}
-\newcommand{\minmod}{\operatorname{minmod}}
-\newcommand{\slope}[2][i,j]{s^{#2}_{#1}}
-\newcommand{\gradCellAvg}[1][i,j]{\gradient{\cellAvg[#1]}}
-\newcommand{\fluxX}{\flux_x}
-\newcommand{\fluxY}{\flux_y}
-
 \chapter{An ADER-DG scheme for the Navier-Stokes Equations}\label{chap:methods}
@@
 We start with a description of the arbitrary high order derivatives (\ader{}) discontinuous Galerkin (\dg{}) method with a focus on equations that contain both advective and diffusive terms.
-We then seque into a short description of the \muscl{} scheme which is a second order finite volume scheme.
-
-e conclude this chapter by a description of finite volume limiting and adaptive mesh refinement (\amr{}).
+We then seque into a short description of the \muscl{} scheme which is a second order finite volume method.
+
+We conclude this chapter by a description of finite volume limiting and adaptive mesh refinement (\amr{}).
 The limiting combines both numerical methods to achieve a stable, high-order method and the \amr{} allows us to perform high quality simulations with a smaller computational cost.
-
 \section{Reactive Compressible Navier Stokes Equations}\label{sec:navier-stokes}
@@
 \end{equation}
-where $\Qrho$ is the density, $\Qj$ is the two or three-dimensional momentum, $\QE$ the energy density and $\QZ$ is the mass fraction of the chemical reactant.
+where $\Qrho$ is the density, $\Qj$ is the two or three-dimensional momentum, $\QE$ is the energy density and $\QZ$ is the mass fraction of the chemical reactant.
 In our case, the chemical reactant is unburnt gas.
-The first row is the conservation of mass, the second is the conservation of momentum, the third is the conservation of energy and the fourth is the continuity of the gas.
-
 The rows of \cref{eq:equation-set} are the conservation of mass, the conservation of momentum, the conservation of energy and the continuity equation of the reactant.
@@
 \end{equation}
+
 The hyperbolic flux is given by
@@
 In this equation $\bm{a} \otimes \bm{b} = \bm{a} \bm{b}^\intercal$ is the Kronecker or outer product of two vectors $\bm{a}$ and $\bm{b}$.
-The pressure $\pressure$ is given by the caloric equation of state of an ideal reacting gas
+The pressure $\pressure$ is given by the equation of state of an ideal reacting gas
 \begin{equation}
@@
 \end{equation}
-The term $q_0 \QZ$ is the chemical energy with the heat release $q_0$, the term $gz$ is the geopotential height.
-The pressure is related to the temperature $T$ by the thermic ideal gas law
+The term $q_0 \QZ$ is the chemical energy with a heat release $q_0$~\cite{helzel2000modified}, the term $gz$ is the geopotential height~\cite{giraldo2008study}.
+We set $g$ to 9.81.
+The pressure is related to the temperature $T$ by the thermal equation of state
 \begin{equation}
   \label{eq:temperature}
-  \pressure = \Qrho R T
+  \pressure = \Qrho R T,
 \end{equation}
@@
   \label{eq:visc-flux}
-  \viscFlux(\Q, \gradQ) = \viscFluxDef.
+  \viscFlux(\Q, \gradQ) = \viscFluxDef,
 \end{equation}
@@
 
-We further introduce the ratio of specific heats $\gamma$ and the heat fraction for constant volume $c_v$ and constant volume $c_r$.
+We further introduce the ratio of specific heats $\gamma$ and the heat fraction for constant volume $c_v$ and constant volume $c_p$.
 These constants are all fluid dependent and relate to each other~\cite{dumbser2010arbitrary} and the gas constant by
@@
 \end{align}
-We can then compute the heat conduction coefficient
+We can compute the heat conduction coefficient
 \begin{equation}
   \label{eq:heat-conduction-coeff}
-  \kappa = \frac{\mu \gamma}{\Pr} \frac{1}{\gamma - 1} R = \frac{\mu \gamma}{\Pr} c_v,
+  \kappa = \frac{\mu \gamma}{\Pr} \frac{1}{\gamma - 1} R = \frac{\mu c_p}{\Pr},
 \end{equation}
@@
 \begin{equation}\label{eq:source-gravity}
-  \source[\Qj] = - g \bm{k} \cdot \Qj,
-\end{equation}
-where $g = 9.81$ and $\bm{k}$ is a unit vector pointing in $z$-direction\todo{Discuss $g$ either in pressure or scenario.}.
+  \source[\Qj] = - g \bm{e_z} \cdot \Qj,
+\end{equation}
+where $\bm{e_z}$ is the unit vector pointing in $z$-direction~\cite{giraldo2008study}.
 
@@
 where $\backgroundPressure$ and $\backgroundRho$ is the background pressure and density.
-We now focus on the following part of the momentum equation (neglecting viscous effects) of \cref{eq:equation-set}
+We now focus on the following part of the momentum equation (neglecting viscous effects) of \cref{eq:equation-set} in combination with gravitational source term~\pcref{eq:source-gravity}
 \begin{equation}
   \label{eq:momentum-equation}
-  \pdv{\Qj}{t}+ \divergence{
-    \Qv \cdot \left( \bm{I} \QE + \bm{I} \pressure \right)
+  \pdv{\Qj}{t}+ \divergence{ \left(
+    \Qv \otimes \Qj + \bm{I} \pressure
+    \right)
   }
@@
   \label{eq:momentum-equation-split}
-  \pdv{\Qj}{t}+ \divergence \left(
-    \Qv \cdot \left( \bm{I} \QE + \bm{I} \pressure' \right)
+  \pdv{\Qj}{t}+ \divergence{ \left(
+    \Qv \otimes \Qj + \bm{I} \pressure'
     \right)
+  }
   =
   -g \bm{k} \Qrho'.
-\end{equation}.
+\end{equation}
 We thus cancel parts of the flux with parts of the source term.
-Note that the time derivative of the background density also vanishes.
 This form of the equation is inspired by equation set 3 of~\cite{giraldo2008study}.
@@
 \sidetitle{Boundary conditions}
-To close the system we need to impose boundary conditions.\todo{Adapt this chapter to implementation!}
-
-%\sidetitle{Cauchy}
-For some scenarios we use Cauchy boundary conditions, i.e.\ we prescribe both $\Q$ and $\gradQ$ at the boundary.
-In most cases, we would like to impose periodic boundary conditions, due to the inner workings of \exahype{} this is not possible.
-Instead we use the analytical solution of our problems at the boundary, imposing both value and gradients of the conservative variables.
-Note that this leads to an error when our problem does not posses an exact analytical solution.
-This is the case for test cases that are analytical solutions to the incompressible Navier Stokes equations but do not satisfy the compressible equation set.
+To close the system we need to impose boundary conditions.
+Many scenarios are described with periodic boundary conditions,
+This is not possible with \exahype{}.
+Instead we use the analytical solution of our problems at the boundary, imposing both the conservative variables $\Q$ and its gradient $\gradQ$.
+This type of boundary condition is called Cauchy condition.
+Note that this leads to an error when our problem does not possess an exact analytical solution.
+This is the case for test cases that are exact solutions for the incompressible Navier Stokes equations but do not satisfy the compressible equation set.
 
 As a physical boundary condition we limit ourselves to wall boundary condition
-
-%\sidetitle{No-Slip}
 A standard wall boundary condition for viscous fluid is the no-slip condition, where we assume that when the fluid is close to a wall, it has a velocity of zero relative to the wall.
@@
   \Qrho^o &= \Qrho^i, \\
-  \Qj^o &= -\Qj^i, \\
+  \Qj^o &= 2 \Qj^w - \Qj^i, \\
   \QE^0 &= \QE^i,\\
+  \QZ^0 &= \QZ^i,\\
   {(\nabla Q)}^o &= {(\nabla Q^o)},
@@
 \end{align}
-where a superscript of $o$ and $i$ denotes the values outside and inside of the boundary respectively.
-
-%\sidetitle{Free-Slip}
+where a superscript of $o$ and $i$ denotes the values outside and inside of the domain respectively.
+The term $\Qj^w$ denotes the velocity of the wall.
+
 Similarly to the no-slip condition, we define the free-slip condition
@@
 \end{equation}
-where only the velocity in normal direction is zero after the Riemann solver.
+where only the velocity in normal direction is zero next to the wall.
 The other variables are extrapolated in the same manner as in \cref{eq:no-slip}.
@@
 \section{The ADER-DG Method}\label{sec:ader-dg}
-\newcommand{\NVar}{N^{\text{var}}}
-\newcommand{\dimensions}{d}
-\newcommand{\mapping}{\mathcal{M}}
-\newcommand{\volume}{V}
-\newcommand{\cellCenter}{\operatorname{cell-center}}
 We describe the arbitrary derivative discontinous Galerkin (\aderdg) method in this chapter.
 Our description of the main method follows~\cite{dumbser2008unified,dumbser2010arbitrary,dumbser2018efficient}, our notation follows primarily~\cite{dumbser2018efficient}.
-Let $\NVar$ be the number of variables, $\dimensions$ the number of spatial dimensions and $N > 0$ the order of the method.
+Let $\NVar$ be the number of variables, $\dimensions$ the number of spatial dimensions and $N > 0$ the degree of the basis functions.
+We also call $N$ the order of the method.
 We discuss the approximation of systems of partial differential equations (\pde) of the form
@@
 
-We discuss the solution of a conservation law \cref{eq:conservation-law-gradient} with two or three dimensional domain $\domain$ and boundary $\boundary$.
+We discuss the solution of a conservation law \cref{eq:conservation-law-gradient} with two or three dimensional domain $\domain$ and its boundary $\boundary$.
 In our implementation of the discontinous Galerkin (\dg) framework, we approximate this solution in the space
@@
 of disjoint quadrilateral cells $\cell$.
-Note that we do not distinguish between the broken approximation space and the domain, the use should be clear given its surrounding context.
-For each cell we denote its center by $\cellCenter{\cell}$ and its size by $\Delta x, \Delta y$ and $\Delta z$.
+Note that we do not distinguish between the approximation space and the domain, the use should be clear given its surrounding context.
+For each cell we denote its center by $\cellCenter (\cell)$ and its size by $\Delta x, \Delta y$ and $\Delta z$.
 
@@
 We first compute a local time evolution of each cell in a predictor step and then add the influence of the neighbors in the corrector step.
-% \begin{algorithm}[H]
-%   \begin{algorithmic}
-%     \Let{$\stpredictor$}{Initial guess}
-%     \Let{$F_h$}{$\flux(\Q, \gradQ)$}
-%     \Let{$\stpredictor$}{Solve \cref{eq:space-time-predictor} using $F_h, \Q, \gradQ$}
-%     \Let{$\left( \hat{F_h}, \hat{\Q}, \hat{\gradQ}, \hat{\stpredictor} \right)$}
-%         {Extrapolate to boundary using \cref{eq:boundary-extrapolation}}
-%     \Let{update}{Use \cref{eq:corrector} with boundary extrapolated values (fluxes of neighbors)}
-%   \end{algorithmic}
-%   \caption{The \textsc{ader-dg} algorithm for one cell.}
-% \end{algorithm}
-
 \sidetitle{Reference Cell}
@@
 We use the quad cell $\hat{\cell} = (0, 1)^\dimensions$ as space reference cell.
-The mapping, which takes a point on the reference cell with coordinates $\hat{\bm{x}}$ and and returns a the coordinates $\bm{x}$ in a grid cell $\cell$ is
+The mapping, which takes a point on the reference cell with coordinates $\hat{\bm{x}}$ and and returns its coordinates $\bm{x}$ in a grid cell $\cell$ is
 \begin{equation}\label{eq:space-mapping}
@@
 \end{equation}
-The inverse mapping $\mapping^{-1}$ can be used to define a function $f(\bm{x})$ acting on a point $\hat{\bm{x}}$ of a regular cell in terms of a function $\hat{f}(\bm{x})$ that acts on the corresponding point of the reference cell by the relation
+The symbol $\mapping^{-1}$ denotes the inverse mapping.
+It can be used to define a function $f(\bm{x})$ acting on a point $\hat{\bm{x}}$ of a regular cell in terms of a function $\hat{f}(\bm{x})$ that acts on the corresponding point of the reference cell by the relation
 \begin{equation}
@@
 where the reference time interval is $[0,1]$ and the time interval of a cell is $[\curTime, \nextTime]$.
-The time at the beginning of a timestep is thus denoted by $\curTime$, the time at the end of a step is denoted by $\nextTime = \curTime + \Delta t$ with timestep size $\Delta t$.
+The time at the beginning of a timestep with index $k$ and timestep size $\Delta t$ is denoted by $\curTime$, the time at the end of a step is $\nextTime = \curTime + \Delta t$.
 
@@
     \hat{f}(\hat{\bm{x}})
-  }
+  }.
 \end{equation}
@@
   \label{eq:lagrange-basis}
-    \lagrangeRef(x) = \prod_{i >0, j>0, i \neq n}^N \frac{x - {\quadNode[j]}}{x_i - \quadNode[j]},
+    \lagrangeRef(x) = \prod_{\substack{0 \leq j \leq N \\ i \neq j}} \frac{x - {\quadNode[j]}}{x_i - \quadNode[j]},
 \end{align}
@@
 
-The basis functions are similarly defined in $\dimensions$-dimensions by considering nodes that are the tensor-products of $d$ one-dimensional Gauss-Legendre quadrature.
+The basis functions are similarly defined in $\dimensions$-dimensions by considering nodes that are the tensor-products of $d$ one-dimensional Gauss-Legendre quadrature nodes.
 They are indexed by a multi-index $n = (n_1, \ldots, n_\dimensions)$
@@
     \end{alignat}
-    where we make use of the Kronecker delta
+    where we made use of the Kronecker delta
 \begin{equation}
@@
   \begin{split}
-  \sbasis[][n] (\bm{x}) &= \sbasisRef[][n] \left( \mapping(\bm{x}) \right)
-  \end{split}
-\end{align}
-where $\sbasisRef$ denotes the basis function on the reference cell.
-
-In addition to the space cells, we also introduce space-time cells $\cell \times [\curTime, \nextTime]$ with reference cell $(0,1)^\dimensions \times  [0,1]$.
+  \sbasis[][n] (\bm{x}) &= \sbasisRef[][n] \left( \mapping^{-1}(\bm{x}) \right).
+  \end{split}
+\end{align}
+In addition to the space cells, we also introduce space-time cells $\cell \times [\curTime, \nextTime]$ with corresponding reference cell $(0,1)^\dimensions \times  [0,1]$.
 A basis for these cells is given by
@@
   \stbasisRef[][l,n](\hat{\bm{x}}, \hat{t}) &= \lagrange[l](t) \sbasis[][n] (x)\\
-  \stbasis[][l,n] (\bm{x}, t) &= \stbasisRef \left( \mapping(\bm{x}), \timeMapping(t) \right)
-  \end{split}
-\end{align}
-where the first index $l = 0, \ldots, N$ runs over times.
-Outside of elements, we define the basis functions to be equal to 0.
+  \stbasis[][l,n] (\bm{x}, t) &= \stbasisRef \left( \mapping^{-1}(\bm{x}), \timeMapping^{-1}(t) \right)
+  \end{split}
+\end{align}
+where the first index $l = 0, \ldots, N$ runs over the time.
+Outside of elements, we define the basis functions to be equal to zero.
 
@@
 \begin{align}
-  \stbasis[][v,n,l] (\bm{x},t)= \bm{I} \otimes \stbasis[][n,l] (\bm{x}, t)
-\end{align}
-with the identity matrix $\bm{I} \in \mathbb{R}^{\NVar}$\todo{Write out definition for space-time basis+both reference basis funcs. Explain kronecker delta, maybe when first used in pde chapter}.
-
-\sidetitle{Expansion of quantities}
+  \begin{split}
+    \stbasis[][v,n,l] (\bm{x},t) &= \bm{e_v} \otimes \stbasis[][n,l] (\bm{x}, t) \\
+    \sbasis[][v,n] (\bm{x}) &= \bm{e_v} \otimes \sbasis[][n] (\bm{x})
+  \end{split}
+\end{align}
+where $\bm{e_v} \in \mathbb{R}^{\NVar}$ is vector with components
+\begin{equation}
+  \left( \bm{e_v} \right)_{v'} = \delta_{v v'},
+\end{equation}
+and $\bm{A} \otimes \bm{B}$ denotes the tensor product between two tensors $\bm{A}$ and $\bm{B}$.
+
+\sidetitle{Expansion of quantities}\todo{Maybe explain this later, right now $\stpredictor$ is not defined!}
 All quantities can be expanded in the space-time basis.
-For example, the expansion of space-time predictor $\stpredictor[\cell]$ can be written as
+For example, the expansion of the space-time predictor $\stpredictor[\cell]$ can be written as
 \begin{equation}
@@
 with coefficients $\spredictorCoeff, \ssolCoeff, \ssourceCoeff$ and $\sfluxCoeff$ respectively.
-The indices are in range of $v' = (0, \ldots, \NVar - 1)$, $n' = (0, \ldots, \sbasisSize - 1)$ and $l' = ( 0, \ldots, N)$.
+Each coefficient index generally has the same range as the corresponding basis index.
+For example, the indices $n$ and $n'$ both run over the entire space-basis.
 
@@
 We are now ready to derive the predictor.
-We first multiply the conservation law by a test function of the same function space as the basis, integrate over a space-time-element $\cell$ and replace all terms with the discrete approximations.
+We first multiply the conservation law by a test function of the same function space as the basis, integrate over a space-time-element $\cell$ and replace all terms with their discrete approximations.
 In particular, we replace the vector of conservative variables $\Q$ with the space-time predictor $\stpredictor[\cell]$.
-\begin{equation}\label{eq:weak-pde-space-time}
+\begin{align}\label{eq:weak-pde-space-time}
+\begin{split}
 \intdt{\intdcell{
@@
 }}
-+
+&+
 \intdt{\intdcell{
@@
 }}
-=
+\\&=
 \intdt{\intdcell{
   \sttestfunction[\cell][v,l,n] \stsource(\bm{x}, t, \stpredictor)
-}},
-\end{equation}
-where the indices $v = (0, \ldots, \NVar-1)$, $n = (0, \ldots, \sbasisSize - 1)$ and $l = (0, \ldots, N)$ run over the variables, space and time.
+}}.
+\end{split}
+\end{align}
+%where the indices $v = (0, \ldots, \NVar-1)$, $n = (0, \ldots, \sbasisSize - 1)$ and $l = (0, \ldots, N)$ run over the variables, space and time.
 
@@
 }}
-= \\
+= 
 \intdcell{
@@
 }
-&+
+\\&+
 \intdt{\intdcell{
@@
 }}
-+
+\\&+
 \intdt{\intdcell{
@@
 Using the expansions in space and time~\pcref{eq:cell-approx-space,eq:cell-approx-space-time} results in a local systems of equations that can be solved by a fixed-point iteration scheme.
-To close the iterative scheme, we set the initial value for the space-time predictor as
+We set the initial value for the space-time predictor as
 \begin{equation}
@@
 In practice, we precompute all integrals that contain only basis functions and their derivatives for the reference cell.
-The computation of the integrals for general space-tiem cells can then be done by \cref{eq:integration-by-substitution}.
-For details and proof of convergence for case of linear \pde{}s, see~\cite{dumbser2008unified}.
+The computation of the integrals for general space-time cells can then be performed by applying \cref{eq:integration-by-substitution}.
+For details and proof of convergence for the case of linear \pde{}s, see~\cite{dumbser2008unified}.
 
 \sidetitle{Preparing for corrector}
-It is useful to compute time-averaged versions of our quantities directly after the predictor.
+It is useful to compute time-averaged versions of our quantities.
 For example, this can be done for the space-time predictor by
@@
 The final step of the \aderdg{}-scheme is the corrector.
-We multiply the system \cref{eq:conservation-law-gradient} by a space test function $\stestfunction$ and integrate over the space-time control volume.
+We multiply the system \cref{eq:conservation-law-gradient} by a space test function and integrate over the space-time control volume.
 This results, yet again, in the weak formulation of the \pde{}
@@
 \end{equation}
-We now insert our discrete approximations and apply the basis expansions~\pcref{eq:cell-approx-space,eq:cell-approx-space-time} to the space-time predictor.
-The first part can be integrated by parts in time with the convenient result that only the boundary terms remain because the basis is constant in time.
+We now insert our discrete approximations and apply the space-basis expansion~\pcref{eq:cell-approx-space} to the discrete solution.
+The first term can be integrated by parts in time.
+This has the convenient result that only the boundary terms remain because the basis is constant in time.
 We then integrate the flux divergence by parts in space and insert the Riemann solver to connect with the neighbouring elements.
@@
   \stestfunction[][v,n] \sbasis[][v,n']
-}}
+}}%
 \begin{align}
@@
 }}\right)
--\\
+\\&-
 \left(\intdt{\intdcell{
@@
 }}\right)
-&=
+\\&=
 \left(\intdt{\intdcell{
@@
 for the coefficients $\ssolCoeff[\nextTime][v,n]$ of the new solution.
-Here the superscripts $\pm$ denotes values that are extrapolated to the boundaries.
+Here the superscripts $\pm$ denote values that are extrapolated to the boundaries.
 Again, the computational effort can be vastly reduced by collecting the integrals into matrices and precomputing as much as possible.
-Using the orthogonality of the basis functions~\pcref{eq:basis-orthogonality} on the first term, it becomes clear that the correction is a simple, explicit computation.
+Using the orthogonality of the basis functions~\pcref{eq:basis-orthogonality} on the first term of \cref{eq:corrector}, it becomes clear that the correction is a simple, explicit computation.
 % The first term is the mass tensor with entries
@@
   \label{eq:rusanov-flux}
-  \Riemann(\Q^-, \gradQ^-; \Q^+, \gradQ^+) \cdot \normal =
+  \begin{split}
+  \Riemann(\Q^-, \gradQ^-; \Q^+, \gradQ^+) \cdot \normal &=
   \frac{1}{2} \left(
@@
     \flux(\Q^-, \gradQ^-)
-  \right) -
+  \right)
+  \\&-
   \frac{1}{2} s_\text{max} (\Q^+ - \Q^-),
+  \end{split}
 \end{equation}
@@
 \end{align}
-in direction of the normal vector $\normal$ to the cell face.
-
+in direction of the normal vector $\normal$. 
 This Riemann solver was first published in~\cite{gassner2008discontinuous} and used for an \textsc{ader-dg} scheme in~\cite{dumbser2010arbitrary}.
-\todo{Should i mention paper only describe for 1D?}
-The timestep per dimension $d$ is restriced to a so-called \textsc{cfl}-type penalty
+
+The timestep is restriced to a so-called \textsc{cfl}-type penalty
 \begin{equation}\label{eq:cfl-aderdg}
  %\Delta t \leq  \text{CFL} \, \frac{\alpha(N) \, h}{\maxConvEigen + 2 \maxViscEigen \frac{1}{\alpha(N) h}}
- \Delta t \leq  \text{CFL} \, \alpha(N) \, h \sum_{i=1}^{\dimensions} \frac{1}{\maxConvEigen + 2 \maxViscEigen \frac{1}{\alpha(N) h}},
+ \Delta t \leq  \text{CFL} \, \alpha(N) \, h \sum_{i=1}^{\dimensions} \frac{1}{\maxConvEigen_i + 2 \maxViscEigen_i \frac{1}{\alpha(N) h}},
 \end{equation}
 where the eigenvalues are evaluated for the flux Jacobian in direction $i$~\cite{dumbser2010arbitrary,gassner2008discontinuous}.
-The constant $\alpha(N) \leq {\left( 2N+1  \right)}^{-1}$ is obtained from von Neumann analysis on a simple model problem and depends on the approximation order~\cite{dumbser2008unified}.
+The constant $\alpha(N) \leq {\left( 2N+1  \right)}^{-1}$ can be obtained from von Neumann analysis on a simple model problem and depends on the approximation order~\cite{dumbser2008unified}.
 We use this constant for both hyperbolic and diffusive penalty terms to ensure stability.
-For a more detailed and rigoruous stability analysis of the Riemann solver, see~\cite{gassner2008discontinuous}.
+For a more detailed and rigorous stability analysis of the Riemann solver, see~\cite{gassner2008discontinuous}.
 We use a value of $0.7$ for the constant $\text{CFL}$.
@@
 In contrast to the previous \dg{} scheme, we now only store averages instead of a full polynomial solution for each cell.
-We achieve higher order then by reconstructing a linear function from a cell and its neighbours.
+We achieve higher order by reconstructing a linear function from a cell and its neighbours.
 Let $\cellAvg$ denote the averages per cell at spatial coordinates $i,j$.
@@
   \label{eq:minmod}
-  \operatorname{minmod}(a, b) =
+  \minmod(a, b) =
   \begin{cases}
@@
 \end{equation}
-to avoid unphyiscally steep gradients and to stabilize the system~\cite{leVeque2002finite}.
+to avoid unphyiscally steep gradients and thus to stabilize the scheme~\cite{leVeque2002finite}.
 This function can be used to compute the slopes
@@
 where $\Delta x$ and $\Delta y$ are the inverse cell sizes in $x$ and $y$ direction respectively.
-
-We use the slope to reconstruct the value at the boundary.
+Here, we apply the $\minmod$ function element-wise.
+
+We use the slope to reconstruct the value at the cell boundaries.
 In the following, $\cellAvg^{\pm x}$ is the average of the left ($+$) or right ($-$) cell boundary.
-Similar, $\cellAvg^{\pm y}$ is the value at the top/bottom cell boundary.
+Similar, $\cellAvg^{\pm y}$ is the value at the top and bottom cell boundary.
 These so called boundary extrapolated values are given by
-\newcommand{\extrapolatedCellAvg}[3][i,j]{\cellAvg[#1]^{#3 #2} = \cellAvg #3 \frac{1}{2} \slope{#2}}
+\newcommand{\extrapolatedCellAvg}[3][i,j]{\cellAvg[#1]^{#3 #2} = \cellAvg #3 \frac{1}{2} \slope{#2}}%
 \begin{equation}
@@
   \begin{split}
-  \forall (k \in \{-x, +x, -y, +y \} ): \quad  \hat{U}_{ij}^k = \cellAvg^k &+
-  \frac{\Delta t}{2 \Delta x} \left[ \fluxX(\cellAvg^{-x}, \gradCellAvg) - \fluxX(\cellAvg^{+x}, \gradCellAvg) \right] \\&+
-  \frac{\Delta t}{2 \Delta y} \left[ \fluxY(\cellAvg^{-y}, \gradCellAvg) - \fluxY(\cellAvg^{+y}, \gradCellAvg) \right],
+    \forall (k \in \{-x, +x, -y, +y \} ): \quad  \hat{U}_{ij}^k &= \cellAvg^k
+\\&+ \frac{\Delta t}{2 \Delta x} \left[ \fluxX(\cellAvg^{-x}, \gradCellAvg) - \fluxX(\cellAvg^{+x}, \gradCellAvg) \right]
+\\&+ \frac{\Delta t}{2 \Delta y} \left[ \fluxY(\cellAvg^{-y}, \gradCellAvg) - \fluxY(\cellAvg^{+y}, \gradCellAvg) \right],
   \end{split}
@@
 \todo{Is this enough detail?}
-We tread the source term by a simple splitting scheme.
+We treat the source term by a simple splitting scheme.
 The interested reader is referred to the discussions in~\cite{leVeque2002finite,toro2009riemann}.
@@
 Both have in common that they change the structure of the grid.
-Instead of a regular grid where each cell has the same size, we now have different cell sizes.
+Instead of a regular grid where each cell has the same size, we now have different cell sizes and even different numerical schemes.
 
@@
 Even worse, in the case of non-linear fluxes, discontinuities can appear even from smooth initial data.
-In addition, oscillations stemming from the high-order polynomical approximation can lead to wrong or unphyiscal data.
+In addition, oscillations stemming from the high-order polynomical approximation can lead to wrong or unphysical data.
 This is called Gibbs phenomenon.
@@
 
-If a solution violates any of our criterions, we recompute the last timestep for the offending cells with a limited finite volume method.
+If a solution violates any of our criteria, we recompute the last timestep for the offending cells with a limited finite volume method.
 In our case we use the \muscl{}-method (\cref{sec:muscl}).
@@
 \Cref{fig:limiting-subcells} depicts the mapping from \dg{}-cells to finite volume subcells.
-For the sake of brevity, we omit technical details and refer the interested reader to~\cite{dumbser2016simple}.
+For the sake of brevity, we omit technical details and refer the interestd reader to~\cite{dumbser2016simple}.
 
@@
 The goal of \amr{} is to increase the computational efficiency by using a coarse spatial resolution in areas with low information content and a higher resolution in areas of interest.
-A simple example for this would be using finer mesh cells for the simulation of a wave, while using a low resolution for areas where the wave does not pass through.
-Of course, the difficult part is defining areas of interest.
+A simple example for this would be using smaller mesh cells for the simulation of a wave, while using larger cells for areas where the wave does not pass through.
+Of course, the difficult part is recognizing interesting areas.
 We use a global, gradient based refinement strategy.
@@
 \newcommand{\sampleVariance}{\overline{\variance}}
-A simple way of determining outliers is by how many standard deviations a value differs from the mean value.
+A simple way of determining outliers is to compute the mean and standard deviation for a set.
+Any value that differs by a certain multitude of the standard deviation from the mean can be marked as an outlier.
 We thus want to compute the mean and variance over all grid cells.
 For computational efficiency and to simplify the implementation, we do this by performing only pairwise merge operations.
-The simplest way to compute is by the textbook definitions of mean $\mean$ and population variance $\variance$ of a random variable $X$
+The simplest way of computing this is by the textbook definitions of mean $\mean$ and population variance $\variance$ of a random variable $X$
 \newcommand{\expectation}{\mathbb{E}}
@@
 where $\expectation \left[ X \right]$ denotes the expectation of a random variable $X$.
-The naive algorithm is numerically unstable when the variance is orders of magnitudes smaller than the mean, as this can lead to catastrophic cancellations.
+This naive algorithm is numerically unstable when the variance is orders of magnitudes smaller than the mean, as this can lead to catastrophic cancellations.
 We thus compute the mean and variance with the parallel algorithm of~\cite{chan1982updating}.
@@
 \end{equation}
-\begin{algorithm}[ht]
+\begin{algorithm}[tb]
   \begin{algorithmic}

### 2019-01-20 writing/thesis/chapters/results.tex
Changes.

@@
   \label{eq:Lp-nrom}
-  \Vert f(x) \Vert_p = \left( \int_K \vert f(x) \vert^p d\mu  \right)^{1/p}.
+  \Vert f(x) \Vert_p = \left( \intddomain{ \vert f(\bm{x}) \vert^p}  \right)^{1/p}.
 \end{equation}
@@
 We first observe that for our approximation space $\broken$ we can split up the error as a sum over all cells.
-We evaluate the cell-wise error with Gaussian quadrature using \cref{eq:integration-by-substitution}
+We evaluate the cell-wise error with Gaussian quadrature~\pcref{eq:quadrature,eq:integration-by-substitution}
  \begin{equation}
@@
    \left( \sum_{\cell[i] \in \broken}
-    \left( V \sum_{\bm{j}} \vert f^{\cell[i]}(\quadNode[j], t) - \hat{f}^{\cell{i}}(\quadNode[j], t) \vert^p \quadWeight[j] \right) \right)^{1/p}.
+    \left( V \sum_{\bm{j}} \vert f^{\cell[i]}(\quadNode[j], t) - \hat{f}^{\cell{i}}(\quadNode[j], t) \vert^p \, \quadWeight[j] \right) \right)^{1/p}.
  \end{equation}
 Here, a superscript of $\cell[j]$ denotes the restriction of the function to a grid cell.
-To increase the quality of the error computation, we evaluate both analytical and approximate solution at the quadrature nodes of a scheme with 10 quadrature nodes $\quadNode[j]$ with weights $\quadWeight[j]$.
+To increase the quadrature quality, we evaluate both analytical and approximate solution at the quadrature nodes of a scheme with 10 quadrature nodes $\quadNode[j]$ with weights $\quadWeight[j]$.
 We then use these nodes to compute the approximation error per cell.
@@
 The size of the slope is then the convergence order.
-Looking at the plot for the $L_2$ error~(\cref{fig:convergence-l2-error}) shows that our method converges for all tested polynomial orders.
+The plot for the $L_2$ error~(\cref{fig:convergence-l2-error}) shows that our method converges for all tested polynomial orders.
 Note that the error for the finest grid with order 6 is worse than the error for order 5.
-For all other meshsizes and orders, a higher order indicates a smaller error.
-If we compare our errors with the optimal order of convergence, we notice that while order 1 exhibits the theoretical order of convergence of 2, larger polynomial orders lead to diminishing returns.
+For all other meshsizes and orders, a higher order implies a smaller error.
+Comparing our errors with the optimal order of convergence $N+1$, we notice that while our scheme exhibits the theoretical order of convergence of 2 for a polynomial order $N=1$, orders have diminishing returns.
 
@@
 In~\cite{dumbser2010arbitrary}, which use a similar numerical method and the same scenario, but a different grid, \citeauthor{dumbser2010arbitrary} achieves the optimal order for most polynomial orders.
-Some \textsc{dg}-methods of odd order only achieve a numerical convergence order of $N+\nicefrac{1}{2}$\todo{Odd polynomial order or convergence order?}.
+Some \textsc{dg}-methods of even polynomial order only achieve a numerical convergence order of $N+\nicefrac{1}{2}$.
+The exact theoretical reason for this is unclear but it shares characteristics with the behaviour of other \dg{}-schemes.
+We refer the interested reader to the discussion of error estimates for nonlinear problems and for multi-dimensional problems with \dg{}-schemes of~\cite{hesthaven2008nodal}.
 
@@
 After we established that our scheme converges, we evaluate it using standard \textsc{cfd} testing scenarios that either have an analytical solution or for which we have a reference solution.
-% Show:
-% \begin{itemize}
-% \item Taylor-Green High Order
-%   LIC, Plot v/p ana vs.\ real
-% \item ABC Medium Order
-%   Plot p ana.\ vs real
-% \item Lid-Driven Cavity
-%   Show LIC, maybe plot over x?
-% \end{itemize}
 
 \sidetitle{Taylor-Green Vortex}
-We used an \aderdg{}-scheme of order 5 with a mesh of size $27 \times 27$ cells to simulate the Taylor-Green Vortex.
+We used an \aderdg{}-scheme of order 5 with a mesh of size $27 \times 27$ cells to simulate the Taylor-Green Vortex~\pcref{eq:taylor-green}.
 The simulation ran for \SI{10}{\s}.
@@
 Furthermore, we compare our results with the analytical solution for the incrompressible case.
-We achieve a small error~(\cref{fig:taylor-green-result}) for both pressure and velocity.
-The small errors are expected and not only stem from numerical inaccuracies but primarily from the fact that we simulate a compressible fluid.
-Note that the error is small over the entire domain, and not only close to the boundary, where we impose the analytical solution.
+We achieved a small error~(\cref{fig:taylor-green-result}) for both pressure and velocity.
+The small errors are expected and not only stem from numerical inaccuracies but primarily from the fact that we simulated a compressible fluid.
+Note that the error is small over the entire domain, and not only close to the boundary, where we imposed the analytical solution.
 Overall, we notice a very good agreement with both the analytical solution and the results of~\cite{dumbser2016high}.
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{thesis_taylor_green_stream}
-  \caption{Streamlines for Taylor-Green vortex}
-  \label{fig:taylor-green-streamlines}
+  \includegraphics[trim={0.0cm 0.0cm 0.5cm 0.5cm},clip]{thesis_taylor_green_stream}
+  \caption{\label{fig:taylor-green-streamlines}%
+    Streamlines for Taylor-Green vortex}
 \end{figure}
@@
     The former is represented by the scatter plot, the latter by the gray line.
-    Note that we only show every 5th point.}
+    Note that we only show every 5th point.
+    The other variable of the slice is held at 0.}
 \end{figure}
@@
 \end{figure}
-We used an \aderdg{}-scheme of order 2 with a mesh consisting of $27 \times 27 \times 27$ cells to simulate the \textsc{abc}-flow.
+We used an \aderdg{}-scheme of order 2 with a mesh consisting of $27 \times 27 \times 27$ cells to simulate the \textsc{abc}-flow~\pcref{eq:abc-flow}.
 We ran the simulation for \SI{1}{\s}.
 Our solution for the pressure shows an excellent agreement~(\cref{fig:abc-result}) with the analytical solution.
-We thus shows that our implementation can also handle three-dimensional scenarios.
+We thus show that our implementation can also handle three-dimensional scenarios.
 
@@
   \centering
-  \begin{subfigure}[t]{0.4\textwidth}
+  \begin{subfigure}[t]{0.5\textwidth}
     \centering
-    \includegraphics[width=1.2\textwidth]{thesis_lid_driven_cavity_stream}
+    \includegraphics[]{thesis_lid_driven_cavity_stream}
     \caption{\label{fig:lid-driven-cavity-streamlines}%
@@
   \end{subfigure}~%
-  \begin{subfigure}[t]{0.7\textwidth}
+  \begin{subfigure}[t]{0.5\textwidth}
     \centering
@@
     \caption{\label{fig:lid-driven-cavity-result}%
-      Plot of velocity slices. Lines are our soulution, scatter plot shows reference solution~\cite{ghia1982high}.}
+      Plot of velocity slices. Lines are our soulution, scatter plot shows reference solution~\cite{ghia1982high}.
+      For each slice, the other variable is hold constant at the center of the domain (0).}
   \end{subfigure}
 
-  \caption{Lid-Driven Cavity solution at $t=\SI{30}{\s}$}
-  \label{fig:lid-driven-cavity}
+  \caption{\label{fig:lid-driven-cavity}%
+    Lid-Driven Cavity solution at $t=\SI{30}{\s}$}
+
 \end{figure}
-We used a \muscl{}-limited \aderdg{}-scheme of order 3 with a mesh of size $27 \times 27$ for the Lid-Driven Cavity.
+We used a \muscl{}-limited \aderdg{}-scheme of order 3 with a mesh of size $27 \times 27$ and a simulation time of $t = \SI{30}{\s}$ for the lid-driven cavity~\pcref{eq:lid-driven-cavity}.
 The streamlines~(\cref{fig:lid-driven-cavity-streamlines}) agree with the expected solution but have two smaller, secondary vortices in the bottom corners.
@@
 Surprisingly, the limiter was not activated at all.
-We noticed that we need the limiter when we use a lower speed of sound and thus a flow with larger Mach number.
+We noticed that we need the limiter when we use a lower speed of sound and thus have a flow with larger Mach number.
 
@@
 \end{figure}
-We ran our first scenario, the cosine bubble, with an \aderdg{}-scheme of order 4 and the adaptive mesh criterion \cref{eq:refinement-criterion} with thresholds of $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$.
-Our coarsest level has $3^3$ cells, our finest level has $3^4$ cells.
-We thus have a resolution of ca.\ \SI{37.037}{\m} up to \SI{12.3457}{\m}.
+We ran our first scenario, the cosine bubble~\pcref{eq:cosine-bubble}, with an \aderdg{}-scheme of order 4 and the adaptive mesh criterion \cref{eq:refinement-criterion} with thresholds of $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$ and the total variation of the potential temperature $\potT$ as indicator variable.
+Our coarsest level had $3^3$ cells, our finest level had $3^4$ cells.
+We thus had a resolution of ca.\ \SI{37.037}{\m} up to \SI{12.3457}{\m}.
 
-The coarse structure of our simulation~(\cref{fig:cosine-bubble-contour-ours}) agree with the reference solution~(\cref{fig:cosine-bubble-contour-giraldo} of~\cite{giraldo2008study} but the fine details differ.
-In contrast to us, they use a scheme of polynomial order 10 and a uniform spatial resolution of \SI{20}{\m}.
-Furthermore, we use a physical viscosity of $0.1$, which explains why we have fewer spurious details while using a lower order.
-This becomes more clear, by comparing the potential temperature pertubation.
+The coarse structure of our results~(\cref{fig:cosine-bubble-contour-ours}) agrees with the reference solution~(\cref{fig:cosine-bubble-contour-giraldo} of~\cite{giraldo2008study} but the fine details differ.
+In contrast to us, they used a scheme of polynomial order 10 and a uniform spatial resolution of \SI{20}{\m}.
+Furthermore, we used a physical viscosity of $0.1$, which explains why we have fewer spurious details while using a lower order.
+This becomes clearer by comparing the potential temperature pertubation.
 Our solution has a smooth distribution inside the cloud~(\cref{fig:cosine-bubble-potT-ours}) while the results of~\cite{giraldo2008study} show sharp peaks~(\cref{fig:cosine-bubble-potT-giraldo}).
@@
   \caption{\label{fig:cosine-bubble-potT}%
-    $z$ vs.\ pertubation of potential temperature for the cosine bubble scenario at $t=\SI{700}{\s}$.
+    Height $z$ vs.\ pertubation of potential temperature for the cosine bubble scenario at $t=\SI{700}{\s}$ and $x = \SI{500}{\m}$.
   }
@@
 \sidetitle{Two Bubbles}
-We ran the second scenario with the same \amr{} settings as the first one.
+We ran the second scenario, the two bubbles scenario~\pcref{eq:bubbles-values}, with the same \amr{} settings as the first one.
 The results in (\cref{fig:two-bubbles-contour}) are comparable to the reference solution~\cite{muller2010adaptive} for the first seven minutes.
@@
 \begin{description}
-\item[AMR] We use a coarse mesh with just $27 \times 27$ cells.
-  Each cell can be refined up to three times.
-  That is, the cells have sidelengths of roughly $\left(\SI{37.04}{\m}, \SI{12.35}{\m} \right)$.
-  As refinement thresholds we use $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$ in \cref{eq:refinement-criterion}.
-  \todo{Maybe not restate here?}
+\item[AMR] We used a coarse mesh with just $27 \times 27$ cells.
+  Each could can be refined once.
+  That is, the cells had sidelengths of roughly \SI{37.04}{\m} and  \SI{12.35}{\m}.
+  As refinement thresholds we used $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$ in \cref{eq:refinement-criterion}.
   They are the exact same settings that we used for the bubble scenarios in the previous section.
-\item[Fine] We use a uniform grid where all cells have a sidelength corresponding to the finest mesh of the \amr{}-test case.
-  In addition, we disable the reduction of global observables.
+\item[Fine] We used a uniform grid where all cells had a sidelength corresponding to the finest mesh of the \amr{}-test case.
+  In addition, we disabled the reduction of global observables.
 \end{description}
-Note, that while our \amr{} criterion is able to cope with an additional, coarser level, the current implementation in \exahype{} is unstable for this scenario.
+Note, that while our \amr{} criterion is able to cope with an additional, coarser level, the current implementation in \exahype{} is unstable in this case.
 This is why we only report an \amr{} run with one level of dynamic refinement.
 
-\begin{figure}[htb]
-  \centering
-  \includegraphics{thesis_two_bubbles_contour_t600_noamr} 
-  \caption{\label{fig:two-bubbles-noamr-contour}%
-    Two bubbles run with fully refined mesh}
-\end{figure}
+% \begin{figure}[htb]
+%   \centering
+%   \includegraphics{thesis_two_bubbles_contour_t600_noamr} 
+%   \caption{\label{fig:two-bubbles-noamr-contour}%
+%     Two bubbles run with fully refined mesh}
+% \end{figure}
 For both settings, we used an \aderdg{}-method of order $4$ and thus have a minimal effective resolution of ca.\ $\SI{3.09}{\m}$.
-The final result for the run with the fully refined mesh (\cref{fig:two-bubbles-noamr-contour}) looks identical to the \amr{} results (\cref{fig:two-bubbles-contour}) shown in the previous section.
-Note that the \amr{} criterion manages to track the bubble correctly~(\cref{fig:two-bubbles-amr-grid}) and is introduces only small errors~(\cref{fig:two-bubbles-amr-error})\todo{Increase font size a bit more}.
+%The final result for the run with the fully refined mesh (\cref{fig:two-bubbles-noamr-contour}) looks identical to the \amr{} results (\cref{fig:two-bubbles-contour}) shown in the previous section.
+Note that the \amr{} criterion manages to track the bubble correctly~(\cref{fig:two-bubbles-amr-grid}) and introduces only small errors~(\cref{fig:two-bubbles-amr-error}) compared to the solution with the fully refined mesh\todo{Increase font size a bit more}.
 
@@
 We now want to compare the time to solution for both settings.
-To ensure a fair comparison, we ran both configurations with the same optimisation options:
+To ensure a fair comparison, we ran both configurations with the same optimization options:
 \begin{verbatim}
@@
 We ran the simulation without plotters to focus on the performance of the numerics and the mesh refinement routines.
-
-We used a single node of the Haswell-nodes of the Supermuc (Phase 2).
+We used a single node Supermuc Phase 2.
 The node has two Intel® Haswell Xeon Processor E5-2697 v3 \textsc{cpu}s with 14 cores each.
@@
 
-The \amr{}-method took \SI{98654.1}{\s} (\SI{1}{\day} \SI{3}{\hour} \SI{24}{\minute} \SI{14}{\s})
+The \amr{}-run took \SI{98654}{\s} (\SI{1}{\day} \SI{3}{\hour} \SI{24}{\minute} \SI{14}{\s})
 while the fully refined grid took \SI{169071}{\s} (\SI{1}{\day} \SI{22}{\hour} \SI{57}{\minute} \SI{51}{\s}).
@@
 
-To summarise, our \amr{} criterion saved a significant amount of computational effort while preserving the fine details of a fully refined grid.
+To summarize, our \amr{} criterion saved a significant amount of computational effort while preserving the fine details of a fully refined grid.
+
 \section{Reactive Euler \textit{\&} Navier Stokes}\label{sec:results-reactive}
-As a final benchmark, we used the reactive Navier-Stokes equations.
+As a final benchmark, we used the \textsc{cj}-detonation wave~\pcref{eq:cj-detonation} to evaluate the reactive Navier-Stokes equations.
 We used a limiting \aderdg{}-scheme with an order of 3.
 For runs without viscosity we used a meshsize of $81 \times 81$, for the runs with a viscosity of $\mu = 0.01$ we used a coarser mesh consisting in $27 \times 27$ cells.
-We chose the smaller grid because our boundary conditions become unstable for finer grids.
-A reason for this might be the fact that we are unable to prescribe the gradient at the boundary in the \muscl{} implementation of \exahype{}.
+We chose the smaller grid because our boundary conditions became unstable for finer grids.
+A reason for this might be the fact that we are unable to prescribe the gradient at the boundary in our \muscl{} implementation.
 For some runs, we used the \textsc{dmp} settings
@@
 where the \texttt{dmp\_relaxation\_parameter} refers to $\varepsilon_0$ and \texttt{dmp\_difference\_scaling} refers to $\varepsilon$ in \cref{eq:limiting-dmp}.
-The large value of $\varepsilon_0$ is necessary, as otherwise the full domain is refined.
+The large value of $\varepsilon_0 = 0.05$ is necessary, as otherwise the full domain is refined.
 We use $\Qrho, \pressure$ and $\QZZ$ as \textsc{dmp} variables.
@@
     Slices along the $x$-axis for our three configurations.
+    The coordinate $z = 0$ is held constant.
     We only show one half of the slice because the scenario is symmetric.

### 2019-01-20 writing/thesis/chapters/scenarios.tex
Changes.

@@
 \chapter{Scenarios}\label{chap:scenarios}
-\begin{table}[htb]
+\begin{table}[b]
   \centering
@@
 Taylor-Green Vortex~\cite{dumbser2016high} & \cmark{} & \xmark{} & \xmark{} & \xmark{} \\
-Lid Driven Cavity~\cite{fambri2017space} & \cmark{} & \xmark{} & \xmark{} & \cmark{} \\
 \textsc{ABC}-Flow~\cite{tavelli2016staggered} & \cmark{} & \xmark{} & \xmark{} & \xmark{} \\
+Lid Driven Cavity~\cite{fambri2017space} & \xmark{} & \xmark{} & \xmark{} & \cmark{} \\
+Cosine Bubble~\cite{giraldo2008study} & \xmark{} & \cmark{} & \xmark{} & \xmark{} \\
 Two Bubbles~\cite{robert1993bubble,muller2010adaptive} & \xmark{} & \cmark{} & \xmark{} & \xmark{} \\
-Cosine Bubble~\cite{giraldo2008study} & \xmark{} & \cmark{} & \xmark{} & \xmark{} \\
 \textsc{CJ}-Detonation~\cite{helzel2000modified,hidalgo2011ader} & \xmark{} & \xmark{} & \cmark{} & \cmark{} \\
@@
 \item The manufactured solution is an exact solution for our equation set and can be thus used to reliably evaluate the quality of our implementation.
-\item The Taylor-Green vortex, the \textsc{abc}-flow and the lid-driven cavity flow are standard \textsc{cfd} testing scenarios for which we have a reference result.
+\item The Taylor-Green vortex, the \textsc{abc}-flow and the lid-driven cavity flow are standard \textsc{cfd} testing scenarios for which we have a reference solution.
 \item The bubble scenarios are simple examples for flows over a realistic background atmosphere.  
@@
 
-We describe some scenarios in terms of the primitive variables $(\Qrho, \Qv, \pressure)$, these can be converted to the conservative variables by the definition of momentum and the definition of energy.
+We describe some scenarios in terms of the primitive variables $(\Qrho, \Qv, \pressure)$, these can be converted to the conservative variables by the definition of momentum and the equation of state \cref{eq:eos}.
+All scenarios, with the exception of the \textsc{cj}-detonation wave, use only the compressible Navier-Stokes equations and do not use the advection equation.
+This corresponds to setting $\QZ = 0$ and $q_0 = 0$.
 
@@
 This is why we follow the method of manufactured solutions~\cite{salari2000code} and create our own.
-Following~\cite{dumbser2010arbitrary}, we assume the solution in primitive variables
+Following~\cite{dumbser2010arbitrary}, we assume that
 \begin{align}\label{eq:manufactured-solution}
@@
 \end{align}
-We set the constants
+We use the constants
 \begin{equation}
@@
 Our computation of the source term can be found at XXX\todo{Cite github repository with notebook!}.
-\Cref{eq:manufactured-solution} then solves our \pde{} combined with the derived source exactly.
+In combination with the derived source term, \cref{eq:manufactured-solution} then is an exact solution of our \pde{}.
 
@@
 \sidetitle{Taylor-Green Vortex}
-%\subsection{Taylor-Green Vortex}
 An interesting testing scenario is the Taylor-Green Vortex, which exhibits a complicated flow from a simple initial condition.
@@
   \begin{split}
-  \Qrho(\bm{x}, t) &= 1\\
+  \Qrho(\bm{x}, t) &= 1,\\
   \Qv(\bm{x}, t) &= \exp(-2 \mu t)
@@
 - \cos(x) \sin(y) 
-    \end{pmatrix} \\
-  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \nicefrac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C
+    \end{pmatrix}, \\
+  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \nicefrac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C,
   \end{split}
@@
 
-As initial conditions we use \cref{eq:taylor-green} at time $(t = 0)$ and as boundary conditions we impose the solution and the corresponding gradients.
-We use a viscosity of $\mu = 0.1$.
+We use a viscosity of $\mu = 0.1$ and Cauchy boundary conditions.
 
-\sidetitle{Lid-Driven Cavity Flow}
+\sidetitle{ABC-Flow}
+%\subsection{ABC-Flow}
+We use the Arnold–Beltrami–Childress (\textsc{abc}) flow as a simple example of a three-dimensional scenario~\cite{tavelli2016staggered}.
+Unlike the three-dimensional Taylor-Green vortex, the \textsc{abc}-flow has the analytical solution
+\begin{align}
+  \label{eq:abc-flow}
+  \begin{split}
+  \Qrho(\bm{x}, t) &= 1,\\
+  \Qv(\bm{x}, t) &= \phantom{-} \exp(-1\mu t)
+  \begin{pmatrix}
+    \sin(z) + \cos(y)\\
+    \sin(x) + \cos(z)\\
+    \sin(y) + \cos(x)
+  \end{pmatrix}, \\
+  \pressure(\bm{x}, t) &= -\exp(-2 \mu t) \, \left(\cos(x)\sin(y) + \sin(x)\cos(z) + \sin(z)\cos(y)\right)
+  + C
+  \end{split}
+\end{align}
+in the incompressible limit.
+Here, $C = \nicefrac{100}{\gamma}$ is an arbitrary constant.
+We use a viscosity of $\mu = 0.01$ and Cauchy boundary conditions.
+
+\sidetitle{Lid-Driven Cavity}
 %\subsection{Lid-Driven Cavity Flow}
@@
 The flow is driven entirely by the boundary conditions.
-They consist in four no-slip walls where the upper wall has a constant velocity $\Qv = (1.0, 0)$.
+They consist in four no-slip walls~\pcref{eq:no-slip} where the upper wall has a constant velocity $\Qv^w = (1.0, 0)$.
 We want to simulate a flow with a Mach number of $M = 0.1$ and a Reynolds number of $\text{Re} = 100$~\cite{fambri2017space}.
@@
   \begin{split}
-  \Qrho(\bm{x}) &= 1\\
-  \Qv(\bm{x}) &=  \bm{0}\\
+  \Qrho(\bm{x}) &= 1,\\
+  \Qv(\bm{x}) &=  \bm{0},\\
   \pressure(\bm{x}) &= \frac{100}{\gamma}.
@@
 % p = (u/M)^2 / gamma
-This scenario is surprisingly difficult for an \textsc{ader-dg} scheme as the boundary conditions can lead to a discontinuity at the corners, because the wall speed is discontinuous.
-Therefore, this scenario is a good choice to test the stability of our limited scheme.
-
-\sidetitle{ABC-Flow}
-%\subsection{ABC-Flow}
-We use the Arnold–Beltrami–Childress (\textsc{abc}) flow as a simple example of a three-dimensional scenario~\cite{tavelli2016staggered}.
-This scenario has, unlike the three-dimensional version of the Taylor-Green vortex, an analytical solution at least for the incompressible case.
-Unlike the three-dimensional Taylor-Green vortex, the \textsc{abc}-flow has the analytical solution
-\begin{align}
-  \label{eq:abc-flow}
-  \begin{split}
-  \Qrho(\bm{x}, t) &= 1\\
-  \Qv(\bm{x}, t) &= \phantom{-} \exp(-1\mu t)
-  \begin{pmatrix}
-    \sin(z) + \cos(y)\\
-    \sin(x) + \cos(z)\\
-    \sin(y) + \cos(x)
-  \end{pmatrix} \\
-  \pressure(\bm{x}, t) &= -\exp(-2 \mu t) \, \left(\cos(x)\sin(y) + \sin(x)\cos(z) + \sin(z)\cos(y)\right)
-  + C
-  \end{split}
-\end{align}
-in the incompressible limit.
-Here, $C = \nicefrac{100}{\gamma}$ is an arbitrary constant.
-We use a viscosity of $\mu = 0.01$.
+This scenario is surprisingly difficult for an \textsc{ader-dg} scheme as the boundary conditions can lead to a discontinuity at the corners, because the wall speed is discontinuous~\cite{fambri2017space}.
+Therefore, this scenario is a good choice to test the stability of our scheme.
 
 \sidetitle{CJ Detonation Wave}
-We investigate the radialsymmetric CJ detonation wave scenario from~\cite{helzel2000modified}.
+We investigate the radialsymmetric Chapman-Jouget (\textsc{cj}) detonation wave scenario from~\cite{helzel2000modified}.
 This scenario for the reactive Navier Stokes equations is set up in a 2D box of size $[-1, 1] \times [-1, 1]$ surrounded by no-slip walls~\pcref{eq:no-slip}.
@@
 Inside a circle of radius $0.3$ we have totally unburnt gas, outside of this circle we have burned gas.
-Let $\alpha =  \operatorname{atan2}(y,x)$ be the angle in polar coordinates.
+Let $\alpha =  \operatorname{atan2}(z,x)$ be the angle in polar coordinates.
 We use the initial conditions
-\begin{equation}
+\begin{equation}\label{eq:cj-detonation}
 \begin{alignedat}{6}
@@
 \begin{equation}
-  \potT = T \frac{p_0}{p}^{R/c_p},
+  \potT = T \left( \frac{p_0}{p} \right)^{R/c_p},
 \end{equation}
 is useful.
-The constant $p_o = \SI{10e5}{\Pa}$ is the reference pressure,.
-Solving for $T$ leads to
+The constant $p_o = \SI{10e5}{\Pa}$ is the reference pressure.
+Solving this equation for $T$ leads to
 \begin{equation}
@@
 \end{equation}
-To allow for an easier description of the initial conditions we split the $\potT$ into a background state $\backgroundPotT$ and a pertubation $\pertubationPotT$
+To allow for an easier description of the initial conditions we split the potential temperature into a background state $\backgroundPotT$ and a pertubation $\pertubationPotT$
 \begin{equation}
@@
 The initial conditions for pressure and density can be computed directly from the \textsc{pde} once few assumptions have been given.
-We assume that $\backgroundPotT$ is constant over the entire domain.
+We assume that $\backgroundPotT$ is constant over the entire domain~\cite{giraldo2008study}.
 Inserting the definition of potential temperature, given by \cref{eq:potTToT}, into the equation of state~\pcref{eq:eos} leads us to
@@
 Next, we compute the pertubated potential temperature $\potT$ and use \cref{eq:potTToT} to convert it to temperature.
-The density $\Qrho(\bm{x})$ can now be evaluated with \cref{eq:temperature}.
+The density $\Qrho(\bm{x})$ can now be evaluated with the thermal equation of state \cref{eq:temperature}.
 Finally, we compute the energy by inserting pressure and density into the equation of state~(\ref{eq:eos}).
@@
 This leaves us with one problem:
-The adiabatic free-slip boundary conditions defined by~\vref{eq:free-slip} are no longer valid.
-Concretely, we need to impose a viscous heat flux to ensure that the atmosphere stays in hydrostatic balance~\cite{giraldo2008study}
+The adiabatic free-slip boundary conditions defined by~\cref{eq:free-slip} are no longer valid.
+Concretely, we need to impose the viscous heat flux
 \begin{equation}
@@
   \viscFlux_{\QE} = \kappa \pdv{\overline{T}}{z} =
-\kappa \frac{R \overline{\theta} \left(\frac{\overline{p}{\left (z \right )}}{p_{0}}\right)^{\frac{R}{c_{p}}} \frac{d}{d z} \overline{p}{\left (z \right )}}{c_{p} \overline{p}{\left (z \right )}}.
+\kappa \frac{R \overline{\theta} \left(\frac{\overline{p}{\left (z \right )}}{p_{0}}\right)^{\frac{R}{c_{p}}} \frac{d}{d z} \overline{p}{\left (z \right )}}{c_{p} \overline{p}{\left (z \right )}}
 \end{equation}
+to ensure that the atmosphere stays in hydrostatic balance~\cite{giraldo2008study}.
 The background pressure can be reconstructed by \cref{eq:hydrostatic-background-pressure}, its derivative is given by \cref{eq:hydrostatic-balance-potT}.
@@
 All scenarios use the gravitational source term~\pcref{eq:source-gravity} and the splitting of density and pressure~\pcref{eq:momentum-equation-split}.
-We use the following set of fluid dependent constants for these scenarios
+We use the following set of constants for these scenarios
 \begin{equation}\label{eq:atmosphere-constants}
-    \gamma = 1.4 ,\qquad \Pr =  0.71 ,\qquad R = 287.058 ,\qquad p_0 = 10000,
+    \gamma = 1.4 ,\qquad \Pr =  0.71 ,\qquad R = 287.058 ,\qquad p_0 = 10000, \qquad g = 9.81,
 \end{equation}
@@
 
-\sidetitle{Two Bubbles}
-%\subsection{Two Bubbles}
-As a simple test case we consider a scenario where we have one large warm air bubble in the middle, and a small cold bubble on the top.
-This scenario was first published by \citeauthor{robert1993bubble}~\cite{robert1993bubble}.
-We use a domain of $\SI{1}{\km} \times \SI{1}{\km}$.
+\sidetitle{Cosine Bubble}
+As a simple test case we consider the cosine bubble scenario where we have one large warm air bubble in the middle of the domain~\cite{giraldo2008study}.
 The initial conditions of the scenario are given by a pertubation of a hydrostatic equlibrium.
-We use a background potential temperature of $\backgroundPotT = 300$.
-
+We use a background potential temperature of $\backgroundPotT = 300$ and a domain of $\SI{1}{\km} \times \SI{1}{\km}$.
 Let
@@
 The pertubation is given by the function
-\begin{equation}
-  \label{eq:bubbles-pertubation}
-  \pertubationPotT =
-  \begin{cases}
-    A & r \leq a \\
-    A \exp \left( - (r-a)^2/s^2 \right) & r > a,
-    \end{cases}
-\end{equation}
-where $A$ denotes the maximal pertubation, $a$ is the size of the bubble and $s$ is the decay rate.
-We have two bubbles, with the values
-\begin{equation}
-  \label{eq:bubbles-values}
-\begin{alignedat}{6}
-  & \text{warm:} \qquad && A = 0.5 \quad&& a = \SI{150}{\m} \quad&& s = \SI{50}{\m} \quad&& x_c = \SI{500}{\m} \quad&& z_c = \SI{300}{\m},\\
-  & \text{cold:} \qquad && A = -0.15 \quad&& a = \SI{0}{\m} \quad&& s = \SI{50}{\m} \quad&& x_c = \SI{560}{\m} \quad&& z_c = \SI{640}{\m}.
-  \end{alignedat}
-\end{equation}
-
-Similar to~\cite{muller2010adaptive}, we use a constant viscosity of $\mu = 0.1$ to regularize the solution.
-
-\sidetitle{Cosine Bubble}
-%\subsection{Cosine Bubble}
-A similar scenario is the cosine bubble as described in~\cite{giraldo2008study}.
-In this scenario the flow is driven by one warm bubble.
-We use the same procedure as before to compute the initial conditions, again with $\backgroundPotT = 300$ but with a pertubation of the form
 \begin{align}
@@
 \end{align}
-where $r$ again is the radius to the center~\pcref{eq:radius} and constants
-\begin{equation}\label{eq:density-bubble}
+where $A$ denotes the maximal pertubation and $a$ is the size of the bubble.
+We use the constants
+\begin{equation}\label{eq:cosine-bubble}
   A = 0.5 \quad a = \SI{250}{\m} \quad x_c = \SI{500}{\m} \quad z_c = \SI{350}{\m}.
 \end{equation}
-Similar to the previous scenario, we use a constant viscosity of $\mu = 0.1$.
+We use a constant viscosity of $\mu = 0.1$.
+
+\sidetitle{Two Bubbles}
+As a simple test case we consider a scenario where we have one large warm air bubble in the middle and a small cold bubble on the top.
+This scenario was first published by \citeauthor{robert1993bubble}~\cite{robert1993bubble}.
+We use the same procedure as before to compute the initial conditions, again with $\backgroundPotT = 300$ but with a pertubation of the form
+
+\begin{equation}
+  \label{eq:bubbles-pertubation}
+  \pertubationPotT =
+  \begin{cases}
+    A & r \leq a, \\
+    A \exp \left( - \frac{(r-a)^2}{s^2} \right) & r > a,
+    \end{cases}
+\end{equation}
+where $s$ is the decay rate and $r$  is the radius to the center~\pcref{eq:radius}.
+We have two bubbles, with constants
+\begin{equation}
+  \label{eq:bubbles-values}
+\begin{alignedat}{6}
+  & \text{warm:} \qquad && A = 0.5, \quad&& a = \SI{150}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{500}{\m,} \quad&& z_c = \SI{300}{\m},\\
+  & \text{cold:} \qquad && A = -0.15, \quad&& a = \SI{0}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{560}{\m}, \quad&& z_c = \SI{640}{\m}.
+  \end{alignedat}
+\end{equation}
+This scenario is interesting because we have small scale details that are important for the resulting flow.
+Similar to~\cite{muller2010adaptive} and to the previous scenario, we use a constant viscosity of $\mu = 0.1$ to regularize the solution.
 

### 2019-01-20 writing/thesis/pages/abstract.tex
Changes.

@@
 This thesis is concerned with the simulation of clouds with the ExaHyPE framework.
-ExaHyPE is an engine for hyperbolic PDEs that uses the ADER-DG scheme.
+ExaHyPE is an engine for hyperbolic partial differential equations that uses the ADER-DG scheme.
 
-We use the compressible Navier-Stokes (NS) equations with heat conduction to simulate the dynamics of clouds.
-Due to the diffusive components, the NS-Equations are not hyperbolic.
+We use the compressible Navier-Stokes equations for computational fluid dynamics.
+Due to the diffusive components, the Navier-Stokes equations are not hyperbolic.
 We thus need to modify parts of the numerical scheme.
+Furthermore, we extend the equation set to the reactive compressible Navier-Stokes equations which include a source term that models chemical reactions.
 
-Furthermore, we extend the equation set to the reactive compressible Navier-Stokes equations which include a source term that models chemical reactions.
+We develop a gradient-based, global adaptive mesh refinement indicator that finds cells with unusually steep gradients.
+
+Our implementation is evaluated for standard two and three dimensional fluid dynamics test cases, for flows over a realistic background atmosphere and for a reactive detonation wave.
+Furthermore, we perform a convergence test and a time-to-solution benchmark that evaluates our proposed AMR criterion.
 

### 2019-01-21 writing/thesis/chapters/results.tex
Small tweaks.

@@
     \centering
-    \includegraphics[]{thesis_lid_driven_cavity_stream}
+    \includegraphics[trim={0.05cm 0.05cm 0.55cm 1.0cm},clip]{thesis_lid_driven_cavity_stream}
     \caption{\label{fig:lid-driven-cavity-streamlines}%
@@
       Plot of velocity slices. Lines are our soulution, scatter plot shows reference solution~\cite{ghia1982high}.
-      For each slice, the other variable is hold constant at the center of the domain (0).}
+      For each slice, the other variable is hold constant at a value of zero.}
   \end{subfigure}
@@
     \centering
-    \includegraphics[scale=1.0]{thesis_cosine_bubble_contour_t700}
+    \includegraphics[trim={0.00cm 0.00cm 6.35cm 0.0cm},clip]{thesis_cosine_bubble_contour_comparison}
     \caption{\label{fig:cosine-bubble-contour-ours}%
@@
     \centering
-    \includegraphics{giraldo_results_cosine_bubble}
+    \includegraphics[trim={6.8cm 0.00cm 0cm 0.0cm},clip]{thesis_cosine_bubble_contour_comparison}
     \caption{\label{fig:cosine-bubble-contour-giraldo}%
@@
   \centering
-  \begin{subfigure}[t]{0.5\textwidth}
+  \begin{subfigure}[t]{0.45\textwidth}
     \centering
-    \includegraphics{thesis_cosine_bubble_pertubation}
+    \includegraphics[trim={0.00cm 0.00cm 8.4cm 0.0cm},clip]{thesis_cosine_bubble_pertubation_comparison}
     \caption{\label{fig:cosine-bubble-potT-ours}%
@@
   \end{subfigure}~%
-  \begin{subfigure}[t]{0.5\textwidth}
+  \begin{subfigure}[t]{0.55\textwidth}
     \centering
-    \includegraphics{giraldo_results_cosine_bubble_pertubation}
+    \includegraphics[trim={7.00cm 0.00cm 0.0cm 0.0cm},clip]{thesis_cosine_bubble_pertubation_comparison}
     \caption{\label{fig:cosine-bubble-potT-giraldo}%
@@
 
-% \begin{figure}[p]
-%   \vspace*{-4.5cm}
-%   \thisfloatpagestyle{empty}
-%   \centering
-%   \begin{subfigure}{1\textwidth}
-%     \centering
-%     \includegraphics{thesis_two_bubbles_contour_collage.pdf}
-%   \end{subfigure}
-%   \vspace*{1cm}
-%   \begin{subfigure}[t]{1\textwidth}
-%     \centering
-%     \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.0cm, clip, scale=1.2]{giraldo_results_two_bubbles}
-%   \end{subfigure}
-%   \caption{\label{fig:two-bubbles-contour}%
-%     Results for two bubble scenario.
-%     On the top is our, the bottom plots are taken from~\cite{muller2010adaptive}.
-%   Contour values for potential temperature pertubation are $-0.05, 0.05, 0.1, \ldots 0.45$.
-% }
-% \end{figure}
 \begin{figure}[p]
   \thisfloatpagestyle{empty}
+  \vspace*{-1cm}
   \centering
@@
     \centering
-  \includegraphics[trim={0cm 0cm 6cm 0cm},clip]{thesis_two_bubbles_contour_collage_comparison} 
+  \includegraphics[trim={0cm 0cm 5.6cm 0cm},clip]{thesis_two_bubbles_contour_collage_comparison} 
   \caption{Our \amr{} solution.}
@@
   % Without z axis on right \includegraphics[trim={8.16cm 0cm 0cm 0cm},clip]{thesis_two_bubbles_contour_collage_comparison} 
-  \includegraphics[trim={7.4cm 0cm 0cm 0cm},clip]{thesis_two_bubbles_contour_collage_comparison} 
+  \includegraphics[trim={6.2cm 0cm 0cm 0cm},clip]{thesis_two_bubbles_contour_collage_comparison} 
   \caption{Reference solution from~\cite{muller2010adaptive}.}
@@
      On the left is our solution, the right plots are taken from~\cite{muller2010adaptive}.
-     We modified the arrangement of the reference plots and the placement of its axes. 
+     We rescaled the reference plots and changed their arrangement and axes placement.
    Contour values for potential temperature pertubation are $-0.05, 0.05, 0.1, \ldots 0.45$.
@@
 %The final result for the run with the fully refined mesh (\cref{fig:two-bubbles-noamr-contour}) looks identical to the \amr{} results (\cref{fig:two-bubbles-contour}) shown in the previous section.
-Note that the \amr{} criterion manages to track the bubble correctly~(\cref{fig:two-bubbles-amr-grid}) and introduces only small errors~(\cref{fig:two-bubbles-amr-error}) compared to the solution with the fully refined mesh\todo{Increase font size a bit more}.
+Note that the \amr{} criterion manages to track the bubble correctly~(\cref{fig:two-bubbles-amr-grid}) and introduces only small errors~(\cref{fig:two-bubbles-amr-error}) compared to the solution with the fully refined mesh.
 

### 2019-01-21 writing/thesis/chapters/implementation.tex
Include corrections from proof reader.

@@
 It uses \softwareName{Intel® Threading Building Blocks} (\tbb{}) for shared memory parallelism and the \softwareName{Message Passing Interface} (\mpi{}) for distributed memory parallelism. 
-In the following we define a \enquote{user} as someone who implements the logic of a \pde{} but does not change the implementation of \exahype{} itself.
+In the following, we define a \enquote{user} as someone who implements the logic of a \pde{} but does not change the implementation of \exahype{} itself.
 This is in contrast with a \enquote{developer} whose scope is the entirety of the source code.
@@
   The methods \funName{boundaryConditions} first calls \funName{boundaryValues} and then solves the Riemann-problem at the boundary.
-  In many cases it thus suffices to only override the latter method.
+  Thus, it suffices in many cases to only override the latter method.
 \item Finally, the user can specify more options such as mesh size and spacing, simulation time, parallelization options, plotters, and optimization parameters.
@@
 \item Often, a mapping calls a method defined in \className{Solver}.
-  These implementation can differ between different solvers.
+  The implementation of this method can differ between different solvers.
 \item The actual numerical logic is outsourced to kernels.
@@
 The information for each \dg{}-cell is defined in the file \fileName{ADERDGCellDescrition.def}.
-Similar files exists for the finite volume solver but are not relevant for us.
+Similar files exist for the finite volume solver but are not relevant for us.
 These files are converted to \cpp{} files by the software \softwareName{DaStGen}~\cite{bungartz2008dastgen}.
@@
    \item In the function \funName{aderExtrapolatorNonlinear}, which implements the boundary extrapolation, we also compute the extrapolated gradient.
-    \item In the function \funName{spaceTimePredictorNonlinear} we also return the extrapolated gradient.
+    \item In the function \funName{spaceTimePredictorNonlinear}, we also return the extrapolated gradient.
   \end{itemize}
@@
 \end{itemize}
-Furthermore, we needed to change the templates for the glue code and needed to modify some function signatures to accompany the other changes.
+Additionaly, we needed to change the templates for the glue code and needed to modify some function signatures to accompany the other changes.
 
@@
   \item We reduce the observables in \funName{leaveCell} by calling the solver method \funName{reduceGlobalObservables} with the \varName{cellInfo} of the current cell as argument.
-    For the mapping \className{UpdateAndReduce} this is done in the method \funName{enterCell} instead.
+    For the mapping \className{UpdateAndReduce}, this is done in the method \funName{enterCell} instead.
   \item If we use \tbb{}, we merge the partially reduced observables in \funName{mergeWithWorkerThread} with \funName{reduceGlobalObservables} using the current reduced observables and the partially reduced observables from the worker.

### 2019-01-21 writing/thesis/chapters/introduction.tex
Include corrections from proof reader.

@@
 Both types of forecasts are difficult problems that are limited by a lack of computational power.
-Especially in a time, where the realization of exascale supercomputers is imminent, scalable numericals model become more and more important.
+Especially in a time where the realization of exascale supercomputers is imminent, scalable numericals model are becoming more and more important.
 Current climate and weather models are not ready for the exascale era~\cite{schulthess2018reflecting}.
@@
 Of course, a finer grid is not useful if the computational effort is too large.
-Thus, they also propose a compute rate of one simulated years per wall-clock day.
+Thus, also propose a compute rate of one simulated years per wall-clock day.
 An example of a recent supercomputing effort in this domain~\cite{fuhrer2018near} achieved a performance of 0.043 simulated years per wall-clock day with a resolution of $\SI{930}{\m}$ for a near-global simulation on the Piz Daint supercomputer.
-They used a \textsc{cosmo}-model which is based on a finite-difference approach.
+They used the \textsc{cosmo} 5.0 model which is based on a finite-difference approach.
 
@@
 \item In \cref{sec:navier-stokes}, we describe a coupling of the compressible Navier-Stokes equations for two and three dimensional problems.
-Furthermore, we adapt the equation set for scenarios with gravity.
-In addition, we present a coupling with an advection-reaction term.
+In addition, we adapt the equation set for scenarios with gravity and present a coupling with an advection-reaction term.
 \item We describe an \aderdg{} (\cref{sec:ader-dg}) and \muscl{}-scheme (\cref{sec:muscl}) for problems with diffusive terms.
   Moreover, we describe a combination of both methods in \cref{sec:limiting}, where we use the \muscl{}-scheme in cases where the \aderdg{}-method is unstable.
-\item In \cref{sec:amr}, we introduce an adaptive mesh refinement (\amr{}) method that checks, whether a local cell is an outlier.
-  As indicator function we use the total variation of the discrete solution and as outlier detection we use the mean and standard variance of this function.
+\item In \cref{sec:amr}, we introduce an adaptive mesh refinement (\amr{}) method that checks whether a local cell is an outlier.
+  As indicator function, we use the total variation of the discrete solution, and as outlier detection, we use the mean and standard variance of this function.
 \item In \cref{chap:implementation} we show how we implemented our proposed method using the \exahype{}-engine.

### 2019-01-21 writing/thesis/chapters/methods.tex
Include corrections from proof reader.

@@
 \chapter{An ADER-DG scheme for the Navier-Stokes Equations}\label{chap:methods}
-This chapter describes the numerical and physical background that is needed to simulate reacting fluids with good accuracy.
-We start with a description of the arbitrary high order derivatives (\ader{}) discontinuous Galerkin (\dg{}) method with a focus on equations that contain both advective and diffusive terms.
-We then seque into a short description of the \muscl{} scheme which is a second order finite volume method.
-
-We conclude this chapter by a description of finite volume limiting and adaptive mesh refinement (\amr{}).
+This chapter describes the numerical and physical background that is needed to simulate reacting fluids with high accuracy.
+We start with a description of the arbitrary high order derivatives (\ader{}) discontinuous Galerkin (\dg{}) method, with a focus on equations that contain both advective and diffusive terms.
+We then seque into a short description of the \muscl{} scheme, which is a second order finite volume method.
+
+We conclude this chapter with a description of finite volume limiting and adaptive mesh refinement (\amr{}).
 The limiting combines both numerical methods to achieve a stable, high-order method and the \amr{} allows us to perform high quality simulations with a smaller computational cost.
@@
 which are the Euler equations coupled with an advection equation.
-In this equation $\bm{a} \otimes \bm{b} = \bm{a} \bm{b}^\intercal$ is the Kronecker or outer product of two vectors $\bm{a}$ and $\bm{b}$.
+In this equation, $\bm{a} \otimes \bm{b} = \bm{a} \bm{b}^\intercal$ is the Kronecker or outer product of two vectors $\bm{a}$ and $\bm{b}$.
 The pressure $\pressure$ is given by the equation of state of an ideal reacting gas
@@
 Inserting this splitting and the definition of divergence into \cref{eq:momentum-equation} allows us to apply \cref{eq:hydrostatic-balance}.
-Furthermore, the background states have zero derivatives in all directions but in $z$.
+The derivatives of the background states are non-zero only for the $z$-direction.
 We arrive at 
@@
 \sidetitle{Boundary conditions}
-To close the system we need to impose boundary conditions.
-Many scenarios are described with periodic boundary conditions,
+To close the system, we need to impose boundary conditions.
+Many scenarios are described with periodic boundary conditions.
 This is not possible with \exahype{}.
-Instead we use the analytical solution of our problems at the boundary, imposing both the conservative variables $\Q$ and its gradient $\gradQ$.
+Instead, we use the analytical solution of our problems at the boundary, imposing both the conservative variables $\Q$ and its gradient $\gradQ$.
 This type of boundary condition is called Cauchy condition.
@@
 
-As a physical boundary condition we limit ourselves to wall boundary condition
+As a physical boundary condition, we limit ourselves to wall boundary condition.
 A standard wall boundary condition for viscous fluid is the no-slip condition, where we assume that when the fluid is close to a wall, it has a velocity of zero relative to the wall.
@@
 of disjoint quadrilateral cells $\cell$.
-Note that we do not distinguish between the approximation space and the domain, the use should be clear given its surrounding context.
+Note that we do not distinguish between the approximation space and the domain; the use should be clear given its surrounding context.
 For each cell we denote its center by $\cellCenter (\cell)$ and its size by $\Delta x, \Delta y$ and $\Delta z$.
@@
 the Jacobian determinant of $\timeMapping$ is $\Delta t$.
+\todo{Similarly -> as well as?}
 This is useful for evaluating derivatives by the chain rule and, similarly, integrals by substitution.
@@
   \label{eq:lagrange-basis}
-    \lagrangeRef(x) = \prod_{\substack{0 \leq j \leq N \\ i \neq j}} \frac{x - {\quadNode[j]}}{x_i - \quadNode[j]},
+    \lagrangeRef(x) = \prod_{\substack{0 \leq j \leq N \\ i \neq j}} \frac{x - {\quadNode[j]}}{x_i - \quadNode[j]}.
 \end{align}
@@
 \end{equation}
-where the basis, unlike in \cref{eq:cell-approx-space-time}, does not depend on the time.
+where the basis does not depend on the time, unlike in \cref{eq:cell-approx-space-time}.
 We need the space-expansion for the predictor $\spredictor$, the discrete solution $\ssol$, the source $\ssource$ and the flux $\sflux$,
@@
 This section is concerned with two different but related concepts:
-finite volume limiting and adaptive mesh refinement (\amr{}).
+finite volume limiting and adaptive mesh refinement.
 Both have in common that they change the structure of the grid.
@@
 Our discussion follows the one in~\cite{dumbser2016simple}.
-This limiting is an a posteriori limiting, which means that we first evaluate a timestep with an unlimited \aderdg{}-method and then check, whether our solution is \enquote{correct}.
+This limiting is an a posteriori limiting, which means that we first evaluate a timestep with an unlimited \aderdg{}-method and then check whether our solution is \enquote{correct}.
 In our case, we check whether the solution is a finite floating point number.
@@
 \subsection{Adaptive Mesh Refinement}\label{sec:amr}
-The goal of \amr{} is to increase the computational efficiency by using a coarse spatial resolution in areas with low information content and a higher resolution in areas of interest.
+The goal of adaptive mesh refinement (\amr{}) is to increase the computational efficiency by using a coarse spatial resolution in areas with low information content and a higher resolution in areas of interest.
 A simple example for this would be using smaller mesh cells for the simulation of a wave, while using larger cells for areas where the wave does not pass through.
@@
 Let $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ be a function that maps the discrete solution of a cell to an arbitrary indicator variable.
-Furthermore, we assume that $\bm{f}$ is expanded in the space-basis \pcref{eq:cell-approx-space}.
+We assume that $\bm{f}$ is expanded in the space-basis \pcref{eq:cell-approx-space}.
 The total variation (\textsc{tv}) of this function is defined by

### 2019-01-21 writing/thesis/chapters/results.tex
Include corrections from proof reader.

@@
 
-Before computing the error we first need to define the $L_p$ norms for a $p > 0$ by
-% notation: https://en.wikipedia.org/wiki/Lp_space#Lp_spaces
+Before computing the error, we first need to define the $L_p$ norms for a $p > 0$ by
 \begin{equation}
   \label{eq:Lp-nrom}
-  \Vert f(x) \Vert_p = \left( \intddomain{ \vert f(\bm{x}) \vert^p}  \right)^{1/p}.
+  \Vert f(\bm{x}) \Vert_p = \left( \intddomain{ \vert f(\bm{x}) \vert^p}  \right)^{1/p}.
 \end{equation}
@@
    \left( \sum_{\cell[i] \in \broken}
-    \left( V \sum_{\bm{j}} \vert f^{\cell[i]}(\quadNode[j], t) - \hat{f}^{\cell{i}}(\quadNode[j], t) \vert^p \, \quadWeight[j] \right) \right)^{1/p}.
+    \left( V \sum_{\bm{j}} \vert f^{\cell[i]}(\quadNodeNd[j], t) - \hat{f}^{\cell{i}}(\quadNodeNd[j], t) \vert^p \, \quadWeight[j] \right) \right)^{1/p}.
  \end{equation}
@@
     The dashed lines are the optimal order of convergence $N+1$.
-  The line is estimated by a linear regression fit and and setting the slope to the ideal order.}
+  The line is estimated by a linear regression fit and setting the slope to the ideal order.}
   \label{fig:convergence-l2-error}
@@
       Plot of velocity slices. Lines are our soulution, scatter plot shows reference solution~\cite{ghia1982high}.
-      For each slice, the other variable is hold constant at a value of zero.}
+      For each slice, the other variable is held constant at a value of zero.}
   \end{subfigure}
@@
 In contrast to us, they used a scheme of polynomial order 10 and a uniform spatial resolution of \SI{20}{\m}.
-Furthermore, we used a physical viscosity of $0.1$, which explains why we have fewer spurious details while using a lower order.
+Moreover, we used a physical viscosity of $0.1$, which explains why we have fewer spurious details despite using a lower order.
 This becomes clearer by comparing the potential temperature pertubation.
@@
 \end{description}
-Note, that while our \amr{} criterion is able to cope with an additional, coarser level, the current implementation in \exahype{} is unstable in this case.
+While our \amr{} criterion is able to cope with an additional, coarser level, the current implementation in \exahype{} is unstable in this case.
 This is why we only report an \amr{} run with one level of dynamic refinement.
@@
 % \end{figure}
-For both settings, we used an \aderdg{}-method of order $4$ and thus have a minimal effective resolution of ca.\ $\SI{3.09}{\m}$.
+For both settings, we used an \aderdg{}-method of order $4$ and thus had a minimal effective resolution of ca.\ $\SI{3.09}{\m}$.
 %The final result for the run with the fully refined mesh (\cref{fig:two-bubbles-noamr-contour}) looks identical to the \amr{} results (\cref{fig:two-bubbles-contour}) shown in the previous section.
@@
 This is not the case for the Navier Stokes equations.
+
 This scenario shows the differences between the viscous Navier-Stokes equations and the Euler equations clearly:
 The viscous effects smooth out the otherwise sharp curves.
-
 Furthermore, they have the effect that fewer cells are limited~(\cref{fig:detonation-pressure-contour}).
@@
 
-It is difficult to compare these results with our references, because they both use different settings.
-In constrast to~\cite{helzel2000modified} we use a non-stiff source term and viscous effects,~\cite{hidalgo2011ader} includes viscosity but is limited to one-dimensional scenarios.
+It is difficult to compare these results with our references because they both use different settings.
+In constrast to~\cite{helzel2000modified} we use a non-stiff source term and viscous effects; \cite{hidalgo2011ader} includes viscosity but is limited to one-dimensional scenarios.
 Comparing with \cref{fig:detonation-contour-reference} we can see that our simulation captures the overall behaviour of the reaction similar to the stiff simulations of~\cite{helzel2000modified}.

### 2019-01-21 writing/thesis/chapters/scenarios.tex
Cite manufactured solution notebook.
Include corrections from proof reader.

@@
 We derive a source term by inserting this solution into the \textsc{pde}~\pcref{eq:equation-set} by using the symbolic math toolkit \textit{Sage}~\cite{sagemath}.
-Our computation of the source term can be found at XXX\todo{Cite github repository with notebook!}.
+Our computation of the source term can be found at~\cite{krenz2018manufactured}.
 In combination with the derived source term, \cref{eq:manufactured-solution} then is an exact solution of our \pde{}.
@@
 We use the reactive source term~\pcref{eq:source-reaction,eq:reaction-model} and set the characteristic timescale to the non-stiff case $\reactionTimescale = 0.1$ and the threshold temperature to $\reactionTemperature = 0.26$.
-Inside a circle of radius $0.3$ we have totally unburnt gas, outside of this circle we have burned gas.
+Inside a circle of radius $0.3$ we have completely unburnt gas, outside of this circle we have burned gas.
 Let $\alpha =  \operatorname{atan2}(z,x)$ be the angle in polar coordinates.
@@
 \end{equation}
-We want to consider flow in hydrostatic equilibrium, i.e.\ flow where the force originating from the pressure-gradient is exactly balanced by gravitation.
+We want to consider flow in hydrostatic equilibrium, i.e.\ a flow for which the pressure-gradient and gravitational force are exactly in balance.
 Inserting this assumption in the momentum equation in $z$-direction and using \cref{eq:eos} once again, we arrive at the ordinary differential equation (\textsc{ode})
@@
 
-We can now compute the initial conditions for a scenario where the background potential energy is in hydrostatic equilbrium with a pertubation that is not in equilbrium.
+We can now compute the initial conditions for a scenario with a background potential energy that is in hydrostatic equilbrium and a pertubation that is not.
 We first compute the background pressure with background potential temperature $\backgroundPotT = \text{const.}$ using \cref{eq:hydrostatic-background-pressure}.
@@
 \sidetitle{Cosine Bubble}
-As a simple test case we consider the cosine bubble scenario where we have one large warm air bubble in the middle of the domain~\cite{giraldo2008study}.
-The initial conditions of the scenario are given by a pertubation of a hydrostatic equlibrium.
+As a simple test case, we consider the cosine bubble scenario that describes a background atmosphere that is pertubated by a large warm air bubble in the middle of the domain~\cite{giraldo2008study}.
 We use a background potential temperature of $\backgroundPotT = 300$ and a domain of $\SI{1}{\km} \times \SI{1}{\km}$.
+The background atmosphere is assumed to be in hydrostatic equilibrium.
 Let
@@
 \sidetitle{Two Bubbles}
-As a simple test case we consider a scenario where we have one large warm air bubble in the middle and a small cold bubble on the top.
-This scenario was first published by \citeauthor{robert1993bubble}~\cite{robert1993bubble}.
+The two bubbles scenario consists of a small cold air bubble that is on top of a large warm air bubble~\cite{robert1993bubble,muller2010adaptive}.
 We use the same procedure as before to compute the initial conditions, again with $\backgroundPotT = 300$ but with a pertubation of the form

### 2019-01-21 writing/thesis/pages/abstract.tex
Small tweaks.
Include corrections from proof reader.

@@
 \chapter{\abstractname}
-This thesis is concerned with the simulation of clouds with the ExaHyPE framework.
+This thesis is concerned with the simulation of clouds using the ExaHyPE framework.
 ExaHyPE is an engine for hyperbolic partial differential equations that uses the ADER-DG scheme.
@@
 We thus need to modify parts of the numerical scheme.
-Furthermore, we extend the equation set to the reactive compressible Navier-Stokes equations which include a source term that models chemical reactions.
+In addition, we extend the equation set to the reactive compressible Navier-Stokes equations which include a source term that models chemical reactions.
 
-We develop a gradient-based, global adaptive mesh refinement indicator that finds cells with unusually steep gradients.
+We develop a gradient-based, global adaptive mesh refinement (AMR) indicator that finds cells with unusually large gradients.
 
 Our implementation is evaluated for standard two and three dimensional fluid dynamics test cases, for flows over a realistic background atmosphere and for a reactive detonation wave.
-Furthermore, we perform a convergence test and a time-to-solution benchmark that evaluates our proposed AMR criterion.
+Additionally, we perform a convergence test and a time-to-solution benchmark that evaluates our proposed AMR criterion.
 

### 2019-01-21 writing/thesis/chapters/conclusion.tex
Spellcheck and other minor changes.

@@
 We implemented a \muscl{}-limited \aderdg{}-scheme with \amr{} for the reactive Navier Stokes equations in this thesis.
-We showed that the scheme works and is capable of simulation different scenarios:\todo{Reference sections of results. Reference theory chapter. Reference implementation.}
+We showed that the scheme works and is capable of simulation different scenarios:
 \begin{itemize}
@@
   Especially the viscous walls for the \muscl{}-method are not correct, due to limitations of \exahype{}.
-\item The\textsc{cfl}-condition~\pcref{eq:cfl-aderdg,eq:cfl-muscl} has the effect that our method needs a large number of timesteps.
-  Even though our \amr{}-criterion is able to reduce the number of needed cells drastically, we could get another large improvement by utilizing local timestepping.
+\item The \textsc{cfl}-condition~\pcref{eq:cfl-aderdg,eq:cfl-muscl} has the effect that our method needs a large number of timesteps.
+  Even though our \amr{}-criterion is able to reduce the number of needed cells drastically, we could get another large improvement by utilizing local time-stepping.
 \item Our implementation of the \textsc{cj}-detonation wave cannot handle realistic detonations because we do not have an implementation of stiff source terms.

### 2019-01-21 writing/thesis/chapters/implementation.tex
Spellcheck and other minor changes.

@@
 This is in contrast with a \enquote{developer} whose scope is the entirety of the source code.
-The goal of our implementation is that all new features should be accesible to users as well.
+The goal of our implementation is that all new features should be accessible to users as well.
 
@@
 \end{itemize}
-Additionaly, we needed to change the templates for the glue code and needed to modify some function signatures to accompany the other changes.
+Additionally, we needed to change the templates for the glue code and needed to modify some function signatures to accompany the other changes.
 
@@
 The vector $(-1, -1, 0)$ is then the base-case for the iteration~\pcref{alg:reduce-gobs} and is thus returned by the function \funName{resetGlobalObservables}.
-The method \funName{mapGlobalObservables} is defined to return $\left( \tv \left[ f(\Q) \right], 0, 1 \right)$, where $f(\Q)$ returns an arbitary indicator value per cell.
+The method \funName{mapGlobalObservables} is defined to return $\left( \tv \left[ f(\Q) \right], 0, 1 \right)$, where $f(\Q)$ returns an arbitrary indicator value per cell.
 Finally, \funName{reduceGlobalObservables} is implemented exactly as described in \cref{alg:merge-variance}.

### 2019-01-21 writing/thesis/chapters/introduction.tex
Spellcheck and other minor changes.

@@
 Both types of forecasts are difficult problems that are limited by a lack of computational power.
-Especially in a time where the realization of exascale supercomputers is imminent, scalable numericals model are becoming more and more important.
+Especially in a time where the realization of exascale supercomputers is imminent, scalable numerical model are becoming more and more important.
 Current climate and weather models are not ready for the exascale era~\cite{schulthess2018reflecting}.
@@
 This method is scalable and of arbitrary order in both time and space.
-With an appropiate limiter, it is also stable, even in the vicinity of discontinuities~\cite{dumbser2016simple}.
+With an appropriate limiter, it is also stable, even in the vicinity of discontinuities~\cite{dumbser2016simple}.
 It is thus a promising candidate for a numerical scheme for the exascale era.

### 2019-01-21 writing/thesis/chapters/methods.tex
Spellcheck and other minor changes.

@@
 We start with a description of the arbitrary high order derivatives (\ader{}) discontinuous Galerkin (\dg{}) method, with a focus on equations that contain both advective and diffusive terms.
-We then seque into a short description of the \muscl{} scheme, which is a second order finite volume method.
+We then segue into a short description of the \muscl{} scheme, which is a second order finite volume method.
 
@@
 \newcommand{\backgroundRho}{\overline{\Qrho}}
-Some of our scenarios can be described as a pertubation of a background state that is initially in hydrostatic balance
+Some of our scenarios can be described as a perturbation of a background state that is initially in hydrostatic balance
 \begin{equation}
@@
 \end{equation}
-The background state \cref{eq:hydrostatic-balance} can be comparitively large and can thus diminish other parts of the flux due to numerical instabilities~\cite{muller2010adaptive}.
+The background state \cref{eq:hydrostatic-balance} can be comparatively large and can thus diminish other parts of the flux due to numerical instabilities~\cite{muller2010adaptive}.
 To avoid this, we split the pressure as $\pressure = \backgroundPressure(z) + \pressure' (\bm{x}, t)$ and the density as $\Qrho = \backgroundRho(z) + \Qrho'(\bm{x}, t)$.
@@
 This form of the equation is inspired by equation set 3 of~\cite{giraldo2008study}.
-They additionally use a splitting of the energy and use the pertubations directly as conservative variables.
+They additionally use a splitting of the energy and use the perturbations directly as conservative variables.
 %We do not use this to simplify the implementation of gradients.
@@
 A standard wall boundary condition for viscous fluid is the no-slip condition, where we assume that when the fluid is close to a wall, it has a velocity of zero relative to the wall.
-We enfore this by setting
+We enforce this by setting
 \begin{align}
@@
 \section{The ADER-DG Method}\label{sec:ader-dg}
-We describe the arbitrary derivative discontinous Galerkin (\aderdg) method in this chapter.
+We describe the arbitrary derivative discontinuous Galerkin (\aderdg) method in this chapter.
 Our description of the main method follows~\cite{dumbser2008unified,dumbser2010arbitrary,dumbser2018efficient}, our notation follows primarily~\cite{dumbser2018efficient}.
@@
 We discuss the solution of a conservation law \cref{eq:conservation-law-gradient} with two or three dimensional domain $\domain$ and its boundary $\boundary$.
-In our implementation of the discontinous Galerkin (\dg) framework, we approximate this solution in the space
+In our implementation of the discontinuous Galerkin (\dg) framework, we approximate this solution in the space
 \begin{equation}
@@
 The next step is the definition of basis functions for our cells.
-We use Langrange polynomials that are defined in the one-dimensional case for the reference interval $(0,1)$ by
+We use Lagrange polynomials that are defined in the one-dimensional case for the reference interval $(0,1)$ by
 \begin{align}
@@
 \end{equation}
-that is linearised such that $n = (0, \ldots, \sbasisSize)$.
+that is linearized such that $n = (0, \ldots, \sbasisSize)$.
 A $d$-dimensional function is then approximated by
@@
 
-\sidetitle{Expansion of quantities}\todo{Maybe explain this later, right now $\stpredictor$ is not defined!}
+\sidetitle{Expansion of quantities}
 All quantities can be expanded in the space-time basis.
@@
   \label{eq:cell-approx-space-time}
-  \stpredictor[\cell] (\bm{x}, t) = \stpredictorCoeff[\cell][v',l',n'] \stbasis[\cell][v',l',n'](\bm{x}, t).
-\end{equation}
+  \stpredictor[\cell] (\bm{x}, t) = \stpredictorCoeff[\cell][v',l',n'] \stbasis[\cell][v',l',n'](\bm{x}, t),
+\end{equation}
+with coefficients $\stpredictorCoeff$.
+The space-time predictor is the result of the predictor step.
 We denote the space-time flux as $\stflux$ and the space-time source as $\stsource$ with coefficient vectors $\stfluxCoeff$ and $\stsourceCoeff$.
@@
 This corresponds to upwinding in time~\cite{dumbser2008unified}.
-Note that this neglects the interaction with neighbouring cells.
+Note that this neglects the interaction with neighboring cells.
 The cell-local scheme is then
@@
 This has the convenient result that only the boundary terms remain because the basis is constant in time.
-We then integrate the flux divergence by parts in space and insert the Riemann solver to connect with the neighbouring elements.
+We then integrate the flux divergence by parts in space and insert the Riemann solver to connect with the neighboring elements.
 Finally, we need to solve
@@
 
-The timestep is restriced to a so-called \textsc{cfl}-type penalty
+The timestep is restricted to a so-called \textsc{cfl}-type penalty
 \begin{equation}\label{eq:cfl-aderdg}
@@
 Our discussion and notation follows the one in~\cite{toro2009riemann}.
-Similar to~\cite{toro2009riemann} we only describe the two-dimensional case without source terms, an extension to three dimensions is straigthforward.
+Similar to~\cite{toro2009riemann} we only describe the two-dimensional case without source terms, an extension to three dimensions is straightforward.
 
 In contrast to the previous \dg{} scheme, we now only store averages instead of a full polynomial solution for each cell.
-We achieve higher order by reconstructing a linear function from a cell and its neighbours.
+We achieve higher order by reconstructing a linear function from a cell and its neighbors.
 Let $\cellAvg$ denote the averages per cell at spatial coordinates $i,j$.
@@
 These so called boundary extrapolated values are given by
-\newcommand{\extrapolatedCellAvg}[3][i,j]{\cellAvg[#1]^{#3 #2} = \cellAvg #3 \frac{1}{2} \slope{#2}}%
 \begin{equation}
@@
 To achieve second order in time, we evolve the boundary extrapolated values
-\newcommand{\evolvedCellAvg}[2][i,j]{\hat{U}_{#1}^{#2}}
 \begin{equation}\label{eq:muscl-time-evolution}
@@
 This results in a scheme that has an order of convergence of two for both space and time.
-\todo{Is this enough detail?}
 We treat the source term by a simple splitting scheme.
@@
 Even worse, in the case of non-linear fluxes, discontinuities can appear even from smooth initial data.
-In addition, oscillations stemming from the high-order polynomical approximation can lead to wrong or unphysical data.
+In addition, oscillations stemming from the high-order polynomial approximation can lead to wrong or unphysical data.
 This is called Gibbs phenomenon.
@@
 
-A relatively recent way of dealing with this problem is the finite volume subcell limiter.
+A relatively recent way of dealing with this problem is the finite volume sub-cell limiter.
 Our discussion follows the one in~\cite{dumbser2016simple}.
@@
 The parameters $\varepsilon$ and $\varepsilon_0$ can be set freely.
-The former controls by which factor the local jump can differ from its neighbourhood, the latter is needed for zero jumps~\cite{dumbser2016simple}.
-Note that this criterion is only a heuristic and is suspectible to false positives.
+The former controls by which factor the local jump can differ from its neighborhood, the latter is needed for zero jumps~\cite{dumbser2016simple}.
+Note that this criterion is only a heuristic and is susceptible to false positives.
 
@@
 In our case we use the \muscl{}-method (\cref{sec:muscl}).
-The recomputation starts by subdividing the infringing cell into $N_s = 2N + 1$ subcells.
-This number of subcells has the advantage that we do not lose spatial resolution and that we can use the same timestep size for both cell types.
+The recomputation starts by subdividing the infringing cell into $N_s = 2N + 1$ sub-cells.
+This number of sub-cells has the advantage that we do not lose spatial resolution and that we can use the same timestep size for both cell types.
 The reason for this is that the \textsc{cfl}-conditions for both schemes \pcref{eq:cfl-aderdg,eq:cfl-muscl} coincide for our choice of $N_s$.
@@
   \centering
-  \includegraphics[scale=0.7]{thesis_aderdg_subcell_grid}
-  \caption{\label{fig:limiting-subcells}Conversion from \dg{} degrees of freedoms to finite volume degree of freedoms. Image taken from~\cite{dumbser2018conformal}. }
+  \includegraphics{thesis_aderdg_subcell_grid}
+  \caption{\label{fig:limiting-subcells}Conversion from \dg{} degrees of freedoms to finite volume degree of freedoms.
+Image taken from~\cite{dumbser2018conformal}.
+We changed the typeface of the figure.}
 \end{figure}
-\todo{Cite source for subcells~\pcref{fig:limiting-subcells}. See guidebook. NOTE THAT IT IS MODIFIED. Also: Fix size, currently font is a ziny bit too small}
-
-\Cref{fig:limiting-subcells} depicts the mapping from \dg{}-cells to finite volume subcells.
-For the sake of brevity, we omit technical details and refer the interestd reader to~\cite{dumbser2016simple}.
+\Cref{fig:limiting-subcells} depicts the mapping from \dg{}-cells to finite volume sub-cells.
+For the sake of brevity, we omit technical details and refer the interested reader to~\cite{dumbser2016simple}.
 
@@
 \end{algorithm}
-Chebychev's inequality
+Chebyshev's inequality
 \begin{equation}
@@
 They can be chosen freely, as long as $T_\text{refine} < T_\text{delete}$.
-Chebychev's inequality~\pcref{eq:chebychev} then guarantees that only a subset of cells is marked for refinement.
+Chebyshev's inequality~\pcref{eq:chebychev} then guarantees that only a subset of cells is marked for refinement.
 Note that this inequality provides only a loose bound.

### 2019-01-21 writing/thesis/chapters/results.tex
Spellcheck and other minor changes.

@@
 
-\newcommand{\error}{\operatorname{Total-Error}}
+\newcommand{\error}{\operatorname{Error}}%
 \section{Convergence Test}\label{sec:results-convergence}
+\begin{figure}[hb]
+  \centering
+  \includegraphics[trim=0.2cm 0.3cm 0.2cm 1.0cm, clip]{thesis_convergence}
+  \caption{\label{fig:convergence-l2-error}%
+    $L_2$-Error vs.\ Grid Size.
+    The dashed lines are the optimal order of convergence $N+1$.
+  The line is estimated by a linear regression fit and setting the slope to the ideal order.}
+\end{figure}
 For the convergence test, we run our manufactured solution scenario~(\cref{sec:manufactured-solution}) for all orders 1 to 6 and for number of cells $3^2, 9^2, 27^2$ and $81^2 $.
 
+In the following, we describe the error for one variable.
+We define the total error as the sum of the error of all conservative variables.
 Before computing the error, we first need to define the $L_p$ norms for a $p > 0$ by
@@
 \end{equation}
-We are interested in the total error which we define as the norm of the difference between an analytical solution $f(\bm{x}, t)$ and our approximation $\hat{f}(\bm{x}, t)$.
+We are interested in the total error which we define as the norm of the difference between an analytical solution $f(\bm{x}, t)$ and our approximation $\ssol(\bm{x}, t)$.
 The error at a time $t$ is thus defined as
@@
   \label{eq:error}
-  \error(t,p) = \Vert f(\bm{x}, t) - \hat{f}(\bm{x}, t) \Vert_p.
+  \error(t,p) = \Vert f(\bm{x}, t) - \ssol (\bm{x}, t) \Vert_p.
 \end{equation}
@@
    \left( \sum_{\cell[i] \in \broken}
-    \left( V \sum_{\bm{j}} \vert f^{\cell[i]}(\quadNodeNd[j], t) - \hat{f}^{\cell{i}}(\quadNodeNd[j], t) \vert^p \, \quadWeight[j] \right) \right)^{1/p}.
+    \left( V \sum_{\quadNodeNd[j] \in \refCell[i]} \vert f^{\cell[i]}(\quadNodeNd[j], t) - \ssol[\cell{i}](\quadNodeNd[j], t) \vert^p \, \quadWeight[j] \right) \right)^{1/p}.
  \end{equation}
@@
 For the limiting case of $p \to \infty$ we use the maximum of the point-wise error over all nodal points.
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[trim=0.2cm 0.3cm 0.2cm 1.0cm, clip]{thesis_convergence}
-  \caption{$L_2$-Error vs.\ Grid Size.
-    The dashed lines are the optimal order of convergence $N+1$.
-  The line is estimated by a linear regression fit and setting the slope to the ideal order.}
-  \label{fig:convergence-l2-error}
-\end{figure}
 
@@
 
-To compute the numerical order of convergence, we perform a linear regression of the logarithm of the error vs.\ the logarithm of the meshsize.
+To compute the numerical order of convergence, we perform a linear regression of the logarithm of the error vs.\ the logarithm of the mesh size.
 The size of the slope is then the convergence order.
@@
 Note that the error for the finest grid with order 6 is worse than the error for order 5.
-For all other meshsizes and orders, a higher order implies a smaller error.
+For all other mesh sizes and orders, a higher order implies a smaller error.
 Comparing our errors with the optimal order of convergence $N+1$, we notice that while our scheme exhibits the theoretical order of convergence of 2 for a polynomial order $N=1$, orders have diminishing returns.
@@
 Some \textsc{dg}-methods of even polynomial order only achieve a numerical convergence order of $N+\nicefrac{1}{2}$.
-The exact theoretical reason for this is unclear but it shares characteristics with the behaviour of other \dg{}-schemes.
+The exact theoretical reason for this is unclear but it shares characteristics with the behavior of other \dg{}-schemes.
 We refer the interested reader to the discussion of error estimates for nonlinear problems and for multi-dimensional problems with \dg{}-schemes of~\cite{hesthaven2008nodal}.
@@
 Our solution resulted in the expected streamlines (\cref{fig:taylor-green-streamlines}).
-Furthermore, we compare our results with the analytical solution for the incrompressible case.
+Furthermore, we compare our results with the analytical solution for the incompressible case.
 We achieved a small error~(\cref{fig:taylor-green-result}) for both pressure and velocity.
@@
     \caption{\label{fig:lid-driven-cavity-result}%
-      Plot of velocity slices. Lines are our soulution, scatter plot shows reference solution~\cite{ghia1982high}.
+      Plot of velocity slices. Lines are our solution, scatter plot shows reference solution~\cite{ghia1982high}.
       For each slice, the other variable is held constant at a value of zero.}
@@
 Moreover, we used a physical viscosity of $0.1$, which explains why we have fewer spurious details despite using a lower order.
-This becomes clearer by comparing the potential temperature pertubation.
+This becomes clearer by comparing the potential temperature perturbation.
 Our solution has a smooth distribution inside the cloud~(\cref{fig:cosine-bubble-potT-ours}) while the results of~\cite{giraldo2008study} show sharp peaks~(\cref{fig:cosine-bubble-potT-giraldo}).
-In addition, our solution does not contain negative values for the pertubation.
-Despite the different parameters, the maximum pertubation and its position matches for both results.
+In addition, our solution does not contain negative values for the perturbation.
+Despite the different parameters, the maximum perturbation and its position matches for both results.
 
@@
     \centering
-    \includegraphics[trim={0.00cm 0.00cm 8.4cm 0.0cm},clip]{thesis_cosine_bubble_pertubation_comparison}
+    \includegraphics[scale=0.974,trim={0.00cm 0.00cm 8.4cm 0.0cm},clip]{thesis_cosine_bubble_pertubation_comparison}
     \caption{\label{fig:cosine-bubble-potT-ours}%
@@
     \centering
-    \includegraphics[trim={7.00cm 0.00cm 0.0cm 0.0cm},clip]{thesis_cosine_bubble_pertubation_comparison}
+    \includegraphics[scale=0.974,trim={7.00cm 0.00cm 0.0cm 0.0cm},clip]{thesis_cosine_bubble_pertubation_comparison}
     \caption{\label{fig:cosine-bubble-potT-giraldo}%
-      Figure taken from~\cite{giraldo2008study}, resolution of \SI{20}{\m}, $N = 10$, \dg{}3 uses modified Navier-Stokes} %poly order
+      Figure taken from~\cite{giraldo2008study}, resolution of \SI{20}{\m}, \\$N = 10$, \dg{}3 uses modified Navier-Stokes} %poly order
   \end{subfigure}
   \caption{\label{fig:cosine-bubble-potT}%
-    Height $z$ vs.\ pertubation of potential temperature for the cosine bubble scenario at $t=\SI{700}{\s}$ and $x = \SI{500}{\m}$.
+    Height $z$ vs.\ perturbation of potential temperature for the cosine bubble scenario at $t=\SI{700}{\s}$ and $x = \SI{500}{\m}$.
   }
@@
 A possible source for this is that we use a different equation set than~\cite{muller2010adaptive}.
-While we use a general purpose set with small modifications for atmospheric flows, they use a equation set that is fully focussed on this scenario.
+While we use a general purpose set with small modifications for atmospheric flows, they use a equation set that is fully focused on this scenario.
 Furthermore, we use the full Navier-Stokes viscous fluxes instead of an approximation.
@@
      We rescaled the reference plots and changed their arrangement and axes placement.
-   Contour values for potential temperature pertubation are $-0.05, 0.05, 0.1, \ldots 0.45$.
+   Contour values for potential temperature perturbation are $-0.05, 0.05, 0.1, \ldots 0.45$.
   }
@@
   Each could can be refined once.
-  That is, the cells had sidelengths of roughly \SI{37.04}{\m} and  \SI{12.35}{\m}.
+  That is, the cells had side lengths of roughly \SI{37.04}{\m} and  \SI{12.35}{\m}.
   As refinement thresholds we used $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$ in \cref{eq:refinement-criterion}.
   They are the exact same settings that we used for the bubble scenarios in the previous section.
-\item[Fine] We used a uniform grid where all cells had a sidelength corresponding to the finest mesh of the \amr{}-test case.
+\item[Fine] We used a uniform grid where all cells had a side length corresponding to the finest mesh of the \amr{}-test case.
   In addition, we disabled the reduction of global observables.
@@
 
-We solely used the \tbb{} parallelisation of \exahype{}.
+We solely used the \tbb{} parallelization of \exahype{}.
 To find a reasonable parameter for the number of background job consumers, we ran a grid search.
-We ran three \amr{} testcases for a simulation time of $\SI{1}{\min}$.
-The testcases were identical in setting to the aforementioned \amr{} run, but with two levels of refinement.
+We ran three \amr{} test cases for a simulation time of $\SI{1}{\min}$.
+The test cases were identical in setting to the aforementioned \amr{} run, but with two levels of refinement.
 The best median performance was achieved by using six background threads.
@@
 We used a limiting \aderdg{}-scheme with an order of 3.
-For runs without viscosity we used a meshsize of $81 \times 81$, for the runs with a viscosity of $\mu = 0.01$ we used a coarser mesh consisting in $27 \times 27$ cells.
+For runs without viscosity we used a mesh size of $81 \times 81$, for the runs with a viscosity of $\mu = 0.01$ we used a coarser mesh consisting in $27 \times 27$ cells.
 We chose the smaller grid because our boundary conditions became unstable for finer grids.
@@
 It is difficult to compare these results with our references because they both use different settings.
-In constrast to~\cite{helzel2000modified} we use a non-stiff source term and viscous effects; \cite{hidalgo2011ader} includes viscosity but is limited to one-dimensional scenarios.
-Comparing with \cref{fig:detonation-contour-reference} we can see that our simulation captures the overall behaviour of the reaction similar to the stiff simulations of~\cite{helzel2000modified}.
+In contrast to~\cite{helzel2000modified} we use a non-stiff source term and viscous effects; \cite{hidalgo2011ader} includes viscosity but is limited to one-dimensional scenarios.
+Comparing with \cref{fig:detonation-contour-reference} we can see that our simulation captures the overall behavior of the reaction similar to the stiff simulations of~\cite{helzel2000modified}.
 The viscous effects have a similar smoothing effect as in~\cite{hidalgo2011ader}.
@@
 \end{figure}
-
-\begin{figure}[htb]
+\begin{figure}[H]
     \centering
-    \includegraphics[width=0.33\textwidth]{leveque_detonation_mass_fraction}
+    \includegraphics[width=0.3\textwidth]{leveque_detonation_mass_fraction}
     \caption{\label{fig:detonation-contour-reference}Reference solution for mass fraction with stiff source.

### 2019-01-21 writing/thesis/chapters/scenarios.tex
Spellcheck and other minor changes.

@@
 \end{table}%
-In this chapter, we introduce various scenarios that we will later use to to evalute the performance of our method.
+In this chapter, we introduce various scenarios that we will later use to to evaluate the performance of our method.
 \Cref{tab:scenarios} shows an overview of our scenarios.
@@
 \section{Atmospheric Scenarios}
-The following scenarios are all described in terms of a pertubation of a balanced atmosphere.
+The following scenarios are all described in terms of a perturbation of a balanced atmosphere.
 This balanced atmosphere is called hydrostatic balance and is described by \cref{eq:hydrostatic-balance}.
@@
 \end{equation}
-To allow for an easier description of the initial conditions we split the potential temperature into a background state $\backgroundPotT$ and a pertubation $\pertubationPotT$
+To allow for an easier description of the initial conditions we split the potential temperature into a background state $\backgroundPotT$ and a perturbation $\pertubationPotT$
 \begin{equation}
@@
 where we use the reference pressure $p_0$ as the pressure on ground level.
-This \textsc{ode} is the hydrostatic equilibrium (similar to \cref{eq:hydrostatic-balance}) in terms of the potential temperature and can be solved by seperation of variables.
+This \textsc{ode} is the hydrostatic equilibrium (similar to \cref{eq:hydrostatic-balance}) in terms of the potential temperature and can be solved by separation of variables.
 After simplifying, we obtain
@@
 
-We can now compute the initial conditions for a scenario with a background potential energy that is in hydrostatic equilbrium and a pertubation that is not.
+We can now compute the initial conditions for a scenario with a background potential energy that is in hydrostatic equilibrium and a perturbation that is not.
 We first compute the background pressure with background potential temperature $\backgroundPotT = \text{const.}$ using \cref{eq:hydrostatic-background-pressure}.
-Next, we compute the pertubated potential temperature $\potT$ and use \cref{eq:potTToT} to convert it to temperature.
+Next, we compute the perturbed potential temperature $\potT$ and use \cref{eq:potTToT} to convert it to temperature.
 The density $\Qrho(\bm{x})$ can now be evaluated with the thermal equation of state \cref{eq:temperature}.
@@
 \sidetitle{Cosine Bubble}
-As a simple test case, we consider the cosine bubble scenario that describes a background atmosphere that is pertubated by a large warm air bubble in the middle of the domain~\cite{giraldo2008study}.
+As a simple test case, we consider the cosine bubble scenario that describes a background atmosphere that is perturbed by a large warm air bubble in the middle of the domain~\cite{giraldo2008study}.
 We use a background potential temperature of $\backgroundPotT = 300$ and a domain of $\SI{1}{\km} \times \SI{1}{\km}$.
@@
 denote the difference between spatial positions $x,z$ and the center of a bubble $x_c, z_c$.
-The pertubation is given by the function
+The perturbation is given by the function
 \begin{align}
@@
 \end{align}
-where $A$ denotes the maximal pertubation and $a$ is the size of the bubble.
+where $A$ denotes the maximal perturbation and $a$ is the size of the bubble.
 We use the constants
@@
 The two bubbles scenario consists of a small cold air bubble that is on top of a large warm air bubble~\cite{robert1993bubble,muller2010adaptive}.
-We use the same procedure as before to compute the initial conditions, again with $\backgroundPotT = 300$ but with a pertubation of the form
+We use the same procedure as before to compute the initial conditions, again with $\backgroundPotT = 300$ but with a perturbation of the form
 

### 2019-01-21 writing/thesis/pages/abstract.tex
Spellcheck and other minor changes.

@@
 This thesis is concerned with the simulation of clouds using the ExaHyPE framework.
-ExaHyPE is an engine for hyperbolic partial differential equations that uses the ADER-DG scheme.
+ExaHyPE is an engine for hyperbolic partial differential equations that uses the \aderdg{} scheme.
 
@@
 
-We develop a gradient-based, global adaptive mesh refinement (AMR) indicator that finds cells with unusually large gradients.
+We develop a gradient-based, global adaptive mesh refinement (\amr{}) indicator that finds cells with unusually large gradients.
 

### 2019-01-21 writing/thesis/pages/acknowledgements.tex
Changes.
Spellcheck and other minor changes.

@@
 
-\renewcommand{\dictumwidth}{\textwidth}
-\setchapterpreamble{\dictum[Booktitle]{
-    Quote!
-}}
-%\addcontentsline{toc}{chapter}{Acknowledgments}
+% \renewcommand{\dictumwidth}{\textwidth}
+% \setchapterpreamble{\dictum[Booktitle]{
+%     Quote!
+% }}
+% %\addcontentsline{toc}{chapter}{Acknowledgments}
 \chapter{Acknowledgments}
 \vspace{1em}
+I want to thank Prof.\ Bader for the chance to work on this exciting topic.
+I also want to thank my advisor Leonhard Rannabauer, whose guidance made this thesis not only possible but also enjoyable.
 
-Acknowledgements here.
+My gratitude extends to my friends and family, who supported me during the entire thesis.
+Special thanks go to my friend William who proof-read the thesis.
 \cleardoublepage{}

### 2019-01-21 writing/thesis/chapters/conclusion.tex
Final (?) changes.

@@
 \item We evaluated our method for standard \textsc{cfd} scenarios~(\cref{sec:cfd}) and achieved competitive results for all used scenarios.
-  This is true for both two-dimensional scenarios (Taylor-Green and Lid-Driven Cavity) and for the three-dimensional \textsc{abc}-flow.
+  This is true for both two-dimensional scenarios (Taylor-Green vortex and lid-driven cavity) and for the three-dimensional \textsc{abc}-flow.
 \item Furthermore, our method allows us to simulate flows in hydrostatic equilibrium correctly (see \cref{sec:results-cloud}).
@@
   It is able to do this without degrading the quality of the solution, even for a scenario that contains small-scale details.
-\item Our results of \cref{sec:results-reactive} show that our implementation is capable of simulating chemical reactions with a limited scheme, at least for a source term that is not stiff.
+\item Our results of \cref{sec:results-reactive} showed that our implementation is capable of simulating chemical reactions with a limited scheme, at least for a source term that is not stiff.
 \end{itemize}
@@
   Even though our \amr{}-criterion is able to reduce the number of needed cells drastically, we could get another large improvement by utilizing local time-stepping.
-\item Our implementation of the \textsc{cj}-detonation wave cannot handle realistic detonations because we do not have an implementation of stiff source terms.
+\item Our implementation of the \textsc{cj} detonation wave cannot handle realistic detonations because we do not have an implementation of stiff source terms.
   An implementation of this is straight-forward but includes changes to the space-time predictor and its initial guess, and also to the \muscl{}-scheme.

### 2019-01-21 writing/thesis/chapters/implementation.tex
Final (?) changes.

@@
 
-\section{Implementing numerics}
+\section{Implementing Numerics}
 We needed to modify the existing implementation of the mappings, solvers and kernels to be able to solve problems with diffusive fluxes.

### 2019-01-21 writing/thesis/chapters/introduction.tex
Final (?) changes.

@@
 Of course, a finer grid is not useful if the computational effort is too large.
-Thus, also propose a compute rate of one simulated years per wall-clock day.
+Thus they propose a compute rate of one simulated years per wall-clock day.
 An example of a recent supercomputing effort in this domain~\cite{fuhrer2018near} achieved a performance of 0.043 simulated years per wall-clock day with a resolution of $\SI{930}{\m}$ for a near-global simulation on the Piz Daint supercomputer.
@@
 \sidetitle{Discontinuous Galerkin}
-The discontinuous Galerkin (\dg{}) methods are an exciting numerical method as they are relatively easy to scale.
+The discontinuous Galerkin (\dg{}) methods are exciting numerical schemes as they are relatively easy to scale.
 In addition, they can be of high order and can perform local grid refinement~\cite{hesthaven2008nodal}.
@@
 Recently, \ader{} discontinuous Galerkin methods has been proposed, for example in~\cite{dumbser2008unified}.
-This method is scalable and of arbitrary order in both time and space.
-With an appropriate limiter, it is also stable, even in the vicinity of discontinuities~\cite{dumbser2016simple}.
-It is thus a promising candidate for a numerical scheme for the exascale era.
+These methods are scalable and of arbitrary order in both time and space.
+With an appropriate limiter, they are also stable, even in the vicinity of discontinuities~\cite{dumbser2016simple}.
+They are thus promising numerical methods, even for the exascale era.
 
-The goal of this thesis is to evaluate the \aderdg{} method for testing scenarios, which have been devised as benchmark examples for meteorological applications~\cite{robert1993bubble,giraldo2008study}.
+The goal of this thesis is to evaluate the \aderdg{} method of~\cite{dumbser2008unified} for testing scenarios, which have been devised as benchmark examples for meteorological applications~\cite{robert1993bubble,giraldo2008study}.
 We implement this with the \exahype{}-engine, which is \enquote{An Exascale Hyperbolic \pde{} Engine}.

### 2019-01-21 writing/thesis/chapters/methods.tex
Final (?) changes.

@@
 % TODO: Extract to settings
-\chapter{An ADER-DG scheme for the Navier-Stokes Equations}\label{chap:methods}
+\chapter{An ADER-DG Scheme for the Navier-Stokes Equations}\label{chap:methods}
 This chapter describes the numerical and physical background that is needed to simulate reacting fluids with high accuracy.
@@
 
+\sidetitle{Hyperbolic flux}
 The hyperbolic flux is given by
@@
 \end{equation}
-The term $q_0 \QZ$ is the chemical energy with a heat release $q_0$~\cite{helzel2000modified}, the term $gz$ is the geopotential height~\cite{giraldo2008study}.
-We set $g$ to 9.81.
+The term $q_0 \QZ$ is the chemical energy with a heat release $q_0$~\cite{helzel2000modified}, the term $gz$ is the geopotential height with the gravity of Earth $g$~\cite{giraldo2008study}.
 The pressure is related to the temperature $T$ by the thermal equation of state
@@
 
+\sidetitle{Viscous flux}
 The viscous flux is
@@
   \begin{split}
-  c_v &= \frac{1}{\gamma - 1} R \\
-  c_p &= \frac{\gamma}{\gamma - 1} R\\
-  R &= c_p - c_v\\
+  c_v &= \frac{1}{\gamma - 1} R, \\
+  c_p &= \frac{\gamma}{\gamma - 1} R,\\
+  R &= c_p - c_v,\\
   \gamma &= \frac{c_p}{c_v}.
@@
 
+\sidetitle{Gravity}
 We also support two different kind of optional source terms.
@@
 
+\sidetitle{Chemical reactions}
 The chemical reactive source term is
@@
 \begin{equation}\label{eq:reaction-model}
+  K(T) = 
 \begin{cases}
@@
 We first compute a local time evolution of each cell in a predictor step and then add the influence of the neighbors in the corrector step.
-\sidetitle{Reference Cell}
+
+\sidetitle{Reference cell}
 For reasons of computational efficiency, we describe the scheme in terms of a reference cell.
@@
 The symbol $\mapping^{-1}$ denotes the inverse mapping.
-It can be used to define a function $f(\bm{x})$ acting on a point $\hat{\bm{x}}$ of a regular cell in terms of a function $\hat{f}(\bm{x})$ that acts on the corresponding point of the reference cell by the relation
+It can be used to define a function $f(\bm{x})$ acting on a point $\bm{x}$ of a regular cell in terms of a function $\hat{f}(\bm{x})$ that acts on the corresponding point of the reference cell by the relation
 \begin{equation}
@@
 the Jacobian determinant of $\timeMapping$ is $\Delta t$.
-\todo{Similarly -> as well as?}
 This is useful for evaluating derivatives by the chain rule and, similarly, integrals by substitution.
@@
 \end{equation}
-\sidetitle{Basis Functions}
+
+\sidetitle{Basis functions}
 The next step is the definition of basis functions for our cells.
@@
   \label{eq:langrange-expansion-1d}
-  f(x) = \sum_{i = 0}^N f(x_i) \lagrangeRef[i](x) = f(x_i) \lagrangeRef[i](x),
+  f(x) = \sum_{i = 0}^N f(\quadNode[i]) \lagrangeRef[i](x) = f(\quadNode[i]) \lagrangeRef[i](x),
 \end{equation}
@@
 
-The basis functions are similarly defined in $\dimensions$-dimensions by considering nodes that are the tensor-products of $d$ one-dimensional Gauss-Legendre quadrature nodes.
-They are indexed by a multi-index $n = (n_1, \ldots, n_\dimensions)$
+The basis functions are similarly defined in $\dimensions$-dimensions by considering nodes that are the tensor-products of $d$ one-dimensional Gauss-Legendre quadrature nodes
 \begin{equation}
   \label{eq:basis-space}
-  \sbasisRef[][n] (\bm{x}) = \prod_{i=0}^{\dimensions} \lagrangeRef[n_i] (x_i)
-\end{equation}
-that is linearized such that $n = (0, \ldots, \sbasisSize)$.
+  \sbasisRef[][n] (\bm{x}) = \prod_{i=0}^{\dimensions} \lagrangeRef[n_i] (x_i).
+\end{equation}
+They are indexed by a multi-index $\bm{n} = (n_1, \ldots, n_\dimensions)$ that is linearized such that $n = (0, \ldots, \sbasisSize)$.
 A $d$-dimensional function is then approximated by
@@
   \label{eq:lagrange-expansion}
-  f(\bm{x}) = \sum_{i = 0}^{\sbasisSize - 1} f(\bm{x}_i) \lagrangeRef[i](\bm{x}) = f(\bm{x}_i) \lagrangeRef[i](\bm{x}).
+  f(\bm{x}) = \sum_{i = 0}^{\sbasisSize - 1} f(\quadNodeNd[i]) \lagrangeRef[i](\bm{x}) = f(\quadNodeNd[i]) \lagrangeRef[i](\bm{x}).
 \end{equation}
@@
 
-We define the basis functions over a space-cell with an index $n = 0, \ldots, \sbasisSize - 1$
+\sidetitle{Cell basis}
+We define the basis functions over a space-cell with an index $n = 0, \ldots, \sbasisSize - 1$ as
 \begin{align}\label{eq:space-basis}
@@
 We first multiply the conservation law by a test function of the same function space as the basis, integrate over a space-time-element $\cell$ and replace all terms with their discrete approximations.
-In particular, we replace the vector of conservative variables $\Q$ with the space-time predictor $\stpredictor[\cell]$.
+In particular, we replace the vector of conservative variables $\Q$ with the space-time predictor $\stpredictor[\cell]$ and arrive at
 \begin{align}\label{eq:weak-pde-space-time}
@@
     \sttestfunction[][v,l,n] (t) \stsource(\stpredictor[i])
-}}.
+}}.\raisetag{0.8cm}
 \end{split}
@@
 This results, yet again, in the weak formulation of the \pde{}
-\begin{equation}
+\begin{align}
+  \begin{split}
   \label{eq:weak-pde}
@@
 }}
-+
+&+
 \intdt{\intdcell{
-    \stestfunction[][v,n] \left( \div{F(\Q, \gradQ } \right)
+    \stestfunction[][v,n] \left( \div{\flux(\Q, \gradQ } \right)
 }}
-=
+\\&=
 \intdt{\intdcell{
-    \stestfunction[][v,n] S(\Q, \bm{x}, t)
+    \stestfunction[][v,n] \source(\Q, \bm{x}, t)
 }}.
-\end{equation}
+  \end{split}
+\end{align}
+
 We now insert our discrete approximations and apply the space-basis expansion~\pcref{eq:cell-approx-space} to the discrete solution.
@@
 }}\right)
-\end{split}
+\end{split}\raisetag{0.8cm}
 \end{align}
@@
 
-\section{MUSCL-Hancock Finite Volume Scheme}\label{sec:muscl}
+\section{The MUSCL-Hancock Scheme}\label{sec:muscl}
 We discussed a modern, high-order \dg{} method in the previous chapter.
@@
 
-\sidetitle{Boundary Extrapolated Values}
+\sidetitle{Boundary extrapolated values}
 We first compute the slope of the linear function connecting the cells.
@@
 which is of course an abuse of notation insofar as it is not the gradient of the constant cell value but rather of the linear reconstruction \pcref{eq:slopes}.
-\sidetitle{Time Evolution}
+\sidetitle{Time evolution}
 To achieve second order in time, we evolve the boundary extrapolated values
@@
 
-\section{Adaptive Mesh Refinement \textit{\&} Finite Volume Limiting}\label{sec:grid}
+\section{Finite Volume Limiting \textit{\&} Adaptive Mesh Refinement}\label{sec:grid}
 This section is concerned with two different but related concepts:
@@
 
-\subsection{Limiting}\label{sec:limiting}
+\subsection{Finite Volume Limiting}\label{sec:limiting}
 Higher order \textsc{dg} methods cannot cope with discontinuous solutions.
@@
 The reason for this is that the \textsc{cfl}-conditions for both schemes \pcref{eq:cfl-aderdg,eq:cfl-muscl} coincide for our choice of $N_s$.
+\Cref{fig:limiting-subcells} depicts the mapping from \dg{}-cells to finite volume sub-cells.
+For the sake of brevity, we omit technical details and refer the interested reader to~\cite{dumbser2016simple}.
 \begin{figure}[htb]
@@
 \end{figure}
-\Cref{fig:limiting-subcells} depicts the mapping from \dg{}-cells to finite volume sub-cells.
-For the sake of brevity, we omit technical details and refer the interested reader to~\cite{dumbser2016simple}.
 
@@
 
+\sidetitle{Total variation}
 Let $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ be a function that maps the discrete solution of a cell to an arbitrary indicator variable.
@@
 \newcommand{\sampleVariance}{\overline{\variance}}
+\sidetitle{Outliers}
 A simple way of determining outliers is to compute the mean and standard deviation for a set.

### 2019-01-21 writing/thesis/chapters/results.tex
Final (?) changes.

@@
 
-\begin{table}[htb]
+\begin{table}[tb]
   \centering
@@
 For all other mesh sizes and orders, a higher order implies a smaller error.
-Comparing our errors with the optimal order of convergence $N+1$, we notice that while our scheme exhibits the theoretical order of convergence of 2 for a polynomial order $N=1$, orders have diminishing returns.
+Comparing our errors with the optimal order of convergence $N+1$, we notice that while our scheme exhibits the theoretical order of convergence of 2 for a polynomial order $N=1$, larger orders exhibit diminishing returns.
 
@@
 This means, that we do not achieve the optimal theoretical order of convergence in general.
-In~\cite{dumbser2010arbitrary}, which use a similar numerical method and the same scenario, but a different grid, \citeauthor{dumbser2010arbitrary} achieves the optimal order for most polynomial orders.
+In~\cite{dumbser2010arbitrary}, which uses a similar numerical method and the same scenario, but a different grid, \citeauthor{dumbser2010arbitrary} achieves the optimal order for most polynomial orders.
 Some \textsc{dg}-methods of even polynomial order only achieve a numerical convergence order of $N+\nicefrac{1}{2}$.
-The exact theoretical reason for this is unclear but it shares characteristics with the behavior of other \dg{}-schemes.
+The exact theoretical reason for this is unclear but this phenomenon is similar to the behavior of other \dg{}-schemes.
 We refer the interested reader to the discussion of error estimates for nonlinear problems and for multi-dimensional problems with \dg{}-schemes of~\cite{hesthaven2008nodal}.
 
-\section{Accurate CFD}\label{sec:cfd}
+\section{Simulation of CFD Scenarios}\label{sec:cfd}
 After we established that our scheme converges, we evaluate it using standard \textsc{cfd} testing scenarios that either have an analytical solution or for which we have a reference solution.
 
-\sidetitle{Taylor-Green Vortex}
+\sidetitle{Taylor-Green vortex}
 We used an \aderdg{}-scheme of order 5 with a mesh of size $27 \times 27$ cells to simulate the Taylor-Green Vortex~\pcref{eq:taylor-green}.
@@
   \caption{\label{fig:taylor-green-streamlines}%
-    Streamlines for Taylor-Green vortex}
+    Streamlines for Taylor-Green vortex at $t=\SI{10}{\s}$}
 \end{figure}
@@
   \caption{\label{fig:taylor-green-result}%
-    Comparison of Taylor-Green simulation with analytical solution.
+    Comparison of Taylor-Green simulation with analytical solution~\pcref{eq:taylor-green} at $t=\SI{10}{\s}$.
     The former is represented by the scatter plot, the latter by the gray line.
     Note that we only show every 5th point.
-    The other variable of the slice is held at 0.}
+    The other variable of the slice is held constant at a value of zero.}
 \end{figure}
 
-\sidetitle{ABC Flow}
+\sidetitle{ABC-flow}
 \begin{figure}[htb]
@@
   \caption{\label{fig:abc-result}%
-  Pressure for the \textsc{abc}-flow.
-  Each column represents a one-dimensional slice, all other coordinates are held constant at their median value.
-  We compare the analytical solution (gray line) with our approximation (scatter plot).
+  Pressure for the \textsc{abc}-flow at $t=\SI{1}{\s}$.
+  Each column represents a one-dimensional slice, all other coordinates are held constant at a value of zero.
+  We compare the analytical solution~\pcref{eq:abc-flow} with our approximation.
+  The former is represented by the gray line, the latter by the scatter plot.
   We only show every 4th point.}
@@
 
-\sidetitle{Lid-Driven Cavity}
+\sidetitle{Lid-driven cavity}
 \begin{figure}[htb]
@@
 
-\section{Accurate Clouds}\label{sec:results-cloud}
+\section{Simulation of Clouds}\label{sec:results-cloud}
 We discussed the capabilities of our scheme regarding standard \textsc{cfd} testing scenario.
 In this section, we consider our bubble scenarios.
-\sidetitle{Cosine Bubble}
+\sidetitle{Cosine bubble}
 \begin{figure}[htb]
@@
 
-\sidetitle{Two Bubbles}
+\sidetitle{Two bubbles}
 We ran the second scenario, the two bubbles scenario~\pcref{eq:bubbles-values}, with the same \amr{} settings as the first one.
@@
 
-\section{AMR vs Static Mesh}\label{sec:results-tts-amr}
+\section{AMR vs.\ Static Mesh}\label{sec:results-tts-amr}
 To show the effectiveness of the \amr{} criterion, we compare the two settings:
@@
 \item[AMR] We used a coarse mesh with just $27 \times 27$ cells.
-  Each could can be refined once.
+  Each could be refined once.
   That is, the cells had side lengths of roughly \SI{37.04}{\m} and  \SI{12.35}{\m}.
@@
 We ran the simulation without plotters to focus on the performance of the numerics and the mesh refinement routines.
-We used a single node Supermuc Phase 2.
+We used a single node of the Supermuc Phase 2.
 The node has two Intel® Haswell Xeon Processor E5-2697 v3 \textsc{cpu}s with 14 cores each.
@@
 The test cases were identical in setting to the aforementioned \amr{} run, but with two levels of refinement.
-The best median performance was achieved by using six background threads.
+The best median performance was achieved with six background threads.
 Note that the results were noisy and it is unclear whether the chosen number of background threads is optimal.
@@
 
-\section{Reactive Euler \textit{\&} Navier Stokes}\label{sec:results-reactive}
-As a final benchmark, we used the \textsc{cj}-detonation wave~\pcref{eq:cj-detonation} to evaluate the reactive Navier-Stokes equations.
+\section{Simulation of Reactive Detonation Waves}\label{sec:results-reactive}
+As a final benchmark, we used the \textsc{cj} detonation wave~\pcref{eq:cj-detonation} to evaluate the reactive Navier-Stokes equations.
 We used a limiting \aderdg{}-scheme with an order of 3.
@@
 We use $\Qrho, \pressure$ and $\QZZ$ as \textsc{dmp} variables.
-\begin{figure}[tb]
+\begin{figure}[t]
   \centering
@@
 The results for runs with and without \textsc{dmp} can be seen in \cref{fig:detonation-line-plots}.
-Note, that oscillations appeared for the Euler equations unless we use the \textsc{dmp}-criterion.
+Note, that oscillations appeared for the Euler equations without the \textsc{dmp}-criterion.
 This is not the case for the Navier Stokes equations.
@@
 Furthermore, they have the effect that fewer cells are limited~(\cref{fig:detonation-pressure-contour}).
-Note that the limiter activation are not symmetric which is unexpected for a radial-symmetric scenario.
+Note that the limiter activation are not symmetric which is unexpected for a radialsymmetric scenario.
 The contours for pressure and mass fraction look similar for all considered settings.
@@
 The viscous effects have a similar smoothing effect as in~\cite{hidalgo2011ader}.
-
-\begin{figure}[htb]
+\begin{figure}[htb!]
   \centering
@@
 \end{figure}
-\begin{figure}[H]
+\begin{figure}[htb]
     \centering
-    \includegraphics[width=0.3\textwidth]{leveque_detonation_mass_fraction}
+    \includegraphics[width=0.4\textwidth]{leveque_detonation_mass_fraction}
     \caption{\label{fig:detonation-contour-reference}Reference solution for mass fraction with stiff source.

### 2019-01-21 writing/thesis/chapters/scenarios.tex
Final (?) changes.

@@
 {Name} & {Analytic Solution} & {Gravity} & {Coupling} & {Limiting}\\ \midrule
-Manufactured Solution~\cite{dumbser2010arbitrary} & \cmark{} & \xmark{} & \xmark{} & \xmark{} \\
-Taylor-Green Vortex~\cite{dumbser2016high} & \cmark{} & \xmark{} & \xmark{} & \xmark{} \\
-\textsc{ABC}-Flow~\cite{tavelli2016staggered} & \cmark{} & \xmark{} & \xmark{} & \xmark{} \\
-Lid Driven Cavity~\cite{fambri2017space} & \xmark{} & \xmark{} & \xmark{} & \cmark{} \\
-Cosine Bubble~\cite{giraldo2008study} & \xmark{} & \cmark{} & \xmark{} & \xmark{} \\
-Two Bubbles~\cite{robert1993bubble,muller2010adaptive} & \xmark{} & \cmark{} & \xmark{} & \xmark{} \\
-\textsc{CJ}-Detonation~\cite{helzel2000modified,hidalgo2011ader} & \xmark{} & \xmark{} & \cmark{} & \cmark{} \\
+Manufactured solution~\cite{dumbser2010arbitrary} & \cmark{} & \xmark{} & \xmark{} & \xmark{} \\
+Taylor-Green vortex~\cite{dumbser2016high} & \cmark{} & \xmark{} & \xmark{} & \xmark{} \\
+\textsc{ABC}-flow~\cite{tavelli2016staggered} & \cmark{} & \xmark{} & \xmark{} & \xmark{} \\
+Lid driven cavity~\cite{fambri2017space} & \xmark{} & \xmark{} & \xmark{} & \cmark{} \\
+Cosine bubble~\cite{giraldo2008study} & \xmark{} & \cmark{} & \xmark{} & \xmark{} \\
+Two bubbles~\cite{robert1993bubble,muller2010adaptive} & \xmark{} & \cmark{} & \xmark{} & \xmark{} \\
+\textsc{CJ} detonation~\cite{helzel2000modified,hidalgo2011ader} & \xmark{} & \xmark{} & \cmark{} & \cmark{} \\
 \bottomrule
@@
 \item The bubble scenarios are simple examples for flows over a realistic background atmosphere.  
-\item The \textsc{cj}-detonation wave uses the reactive advection term to model a detonation.
+\item The \textsc{cj} detonation wave uses the reactive advection term to model a detonation.
 \end{itemize}
@@
 
-\sidetitle{Taylor-Green Vortex}
-An interesting testing scenario is the Taylor-Green Vortex, which exhibits a complicated flow from a simple initial condition.
+\sidetitle{Taylor-Green vortex}
+An interesting testing scenario is the Taylor-Green vortex, which exhibits a complicated flow from a simple initial condition.
 It is an analytic solution for the incompressible Navier-Stokes equations which agrees relatively well with our equation set at low Mach numbers.
@@
 \end{align}
-where $C = 100/\gamma$ is a constant that governs the speed of sound and thus the Mach number~\cite{dumbser2016high}.
+where $C = \nicefrac{100}{\gamma}$ is a constant that governs the speed of sound and thus the Mach number~\cite{dumbser2016high}.
 
@@
 
-\sidetitle{ABC-Flow}
+\sidetitle{ABC-flow}
 %\subsection{ABC-Flow}
@@
 
-\sidetitle{Lid-Driven Cavity}
-%\subsection{Lid-Driven Cavity Flow}
+\sidetitle{Lid-driven cavity}
 The lid-driven cavity flow is another simple testing scenario for the Navier-Stokes equations.
@@
   \Qv(\bm{x}) &=  \bm{0},\\
-  \pressure(\bm{x}) &= \frac{100}{\gamma}.
+  \pressure(\bm{x}) &= \nicefrac{100}{\gamma}.
   \end{split}
@@
 
-\sidetitle{CJ Detonation Wave}
+\sidetitle{CJ detonation wave}
 We investigate the radialsymmetric Chapman-Jouget (\textsc{cj}) detonation wave scenario from~\cite{helzel2000modified}.
@@
 
-The initial conditions for pressure and density can be computed directly from the \textsc{pde} once few assumptions have been given.
+The initial conditions for pressure and density can be computed directly from the \textsc{pde} given a few assumptions.
 We assume that $\backgroundPotT$ is constant over the entire domain~\cite{giraldo2008study}.
@@
 \end{equation}
-We want to consider flow in hydrostatic equilibrium, i.e.\ a flow for which the pressure-gradient and gravitational force are exactly in balance.
+We want to consider flow in hydrostatic equilibrium, i.e.\ a flow for which the pressure-gradient and gravitational force are exactly in balance~\cite{muller2010adaptive}.
 Inserting this assumption in the momentum equation in $z$-direction and using \cref{eq:eos} once again, we arrive at the ordinary differential equation (\textsc{ode})
@@
                                      = 
-        - \frac{g p_{0}^{\frac{R}{c_{p}}} p^{\frac{1}{\gamma}}{\left (z \right )}}{R \backgroundPotT}\\
-  p{\left (0 \right )} &= p_0
+        - \frac{g p_{0}^{\frac{R}{c_{p}}} p^{\frac{1}{\gamma}}{\left (z \right )}}{R \backgroundPotT},\\
+  p{\left (0 \right )} &= p_0,
   \end{split}
@@
 
-\sidetitle{Hydrostatic Wall}
+\sidetitle{Hydrostatic wall}
 This leaves us with one problem:
@@
 
-\sidetitle{Cosine Bubble}
-As a simple test case, we consider the cosine bubble scenario that describes a background atmosphere that is perturbed by a large warm air bubble in the middle of the domain~\cite{giraldo2008study}.
+\sidetitle{Cosine bubble}
+As a simple test case, we consider the cosine bubble scenario which describes a background atmosphere that is perturbed by a large warm air bubble in the middle of the domain~\cite{giraldo2008study}.
 We use a background potential temperature of $\backgroundPotT = 300$ and a domain of $\SI{1}{\km} \times \SI{1}{\km}$.
@@
 
-\sidetitle{Two Bubbles}
+\sidetitle{Two bubbles}
 The two bubbles scenario consists of a small cold air bubble that is on top of a large warm air bubble~\cite{robert1993bubble,muller2010adaptive}.

### 2019-01-21 writing/thesis/pages/acknowledgements.tex
Final (?) changes.

@@
 \vspace{1em}
-I want to thank Prof.\ Bader for the chance to work on this exciting topic.
-I also want to thank my advisor Leonhard Rannabauer, whose guidance made this thesis not only possible but also enjoyable.
+I want to thank Prof.\ Michael Bader for the chance to work on this exciting topic.
+I am particularly grateful to my advisor Leonhard Rannabauer, whose guidance made this thesis not only possible but also enjoyable.
+Additionally, I wish to acknowledge the support of Dominic Charrier, who was of great help with the implementation in \exahype{}.
 
 My gratitude extends to my friends and family, who supported me during the entire thesis.
-Special thanks go to my friend William who proof-read the thesis.
+Special thanks go to my friend William who proofread this document.
 \cleardoublepage{}

### 2019-01-23 writing/slides/final.tex
Add draft of final slides.

% https://tex.stackexchange.com/questions/123106/detect-aspect-ratio-in-beamer?noredirect=1&lq=1
\documentclass[aspectratio=169]{beamer}
%\documentclass[]{beamer}
%\usepackage{eulervm}
\usetheme{metropolis} % Use metropolis theme
\usepackage{appendixnumberbeamer}
\usepackage{lmodern}

\renewcommand{\footnoterule}{%
  \hspace{2cm}
  \kern -3pt
  \hrule width \textwidth height 1pt
  \kern 2pt
}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[autostyle, english = british]{csquotes}
\usepackage[british]{babel}
\usepackage{todonotes}
\usepackage[%
  backend=biber,
  doi=false,
  url=false,
  isbn=false,
  eprint=false,
  style=verbose,
  citestyle=verbose,
  hyperref=true,
  maxnames=99,
  minnames=1,
  maxbibnames=99,
  firstinits,
  uniquename=init]{biblatex}
%\DeclareFieldFormat[inproceedings, article]{pages}{}%
%\DeclareFieldFormat[inproceedings]{organization}{}%
  % ignore some field for citations
\DeclareSourcemap{
  \maps[datatype=bibtex, overwrite]{
    \map{
      \step[fieldset=edition, null]
      \step[fieldset=publisher, null]
      \step[fieldset=pages, null]
      \step[fieldset=organization, null]
    }
  }
}

\addbibresource{../bibliography.bib}

\let\oldfootnotesize\footnotesize
\renewcommand*{\footnotesize}{\oldfootnotesize\fontsize{6}{6}}

\usepackage{caption}
\usepackage{xpatch}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{mathtools} % for \mathclap
\usepackage{nicefrac}
\usepackage{physics} % for derivatives
\usepackage{varioref}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage[noabbrev]{cleveref}
\newcommand{\creflastconjunction}{, and\nobreakspace} % use Oxford comma
\usepackage{todonotes}
\usepackage{multimedia}

\graphicspath{{../figures/}}
\let\boundary\undefined%

\usepackage{bm}
\input{../thesis/macros.tex}

\input{ifaspectratio.tex}

% \newcommand{\Qrho}{\ensuremath{\rho}}
% \newcommand{\Qj}{\ensuremath{\rho \bm{v}}}
% %\newcommand{\Qv}{\ensuremath{\Qrho^{-1} \Qj}}
% \newcommand{\Qv}{\ensuremath{\bm{v}}}
% \newcommand{\QE}{\ensuremath{\rho E}}
% \newcommand{\stressT}{\ensuremath{\bm{\sigma}}}
% \newcommand{\pressure}{\ensuremath{p}}
% \newcommand{\maxConvEigen}{\ensuremath{\vert \lambda_c^{\text{max}} \vert}}
% \newcommand{\maxViscEigen}{\ensuremath{\vert \lambda_v^{\text{max}} \vert}}

\newcommand{\cn}{\footnote{\enquote{TODO: Citation.}, 2017, \textbf{Conference}, \textit{Author 1, Author 2, Author 3, Author 4} }}

\title{Cloud Simulation with the ExaHyPE-Engine\\Master Thesis Final}
\author{Lukas Krenz\\Adviser: Leonhard Rannabauer\\Supervisor: Prof.\ Dr.\ Michael Bader}
\date{January 24, 2019} 
\institute{\textsc{tum}, Chair for Scientific Computing}

\begin{document}
\maketitle
\begin{frame}{Two Bubbles: Hydrostatic Equilibrium\footfullcite{robert1993bubble}}
  \begin{columns}
    \begin{column}[t]{0.5\textwidth}
      \begin{itemize}
      \item 
  Air is in hydrostatic equilibrium:

  Gravitational force and pressure-gradient force are \textbf{exactly balanced}.

  \item Constant potential temperature (temperature normalized by pressure) with larger, warm bubble and small, cold bubble on top.

  \end{itemize}
    \end{column}~%
    \begin{column}[t]{0.5\textwidth}
      \begin{figure}[h]
        \ifratio{43}{
          \includegraphics{beamer_43_hydrostatic_equilibrium}
        } {
          \includegraphics{beamer_169_hydrostatic_equilibrium}
        }
\caption{Background pressure in equilibrium}
\end{figure}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Two Bubbles: Simulation}
   \begin{figure}[h]
    \centering
    \ifratio{43}{
    \movie[width=0.9\textwidth, height=0.6\textwidth, autostart,, loop, poster]{}{two_bubbles_cartesian.ogv}
  } {
    \movie[width=0.7\textwidth, height=0.466666\textwidth, autostart,, loop, poster]{}{two_bubbles_cartesian.ogv}
  }
    \caption{Two Bubbles scenario}
  \end{figure}
\end{frame}

\begin{frame}{The ADER-DG Approach\footfullcite{dumbser2008unified}}
  Solve \textbf{hyperbolic conservation laws} of the form
\begin{equation}
  \label{eq:conservation-law}
 \frac{\partial}{\partial_t}  \Q + \divergence{\flux(\Q)} = \source(\bm{x}, t, \Q)
\end{equation}
with $Q$ vector of conserved variables, $\bm{x}$ position, $t$ time,  $\nabla \cdot F(Q)$ divergence of flux and $S(\bm{x}, t, Q)$ source term.

\textbf{Discontinuous Galerkin} (\textsc{DG}) divides domain into disjoint elements, approximates solutions by piecewise-polynomials.
Elements are connected by solving the Riemann problem.

\textbf{ADER}-Approach uses space-time polynomials for time integration instead of Runge-Kutta procedures.

Implemented in the \textsc{PDE}-Framework \textbf{ExaHyPE}.
\end{frame}

\begin{frame}{The Navier-Stokes Equations (with advection coupling\footfullcite{hidalgo2011ader})}
  Vector of conserved quantities:
\begin{equation}
  \label{eq:conserved-variables}
 \Q = \left( \Qrho, \Qj, \QE, \QZ \right) 
\end{equation}
With $\Qrho$ density of fluid, $\Qj$ velocity density, $\QE$ energy density, $\QZ$ mass fraction of unburnt gas.

Flux:
\begin{equation}
  F(\Q, \textcolor{orange}{\gradQ}) = 
  \begin{pmatrix}
    \Qj \\
    \Qv  \otimes \Qj + \bm{I} \pressure + \textcolor{orange}{\stressT} (\Q, \gradQ)  \\
    \Qv \cdot \left(\bm{I} \QE + \bm{I} \pressure + \textcolor{orange}{\stressT (\Q, \gradQ)} \right) -
    \textcolor{orange}{\kappa \nabla T}\\
    \Qj \QZZ
  \end{pmatrix}
\end{equation}

$T$ temperature, $\pressure(\Q)$ pressure,
$\textcolor{orange}{\stressT}$ stress tensor, $\textcolor{orange}{\kappa \nabla T}$ heat diffusion term
\end{frame}

\begin{frame}{Problem: Not hyperbolic}
  \textsc{DG} solves equations of the form (e.g.\ Euler):
  \begin{equation}
  \label{eq:conservation-law}
 \pdv{\Q}{t} + \divergence{\flux(\Q)} = \source(\bm{x}, t, \Q)
\end{equation}

We have:
\begin{equation}
  \label{eq:conservation-law-gradient}
 \pdv{\Q}{t} + \divergence{\flux(\Q, \textcolor{orange}{\gradQ})} = \source(\bm{x}, t, \Q)
\end{equation}

\textbf{Solution}:
Modify numerical flux (Riemann solver), time step size (\textsc{cfl}-Condition) and boundary conditions to \textbf{allow diffusive terms}\footfullcite{dumbser2010arbitrary}.

\alert{No explicit discretization} of gradient $\gradQ$.
\end{frame}

\begin{frame}{Convergence Tests}
  \begin{figure}[h]
    \centering
    \ifratio{43}{
      \includegraphics[]{{beamer_43_convergence}}
  } {
    \includegraphics[]{{beamer_169_convergence}}
  }

    \caption{Errors. $N$ polynomial order. Dotted lines optimal order $N+1$. }
  \end{figure}
\end{frame}

\begin{frame}{Adaptive Mesh Refinement: Indicator}
  $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ maps solution to indicator variable.

  In our case: potential temperature.

  Total variation of $f$:
\begin{equation}
  \label{eq:tv}
  \tv \left[ f(\bm{x}) \right] =
  \Vert
\intdcell{ \vert \gradient{f \left( \bm{x} \right)} \vert }
\Vert_1
\end{equation}

\end{frame}

\begin{frame}{Adaptive Mesh Refinement: Global Criterion}
  \begin{block}{Chebyshev's inequality}
\begin{equation}
  \label{eq:chebychev}
  \mathbb{P}(\vert X - \mu \vert \geq c \sigma) \leq \frac{1}{c^2}
\end{equation}
\end{block}

\begin{block}{Criterion}

\begin{equation}
  \label{eq:refinement-criterion}
  \operatorname{evaluate-refinement}(\Q, \mu, \sigma) =
  \begin{cases}
    \text{refine} & \text{if } \tv(\Q) \geq \mu + T_\text{refine} \sigma \\
    \text{delete} & \text{if } \tv(\Q) < \mu + T_\text{delete} \sigma \\
    \text{keep} & \text{otherwise}
    \end{cases}
\end{equation}
Computation of $\mu, \sigma$ with stable, pairwise reduction\footfullcite{chan1982updating}.

Global observables implemented in \exahype{} for \textbf{general} pairwise reductions.
\end{block}
\end{frame}

\begin{frame}
  \frametitle{AMR vs.\ fully refined grid: Settings \textit{\&} time
    to solution}
  \begin{block}{Settings}
    \begin{description}
    \item[AMR] Coarse mesh size with $27 \times 27$ cells, one adaptive level.

      Potentially up to $81 \times 81$ cells.

      $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$.
    \item[Reference] $81 \times 81$ cells.
    \end{description}
  \end{block}
  Both polynomial order 4.

  Fully refined grid took \textbf{71\%} longer!
\end{frame}

\begin{frame}
  \frametitle{AMR vs.\ fully refined grid: Grid}
   \begin{figure}[h]
    \centering
    \ifratio{43}{
    \movie[width=0.9\textwidth, height=0.6\textwidth, autostart,, loop, poster]{}{two_bubbles_legendre.ogv}
  }{
    \movie[width=0.7\textwidth, height=0.46666\textwidth, autostart,, loop, poster]{}{two_bubbles_legendre.ogv}
  }
    \caption{Two bubbles scenario, with \amr{}}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{AMR vs.\ fully refined grid: Error}
  \begin{figure}[H]
    \centering
    \ifratio{43}{
\includegraphics[width=0.9\textwidth]{thesis_two_bubbles_amr_error}
  } {
\includegraphics[width=0.6\textwidth]{thesis_two_bubbles_amr_error}
  }
\caption{Potential temperature of fully refined solution minus \amr{} grid.}
  \end{figure}
\end{frame}

\begin{frame}{MUSCL-Hancock Scheme~\footfullcite{vanLeer1979towards}}
  Finite Volume scheme: store only \textbf{cell averages}

  \textbf{Reconstruction} of linear function

  \textbf{Second order} in time and space

  \textbf{Stabilized} with (minmod) slope limiter

  Problem in \exahype{}: Boundary conditions \textbf{unstable}, can only prescribe values at boundary.
\end{frame}

\begin{frame}{Finite Volume Limiting\footfullcite{dumbser2016simple}}
  \begin{description}
\item[ADER-DG] high order, but unstable
\item[MUSCL] low order, but stable
\item[Combination] high order \textbf{and} stable
  \end{description}

Recompute if solution:
\begin{itemize}
\item varies by a suspicious amount, using discrete maximum principle (\textsc{dmp}) as heuristic
\item is NaN or $\infty$
\item is unphysical
 \begin{equation}
  \label{eq:limiting-physical}
  \operatorname{is-admissible}(\Q) =
  \begin{cases}
    \text{true} & \Qrho > 0 \land \pressure > 0 \land \QZZ \geq 0 \\
    \text{false} & \text{otherwise}
  \end{cases}
\end{equation}
\end{itemize}
\end{frame}

\begin{frame}\frametitle{Reactive Source\footfullcite{hidalgo2011ader,helzel2000modified}}
Source term for mass fraction $\QZ$:  
 \begin{equation}\label{eq:source-reaction}
  \source[\QZ] = - K(T) \QZ
\end{equation}

Reaction model:
\begin{equation}\label{eq:reaction-model}
  K(T) = 
\begin{cases}
  - \frac{1}{\reactionTimescale} & T > \reactionTemperature\\
  0 & \text{otherwise}
\end{cases}  
\end{equation}
$\reactionTimescale = 0.01$ timescale of reaction

$\reactionTemperature$ activation temperature
\end{frame}

\begin{frame}
  \frametitle{Result Reactive}
   \begin{figure}[h]
    \centering
    \ifratio{43}{
    \movie[width=0.9\textwidth, height=0.6\textwidth, autostart,, loop, poster]{}{detonation.ogv}
  }{
    \movie[width=0.7\textwidth, height=0.46666\textwidth, autostart,, loop, poster]{}{detonation.ogv}
  }
    \caption{Detonation. Height is pressure, color refinement.
    Reactive Euler Equations.}
  \end{figure}
\end{frame}

\begin{frame}{Summary}
  \begin{block}{}
  \begin{itemize}
  \item \aderdg{} \textbf{converges} for Navier Stokes equations
  \item \aderdg{} shows \textbf{good results} for large set of scenarios (many not shown here!)
  \item (Limiting) \aderdg{} works for reactive Euler \textit{\&} Navier-Stokes
  \item \amr{}-criterion is \textbf{faster} and tracks cloud \textbf{correctly}.
  \item All \textbf{extensions} to engine (diffusive fluxes, global observables) useful for \textbf{other users} of \exahype{}.
  \end{itemize}
  \end{block}

  \begin{block}{Future Work}
    \begin{itemize}
    \item Extension to stiff source terms
    \item Boundary conditions for \muscl{}.  
    \end{itemize}

  \end{block}
\end{frame}

\appendix
\begin{frame}
  \frametitle{Reference Solution Two Bubbles\footfullcite{muller2010adaptive}}
  \begin{center}
    \ifratio{43}{
\only<1>{\includegraphics[scale=0.8,trim={0cm 16.3cm 0cm 0cm}, clip]{beamer_two_bubbles_contour_collage_alternative}}
\only<2>{\includegraphics[scale=0.8,trim={0cm 11.0cm 0cm 5.2cm}, clip]{beamer_two_bubbles_contour_collage_alternative}}
\only<3>{\includegraphics[scale=0.8,trim={0cm 5.6cm 0cm 10.6cm}, clip]{beamer_two_bubbles_contour_collage_alternative}} 
\only<4>{\includegraphics[scale=0.8,trim={0cm 0.0cm 0cm 16cm}, clip]{beamer_two_bubbles_contour_collage_alternative}}

} {
\only<1>{\includegraphics[scale=1.0,trim={0cm 16.3cm 0cm 0cm}, clip]{beamer_two_bubbles_contour_collage_alternative}}
\only<2>{\includegraphics[scale=1.0,trim={0cm 11.0cm 0cm 5.2cm}, clip]{beamer_two_bubbles_contour_collage_alternative}}
\only<3>{\includegraphics[scale=1.0,trim={0cm 5.6cm 0cm 10.6cm}, clip]{beamer_two_bubbles_contour_collage_alternative}} 
\only<4>{\includegraphics[scale=1.0,trim={0cm 0.0cm 0cm 16cm}, clip]{beamer_two_bubbles_contour_collage_alternative}}
}
 \end{center}
\end{frame}

\end{document}

### 2019-01-24 writing/slides/final.tex
Small fixes for slides.

@@
 \end{equation}
-with $Q$ vector of conserved variables, $\bm{x}$ position, $t$ time,  $\nabla \cdot F(Q)$ divergence of flux and $S(\bm{x}, t, Q)$ source term.
+with $\Q$ vector of conserved variables, $\bm{x}$ position, $t$ time,  $\divergence{\flux(\Q)}$ divergence of flux and $\source(\bm{x}, t, \Q)$ source term.
 
@@
 \end{equation}
-With $\Qrho$ density of fluid, $\Qj$ velocity density, $\QE$ energy density, $\QZ$ mass fraction of unburnt gas.
+With $\Qrho$ density of fluid, $\Qj$ velocity density, $\QE$ energy density, $\QZ$ mass fraction of chemical reactant (unburnt gas).
 
@@
     \Qj \\
-    \Qv  \otimes \Qj + \bm{I} \pressure + \textcolor{orange}{\stressT} (\Q, \gradQ)  \\
+    \Qv  \otimes \Qj + \bm{I} \pressure + \textcolor{orange}{\stressT (\Q, \gradQ)}  \\
     \Qv \cdot \left(\bm{I} \QE + \bm{I} \pressure + \textcolor{orange}{\stressT (\Q, \gradQ)} \right) -
@@
 
-$T$ temperature, $\pressure(\Q)$ pressure,
-$\textcolor{orange}{\stressT}$ stress tensor, $\textcolor{orange}{\kappa \nabla T}$ heat diffusion term
+Pressure $\pressure(\Q)$,
+stress tensor $\textcolor{orange}{\stressT}$, heat diffusion $\textcolor{orange}{\kappa \nabla T}$ with temperature $T$.
 \end{frame}
@@
 \textbf{Solution}:
-Modify numerical flux (Riemann solver), time step size (\textsc{cfl}-Condition) and boundary conditions to \textbf{allow diffusive terms}\footfullcite{dumbser2010arbitrary}.
+Modify numerical flux (Riemann solver), time step size (\textsc{cfl}-Condition) and boundary conditions to \textbf{allow diffusive terms}\footfullcite{dumbser2010arbitrary,gassner2008discontinuous}.
 
@@
 
-  Total variation of $f$:
+  Total variation of $\bm{x}$ for cell $\cell$:
 \begin{equation}
@@
 \end{equation}
-Computation of $\mu, \sigma$ with stable, pairwise reduction\footfullcite{chan1982updating}.
+Computation of mean $\mu$, standard deviation $\sigma$ with \textbf{stable}, pairwise reduction\footfullcite{chan1982updating}.
 
@@
   }
-\caption{Potential temperature of fully refined solution minus \amr{} grid.}
+\caption{Potential temperature of fully refined solution minus \amr{} solution.}
   \end{figure}
@@
  \begin{equation}\label{eq:source-reaction}
-  \source[\QZ] = - K(T) \QZ
-\end{equation}
-
-Reaction model:
-\begin{equation}\label{eq:reaction-model}
-  K(T) = 
-\begin{cases}
-  - \frac{1}{\reactionTimescale} & T > \reactionTemperature\\
+  \source[\QZ] =\begin{cases}
+  - \frac{1}{\reactionTimescale} \QZ  & T > \reactionTemperature\\
   0 & \text{otherwise}
@@
 \end{equation}
-$\reactionTimescale = 0.01$ timescale of reaction
 
-$\reactionTemperature$ activation temperature
+$\reactionTimescale = 0.01$ timescale of reaction.
+
+$\reactionTemperature$ activation temperature.
 \end{frame}
@@
 \begin{frame}{Summary}
-  \begin{block}{}
+  \begin{block}{Results}
   \begin{itemize}
@@
   \item \aderdg{} shows \textbf{good results} for large set of scenarios (many not shown here!)
-  \item (Limiting) \aderdg{} works for reactive Euler \textit{\&} Navier-Stokes
   \item \amr{}-criterion is \textbf{faster} and tracks cloud \textbf{correctly}.
+  \item (Limited) \aderdg{} works for reactive Euler \textit{\&} Navier-Stokes
   \item All \textbf{extensions} to engine (diffusive fluxes, global observables) useful for \textbf{other users} of \exahype{}.

### 2019-03-05 writing/paper/paper.tex
Begin writing PPAM paper.

\documentclass[runningheads]{llncs}
\title{Clouds}
\author{$\ldots$}
\institute{$\ldots$}

\usepackage{caption}
\usepackage{xparse} % for NewDocumentCommand
\usepackage{etoolbox} % for notblank (brackets only when argument)
\usepackage{xstring} % for \IfSubStr
\usepackage{xpatch}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathtools} % for \mathclap
\usepackage{nicefrac}
\usepackage{physics} % for derivatives
\usepackage{varioref}
\usepackage{nicefrac}
\usepackage{physics} % for derivatives
\usepackage[separate-uncertainty]{siunitx}
\usepackage{hyperref}
\usepackage[noabbrev]{cleveref}
\newcommand{\creflastconjunction}{, and\nobreakspace} % use Oxford comma
\usepackage{todonotes}
\usepackage{multimedia}
\graphicspath{{../figures/}}
\let\boundary\undefined%
\crefformat{equation}{\eqA{}eq.~\eqB #2#1#3)}
% TODO: Fix for more than two equations!
\crefmultiformat{equation}{eqs.~\eqMultiA#2#1#3\eqMultiB}%
{ and \eqMultiA#2#1#3\eqMultiB}{, \eqMultiA#2#1#3\eqMultiB}{ and~\eqMultiA#2#1#3\eqMultiB}
\newcommand{\eqA}{}
\newcommand{\eqB}{(}
\newcommand{\eqMultiA}{(}
\newcommand{\eqMultiB}{)}
\DeclareRobustCommand{\pcrefSingle}[1]{%
\begingroup%
  \renewcommand{\eqA}{(}\renewcommand{\eqB}{}%
\cref{#1}%
\endgroup%
}
\DeclareRobustCommand{\pcrefMulti}[1]{%
\begingroup%
    \renewcommand{\eqMultiA}{}\renewcommand{\eqMultiB}{}%
    (\cref{#1})%
\endgroup%
}
\DeclareRobustCommand{\pcref}[1]{%
\IfSubStr{#1}{,}{\pcrefMulti{#1}}{\pcrefSingle{#1}}%
}

\usepackage{bm}
\input{../thesis/macros.tex}

\begin{document}
\maketitle
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
\section{Introduction}
\newcommand{\diffCoeff}{\varepsilon}
\newcommand{\hyperFluxDef}{
  \begin{pmatrix}
    \Qj \\
    \Qv  \otimes \Qj + \bm{I} \pressure  \\
    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure) \\
    \Qj \QZZ
  \end{pmatrix}
}
\newcommand{\viscFluxDef}{
  \begin{pmatrix}
    0\\
     \stressT (\Q, \gradQ)  \\
     \Qv \cdot \stressT (\Q, \gradQ) - \kappa \gradient{T}\\
     0\\
   \end{pmatrix}
}%
We solve the reactive compressible Navier-Stokes equations in the conservative form% \pcref{eq:conservation-law-gradient}
\begin{equation}
 \label{eq:equation-set} 
%  \begin{array}{l}
%  \text{mass cons.} \\
%  \text{momentum cons.} \\
%  \text{energy cons.} \\
%  \text{cont.\ gas} 
% \end{array}
% :
\quad
  \pdv{}{t}
  \underbrace{
  \begin{pmatrix}
    \Qrho\\
    \Qj\\
    \QE\\
    \QZ
    \end{pmatrix}}_{\Q}
  +
  \divergence{
  \underbrace{
  \left(
   \underbrace{\hyperFluxDef}_{\hyperFlux(\Q)}
+
\underbrace{\viscFluxDef}_{\viscFlux(\Q, \gradQ)}
  \right)}_{\flux(\Q, \gradQ)}}
 =
  \underbrace{
  \begin{pmatrix}
    \source[\Qrho\phantom{\Qrho}]\\
    \source[\Qj]\\
    \source[\QE]\\
    \source[\QZ]
    \end{pmatrix}}_{\source(\Q, \bm{x}, t)}
\end{equation}
which describes the time evolution of variables $\Q$ with respect to a flux $\flux(\Q, \gradQ)$ and a source $\source(\Q)$.
The vector of conserved quantities is given by
\begin{equation}
  \label{eq:conserved-variables}
 \Q = \left( \Qrho, \Qj, \QE, \QZ \right),
\end{equation}
where $\Qrho$ is the density, $\Qj$ is the two or three-dimensional momentum, $\QE$ is the energy density and $\QZ$ is the mass fraction of the chemical reactant.
The pressure $\pressure$ is given by the equation of state of an ideal reacting gas
\begin{equation}
  \label{eq:eos}
  \pressure = (\gamma - 1) \left(\QE - \frac{1}{2} \left(\Qv \cdot \Qj \right)  - q_0 \QZ - gz \right).
\end{equation}
The term $q_0 \QZ$ is the chemical energy with a heat release $q_0$~\cite{helzel2000modified}, the term $gz$ is the geopotential height with the gravity of Earth $g$~\cite{giraldo2008study}.
We model the diffusive effects of the flow by the standard stress tensor
\begin{equation}
  \label{eq:stress-tensor}
  \stressT(Q, \nabla Q) =
  \mu
  \left(
  \left(\nicefrac{2}{3} \divergence{\Qv} \right) -
  \left( \gradient{\Qv} + \gradient{\Qv}^\intercal \right)
  \right),
\end{equation}
with viscosity $\mu$.

Many realistic, atmospheric flows can be described by a pertubation over a background state that is in hydrostatic equilibrium
\newcommand{\backgroundPressure}{\overline{\pressure}}
\newcommand{\backgroundRho}{\overline{\Qrho}}
\begin{equation}
  \label{eq:hydrostatic-balance}
  \pdv{}{z} \backgroundPressure{\left (z \right )} = -g \backgroundRho(z).
\end{equation}
The momentum equation is dominated by the background flow in this case.
This leads to numerical instabilities.
We avoid this by splitting the pressure $\pressure = \backgroundPressure + \pressure'$ and density $\Qrho = \backgroundRho + \Qrho'$
\begin{equation}
  \label{eq:momentum-equation-split}
  \pdv{\Qj}{t}+ \divergence{ \left(
    \Qv \otimes \Qj + \bm{I} \pressure'
    \right)
  } + \viscFlux_\Qj
  =
  -g \bm{k} \Qrho'.
\end{equation}

The rest of this paper is organized as follows:
\begin{itemize}
\item Efficient, explicit \aderdg{}-scheme with shared and distributed memory parallelization.
\item An \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
\item Evaluation with standard \textsc{cfd} scenarios, atmospheric and reactive flows.
\end{itemize}

\section{Methods}
Maybe numerics (dg+muscl?), at least ref.
Exahype?!

We use the \aderdg{}-scheme as proposed in xxx together with a Rusanov-style flux, which is adapted for \pde{}s with diffusive terms.

Let $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ be a function that maps the discrete solution at a point $\bm{x}$ to an arbitrary indicator variable.
The total variation (\textsc{tv}) of this function is defined by
\begin{equation}
  \label{eq:tv}
  \tv \left[ f(\bm{x}) \right] =
  \Vert
\intdcell{ \vert \gradient{f \left( \bm{x} \right)} \vert }
\Vert_1
\end{equation}
for each cell.
The operator $\Vert \cdot \Vert_1$ denotes the discrete $l_1$ norm in this equation.
We compute this efficiently with Gaussian quadrature over the collocated quadrature points.
\newcommand{\mean}{\mu}%
\newcommand{\std}{\sigma}%
\newcommand{\variance}{\std^2}%
\newcommand{\Trefine}{T_\text{refine}}%
\newcommand{\Tdelete}{T_\text{delete}}%
How can we decide whether a cell is important or not?
To resolve this conundrum, we compute the mean and the population standard deviation of the total variation of all cells.
It is important to note that we use the method of Chan/LeVeque to compute the modes in a parallel and numerical stable manner.
A cell is then considered to contain significant information if its deviates from the mean more than a given threshold.
This criterion can be described formally by
\begin{equation}
  \label{eq:refinement-criterion}
  \operatorname{evaluate-refinement}(\Q, \mu, \sigma) =
  \begin{cases}
    \text{refine} & \text{if } \tv(\Q) \geq \mu + \Trefine \sigma \\
    \text{delete} & \text{if } \tv(\Q) < \mu + \Tdelete \sigma \\
    \text{keep} & \text{otherwise}.
    \end{cases}
\end{equation}
The parameters $\Trefine > \Tdelete$ can be chosen freely.
Chebyshev's inequality
\begin{equation}
  \label{eq:chebychev}
  \mathbb{P}(\vert X - \mu \vert \geq c \sigma) \leq \frac{1}{c^2},
\end{equation}
with probability $\mathbb{P}$ guarantees that we neither refine nor delete all cells.
This inequality holds for arbitrary distributions under the weak assumption that they have a mean $\mu$ and standard deviation $\sigma$~\cite{wasserman2004all}.

We use a muscl-hancock based finite volume limiting as proposed in xxx.
Briefly, we first compute a candidate solution with our \aderdg{}-scheme and check whether it is valid.
A solution is considered to be invalid if it is a non-finite floating point number or if it is unphysical, i.e.\ if the pressure or density are not positive.
\todo{dmp?}
In case of an invalid solution, we recompute the timestep with a limited \muscl{} finite volume method.

\section{Results}
We use a diverse mix of benchmarking scenarios that consist of standard \textsc{cfd} scenarios, and atmospheric and reactive flows.

A simple scenario is the Taylor-Green vortex.
It has an analytical solution in the incompressible limit
The solution is
\begin{align}
  \label{eq:taylor-green}
  \begin{split}
  \Qrho(\bm{x}, t) &= 1,\\
  \Qv(\bm{x}, t) &= \exp(-2 \mu t)
  \begin{pmatrix}
    \phantom{-}\sin(x) \cos(y) \\
- \cos(x) \sin(y) 
    \end{pmatrix}, \\
  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \nicefrac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C,
  \end{split}
\end{align}
where $C = \nicefrac{100}{\gamma}$ is a constant that governs the speed of sound and thus the Mach number~\cite{dumbser2016high}.
We use a viscosity of $\mu = 0.1$ and Cauchy boundary conditions.

We use the Arnold–Beltrami–Childress (\textsc{abc}) flow as a simple three-dimensional flow~\cite{tavelli2016staggered}.
It also has an exact solution under the assumption of incompressibility
\begin{align}
  \label{eq:abc-flow}
  \begin{split}
  \Qrho(\bm{x}, t) &= 1,\\
  \Qv(\bm{x}, t) &= \phantom{-} \exp(-1\mu t)
  \begin{pmatrix}
    \sin(z) + \cos(y)\\
    \sin(x) + \cos(z)\\
    \sin(y) + \cos(x)
  \end{pmatrix}, \\
  \pressure(\bm{x}, t) &= -\exp(-2 \mu t) \, \left(\cos(x)\sin(y) + \sin(x)\cos(z) + \sin(z)\cos(y)\right)
  + C
  \end{split}
\end{align}
Here, $C = \nicefrac{100}{\gamma}$ is an arbitrary constant.
We use a viscosity of $\mu = 0.01$ and Cauchy boundary conditions.

As a final example of standard flow scenarios, we consider the lid-driven cavity flow which initial conditions are given by a fluid at rest, with $\pressure = \text{?}$, etc.
We consider a domain of size $1 \times 1 \text{?}$ which is surrounded by no-slip walls.
The flow is driven entirely by the upper wall which has a velocity of $v_x = 1$.

Clouds with 2+ AMR Levels (if working?)

Reactive Detonation Waves (maybe with stiff source term and/or fixed bcs)

\section{Conclusion}
\end{document}

### 2019-03-07 writing/paper/paper.tex
Paper: Further copy/pasting, fix biblatex.

@@
 \documentclass[runningheads]{llncs}
-\title{Clouds}
+\title{Cloud Supercomputing}
 \author{$\ldots$}
 \institute{$\ldots$}
+\usepackage[american]{babel}
+\usepackage[autostyle, english = american]{csquotes}
+\usepackage[%
+  % backend=biber,
+  % url=false,
+  % style=alphabetic,
+  % backref=true,
+  % hyperref=true,
+  % maxnames=4,
+  % minnames=3,
+  % maxbibnames=99,
+  % firstinits,
+  % uniquename=init
+  ]{biblatex}
+\DefineBibliographyStrings{english}{%
+  backrefpage = {see p.},
+  backrefpages = {see pp.}
+}
+\addbibresource{../bibliography.bib}
 
@@
 The term $q_0 \QZ$ is the chemical energy with a heat release $q_0$~\cite{helzel2000modified}, the term $gz$ is the geopotential height with the gravity of Earth $g$~\cite{giraldo2008study}.
+We set $\QZZ$ and $q_0$ to zero for scenarios without a reactive component.
 We model the diffusive effects of the flow by the standard stress tensor
@@
 \end{equation}
+The right side of this equation is implemented as a source term.
+
+\todo{Notation? Introduce $T$}For reactive problems, we use the simple reaction model
+\begin{equation}
+  \label{eq:reaction-model}
+  \source[\QZ] = - \frac{1}{\reactionTimescale} \left[T > \reactionTemperature \right]\QZ
+\end{equation}
+where $\reactionTimescale$ is the time scale of the reaction and $\reactionTemperature$ is the critical temperature~\cite{hidalgo2011ader,helzel2000modified}.
+We only consider the case of $\reactionTimescale \geq 10^{-2}$ which corresponds to a non-stiff source.
 
@@
 \section{Methods}
+\todo{Write \aderdg{}/\exahype{} section!}
 Maybe numerics (dg+muscl?), at least ref.
@@
 with probability $\mathbb{P}$ guarantees that we neither refine nor delete all cells.
-This inequality holds for arbitrary distributions under the weak assumption that they have a mean $\mu$ and standard deviation $\sigma$~\cite{wasserman2004all}.
+This inequality holds for arbitrary distributions under the weak assumption that their mean $\mu$ and standard deviation $\sigma$ are finite~\cite{wasserman2004all}.
 
@@
 
+\todo{Constants of fluids?}
 A simple scenario is the Taylor-Green vortex.
-It has an analytical solution in the incompressible limit
-The solution is
+It has an analytical solution in the incompressible limit which is given by
 \begin{align}
@@
     \end{pmatrix}, \\
-  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \nicefrac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C,
+  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \nicefrac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C.
   \end{split}
 \end{align}
-where $C = \nicefrac{100}{\gamma}$ is a constant that governs the speed of sound and thus the Mach number~\cite{dumbser2016high}.
+In this equation, $C = \nicefrac{100}{\gamma}$ is a constant that governs the speed of sound and thus the Mach number~\cite{dumbser2016high}.
 We use a viscosity of $\mu = 0.1$ and Cauchy boundary conditions.
 
-We use the Arnold–Beltrami–Childress (\textsc{abc}) flow as a simple three-dimensional flow~\cite{tavelli2016staggered}.
+We use the Arnold-Beltrami-Childress (\textsc{abc}) flow as a simple three-dimensional flow~\cite{tavelli2016staggered}.
 It also has an exact solution under the assumption of incompressibility
@@
 
-As a final example of standard flow scenarios, we consider the lid-driven cavity flow which initial conditions are given by a fluid at rest, with $\pressure = \text{?}$, etc.
-We consider a domain of size $1 \times 1 \text{?}$ which is surrounded by no-slip walls.
-The flow is driven entirely by the upper wall which has a velocity of $v_x = 1$.
+As a final example of standard flow scenarios, we consider the lid-driven cavity flow which initial conditions are given by a fluid at rest, with $\Qrho = 0, \pressure(\bm{x}) = \nicefrac{100}{\gamma}$.
+
+We consider a domain of size $\SI{\pi}{m} \times \SI{\pi}{\m} \text{?}$ which is surrounded by no-slip walls.
+The flow is driven entirely by the upper wall which has a velocity of $v_x = \SI{1}{\m/s}$.
+\begin{equation}\label{eq:atmosphere-constants}
+    \gamma = 1.4 ,\qquad \Pr =  0.71 ,\qquad R = 287.058 ,\qquad p_0 = 10000, \qquad g = 9.81,
+\end{equation}
+Our atmospheric flow scenarios are described in terms of the potential energy
+\begin{equation}
+  \potT = T \left( \frac{p_0}{p} \right)^{R/c_p},
+\end{equation}
+with the reference pressure $p_o = \SI{10e5}{\Pa}$.
+
+We compute the initial background density and pressure by inserting the assumption of a constant background energy in \cref{eq:hydrostatic-balance}.
+The background atmosphere is then perturbed.
+\todo{What about our weird boundary condition for heat flux and energy?}
+Let
+\begin{equation}
+  \label{eq:radius}
+  r^2 = (x - x_0)^2 + (z - z_0)^2
+\end{equation}
+denote the difference between spatial positions $x,z$ and the center of a bubble $x_c, z_c$.
+For our first scenario, the cosine bubble, we use a pertubation of the form
+\begin{equation}
+  \label{eq:cos-pertubation-alt}
+  \pertubationPotT = 
+    \nicefrac{A}{2} \left( 1 + \cos(\pi r) \right) \left[ r \leq a \right]
+\end{equation}
+\begin{align}
+  \label{eq:cos-pertubation}
+  \pertubationPotT &= \begin{cases}
+    \nicefrac{A}{2} \left[ 1 + \cos(\pi r) \right] & r \leq a, \\
+    0 & r > a,
+    \end{cases}
+\end{align}
+where $A$ denotes the maximal perturbation and $a$ is the size of the bubble.
+We use the constants
+\begin{equation}\label{eq:cosine-bubble}
+  A = 0.5 \quad a = \SI{250}{\m} \quad x_c = \SI{500}{\m} \quad z_c = \SI{350}{\m}.
+\end{equation}
+We use a constant viscosity of $\mu = 0.1$.
+For our second scenario, the cold bubble on top of a warm bubble, we use the pertubation of the form
+\begin{equation}
+  \label{eq:bubbles-pertubation}
+  \pertubationPotT =
+  \begin{cases}
+    A & r \leq a, \\
+    A \exp \left( - \frac{(r-a)^2}{s^2} \right) & r > a,
+    \end{cases}
+\end{equation}
+where $s$ is the decay rate and $r$  is the radius to the center~\pcref{eq:radius}.
+We have two bubbles, with constants
+\begin{equation}
+  \label{eq:bubbles-values}
+\begin{alignedat}{6}
+  & \text{warm:} \qquad && A = 0.5, \quad&& a = \SI{150}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{500}{\m,} \quad&& z_c = \SI{300}{\m},\\
+  & \text{cold:} \qquad && A = -0.15, \quad&& a = \SI{0}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{560}{\m}, \quad&& z_c = \SI{640}{\m}.
+  \end{alignedat}
+\end{equation}
+Similar to~\cite{muller2010adaptive} and to the previous scenario, we use a constant viscosity of $\mu = 0.1$ to regularize the solution.
+
+We start with a coarse mesh that is then subdivided up to two times in an adaptive manner.
+For this we use the criterion of \cref{eq:refinement-criterion} with parameters xxx and xxx.
+We compare this with a simulation obtained by a fully refined grid.
 
 Clouds with 2+ AMR Levels (if working?)
-
 Reactive Detonation Waves (maybe with stiff source term and/or fixed bcs)
+Finally, we consider the radialsymmetric detonation wave of xxx, which uses the coupled advection-reaction equation.
+Its initial conditions are given by xxx.
+We evaluate this scenario both with a viscosity xxx and with zero viscosity.
 
 \section{Conclusion}
+Insert conclusion here.
+
+\printbibliography{}
 \end{document}

### 2019-03-14 writing/paper/paper.tex
Some small changes to paper.

@@
 \title{Cloud Supercomputing}
-\author{$\ldots$}
-\institute{$\ldots$}
+\author{Authors}
+\institute{Institute}
+\usepackage[utf8]{inputenc}
+%\usepackage[T1]{fontenc}
 \usepackage[american]{babel}
@@
 \end{equation}
-which describes the time evolution of variables $\Q$ with respect to a flux $\flux(\Q, \gradQ)$ and a source $\source(\Q)$.
-The vector of conserved quantities is given by
+with vector of conserved quantitites $\Q$, flux $\flux(\Q, \gradQ)$ and source $\source(\Q)$.
+The conserved quantities
 \begin{equation}
@@
 \end{equation}
-where $\Qrho$ is the density, $\Qj$ is the two or three-dimensional momentum, $\QE$ is the energy density and $\QZ$ is the mass fraction of the chemical reactant.
+are the density $\Qrho$, the two or three-dimensional momentum $\Qj$, the energy density $\QE$ and the mass fraction of the chemical reactant $\QZ$.
 The pressure $\pressure$ is given by the equation of state of an ideal reacting gas
@@
 \end{equation}
+and relates to the temperature $T$ by the thermal equation of state
+\begin{equation}
+  \label{eq:temperature}
+  \pressure = \Qrho R T,
+\end{equation}
+where $R$ is the specific gas constant of a fluid.
+
 The term $q_0 \QZ$ is the chemical energy with a heat release $q_0$~\cite{helzel2000modified}, the term $gz$ is the geopotential height with the gravity of Earth $g$~\cite{giraldo2008study}.
@@
   \label{eq:hydrostatic-balance}
-  \pdv{}{z} \backgroundPressure{\left (z \right )} = -g \backgroundRho(z).
+  \pdv{}{z} \backgroundPressure{\left (z \right )} = -g \backgroundRho(z),
 \end{equation}
+i.e.\ a state where the pressure differences are exactly balanced with the gravitational source term.
 The momentum equation is dominated by the background flow in this case.
 This leads to numerical instabilities.
-We avoid this by splitting the pressure $\pressure = \backgroundPressure + \pressure'$ and density $\Qrho = \backgroundRho + \Qrho'$
+To avoid this, we split the pressure $\pressure = \backgroundPressure + \pressure'$ and density $\Qrho = \backgroundRho + \Qrho'$, arriving at the modified equation
 \begin{equation}
@@
 \end{equation}
-The right side of this equation is implemented as a source term.
 
@@
 
-The rest of this paper is organized as follows:
+In the rest of the paper, we make the following contributions:
 \begin{itemize}
@@
 
-We use the \aderdg{}-scheme as proposed in xxx together with a Rusanov-style flux, which is adapted for \pde{}s with diffusive terms.
+We use the \aderdg{}-scheme as proposed in \cite{dumbser2008unified} together with a Rusanov-style flux~\cite{gassner2008discontinuous,fambri2017space} that is adapted for \pde{}s with diffusive terms.
 
@@
 The operator $\Vert \cdot \Vert_1$ denotes the discrete $l_1$ norm in this equation.
-We compute this efficiently with Gaussian quadrature over the collocated quadrature points.
+We compute the integral efficiently with Gaussian quadrature over the collocated quadrature points.
 \newcommand{\mean}{\mu}%
@@
 To resolve this conundrum, we compute the mean and the population standard deviation of the total variation of all cells.
-It is important to note that we use the method of Chan/LeVeque to compute the modes in a parallel and numerical stable manner.
+It is important to note that we use the method of~\cite{chan1982updating} to compute the modes in a parallel and numerical stable manner.
 A cell is then considered to contain significant information if its deviates from the mean more than a given threshold.
@@
 
-We use a muscl-hancock based finite volume limiting as proposed in xxx.
+We use a \muscl{}-hancock based finite volume limiting as proposed in~\cite{dumbser2016simple}.
 Briefly, we first compute a candidate solution with our \aderdg{}-scheme and check whether it is valid.
@@
 \todo{dmp?}
-In case of an invalid solution, we recompute the timestep with a limited \muscl{} finite volume method.
+In case of an invalid solution, we recompute the timestep with a limited \muscl{} finite volume method\todo{Source for the fv method}.
 
@@
 \end{align}
-In this equation, $C = \nicefrac{100}{\gamma}$ is a constant that governs the speed of sound and thus the Mach number~\cite{dumbser2016high}.
+The constant $C = \nicefrac{100}{\gamma}$ governs the speed of sound and thus the Mach number~\cite{dumbser2016high}.
 We use a viscosity of $\mu = 0.1$ and Cauchy boundary conditions.
@@
 
-As a final example of standard flow scenarios, we consider the lid-driven cavity flow which initial conditions are given by a fluid at rest, with $\Qrho = 0, \pressure(\bm{x}) = \nicefrac{100}{\gamma}$.
+As a final example of standard flow scenarios, we consider the lid-driven cavity flow which initial conditions are given by a fluid at rest, with $\Qrho = 1, \pressure(\bm{x}) = \nicefrac{100}{\gamma}$.
 
-We consider a domain of size $\SI{\pi}{m} \times \SI{\pi}{\m} \text{?}$ which is surrounded by no-slip walls.
-The flow is driven entirely by the upper wall which has a velocity of $v_x = \SI{1}{\m/s}$.
-\begin{equation}\label{eq:atmosphere-constants}
-    \gamma = 1.4 ,\qquad \Pr =  0.71 ,\qquad R = 287.058 ,\qquad p_0 = 10000, \qquad g = 9.81,
-\end{equation}
+We consider a domain of size $\SI{2\pi}{m} \times \SI{2\pi}{\m}$ which is surrounded by no-slip walls.
+The flow is driven entirely by the upper wall which has a velocity of $v_x = \SI{1}{\m/\s}$.
+The simulation runs for $\SI{10}{\s}$
+
 Our atmospheric flow scenarios are described in terms of the potential energy
@@
 \end{equation}
-with the reference pressure $p_o = \SI{10e5}{\Pa}$.
+with reference pressure $p_o = \SI{10e5}{\Pa}$~\cite{muller2010adaptive,giraldo2008study}.
+For all remaining scenarions, we use the constants
+\begin{equation}\label{eq:atmosphere-constants}
+    \gamma = 1.4 ,\qquad \Pr =  0.71 ,\qquad R = 287.058 ,\qquad p_0 = 10000, \qquad g = 9.8.
+\end{equation}
 
@@
 We use a constant viscosity of $\mu = 0.1$.
-For our second scenario, the cold bubble on top of a warm bubble, we use the pertubation of the form
+For our second scenario, the cold bubble on top of a warm bubble, we use the pertubations
 \begin{equation}
@@
 Similar to~\cite{muller2010adaptive} and to the previous scenario, we use a constant viscosity of $\mu = 0.1$ to regularize the solution.
+To ensure that the atmosphere stays in hydrostatic balance~\cite{giraldo2008study}, we need to impose the viscous heat flux\todo{Show full bc?}
+\begin{equation}
+  \label{eq:atmosphere-bc}
+  \viscFlux_{\QE} = \kappa \pdv{\overline{T}}{z}% =
+%\kappa \frac{R \overline{\theta} \left(\frac{\overline{p}{\left (z \right )}}{p_{0}}\right)^{\frac{R}{c_{p}}} \frac{d}{d z} \overline{p}{\left (z \right )}}{c_{p} \overline{p}{\left (z \right )}}.
+\end{equation}
 
@@
 
+TODO, Show following results:
+\begin{itemize}
+\item Simple cfd: Taylor Green, ABC, Lid Driven Cavity
+\item Two Bubbles with and without amr
+\item Limited Reactive euler/and maybe ns
+\end{itemize}
+
 \section{Conclusion}
-Insert conclusion here.
+We presented a \muscl{}-limited \aderdg{}-scheme with \amr{} for the reactive Navier-Stokes equations.
+Our implementation is capable of simulating different scenarios:
+\begin{itemize}
+  % Convergence test?
+\item We evaluated our method for standard \textsc{cfd} scenarios and achieved competitive results for all used scenarios.
+  This is true for both two-dimensional scenarios (Taylor-Green vortex and lid-driven cavity) and for the three-dimensional \textsc{abc}-flow.
+\item Furthermore, our method allows us to simulate flows in hydrostatic equilibrium correctly.
+\item We showed that our \amr{}-criterion is able to vastly reduce the number of grid cells while preserving the quality of the results.
+\item Our results of for the reactive detonation waves showed that our implementation is capable of simulating chemical reactions with a limited scheme, at least for a non-stiff source term.
+\end{itemize}
 

### 2019-03-25 writing/paper/paper.tex
Proof reading.

@@
 are the density $\Qrho$, the two or three-dimensional momentum $\Qj$, the energy density $\QE$ and the mass fraction of the chemical reactant $\QZ$.
-The pressure $\pressure$ is given by the equation of state of an ideal reacting gas
+In \cref{eq:equation-set}, the rows are the conservation of mass, the conservation of momentum, the conservation of energy and the continuity equation of the reactant.
+
+The pressure $\pressure$ is given by the equation of state of an ideal reacting gas\todo{Describe gravitation?}
 \begin{equation}
@@
 \end{equation}
-and relates to the temperature $T$ by the thermal equation of state
+The term $q_0 \QZ$ is the chemical energy with a heat release $q_0$~\cite{helzel2000modified}, the term $gz$ is the geopotential height with the gravity of Earth $g$~\cite{giraldo2008study}.
+We set $\QZZ$ or $q_0$ to zero for scenarios without a reactive component.
+The temperature $T$ relates to the pressure by the thermal equation of state
 \begin{equation}
@@
 
-The term $q_0 \QZ$ is the chemical energy with a heat release $q_0$~\cite{helzel2000modified}, the term $gz$ is the geopotential height with the gravity of Earth $g$~\cite{giraldo2008study}.
-We set $\QZZ$ and $q_0$ to zero for scenarios without a reactive component.
-We model the diffusive effects of the flow by the standard stress tensor
+We model the diffusivity of the flow by the stress tensor
 \begin{equation}
@@
 \end{equation}
-with viscosity $\mu$.
+with constant viscosity $\mu$.
+The heat diffusion is governed by the coefficient
+\begin{equation}
+  \label{eq:heat-conduction-coeff}
+  \kappa = \frac{\mu \gamma}{\Pr} \frac{1}{\gamma - 1} R = \frac{\mu c_p}{\Pr},
+\end{equation}
+where the ratio of specific heats $\gamma$, the heat capacity at constant pressure $c_p$ and the Prandtl number $\Pr$ depend on the fluid.
 
-Many realistic, atmospheric flows can be described by a pertubation over a background state that is in hydrostatic equilibrium
+Many realistic atmospheric flows can be described by a pertubation over a background state that is in hydrostatic equilibrium
 \newcommand{\backgroundPressure}{\overline{\pressure}}
@@
 \end{equation}
-i.e.\ a state where the pressure differences are exactly balanced with the gravitational source term.
+i.e.\ a state where the pressure gradient is exactly balanced with the gravitational source term.
 The momentum equation is dominated by the background flow in this case.
 This leads to numerical instabilities.
-To avoid this, we split the pressure $\pressure = \backgroundPressure + \pressure'$ and density $\Qrho = \backgroundRho + \Qrho'$, arriving at the modified equation
+To avoid this, we split the pressure $\pressure = \backgroundPressure + \pressure'$ into a sum of the background pressure $\backgroundPressure(z)$ and pertubation $\pressure'(\bm{x}, t)$.
+We split the density $\Qrho = \backgroundRho + \Qrho'$ in the same manner and arrive at
 \begin{equation}
@@
 \begin{itemize}
-\item Efficient, explicit \aderdg{}-scheme with shared and distributed memory parallelization.
-\item An \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
-\item Evaluation with standard \textsc{cfd} scenarios, atmospheric and reactive flows.
+\item We present an efficient, explicit \aderdg{}-scheme with shared and distributed memory parallelization for our equation set.
+\item We show an \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
+\item We evaluate our implementation with standard \textsc{cfd} scenarios, atmospheric and reactive flows.
 \end{itemize}
@@
 \section{Methods}
-\todo{Write \aderdg{}/\exahype{} section!}
+\todo{Write \aderdg{}/\exahype{} section! Riemann solver + timestep}
 Maybe numerics (dg+muscl?), at least ref.
@@
   \pressure(\bm{x}, t) &= -\exp(-2 \mu t) \, \left(\cos(x)\sin(y) + \sin(x)\cos(z) + \sin(z)\cos(y)\right)
-  + C
+  + C.
   \end{split}
@@
 
-As a final example of standard flow scenarios, we consider the lid-driven cavity flow which initial conditions are given by a fluid at rest, with $\Qrho = 1, \pressure(\bm{x}) = \nicefrac{100}{\gamma}$.
+As a final example of standard flow scenarios, we consider the lid-driven cavity flow where the fluid is at rest initially, with $\Qrho = 1$ and $ \pressure(\bm{x}) = \nicefrac{100}{\gamma}$.
 
@@
 \end{equation}
-with reference pressure $p_o = \SI{10e5}{\Pa}$~\cite{muller2010adaptive,giraldo2008study}.
+with reference pressure $p_o$~\cite{muller2010adaptive,giraldo2008study}.
 For all remaining scenarions, we use the constants
 \begin{equation}\label{eq:atmosphere-constants}
-    \gamma = 1.4 ,\qquad \Pr =  0.71 ,\qquad R = 287.058 ,\qquad p_0 = 10000, \qquad g = 9.8.
+    \gamma = 1.4 ,\qquad \Pr =  0.71 ,\qquad R = 287.058 ,\qquad p_0 = \SI{10e5}{\Pa}, \qquad g = 9.8.
 \end{equation}
@@
   \label{eq:atmosphere-bc}
-  \viscFlux_{\QE} = \kappa \pdv{\overline{T}}{z}% =
+  \viscFlux_{\QE} = \kappa \pdv{\overline{T}}{z}.% =
 %\kappa \frac{R \overline{\theta} \left(\frac{\overline{p}{\left (z \right )}}{p_{0}}\right)^{\frac{R}{c_{p}}} \frac{d}{d z} \overline{p}{\left (z \right )}}{c_{p} \overline{p}{\left (z \right )}}.

### 2019-04-02 writing/paper/paper.tex
Added comments

@@
 }%
-We solve the reactive compressible Navier-Stokes equations in the conservative form% \pcref{eq:conservation-law-gradient}
+We \todo{LR: General introduction is missing.
+Where do we see our paper, what has been done before?
+Here we should also introduce and describe the ExaHyPE-Engine as base of the paper} solve the reactive compressible Navier-Stokes equations in the conservative form% \pcref{eq:conservation-law-gradient}
 \begin{equation}
@@
 \end{equation}
-are the density $\Qrho$, the two or three-dimensional momentum $\Qj$, the energy density $\QE$ and the mass fraction of the chemical reactant $\QZ$.
+are the density $\Qrho$, the two or three-dimensional momentum $\Qj$, the energy density $\QE$ and the mass fraction of the chemical reactant $\QZ$ \todo{TODO: Reference to Dumbser is missing -> What are we doing differently?}.
 In \cref{eq:equation-set}, the rows are the conservation of mass, the conservation of momentum, the conservation of energy and the continuity equation of the reactant.
@@
 Maybe numerics (dg+muscl?), at least ref.
-Exahype?!
+Exahype?! \todo{LR: Die Engine würde ich vor der Formel beschreibung machen: Also erst was macht die Engine, dann wie haben wir sie angewandt.}
 
@@
 \end{equation}
-with probability $\mathbb{P}$ guarantees that we neither refine nor delete all cells.
+with probability $\mathbb{P}$ guarantees that we neither refine nor delete all cells. \todo{LR: Was gibt es an compressible NS mit dynamic AMR, wie unterscheiden wir uns im Refinement Kriterium?}
 This inequality holds for arbitrary distributions under the weak assumption that their mean $\mu$ and standard deviation $\sigma$ are finite~\cite{wasserman2004all}.
@@
 A solution is considered to be invalid if it is a non-finite floating point number or if it is unphysical, i.e.\ if the pressure or density are not positive.
-\todo{dmp?}
+\todo{dmp? LR: Just mention .. if the pressure or density are not positive. Simultenously we validate against the discrete maximum principle, defined by Dumser et al ref}
 In case of an invalid solution, we recompute the timestep with a limited \muscl{} finite volume method\todo{Source for the fv method}.

### 2019-04-02 writing/paper/paper.tex
added exahype introduction

@@
 \section{Introduction}
+\subsection{The ExaHyPE-Engine}
+The ExaHyPE project (www.exahype.eu) develops an engine to solve arbitrary hyperbolic partial differential equations (PDEs) on expected exascale high performance computing architectures.
+A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well posed Cauchy problem for a system of hyperbolic PDEs.
+The actual numerical scheme, domain decomposition and parallelisation techniques are left as black box to the user.
+Internally the ExaHyPE-Engine implements a high order ADER-DG scheme on Legendre basis nodes \todo{LR: ref}.
+The mesh is incorporated from the the Peano framework\todo{LR: ref}, which is based on spacetrees for Cartesian meshes.
+The framework provides a distributed (MPI) and shared memory (Intel TBB) parallelisation tailored to dynamic adaptive mesh refinement (AMR) \ref{LR: ref}.
+As the ADER-DG scheme is highly volatile as soon as shocks develop we additionally provide \textit{a posteriori} finite volume limiting, recently developed by Dumbser et al. \todo{LR: ref}.
+We want to emphasize the recent work by D.E. Charrier et al. \todo{LR: ref: Stop talking to me} which describes our communication avoiding implementation of the whole numerical scheme.
+
 \newcommand{\diffCoeff}{\varepsilon}

### 2019-04-03 writing/paper/paper.tex
Add some references, remove some typos.

--- 2019-04-02 writing/paper/paper.tex
@@
 \section{Introduction}
+\subsection{The ExaHyPE-Engine}
+The ExaHyPE project (\url{www.exahype.eu}) develops an engine to solve arbitrary hyperbolic partial differential equations (\pde{}s) on expected exascale high performance computing architectures.
+A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well posed Cauchy problem for a system of hyperbolic \pde{}s.
+The actual numerical scheme, domain decomposition and parallelisation techniques are left as black box to the user.
+Internally the ExaHyPE-Engine implements a high order ADER-DG scheme on Legendre basis nodes \todo{LR: ref}.
+The mesh is incorporated from the the Peano framework~\cite{weinzierl2011}, which is based on spacetrees for Cartesian meshes.
+The framework provides a distributed (\mpi{}) and shared memory (Intel \textsc{tbb}) parallelization tailored to dynamic adaptive mesh refinement (\amr{})~\todo{LR: ref}.
+As the ADER-DG scheme is highly volatile as soon as shocks develop we additionally provide \textit{a posteriori} finite volume limiting, recently developed by \citeauthor{dumbser2016simple} in~\cite{dumbser2016simple}.
+We want to emphasize the recent work~\cite{charrier2018stop} by \citeauthor{charrier2018stop} which describes our communication-avoiding implementation of the whole numerical scheme.
 \newcommand{\diffCoeff}{\varepsilon}

### 2019-04-03 writing/paper/paper.tex
Added some comments. Fixed some typos

@@
 The ExaHyPE project (\url{www.exahype.eu}) develops an engine to solve arbitrary hyperbolic partial differential equations (\pde{}s) on expected exascale high performance computing architectures.
-A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well posed Cauchy problem for a system of hyperbolic \pde{}s.
+A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well posed Cauchy problem for a system of hyperbolic \pde{}s of first order.
 The actual numerical scheme, domain decomposition and parallelisation techniques are left as black box to the user.
-Internally the ExaHyPE-Engine implements a high order ADER-DG scheme on Legendre basis nodes \todo{LR: ref}.
-The mesh is incorporated from the the Peano framework~\cite{weinzierl2011}, which is based on spacetrees for Cartesian meshes.
+Internally the ExaHyPE-Engine implements a high order ADER-DG scheme on Legendre basis nodes.
+The mesh is incorporated from the Peano framework~\cite{weinzierl2011}, which is based on spacetrees for Cartesian meshes.
 The framework provides a distributed (\mpi{}) and shared memory (Intel \textsc{tbb}) parallelization tailored to dynamic adaptive mesh refinement (\amr{})~\todo{LR: ref}.
@@
 \end{equation}
-are the density $\Qrho$, the two or three-dimensional momentum $\Qj$, the energy density $\QE$ and the mass fraction of the chemical reactant $\QZ$ \todo{TODO: Reference to Dumbser is missing -> What are we doing differently?}.
+are the density $\Qrho$, the two or three-dimensional momentum $\Qj$, the energy density $\QE$ and the mass fraction of the chemical reactant $\QZ$.
 In \cref{eq:equation-set}, the rows are the conservation of mass, the conservation of momentum, the conservation of energy and the continuity equation of the reactant.
@@
 \begin{itemize}
-\item We present an efficient, explicit \aderdg{}-scheme with shared and distributed memory parallelization for our equation set.
+\item We present an efficient, explicit \aderdg{}-scheme with shared and distributed memory parallelization for our equation set \todo{LR: das ist kein Beitrag von uns}.
 \item We show an \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.

### 2019-04-03 writing/paper/paper.tex
Added/Removed todos. Added introduction for AMR criterion

@@
 \section{Methods}
-\todo{Write \aderdg{}/\exahype{} section! Riemann solver + timestep}
+\todo{Write \aderdg{}/\exahype{} section! Riemann solver + timestep. LR: Was sollen wir da deiner Meinung nach noch erwähnen?}
 Maybe numerics (dg+muscl?), at least ref.
-Exahype?! \todo{LR: Die Engine würde ich vor der Formel beschreibung machen: Also erst was macht die Engine, dann wie haben wir sie angewandt.}
+Exahype?! 
+We use the \aderdg{}-scheme as proposed in \cite{dumbser2008unified} together with a Rusanov-style flux~\cite{gassner2008discontinuous,fambri2017space} that is adapted for \pde{}s with diffusive terms.
+\todo{LR: Hier würde ich noch ein paar einleitende Worte hinzufügen}
 
-We use the \aderdg{}-scheme as proposed in \cite{dumbser2008unified} together with a Rusanov-style flux~\cite{gassner2008discontinuous,fambri2017space} that is adapted for \pde{}s with diffusive terms.
-
+Rules for dynamic AMR can be stated by the user with element wise checks against a custom defined set of criteria.
+We use an element local error estimate based on the total variation of the numerical solution.
 Let $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ be a function that maps the discrete solution at a point $\bm{x}$ to an arbitrary indicator variable.

### 2019-04-05 writing/paper/paper.tex
Fix some small issues.

@@
 \subsection{The ExaHyPE-Engine}
-The ExaHyPE project (\url{www.exahype.eu}) develops an engine to solve arbitrary hyperbolic partial differential equations (\pde{}s) on expected exascale high performance computing architectures.
+The \exahype{} project (\url{www.exahype.eu}) develops an engine to solve arbitrary hyperbolic partial differential equations (\pde{}s) on upcoming exascale high performance computing architectures.
 A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well posed Cauchy problem for a system of hyperbolic \pde{}s of first order.
 The actual numerical scheme, domain decomposition and parallelisation techniques are left as black box to the user.
-Internally the ExaHyPE-Engine implements a high order ADER-DG scheme on Legendre basis nodes.
+Internally the \exahypeengine{} implements a high order \aderdg{} scheme on Legendre basis nodes.
 The mesh is incorporated from the Peano framework~\cite{weinzierl2011}, which is based on spacetrees for Cartesian meshes.
@@
 We want to emphasize the recent work~\cite{charrier2018stop} by \citeauthor{charrier2018stop} which describes our communication-avoiding implementation of the whole numerical scheme.
-\newcommand{\diffCoeff}{\varepsilon}
+\newcommand{\diffCoeff}{\varepsilon}%
 \newcommand{\hyperFluxDef}{
@@
   \end{pmatrix}
-}
+}%
 \newcommand{\viscFluxDef}{
@@
 
-The pressure $\pressure$ is given by the equation of state of an ideal reacting gas\todo{Describe gravitation?}
+The pressure $\pressure$ is given by the equation of state of an ideal reacting gas
 \begin{equation}
@@
 \end{equation}
-i.e.\ a state where the pressure gradient is exactly balanced with the gravitational source term.
+i.e.\ a state, where the pressure gradient is exactly in balance with the gravitational source term.
 The momentum equation is dominated by the background flow in this case.
@@
 \begin{itemize}
-\item We present an efficient, explicit \aderdg{}-scheme with shared and distributed memory parallelization for our equation set \todo{LR: das ist kein Beitrag von uns}.
+\item
+  We utilize an efficient and  explicit \aderdg{}-scheme with shared and distributed memory parallelization for our equation set.
 \item We show an \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
@@
 \section{Methods}
-\todo{Write \aderdg{}/\exahype{} section! Riemann solver + timestep. LR: Was sollen wir da deiner Meinung nach noch erwähnen?}
+\todo{Write \aderdg{}/\exahype{} section! Riemann solver + timestep. LR: Was sollen wir da deiner Meinung nach noch erwähnen?
+
+LK: CFL Condition ist wictig, wg.\ skalierung, Riemann solver weil wir eben nicht mixed-elements machen und keinen gradienten speichern müssen. Außerdem mehr oder weniger general purpose flux.
+}
 Maybe numerics (dg+muscl?), at least ref.
@@
 
-Rules for dynamic AMR can be stated by the user with element wise checks against a custom defined set of criteria.
+Rules for dynamic \amr{} can be stated by the user with element wise checks against a custom defined set of criteria.
 We use an element local error estimate based on the total variation of the numerical solution.
@@
 The operator $\Vert \cdot \Vert_1$ denotes the discrete $l_1$ norm in this equation.
-We compute the integral efficiently with Gaussian quadrature over the collocated quadrature points.
+We compute the integral efficiently with Gaussian quadrature over the collocated quadrature points.\todo{If using muscl, add sentence about finite differences estimate}
 \newcommand{\mean}{\mu}%
@@
   \begin{cases}
-    \text{refine} & \text{if } \tv(\Q) \geq \mu + \Trefine \sigma \\
-    \text{delete} & \text{if } \tv(\Q) < \mu + \Tdelete \sigma \\
+    \text{refine} & \text{if } \tv(\Q) \geq \mu + \Trefine \sigma, \\
+    \text{delete} & \text{if } \tv(\Q) < \mu + \Tdelete \sigma, \\
     \text{keep} & \text{otherwise}.

### 2019-04-08 writing/paper/paper.tex
Fix small errors.
Remove reactive part of equations.

@@
     \Qv  \otimes \Qj + \bm{I} \pressure  \\
-    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure) \\
-    \Qj \QZZ
+    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure)
   \end{pmatrix}
@@
      \stressT (\Q, \gradQ)  \\
-     \Qv \cdot \stressT (\Q, \gradQ) - \kappa \gradient{T}\\
-     0\\
+     \Qv \cdot \stressT (\Q, \gradQ) - \kappa \gradient{T}
    \end{pmatrix}
@@
 Where do we see our paper, what has been done before?
-Here we should also introduce and describe the ExaHyPE-Engine as base of the paper} solve the reactive compressible Navier-Stokes equations in the conservative form% \pcref{eq:conservation-law-gradient}
+Here we should also introduce and describe the ExaHyPE-Engine as base of the paper} solve the compressible Navier-Stokes equations in the conservative form% \pcref{eq:conservation-law-gradient}
 \begin{equation}
@@
     \Qj\\
-    \QE\\
-    \QZ
+    \QE
     \end{pmatrix}}_{\Q}
@@
     \source[\Qj]\\
-    \source[\QE]\\
-    \source[\QZ]
+    \source[\QE]
     \end{pmatrix}}_{\source(\Q, \bm{x}, t)}
@@
 \end{equation}
-are the density $\Qrho$, the two or three-dimensional momentum $\Qj$, the energy density $\QE$ and the mass fraction of the chemical reactant $\QZ$.
-In \cref{eq:equation-set}, the rows are the conservation of mass, the conservation of momentum, the conservation of energy and the continuity equation of the reactant.
+are the density $\Qrho$, the two or three-dimensional momentum $\Qj$, the energy density $\QE$.
+In \cref{eq:equation-set}, the rows are the conservation of mass, the conservation of momentum, the conservation of energy.
 
-The pressure $\pressure$ is given by the equation of state of an ideal reacting gas
+The pressure $\pressure$ is given by the equation of state of an ideal gas
 \begin{equation}
   \label{eq:eos}
-  \pressure = (\gamma - 1) \left(\QE - \frac{1}{2} \left(\Qv \cdot \Qj \right)  - q_0 \QZ - gz \right).
+  \pressure = (\gamma - 1) \left(\QE - \frac{1}{2} \left(\Qv \cdot \Qj \right) - gz \right).
 \end{equation}
-The term $q_0 \QZ$ is the chemical energy with a heat release $q_0$~\cite{helzel2000modified}, the term $gz$ is the geopotential height with the gravity of Earth $g$~\cite{giraldo2008study}.
-We set $\QZZ$ or $q_0$ to zero for scenarios without a reactive component.
+The term $gz$ is the geopotential height with the gravity of Earth $g$~\cite{giraldo2008study}.
 The temperature $T$ relates to the pressure by the thermal equation of state
@@
 
-\todo{Notation? Introduce $T$}For reactive problems, we use the simple reaction model
-\begin{equation}
-  \label{eq:reaction-model}
-  \source[\QZ] = - \frac{1}{\reactionTimescale} \left[T > \reactionTemperature \right]\QZ
-\end{equation}
-where $\reactionTimescale$ is the time scale of the reaction and $\reactionTemperature$ is the critical temperature~\cite{hidalgo2011ader,helzel2000modified}.
-We only consider the case of $\reactionTimescale \geq 10^{-2}$ which corresponds to a non-stiff source.
-
 In the rest of the paper, we make the following contributions:
@@
 \item We show an \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
-\item We evaluate our implementation with standard \textsc{cfd} scenarios, atmospheric and reactive flows.
+\item We evaluate our implementation with standard \textsc{cfd} scenarios and atmospheric.
 \end{itemize}
@@
 \section{Results}
-We use a diverse mix of benchmarking scenarios that consist of standard \textsc{cfd} scenarios, and atmospheric and reactive flows.
+We use a diverse mix of benchmarking scenarios that consist of standard \textsc{cfd} scenarios, and atmospheric flows.
 
@@
 \begin{equation}\label{eq:atmosphere-constants}
-    \gamma = 1.4 ,\qquad \Pr =  0.71 ,\qquad R = 287.058 ,\qquad p_0 = \SI{10e5}{\Pa}, \qquad g = 9.8.
+    \gamma = 1.4 ,\qquad \Pr =  0.71 ,\qquad R = 287.058 ,\qquad p_0 = \SI{10e5}{\Pa}, \qquad g = \SI{9.8}{m/s^2}.
 \end{equation}
@@
 \begin{equation}\label{eq:cosine-bubble}
-  A = 0.5 \quad a = \SI{250}{\m} \quad x_c = \SI{500}{\m} \quad z_c = \SI{350}{\m}.
+  A = \SI{0.5}{\K} \quad a = \SI{250}{\m} \quad x_c = \SI{500}{\m} \quad z_c = \SI{350}{\m}.
 \end{equation}
@@
 \begin{alignedat}{6}
-  & \text{warm:} \qquad && A = 0.5, \quad&& a = \SI{150}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{500}{\m,} \quad&& z_c = \SI{300}{\m},\\
-  & \text{cold:} \qquad && A = -0.15, \quad&& a = \SI{0}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{560}{\m}, \quad&& z_c = \SI{640}{\m}.
+  & \text{warm:} \qquad && A = \SI{0.5}{\K}, \quad&& a = \SI{150}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{500}{\m,} \quad&& z_c = \SI{300}{\m},\\
+  & \text{cold:} \qquad && A = \SI{-0.15}{\K}, \quad&& a = \SI{0}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{560}{\m}, \quad&& z_c = \SI{640}{\m}.
   \end{alignedat}
@@
 Clouds with 2+ AMR Levels (if working?)
-Reactive Detonation Waves (maybe with stiff source term and/or fixed bcs)
-Finally, we consider the radialsymmetric detonation wave of xxx, which uses the coupled advection-reaction equation.
-Its initial conditions are given by xxx.
 We evaluate this scenario both with a viscosity xxx and with zero viscosity.
@@
 \item Two Bubbles with and without amr
-\item Limited Reactive euler/and maybe ns
 \end{itemize}
@@
 \section{Conclusion}
-We presented a \muscl{}-limited \aderdg{}-scheme with \amr{} for the reactive Navier-Stokes equations.
+We presented a \muscl{}-limited \aderdg{}-scheme with \amr{} for the Navier-Stokes equations.
 Our implementation is capable of simulating different scenarios:
@@
 \item We showed that our \amr{}-criterion is able to vastly reduce the number of grid cells while preserving the quality of the results.
-\item Our results of for the reactive detonation waves showed that our implementation is capable of simulating chemical reactions with a limited scheme, at least for a non-stiff source term.
 \end{itemize}

### 2019-04-08 writing/paper/paper.tex
Fix typos & other errors

@@
 A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well posed Cauchy problem for a system of hyperbolic \pde{}s of first order.
-The actual numerical scheme, domain decomposition and parallelisation techniques are left as black box to the user.
+The actual numerical scheme, domain decomposition and parallelisation techniques are left as a black box to the user.
 Internally the \exahypeengine{} implements a high order \aderdg{} scheme on Legendre basis nodes.
@@
 The framework provides a distributed (\mpi{}) and shared memory (Intel \textsc{tbb}) parallelization tailored to dynamic adaptive mesh refinement (\amr{})~\todo{LR: ref}.
-As the ADER-DG scheme is highly volatile as soon as shocks develop we additionally provide \textit{a posteriori} finite volume limiting, recently developed by \citeauthor{dumbser2016simple} in~\cite{dumbser2016simple}.
-We want to emphasize the recent work~\cite{charrier2018stop} by \citeauthor{charrier2018stop} which describes our communication-avoiding implementation of the whole numerical scheme.
+As the ADER-DG scheme is highly volatile as soon as shocks develop, we additionally provide \textit{a posteriori} finite volume limiting, recently\todo{Is 2016 recently?
+Originally developed in this paper, or just this special version?} developed by \citeauthor{dumbser2016simple} in~\cite{dumbser2016simple}.
+We want to emphasize the recent work~\cite{charrier2018stop} by \citeauthor{charrier2018stop}, which describes our communication-avoiding implementation of the whole numerical scheme.
 \newcommand{\diffCoeff}{\varepsilon}%
@@
 \end{equation}
-are the density $\Qrho$, the two or three-dimensional momentum $\Qj$, the energy density $\QE$.
-In \cref{eq:equation-set}, the rows are the conservation of mass, the conservation of momentum, the conservation of energy.
+are the density $\Qrho$, the two or three-dimensional momentum $\Qj$ and the energy density $\QE$.
+The rows of \cref{eq:equation-set} are the conservation of mass, the conservation of momentum and the conservation of energy.
 
@@
 
-We model the diffusivity of the flow by the stress tensor
+We model the diffusivity by the stress tensor
 \begin{equation}
@@
 The momentum equation is dominated by the background flow in this case.
-This leads to numerical instabilities.
+This can lead to numerical instabilities.
 To avoid this, we split the pressure $\pressure = \backgroundPressure + \pressure'$ into a sum of the background pressure $\backgroundPressure(z)$ and pertubation $\pressure'(\bm{x}, t)$.
@@
 \item We show an \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
-\item We evaluate our implementation with standard \textsc{cfd} scenarios and atmospheric.
+\item We evaluate our implementation with standard \textsc{cfd} scenarios and atmospheric flows.
 \end{itemize}
@@
 
-Rules for dynamic \amr{} can be stated by the user with element wise checks against a custom defined set of criteria.
+The user can state dynamic \amr{} rules by supplying custom criteria that are evaluated pointwise.
 We use an element local error estimate based on the total variation of the numerical solution. 
@@
 \section{Results}
-We use a diverse mix of benchmarking scenarios that consist of standard \textsc{cfd} scenarios, and atmospheric flows.
+We use a diverse mix of benchmarking scenarios that consist of standard \textsc{cfd} scenarios and atmospheric flows.
 
@@
 with reference pressure $p_o$~\cite{muller2010adaptive,giraldo2008study}.
-For all remaining scenarions, we use the constants
+We use the constants
 \begin{equation}\label{eq:atmosphere-constants}
-    \gamma = 1.4 ,\qquad \Pr =  0.71 ,\qquad R = 287.058 ,\qquad p_0 = \SI{10e5}{\Pa}, \qquad g = \SI{9.8}{m/s^2}.
+    \gamma = 1.4 ,\qquad \Pr =  0.71 ,\qquad R = 287.058 ,\qquad p_0 = \SI{10e5}{\Pa}, \qquad g = \SI{9.8}{m/s^2},
 \end{equation}
+for all remaining scenarios.
 

### 2019-04-11 writing/paper/paper.tex
Changed intro

@@
 \subsection{The ExaHyPE-Engine}
-The \exahype{} project (\url{www.exahype.eu}) develops an engine to solve arbitrary hyperbolic partial differential equations (\pde{}s) on upcoming exascale high performance computing architectures.
+The \exahype{} project (\url{www.exahype.eu}) develops an engine to solve arbitrary hyperbolic partial differential equations (\pde{}s).
 A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well posed Cauchy problem for a system of hyperbolic \pde{}s of first order.
-The actual numerical scheme, domain decomposition and parallelisation techniques are left as a black box to the user.
-Internally the \exahypeengine{} implements a high order \aderdg{} scheme on Legendre basis nodes.
-The mesh is incorporated from the Peano framework~\cite{weinzierl2011}, which is based on spacetrees for Cartesian meshes.
-The framework provides a distributed (\mpi{}) and shared memory (Intel \textsc{tbb}) parallelization tailored to dynamic adaptive mesh refinement (\amr{})~\todo{LR: ref}.
-As the ADER-DG scheme is highly volatile as soon as shocks develop, we additionally provide \textit{a posteriori} finite volume limiting, recently\todo{Is 2016 recently?
-Originally developed in this paper, or just this special version?} developed by \citeauthor{dumbser2016simple} in~\cite{dumbser2016simple}.
-We want to emphasize the recent work~\cite{charrier2018stop} by \citeauthor{charrier2018stop}, which describes our communication-avoiding implementation of the whole numerical scheme.
+The underlying ADER-DG method, parallelisation techniques and dynamic adaptive mesh refinement are available for simulation while the implementations are left as a black box to the user.
+An introduction to the communication-avoiding implementation of the whole numerical scheme can be found in the recent work~\cite{charrier2018stop} by \citeauthor{charrier2018stop}.
+In this paper we extended this generic approach for hyperbolic \pde{}s by parabolic terms.
+We base this extension on the work of \citeauthor{gassner2008discontinuous} \cite{gassner2008discontinuous}, which has already been applied to the ADER-DG method in \cite{dumbser2010arbitrary}.
+%Including these terms gives users the option to solve arbitrary parabolic \pde{}s \todo{LR: stimmt das ?}.
+We want to emphasize that with this extension we add the option to limit the numerical scheme \todo{LR: ref Ja/Nein?} with viscosity terms.
+This will exploited in this paper in a series of scenarios for the compressible Navier-Stokes equations which implicitly include viscosity as part of the equation.
+
 \newcommand{\diffCoeff}{\varepsilon}%
@@
 }%
-We \todo{LR: General introduction is missing.
-Where do we see our paper, what has been done before?
-Here we should also introduce and describe the ExaHyPE-Engine as base of the paper} solve the compressible Navier-Stokes equations in the conservative form% \pcref{eq:conservation-law-gradient}
+The compressible Navier-Stokes equations in the conservative form are defined as% \pcref{eq:conservation-law-gradient}
 \begin{equation}

### 2019-04-11 writing/paper/paper.tex
Update introduction.

@@
 \title{Cloud Supercomputing}
-\author{Authors}
-\institute{Institute}
+\author{Lukas Krenz\inst{1} \and{} Leonhard Rannabauer\inst{1} \and{} Michael Bader\inst{1}}
+\institute{Technical University of Munich}
 \usepackage[utf8]{inputenc}
@@
 \section{Introduction}
-\subsection{The ExaHyPE-Engine}
-The \exahype{} project (\url{www.exahype.eu}) develops an engine to solve arbitrary hyperbolic partial differential equations (\pde{}s).
+In this paper we use the \aderdg{} method of~\cite{dumbser2008unified} to simulate various computational fluid dynamics (\textsc{cfd}) scenarios with a focus on hydrostatic flows\todo{LK: Heißt das so?}.
+To include viscosity, we use the numerical flux of \citeauthor{gassner2008discontinuous}~\cite{gassner2008discontinuous} to include the parabolic terms of the compressible Navier-Stokes equations.
+This flux has already been applied to the \aderdg{} method in~\cite{dumbser2010arbitrary}.
+\todo{Einordnung, Kontext zu giraldo, etc$\ldots$}
+
+We utilize the \exahypeengine{} (\url{www.exahype.eu}) which is an engine that can solve arbitrary hyperbolic partial differential equations.
 A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well posed Cauchy problem for a system of hyperbolic \pde{}s of first order.
-The underlying ADER-DG method, parallelisation techniques and dynamic adaptive mesh refinement are available for simulation while the implementations are left as a black box to the user.
+The underlying \aderdg{} method, parallelization techniques and dynamic adaptive mesh refinement are available for simulations while the implementations are left as a black box to the user.
 An introduction to the communication-avoiding implementation of the whole numerical scheme can be found in the recent work~\cite{charrier2018stop} by \citeauthor{charrier2018stop}.
-In this paper we extended this generic approach for hyperbolic \pde{}s by parabolic terms.
-We base this extension on the work of \citeauthor{gassner2008discontinuous} \cite{gassner2008discontinuous}, which has already been applied to the ADER-DG method in \cite{dumbser2010arbitrary}.
-%Including these terms gives users the option to solve arbitrary parabolic \pde{}s \todo{LR: stimmt das ?}.
-We want to emphasize that with this extension we add the option to limit the numerical scheme \todo{LR: ref Ja/Nein?} with viscosity terms.
-This will exploited in this paper in a series of scenarios for the compressible Navier-Stokes equations which implicitly include viscosity as part of the equation.
 
+We make the following contributions:
+\begin{itemize}%
+\item We extend the \exahypeengine{} to allow diffusive terms following the aforementioned numerical scheme.
+\item We use this to provide an implementation of the compressible Navier-Stokes equations.
+\item We show an \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
+\item We evaluate our implementation with standard \textsc{cfd} scenarios and atmospheric flows.
+\end{itemize}
+
+\section{Equation Set}
 \newcommand{\diffCoeff}{\varepsilon}%
@@
 \end{equation}
-with vector of conserved quantitites $\Q$, flux $\flux(\Q, \gradQ)$ and source $\source(\Q)$.
+with vector of conserved quantities $\Q$, flux $\flux(\Q, \gradQ)$ and source $\source(\Q)$.
 The conserved quantities
@@
 
-Many realistic atmospheric flows can be described by a pertubation over a background state that is in hydrostatic equilibrium
+Many realistic atmospheric flows can be described by a perturbation over a background state that is in hydrostatic equilibrium
 \newcommand{\backgroundPressure}{\overline{\pressure}}
@@
 This can lead to numerical instabilities.
-To avoid this, we split the pressure $\pressure = \backgroundPressure + \pressure'$ into a sum of the background pressure $\backgroundPressure(z)$ and pertubation $\pressure'(\bm{x}, t)$.
+To avoid this, we split the pressure $\pressure = \backgroundPressure + \pressure'$ into a sum of the background pressure $\backgroundPressure(z)$ and perturbation $\pressure'(\bm{x}, t)$.
 We split the density $\Qrho = \backgroundRho + \Qrho'$ in the same manner and arrive at
@@
 \end{equation}
+\section{Numerics}
 
-In the rest of the paper, we make the following contributions:
-\begin{itemize}
-\item
-  We utilize an efficient and  explicit \aderdg{}-scheme with shared and distributed memory parallelization for our equation set.
-\item We show an \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
-\item We evaluate our implementation with standard \textsc{cfd} scenarios and atmospheric flows.
-\end{itemize}
+\todo{LR: Hier würde ich noch ein paar einleitende Worte hinzufügen}
+\todo{LK: CFL? Riemannsolver (no gradients)}
+We use the \aderdg{}-scheme as proposed in \cite{dumbser2008unified} together with a Rusanov-style flux~\cite{gassner2008discontinuous,fambri2017space} that is adapted for \pde{}s with diffusive terms.
+In addition, we use a \muscl{} finite volume method with the same flux and the xxx \todo{LK: Which one is best? Cite.} limiter.
 
-\section{Methods}
-\todo{Write \aderdg{}/\exahype{} section! Riemann solver + timestep. LR: Was sollen wir da deiner Meinung nach noch erwähnen?
-
-LK: CFL Condition ist wictig, wg.\ skalierung, Riemann solver weil wir eben nicht mixed-elements machen und keinen gradienten speichern müssen. Außerdem mehr oder weniger general purpose flux.
-}
-Maybe numerics (dg+muscl?), at least ref.
-Exahype?! 
-We use the \aderdg{}-scheme as proposed in \cite{dumbser2008unified} together with a Rusanov-style flux~\cite{gassner2008discontinuous,fambri2017space} that is adapted for \pde{}s with diffusive terms.
-\todo{LR: Hier würde ich noch ein paar einleitende Worte hinzufügen}
-
-The user can state dynamic \amr{} rules by supplying custom criteria that are evaluated pointwise.
+The user can state dynamic \amr{} rules by supplying custom criteria that are evaluated point-wise.
 We use an element local error estimate based on the total variation of the numerical solution. 
@@
 The operator $\Vert \cdot \Vert_1$ denotes the discrete $l_1$ norm in this equation.
-We compute the integral efficiently with Gaussian quadrature over the collocated quadrature points.\todo{If using muscl, add sentence about finite differences estimate}
+We compute the integral efficiently with Gaussian quadrature over the collocated quadrature points.
+\todo{LK: If using limiting, add sentence about tv computation for fv}
 \newcommand{\mean}{\mu}%
@@
 \end{equation}
-with probability $\mathbb{P}$ guarantees that we neither refine nor delete all cells. \todo{LR: Was gibt es an compressible NS mit dynamic AMR, wie unterscheiden wir uns im Refinement Kriterium?}
+with probability $\mathbb{P}$ guarantees that we neither refine nor delete all cells.
+\todo{LR: Was gibt es an compressible NS mit dynamic AMR, wie unterscheiden wir uns im Refinement Kriterium?}
 This inequality holds for arbitrary distributions under the weak assumption that their mean $\mu$ and standard deviation $\sigma$ are finite~\cite{wasserman2004all}.
 
-We use a \muscl{}-hancock based finite volume limiting as proposed in~\cite{dumbser2016simple}.
+We use a \muscl{} based finite volume limiting as proposed in~\cite{dumbser2016simple}.
 Briefly, we first compute a candidate solution with our \aderdg{}-scheme and check whether it is valid.
 A solution is considered to be invalid if it is a non-finite floating point number or if it is unphysical, i.e.\ if the pressure or density are not positive.
-\todo{dmp? LR: Just mention .. if the pressure or density are not positive. Simultenously we validate against the discrete maximum principle, defined by Dumser et al ref}
-In case of an invalid solution, we recompute the timestep with a limited \muscl{} finite volume method\todo{Source for the fv method}.
+\todo{LK: Mention dmp if using, mention tv-indicator for limiting if using}
+In case of an invalid solution, we recompute the timestep with a our \muscl{} finite volume method.\todo{Source for the fv method}
 
@@
 
-\todo{Constants of fluids?}
+\todo{LK: Constants of fluids?}
 A simple scenario is the Taylor-Green vortex.
@@
 \end{align}
-The constant $C = \nicefrac{100}{\gamma}$ governs the speed of sound and thus the Mach number~\cite{dumbser2016high}.
-We use a viscosity of $\mu = 0.1$ and Cauchy boundary conditions.
+The constant $C = \nicefrac{100}{\gamma}$ governs the speed of sound and thus the Mach number~\cite{dumbser2016high}, the viscosity is set to $\mu = 0.1$.
+We use a domain of size $(\SI{2 \pi}{\m} \times \SI{2 \pi}{\m})$ and impose the analytical solution at the boundary.
 
 We use the Arnold-Beltrami-Childress (\textsc{abc}) flow as a simple three-dimensional flow~\cite{tavelli2016staggered}.
-It also has an exact solution under the assumption of incompressibility
+It also has an exact solution in the domain of \( \left[ -\SI{\pi}{\m}, \SI{\pi}{\m} \right]^3 \) under the assumption of incompressibility
 \begin{align}
@@
 \end{align}
-Here, $C = \nicefrac{100}{\gamma}$ is an arbitrary constant.
-We use a viscosity of $\mu = 0.01$ and Cauchy boundary conditions.
+The constant $C = \nicefrac{100}{\gamma}$ is chosen as before.
+We use a viscosity of $\mu = 0.01$ and analytical boundary conditions.
 
 As a final example of standard flow scenarios, we consider the lid-driven cavity flow where the fluid is at rest initially, with $\Qrho = 1$ and $ \pressure(\bm{x}) = \nicefrac{100}{\gamma}$.
-
-We consider a domain of size $\SI{2\pi}{m} \times \SI{2\pi}{\m}$ which is surrounded by no-slip walls.
+We consider a domain of size $\SI{1}{m} \times \SI{1}{\m}$ which is surrounded by no-slip walls.
 The flow is driven entirely by the upper wall which has a velocity of $v_x = \SI{1}{\m/\s}$.
@@
 The background atmosphere is then perturbed.
-\todo{What about our weird boundary condition for heat flux and energy?}
+\todo{LK: Mention bcs briefly?}
 Let
@@
 For our first scenario, the cosine bubble, we use a pertubation of the form
-\begin{equation}
-  \label{eq:cos-pertubation-alt}
-  \pertubationPotT = 
-    \nicefrac{A}{2} \left( 1 + \cos(\pi r) \right) \left[ r \leq a \right]
-\end{equation}
+% \begin{equation}
+%   \label{eq:cos-pertubation-alt}
+%   \pertubationPotT = 
+%     \nicefrac{A}{2} \left( 1 + \cos(\pi r) \right) \left[ r \leq a \right]
+% \end{equation}
 \begin{align}
@@
 We use a constant viscosity of $\mu = 0.1$.
-For our second scenario, the cold bubble on top of a warm bubble, we use the pertubations
+For our second scenario, the cold bubble on top of a warm bubble, we use the perturbations
 \begin{equation}
@@
 Similar to~\cite{muller2010adaptive} and to the previous scenario, we use a constant viscosity of $\mu = 0.1$ to regularize the solution.
-To ensure that the atmosphere stays in hydrostatic balance~\cite{giraldo2008study}, we need to impose the viscous heat flux\todo{Show full bc?}
+To ensure that the atmosphere stays in hydrostatic balance~\cite{giraldo2008study}, we need to impose the viscous heat flux\todo{LK: Show full bc?}
 \begin{equation}
@@
 
-We start with a coarse mesh that is then subdivided up to two times in an adaptive manner.
-For this we use the criterion of \cref{eq:refinement-criterion} with parameters xxx and xxx.
-We compare this with a simulation obtained by a fully refined grid.
+% We start with a coarse mesh that is then subdivided up to two times in an adaptive manner.
+% For this we use the criterion of \cref{eq:refinement-criterion} with parameters xxx and xxx.
+% We compare this with a simulation obtained by a fully refined grid.
 
-Clouds with 2+ AMR Levels (if working?)
-We evaluate this scenario both with a viscosity xxx and with zero viscosity.
-
-TODO, Show following results:
+Show following results:
 \begin{itemize}
 \item Simple cfd: Taylor Green, ABC, Lid Driven Cavity
-\item Two Bubbles with and without amr
+\item Two Bubbles with \amr{} (2 levels if possible) and no \amr{} (comparison)
+\item Two Bubbles (Euler eqs, FV\todo{Fix parameters})  
+\item Two Bubbles with limiting instead of visc.\ if working  
+\item Cosine bubble in 2D and possibly 3D, if working \todo{move bubble downwards for 3d}
 \end{itemize}
@@
 \section{Conclusion}
-We presented a \muscl{}-limited \aderdg{}-scheme with \amr{} for the Navier-Stokes equations.
+We presented our implementation of a \muscl{}-limited \aderdg{}-scheme with \amr{} for the Navier-Stokes equations.
 Our implementation is capable of simulating different scenarios:
@@
 \end{itemize}
+\todo{LK: Flesh this out a tiny bit, mention properties of \amr{} criterion}
 

### 2019-04-11 writing/paper/paper.tex
Include MB's comments.

@@
 In this paper we use the \aderdg{} method of~\cite{dumbser2008unified} to simulate various computational fluid dynamics (\textsc{cfd}) scenarios with a focus on hydrostatic flows\todo{LK: Heißt das so?}.
-To include viscosity, we use the numerical flux of \citeauthor{gassner2008discontinuous}~\cite{gassner2008discontinuous} to include the parabolic terms of the compressible Navier-Stokes equations.
+To include viscosity\todo{MB meint (zu recht), dass die viscosity unmotiviert ist.
+  Lieber noch so 10--15 Zeilen drüber schreiben.}, we use the numerical flux of \citeauthor{gassner2008discontinuous}~\cite{gassner2008discontinuous} to include the parabolic terms of the compressible Navier-Stokes equations.
 This flux has already been applied to the \aderdg{} method in~\cite{dumbser2010arbitrary}.
@@
 
-We make the following contributions:
+We make the following contributions\todo{Feedback von MB: Besser hervorheben, warum diese Sachen interessant/neu sind.
+Dumbser macht in seinen NS-DG papern keine komplexen Source terme, keine hydrostatic flows, etc.
+}:
 \begin{itemize}%

### 2019-04-15 writing/paper/paper.tex
Fix bibliography style, add acknowledgements.

@@
 \author{Lukas Krenz\inst{1} \and{} Leonhard Rannabauer\inst{1} \and{} Michael Bader\inst{1}}
-\institute{Technical University of Munich}
+\institute{Technical University of Munich} % todo emails and stuff
 \usepackage[utf8]{inputenc}
@@
 \usepackage[%
-  % backend=biber,
-  % url=false,
+  backend=biber,
+  url=false,
+  doi=false,
   % style=alphabetic,
@@
   % hyperref=true,
-  % maxnames=4,
+  maxnames=3,
   % minnames=3,
   % maxbibnames=99,
-  % firstinits,
+  firstinits=true,
   % uniquename=init
@@
 
+\subsection*{Acknowledgements}
+Lukas Krenz was funded by ChEESE (823844), Leonhard Rannabauer was funded by ExaHyPE (671698).
+\todo{LK: Standard sentence is: This research was funded by the European Union’s Horizon 2020 Research and Innovation Programme under theproject ExaHyPE, grant no.  671698 (call FETHPC-1-2014).
+
+Also LRZ?}
+
 \printbibliography{}

### 2019-04-16 writing/paper/paper.tex
Small changes.

@@
 In this paper we use the \aderdg{} method of~\cite{dumbser2008unified} to simulate various computational fluid dynamics (\textsc{cfd}) scenarios with a focus on hydrostatic flows\todo{LK: Heißt das so?}.
-To include viscosity\todo{MB meint (zu recht), dass die viscosity unmotiviert ist.
+To include viscosity\todo{MB: viscosity ist unmotiviert ist.
   Lieber noch so 10--15 Zeilen drüber schreiben.}, we use the numerical flux of \citeauthor{gassner2008discontinuous}~\cite{gassner2008discontinuous} to include the parabolic terms of the compressible Navier-Stokes equations.
@@
 \end{equation}
+\todo{Note that similar splitting is performed in giraldo}
 \section{Numerics}
@@
 We use the \aderdg{}-scheme as proposed in \cite{dumbser2008unified} together with a Rusanov-style flux~\cite{gassner2008discontinuous,fambri2017space} that is adapted for \pde{}s with diffusive terms.
-In addition, we use a \muscl{} finite volume method with the same flux and the xxx \todo{LK: Which one is best? Cite.} limiter.
+In addition, we use a \muscl{} finite volume method with the same flux and the van Albada \todo{LK: Which one is best? Cite vanalbada} limiter.
 
@@
 \end{equation}
-with probability $\mathbb{P}$ guarantees that we neither refine nor delete all cells.
+with probability $\mathbb{P}$ guarantees that we neither refine nor delete all cells.\todo{Mention that all cells of a smaller level need to be \textbf{marked} as erase to trigger coarsening.}
 \todo{LR: Was gibt es an compressible NS mit dynamic AMR, wie unterscheiden wir uns im Refinement Kriterium?}

### 2019-04-16 writing/paper/paper.tex
Another read-through.

--- 2019-04-15 writing/paper/paper.tex
@@
 
-\keywords{First keyword  \and Second keyword \and Another keyword.}
+\keywords{\aderdg{}  \and Navier-Stokes \and Another keyword.}
 \end{abstract}
 \section{Introduction}
+Insert references to Giraldo SE/DG bubbles~\cite{giraldo2008study}, 3D bubbles~\cite{giraldo2013implicit,kelly2012continuous}, bubble amr (müller~\cite{muller2010adaptive}).
+
 In this paper we use the \aderdg{} method of~\cite{dumbser2008unified} to simulate various computational fluid dynamics (\textsc{cfd}) scenarios with a focus on hydrostatic flows\todo{LK: Heißt das so?}.
-To include viscosity\todo{MB meint (zu recht), dass die viscosity unmotiviert ist.
+To include viscosity\todo{MB: viscosity ist unmotiviert ist.
   Lieber noch so 10--15 Zeilen drüber schreiben.}, we use the numerical flux of \citeauthor{gassner2008discontinuous}~\cite{gassner2008discontinuous} to include the parabolic terms of the compressible Navier-Stokes equations.
@@
 
-We utilize the \exahypeengine{} (\url{www.exahype.eu}) which is an engine that can solve arbitrary hyperbolic partial differential equations.
+We utilize the \exahypeengine{} (\url{www.exahype.eu}) which is a framework that can solve arbitrary hyperbolic partial differential equations.
 A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well posed Cauchy problem for a system of hyperbolic \pde{}s of first order.
-The underlying \aderdg{} method, parallelization techniques and dynamic adaptive mesh refinement are available for simulations while the implementations are left as a black box to the user.
+The underlying \aderdg{} method\todo{\muscl{}?}, parallelization techniques and dynamic adaptive mesh refinement are available for simulations while the implementations are left as a black box to the user.
 An introduction to the communication-avoiding implementation of the whole numerical scheme can be found in the recent work~\cite{charrier2018stop} by \citeauthor{charrier2018stop}.
@@
 \begin{itemize}%
-\item We extend the \exahypeengine{} to allow diffusive terms following the aforementioned numerical scheme.
+\item We extend the \exahypeengine{} to allow viscous terms following the aforementioned numerical scheme.
 \item We use this to provide an implementation of the compressible Navier-Stokes equations.
 \item We show an \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
-\item We evaluate our implementation with standard \textsc{cfd} scenarios and atmospheric flows.
+\item We evaluate our implementation with standard \textsc{cfd} scenarios and atmospheric flows and inspect the effectiveness of our proposed \amr{}-criterion.
 \end{itemize}
@@
 with vector of conserved quantities $\Q$, flux $\flux(\Q, \gradQ)$ and source $\source(\Q)$.
+Note that the flux can be split into a hyperbolic part $\hyperFlux(\Q)$,
+which is identical to the flux of the Euler equations,
+and a viscous part $\viscFlux(\Q, \gradQ)$.
 The conserved quantities
-\begin{equation} 
-  \label{eq:conserved-variables}
- \Q = \left( \Qrho, \Qj, \QE, \QZ \right),
-\end{equation}
+\(\Q\)
+% \begin{equation} 
+%   \label{eq:conserved-variables}
+%  \Q = \left( \Qrho, \Qj, \QE, \QZ \right),
+% \end{equation}
 are the density $\Qrho$, the two or three-dimensional momentum $\Qj$ and the energy density $\QE$.
@@
   \label{eq:stress-tensor}
-  \stressT(Q, \nabla Q) =
+  \stressT(\Q, \gradQ) =
   \mu
@@
 
-Many realistic atmospheric flows can be described by a perturbation over a background state that is in hydrostatic equilibrium
+Many realistic atmospheric flows can be described by a perturbation over a background state that is in hydrostatic equilibrium\todo{Mention source}
 \newcommand{\backgroundPressure}{\overline{\pressure}}
@@
 \end{equation}
+Note that a smilar splitting is performed in~\cite{muller2010adaptive,giraldo2008study}.
+\todo{Mention differences in splitting methods}
 \section{Numerics}
@@
 \todo{LK: CFL? Riemannsolver (no gradients)}
-We use the \aderdg{}-scheme as proposed in \cite{dumbser2008unified} together with a Rusanov-style flux~\cite{gassner2008discontinuous,fambri2017space} that is adapted for \pde{}s with diffusive terms.
-In addition, we use a \muscl{} finite volume method with the same flux and the xxx \todo{LK: Which one is best? Cite.} limiter.
+We use an \aderdg{}-scheme and a \muscl{} finite volume method.
+Both can be considered as instances of the more general \textsc{PnPm} schemes of~\cite{dumbser2008unified}.
+We use a Rusanov-style flux that is adapted to \pde{}s with viscous terms~\cite{gassner2008discontinuous,fambri2017space}.
+The finite volume scheme is stabilized with the van Albada limiter\todo{LK: Which one is best? Cite vanalbada}.
 
@@
 We use an element local error estimate based on the total variation of the numerical solution. 
-Let $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ be a function that maps the discrete solution at a point $\bm{x}$ to an arbitrary indicator variable.
+Let $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ be a sufficiently smooth function that maps the discrete solution at a point $\bm{x}$ to an arbitrary indicator variable.
 The total variation (\textsc{tv}) of this function is defined by
@@
 \newcommand{\Trefine}{T_\text{refine}}%
-\newcommand{\Tdelete}{T_\text{delete}}%
+\newcommand{\Tdelete}{T_\text{erase}}%
 How can we decide whether a cell is important or not?
@@
     \text{refine} & \text{if } \tv(\Q) \geq \mu + \Trefine \sigma, \\
-    \text{delete} & \text{if } \tv(\Q) < \mu + \Tdelete \sigma, \\
+    \text{erase} & \text{if } \tv(\Q) < \mu + \Tdelete \sigma, \\
     \text{keep} & \text{otherwise}.
@@
 \end{equation}
-with probability $\mathbb{P}$ guarantees that we neither refine nor delete all cells.
+with probability $\mathbb{P}$ guarantees that we neither mark all cells for refinement nor for erasement.
 \todo{LR: Was gibt es an compressible NS mit dynamic AMR, wie unterscheiden wir uns im Refinement Kriterium?}
-This inequality holds for arbitrary distributions under the weak assumption that their mean $\mu$ and standard deviation $\sigma$ are finite~\cite{wasserman2004all}.
+This inequality holds for arbitrary distributions under the weak assumption that they have a finite mean $\mu$ and a finite standard deviation $\sigma$~\cite{wasserman2004all}.
+Note that subcells are coarsened only if all subcells belonging to the coarse cell are marked for erasion.
 
@@
 The constant $C = \nicefrac{100}{\gamma}$ governs the speed of sound and thus the Mach number~\cite{dumbser2016high}, the viscosity is set to $\mu = 0.1$.
-We use a domain of size $(\SI{2 \pi}{\m} \times \SI{2 \pi}{\m})$ and impose the analytical solution at the boundary.
+We use a domain of size $(\SI{2 \pi}{\m} \times \SI{2 \pi}{\m})$ and impose the analytical solution at the boundary\todo{tEnd, mach=0.1}.
 
@@
 The constant $C = \nicefrac{100}{\gamma}$ is chosen as before.
-We use a viscosity of $\mu = 0.01$ and analytical boundary conditions.
+We use a viscosity of $\mu = 0.01$ and analytical boundary conditions\todo{tEnd}.
 
-As a final example of standard flow scenarios, we consider the lid-driven cavity flow where the fluid is at rest initially, with $\Qrho = 1$ and $ \pressure(\bm{x}) = \nicefrac{100}{\gamma}$.
+As a final example of standard flow scenarios, we consider the lid-driven cavity flow where the fluid is initially at rest, with $\Qrho = 1$ and $ \pressure(\bm{x}) = \nicefrac{100}{\gamma}$.
 We consider a domain of size $\SI{1}{m} \times \SI{1}{\m}$ which is surrounded by no-slip walls.
@@
 \end{equation}
-denote the difference between spatial positions $x,z$ and the center of a bubble $x_c, z_c$.
+denote the difference between spatial positions $x,z$ and the center of a bubble $x_c, z_c$\todo{3D}.
 For our first scenario, the cosine bubble, we use a pertubation of the form
@@
 where $A$ denotes the maximal perturbation and $a$ is the size of the bubble.
-We use the constants
+We use the constants\todo{3d bubble is higher}
 \begin{equation}\label{eq:cosine-bubble}
@@
 \end{equation}
-We use a constant viscosity of $\mu = 0.1$.
-For our second scenario, the cold bubble on top of a warm bubble, we use the perturbations
+We use a constant viscosity of $\mu = 0.1$\todo{tend = 400 for 3d and 600 for 2d}.
+For our second scenario, the colliding bubbles, we use perturbations of the form
 \begin{equation}
@@
 Similar to~\cite{muller2010adaptive} and to the previous scenario, we use a constant viscosity of $\mu = 0.1$ to regularize the solution.
-To ensure that the atmosphere stays in hydrostatic balance~\cite{giraldo2008study}, we need to impose the viscous heat flux\todo{LK: Show full bc?}
+To ensure that the atmosphere stays in hydrostatic balance~\cite{giraldo2008study}, we need to impose the viscous heat flux
 \begin{equation}
@@
 \end{equation}
+where $\overline{T}(z)$ is the background temperature at position $z$ which can be computed from \cref{eq:hydrostatic-balance,eq:eos}.
+We furthermore set the density and energy at the boundary such that it corresponds to the background atmosphere.
 
@@
 \item Two Bubbles with \amr{} (2 levels if possible) and no \amr{} (comparison)
-\item Two Bubbles (Euler eqs, FV\todo{Fix parameters})  
+\item Two Bubbles (Euler eqs, FV)  
 \item Two Bubbles with limiting instead of visc.\ if working  
-\item Cosine bubble in 2D and possibly 3D, if working \todo{move bubble downwards for 3d}
+\item Cosine bubble in 2D and possibly 3D, if working
 \end{itemize}
@@
   This is true for both two-dimensional scenarios (Taylor-Green vortex and lid-driven cavity) and for the three-dimensional \textsc{abc}-flow.
-\item Furthermore, our method allows us to simulate flows in hydrostatic equilibrium correctly.
+\item Furthermore, our method allows us to simulate flows in hydrostatic equilibrium correctly as our results for the cosine and colliding bubble scenarios showed.
 \item We showed that our \amr{}-criterion is able to vastly reduce the number of grid cells while preserving the quality of the results.

### 2019-04-16 src/dataset_utils.py
Add plotting scripts.

@@ -1,0 +1,130 @@
+import vtk
+import vtk.util.numpy_support as vutil
+import numpy as np
+import pandas as pd
+
+def read_solution(path, order=None, size=10, limiting=False, advection=False):
+    reader = vtk.vtkXMLUnstructuredGridReader()
+    reader.SetFileName(path)
+    reader.Update()
+    output = reader.GetOutput()
+    n_points = reader.GetNumberOfPoints()
+        
+    nodes = output.GetPoints().GetData()
+    po_d = output.GetPointData()
+    time_idx = 3 if limiting else 1
+    time = po_d.GetArray(time_idx).GetTuple(0)[0]
+    
+    number_of_data = int(po_d.GetArray(0).GetSize()/n_points)
+    # Are we 2d or 3d?
+    # Data is [rho, v, p, potT] 
+    number_of_data_2d = 6 if advection else 5
+    number_of_coords = 2 if number_of_data == number_of_data_2d else 3
+    
+    store_refinement_status = (number_of_coords == 2)
+    num_refinement_cols = 1 if store_refinement_status else 0
+    data = np.zeros((n_points, 3 + number_of_data + num_refinement_cols)) * float('NaN')
+    for i in range(n_points):
+        if number_of_coords == 2:
+            x, y, z = nodes.GetTuple(i)
+            if limiting:
+                refinement_status = np.longfloat(output.GetPointData().GetArray(1).GetTuple(i))
+            else:
+                refinement_status = 4
+            if advection:
+                rho, v_x, v_y, p, Z, potT = np.longfloat(output.GetPointData().GetArray(0).GetTuple(i))
+                data[i, :] = np.array([x, y, z, rho, v_x, v_y, p, Z, potT, refinement_status])
+            else:                
+                rho, v_x, v_y, p, potT = np.longfloat(output.GetPointData().GetArray(0).GetTuple(i))
+                data[i, :] = np.array([x, y, z, rho, v_x, v_y, p, potT, refinement_status])
+        else:
+            assert(not advection and not limiting)
+            x, y, z = nodes.GetTuple(i)
+            rho, v_x, v_y, v_z, p, potT = np.longfloat(output.GetPointData().GetArray(0).GetTuple(i))
+            data[i, :] = np.array([x, y, z, rho, v_x, v_y, v_z, p, potT])       
+
+    if number_of_coords == 2:
+        if advection:
[…]

### 2019-04-16 src/plot_abc.py

@@ -1,0 +1,102 @@
+#!/usr/bin/env python3
+import numpy as np
+
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+from plot_utils import *
+from dataset_utils import *
+
+# Analytical solutions
+    
+def analytical_solution_p_abc(x,y,z,time,mu):
+    C = 100/1.4
+    decay = np.exp(-2 * mu * time)
+    return C - (np.cos(x) * np.sin(y) + np.sin(x) * np.cos(z) + np.sin(z) * np.cos(y)) * decay
+
+def analytical_solution_u_abc(x,y,z,time,mu):
+    decay = np.exp(-1 * mu * time)
+    return (np.sin(z) + np.cos(y)) * decay
+
+def analytical_solution_v_abc(x,y,z,time,mu):
+    decay = np.exp(-1 * mu * time)
+    return (np.sin(x) + np.cos(z)) * decay
+
+def analytical_solution_w_abc(x,y,z,time,mu):
+    decay = np.exp(-1 * mu * time)
+    return (np.sin(y) + np.cos(x)) * decay
+
+def analytical_solution_abc(x,y,z,time,mu,var):
+    if var == 'p':
+        return analytical_solution_p_abc(x,y,z,time,mu)
+    elif var == 'u':
+        return analytical_solution_u_abc(x,y,z,time,mu)
+    elif var == 'v':
+        return analytical_solution_v_abc(x,y,z,time,mu)
+    else:
+        return analytical_solution_w_abc(x,y,z,time,mu)
+
+def plot_abc(fig_path, solution_path, target, order=2):
+    df, time, order, dim, dx, n_points = read_solution(solution_path, order=order)
+    time, order, dim, dx, n_points
+    
+    analytical_solution = analytical_solution_abc
+    coord = 'x'
+    var = 'p'
+
+    fs = figsize(1.0, target=target)
+    fs = fs[0], 0.5*fs[1]
+
+    fig, axs = plt.subplots(ncols=3, figsize=fs, sharey=True)
+
+    markers = ['o', 'x', 'X']
+    marker = markers[0]
+
+    for ax, coord in zip(axs, ['x', 'y', 'z']):
+    #_, _, c = plot_contour(df_cut, fig, ax, var, levels=4, coords=others, num_sample=500,colored=False)
+        coord_cut, p_approx_cut, p_ana_cut, vel_approx_cut, vel_ana_cut = eval_cut(df, coord, time, mu=0.01,
[…]

### 2019-04-16 src/plot_bubbles.py

@@ -1,0 +1,22 @@
+#!/usr/bin/env python3
+import numpy as np
+
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+from plot_utils import *
+from dataset_utils import *
+
+def plot_bubbles(fig_path, solution_path, target):
+    pass
+
+def main():
+    set_plot_defaults()
+    fig_path='output/'
+    plot_cavity(fig_path=fig_path,
+                solution_path='/home/lukas/Documents/MA-results/lid-driven-cavity/solution-3.vtu',
+                target='paper')
+        
+if __name__ == '__main__':
+    main()
+    

### 2019-04-16 src/plot_cavity.py

@@ -1,0 +1,126 @@
+#!/usr/bin/env python3
+import numpy as np
+
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+from plot_utils import *
+from dataset_utils import *
+
+def plot_cavity(fig_path, solution_path, target):
+    # TODO: Use current solution
+    df, time, order, dim, dx, n_points = read_solution(solution_path, order=3, size=1, limiting=True)
+    print(time, order, dim, dx, n_points)
+
+    sns.set_palette(sns.color_palette('Paired'))
+
+    # Compare with reference data from High-Re Solutions 
+    # for Incompressible Flow Using the Navier-Stokes Equations and a Multigrid Method
+    ref_y, ref_v_x = np.array([
+        1.0000, 1.00000,
+        0.9766, 0.84123,
+        0.9688, 0.78871,
+        0.9609, 0.73722,
+        0.9531, 0.68717,
+        0.8516, 0.23151,
+        0.7344, 0.00332,
+        0.6172,-0.13641,
+        0.5000,-0.20581,
+        0.4531,-0.21090,
+        0.2813,-0.15662,
+        0.1719,-0.10150,
+        0.1016,-0.06434,
+        0.0703,-0.04775,
+        0.0625,-0.04192,
+        0.0547,-0.03717,
+        0.0000,-0.00000
+    ]).reshape(-1,2).T
+    ref_y -= 0.5
+
+    ref_x, ref_v_y = np.array([
+        1.0000, 0.00000,
+        0.9688,-0.05906,
+        0.9609,-0.07391,
+        0.9531,-0.08864,
+        0.9453,-0.10313,
+        0.9063,-0.16914,
+        0.8594,-0.22445,
+        0.8047,-0.24533,    
+        0.5000, 0.05454,
+        0.2344, 0.17527,
+        0.2266, 0.17507,
+        0.1563, 0.16077,
+        0.0938, 0.12317,
+        0.0781, 0.10890,
+        0.0703, 0.10091,
+        0.0625, 0.09233,    
+        0.0000, 0.00000
+
+    ]).reshape(-1,2).T
+    ref_x -= 0.5
+
+
+    df_cut = cut_dataset(df, 'y', dim=2, cut_at=[None, None])
+    fig, ax = plt.subplots(figsize=figsize(0.5, target=target))
+    ax.plot(df_cut['y'], df_cut['v_x'], label='$v_x(z)$')
+
[…]

### 2019-04-16 src/plot_cosine_bubble.py

@@ -1,0 +1,57 @@
+#!/usr/bin/env python3
+import numpy as np
+
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+from plot_utils import *
+from dataset_utils import *
+
+from matplotlib import ticker
+
+
+def plot_cosine_bubble(fig_path, solution_path, target, order=4):
+    df, time, order, dim, dx, n_points = read_solution(solution_path, order=order, size=1000)
+    print(time, order, dim, dx, n_points)
+
+    # Fig 4 giraldo
+    df_cut = cut_dataset(df, 'y', dim=2, cut_at=[None, None])
+    fig, ax = plt.subplots(figsize=quadratic_figsize(scale=0.5, target=target))
+    ax.plot(df_cut['y'], df_cut['potT']-300, c='black')
+    ax.set_xlim(850, 1000)
+    ax.set_ylim(-0.1, 0.6)
+    ax.set_xlabel('$z [\si{m}]$')
+    ax.set_ylabel("$\Theta\'$")
+    fig.subplots_adjust(left=0.2)
+
+    fig.savefig(fig_path + f'{target}_cosine_bubble_pertubation.pdf', transparent=True)
+
+    fig, ax = plt.subplots(figsize=quadratic_figsize(0.5, target=target))
+    df['potTPertubation'] = df['potT'] - 300
+    levels = np.arange(-0.05, 0.525+0.025, 0.025)
+    levels = levels[levels!=0]
+    _,_, c = plot_contour(df=df, fig=fig, ax=ax, var='potTPertubation', num_sample=1000, levels=levels, axis_off='on')
+
+    sns.despine(fig, ax)
+    ax.set_xlabel('$x [\si{m}]$')
+    ax.set_ylabel('$z [\si{m}]$')
+    ax.text(100,300, r'$t = \SI{700}{\s}$')
+
+    fig.subplots_adjust(left=0.2, right=0.87, bottom=0.2)
+    cax = fig.add_axes([0.25, 0.2, .6, .05])
+    cb = fig.colorbar(mappable=c,cax=cax, orientation='horizontal')
+    cb.locator = ticker.MaxNLocator(nbins=5)
+    cb.update_ticks()
+
+    fig.savefig(fig_path + f'{target}_cosine_bubble_contour_t700.pdf', transparent=True)
+
+
+def main():
+    set_plot_defaults()
+    fig_path = 'output/'
+    plot_cosine_bubble(fig_path=fig_path,
[…]

### 2019-04-16 src/plot_taylor_green.py

@@ -1,0 +1,94 @@
+#!/usr/bin/env python3
+import numpy as np
+
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+from plot_utils import *
+from dataset_utils import *
+
+# Analytical solutions
+def analytical_solution_p_tg(x,y,time,mu):
+    C = 100/1.4
+    decay = np.exp(-4 * mu * time)
+    return C + 1/4 * (np.cos(2*x) + np.cos(2*y)) * decay
+
+def analytical_solution_u_tg(x,y,time,mu):
+    decay = np.exp(-2 * mu * time)
+    return np.sin(x) * np.cos(y) * decay
+
+def analytical_solution_v_tg(x,y,time,mu):
+    decay = np.exp(-2 * mu * time)
+    return -np.cos(x) * np.sin(y) * decay
+
+def analytical_solution_taylor_green(x,y,z,time,mu,var):
+    if var == 'p':
+        return analytical_solution_p_tg(x,y,time,mu)
+    elif var == 'u':
+        return analytical_solution_u_tg(x,y,time,mu)
+    else:
+        return analytical_solution_v_tg(x,y,time,mu)
+
+def plot_taylor_green(fig_path, solution_path, target, order=5):
+    df, time, order, dim, dx, n_points = read_solution(solution_path, order=order, size=2*np.pi)
+    print(time, order, dim, dx, n_points)
+
+    scenario = 'taylor-green' if dim == 2 else 'abc'
+    analytical_solution = analytical_solution_taylor_green if scenario == 'taylor-green' else analytical_solution_abc
+
+    fig, ax = plt.subplots(figsize=figsize(scale=0.5, target=target))
+    if dim == 2:
+        coords = ['x', 'y']
+        markers = ['o', 'x']   
+    else:
+        coords = ['x', 'y', 'z']
+        markers = ['o', 'x', 'X']
+        #coords = ['x']
+        #markers = ['x']
+
+    # Velocities
+    for coord, marker in zip(coords, markers):
+        coord_cut, p_approx_cut, p_ana_cut, vel_approx_cut, vel_ana_cut = eval_cut(df, coord, time, mu=0.01,
+                                                                    analytical_solution=analytical_solution,
+                                                                                dim=dim)
+        ax.plot(coord_cut, vel_ana_cut, c='gray', linestyle='solid', zorder=-1, label=None)
[…]

### 2019-04-16 src/plot_two_bubbles.py

@@ -1,0 +1,38 @@
+#!/usr/bin/env python3
+import numpy as np
+
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+from plot_utils import *
+from dataset_utils import *
+
+from matplotlib import ticker
+
+
+def plot_two_bubbles(fig_path, solution_path, target, order=4):
+    df, time, order, dim, dx, n_points = read_solution(solution_path, order=order, size=1000)
+    print(time, order, dim, dx, n_points)
+    
+    fig, ax = plt.subplots(figsize=quadratic_figsize(0.5, target=target))
+    df['potTPertubation'] = df['potT'] - 300
+    levels = np.arange(-0.05, 0.45+0.05, 0.05)
+    levels = levels[levels!=0]
+    plot_contour(df=df, fig=fig, ax=ax, var='potTPertubation', num_sample=100, levels=levels, axis_off='on', colored=False,
+                linewidths=0.5)
+    sns.despine(fig, ax)
+    ax.set_xlabel('$x [\si{m}]$')
+    ax.set_ylabel('$z [\si{m}]$')
+    ax.text(100,100, r'$t = \SI{' + str(time) + r'}{\s}$')
+    fig.subplots_adjust(left=0.2, bottom=0.15)
+    fig.savefig(fig_path + f'{target}_two_bubbles_contour_t{time}.pdf', transparent=True)
+
+def main():
+    set_plot_defaults()
+    fig_path = 'output/'
+    plot_two_bubbles(fig_path=fig_path,
+                       solution_path='/home/lukas/Documents/MA-results/AMR/solution_cartesian-10.vtu',
+                       target='paper')
+
+if __name__ == '__main__':
+    main()

### 2019-04-16 src/plot_utils.py

@@ -1,0 +1,117 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import seaborn as sns
+from scipy.interpolate import griddata
+
+
+import streamplot_mod # fixes some issues with streamplot
+
+def figsize(scale=1.0, target='thesis'):
+    width_map = {
+        'thesis': 418.25555,
+        'beamer_169' : 398.3386,
+        'beamer_43': 307.28987,
+        'paper': 347.12354 #llncs
+    }
+    latex_width = width_map[target]
+    fig_width = latex_width/72.27 # inches
+    fig_height = fig_width * (np.sqrt(5)-1.0)/2.0
+    return [fig_width*scale, fig_height*scale]
+    
+
+def quadratic_figsize(scale=1.0, target='thesis'):
+    fs = figsize(scale=scale, target=target)
+    size = (fs[0], fs[0])
+    return size
+    
+def set_plot_defaults():
+    sns.set_style('white')
+    #sns.set_palette(sns.color_palette('viridis'))
+    sns.set_palette(sns.color_palette('Paired'))
+
+    params = {
+        'font.size': 11,
+        'font.family': 'serif',
+        'font.serif': [],
+        'axes.labelsize': 11,
+        'legend.fontsize': 11,
+        'xtick.labelsize': 8,
+        'ytick.labelsize': 8,
+        'figure.figsize': figsize(scale=1.0),
+        'text.usetex': True,
+        'pgf.texsystem': 'pdflatex',
+        'text.latex.unicode': True
+        }
+    plt.rcParams.update(params)
+    plt.rcParams['text.latex.preamble'].extend([
+        r'\usepackage{amsmath}'
+        r'\usepackage[separate-uncertainty]{siunitx}'],)
+
+def plot_stream_lines(df, fig, ax, num_sample=500, density=2, minlength=0.01, maxlength=2, arrowsize=10e-100, start_points=None, interpolator='cubic',
+                     modified_streamline=False, linewidth=None):
+    x = df['x']
+    y = df['y']
+    u = df['v_x']
+    v = df['v_y']
+    
+    xx = np.linspace(x.min(), x.max(), num_sample)
+    yy = np.linspace(y.min(), y.max(), num_sample)
+
+    X, Y = np.meshgrid(xx,yy)
+
+    uu = griddata((x,y), u, (X,Y))
+    vv = griddata((x,y), v, (X,Y))
+
+    fs = figsize(scale=1.0)
[…]

### 2019-04-16 src/streamplot_mod.py

@@ -1,0 +1,675 @@
+"""
+Streamline plotting for 2D vector fields.
+
+"""
+
+import numpy as np
+
+import matplotlib
+import matplotlib.cm as cm
+import matplotlib.colors as mcolors
+import matplotlib.collections as mcollections
+import matplotlib.lines as mlines
+import matplotlib.patches as patches
+
+
+__all__ = ['streamplot']
+
+
+def streamplot(axes, x, y, u, v, density=1, linewidth=None, color=None,
+               cmap=None, norm=None, arrowsize=1, arrowstyle='-|>',
+               minlength=0.1, transform=None, zorder=None, start_points=None,
+               maxlength=4.0, integration_direction='both'):
+    """
+    Draw streamlines of a vector flow.
+
+    Parameters
+    ----------
+    x, y : 1d arrays
+        An evenly spaced grid.
+    u, v : 2d arrays
+        *x* and *y*-velocities. Number of rows should match length of *y*, and
+        the number of columns should match *x*.
+    density : float or 2-tuple
+        Controls the closeness of streamlines. When ``density = 1``, the domain
+        is divided into a 30x30 grid---*density* linearly scales this grid.
+        Each cell in the grid can have, at most, one traversing streamline.
+        For different densities in each direction, use [density_x, density_y].
+    linewidth : numeric or 2d array
+        Vary linewidth when given a 2d array with the same shape as velocities.
+    color : matplotlib color code, or 2d array
+        Streamline color. When given an array with the same shape as
+        velocities, *color* values are converted to colors using *cmap*.
+    cmap : `~matplotlib.colors.Colormap`
+        Colormap used to plot streamlines and arrows. Only necessary when using
+        an array input for *color*.
+    norm : `~matplotlib.colors.Normalize`
+        Normalize object used to scale luminance data to 0, 1. If ``None``,
+        stretch (min, max) to (0, 1). Only necessary when *color* is an array.
+    arrowsize : float
+        Factor scale arrow size.
+    arrowstyle : str
+        Arrow style specification.
+        See `~matplotlib.patches.FancyArrowPatch`.
+    minlength : float
+        Minimum length of streamline in axes coordinates.
+    start_points : Nx2 array
+        Coordinates of starting points for the streamlines.
[…]

### 2019-04-16 writing/paper/paper.tex
Abstract, some items.

@@
 \begin{abstract}
+
+\begin{itemize}
+\item Implementation of compressible Navier Stokes with a high-order \aderdg{}-method and a low order finite volume \muscl{}-scheme.
+\item Implementation in \exahypeengine{}, a scalable \pde{} framework.
+\item Outlier and total variation based adaptive mesh refinement that reduced number of grid cells drastically and preserves solution quality.
+\item Simulation of challenging flows over hydrostatic background atmosphere.
+\item Competitive results for both classical cfd scenarios and hydrostatic scenarios in two and three dimensions.
+\end{itemize}
+
 The abstract should briefly summarize the contents of the paper in
@@
 \section{Introduction}
+
 Insert references to Giraldo SE/DG bubbles~\cite{giraldo2008study}, 3D bubbles~\cite{giraldo2013implicit,kelly2012continuous}, bubble amr (müller~\cite{muller2010adaptive}).

### 2019-04-16 writing/paper/paper.tex
Rewrite introduction.

@@
 \section{Introduction}
+The accurate simulation of fluid dynamics is crucial for detailed weather prediction.
+\todo{Most results here are quite old.}
+Because these dynamics are approximated well with the compressible Navier-Stokes equations, this is the equation set of our choice.
+There are some examples, where higher order methods have been used for the simulation of clouds, such as~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
+Even though these methods use a discretization with a (theoretical) unlimited space-order, they use either Runge-Kutta time integrators or semi-implicit methods.
+It is well known that Runge-Kutta methods become more ineffecient for very high orders.
+Furthermore, they and the implicit methods are more communication-intensive and thus require a larger overhead.
 
-Insert references to Giraldo SE/DG bubbles~\cite{giraldo2008study}, 3D bubbles~\cite{giraldo2013implicit,kelly2012continuous}, bubble amr (müller~\cite{muller2010adaptive}).
+We thus follow a different approach in this paper and use the \aderdg{} method of~\cite{dumbser2008unified} to simulate various computational fluid dynamics (\textsc{cfd}) scenarios with a focus on hydrostatic flows.
+\todo{LK: Heißt das hydrostatic?}
+%\todo{MB: viscosity ist unmotiviert ist.
+ % Lieber noch so 10--15 Zeilen drüber schreiben.}
+Due to the viscous components of the Navier-Stokes equations, it is not straightforward to apply the \dg{} method.
+For high-order \dg{} methods, viscosity not only models the physical reality of the problem but also helps us by smoothing out oscillations and discontinuities, thus stabilizing the simulation.
+To include viscosity, we use the numerical flux for the compressible Navier-Stokes equations of \citeauthor{gassner2008discontinuous}~\cite{gassner2008discontinuous}.
+This flux has already been applied to the \aderdg{} method in~\cite{dumbser2010arbitrary}.
+In contrast to this paper, we focus on the simulation of complex flows with a gravitational source term and a realistic background atmosphere.
+%\todo{Einordnung, Kontext zu giraldo, etc$\ldots$}
 
-In this paper we use the \aderdg{} method of~\cite{dumbser2008unified} to simulate various computational fluid dynamics (\textsc{cfd}) scenarios with a focus on hydrostatic flows\todo{LK: Heißt das so?}.
-To include viscosity\todo{MB: viscosity ist unmotiviert ist.
-  Lieber noch so 10--15 Zeilen drüber schreiben.}, we use the numerical flux of \citeauthor{gassner2008discontinuous}~\cite{gassner2008discontinuous} to include the parabolic terms of the compressible Navier-Stokes equations.
-This flux has already been applied to the \aderdg{} method in~\cite{dumbser2010arbitrary}.
-\todo{Einordnung, Kontext zu giraldo, etc$\ldots$}
+%Insert references to Giraldo SE/DG bubbles~\cite{giraldo2008study}, 3D bubbles~\cite{giraldo2013implicit,kelly2012continuous}, bubble amr (müller~\cite{muller2010adaptive}).
 
-We utilize the \exahypeengine{} (\url{www.exahype.eu}) which is a framework that can solve arbitrary hyperbolic partial differential equations.
+We base our work on the \exahypeengine{} (\url{www.exahype.eu}) which is a framework that can solve arbitrary hyperbolic partial differential equations.
 A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well posed Cauchy problem for a system of hyperbolic \pde{}s of first order.
@@
 \item We extend the \exahypeengine{} to allow viscous terms following the aforementioned numerical scheme.
-\item We use this to provide an implementation of the compressible Navier-Stokes equations.
+\item We use this to provide an implementation of the compressible Navier-Stokes equation.
 \item We show an \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
@@
 The momentum equation is dominated by the background flow in this case.
-This can lead to numerical instabilities.
-To avoid this, we split the pressure $\pressure = \backgroundPressure + \pressure'$ into a sum of the background pressure $\backgroundPressure(z)$ and perturbation $\pressure'(\bm{x}, t)$.
+Because this can lead to numerical instabilities, problems of this kind are challenging and require some care.
+To lessen the impact of this, we split the pressure $\pressure = \backgroundPressure + \pressure'$ into a sum of the background pressure $\backgroundPressure(z)$ and perturbation $\pressure'(\bm{x}, t)$.
 We split the density $\Qrho = \backgroundRho + \Qrho'$ in the same manner and arrive at
@@
 \end{equation}
-Note that a smilar splitting is performed in~\cite{muller2010adaptive,giraldo2008study}.
+Note that a similar and more complex splitting is performed in~\cite{muller2010adaptive,giraldo2008study}.
+In contrast to this, we use the true compressible Navier-Stokes equations with minimal modifications.
 \todo{Mention differences in splitting methods}

### 2019-04-17 writing/paper/paper.tex
Some more work on introduction.

@@
 \section{Introduction}
-The accurate simulation of fluid dynamics is crucial for detailed weather prediction.
-\todo{Most results here are quite old.}
-Because these dynamics are approximated well with the compressible Navier-Stokes equations, this is the equation set of our choice.
-There are some examples, where higher order methods have been used for the simulation of clouds, such as~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
-Even though these methods use a discretization with a (theoretical) unlimited space-order, they use either Runge-Kutta time integrators or semi-implicit methods.
+The accurate simulation of clouds is crucial for detailed weather prediction.
+Because cloud dynamics can be approximated well with the compressible Navier-Stokes equations, this is the equation set of our choice.
+These equations are often space-discretized by higher order Galerkin methods, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
+Even though all of these implementations use a discretization with a (theoretical) unlimited space-order, they use Runge-Kutta time integrators or semi-implicit methods.
 It is well known that Runge-Kutta methods become more ineffecient for very high orders.
-Furthermore, they and the implicit methods are more communication-intensive and thus require a larger overhead.
+Furthermore, they and the implicit methods are more communication-intensive and thus require a larger overhead and are more complicated to scale.
 
-We thus follow a different approach in this paper and use the \aderdg{} method of~\cite{dumbser2008unified} to simulate various computational fluid dynamics (\textsc{cfd}) scenarios with a focus on hydrostatic flows.
-\todo{LK: Heißt das hydrostatic?}
-%\todo{MB: viscosity ist unmotiviert ist.
- % Lieber noch so 10--15 Zeilen drüber schreiben.}
+We follow a different approach in this paper and use the \aderdg{} method of~\cite{dumbser2008unified} to simulate various computational fluid dynamics (\textsc{cfd}) scenarios with a focus on flows with stratified flows.
+\todo{LK: Ist hier stratified flows korrekt?}
+\todo{MB: viscosity ist unmotiviert ist.
+    Lieber noch so 10--15 Zeilen drüber schreiben.}
 Due to the viscous components of the Navier-Stokes equations, it is not straightforward to apply the \dg{} method.
@@
 In contrast to this paper, we focus on the simulation of complex flows with a gravitational source term and a realistic background atmosphere.
+Additionally, we use adaptive mesh refinement (\textsc{amr}) to increase the spatial resolution in areas of interest.
+This has been shown to work well for the simulation of cloud dynamics~\cite{muller2010adaptive}.
 %\todo{Einordnung, Kontext zu giraldo, etc$\ldots$}
-
 %Insert references to Giraldo SE/DG bubbles~\cite{giraldo2008study}, 3D bubbles~\cite{giraldo2013implicit,kelly2012continuous}, bubble amr (müller~\cite{muller2010adaptive}).
 
-We base our work on the \exahypeengine{} (\url{www.exahype.eu}) which is a framework that can solve arbitrary hyperbolic partial differential equations.
+We base our work on the \exahypeengine{} (\url{www.exahype.eu}), which is a framework that can solve arbitrary hyperbolic partial differential equations.
 A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well posed Cauchy problem for a system of hyperbolic \pde{}s of first order.
@@
 \item We use this to provide an implementation of the compressible Navier-Stokes equation.
-\item We show an \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
+  In addition, we tailor the equation set to stratified flows with gravitational source term.
+\item We present a general \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
+  Furthermore, we show how to utilize this criterion for stratified flows.
 \item We evaluate our implementation with standard \textsc{cfd} scenarios and atmospheric flows and inspect the effectiveness of our proposed \amr{}-criterion.

### 2019-04-17 src/plot_two_bubbles.py
Improve two bubbles plot slightly.

@@ -13,26 +13,26 @@ from matplotlib import ticker
 def plot_two_bubbles(fig_path, solution_path, target, order=4):
     df, time, order, dim, dx, n_points = read_solution(solution_path, order=order, size=1000)
     print(time, order, dim, dx, n_points)
+    time = np.round(time)
     
     fig, ax = plt.subplots(figsize=quadratic_figsize(0.5, target=target))
     df['potTPertubation'] = df['potT'] - 300
     levels = np.arange(-0.05, 0.45+0.05, 0.05)
     levels = levels[levels!=0]
-    plot_contour(df=df, fig=fig, ax=ax, var='potTPertubation', num_sample=100, levels=levels, axis_off='on', colored=False,
-                linewidths=0.5)
+    plot_contour(df=df, fig=fig, ax=ax, var='potTPertubation', num_sample=500, levels=levels, axis_off='on', colored=False, linewidths=0.3)
     sns.despine(fig, ax)
     ax.set_xlabel('$x [\si{m}]$')
     ax.set_ylabel('$z [\si{m}]$')
     ax.text(100,100, r'$t = \SI{' + str(time) + r'}{\s}$')
-    fig.subplots_adjust(left=0.2, bottom=0.15)
-    fig.savefig(fig_path + f'{target}_two_bubbles_contour_t{time}.pdf', transparent=True)
+    fig.subplots_adjust(left=0.3, bottom=0.2)
+    fig.savefig(fig_path + '{}_two_bubbles_contour_t{}.pdf'.format(target, np.round(time)), transparent=True)
 
 def main():
     set_plot_defaults()
     fig_path = 'output/'
     plot_two_bubbles(fig_path=fig_path,
-                       solution_path='/home/lukas/Documents/MA-results/AMR/solution_cartesian-10.vtu',
-                       target='paper')
+                     solution_path='/work_fast/krenz/bubble_amr/solution_cartesian-10.vtu',
+                     target='paper')
 
 if __name__ == '__main__':
     main()

### 2019-04-17 src/plot_utils.py

@@ -99,9 +99,6 @@ def plot_contour(df, fig, ax, var, num_sample=500, levels=5, axis_off='off', col
 
     rr = griddata((x,y), r, (xx[None,:], yy[:,None]), method='cubic')
 
-    fs = figsize(scale=1.0)
-    size = (fs[0], fs[0])
-
     ax.axis(axis_off)
     
     ax.set_xlabel('$x$')
@@ -110,7 +107,8 @@ def plot_contour(df, fig, ax, var, num_sample=500, levels=5, axis_off='off', col
     if colored:
         c = ax.contour(xx, yy, rr, levels=levels, cmap='viridis', linewidths=linewidths)
     else:
-        c = ax.contour(xx, yy, rr, levels=levels, colors='black', linewidths=linewidths)
+        c = ax.contour(xx, yy, rr, levels=levels, colors='black', linewidths=linewidths,
+                       antialiased=True)
     
     return fig, ax, c
 

### 2019-04-18 src/plot_cavity.py
Change format strings in plot scripts

@@ -80,7 +80,7 @@ def plot_cavity(fig_path, solution_path, target):
     ax.set_xticks(xticks)
     ax.set_xticklabels(xticks)
 
-    fig.savefig(fig_path + f'{target}_lid_driven_cavity.pdf', transparent=True)
+    fig.savefig(fig_path + '{}_lid_driven_cavity.pdf'.format(target), transparent=True)
 
     # Contour
     fig, ax = plt.subplots(figsize=quadratic_figsize(scale=0.5, target=target))
@@ -112,13 +112,13 @@ def plot_cavity(fig_path, solution_path, target):
     ax.set_yticks(ticks)
     ax.set_yticklabels(ticks)
     # https://github.com/matplotlib/matplotlib/issues/8388 ?
-    fig.savefig(fig_path + f'{target}_lid_driven_cavity_stream.pdf', transparent=True)
+    fig.savefig(fig_path + '{}_lid_driven_cavity_stream.pdf'.format(target), transparent=True)
 
 def main():
     set_plot_defaults()
     fig_path='output/'
     plot_cavity(fig_path=fig_path,
-                solution_path='/home/lukas/Documents/MA-results/lid-driven-cavity/solution-3.vtu',
+                solution_path='/work_fast/krenz/cavity/solution-6.vtu',
                 target='paper')
         
 if __name__ == '__main__':

### 2019-04-18 src/plot_taylor_green.py

@@ -57,7 +57,7 @@ def plot_taylor_green(fig_path, solution_path, target, order=5):
         #ax.scatter(coord_cut, vel_approx_cut, c='black', marker=marker, s=1., lw=6, facecolors='none',
         #          label=f'$v_{coord_label} ({other})$')
         ax.plot(coord_cut, vel_approx_cut, 'o', c='black', marker=marker,lw=6, mfc='none',
-                label=f'$v_{coord_label} ({other})$')
+                label='$v_{coord_label} ({other})$'.format(coord_label=coord_label, other=other))
 
     ax.set_xlabel('$x, z$')
     ax.set_ylabel('$v_x(z), v_z(x)$')
@@ -66,7 +66,7 @@ def plot_taylor_green(fig_path, solution_path, target, order=5):
     fig.subplots_adjust(left=0.2, bottom=0.2, right=0.85)
     fig.legend(loc='upper right', bbox_to_anchor=(1.01,1), handletextpad=10e-100, )
     sns.despine(fig,ax)
-    fig.savefig(fig_path + f'{target}_taylor_green_vel.pdf', transparent=True)
+    fig.savefig(fig_path + '{target}_taylor_green_vel.pdf'.format(target=target), transparent=True)
 
     fig, ax = plt.subplots(figsize=figsize(scale=0.5, target=target))
     coord_cut, p_approx_cut, p_ana_cut, vel_approx_cut, vel_ana_cut = eval_cut(df, 'x', time, mu=0.01,
@@ -80,13 +80,13 @@ def plot_taylor_green(fig_path, solution_path, target, order=5):
     ax.set_xticklabels([0, '$\pi$', '$2\pi$'])
     sns.despine(fig,ax)
     fig.subplots_adjust(left=0.2, bottom=0.2)
-    fig.savefig(fig_path + f'{target}_taylor_green_pressure.pdf', transparent=True)
+    fig.savefig(fig_path + '{}_taylor_green_pressure.pdf'.format(target), transparent=True)
 
 def main():
     set_plot_defaults()
     fig_path='output/'
     plot_taylor_green(fig_path=fig_path,
-                      solution_path='/home/lukas/Documents/MA-results/taylor-green/solution-2.vtu',
+                      solution_path='/import/home/ga24dib/src/ExaHyPE-OptNS/ApplicationExamples/CompressibleNavierStokes/output/solution_cartesian-6.vtu',
                       target='paper')
         
 if __name__ == '__main__':

### 2019-04-25 writing/paper/paper.tex
Add more work on introduction.

@@
 \section{Introduction}
-The accurate simulation of clouds is crucial for detailed weather prediction.
-Because cloud dynamics can be approximated well with the compressible Navier-Stokes equations, this is the equation set of our choice.
-These equations are often space-discretized by higher order Galerkin methods, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
+Numerical weather prediction (\textsc{nwp}) contains processes of different spatio-temporal scales.
+An important part of future \textsc{nwp} models will be the the resolution of convective processes~\cite{bauer2015quiet}.
+This part requires both suitable physical models and effective computational realisations. 
+We focus on the simulation of cloud formation processes with simple benchmark scenarios~\cite{giraldo2008study}.
+These relatively small scale effects are well approximated with the compressible Navier-Stoks equations.
+They are often space-discretized by higher order Galerkin methods, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
 Even though all of these implementations use a discretization with a (theoretical) unlimited space-order, they use Runge-Kutta time integrators or semi-implicit methods.
@@
   In addition, we tailor the equation set to stratified flows with gravitational source term.
+  We want to emphasize here that we use a standard formulation of the Navier-Stokes equations as seen in the field of computational fluid mechanics and only use small modifcations of the governing equations, in contrast to a equation set that is tailored exactly to the application area.
 \item We present a general \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
@@
 \item We evaluate our implementation with standard \textsc{cfd} scenarios and atmospheric flows and inspect the effectiveness of our proposed \amr{}-criterion.
+  We thus inspect, whether our proposed general implementation can achieve results that are competitive with the state-of-the-art models that rely on heavily specified equations and numerics.
 \end{itemize}
@@
 }%
+
+\begin{equation}
+  \label{eq:ns-short}
+ \pdv{}{t} \bm{Q} + \divergence{\bm{F}(\bm{Q}, \gradient{\bm{Q}})} = \bm{S}(\bm{Q}) 
+\end{equation}
 The compressible Navier-Stokes equations in the conservative form are defined as% \pcref{eq:conservation-law-gradient}

### 2019-04-25 writing/paper/paper.tex
added abstract. changed first sentences.

@@
 \begin{document}
-\maketitle
+\maketitlet 
 \begin{abstract}
-
+  In the context of simulation of convective proceess for numerical weather prediction, we present an application of the compressible Navier Stokes equations on cloud formation processes.
+  While established methods have to use tailored numerics towards the specific simulation, our generic scheme shows competitive results for both classical cfd and hydrostatic scenarios.
+  Our scheme exploits an underlying parallelized implementation of the \aderdg{} method with dynamic adaptive mesh refinement. 
+  We improve our method by a PDE independent general refinement criterion, based on the local total variation of the numerical solution.
+  All together our method can be seen as a perfect candidate for large scale cloud simulation runs on current and future super computers.
 \begin{itemize}
@@
 \section{Introduction}
-Numerical weather prediction (\textsc{nwp}) contains processes of different spatio-temporal scales.
-An important part of future \textsc{nwp} models will be the the resolution of convective processes~\cite{bauer2015quiet}.
-This part requires both suitable physical models and effective computational realisations. 
+In this paper we address the resolution of convective processes in the context of numerical weather prediction (\textsc{nwp}), on modern super computer systems.
+The simulation of these process, with suitable physical models and on large scale clusters is expected to play an important role in future \textsc{nwp}~\cite{bauer2015quiet}.
+%% Numerical weather prediction (\textsc{nwp}) contains processes of different spatio-temporal scales.
+%% An important part of future \textsc{nwp} models will be the the resolution of convective processes~\cite{bauer2015quiet}.
+%% This part requires both suitable physical models and effective computational realisations. 
 We focus on the simulation of cloud formation processes with simple benchmark scenarios~\cite{giraldo2008study}.
-These relatively small scale effects are well approximated with the compressible Navier-Stoks equations.
-They are often space-discretized by higher order Galerkin methods, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
+These relatively small scale effects are well approximated with the compressible Navier-Stokes equations.
+The general approach is to use a space-discretized by higher order Galerkin method, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
+%%They are often space-discretized by higher order Galerkin methods, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
 Even though all of these implementations use a discretization with a (theoretical) unlimited space-order, they use Runge-Kutta time integrators or semi-implicit methods.

### 2019-04-27 writing/paper/paper.tex
Fix some small issues.

@@
 \begin{document}
-\maketitlet 
+\maketitle 
 \begin{abstract}
   In the context of simulation of convective proceess for numerical weather prediction, we present an application of the compressible Navier Stokes equations on cloud formation processes.
-  While established methods have to use tailored numerics towards the specific simulation, our generic scheme shows competitive results for both classical cfd and hydrostatic scenarios.
+  While established methods have to use tailored numerics towards the specific simulation, our generic scheme shows competitive results for both classical \textsc{cfd} and stratified scenarios.
   Our scheme exploits an underlying parallelized implementation of the \aderdg{} method with dynamic adaptive mesh refinement. 
-  We improve our method by a PDE independent general refinement criterion, based on the local total variation of the numerical solution.
+  We improve our method by a  \pde{} independent general refinement criterion, based on the local total variation of the numerical solution.
   All together our method can be seen as a perfect candidate for large scale cloud simulation runs on current and future super computers.
-\begin{itemize}
-\item Implementation of compressible Navier Stokes with a high-order \aderdg{}-method and a low order finite volume \muscl{}-scheme.
-\item Implementation in \exahypeengine{}, a scalable \pde{} framework.
-\item Outlier and total variation based adaptive mesh refinement that reduced number of grid cells drastically and preserves solution quality.
-\item Simulation of challenging flows over hydrostatic background atmosphere.
-\item Competitive results for both classical cfd scenarios and hydrostatic scenarios in two and three dimensions.
-\end{itemize}
+% \begin{itemize}
+% \item Implementation of compressible Navier Stokes with a high-order \aderdg{}-method and a low order finite volume \muscl{}-scheme.
+% \item Implementation in \exahypeengine{}, a scalable \pde{} framework.
+% \item Outlier and total variation based adaptive mesh refinement that reduced number of grid cells drastically and preserves solution quality.
+% \item Simulation of challenging flows over hydrostatic background atmosphere.
+% \item Competitive results for both classical cfd scenarios and hydrostatic scenarios in two and three dimensions.
+% \end{itemize}
 
-The abstract should briefly summarize the contents of the paper in
-150--250 words.
+%The abstract should briefly summarize the contents of the paper in
+%150--250 words.
 
@@
 \section{Introduction}
-In this paper we address the resolution of convective processes in the context of numerical weather prediction (\textsc{nwp}), on modern super computer systems.
+In this paper we address the resolution of convective processes in the context of numerical weather prediction (\textsc{nwp}) on modern super computer systems.
 The simulation of these process, with suitable physical models and on large scale clusters is expected to play an important role in future \textsc{nwp}~\cite{bauer2015quiet}.
@@
 We follow a different approach in this paper and use the \aderdg{} method of~\cite{dumbser2008unified} to simulate various computational fluid dynamics (\textsc{cfd}) scenarios with a focus on flows with stratified flows.
-\todo{LK: Ist hier stratified flows korrekt?}
-\todo{MB: viscosity ist unmotiviert ist.
-    Lieber noch so 10--15 Zeilen drüber schreiben.}
 Due to the viscous components of the Navier-Stokes equations, it is not straightforward to apply the \dg{} method.
@@
 
-We make the following contributions\todo{Feedback von MB: Besser hervorheben, warum diese Sachen interessant/neu sind.
-Dumbser macht in seinen NS-DG papern keine komplexen Source terme, keine hydrostatic flows, etc.
-}:
+We make the following contributions:
 \begin{itemize}%
@@
 We use an element local error estimate based on the total variation of the numerical solution. 
+\todo{Mention intuition, i.e.\ tvd stuff}
 Let $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ be a sufficiently smooth function that maps the discrete solution at a point $\bm{x}$ to an arbitrary indicator variable.
@@
 We compute the integral efficiently with Gaussian quadrature over the collocated quadrature points.
-\todo{LK: If using limiting, add sentence about tv computation for fv}
+%\todo{LK: If using limiting, add sentence about tv computation for fv}
 \newcommand{\mean}{\mu}%
@@
 A solution is considered to be invalid if it is a non-finite floating point number or if it is unphysical, i.e.\ if the pressure or density are not positive.
-\todo{LK: Mention dmp if using, mention tv-indicator for limiting if using}
+%\todo{LK: Mention dmp if using, mention tv-indicator for limiting if using}
 In case of an invalid solution, we recompute the timestep with a our \muscl{} finite volume method.\todo{Source for the fv method}
@@
 \todo{LK: Standard sentence is: This research was funded by the European Union’s Horizon 2020 Research and Innovation Programme under theproject ExaHyPE, grant no.  671698 (call FETHPC-1-2014).
-
+Special thanks goes to Dominic E.\ Charrier who provided help with the implementation in the \exahypeegine{}.
 Also LRZ?}

### 2019-05-02 src/dataset_utils.py
FIx some plots.

@@ -3,7 +3,7 @@ import vtk.util.numpy_support as vutil
 import numpy as np
 import pandas as pd
 
-def read_solution(path, order=None, size=10, limiting=False, advection=False):
+def read_solution(path, order=None, size=10, limiting=False, advection=False, dimensions=2):
     reader = vtk.vtkXMLUnstructuredGridReader()
     reader.SetFileName(path)
     reader.Update()
@@ -43,7 +43,7 @@ def read_solution(path, order=None, size=10, limiting=False, advection=False):
             rho, v_x, v_y, v_z, p, potT = np.longfloat(output.GetPointData().GetArray(0).GetTuple(i))
             data[i, :] = np.array([x, y, z, rho, v_x, v_y, v_z, p, potT])       
 
-    if number_of_coords == 2:
+    if number_of_coords == 2 and dimensions == 2:
         if advection:
             columns = ['x', 'y', 'z', 'rho', 'v_x', 'v_y', 'p', 'Z', 'potT', 'refinementStatus']
         else:

### 2019-05-02 src/plot_abc.py

@@ -37,7 +37,8 @@ def analytical_solution_abc(x,y,z,time,mu,var):
         return analytical_solution_w_abc(x,y,z,time,mu)
 
 def plot_abc(fig_path, solution_path, target, order=2):
-    df, time, order, dim, dx, n_points = read_solution(solution_path, order=order)
+    df, time, order, dim, dx, n_points = read_solution(solution_path, order=order, dimensions=3)
+    print(df.columns)
     time, order, dim, dx, n_points
     
     analytical_solution = analytical_solution_abc
@@ -50,7 +51,7 @@ def plot_abc(fig_path, solution_path, target, order=2):
     fig, axs = plt.subplots(ncols=3, figsize=fs, sharey=True)
 
     markers = ['o', 'x', 'X']
-    marker = markers[0]
+    marker = markers[1]
 
     for ax, coord in zip(axs, ['x', 'y', 'z']):
     #_, _, c = plot_contour(df_cut, fig, ax, var, levels=4, coords=others, num_sample=500,colored=False)
@@ -62,39 +63,39 @@ def plot_abc(fig_path, solution_path, target, order=2):
         if coord == 'x':
             ax.set_ylabel('$p$')
 
-        ax.set_xlabel(f'${coord}$')
+        ax.set_xlabel(str(coord))
         ax.set_xticks([-np.pi, 0, np.pi])
         ax.set_xticklabels(['$-\pi$', '$0$', '$\pi$'])
         sns.despine(fig,ax)
         fig.subplots_adjust(left=0.1, bottom=0.2, top=0.95, right=0.95)
 
-    fig.savefig(fig_path + f'{target}_abc_flow_pressure.pdf', transparent=True)
+    fig.savefig(fig_path + '{target}_abc_flow_pressure.pdf'.format(target=target), transparent=True)
 
-    fig, axs = plt.subplots(ncols=3, figsize=figsize(1.0, target=target), sharey=True)
+    fig, axs = plt.subplots(ncols=3, figsize=figsize(0.5, target=target), sharey=True)
 
     for ax, coord, vel_var in zip(axs, ['x', 'y', 'z'], ['v', 'v', 'v']):
     #_, _, c = plot_contour(df_cut, fig, ax, var, levels=4, coords=others, num_sample=500,colored=False)
         coord_cut, p_approx_cut, p_ana_cut, vel_approx_cut, vel_ana_cut = eval_cut(df, coord, time, mu=0.01,
                                                                         analytical_solution=analytical_solution,
[…]

### 2019-05-02 src/plot_cosine_bubble.py

@@ -24,7 +24,7 @@ def plot_cosine_bubble(fig_path, solution_path, target, order=4):
     ax.set_ylabel("$\Theta\'$")
     fig.subplots_adjust(left=0.2)
 
-    fig.savefig(fig_path + f'{target}_cosine_bubble_pertubation.pdf', transparent=True)
+    fig.savefig(fig_path + '{target}_cosine_bubble_pertubation.pdf'.format(target=target), transparent=True)
 
     fig, ax = plt.subplots(figsize=quadratic_figsize(0.5, target=target))
     df['potTPertubation'] = df['potT'] - 300
@@ -43,14 +43,14 @@ def plot_cosine_bubble(fig_path, solution_path, target, order=4):
     cb.locator = ticker.MaxNLocator(nbins=5)
     cb.update_ticks()
 
-    fig.savefig(fig_path + f'{target}_cosine_bubble_contour_t700.pdf', transparent=True)
+    fig.savefig(fig_path + '{target}_cosine_bubble_contour_t700.pdf'.format(target=target), transparent=True)
 
 
 def main():
     set_plot_defaults()
     fig_path = 'output/'
     plot_cosine_bubble(fig_path=fig_path,
-                       solution_path='/home/lukas/tmp/benchmark_results_cosine/solution_cartesian-10.vtu',
+                       solution_path='/work_fast/krenz/cosine_bubble_opt/solution_cart-9.vtu',
                        target='paper')
 
 if __name__ == '__main__':

### 2019-05-02 src/plot_taylor_green.py

@@ -86,7 +86,7 @@ def main():
     set_plot_defaults()
     fig_path='output/'
     plot_taylor_green(fig_path=fig_path,
-                      solution_path='/import/home/ga24dib/src/ExaHyPE-OptNS/ApplicationExamples/CompressibleNavierStokes/output/solution_cartesian-6.vtu',
+                      solution_path='/work_fast/krenz/taylor_green/solution_cartesian-5.vtu',
                       target='paper')
         
 if __name__ == '__main__':

### 2019-05-02 writing/paper/paper.tex
Further work on paper.

@@
 \end{equation}
-i.e.\ a state, where the pressure gradient is exactly in balance with the gravitational source term.
+i.e.\ a state, where the pressure gradient is exactly in balance with the gravitational source term $\source[\Qj] = - \bm{k} \Qrho g$.
+The vector $\bm{k}$ is the unit vector pointing in $z$-direction.
 The momentum equation is dominated by the background flow in this case.
@@
 We use an element local error estimate based on the total variation of the numerical solution. 
-\todo{Mention intuition, i.e.\ tvd stuff}
+We use the fact that the total variation of a numerical solution is a perfect indicator for edges of a wavefront.
 Let $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ be a sufficiently smooth function that maps the discrete solution at a point $\bm{x}$ to an arbitrary indicator variable.
@@
 with probability $\mathbb{P}$ guarantees that we neither mark all cells for refinement nor for erasement.
-\todo{LR: Was gibt es an compressible NS mit dynamic AMR, wie unterscheiden wir uns im Refinement Kriterium?}
 This inequality holds for arbitrary distributions under the weak assumption that they have a finite mean $\mu$ and a finite standard deviation $\sigma$~\cite{wasserman2004all}.
 Note that subcells are coarsened only if all subcells belonging to the coarse cell are marked for erasion.
+In contrast to already published criteria which are either designed solely for the simulation of clouds~\cite{muller2010adaptive} or computationally expensive~\cite{fambri2017space}, our criterion works for arbitrary \pde{}s and yet, is easy to compute and intuitive.
 
@@
 We use a diverse mix of benchmarking scenarios that consist of standard \textsc{cfd} scenarios and atmospheric flows.
+
+For the \textsc{cfd} scenarios, we use the following constants of fluids:
+\begin{equation}
+  \gamma = 1.4, \quad \Pr = 0.7, \quad c_v = 1.0.
+\end{equation}
 
@@
 \end{align}
-The constant $C = \nicefrac{100}{\gamma}$ governs the speed of sound and thus the Mach number~\cite{dumbser2016high}, the viscosity is set to $\mu = 0.1$.
-We use a domain of size $(\SI{2 \pi}{\m} \times \SI{2 \pi}{\m})$ and impose the analytical solution at the boundary\todo{tEnd, mach=0.1}.
+The constant $C = \nicefrac{100}{\gamma}$ governs the speed of sound and thus the Mach number $\text{Ma} = 0.1$~\cite{dumbser2016high}, the viscosity is set to $\mu = 0.1$.
+We use a domain of size $(\SI{2 \pi}{\m} \times \SI{2 \pi}{\m})$ and impose the analytical solution at the boundary.
+A comparison at time $t = 1.0$ of the analytical solution for the pressure with our approximation (figure xxx) shows an excellent agreement.\todo{fig, check time, fix order/cells.}
+We used an \aderdg{}-scheme of order $5$ with a grid of $25^2$ cells.
 
-We use the Arnold-Beltrami-Childress (\textsc{abc}) flow as a simple three-dimensional flow~\cite{tavelli2016staggered}.
-It also has an exact solution in the domain of \( \left[ -\SI{\pi}{\m}, \SI{\pi}{\m} \right]^3 \) under the assumption of incompressibility
+The Arnold-Beltrami-Childress (\textsc{abc}) flow is similar to the Taylor-Green vortex but posses an analyitcal solution fir three-dimensions as well~\cite{tavelli2016staggered}.
+It is defined in the domain \( \left[ -\SI{\pi}{\m}, \SI{\pi}{\m} \right]^3 \) as
 \begin{align}
@@
 \end{align}
+again under the assumption of incompressibility.
 The constant $C = \nicefrac{100}{\gamma}$ is chosen as before.
-We use a viscosity of $\mu = 0.01$ and analytical boundary conditions\todo{tEnd}.
+We use a viscosity of $\mu = 0.01$ and analytical boundary conditions.
+Figure xxx show a good agreement between the analytical solution and our approximation with an \aderdg{}-scheme of order $2$ with a mesh consisting of $27^3$ cells at time $t = \SI{0.1}{\s}$\todo{Figure}.
 
@@
 The simulation runs for $\SI{10}{\s}$
+Again, our results have an excellent agreement with the reference solution of~\cite{ghia1982high}.
+We used an \aderdg{}-method of order $3$ with a mesh of size $27^2$\todo{check!}.
 
-Our atmospheric flow scenarios are described in terms of the potential energy
+Our stratified flow scenarios are described in terms of the potential energy
 \begin{equation}
@@
 The background atmosphere is then perturbed.
-\todo{LK: Mention bcs briefly?}
 Let
@@
   \label{eq:radius}
-  r^2 = (x - x_0)^2 + (z - z_0)^2
+  r^2 = \Vert \bm{x} - \bm{x_c} \Vert_2 %(x - x_0)^2 + (z - z_0)^2
 \end{equation}
-denote the difference between spatial positions $x,z$ and the center of a bubble $x_c, z_c$\todo{3D}.
+denote the euclidian distance between the spatial positions $\bm{x} = x, z$ and the center of a bubble $\bm{x_c} = x_c, z_c$.
+In case of three-dimensional scenarios the vectors $\bm{x}$ and $\bm{x_c}$ also contain a y coordinate.
 For our first scenario, the cosine bubble, we use a pertubation of the form
-% \begin{equation}
-%   \label{eq:cos-pertubation-alt}
-%   \pertubationPotT = 
-%     \nicefrac{A}{2} \left( 1 + \cos(\pi r) \right) \left[ r \leq a \right]
-% \end{equation}
 \begin{align}
@@
 \end{equation}
-We use a constant viscosity of $\mu = 0.1$\todo{tend = 400 for 3d and 600 for 2d}.
+For the three-dimensional bubble, we set $y_c = x_c = \SI{500}{\m}$ and lower the bubble to $z_c = \SI{260}{\m}$
+We use a constant viscosity of $\mu = 0.1$ and a simulation time of $\SI{400}{\s}$ for 3d and $\SI{600}{\s}$ for 2d.
+
 For our second scenario, the colliding bubbles, we use perturbations of the form
@@
 Similar to~\cite{muller2010adaptive} and to the previous scenario, we use a constant viscosity of $\mu = 0.1$ to regularize the solution.
-To ensure that the atmosphere stays in hydrostatic balance~\cite{giraldo2008study}, we need to impose the viscous heat flux
+To ensure that the atmosphere stays in hydrostatic balance, we need to impose the viscous heat flux
 \begin{equation}
@@
 \end{equation}
-where $\overline{T}(z)$ is the background temperature at position $z$ which can be computed from \cref{eq:hydrostatic-balance,eq:eos}.
+where $\overline{T}(z)$ is the background temperature at position $z$ which can be computed from \cref{eq:hydrostatic-balance,eq:eos}~\cite{giraldo2008study}.
 We furthermore set the density and energy at the boundary such that it corresponds to the background atmosphere.
@@
 % We compare this with a simulation obtained by a fully refined grid.
-
-Show following results:
-\begin{itemize}
-\item Simple cfd: Taylor Green, ABC, Lid Driven Cavity
-\item Two Bubbles with \amr{} (2 levels if possible) and no \amr{} (comparison)
-\item Two Bubbles (Euler eqs, FV)  
-\item Two Bubbles with limiting instead of visc.\ if working  
-\item Cosine bubble in 2D and possibly 3D, if working
-\end{itemize}
 
@@
 \todo{LK: Standard sentence is: This research was funded by the European Union’s Horizon 2020 Research and Innovation Programme under theproject ExaHyPE, grant no.  671698 (call FETHPC-1-2014).
-Special thanks goes to Dominic E.\ Charrier who provided help with the implementation in the \exahypeegine{}.
+Special thanks goes to Dominic E.\ Charrier who provided help with the implementation in the %\exahypeegine{}.
 Also LRZ?}

### 2019-05-02 writing/paper/paper.tex
More work on paper.

@@
 \usepackage{caption}
+\usepackage{subcaption}
 \usepackage{xparse} % for NewDocumentCommand
@@
 This has been shown to work well for the simulation of cloud dynamics~\cite{muller2010adaptive}.
-%\todo{Einordnung, Kontext zu giraldo, etc$\ldots$}
 %Insert references to Giraldo SE/DG bubbles~\cite{giraldo2008study}, 3D bubbles~\cite{giraldo2013implicit,kelly2012continuous}, bubble amr (müller~\cite{muller2010adaptive}).
@@
 
-We make the following contributions:
+We make the following contributions:%
 \begin{itemize}%
@@
 \end{itemize}
-
+%
 \section{Equation Set}
@@
 }%
-
-\begin{equation}
-  \label{eq:ns-short}
- \pdv{}{t} \bm{Q} + \divergence{\bm{F}(\bm{Q}, \gradient{\bm{Q}})} = \bm{S}(\bm{Q}) 
-\end{equation}
+% \begin{equation}
+%   \label{eq:ns-short}
+%  \pdv{}{t} \bm{Q} + \divergence{\bm{F}(\bm{Q}, \gradient{\bm{Q}})} = \bm{S}(\bm{Q}) 
+% \end{equation}
 The compressible Navier-Stokes equations in the conservative form are defined as% \pcref{eq:conservation-law-gradient}
@@
 In contrast to this, we use the true compressible Navier-Stokes equations with minimal modifications.
-\todo{Mention differences in splitting methods}
 \section{Numerics}
-
 \todo{LR: Hier würde ich noch ein paar einleitende Worte hinzufügen}
-\todo{LK: CFL? Riemannsolver (no gradients)}
 We use an \aderdg{}-scheme and a \muscl{} finite volume method.
@@
 We use a Rusanov-style flux that is adapted to \pde{}s with viscous terms~\cite{gassner2008discontinuous,fambri2017space}.
-The finite volume scheme is stabilized with the van Albada limiter\todo{LK: Which one is best? Cite vanalbada}.
+The finite volume scheme is stabilized with the van Albada limiter\todo{Cite vanalbada}.
 
@@
 We compute the integral efficiently with Gaussian quadrature over the collocated quadrature points.
-%\todo{LK: If using limiting, add sentence about tv computation for fv}
 \newcommand{\mean}{\mu}%
@@
 \end{equation}
-The parameters $\Trefine > \Tdelete$ can be chosen freely.
+The parameters $\Trefine > \Tdelete$ can be chosen freely\todo{LK: Do we need the ineq.?}.
 Chebyshev's inequality
@@
 
-We use a \muscl{} based finite volume limiting as proposed in~\cite{dumbser2016simple}.
-Briefly, we first compute a candidate solution with our \aderdg{}-scheme and check whether it is valid.
-A solution is considered to be invalid if it is a non-finite floating point number or if it is unphysical, i.e.\ if the pressure or density are not positive.
-%\todo{LK: Mention dmp if using, mention tv-indicator for limiting if using}
-In case of an invalid solution, we recompute the timestep with a our \muscl{} finite volume method.\todo{Source for the fv method}
-
 \section{Results}
@@
 
-For the \textsc{cfd} scenarios, we use the following constants of fluids:
+For the standard \textsc{cfd} testing scenarios, we use the following constants of fluids:
 \begin{equation}
@@
 \end{equation}
-
-\todo{LK: Constants of fluids?}
 A simple scenario is the Taylor-Green vortex.
@@
 We use a domain of size $(\SI{2 \pi}{\m} \times \SI{2 \pi}{\m})$ and impose the analytical solution at the boundary.
-A comparison at time $t = 1.0$ of the analytical solution for the pressure with our approximation (figure xxx) shows an excellent agreement.\todo{fig, check time, fix order/cells.}
+A comparison at time $t = 10.0$ of the analytical solution for the pressure with our approximation (figure xxx) shows an excellent agreement.\todo{fig, check time, fix order/cells.}
 We used an \aderdg{}-scheme of order $5$ with a grid of $25^2$ cells.
 
-The Arnold-Beltrami-Childress (\textsc{abc}) flow is similar to the Taylor-Green vortex but posses an analyitcal solution fir three-dimensions as well~\cite{tavelli2016staggered}.
+\begin{figure}[htb]
+  \centering
+  \begin{subfigure}[t]{0.5\textwidth}
+    \centering
+    \includegraphics{paper_lid_driven_cavity}
+    \caption{\label{fig:cavity-flow}Our approximation (lines) of the lid-driven cavity flow vs.\ reference solution (markers) of~\cite{ghia1982high}.}
+  \end{subfigure}~%
+  \begin{subfigure}[t]{0.5\textwidth}
+    \centering
+    \includegraphics{paper_abc_flow_velocity}
+    \caption{\label{fig:abc-flow}\textsc{abc}-flow. We show the velocity in $x$-direction for slices through the domain, where all but the mentioned coordinates are held constant at a value of zero.
+    The analytical solution is represented by lines, the numerical results by markers.}
+  \end{subfigure}
+  \caption{\textsc{cfd} scenarios}
+  \label{fig:cdf-results}
+\end{figure}
+
+The Arnold-Beltrami-Childress (\textsc{abc}) flow is similar to the Taylor-Green vortex but posesses an analytical solution for three-dimensions as well~\cite{tavelli2016staggered}.
 It is defined in the domain \( \left[ -\SI{\pi}{\m}, \SI{\pi}{\m} \right]^3 \) as
@@
 We use a viscosity of $\mu = 0.01$ and analytical boundary conditions.
-Figure xxx show a good agreement between the analytical solution and our approximation with an \aderdg{}-scheme of order $2$ with a mesh consisting of $27^3$ cells at time $t = \SI{0.1}{\s}$\todo{Figure}.
+Our results (\cref{fig:abc-flow}) show a good agreement between the analytical solution and our approximation with an \aderdg{}-scheme of order $3$ with a mesh consisting of $27^3$ cells at time $t = \SI{0.1}{\s}$.
 
@@
 The simulation runs for $\SI{10}{\s}$
-Again, our results have an excellent agreement with the reference solution of~\cite{ghia1982high}.
-We used an \aderdg{}-method of order $3$ with a mesh of size $27^2$\todo{check!}.
+Again, our results (\cref{fig:cavity-flow}) have an excellent agreement with the reference solution of~\cite{ghia1982high}.
+We used an \aderdg{}-method of order $3$ with a mesh of size $27^2$.
 
-Our stratified flow scenarios are described in terms of the potential energy
+Our stratified flow scenarios are described in terms of the potential temperature
 \begin{equation}
@@
 The background atmosphere is then perturbed.
+We set the density and energy at the boundary such that it corresponds to the background atmosphere.
+Furthermore, to ensure that the atmosphere stays in hydrostatic balance, we need to impose the viscous heat flux
+\begin{equation}
+  \label{eq:atmosphere-bc}
+  \viscFlux_{\QE} = \kappa \pdv{\overline{T}}{z}.% =
+%\kappa \frac{R \overline{\theta} \left(\frac{\overline{p}{\left (z \right )}}{p_{0}}\right)^{\frac{R}{c_{p}}} \frac{d}{d z} \overline{p}{\left (z \right )}}{c_{p} \overline{p}{\left (z \right )}}.
+\end{equation}
+at the boundary.
+In this equation, $\overline{T}(z)$ is the background temperature at position $z$, which can be computed from \cref{eq:hydrostatic-balance,eq:eos}~\cite{giraldo2008study}.
+
 Let
@@
 \end{equation}
-denote the euclidian distance between the spatial positions $\bm{x} = x, z$ and the center of a bubble $\bm{x_c} = x_c, z_c$.
+denote the Euclidian distance between the spatial positions $\bm{x} = x, z$ and the center of a bubble $\bm{x_c} = x_c, z_c$.
 In case of three-dimensional scenarios the vectors $\bm{x}$ and $\bm{x_c}$ also contain a y coordinate.
@@
 where $A$ denotes the maximal perturbation and $a$ is the size of the bubble.
-We use the constants\todo{3d bubble is higher}
+We use the constants
 \begin{equation}\label{eq:cosine-bubble}
@@
 \end{equation}
-For the three-dimensional bubble, we set $y_c = x_c = \SI{500}{\m}$ and lower the bubble to $z_c = \SI{260}{\m}$
-We use a constant viscosity of $\mu = 0.1$ and a simulation time of $\SI{400}{\s}$ for 3d and $\SI{600}{\s}$ for 2d.
+For the three-dimensional bubble, we set $y_c = x_c = \SI{500}{\m}$ and lower the bubble to $z_c = \SI{260}{\m}$.
+We use a constant viscosity of $\mu = 0.01$ and a simulation time of $\SI{400}{\s}$ for 3D and $\SI{600}{\s}$ for 2D\todo{viscosity for 3D?}.
+We specialize the \amr{}-criterion~\pcref{eq:refinement-criterion} to our stratified flows by using the potential temperature.
 
-For our second scenario, the colliding bubbles, we use perturbations of the form
+\begin{figure}[htb]
+  \centering
+  \begin{subfigure}[t]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{paper_cosine_bubble}
+    \caption{2D Cosine Bubble}
+  \end{subfigure}~%
+  \begin{subfigure}[t]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{paper_cosine_bubble}
+    \caption{3D Cosine Bubble}
+  \end{subfigure}
+  \caption{Cosine Bubble Scenarios}
+  \label{fig:cosine-bubbles-results}
+\end{figure}
+
+For our second scenario, the colliding bubbles~\cite{muller2010adaptive}, we use perturbations of the form
 \begin{equation}
@@
 \end{equation}
-Similar to~\cite{muller2010adaptive} and to the previous scenario, we use a constant viscosity of $\mu = 0.1$ to regularize the solution.
-To ensure that the atmosphere stays in hydrostatic balance, we need to impose the viscous heat flux
-\begin{equation}
-  \label{eq:atmosphere-bc}
-  \viscFlux_{\QE} = \kappa \pdv{\overline{T}}{z}.% =
-%\kappa \frac{R \overline{\theta} \left(\frac{\overline{p}{\left (z \right )}}{p_{0}}\right)^{\frac{R}{c_{p}}} \frac{d}{d z} \overline{p}{\left (z \right )}}{c_{p} \overline{p}{\left (z \right )}}.
-\end{equation}
-where $\overline{T}(z)$ is the background temperature at position $z$ which can be computed from \cref{eq:hydrostatic-balance,eq:eos}~\cite{giraldo2008study}.
-We furthermore set the density and energy at the boundary such that it corresponds to the background atmosphere.
+Similar to~\cite{muller2010adaptive} and to the previous scenario, we use a constant viscosity of $\mu = 0.01$ to regularize the solution\todo{We use lower visc!}.
+We ran this scenario twice, firstly without \amr{} and a mesh of size $\SI{1000/81}{\m} = \SI{12.35}{\m}$.
+For the second run we used \amr{} with two adaptive refinement levels and parameters $\Trefine = 2.5$ and $\Tdelete = -0.5$.
+This resulted in a mesh with cell sizes lengths of ca. $\SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.34}{\m}$ up to.
+The resulting mesh can be observed in \cref{fig:two-bubbles-ader}.
+We observed that even though both results are nearly identical, the \amr{} run managed to use only 1953 cells, instead of 6561 cells for the fully refined solution. 
+% points: 70308, 23619
+We further want to emphasize that our \amr{}-criterion is able to accurately track the position of the edges of cloud instead of only its position.
+This is the main advantage of our gradient-based method in contrast to methods working directly with the value of the solution, as for example~\cite{muller2010adaptive}.
+Overall, our result for this benchmark shows an excellent agreement to the previous solutions of~\cite{muller2010adaptive,giraldo2008study}\todo{Is coll.\ bubble contained in se study?}.
 
-% We start with a coarse mesh that is then subdivided up to two times in an adaptive manner.
-% For this we use the criterion of \cref{eq:refinement-criterion} with parameters xxx and xxx.
-% We compare this with a simulation obtained by a fully refined grid.
+In addition, we simulated the same scenario with our \muscl{} method, using $3^2$ patches with $80^2$ finite volume cells each~\todo{check}.
+As we use limiting, we do not need any viscosity.
+The results of this method (\cref{fig:two-bubbles-fv}) also agree with the reference.
+Note that the numerical dissapitivity of the finite volume scheme has a smoothing effect that is similar to the smoothing caused by viscosity.
+\begin{figure}[htb]
+  \centering
+  \begin{subfigure}[t]{0.8\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{paper_two_bubbles}
+    \caption{\label{fig:two-bubbles-ader}Colliding Bubbles \aderdg{}}
+  \end{subfigure}~%
+  \begin{subfigure}[t]{0.5\textwidth}
+    \centering
+    \includegraphics{paper_lid_driven_cavity}
+    \caption{\label{fig:two-bubbles-fv}Colliding Bubbles \muscl{}}
+  \end{subfigure}
+  \caption{Cosine Bubble Scenarios}
+  \label{fig:two-bubbles-results}
+\end{figure}
 
 \section{Conclusion}
-We presented our implementation of a \muscl{}-limited \aderdg{}-scheme with \amr{} for the Navier-Stokes equations.
+We presented our implementation of an \aderdg{}-method and a \muscl{}-scheme with \amr{} for the Navier-Stokes equations.
 Our implementation is capable of simulating different scenarios:
 \begin{itemize}
-  % Convergence test?
 \item We evaluated our method for standard \textsc{cfd} scenarios and achieved competitive results for all used scenarios.
@@
 Lukas Krenz was funded by ChEESE (823844), Leonhard Rannabauer was funded by ExaHyPE (671698).
-\todo{LK: Standard sentence is: This research was funded by the European Union’s Horizon 2020 Research and Innovation Programme under theproject ExaHyPE, grant no.  671698 (call FETHPC-1-2014).
+\todo{LK: Standard sentence is: This research was funded by the European Union’s Horizon 2020 Research and Innovation Programme under the project ExaHyPE, grant no.  671698 (call FETHPC-1-2014).
 Special thanks goes to Dominic E.\ Charrier who provided help with the implementation in the %\exahypeegine{}.

### 2019-05-03 writing/paper/paper.tex
Edited introduction

--- 2019-05-02 writing/paper/paper.tex
@@
 \begin{abstract}
-  In the context of simulation of convective proceess for numerical weather prediction, we present an application of the compressible Navier Stokes equations on cloud formation processes.
-  While established methods have to use tailored numerics towards the specific simulation, our generic scheme shows competitive results for both classical \textsc{cfd} and stratified scenarios.
-  Our scheme exploits an underlying parallelized implementation of the \aderdg{} method with dynamic adaptive mesh refinement. 
+  We present an application of the compressible Navier Stokes equations for cloud formation processes.
+  The scheme exploits an underlying parallelized implementation of the \aderdg{} method with dynamic adaptive mesh refinement. 
   We improve our method by a \pde{} independent general refinement criterion, based on the local total variation of the numerical solution.
+  Our generic scheme shows competitive results for both classical \textsc{cfd} and stratified scenarios.
+  While established methods use tailored numerics towards the specific simulation, our scheme works scenario independent.
   All together our method can be seen as a perfect candidate for large scale cloud simulation runs on current and future super computers.
@@
 \section{Introduction}
-In this paper we address the resolution of convective processes in the context of numerical weather prediction (\textsc{nwp}) on modern super computer systems.
-The simulation of these process, with suitable physical models and on large scale clusters is expected to play an important role in future \textsc{nwp}~\cite{bauer2015quiet}.
+In this paper we address the resolution of basic cloud formation processes on modern super computer systems.
+%%of convective processes in the context of numerical weather prediction (\textsc{nwp}) on modern super computer systems.
+The simulation of cloud formations, as part of convective processes, is expected to play an important role in future numerical weather prediction~\cite{bauer2015quiet}.
 %% Numerical weather prediction (\textsc{nwp}) contains processes of different spatio-temporal scales.
 %% An important part of future \textsc{nwp} models will be the the resolution of convective processes~\cite{bauer2015quiet}.
-%% This part requires both suitable physical models and effective computational realisations. 
-We focus on the simulation of cloud formation processes with simple benchmark scenarios~\cite{giraldo2008study}.
+This requires both suitable physical models and effective computational realisations. 
+Here we focus on the simulation of simple benchmark scenarios~\cite{giraldo2008study}.
 These relatively small scale effects are well approximated with the compressible Navier-Stokes equations.
-The general approach is to use a space-discretized by higher order Galerkin method, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
+We use the \aderdg{} method of~\cite{dumbser2008unified}, which allows us to simulate the Naview-Stokes equations with a space-time-discretization of arbitrary high order.
+In contrast to Runge-Kutta time integrators or semi-implicit methods, an increase of the order of \aderdg{} only results in larger computational kernels and does not affect the complexity of the scheme.
+Additionally \aderdg{} is a communication avoiding scheme and reduces the overhead on larger scale.
+We see our scheme in the regime of already established methods for cloud simulations, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
+%%The general approach is to use a space-discretized by higher order Galerkin method, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
 %%They are often space-discretized by higher order Galerkin methods, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
-Even though all of these implementations use a discretization with a (theoretical) unlimited space-order, they use Runge-Kutta time integrators or semi-implicit methods.
-It is well known that Runge-Kutta methods become more ineffecient for very high orders.
-Furthermore, they and the implicit methods are more communication-intensive and thus require a larger overhead and are more complicated to scale.
+%%Even though all of these implementations use a discretization with a (theoretical) unlimited space-order, they use Runge-Kutta time integrators or semi-implicit methods.
+%%It is well known that Runge-Kutta methods become more ineffecient for very high orders.
+%%Furthermore, they and the implicit methods are more communication-intensive and thus require a larger overhead and are more complicated to scale.
+%%We follow a different approach in this paper and use the \aderdg{} method of~\cite{dumbser2008unified} to simulate various computational fluid dynamics (\textsc{cfd}) scenarios with a focus on flows with stratified flows.
 
-We follow a different approach in this paper and use the \aderdg{} method of~\cite{dumbser2008unified} to simulate various computational fluid dynamics (\textsc{cfd}) scenarios with a focus on flows with stratified flows.
 Due to the viscous components of the Navier-Stokes equations, it is not straightforward to apply the \dg{} method.

### 2019-05-03 writing/paper/paper.tex
Improve results chapter.

@@
 Here we focus on the simulation of simple benchmark scenarios~\cite{giraldo2008study}.
-These relatively small scale effects are well approximated with the compressible Navier-Stokes equations.
+They contain relatively small scale effects which are well approximated with the compressible Navier-Stokes equations.
 We use the \aderdg{} method of~\cite{dumbser2008unified}, which allows us to simulate the Naview-Stokes equations with a space-time-discretization of arbitrary high order.
 In contrast to Runge-Kutta time integrators or semi-implicit methods, an increase of the order of \aderdg{} only results in larger computational kernels and does not affect the complexity of the scheme.
-Additionally \aderdg{} is a communication avoiding scheme and reduces the overhead on larger scale.
+Additionally, \aderdg{} is a communication avoiding scheme and reduces the overhead on larger scale.
 We see our scheme in the regime of already established methods for cloud simulations, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
@@
 We use a Rusanov-style flux that is adapted to \pde{}s with viscous terms~\cite{gassner2008discontinuous,fambri2017space}.
-The finite volume scheme is stabilized with the van Albada limiter\todo{Cite vanalbada}.
+The finite volume scheme is stabilized with the van Albada limiter~\cite{van1997comparative}.
 
@@
     \centering
-    \includegraphics{paper_abc_flow_velocity}
-    \caption{\label{fig:abc-flow}\textsc{abc}-flow. We show the velocity in $x$-direction for slices through the domain, where all but the mentioned coordinates are held constant at a value of zero.
-    The analytical solution is represented by lines, the numerical results by markers.}
+    \includegraphics{paper_taylor_green_vel}
+    \caption{\label{fig:taylor-green}Taylor green, velocity slices.}
+
+    %\includegraphics{paper_abc_flow_velocity}
+    %\caption{\label{fig:abc-flow}\textsc{abc}-flow. We show the velocity in $x$-direction for slices through the domain, where all but the mentioned coordinates are held constant at a value of zero.
+    %The analytical solution is represented by lines, the numerical results by markers.}
   \end{subfigure}
-  \caption{\textsc{cfd} scenarios}
+  \caption{Two dimensional \textsc{cfd} scenarios}
   \label{fig:cdf-results}
@@
 Our results (\cref{fig:abc-flow}) show a good agreement between the analytical solution and our approximation with an \aderdg{}-scheme of order $3$ with a mesh consisting of $27^3$ cells at time $t = \SI{0.1}{\s}$.
+
+\begin{figure}[tb]
+\centering
+\begin{minipage}{.5\textwidth}
+  \centering
+    \includegraphics{paper_abc_flow_velocity}
+    \captionof{figure}{\label{fig:abc-flow}Our approximation (lines) of the lid-driven cavity flow vs.\ reference solution (markers) of~\cite{ghia1982high}.}
+\end{minipage}%
+\begin{minipage}{.5\textwidth}
+  \centering
+    \includegraphics[width=\textwidth]{paper_two_bubbles_fv}
+    \captionof{figure}{\label{fig:two-bubbles-fv}%
+    Colliding bubbles with \muscl{}}
+\end{minipage}
+\end{figure}
 
@@
 In case of three-dimensional scenarios the vectors $\bm{x}$ and $\bm{x_c}$ also contain a y coordinate.
-For our first scenario, the cosine bubble, we use a pertubation of the form
-\begin{align}
-  \label{eq:cos-pertubation}
-  \pertubationPotT &= \begin{cases}
-    \nicefrac{A}{2} \left[ 1 + \cos(\pi r) \right] & r \leq a, \\
-    0 & r > a,
-    \end{cases}
-\end{align}
-where $A$ denotes the maximal perturbation and $a$ is the size of the bubble.
-We use the constants
-\begin{equation}\label{eq:cosine-bubble}
-  A = \SI{0.5}{\K} \quad a = \SI{250}{\m} \quad x_c = \SI{500}{\m} \quad z_c = \SI{350}{\m}.
-\end{equation}
-For the three-dimensional bubble, we set $y_c = x_c = \SI{500}{\m}$ and lower the bubble to $z_c = \SI{260}{\m}$.
-We use a constant viscosity of $\mu = 0.01$ and a simulation time of $\SI{400}{\s}$ for 3D and $\SI{600}{\s}$ for 2D\todo{viscosity for 3D?}.
-We specialize the \amr{}-criterion~\pcref{eq:refinement-criterion} to our stratified flows by using the potential temperature.
 
-\begin{figure}[htb]
-  \centering
-  \begin{subfigure}[t]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{paper_cosine_bubble}
-    \caption{2D Cosine Bubble}
-  \end{subfigure}~%
-  \begin{subfigure}[t]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{paper_cosine_bubble}
-    \caption{3D Cosine Bubble}
-  \end{subfigure}
-  \caption{Cosine Bubble Scenarios}
-  \label{fig:cosine-bubbles-results}
-\end{figure}
-
-For our second scenario, the colliding bubbles~\cite{muller2010adaptive}, we use perturbations of the form
+Our first scenario is the colliding bubbles scenario~\cite{muller2010adaptive}.
+We use perturbations of the form
 \begin{equation}
@@
 \end{equation}
-Similar to~\cite{muller2010adaptive} and to the previous scenario, we use a constant viscosity of $\mu = 0.01$ to regularize the solution\todo{We use lower visc!}.
+Similar to~\cite{muller2010adaptive}, we use a constant viscosity of $\mu = 0.01$ to regularize the solution.
+Note that we use a different implementation of viscosity than~\cite{muller2010adaptive}.
+Hence, it is difficult to compare the parametrization directly.
 We ran this scenario twice, firstly without \amr{} and a mesh of size $\SI{1000/81}{\m} = \SI{12.35}{\m}$.
 For the second run we used \amr{} with two adaptive refinement levels and parameters $\Trefine = 2.5$ and $\Tdelete = -0.5$.
-This resulted in a mesh with cell sizes lengths of ca. $\SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.34}{\m}$ up to.
+We specialize the \amr{}-criterion~\pcref{eq:refinement-criterion} to our stratified flows by using the potential temperature.
+This resulted in a mesh with cell sizes lengths of ca. $\SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.34}{\m}$.
 The resulting mesh can be observed in \cref{fig:two-bubbles-ader}.
@@
 Note that the numerical dissapitivity of the finite volume scheme has a smoothing effect that is similar to the smoothing caused by viscosity.
+
+For our second scenario, the cosine bubble, we use a pertubation of the form
+\begin{align}
+  \label{eq:cos-pertubation}
+  \pertubationPotT &= \begin{cases}
+    \nicefrac{A}{2} \left[ 1 + \cos(\pi r) \right] & r \leq a, \\
+    0 & r > a,
+    \end{cases}
+\end{align}
+where $A$ denotes the maximal perturbation and $a$ is the size of the bubble.
+We use the constants
+\begin{equation}\label{eq:cosine-bubble}
+  A = \SI{0.5}{\K} \quad a = \SI{250}{\m} \quad x_c = \SI{500}{\m} \quad z_c = \SI{350}{\m}.
+\end{equation}
+For the three-dimensional bubble, we set $y_c = x_c = \SI{500}{\m}$ and lower the bubble to $z_c = \SI{260}{\m}$.
+This corresponds to the parameters used in~\cite{kelly2012continuous}.
+For the 2D case, we use a constant viscosity of $\mu = 0.01$, an \aderdg{}-method of order 5 with two levels of dynamic \amr{}, resulting again in cell sizes of roughly $\SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.34}{\m}$.
+We use slightly different \amr{} parameters of $\Trefine = 1.5$ and $\Tdelete = -0.5$ and let the simulation run for \SI{600}{\s}.
+Note that, as seen in \cref{fig:cosine-2d}, our \amr{}-criterion tracks the wavefront of the cloud accurately.
+This result shows an excellent agreement to the ones achieved in~\cite{giraldo2008study}\todo{correct source?}.
+
+For the 3D case, we use an \aderdg{}-scheme of order 3 with a static mesh with cell sizes of \SI{40}{\m}. and a shorter simulation duration of \SI{400}{\s}.
+Due to the relatively coarse resolution and the hence increased aliasing errors, we need to increase the viscosity to $\mu = 0.02$.
+This corresponds to a larger amount of smoothing.
+Our results (\cref{fig:cosine-3d}) capture the overall dynamics of the scenario well, similar to the reference solution of~\cite{kelly2012continuous}.
+
+We again use a constant viscosity of $\mu = 0.01$ for the 2D case, and a viscosity of $\mu = 0.02$ for the 3D case.
+The simulations run for a time of $\SI{600}{\s}$ and $\SI{400}{\s}$ for two and three-dimensional scenarios respectively.
+
 \begin{figure}[htb]
   \centering
-  \begin{subfigure}[t]{0.8\textwidth}
+  \includegraphics[width=1.0\textwidth]{paper_two_bubbles}
+  \caption{\label{fig:two-bubbles-ader}Colliding Bubbles \aderdg{}}
+\end{figure}
+
+\begin{figure}[htb]
   \centering
-    \includegraphics[width=\textwidth]{paper_two_bubbles}
-    \caption{\label{fig:two-bubbles-ader}Colliding Bubbles \aderdg{}}
+  \begin{subfigure}[t]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{paper_cosine_bubble}
+    \caption{\label{fig:cosine-2d}2D Cosine Bubble}
   \end{subfigure}~%
@@
     \centering
-    \includegraphics{paper_lid_driven_cavity}
-    \caption{\label{fig:two-bubbles-fv}Colliding Bubbles \muscl{}}
+    \includegraphics[width=\textwidth]{paper_cosine_bubble_3d}
+    \caption{3D Cosine Bubble}
   \end{subfigure}
-  \caption{Cosine Bubble Scenarios}
-  \label{fig:two-bubbles-results}
+  \caption{\label{fig:cosine-3d}Cosine Bubble Scenarios}
+  \label{fig:cosine-bubbles-results}
 \end{figure}
@@
 We presented our implementation of an \aderdg{}-method and a \muscl{}-scheme with \amr{} for the Navier-Stokes equations.
-Our implementation is capable of simulating different scenarios:
+Our implementation is capable of simulating different scenarios:\todo{LK: Flesh this out a tiny bit, mention properties of \amr{} criterion}
 \begin{itemize}
@@
 \end{itemize}
-\todo{LK: Flesh this out a tiny bit, mention properties of \amr{} criterion}
 
 \subsection*{Acknowledgements}
-Lukas Krenz was funded by ChEESE (823844), Leonhard Rannabauer was funded by ExaHyPE (671698).
-\todo{LK: Standard sentence is: This research was funded by the European Union’s Horizon 2020 Research and Innovation Programme under the project ExaHyPE, grant no.  671698 (call FETHPC-1-2014).
-Special thanks goes to Dominic E.\ Charrier who provided help with the implementation in the %\exahypeegine{}.
-Also LRZ?}
+Leonhard Rannabauer was funded by the European Union’s Horizon 2020 Research and Innovation Programme under the project ExaHyPE, grant no.  671698 (call FETHPC-1-2014)
+Lukas Krenz  the European Union’s Horizon 2020 Research and Innovation Programme under the project ChEESE, grant no.\ 823844.
+Special thanks goes to Dominic E.\ Charrier who provided help with the implementation in the \exahypeengine{}.
+\todo{Are those ack.\ correct, esp. call no.\ for Cheese? Also thank lrz?}
 

### 2019-05-03 writing/paper/paper.tex
Minor changes

--- 2019-05-03 writing/paper/paper.tex
@@
 \section{Numerics}
-\todo{LR: Hier würde ich noch ein paar einleitende Worte hinzufügen}
 We use an \aderdg{}-scheme and a \muscl{} finite volume method.
@@
 The finite volume scheme is stabilized with the van Albada limiter\todo{Cite vanalbada}.
-
 The user can state dynamic \amr{} rules by supplying custom criteria that are evaluated point-wise.
-We use an element local error estimate based on the total variation of the numerical solution. 
-We use the fact that the total variation of a numerical solution is a perfect indicator for edges of a wavefront.
+Our criterium uses an element local error estimate based on the total variation of the numerical solution.
+We exploit the fact that the total variation of a numerical solution is a perfect indicator for edges of a wavefront.
 Let $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ be a sufficiently smooth function that maps the discrete solution at a point $\bm{x}$ to an arbitrary indicator variable.

### 2019-05-03 writing/paper/paper.tex

--- 2019-05-03 writing/paper/paper.tex
@@
 The finite volume scheme is stabilized with the van Albada limiter~\cite{van1997comparative}.
-
 The user can state dynamic \amr{} rules by supplying custom criteria that are evaluated point-wise.
-We use an element local error estimate based on the total variation of the numerical solution. 
-We use the fact that the total variation of a numerical solution is a perfect indicator for edges of a wavefront.
+Our criterium uses an element local error estimate based on the total variation of the numerical solution.
+We exploit the fact that the total variation of a numerical solution is a perfect indicator for edges of a wavefront.
 Let $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ be a sufficiently smooth function that maps the discrete solution at a point $\bm{x}$ to an arbitrary indicator variable.

### 2019-05-03 writing/paper/paper.tex
More changes.

@@
 \usepackage{hyperref}
-\usepackage[noabbrev]{cleveref}
+\usepackage[]{cleveref}
 \newcommand{\creflastconjunction}{, and\nobreakspace} % use Oxford comma
@@
 
-Many realistic atmospheric flows can be described by a perturbation over a background state that is in hydrostatic equilibrium\todo{Mention source}
+Many realistic atmospheric flows can be described by a perturbation over a background state that is in hydrostatic equilibrium
 \newcommand{\backgroundPressure}{\overline{\pressure}}
@@
 
-\begin{figure}[htb]
+\begin{figure}[tb]
   \centering
@@
 The resulting mesh can be observed in \cref{fig:two-bubbles-ader}.
-We observed that even though both results are nearly identical, the \amr{} run managed to use only 1953 cells, instead of 6561 cells for the fully refined solution. 
+We observe that the $L_2$ difference between the potential temperature of the \amr{} run, which uses 1953 cells, and the one of the fully refined run with 6561 cells, is only $1.87$.
+The relative error is \num{6.69e-6}.
 % points: 70308, 23619
@@
 We presented our implementation of an \aderdg{}-method and a \muscl{}-scheme with \amr{} for the Navier-Stokes equations.
-Our implementation is capable of simulating different scenarios:\todo{LK: Flesh this out a tiny bit, mention properties of \amr{} criterion}
-\begin{itemize}
-\item We evaluated our method for standard \textsc{cfd} scenarios and achieved competitive results for all used scenarios.
+Our implementation is capable of simulating different scenarios: \todo{LK: Flesh this out a tiny bit, mention properties of \amr{} criterion}
+We evaluated our method for standard \textsc{cfd} scenarios and achieved competitive results for all used scenarios.
 This is true for both two-dimensional scenarios (Taylor-Green vortex and lid-driven cavity) and for the three-dimensional \textsc{abc}-flow.
-\item Furthermore, our method allows us to simulate flows in hydrostatic equilibrium correctly as our results for the cosine and colliding bubble scenarios showed.
-\item We showed that our \amr{}-criterion is able to vastly reduce the number of grid cells while preserving the quality of the results.
-\end{itemize}
+
+Furthermore, our method allows us to simulate flows in hydrostatic equilibrium correctly, as our results for the cosine and colliding bubble scenarios showed.
+We showed that our \amr{}-criterion is able to vastly reduce the number of grid cells while preserving the quality of the results.
 

### 2019-05-03 writing/paper/paper.tex
Some more changes.

@@
 The user can state dynamic \amr{} rules by supplying custom criteria that are evaluated point-wise.
-Our criterium uses an element local error estimate based on the total variation of the numerical solution.
+Our criterion uses an element local error estimate based on the total variation of the numerical solution.
 We exploit the fact that the total variation of a numerical solution is a perfect indicator for edges of a wavefront.
@@
   \viscFlux_{\QE} = \kappa \pdv{\overline{T}}{z}.% =
-%\kappa \frac{R \overline{\theta} \left(\frac{\overline{p}{\left (z \right )}}{p_{0}}\right)^{\frac{R}{c_{p}}} \frac{d}{d z} \overline{p}{\left (z \right )}}{c_{p} \overline{p}{\left (z \right )}}.
 \end{equation}
@@
 This is the main advantage of our gradient-based method in contrast to methods working directly with the value of the solution, as for example~\cite{muller2010adaptive}.
-Overall, our result for this benchmark shows an excellent agreement to the previous solutions of~\cite{muller2010adaptive,giraldo2008study}\todo{Is coll.\ bubble contained in se study?}.
+Overall, our result for this benchmark shows an excellent agreement to the previous solutions of~\cite{muller2010adaptive}.
 
@@
 As we use limiting, we do not need any viscosity.
-The results of this method (\cref{fig:two-bubbles-fv}) also agree with the reference.
+The results of this method (\cref{fig:two-bubbles-fv}) also agree with the reference but contain fewer details.
 Note that the numerical dissapitivity of the finite volume scheme has a smoothing effect that is similar to the smoothing caused by viscosity.
@@
 For the three-dimensional bubble, we set $y_c = x_c = \SI{500}{\m}$ and lower the bubble to $z_c = \SI{260}{\m}$.
-This corresponds to the parameters used in~\cite{kelly2012continuous}.
-For the 2D case, we use a constant viscosity of $\mu = 0.01$, an \aderdg{}-method of order 5 with two levels of dynamic \amr{}, resulting again in cell sizes of roughly $\SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.34}{\m}$.
+This corresponds to the parameters used in~\cite{kelly2012continuous}\footnote{Note that the parameters presented in~\cite{kelly2012continuous} do not agree with their results, we instead use the same parameters as for 2D simulations.}.
+For the 2D case, we use a constant viscosity of $\mu = 0.01$ and an \aderdg{}-method of order 5 with two levels of dynamic \amr{}, resulting again in cell sizes of roughly $\SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.34}{\m}$.
 We use slightly different \amr{} parameters of $\Trefine = 1.5$ and $\Tdelete = -0.5$ and let the simulation run for \SI{600}{\s}.
 Note that, as seen in \cref{fig:cosine-2d}, our \amr{}-criterion tracks the wavefront of the cloud accurately.
-This result shows an excellent agreement to the ones achieved in~\cite{giraldo2008study}\todo{correct source?}.
+This result shows an excellent agreement to the ones achieved in~\cite{giraldo2008study,muller2010adaptive}.
 
@@
 Our results (\cref{fig:cosine-3d}) capture the overall dynamics of the scenario well, similar to the reference solution of~\cite{kelly2012continuous}.
-
-We again use a constant viscosity of $\mu = 0.01$ for the 2D case, and a viscosity of $\mu = 0.02$ for the 3D case.
-The simulations run for a time of $\SI{600}{\s}$ and $\SI{400}{\s}$ for two and three-dimensional scenarios respectively.
 
@@
 Leonhard Rannabauer was funded by the European Union’s Horizon 2020 Research and Innovation Programme under the project ExaHyPE, grant no.  671698 (call FETHPC-1-2014)
-Lukas Krenz  the European Union’s Horizon 2020 Research and Innovation Programme under the project ChEESE, grant no.\ 823844.
+Lukas Krenz  was funded by the European Union’s Horizon 2020 Research and Innovation Programme under the project ChEESE, grant no.\ 823844.
 Special thanks goes to Dominic E.\ Charrier who provided help with the implementation in the \exahypeengine{}.

### 2019-05-03 src/plot_taylor_green.py

@@ -63,7 +63,7 @@ def plot_taylor_green(fig_path, solution_path, target, order=5):
     ax.set_ylabel('$v_x(z), v_z(x)$')
     ax.set_xticks([0, np.pi, 2*np.pi])
     ax.set_xticklabels([0, '$\pi$', '$2\pi$'])
-    fig.subplots_adjust(left=0.2, bottom=0.2, right=0.85)
+    fig.subplots_adjust(left=0.24, bottom=0.28, right=0.95)
     fig.legend(loc='upper right', bbox_to_anchor=(1.01,1), handletextpad=10e-100, )
     sns.despine(fig,ax)
     fig.savefig(fig_path + '{target}_taylor_green_vel.pdf'.format(target=target), transparent=True)
@@ -79,7 +79,7 @@ def plot_taylor_green(fig_path, solution_path, target, order=5):
     ax.set_xticks([0, np.pi, 2*np.pi])
     ax.set_xticklabels([0, '$\pi$', '$2\pi$'])
     sns.despine(fig,ax)
-    fig.subplots_adjust(left=0.2, bottom=0.2)
+    fig.subplots_adjust(left=0.3, bottom=0.3)
     fig.savefig(fig_path + '{}_taylor_green_pressure.pdf'.format(target), transparent=True)
 
 def main():

### 2019-05-03 writing/paper/paper.tex
Add makefile/fix small typo.

@@
 We use a domain of size $(\SI{2 \pi}{\m} \times \SI{2 \pi}{\m})$ and impose the analytical solution at the boundary.
-A comparison at time $t = 10.0$ of the analytical solution for the pressure with our approximation (figure xxx) shows an excellent agreement.\todo{fig, check time, fix order/cells.}
+A comparison at time $t = 10.0$ of the analytical solution for the velocities with our approximation (\cref{fig:taylor-green}) shows an excellent agreement.
 We used an \aderdg{}-scheme of order $5$ with a grid of $25^2$ cells.
@@
     \includegraphics{paper_abc_flow_velocity}
-    \captionof{figure}{\label{fig:abc-flow}Our approximation (lines) of the lid-driven cavity flow vs.\ reference solution (markers) of~\cite{ghia1982high}.}
+    \captionof{figure}{\label{fig:abc-flow}Our approximation (markers) of the \textsc{abc}-flow vs.\ analytical solution (lines, \cref{eq:abc-flow}).
+    All other axes are held constant at a value of 0.}
 \end{minipage}%
@@
 
-In addition, we simulated the same scenario with our \muscl{} method, using $3^2$ patches with $80^2$ finite volume cells each~\todo{check}.
+In addition, we simulated the same scenario with our \muscl{} method, using $3^2$ patches with $80^2$ finite volume cells each and no viscosity~\todo{check}.
 As we use limiting, we do not need any viscosity.

### 2019-05-03 writing/paper/paper.tex
read through the paper and applied corrections

--- 2019-05-03 writing/paper/paper.tex
@@
 \let\boundary\undefined%
-\crefformat{equation}{\eqA{}eq.~\eqB #2#1#3)}
+\crefformat{equation}{\eqA{}Eq.~\eqB #2#1#3)}
 % TODO: Fix for more than two equations!
-\crefmultiformat{equation}{eqs.~\eqMultiA#2#1#3\eqMultiB}%
+\crefmultiformat{equation}{Eqs.~\eqMultiA#2#1#3\eqMultiB}%
 { and \eqMultiA#2#1#3\eqMultiB}{, \eqMultiA#2#1#3\eqMultiB}{ and~\eqMultiA#2#1#3\eqMultiB}
@@
 \begin{abstract}
-  We present an application of the compressible Navier Stokes equations for cloud formation processes.
+  We present a high-order discontinuous Galerkin (DG) solver of the compressible Navier Stokes equations for cloud formation processes.
   The scheme exploits an underlying parallelized implementation of the \aderdg{} method with dynamic adaptive mesh refinement. 
-  We improve our method by a \pde{} independent general refinement criterion, based on the local total variation of the numerical solution.
+  We improve our method by a \pde-independent general refinement criterion, based on the local total variation of the numerical solution.
   Our generic scheme shows competitive results for both classical \textsc{cfd} and stratified scenarios.
@@
 
-Due to the viscous components of the Navier-Stokes equations, it is not straightforward to apply the \dg{} method.
-For high-order \dg{} methods, viscosity not only models the physical reality of the problem but also helps us by smoothing out oscillations and discontinuities, thus stabilizing the simulation.
+Due to the viscous components of the Navier-Stokes equations, it is not straightforward to apply the \aderdg{} formalism of~\cite{dumbser2008unified}, which addresses hyperbolic systems of partial differentials equations (\pde{}s) in first-order formulation.
 To include viscosity, we use the numerical flux for the compressible Navier-Stokes equations of \citeauthor{gassner2008discontinuous}~\cite{gassner2008discontinuous}.
@@
 This has been shown to work well for the simulation of cloud dynamics~\cite{muller2010adaptive}.
+Regarding the issue of limiting in high-order \dg{} methods, we note that viscosity not only models the correct physics of the problem but also smoothes oscillations and discontinuities, thus stabilizing the simulation.
 %Insert references to Giraldo SE/DG bubbles~\cite{giraldo2008study}, 3D bubbles~\cite{giraldo2013implicit,kelly2012continuous}, bubble amr (müller~\cite{muller2010adaptive}).
 
-We base our work on the \exahypeengine{} (\url{www.exahype.eu}), which is a framework that can solve arbitrary hyperbolic partial differential equations.
-A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well posed Cauchy problem for a system of hyperbolic \pde{}s of first order.
+We base our work on the \exahypeengine{} (\url{www.exahype.eu}), which is a framework that can solve arbitrary hyperbolic \pde\ systems.
+A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well-posed Cauchy problem for a system of hyperbolic \pde{}s of first order.
 The underlying \aderdg{} method\todo{\muscl{}?}, parallelization techniques and dynamic adaptive mesh refinement are available for simulations while the implementations are left as a black box to the user.
-An introduction to the communication-avoiding implementation of the whole numerical scheme can be found in the recent work~\cite{charrier2018stop} by \citeauthor{charrier2018stop}.
+An introduction to the communication-avoiding implementation of the whole numerical scheme can be found in~\cite{charrier2018stop}.% by \citeauthor{charrier2018stop}.
 
-We make the following contributions:%
+To summarize, we make the following contributions in this paper:%
 \begin{itemize}%
 \item We extend the \exahypeengine{} to allow viscous terms following the aforementioned numerical scheme.
-\item We use this to provide an implementation of the compressible Navier-Stokes equation.
+\item We thus provide an implementation of the compressible Navier-Stokes equations.
   In addition, we tailor the equation set to stratified flows with gravitational source term.
-  We want to emphasize here that we use a standard formulation of the Navier-Stokes equations as seen in the field of computational fluid mechanics and only use small modifcations of the governing equations, in contrast to a equation set that is tailored exactly to the application area.
+  We emphasize that we use a standard formulation of the Navier-Stokes equations as seen in the field of computational fluid mechanics and only use small modifcations of the governing equations, in contrast to a equation set that is tailored exactly to the application area.
 \item We present a general \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
@@
 % \end{equation}
-The compressible Navier-Stokes equations in the conservative form are defined as% \pcref{eq:conservation-law-gradient}
+The compressible Navier-Stokes equations in the conservative form are given as% \pcref{eq:conservation-law-gradient}
 \begin{equation}
@@
 \end{equation}
-with vector of conserved quantities $\Q$, flux $\flux(\Q, \gradQ)$ and source $\source(\Q)$.
+with the vector of conserved quantities $\Q$, flux $\flux(\Q, \gradQ)$ and source $\source(\Q)$.
 Note that the flux can be split into a hyperbolic part $\hyperFlux(\Q)$,
@@
   \mu
-  \left(
+  \bigl(
   \left(\nicefrac{2}{3} \divergence{\Qv} \right) -
   \left( \gradient{\Qv} + \gradient{\Qv}^\intercal \right)
-  \right),
+  \bigr),
 \end{equation}
@@
 In contrast to this, we use the true compressible Navier-Stokes equations with minimal modifications.
+
 \section{Numerics}
-We use an \aderdg{}-scheme and a \muscl{} finite volume method.
+The \exahypeengine{} implements an \aderdg{}-scheme and a \muscl{} finite volume method.
 Both can be considered as instances of the more general \textsc{PnPm} schemes of~\cite{dumbser2008unified}.
@@
 The user can state dynamic \amr{} rules by supplying custom criteria that are evaluated point-wise.
-Our criterion uses an element local error estimate based on the total variation of the numerical solution.
+Our criterion uses an element-local error estimate based on the total variation of the numerical solution.
 We exploit the fact that the total variation of a numerical solution is a perfect indicator for edges of a wavefront.
@@
   \tv \left[ f(\bm{x}) \right] =
-  \Vert
+  \left\Vert
 \intdcell{ \vert \gradient{f \left( \bm{x} \right)} \vert }
-\Vert_1
+\right\Vert_1
 \end{equation}
 for each cell.
-The operator $\Vert \cdot \Vert_1$ denotes the discrete $l_1$ norm in this equation.
+The operator $\Vert \cdot \Vert_1$ denotes the discrete $L_1$ norm in this equation.
 We compute the integral efficiently with Gaussian quadrature over the collocated quadrature points.
@@
 \newcommand{\Trefine}{T_\text{refine}}%
-\newcommand{\Tdelete}{T_\text{erase}}%
+\newcommand{\Tdelete}{T_\text{coarsen}}%
 How can we decide whether a cell is important or not?
 To resolve this conundrum, we compute the mean and the population standard deviation of the total variation of all cells.
-It is important to note that we use the method of~\cite{chan1982updating} to compute the modes in a parallel and numerical stable manner.
+It is important that we use the method of~\cite{chan1982updating} to compute the modes in a parallel and numerical stable manner.
 A cell is then considered to contain significant information if its deviates from the mean more than a given threshold.
@@
     \text{refine} & \text{if } \tv(\Q) \geq \mu + \Trefine \sigma, \\
-    \text{erase} & \text{if } \tv(\Q) < \mu + \Tdelete \sigma, \\
+    \text{coarsen} & \text{if } \tv(\Q) < \mu + \Tdelete \sigma, \\
     \text{keep} & \text{otherwise}.
@@
   \label{eq:chebychev}
-  \mathbb{P}(\vert X - \mu \vert \geq c \sigma) \leq \frac{1}{c^2},
+  \mathbb{P}\bigl(\vert X - \mu \vert \geq c \sigma \bigr) \leq \frac{1}{c^2},
 \end{equation}
-with probability $\mathbb{P}$ guarantees that we neither mark all cells for refinement nor for erasement.
+with probability $\mathbb{P}$ guarantees that we neither mark all cells for refinement nor for coarsening.
 This inequality holds for arbitrary distributions under the weak assumption that they have a finite mean $\mu$ and a finite standard deviation $\sigma$~\cite{wasserman2004all}.
-Note that subcells are coarsened only if all subcells belonging to the coarse cell are marked for erasion.
+Note that subcells are coarsened only if all subcells belonging to the coarse cell are marked for coarsening.
 In contrast to already published criteria which are either designed solely for the simulation of clouds~\cite{muller2010adaptive} or computationally expensive~\cite{fambri2017space}, our criterion works for arbitrary \pde{}s and yet, is easy to compute and intuitive.
@@
 \section{Results}
-We use a diverse mix of benchmarking scenarios that consist of standard \textsc{cfd} scenarios and atmospheric flows.
-
+We use a mix of various benchmarking scenarios that consist of standard \textsc{cfd} scenarios and atmospheric flows.
+%
 For the standard \textsc{cfd} testing scenarios, we use the following constants of fluids:
@@
 \end{align}
-The constant $C = \nicefrac{100}{\gamma}$ governs the speed of sound and thus the Mach number $\text{Ma} = 0.1$~\cite{dumbser2016high}, the viscosity is set to $\mu = 0.1$.
-We use a domain of size $(\SI{2 \pi}{\m} \times \SI{2 \pi}{\m})$ and impose the analytical solution at the boundary.
+The constant $C = \nicefrac{100}{\gamma}$ governs the speed of sound and thus the Mach number $\text{Ma} = 0.1$~\cite{dumbser2016high}, the viscosity is set to $\mu = 0.1$. \todo{grammar broken.}
+
+We simulate on the domain $[0,2\pi]^2$ 
+%We use a domain of size 
+%$(\SI{2 \pi}{\m} \times \SI{2 \pi}{\m})$ 
+%% keine Meter-Angaben bei analytischen Testcases
+and impose the analytical solution at the boundary.
 A comparison at time $t = 10.0$ of the analytical solution for the pressure with our approximation (figure xxx) shows an excellent agreement.\todo{fig, check time, fix order/cells.}
@@
     \includegraphics{paper_lid_driven_cavity}
-    \caption{\label{fig:cavity-flow}Our approximation (lines) of the lid-driven cavity flow vs.\ reference solution (markers) of~\cite{ghia1982high}.}
+    \caption{\label{fig:cavity-flow}Our approximation (solid lines) of the lid-driven cavity flow vs.\ reference solution (crosses) of~\cite{ghia1982high}.}
   \end{subfigure}~%
@@
 
-The Arnold-Beltrami-Childress (\textsc{abc}) flow is similar to the Taylor-Green vortex but posesses an analytical solution for three-dimensions as well~\cite{tavelli2016staggered}.
-It is defined in the domain \( \left[ -\SI{\pi}{\m}, \SI{\pi}{\m} \right]^3 \) as
+The Arnold-Beltrami-Childress (\textsc{abc}) flow is similar to the Taylor-Green vortex but possesses an analytical solution for three-dimensions as well~\cite{tavelli2016staggered}.
+It is defined in the domain \( \left[ -\pi, \pi \right]^3 \) as
 \begin{align}
@@
 
-Our stratified flow scenarios are described in terms of the potential temperature
+With  the constants
+\begin{equation}\label{eq:atmosphere-constants}
+    \gamma = 1.4 ,\quad \Pr =  0.71 ,\quad R = 287.058 ,\quad p_0 = \SI{10e5}{\Pa}, \quad g = \SI{9.8}{m/s^2},
+\end{equation}
+all following stratified flow scenarios are described in terms of the potential temperature
 \begin{equation}
-  \potT = T \left( \frac{p_0}{p} \right)^{R/c_p},
+  \potT = T \left( \frac{p_o}{p} \right)^{R/c_p},
 \end{equation}
 with reference pressure $p_o$~\cite{muller2010adaptive,giraldo2008study}.
-We use the constants
-\begin{equation}\label{eq:atmosphere-constants}
-    \gamma = 1.4 ,\qquad \Pr =  0.71 ,\qquad R = 287.058 ,\qquad p_0 = \SI{10e5}{\Pa}, \qquad g = \SI{9.8}{m/s^2},
-\end{equation}
-for all remaining scenarios.
-
+%
 We compute the initial background density and pressure by inserting the assumption of a constant background energy in \cref{eq:hydrostatic-balance}.
@@
 
-Let
-\begin{equation}
-  \label{eq:radius}
-  r^2 = \Vert \bm{x} - \bm{x_c} \Vert_2 %(x - x_0)^2 + (z - z_0)^2
-\end{equation}
-denote the Euclidian distance between the spatial positions $\bm{x} = x, z$ and the center of a bubble $\bm{x_c} = x_c, z_c$.
-In case of three-dimensional scenarios the vectors $\bm{x}$ and $\bm{x_c}$ also contain a y coordinate.
+%Let
+%\begin{equation}
+%  \label{eq:radius}
+%  r^2 = \Vert \bm{x} - \bm{x_c} \Vert_2 %(x - x_0)^2 + (z - z_0)^2
+%\end{equation}
+%denote the Euclidian distance between the spatial positions $\bm{x} = x, z$ and the center of a bubble $\bm{x_c} = x_c, z_c$.
+%In case of three-dimensional scenarios the vectors $\bm{x}$ and $\bm{x_c}$ also contain a $y$ coordinate.
 
@@
 \end{equation}
-where $s$ is the decay rate and $r$  is the radius to the center~\pcref{eq:radius}.
+where $s$ is the decay rate and $r$  is the radius to the center~\pcref{eq:radius}:
+\begin{equation}
+  \label{eq:radius}
+  r^2 = \Vert \bm{x} - \bm{x_c} \Vert_2 %(x - x_0)^2 + (z - z_0)^2
+\end{equation}
+i.e., $r$ denotes the Euclidian distance between the spatial positions $\bm{x} = (x, z)$ and the center of a bubble $\bm{x_c} = (x_c, z_c)$ -- for three-dimensional scenarios $\bm{x}$ and $\bm{x_c}$ also contain a $y$ coordinate.
+
 We have two bubbles, with constants
@@
 Hence, it is difficult to compare the parametrization directly.
-We ran this scenario twice, firstly without \amr{} and a mesh of size $\SI{1000/81}{\m} = \SI{12.35}{\m}$.
-For the second run we used \amr{} with two adaptive refinement levels and parameters $\Trefine = 2.5$ and $\Tdelete = -0.5$.
+We ran this scenario twice: once without \amr{} and a mesh of size $\SI{1000/81}{\m} = \SI{12.35}{\m}$ and 
+once with \amr{} with two adaptive refinement levels and parameters $\Trefine = 2.5$ and $\Tdelete = -0.5$.
 We specialize the \amr{}-criterion~\pcref{eq:refinement-criterion} to our stratified flows by using the potential temperature.
-This resulted in a mesh with cell sizes lengths of ca. $\SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.34}{\m}$.
+This resulted in a mesh with cell-size lengths of approx.\ $\SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.34}{\m}$.
 The resulting mesh can be observed in \cref{fig:two-bubbles-ader}.
@@
 % points: 70308, 23619
-We further want to emphasize that our \amr{}-criterion is able to accurately track the position of the edges of cloud instead of only its position.
+We further emphasize that our \amr{}-criterion accurately tracks the position of the edges of cloud instead of only its position.
 This is the main advantage of our gradient-based method in contrast to methods working directly with the value of the solution, as for example~\cite{muller2010adaptive}.
@@
 
-In addition, we simulated the same scenario with our \muscl{} method, using $3^2$ patches with $80^2$ finite volume cells each~\todo{check}.
+In addition, we simulated the same scenario with our \muscl{} method, using $3^2$ patches with $80^2$ finite volume cells each\todo{check}.
 As we use limiting, we do not need any viscosity.
 The results of this method (\cref{fig:two-bubbles-fv}) also agree with the reference but contain fewer details.
-Note that the numerical dissapitivity of the finite volume scheme has a smoothing effect that is similar to the smoothing caused by viscosity.
+Note that the numerical dissipativity of the finite volume scheme has a smoothing effect that is similar to the smoothing caused by viscosity.
 
-For our second scenario, the cosine bubble, we use a pertubation of the form
+For our second scenario, the cosine bubble, we use a perturbation of the form
 \begin{align}
@@
 For the three-dimensional bubble, we set $y_c = x_c = \SI{500}{\m}$ and lower the bubble to $z_c = \SI{260}{\m}$.
-This corresponds to the parameters used in~\cite{kelly2012continuous}\footnote{Note that the parameters presented in~\cite{kelly2012continuous} do not agree with their results, we instead use the same parameters as for 2D simulations.}.
+This corresponds to the parameters used in~\cite{kelly2012continuous}\footnote{%
+We found that the parameters presented in the manuscript of~\cite{kelly2012continuous} only agree with the results, if we use the same parameters as for 2D simulations.}.
 For the 2D case, we use a constant viscosity of $\mu = 0.01$ and an \aderdg{}-method of order 5 with two levels of dynamic \amr{}, resulting again in cell sizes of roughly $\SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.34}{\m}$.
@@
 \section{Conclusion}
-We presented our implementation of an \aderdg{}-method and a \muscl{}-scheme with \amr{} for the Navier-Stokes equations.
+We presented an implementation of an \aderdg{}-method and a \muscl{}-scheme with \amr{} for the Navier-Stokes equations, based on the \exahypeengine.
 Our implementation is capable of simulating different scenarios: \todo{LK: Flesh this out a tiny bit, mention properties of \amr{} criterion}
@@
 \subsection*{Acknowledgements}
-Leonhard Rannabauer was funded by the European Union’s Horizon 2020 Research and Innovation Programme under the project ExaHyPE, grant no.  671698 (call FETHPC-1-2014)
-Lukas Krenz  was funded by the European Union’s Horizon 2020 Research and Innovation Programme under the project ChEESE, grant no.\ 823844.
-Special thanks goes to Dominic E.\ Charrier who provided help with the implementation in the \exahypeengine{}.
-\todo{Are those ack.\ correct, esp. call no.\ for Cheese? Also thank lrz?}
+This work was funded by the European Union’s Horizon 2020 Research and Innovation Programme under grant agreements 
+No~671698 (project ExaHyPE, \url{www.exahype.eu}) and 
+No~823844 (ChEESE centre of excellence, \url{www.cheese-coe.eu}).
+Computing resources were provided by the Leibniz Supercomputing Centre (project XXX). \todo{Add project number(s)?}
+Special thanks go to Dominic E.\ Charrier for his support with the implementation in the \exahypeengine{}.
 

### 2019-05-03 writing/paper/paper.tex

@@
 \documentclass[runningheads]{llncs}
-\title{Cloud Supercomputing}
+\title{A High-Order Discontinuous Galerkin Solver with Dynamic Adaptive Mesh Refinement to Simulate Cloud Formation Processes }
 \author{Lukas Krenz\inst{1} \and{} Leonhard Rannabauer\inst{1} \and{} Michael Bader\inst{1}}
-\institute{Technical University of Munich} % todo emails and stuff
+\institute{Department of Informatics, Technical University of Munich} % todo emails and stuff
 \usepackage[utf8]{inputenc}
@@
 \end{align}
-The constant $C = \nicefrac{100}{\gamma}$ governs the speed of sound and thus the Mach number $\text{Ma} = 0.1$~\cite{dumbser2016high}, the viscosity is set to $\mu = 0.1$. \todo{grammar broken.}
+The constant $C = \nicefrac{100}{\gamma}$ governs the speed of sound and thus the Mach number $\text{Ma} = 0.1$~\cite{dumbser2016high}. The viscosity is set to $\mu = 0.1$.
 
@@
 and impose the analytical solution at the boundary.
-A comparison at time $t = 10.0$ of the analytical solution for the pressure with our approximation (figure xxx) shows an excellent agreement.\todo{fig, check time, fix order/cells.}
+A comparison at time $t = 10.0$ of the analytical solution for the pressure with our approximation (\cref{fig:taylor-green}) shows excellent agreement.
 We used an \aderdg{}-scheme of order $5$ with a grid of $25^2$ cells.

### 2019-05-03 writing/paper/paper.tex
Small detail fixes.

@@
     \includegraphics{paper_taylor_green_vel}
-    \caption{\label{fig:taylor-green}Taylor green, velocity slices.}
+    \caption{\label{fig:taylor-green}Our result (markers) of the Taylor-Green vortex vs.\ the analytical solution (lines) \cref{eq:taylor-green}.
+    The plot shows two velocity slices, the respective other coordinate is held constant at a value of $\pi$.}
 
@@
 \centering
+% or .473 size each, and \\quad inbetween
 \begin{minipage}{.5\textwidth}
@@
     \captionof{figure}{\label{fig:abc-flow}Our approximation (markers) of the \textsc{abc}-flow vs.\ analytical solution (lines, \cref{eq:abc-flow}).
-    All other axes are held constant at a value of 0.}
-\end{minipage}%
+    All other axes are held constant at a value of 0. We show every 6th value.}
+\end{minipage}~%
 \begin{minipage}{.5\textwidth}
@@
 
-In addition, we simulated the same scenario with our \muscl{} method, using $3^2$ patches with $80^2$ finite volume cells each\todo{check}.
+In addition, we simulated the same scenario with our \muscl{} method, using $7^2$ patches with $90^2$ finite volume cells each.
 As we use limiting, we do not need any viscosity.

### 2019-05-03 src/plot_abc.py

@@ -77,7 +77,7 @@ def plot_abc(fig_path, solution_path, target, order=2):
     #_, _, c = plot_contour(df_cut, fig, ax, var, levels=4, coords=others, num_sample=500,colored=False)
         coord_cut, p_approx_cut, p_ana_cut, vel_approx_cut, vel_ana_cut = eval_cut(df, coord, time, mu=0.01,
                                                                         analytical_solution=analytical_solution,
-                                                                        dim=dim, every_nth=6, vel_var=vel_var)
+                                                                        dim=dim, every_nth=6, vel_var='v')
         ax.plot(coord_cut, vel_ana_cut,  c='gray', linestyle='solid', zorder=-1)
         ax.scatter(coord_cut, vel_approx_cut, c='black', marker=marker, label=coord, s=1., lw=6, facecolors='none',)
         if coord == 'x':

### 2019-05-03 writing/paper/paper.tex
Fix small errors.

@@
 \title{A High-Order Discontinuous Galerkin Solver with Dynamic Adaptive Mesh Refinement to Simulate Cloud Formation Processes }
+\titlerunning{A High-Order DG Solver to Simulate Cloud Formation Processes}
 \author{Lukas Krenz\inst{1} \and{} Leonhard Rannabauer\inst{1} \and{} Michael Bader\inst{1}}
-\institute{Department of Informatics, Technical University of Munich} % todo emails and stuff
+\authorrunning{L.\ Krenz, L.\ Rannabauer, M.\ Bader}
+\institute{Department of Informatics, Technical University of Munich\\
+  \email{lukas.krenz@in.tum.de}, \email{rannabauer@in.tum.de}, \email{bader@in.tum.de}
+\vspace*{-0.2cm}
+} % todo emails and stuff
 \usepackage[utf8]{inputenc}
@@
 
-\keywords{\aderdg{}  \and Navier-Stokes \and Another keyword.}
+\keywords{\aderdg{}  \and Navier-Stokes \and Adaptive Mesh Refinement.}
 \end{abstract}
@@
 Regarding the issue of limiting in high-order \dg{} methods, we note that viscosity not only models the correct physics of the problem but also smoothes oscillations and discontinuities, thus stabilizing the simulation.
-%Insert references to Giraldo SE/DG bubbles~\cite{giraldo2008study}, 3D bubbles~\cite{giraldo2013implicit,kelly2012continuous}, bubble amr (müller~\cite{muller2010adaptive}).
 
@@
 The underlying \aderdg{} method\todo{\muscl{}?}, parallelization techniques and dynamic adaptive mesh refinement are available for simulations while the implementations are left as a black box to the user.
-An introduction to the communication-avoiding implementation of the whole numerical scheme can be found in~\cite{charrier2018stop}.% by \citeauthor{charrier2018stop}.
+An introduction to the communication-avoiding implementation of the whole numerical scheme can be found in~\cite{charrier2018stop}.
 
@@
 \end{equation}
-The parameters $\Trefine > \Tdelete$ can be chosen freely\todo{LK: Do we need the ineq.?}.
+The parameters $\Trefine > \Tdelete$ can be chosen freely.
 Chebyshev's inequality
@@
   \centering
-  \begin{subfigure}[t]{0.5\textwidth}
+  \begin{subfigure}[t]{.473\textwidth}
     \centering
     \includegraphics{paper_lid_driven_cavity}
-    \caption{\label{fig:cavity-flow}Our approximation (solid lines) of the lid-driven cavity flow vs.\ reference solution (crosses) of~\cite{ghia1982high}.}
-  \end{subfigure}~%
-  \begin{subfigure}[t]{0.5\textwidth}
+    \caption{\label{fig:cavity-flow}Our approximation (solid lines) of the lid-driven cavity flow vs.\ reference solution (crosses) of~\cite{ghia1982high}.
+    The respective other coordinate is held constant at a value of 0.}
+  \end{subfigure}\quad%
+  \begin{subfigure}[t]{0.473\textwidth}
     \centering
@@
 % or .473 size each, and \\quad inbetween
-\begin{minipage}{.5\textwidth}
+\begin{minipage}[t]{.473\textwidth}
   \centering
@@
     All other axes are held constant at a value of 0. We show every 6th value.}
-\end{minipage}~%
-\begin{minipage}{.5\textwidth}
+\end{minipage}\qquad%
+\begin{minipage}[t]{.473\textwidth}
   \centering
@@
 
-%Let
-%\begin{equation}
-%  \label{eq:radius}
-%  r^2 = \Vert \bm{x} - \bm{x_c} \Vert_2 %(x - x_0)^2 + (z - z_0)^2
-%\end{equation}
-%denote the Euclidian distance between the spatial positions $\bm{x} = x, z$ and the center of a bubble $\bm{x_c} = x_c, z_c$.
-%In case of three-dimensional scenarios the vectors $\bm{x}$ and $\bm{x_c}$ also contain a $y$ coordinate.
-
 Our first scenario is the colliding bubbles scenario~\cite{muller2010adaptive}.
@@
   \label{eq:radius}
-  r^2 = \Vert \bm{x} - \bm{x_c} \Vert_2 %(x - x_0)^2 + (z - z_0)^2
+  r^2 = \Vert \bm{x} - \bm{x_c} \Vert_2
 \end{equation}
@@
 The relative error is \num{6.69e-6}.
-% points: 70308, 23619
 We further emphasize that our \amr{}-criterion accurately tracks the position of the edges of cloud instead of only its position.
@@
 No~823844 (ChEESE centre of excellence, \url{www.cheese-coe.eu}).
-Computing resources were provided by the Leibniz Supercomputing Centre (project XXX). \todo{Add project number(s)?}
+Computing resources were provided by the Leibniz Supercomputing Centre (project pr83no).
 Special thanks go to Dominic E.\ Charrier for his support with the implementation in the \exahypeengine{}.

### 2019-05-03 writing/paper/paper.tex
Improve figures, ticks now readable.

@@
 A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well-posed Cauchy problem for a system of hyperbolic \pde{}s of first order.
-The underlying \aderdg{} method\todo{\muscl{}?}, parallelization techniques and dynamic adaptive mesh refinement are available for simulations while the implementations are left as a black box to the user.
+The underlying \aderdg{} method, parallelization techniques and dynamic adaptive mesh refinement are available for simulations while the implementations are left as a black box to the user.
 An introduction to the communication-avoiding implementation of the whole numerical scheme can be found in~\cite{charrier2018stop}.
@@
     \captionof{figure}{\label{fig:two-bubbles-fv}%
-    Colliding bubbles with \muscl{}}
+    Colliding bubbles with \muscl{}. Contour values for potential temperature pertubation are $-0.05, 0.05, 0.1, \ldots 0.45$.}
 \end{minipage}
@@
 We specialize the \amr{}-criterion~\pcref{eq:refinement-criterion} to our stratified flows by using the potential temperature.
-This resulted in a mesh with cell-size lengths of approx.\ $\SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.34}{\m}$.
+This resulted in a mesh with cell-size lengths of approx.\ \SI{111.1}{\m}, \SI{37.04}{\m}, and \SI{12.34}{\m}.
 The resulting mesh can be observed in \cref{fig:two-bubbles-ader}.
@@
   \centering
-  \includegraphics[width=1.0\textwidth]{paper_two_bubbles}
-  \caption{\label{fig:two-bubbles-ader}Colliding Bubbles \aderdg{}}
+  \includegraphics[width=0.90\textwidth]{paper_two_bubbles}
+  \caption{\label{fig:two-bubbles-ader}Colliding Bubbles \aderdg{}. Contour values for potential temperature pertubation are $-0.05, 0.05, 0.1, \ldots 0.45$.}
 \end{figure}
@@
     \includegraphics[width=\textwidth]{paper_cosine_bubble}
-    \caption{\label{fig:cosine-2d}2D Cosine Bubble}
+    \caption{\label{fig:cosine-2d}2D Cosine Bubble.}%todo: Contour lines?
   \end{subfigure}~%
@@
 We presented an implementation of an \aderdg{}-method and a \muscl{}-scheme with \amr{} for the Navier-Stokes equations, based on the \exahypeengine.
-Our implementation is capable of simulating different scenarios: \todo{LK: Flesh this out a tiny bit, mention properties of \amr{} criterion}
+Our implementation is capable of simulating different scenarios:
 We evaluated our method for standard \textsc{cfd} scenarios and achieved competitive results for all used scenarios.

### 2019-05-03 writing/paper/paper.tex
Spelling.

@@
 %% An important part of future \textsc{nwp} models will be the the resolution of convective processes~\cite{bauer2015quiet}.
-This requires both suitable physical models and effective computational realisations. 
+This requires both suitable physical models and effective computational realizations. 
 Here we focus on the simulation of simple benchmark scenarios~\cite{giraldo2008study}.
 They contain relatively small scale effects which are well approximated with the compressible Navier-Stokes equations.
-We use the \aderdg{} method of~\cite{dumbser2008unified}, which allows us to simulate the Naview-Stokes equations with a space-time-discretization of arbitrary high order.
+We use the \aderdg{} method of~\cite{dumbser2008unified}, which allows us to simulate the Navier-Stokes equations with a space-time-discretization of arbitrary high order.
 In contrast to Runge-Kutta time integrators or semi-implicit methods, an increase of the order of \aderdg{} only results in larger computational kernels and does not affect the complexity of the scheme.
@@
 This has been shown to work well for the simulation of cloud dynamics~\cite{muller2010adaptive}.
-Regarding the issue of limiting in high-order \dg{} methods, we note that viscosity not only models the correct physics of the problem but also smoothes oscillations and discontinuities, thus stabilizing the simulation.
+Regarding the issue of limiting in high-order \dg{} methods, we note that viscosity not only models the correct physics of the problem but also smooths oscillations and discontinuities, thus stabilizing the simulation.
 
@@
   In addition, we tailor the equation set to stratified flows with gravitational source term.
-  We emphasize that we use a standard formulation of the Navier-Stokes equations as seen in the field of computational fluid mechanics and only use small modifcations of the governing equations, in contrast to a equation set that is tailored exactly to the application area.
+  We emphasize that we use a standard formulation of the Navier-Stokes equations as seen in the field of computational fluid mechanics and only use small modifications of the governing equations, in contrast to a equation set that is tailored exactly to the application area.
 \item We present a general \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
@@
 \end{equation}
-i.e., $r$ denotes the Euclidian distance between the spatial positions $\bm{x} = (x, z)$ and the center of a bubble $\bm{x_c} = (x_c, z_c)$ -- for three-dimensional scenarios $\bm{x}$ and $\bm{x_c}$ also contain a $y$ coordinate.
+i.e., $r$ denotes the Euclidean distance between the spatial positions $\bm{x} = (x, z)$ and the center of a bubble $\bm{x_c} = (x_c, z_c)$ -- for three-dimensional scenarios $\bm{x}$ and $\bm{x_c}$ also contain a $y$ coordinate.
 
@@
 
-\subsection*{Acknowledgements}
+\subsection*{Acknowledgments}
 This work was funded by the European Union’s Horizon 2020 Research and Innovation Programme under grant agreements 

### 2019-05-03 writing/paper/paper.tex
More spelling, remove some comments.

@@
 \begin{abstract}
-  We present a high-order discontinuous Galerkin (DG) solver of the compressible Navier Stokes equations for cloud formation processes.
+  We present a high-order discontinuous Galerkin (\dg{}) solver of the compressible Navier Stokes equations for cloud formation processes.
   The scheme exploits an underlying parallelized implementation of the \aderdg{} method with dynamic adaptive mesh refinement. 
-  We improve our method by a \pde-independent general refinement criterion, based on the local total variation of the numerical solution.
+  We improve our method by a \pde{}-independent general refinement criterion, based on the local total variation of the numerical solution.
   Our generic scheme shows competitive results for both classical \textsc{cfd} and stratified scenarios.
@@
   All together our method can be seen as a perfect candidate for large scale cloud simulation runs on current and future super computers.
-% \begin{itemize}
-% \item Implementation of compressible Navier Stokes with a high-order \aderdg{}-method and a low order finite volume \muscl{}-scheme.
-% \item Implementation in \exahypeengine{}, a scalable \pde{} framework.
-% \item Outlier and total variation based adaptive mesh refinement that reduced number of grid cells drastically and preserves solution quality.
-% \item Simulation of challenging flows over hydrostatic background atmosphere.
-% \item Competitive results for both classical cfd scenarios and hydrostatic scenarios in two and three dimensions.
-% \end{itemize}
-
-%The abstract should briefly summarize the contents of the paper in
-%150--250 words.
 
@@
 In this paper we address the resolution of basic cloud formation processes on modern super computer systems.
-%%of convective processes in the context of numerical weather prediction (\textsc{nwp}) on modern super computer systems.
 The simulation of cloud formations, as part of convective processes, is expected to play an important role in future numerical weather prediction~\cite{bauer2015quiet}.
-%% Numerical weather prediction (\textsc{nwp}) contains processes of different spatio-temporal scales.
-%% An important part of future \textsc{nwp} models will be the the resolution of convective processes~\cite{bauer2015quiet}.
 This requires both suitable physical models and effective computational realizations. 
@@
 We see our scheme in the regime of already established methods for cloud simulations, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
-%%The general approach is to use a space-discretized by higher order Galerkin method, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
-%%They are often space-discretized by higher order Galerkin methods, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
-%%Even though all of these implementations use a discretization with a (theoretical) unlimited space-order, they use Runge-Kutta time integrators or semi-implicit methods.
-%%It is well known that Runge-Kutta methods become more ineffecient for very high orders.
-%%Furthermore, they and the implicit methods are more communication-intensive and thus require a larger overhead and are more complicated to scale.
-%%We follow a different approach in this paper and use the \aderdg{} method of~\cite{dumbser2008unified} to simulate various computational fluid dynamics (\textsc{cfd}) scenarios with a focus on flows with stratified flows.
 
@@
     \captionof{figure}{\label{fig:two-bubbles-fv}%
-    Colliding bubbles with \muscl{}. Contour values for potential temperature pertubation are $-0.05, 0.05, 0.1, \ldots 0.45$.}
+    Colliding bubbles with \muscl{}. Contour values for potential temperature perturbation are $-0.05, 0.05, 0.1, \ldots 0.45$.}
 \end{minipage}
@@
   \includegraphics[width=0.90\textwidth]{paper_two_bubbles}
-  \caption{\label{fig:two-bubbles-ader}Colliding Bubbles \aderdg{}. Contour values for potential temperature pertubation are $-0.05, 0.05, 0.1, \ldots 0.45$.}
+  \caption{\label{fig:two-bubbles-ader}Colliding Bubbles \aderdg{}. Contour values for potential temperature perturbation are $-0.05, 0.05, 0.1, \ldots 0.45$.}
 \end{figure}

### 2019-05-04 writing/paper/paper.tex
Add version to be submitted to PPAM, final (?).

@@
   Our generic scheme shows competitive results for both classical \textsc{cfd} and stratified scenarios.
-  While established methods use tailored numerics towards the specific simulation, our scheme works scenario independent.
-  All together our method can be seen as a perfect candidate for large scale cloud simulation runs on current and future super computers.
+  While established methods use numerics tailored towards the specific simulation, our scheme works scenario independent.
+  All together, our method can be seen as a perfect candidate for large scale cloud simulation runs on current and future super computers.
 
@@
 The flow is driven entirely by the upper wall which has a velocity of $v_x = \SI{1}{\m/\s}$.
-The simulation runs for $\SI{10}{\s}$
+The simulation runs for $\SI{10}{\s}$.
 Again, our results (\cref{fig:cavity-flow}) have an excellent agreement with the reference solution of~\cite{ghia1982high}.
@@
 \begin{equation}
-  \potT = T \left( \frac{p_o}{p} \right)^{R/c_p},
+  \potT = T \left( \frac{p_0}{p} \right)^{R/c_p},
 \end{equation}
-with reference pressure $p_o$~\cite{muller2010adaptive,giraldo2008study}.
+with reference pressure $p_0$~\cite{muller2010adaptive,giraldo2008study}.
 %
@@
 \end{equation}
-at the boundary.
-In this equation, $\overline{T}(z)$ is the background temperature at position $z$, which can be computed from \cref{eq:hydrostatic-balance,eq:eos}~\cite{giraldo2008study}.
+at the boundary~\cite{giraldo2008study}.
+In this equation, $\overline{T}(z)$ is the background temperature at position $z$, which can be computed from \cref{eq:hydrostatic-balance,eq:eos}.
 
@@
 \end{equation}
-where $s$ is the decay rate and $r$  is the radius to the center~\pcref{eq:radius}:
+where $s$ is the decay rate and $r$  is the radius to the center
 \begin{equation}
   \label{eq:radius}
-  r^2 = \Vert \bm{x} - \bm{x_c} \Vert_2
+  r^2 = \Vert \bm{x} - \bm{x_c} \Vert_2,
 \end{equation}
@@
 This resulted in a mesh with cell-size lengths of approx.\ \SI{111.1}{\m}, \SI{37.04}{\m}, and \SI{12.34}{\m}.
-The resulting mesh can be observed in \cref{fig:two-bubbles-ader}.
+The resulting mesh can be seen in \cref{fig:two-bubbles-ader}.
 We observe that the $L_2$ difference between the potential temperature of the \amr{} run, which uses 1953 cells, and the one of the fully refined run with 6561 cells, is only $1.87$.
 The relative error is \num{6.69e-6}.
-We further emphasize that our \amr{}-criterion accurately tracks the position of the edges of cloud instead of only its position.
+We further emphasize that our \amr{}-criterion accurately tracks the position of the edges of the cloud instead of only its position.
 This is the main advantage of our gradient-based method in contrast to methods working directly with the value of the solution, as for example~\cite{muller2010adaptive}.
@@
 \end{equation}
-For the three-dimensional bubble, we set $y_c = x_c = \SI{500}{\m}$ and lower the bubble to $z_c = \SI{260}{\m}$.
+For the three-dimensional bubble, we set $y_c = x_c = \SI{500}{\m}$.
 This corresponds to the parameters used in~\cite{kelly2012continuous}\footnote{%
@@
 
-For the 3D case, we use an \aderdg{}-scheme of order 3 with a static mesh with cell sizes of \SI{40}{\m}. and a shorter simulation duration of \SI{400}{\s}.
-Due to the relatively coarse resolution and the hence increased aliasing errors, we need to increase the viscosity to $\mu = 0.02$.
+For the 3D case, we use an \aderdg{}-scheme of order 3 with a static mesh with cell sizes of \SI{40}{\m} and a shorter simulation duration of \SI{400}{\s}.
+Due to the relatively coarse resolution and the hence increased aliasing errors, we need to increase the viscosity to $\mu = 0.05$.
 This corresponds to a larger amount of smoothing.
-Our results (\cref{fig:cosine-3d}) capture the overall dynamics of the scenario well, similar to the reference solution of~\cite{kelly2012continuous}.
+Our results (\cref{fig:cosine-3d}) capture the dynamics of the scenario well and agree with the reference solution of~\cite{kelly2012continuous}.
 
@@
   \includegraphics[width=0.90\textwidth]{paper_two_bubbles}
-  \caption{\label{fig:two-bubbles-ader}Colliding Bubbles \aderdg{}. Contour values for potential temperature perturbation are $-0.05, 0.05, 0.1, \ldots 0.45$.}
+  \caption{\label{fig:two-bubbles-ader}Colliding Bubbles with \aderdg{}. Contour values for potential temperature perturbation are $-0.05, 0.05, 0.1, \ldots 0.45$.}
 \end{figure}
@@
     \centering
-    \includegraphics[width=\textwidth]{paper_cosine_bubble}
+    \includegraphics[width=\textwidth, trim={0cm 0 23cm 0},clip]{paper_cosine_bubble_collage}
+    %\includegraphics[width=\textwidth]{paper_cosine_bubble}
     \caption{\label{fig:cosine-2d}2D Cosine Bubble.}%todo: Contour lines?
@@
     \centering
-    \includegraphics[width=\textwidth]{paper_cosine_bubble_3d}
-    \caption{3D Cosine Bubble}
+    \includegraphics[width=\textwidth, trim={23cm 0 0cm 0},clip]{paper_cosine_bubble_collage}
+    %\includegraphics[width=\textwidth]{paper_cosine_bubble_3d}
+    \caption{\label{fig:cosine-3d}3D Cosine Bubble}
   \end{subfigure}
-  \caption{\label{fig:cosine-3d}Cosine Bubble Scenarios}
-  \label{fig:cosine-bubbles-results}
+  \caption{\label{fig:cosine-bubbles-results}Cosine Bubble Scenario}
 \end{figure}

### 2019-05-04 writing/paper/paper.tex
Fix small typo.

@@
 \begin{abstract}
-  We present a high-order discontinuous Galerkin (\dg{}) solver of the compressible Navier Stokes equations for cloud formation processes.
+  We present a high-order discontinuous Galerkin (\dg{}) solver of the compressible Navier-Stokes equations for cloud formation processes.
   The scheme exploits an underlying parallelized implementation of the \aderdg{} method with dynamic adaptive mesh refinement. 

### 2019-08-28 writing/slides/ppam.tex
Add first draft of slides for PPAM.

--- 2019-01-24 writing/slides/final.tex
@@
 %\usepackage{eulervm}
-\usetheme{metropolis} % Use metropolis theme
+%\usetheme{metropolis} % Use metropolis theme
+\usepackage[conference]{beamertheme_tumtalk} % headline and footline
+\usepackage{beamercolorscheme_tum} % colorscheme
+\usepackage{beamerfontthemestructurebold} % bold headings
+
 \usepackage{appendixnumberbeamer}
-\usepackage{lmodern}
+\renewcommand\footnoterule{}
 
-\renewcommand{\footnoterule}{%
-  \hspace{2cm}
-  \kern -3pt
-  \hrule width \textwidth height 1pt
-  \kern 2pt
-}
 \usepackage[utf8]{inputenc}
@@
 
-\title{Cloud Simulation with the ExaHyPE-Engine\\Master Thesis Final}
-\author{Lukas Krenz\\Adviser: Leonhard Rannabauer\\Supervisor: Prof.\ Dr.\ Michael Bader}
-\date{January 24, 2019} 
-\institute{\textsc{tum}, Chair for Scientific Computing}
+\title[High-Order DG with Dynamic AMR to Simulate Clouds]{A High-Order Discontinuous Galerkin Solver with Dynamic Adaptive Mesh Refinement to Simulate Cloud Formation Processes}
+\subtitle{PPAM 209}
+\author[L.\ Krenz, L.\ Rannabauer, M.\ Bader]{Lukas Krenz, Leonhard Rannabauer and Michael Bader}
+\date{\today} 
+\institute{Technical University of Munich}
 
@@
 \maketitle
+\begin{frame}{The ExaHyPE-Engine\footfullcite{reinarz2019exahype}}
+  \begin{block}{Goals}
+   A PDE \enquote{engine} (\enquote{engine} as in \enquote{game engine}).
+
+   Provides numerics/mesh for user-defined applications.
+
+   Allow \textbf{smaller} teams to realize \textbf{large-scale} simulations of hyperbolic PDEs.
+  \end{block}
+  \begin{block}{Capabilities}
+    \begin{itemize}
+    \item Optimized kernels for ADER-DG and a Finite Volume Scheme
+    \item Dynamic Adaptive Mesh Refinement (AMR)
+    \item Hybrid MPI + Intel TBB Parallelism
+    \end{itemize}
+  \end{block}
+
+  Available (\textbf{open-source}) at \url{exahype.eu}
+\end{frame}
+
 \begin{frame}{Two Bubbles: Hydrostatic Equilibrium\footfullcite{robert1993bubble}}
@@
         \ifratio{43}{
-          \includegraphics{beamer_43_hydrostatic_equilibrium}
+          %\includegraphics{beamer_43_hydrostatic_equilibrium}
         } {
-          \includegraphics{beamer_169_hydrostatic_equilibrium}
+          %\includegraphics{beamer_169_hydrostatic_equilibrium}
         }
@@
   \frametitle{Two Bubbles: Simulation}
-   \begin{figure}[h]
-    \centering
-    \ifratio{43}{
-    \movie[width=0.9\textwidth, height=0.6\textwidth, autostart,, loop, poster]{}{two_bubbles_cartesian.ogv}
-  } {
-    \movie[width=0.7\textwidth, height=0.466666\textwidth, autostart,, loop, poster]{}{two_bubbles_cartesian.ogv}
-  }
-    \caption{Two Bubbles scenario}
-  \end{figure}
+  %  \begin{figure}[h]
+  %   \centering
+  %   \ifratio{43}{
+  %   \movie[width=0.9\textwidth, height=0.6\textwidth, autostart,, loop, poster]{}{two_bubbles_cartesian.ogv}
+  % } {
+  %   \movie[width=0.7\textwidth, height=0.466666\textwidth, autostart,, loop, poster]{}{two_bubbles_cartesian.ogv}
+  % }
+  %   \caption{Two Bubbles scenario}
+  % \end{figure}
+  Here: AMR simulation of two bubbles scenario (video)
 \end{frame}
@@
 
-\textbf{ADER}-Approach uses space-time polynomials for time integration instead of Runge-Kutta procedures.
-
 Implemented in the \textsc{PDE}-Framework \textbf{ExaHyPE}.
@@
 
-\begin{frame}{The Navier-Stokes Equations (with advection coupling\footfullcite{hidalgo2011ader})}
+\begin{frame}{The Navier-Stokes Equations}
+  TODO PDE Conservative form(?)
   Vector of conserved quantities:
@@
   \label{eq:conserved-variables}
- \Q = \left( \Qrho, \Qj, \QE, \QZ \right) 
+ \Q = \left( \Qrho, \Qj, \QE \right) 
 \end{equation}
-With $\Qrho$ density of fluid, $\Qj$ velocity density, $\QE$ energy density, $\QZ$ mass fraction of chemical reactant (unburnt gas).
+With $\Qrho$ density of fluid, $\Qj$ velocity density and $\QE$ energy density
 
@@
     \Qv \cdot \left(\bm{I} \QE + \bm{I} \pressure + \textcolor{orange}{\stressT (\Q, \gradQ)} \right) -
-    \textcolor{orange}{\kappa \nabla T}\\
-    \Qj \QZZ
+    \textcolor{orange}{\kappa \nabla T}
   \end{pmatrix}
@@
 
-Pressure $\pressure(\Q)$,
+Pressure with gravitational term $\pressure(\Q, z)$,
 stress tensor $\textcolor{orange}{\stressT}$, heat diffusion $\textcolor{orange}{\kappa \nabla T}$ with temperature $T$.
@@
 \begin{frame}{Problem: Not hyperbolic}
-  \textsc{DG} solves equations of the form (e.g.\ Euler):
+  ExahyPE (thus far) solves equations of the form (e.g.\ Euler):
+  TODO: Other terms in gray!
   \begin{equation}
@@
 
-\alert{No explicit discretization} of gradient $\gradQ$.
-\end{frame}
-
-\begin{frame}{Convergence Tests}
-  \begin{figure}[h]
-    \centering
-    \ifratio{43}{
-      \includegraphics[]{{beamer_43_convergence}}
-  } {
-    \includegraphics[]{{beamer_169_convergence}}
-  }
-
-    \caption{Errors. $N$ polynomial order. Dotted lines optimal order $N+1$. }
-  \end{figure}
+\textcolor{orange}{No explicit discretization} of gradient $\gradQ$.
 \end{frame}
@@
 
-  Total variation of $\bm{x}$ for cell $\cell$:
+  Total variation of $\bm{x}$ for a cell $\cell$:
 \begin{equation}
@@
 
+\begin{block}{Intuition}
+  \begin{itemize}
+\item \textbf{Large} total variation $\mapsto$ interesting
+\item \textbf{Small} total variation $\mapsto$ boring
+  \end{itemize}
+  \enquote{Edge detection} of numerical solution
+\end{block}
+
 \end{frame}
 
-\begin{frame}{Adaptive Mesh Refinement: Global Criterion}
+\begin{frame}{Adaptive Mesh Refinement: Outliers}
   \begin{block}{Chebyshev's inequality}
@@
 \end{equation}
+Intuition: Not all variables are outliers.
+Feature detection
 \end{block}
+\end{frame}
 
+\begin{frame}{Adaptive Mesh Refinement: Global Criterion}
 \begin{block}{Criterion}
@@
 \begin{frame}
-  \frametitle{AMR vs.\ fully refined grid: Settings \textit{\&} time
-    to solution}
+  \frametitle{AMR vs.\ Fully Refined Grid: Settings \textit{\&} Time
+    To Solution}
   \begin{block}{Settings}
     \begin{description}
-    \item[AMR] Coarse mesh size with $27 \times 27$ cells, one adaptive level.
+    \item[AMR]
+      Mesh with sizes from $\SI{1000/81}{\m} = \SI{12.35}{\m}$ to $\SI{1000/3}{\m} = \SI{333.33}{\m}$.
 
-      Potentially up to $81 \times 81$ cells.
+      Two levels of dynamic AMR.
 
       $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$.
-    \item[Reference] $81 \times 81$ cells.
+    \item[Reference] $81 \times 81 = 6561$ cells.
     \end{description}
   \end{block}
-  Both polynomial order 4.
+  Both polynomial order 5. Viscosity $\mu = 0.01$. (?)
 
-  Fully refined grid took \textbf{71\%} longer!
+  AMR grid: 1953 cells.
+
+  Relative $L_2$-error between AMR and fully refined: \num{6.69e-6}.
 \end{frame}
@@
 \begin{frame}
-  \frametitle{AMR vs.\ fully refined grid: Grid}
-   \begin{figure}[h]
-    \centering
-    \ifratio{43}{
-    \movie[width=0.9\textwidth, height=0.6\textwidth, autostart,, loop, poster]{}{two_bubbles_legendre.ogv}
-  }{
-    \movie[width=0.7\textwidth, height=0.46666\textwidth, autostart,, loop, poster]{}{two_bubbles_legendre.ogv}
-  }
-    \caption{Two bubbles scenario, with \amr{}}
-  \end{figure}
+  \frametitle{AMR vs.\ Fully Refined Grid: Grid}
+
+  Here: Video/Figure of AMR grid
+  %  \begin{figure}[h]
+  %   \centering
+  %   \ifratio{43}{
+  %   \movie[width=0.9\textwidth, height=0.6\textwidth, autostart,, loop, poster]{}{two_bubbles_legendre.ogv}
+  % }{
+  %   \movie[width=0.7\textwidth, height=0.46666\textwidth, autostart,, loop, poster]{}{two_bubbles_legendre.ogv}
+  % }
+  %   \caption{Two bubbles scenario, with \amr{}}
+  % \end{figure}
 \end{frame}
@@
 \begin{frame}
-  \frametitle{AMR vs.\ fully refined grid: Error}
-  \begin{figure}[H]
-    \centering
-    \ifratio{43}{
-\includegraphics[width=0.9\textwidth]{thesis_two_bubbles_amr_error}
-  } {
-\includegraphics[width=0.6\textwidth]{thesis_two_bubbles_amr_error}
-  }
-\caption{Potential temperature of fully refined solution minus \amr{} solution.}
-  \end{figure}
+  \frametitle{AMR vs.\ Fully Refined Grid: Error}
+
+  Here: Figure AMR error on grid
+%   \begin{figure}[H]
+%     \centering
+%     \ifratio{43}{
+% %\includegraphics[width=0.9\textwidth]{thesis_two_bubbles_amr_error}
+%   } {
+% %\includegraphics[width=0.6\textwidth]{thesis_two_bubbles_amr_error}
+%   }
+% \caption{Potential temperature of fully refined solution minus \amr{} solution.}
+%   \end{figure}
+\end{frame}
+
+\begin{frame}{3D Cosine Bubble}
+  TODO
 \end{frame}
@@
 
-  \textbf{Stabilized} with (minmod) slope limiter
-
-  Problem in \exahype{}: Boundary conditions \textbf{unstable}, can only prescribe values at boundary.
-\end{frame}
-
-\begin{frame}{Finite Volume Limiting\footfullcite{dumbser2016simple}}
-  \begin{description}
-\item[ADER-DG] high order, but unstable
-\item[MUSCL] low order, but stable
-\item[Combination] high order \textbf{and} stable
-  \end{description}
-
-Recompute if solution:
-\begin{itemize}
-\item varies by a suspicious amount, using discrete maximum principle (\textsc{dmp}) as heuristic
-\item is NaN or $\infty$
-\item is unphysical
- \begin{equation}
-  \label{eq:limiting-physical}
-  \operatorname{is-admissible}(\Q) =
-  \begin{cases}
-    \text{true} & \Qrho > 0 \land \pressure > 0 \land \QZZ \geq 0 \\
-    \text{false} & \text{otherwise}
-  \end{cases}
-\end{equation}
-\end{itemize}
-\end{frame}
-
-\begin{frame}\frametitle{Reactive Source\footfullcite{hidalgo2011ader,helzel2000modified}}
-Source term for mass fraction $\QZ$:  
- \begin{equation}\label{eq:source-reaction}
-  \source[\QZ] =\begin{cases}
-  - \frac{1}{\reactionTimescale} \QZ  & T > \reactionTemperature\\
-  0 & \text{otherwise}
-\end{cases}  
-\end{equation}
-
-$\reactionTimescale = 0.01$ timescale of reaction.
-
-$\reactionTemperature$ activation temperature.
+  \textbf{Stabilized} with (minmod) slope limiter (TODO)
 \end{frame}
@@
 \begin{frame}
-  \frametitle{Result Reactive}
-   \begin{figure}[h]
-    \centering
-    \ifratio{43}{
-    \movie[width=0.9\textwidth, height=0.6\textwidth, autostart,, loop, poster]{}{detonation.ogv}
-  }{
-    \movie[width=0.7\textwidth, height=0.46666\textwidth, autostart,, loop, poster]{}{detonation.ogv}
-  }
-    \caption{Detonation. Height is pressure, color refinement.
-    Reactive Euler Equations.}
-  \end{figure}
+  \frametitle{Two Bubbles: Finite Volume}
+
+\end{frame}
+
+\begin{frame}
+  \frametitle{Other results?}
+  \begin{itemize}
+  \item Taylor-Green?
+  \item ABC-Flow?
+  \item Cavity?
+  \item 2D Cosine bubble?
+  \end{itemize}
 \end{frame}
@@
   \begin{block}{Results}
-  \begin{itemize}
-  \item \aderdg{} \textbf{converges} for Navier Stokes equations
-  \item \aderdg{} shows \textbf{good results} for large set of scenarios (many not shown here!)
-  \item \amr{}-criterion is \textbf{faster} and tracks cloud \textbf{correctly}.
-  \item (Limited) \aderdg{} works for reactive Euler \textit{\&} Navier-Stokes
-  \item All \textbf{extensions} to engine (diffusive fluxes, global observables) useful for \textbf{other users} of \exahype{}.
-  \end{itemize}
-  \end{block}
-
-  \begin{block}{Future Work}
-    \begin{itemize}
-    \item Extension to stiff source terms
-    \item Boundary conditions for \muscl{}.  
-    \end{itemize}
-
+  % \begin{itemize}
+  % \item \aderdg{} \textbf{converges} for Navier Stokes equations
+  % \item \aderdg{} shows \textbf{good results} for large set of scenarios (many not shown here!)
+  % \item \amr{}-criterion is \textbf{faster} and tracks cloud \textbf{correctly}.
+  % \item (Limited) \aderdg{} works for reactive Euler \textit{\&} Navier-Stokes
+  % \item All \textbf{extensions} to engine (diffusive fluxes, global observables) useful for \textbf{other users} of \exahype{}.
+  % \end{itemize}
   \end{block}
@@
 
-\appendix
-\begin{frame}
-  \frametitle{Reference Solution Two Bubbles\footfullcite{muller2010adaptive}}
-  \begin{center}
-    \ifratio{43}{
-\only<1>{\includegraphics[scale=0.8,trim={0cm 16.3cm 0cm 0cm}, clip]{beamer_two_bubbles_contour_collage_alternative}}
-\only<2>{\includegraphics[scale=0.8,trim={0cm 11.0cm 0cm 5.2cm}, clip]{beamer_two_bubbles_contour_collage_alternative}}
-\only<3>{\includegraphics[scale=0.8,trim={0cm 5.6cm 0cm 10.6cm}, clip]{beamer_two_bubbles_contour_collage_alternative}} 
-\only<4>{\includegraphics[scale=0.8,trim={0cm 0.0cm 0cm 16cm}, clip]{beamer_two_bubbles_contour_collage_alternative}}
+\begin{frame}{Acknowledgements}
+This project has received funding from the European Union's Horizon 2020 research and
+innovation programme under grant agreement No 823844 (ChEESE) and 671698 (ExaHyPE).
 
-} {
-\only<1>{\includegraphics[scale=1.0,trim={0cm 16.3cm 0cm 0cm}, clip]{beamer_two_bubbles_contour_collage_alternative}}
-\only<2>{\includegraphics[scale=1.0,trim={0cm 11.0cm 0cm 5.2cm}, clip]{beamer_two_bubbles_contour_collage_alternative}}
-\only<3>{\includegraphics[scale=1.0,trim={0cm 5.6cm 0cm 10.6cm}, clip]{beamer_two_bubbles_contour_collage_alternative}} 
-\only<4>{\includegraphics[scale=1.0,trim={0cm 0.0cm 0cm 16cm}, clip]{beamer_two_bubbles_contour_collage_alternative}}
-}
- \end{center}
+TODO: Grants correct?
+
+TODO: Logos
 \end{frame}
-
 \end{document}

### 2019-09-05 writing/slides/ppam.tex
Some small changes to ppam slides.

@@
 \title[High-Order DG with Dynamic AMR to Simulate Clouds]{A High-Order Discontinuous Galerkin Solver with Dynamic Adaptive Mesh Refinement to Simulate Cloud Formation Processes}
-\subtitle{PPAM 209}
-\author[L.\ Krenz, L.\ Rannabauer, M.\ Bader]{Lukas Krenz, Leonhard Rannabauer and Michael Bader}
-\date{\today} 
+\subtitle[PPAM]{PPAM 2019}
+%\author[L.\ Krenz, L.\ Rannabauer, M.\ Bader]{Lukas Krenz, Leonhard Rannabauer and Michael Bader}
+\author[Krenz, Rannabauer, Bader]{Lukas Krenz, Leonhard Rannabauer and Michael Bader}
+\date{10th September 2019} 
 \institute{Technical University of Munich}
@@
     \begin{itemize}
-    \item Optimized kernels for ADER-DG and a Finite Volume Scheme
+    \item Numerics: ADER-DG (optimized) \textit{\&} Finite Volume
     \item Dynamic Adaptive Mesh Refinement (AMR)
-    \item Hybrid MPI + Intel TBB Parallelism
+    \item Hybrid MPI + Intel TBB Parallelization
     \end{itemize}
@@
 \begin{frame}{The Navier-Stokes Equations}
-  TODO PDE Conservative form(?)
-  Vector of conserved quantities:
+\newcommand{\diffCoeff}{\varepsilon}%
+\newcommand{\hyperFluxDef}{
+  \begin{pmatrix}
+    \Qj \\
+    \Qv  \otimes \Qj + \bm{I} \pressure  \\
+    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure)
+  \end{pmatrix}
+}%
+\newcommand{\viscFluxDef}{
+  \begin{pmatrix}
+    0\\
+     \stressT (\Q, \gradQ)  \\
+     \Qv \cdot \stressT (\Q, \gradQ) - \kappa \gradient{T}
+   \end{pmatrix}
+}%
+
   \begin{equation}
-  \label{eq:conserved-variables}
- \Q = \left( \Qrho, \Qj, \QE \right) 
-\end{equation}
-With $\Qrho$ density of fluid, $\Qj$ velocity density and $\QE$ energy density
-
-Flux:
-\begin{equation}
-  F(\Q, \textcolor{orange}{\gradQ}) = 
+ \label{eq:equation-set} 
+%  \begin{array}{l}
+%  \text{mass cons.} \\
+%  \text{momentum cons.} \\
+%  \text{energy cons.} \\
+%  \text{cont.\ gas} 
+% \end{array}
+% :
+\quad
+  \pdv{}{t}
+  \underbrace{
+  \begin{pmatrix}
+    \Qrho\\
+    \Qj\\
+    \QE
+    \end{pmatrix}}_{\Q}
+  +
+  \divergence{\underbrace{
   \begin{pmatrix}
@@
     \textcolor{orange}{\kappa \nabla T}
-  \end{pmatrix}
+  \end{pmatrix}}}_{\flux(\Q, \gradQ)}
+ =
+  \underbrace{
+  \begin{pmatrix}
+    \source[\Qrho\phantom{\Qrho}]\\
+    - \bm{k} \Qrho g\\
+    \source[\QE]
+    \end{pmatrix}}_{\source(\Q, \bm{x}, t)}
 \end{equation}
+
+With $\Qrho$ density of fluid, $\Qj$ velocity density and $\QE$ energy density, $\bm{k}$ unit vector in z-direction.
 
@@
 stress tensor $\textcolor{orange}{\stressT}$, heat diffusion $\textcolor{orange}{\kappa \nabla T}$ with temperature $T$.
+
+\textbf{Trick}: cancel out constant background pressure in flux and source
+
 \end{frame}
+
+% \begin{frame}{The Navier-Stokes Equations}
+%   TODO PDE Conservative form(?)
+%   Vector of conserved quantities:
+% \begin{equation}
+%   \label{eq:conserved-variables}
+%  \Q = \left( \Qrho, \Qj, \QE \right) 
+% \end{equation}
+% With $\Qrho$ density of fluid, $\Qj$ velocity density and $\QE$ energy density
+
+% Flux:
+% \begin{equation}
+%   F(\Q, \textcolor{orange}{\gradQ}) = 
+%   \begin{pmatrix}
+%     \Qj \\
+%     \Qv  \otimes \Qj + \bm{I} \pressure + \textcolor{orange}{\stressT (\Q, \gradQ)}  \\
+%     \Qv \cdot \left(\bm{I} \QE + \bm{I} \pressure + \textcolor{orange}{\stressT (\Q, \gradQ)} \right) -
+%     \textcolor{orange}{\kappa \nabla T}
+%   \end{pmatrix}
+% \end{equation}
+
+% Pressure with gravitational term $\pressure(\Q, z)$,
+% stress tensor $\textcolor{orange}{\stressT}$, heat diffusion $\textcolor{orange}{\kappa \nabla T}$ with temperature $T$.
+% \end{frame}
 
@@
   ExahyPE (thus far) solves equations of the form (e.g.\ Euler):
-  TODO: Other terms in gray!
   \begin{equation}
   \label{eq:conservation-law}
- \pdv{\Q}{t} + \divergence{\flux(\Q)} = \source(\bm{x}, t, \Q)
+  \mathbf{\textcolor{gray}{P}}\pdv{\Q}{t} + \divergence{\flux(\Q)}
+ +  \textcolor{gray}{\sum_{i=1}^d \mathbf{B}_i (\mathbf{Q}) \pdv{\Q}{x_i}}
+  = \source(\bm{x}, t, \Q)
 \end{equation}
@@
   \label{eq:conservation-law-gradient}
- \pdv{\Q}{t} + \divergence{\flux(\Q, \textcolor{orange}{\gradQ})} = \source(\bm{x}, t, \Q)
+  \mathbf{\textcolor{gray}{P}}\pdv{\Q}{t} + \divergence{\flux(\Q, \textcolor{orange}{\gradQ})}
+ +  \textcolor{gray}{\sum_{i=1}^d \mathbf{B}_i (\mathbf{Q}) \pdv{\Q}{x_i}}
+  = \source(\bm{x}, t, \Q)
 \end{equation}
@@
 \begin{frame}{Adaptive Mesh Refinement: Indicator}
-  $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ maps solution to indicator variable.
+  \begin{block}{Total Variation}
+  $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ maps solution to indicator variable (here: potential temperature).
 
-  In our case: potential temperature.
-
-  Total variation of $\bm{x}$ for a cell $\cell$:
+  Total variation of $\bm{f}$ for a cell $\cell$:
 \begin{equation}
@@
 \end{equation}
+
+  \end{block}
 
@@
 \end{equation}
-Intuition: Not all variables are outliers.
+Mean $\mu$, standard deviation $\sigma$, constant $c$
+
+Better bounds exist with further assumptions on distribution.
+\end{block}
+
+\begin{block}{Intuition}
+Not all variables are sufficiently special.
+
 Feature detection
 \end{block}
+
 \end{frame}
@@
 Computation of mean $\mu$, standard deviation $\sigma$ with \textbf{stable}, pairwise reduction\footfullcite{chan1982updating}.
-
-Global observables implemented in \exahype{} for \textbf{general} pairwise reductions.
 \end{block}
@@
   \frametitle{Two Bubbles: Finite Volume}
-
-\end{frame}
-
-\begin{frame}
-  \frametitle{Other results?}
-  \begin{itemize}
-  \item Taylor-Green?
-  \item ABC-Flow?
-  \item Cavity?
-  \item 2D Cosine bubble?
-  \end{itemize}
+ TODO  
 \end{frame}
@@
   \begin{block}{Results}
+    \begin{itemize}
+    \item \textbf{ADER-DG} can be used to simulate Navier-Stokes equations.
+    \item Total variation \textbf{measures edges} of numerical solution.
+    \item Chebyshev's criterion finds \textbf{interesting cells}.
+    \item Combination of both \textbf{accurately tracks} cloud.
+    \item AMR solution is close to fully refined solution but \textbf{faster}.
+    \item \textbf{Artifical viscosity} of finite volume has a similar effect to \textbf{physical viscosity} of Navier-Stokes.  
+    \end{itemize}
   % \begin{itemize}
@@
 This project has received funding from the European Union's Horizon 2020 research and
-innovation programme under grant agreement No 823844 (ChEESE) and 671698 (ExaHyPE).
+innovation programme under grant agreement No 823844 (\textbf{ChEESE}) and 671698 (\textbf{ExaHyPE}).
 
@@
 
-TODO: Logos
+\begin{center}
+\includegraphics[width=0.7\textwidth]{logos}
+\end{center}
 \end{frame}

### 2019-09-06 writing/slides/ppam.tex
Update slides.

@@
   \frametitle{Two Bubbles: Simulation}
-  %  \begin{figure}[h]
-  %   \centering
-  %   \ifratio{43}{
-  %   \movie[width=0.9\textwidth, height=0.6\textwidth, autostart,, loop, poster]{}{two_bubbles_cartesian.ogv}
-  % } {
-  %   \movie[width=0.7\textwidth, height=0.466666\textwidth, autostart,, loop, poster]{}{two_bubbles_cartesian.ogv}
-  % }
-  %   \caption{Two Bubbles scenario}
-  % \end{figure}
-  Here: AMR simulation of two bubbles scenario (video)
+  \begin{center}
+   \ifratio{43}{
+%   \movie[width=0.9\textwidth, height=0.466666\textwidth, autostart,, loop, poster]{}{ppam_two_bubbles_cart.ogv}
+ } {
+   % todo: compute aspect ratio
+   \movie[width=0.5\textwidth, height=0.31891168599\textwidth,autostart,, loop, poster]{}{ppam_two_bubbles_cart.ogv}
+ }
+  \end{center}
 \end{frame}
@@
 
-\textbf{Discontinuous Galerkin} (\textsc{DG}) divides domain into disjoint elements, approximates solutions by piecewise-polynomials.
+\textbf{Discontinuous Galerkin} (DG) divides domain into disjoint elements, approximates solutions by piecewise-polynomials.
 Elements are connected by solving the Riemann problem.
 
-Implemented in the \textsc{PDE}-Framework \textbf{ExaHyPE}.
+\textbf{ADER}-Approach uses space-time polynomials for time integration instead of Runge-Kutta procedures.
 \end{frame}
@@
 
-With $\Qrho$ density of fluid, $\Qj$ velocity density and $\QE$ energy density, $\bm{k}$ unit vector in z-direction.
+With $\Qrho$ density of fluid, $\Qj$ velocity density, $\QE$ energy density, and $\bm{k}$ unit vector in z-direction.
 
@@
 
-% \begin{frame}{The Navier-Stokes Equations}
-%   TODO PDE Conservative form(?)
-%   Vector of conserved quantities:
-% \begin{equation}
-%   \label{eq:conserved-variables}
-%  \Q = \left( \Qrho, \Qj, \QE \right) 
-% \end{equation}
-% With $\Qrho$ density of fluid, $\Qj$ velocity density and $\QE$ energy density
-
-% Flux:
-% \begin{equation}
-%   F(\Q, \textcolor{orange}{\gradQ}) = 
-%   \begin{pmatrix}
-%     \Qj \\
-%     \Qv  \otimes \Qj + \bm{I} \pressure + \textcolor{orange}{\stressT (\Q, \gradQ)}  \\
-%     \Qv \cdot \left(\bm{I} \QE + \bm{I} \pressure + \textcolor{orange}{\stressT (\Q, \gradQ)} \right) -
-%     \textcolor{orange}{\kappa \nabla T}
-%   \end{pmatrix}
-% \end{equation}
-
-% Pressure with gravitational term $\pressure(\Q, z)$,
-% stress tensor $\textcolor{orange}{\stressT}$, heat diffusion $\textcolor{orange}{\kappa \nabla T}$ with temperature $T$.
-% \end{frame}
-
 \begin{frame}{Problem: Not hyperbolic}
-  ExahyPE (thus far) solves equations of the form (e.g.\ Euler):
+  ExaHyPE (thus far) solves equations of the form (e.g.\ Euler):
   \begin{equation}
@@
 \textbf{Solution}:
-Modify numerical flux (Riemann solver), time step size (\textsc{cfl}-Condition) and boundary conditions to \textbf{allow diffusive terms}\footfullcite{dumbser2010arbitrary,gassner2008discontinuous}.
+Modify numerical flux (Riemann solver), time step size (cfl-Condition) and boundary conditions to \textbf{allow diffusive terms}\footfullcite{dumbser2010arbitrary,gassner2008discontinuous}.
 
@@
 
-\begin{frame}{Adaptive Mesh Refinement: Outliers}
+\begin{frame}{Adaptive Mesh Refinement: Feature Detection}
   \begin{block}{Chebyshev's inequality}
@@
   \label{eq:chebychev}
-  \mathbb{P}(\vert X - \mu \vert \geq c \sigma) \leq \frac{1}{c^2}
+  \mathbb{P}(\vert X - \mu \vert \geq c \sigma) \leq \nicefrac{1}{c^2}
 \end{equation}
@@
   \begin{cases}
-    \text{refine} & \text{if } \tv(\Q) \geq \mu + T_\text{refine} \sigma \\
-    \text{delete} & \text{if } \tv(\Q) < \mu + T_\text{delete} \sigma \\
+    \text{refine} & \text{if } \tv\left(\bm{f}(\Q)\right) \geq \mu + T_\text{refine} \sigma \\
+    \text{delete} & \text{if } \tv\left(\bm{f}(\Q)\right) < \mu + T_\text{delete} \sigma \\
     \text{keep} & \text{otherwise}
@@
 \end{equation}
+Choose $T_\text{refine}$ and $T_\text{delete}$ according to cost-quality trade-off.
+
 Computation of mean $\mu$, standard deviation $\sigma$ with \textbf{stable}, pairwise reduction\footfullcite{chan1982updating}.
@@
   \end{block}
-  Both polynomial order 5. Viscosity $\mu = 0.01$. (?)
+  Both polynomial order 6. Viscosity $\mu = 0.01$.
 
-  AMR grid: 1953 cells.
+  AMR grid: 1953 cells. Less than \textbf{30\%} of full grid!
 
-  Relative $L_2$-error between AMR and fully refined: \num{6.69e-6}.
+  Relative $L_2$-error between AMR and fully refined: \num{2.6e-6}.
 \end{frame}
@@
   \frametitle{AMR vs.\ Fully Refined Grid: Grid}
-
-  Here: Video/Figure of AMR grid
   %  \begin{figure}[h]
@@
   % }{
-  %   \movie[width=0.7\textwidth, height=0.46666\textwidth, autostart,, loop, poster]{}{two_bubbles_legendre.ogv}
+  \begin{center}
+   \movie[width=0.5\textwidth, height=0.318911685990\textwidth, autostart,, loop, poster]{}{ppam_two_bubbles_leg.ogv}
+  \end{center}
   % }
@@
   \frametitle{AMR vs.\ Fully Refined Grid: Error}
-
-  Here: Figure AMR error on grid
-%   \begin{figure}[H]
-%     \centering
+  \begin{figure}[H]
+     \centering
 %     \ifratio{43}{
@@
 %   } {
-% %\includegraphics[width=0.6\textwidth]{thesis_two_bubbles_amr_error}
+\includegraphics[width=0.55\textwidth]{ppam_two_bubbles_amr_error}
 %   }
-% \caption{Potential temperature of fully refined solution minus \amr{} solution.}
-%   \end{figure}
+ \caption*{Potential temperature of fully refined solution minus AMR solution.}
+   \end{figure}
 \end{frame}
 
-\begin{frame}{3D Cosine Bubble}
-  TODO
+\begin{frame}{3D Cosine Bubble\footfullcite{kelly2012continuous}}
+  \begin{columns}
+    \begin{column}{0.6\textwidth}
+  \begin{center}
+    \includegraphics[width=0.85\textwidth]{ppam_cosine_bubble_3d}
+  \end{center}
+    \end{column}
+    \begin{column}{0.4\textwidth}
+      \begin{itemize}
+      \item Polynomial Order 3
+      \item $25^3$ cells
+      \item Time: \SI{400}{\s}
+      \item Viscosity: $\mu = 0.05$
+      \end{itemize}
+    \end{column}
+
+  \end{columns}
 \end{frame}
 
-\begin{frame}{MUSCL-Hancock Scheme~\footfullcite{vanLeer1979towards}}
+\begin{frame}{MUSCL-Hancock Scheme}
   Finite Volume scheme: store only \textbf{cell averages}
@@
 
-  \textbf{Second order} in time and space
+  \textbf{Second order} in time and space\footfullcite{vanLeer1979towards}
 
-  \textbf{Stabilized} with (minmod) slope limiter (TODO)
+  \textbf{Stabilized} with (Van Albada~\footfullcite{van1997comparative}) slope limiter
+
+  Very stable, larger \textbf{numerical viscosity}
 \end{frame}
@@
   \frametitle{Two Bubbles: Finite Volume}
- TODO  
+  \begin{center}
+    \includegraphics[width=0.6\textwidth]{paper_two_bubbles_fv}
+  \end{center}
 \end{frame}
@@
     \item Combination of both \textbf{accurately tracks} cloud.
-    \item AMR solution is close to fully refined solution but \textbf{faster}.
-    \item \textbf{Artifical viscosity} of finite volume has a similar effect to \textbf{physical viscosity} of Navier-Stokes.  
+    \item AMR solution is close to fully refined solution but needs \textbf{fewer} cells.
+    \item \textbf{Artificial viscosity} of finite volume has a similar effect as \textbf{physical viscosity} of Navier-Stokes.  
     \end{itemize}
@@
 
-\begin{frame}{Acknowledgements}
+\begin{frame}{Acknowledgments}
 This project has received funding from the European Union's Horizon 2020 research and
 innovation programme under grant agreement No 823844 (\textbf{ChEESE}) and 671698 (\textbf{ExaHyPE}).
-
-TODO: Grants correct?
 
@@
 \end{frame}
+
+\begin{frame}
+  \frametitle{Shared-Memory Scaling (from\footfullcite{reinarz2019exahype})}
+
+  \begin{center}
+  \includegraphics[width=0.4\textwidth]{speedup_tbb}
+  \end{center}
+
+\end{frame}
 \end{document}

### 2019-09-09 writing/slides/ppam.tex
Update FV slide.
Add updatred cosine bubble.
Update stuff.

@@
   hyperref=true,
-  maxnames=99,
+  maxnames=3,
   minnames=1,
@@
       \begin{itemize}
-      \item 
-  Air is in hydrostatic equilibrium:
+      \item Air is in hydrostatic equilibrium:
 
@@
   \item Constant potential temperature (temperature normalized by pressure) with larger, warm bubble and small, cold bubble on top.
-
   \end{itemize}
@@
     \begin{column}[t]{0.5\textwidth}
-      \begin{figure}[h]
-        \ifratio{43}{
+      \begin{center}
+%        \ifratio{43}{
           %\includegraphics{beamer_43_hydrostatic_equilibrium}
-        } {
-          %\includegraphics{beamer_169_hydrostatic_equilibrium}
-        }
-\caption{Background pressure in equilibrium}
-\end{figure}
+%        } {
+          \includegraphics[trim={0 0 0 0.5cm}, clip]{ppam_hydrostatic}
+%        }
+Background pressure in equilibrium
+\end{center}
     \end{column}
@@
    % todo: compute aspect ratio
-   \movie[width=0.5\textwidth, height=0.31891168599\textwidth,autostart,, loop, poster]{}{ppam_two_bubbles_cart.ogv}
+   %\movie[width=0.5\textwidth, height=0.31891168599\textwidth,autostart,, loop, poster]{}{ppam_two_bubbles_cart.ogv}
+   \movie[width=0.6\textwidth, height=0.37571265678449256\textwidth,autostart,loop , poster]{}{ppam_two_bubbles_cart.ogv}
  }
@@
     \textcolor{orange}{\kappa \nabla T}
-  \end{pmatrix}}}_{\flux(\Q, \gradQ)}
+  \end{pmatrix}}}_{\flux(\Q, \textcolor{orange}{\gradQ})}
  =
@@
 
-\textbf{Trick}: cancel out constant background pressure in flux and source
+\textbf{Trick}: cancel out constant background pressure in flux and source.
 
@@
 \textbf{Solution}:
-Modify numerical flux (Riemann solver), time step size (cfl-Condition) and boundary conditions to \textbf{allow diffusive terms}\footfullcite{dumbser2010arbitrary,gassner2008discontinuous}.
+Modify numerical flux (Riemann solver), time step size (CFL-condition) and boundary conditions to \textbf{allow diffusive terms}\footfullcite{dumbser2010arbitrary,gassner2008discontinuous}.
 
-\textcolor{orange}{No explicit discretization} of gradient $\gradQ$.
+\textbf{No explicit discretization} of gradient \textcolor{orange}{$\gradQ$}.
 \end{frame}
@@
 \end{equation}
-Choose $T_\text{refine}$ and $T_\text{delete}$ according to cost-quality trade-off.
+Choose $T_\text{refine}$ and $T_\text{delete}$ according to cost-accuracy trade-off.
 
@@
 \begin{frame}
-  \frametitle{AMR vs.\ Fully Refined Grid: Settings \textit{\&} Time
-    To Solution}
+  \frametitle{AMR vs.\ Fully Refined Grid}
   \begin{block}{Settings}
@@
   \end{block}
-  Both polynomial order 6. Viscosity $\mu = 0.01$.
+  Both polynomial order 6. Viscosity $\mu = 0.01$. Simulate until $t_\text{end} = \SI{600}{\s}$.
 
+  \begin{block}{Results}
   AMR grid: 1953 cells. Less than \textbf{30\%} of full grid!
@@
   Relative $L_2$-error between AMR and fully refined: \num{2.6e-6}.
+
+  \end{block}
 \end{frame}
@@
   \begin{center}
-   \movie[width=0.5\textwidth, height=0.318911685990\textwidth, autostart,, loop, poster]{}{ppam_two_bubbles_leg.ogv}
+   \movie[width=0.6\textwidth, height=0.382694023188\textwidth, autostart,, loop, poster]{}{ppam_two_bubbles_leg.ogv}
   \end{center}
@@
   \frametitle{Two Bubbles: Finite Volume}
+  \begin{columns}
+    \begin{column}{0.6\textwidth}
   \begin{center}
-    \includegraphics[width=0.6\textwidth]{paper_two_bubbles_fv}
+    \includegraphics[width=1.0\textwidth]{paper_two_bubbles_fv}
   \end{center}
+    \end{column}
+    \begin{column}{0.4\textwidth}
+      \begin{itemize}
+      \item $7^2$ patches with $90^2$ cells each
+      \item Euler equations ($\mu = 0$)
+      \item Numerical viscosity smooths solution
+      \end{itemize}
+    \end{column}
+  \end{columns}
 \end{frame}
@@
 \begin{frame}{Summary}
-  \begin{block}{Results}
     \begin{itemize}
@@
     \item AMR solution is close to fully refined solution but needs \textbf{fewer} cells.
-    \item \textbf{Artificial viscosity} of finite volume has a similar effect as \textbf{physical viscosity} of Navier-Stokes.  
+    \item \textbf{Artificial viscosity} of Finite Volume has a similar effect as \textbf{physical viscosity} of Navier-Stokes.  
     \end{itemize}
-  % \begin{itemize}
-  % \item \aderdg{} \textbf{converges} for Navier Stokes equations
-  % \item \aderdg{} shows \textbf{good results} for large set of scenarios (many not shown here!)
-  % \item \amr{}-criterion is \textbf{faster} and tracks cloud \textbf{correctly}.
-  % \item (Limited) \aderdg{} works for reactive Euler \textit{\&} Navier-Stokes
-  % \item All \textbf{extensions} to engine (diffusive fluxes, global observables) useful for \textbf{other users} of \exahype{}.
-  % \end{itemize}
-  \end{block}
 \end{frame}
@@
   \frametitle{Shared-Memory Scaling (from\footfullcite{reinarz2019exahype})}
-
   \begin{center}

### 2019-09-09 writing/slides/ppam.tex
Add 4:3 support for PPAM slides.

@@
 \documentclass[aspectratio=169]{beamer}
-%\documentclass[]{beamer}
-%\usepackage{eulervm}
-%\usetheme{metropolis} % Use metropolis theme
+%\documentclass[aspectratio=43]{beamer}
 \usepackage[conference]{beamertheme_tumtalk} % headline and footline
@@
 
-% \newcommand{\Qrho}{\ensuremath{\rho}}
-% \newcommand{\Qj}{\ensuremath{\rho \bm{v}}}
-% %\newcommand{\Qv}{\ensuremath{\Qrho^{-1} \Qj}}
-% \newcommand{\Qv}{\ensuremath{\bm{v}}}
-% \newcommand{\QE}{\ensuremath{\rho E}}
-% \newcommand{\stressT}{\ensuremath{\bm{\sigma}}}
-% \newcommand{\pressure}{\ensuremath{p}}
-% \newcommand{\maxConvEigen}{\ensuremath{\vert \lambda_c^{\text{max}} \vert}}
-% \newcommand{\maxViscEigen}{\ensuremath{\vert \lambda_v^{\text{max}} \vert}}
-
 \newcommand{\cn}{\footnote{\enquote{TODO: Citation.}, 2017, \textbf{Conference}, \textit{Author 1, Author 2, Author 3, Author 4} }}
 
+\ifratio{43} {
+\title[DG w/ AMR for Cloud Simulation]{A High-Order Discontinuous Galerkin Solver with Dynamic Adaptive Mesh Refinement to Simulate Cloud Formation Processes}
+} {
 \title[High-Order DG with Dynamic AMR to Simulate Clouds]{A High-Order Discontinuous Galerkin Solver with Dynamic Adaptive Mesh Refinement to Simulate Cloud Formation Processes}
+}
 \subtitle[PPAM]{PPAM 2019}
@@
       \begin{center}
-%        \ifratio{43}{
+        \ifratio{43}{
           %\includegraphics{beamer_43_hydrostatic_equilibrium}
-%        } {
+          \includegraphics[scale=0.8,trim={0 0 0 0.5cm}, clip]{ppam_hydrostatic}
+        } {
           \includegraphics[trim={0 0 0 0.5cm}, clip]{ppam_hydrostatic}
-%        }
+        }
 Background pressure in equilibrium
@@
    \ifratio{43}{
-%   \movie[width=0.9\textwidth, height=0.466666\textwidth, autostart,, loop, poster]{}{ppam_two_bubbles_cart.ogv}
+   \movie[width=0.8\textwidth, height=0.5009502090459902\textwidth,autostart,loop , poster]{}{ppam_two_bubbles_cart.ogv}
  } {
@@
     \item[AMR]
-      Mesh with sizes from $\SI{1000/81}{\m} = \SI{12.35}{\m}$ to $\SI{1000/3}{\m} = \SI{333.33}{\m}$.
+      Mesh with sizes from $\SI{1000/81}{\m} \approx \SI{12.35}{\m}$ to $\SI{1000/3}{\m} \approx \SI{333.33}{\m}$.
 
@@
   \begin{center}
+     \ifratio{43}{
+   \movie[width=0.8\textwidth, height=0.5102586975840001\textwidth, autostart,, loop, poster]{}{ppam_two_bubbles_leg.ogv}
+
+       } {
    \movie[width=0.6\textwidth, height=0.382694023188\textwidth, autostart,, loop, poster]{}{ppam_two_bubbles_leg.ogv}
+   }
   \end{center}
@@
      \centering
-%     \ifratio{43}{
-% %\includegraphics[width=0.9\textwidth]{thesis_two_bubbles_amr_error}
-%   } {
+     \ifratio{43}{
+\includegraphics[width=0.7\textwidth]{ppam_two_bubbles_amr_error}
+   } {
 \includegraphics[width=0.55\textwidth]{ppam_two_bubbles_amr_error}
-%   }
+   }
  \caption*{Potential temperature of fully refined solution minus AMR solution.}
@@
   \begin{center}
+    \ifratio{43}{
+    \includegraphics[width=0.95\textwidth]{ppam_cosine_bubble_3d}
+    } {
     \includegraphics[width=0.85\textwidth]{ppam_cosine_bubble_3d}
+    }
   \end{center}
@@
   \begin{center}
+    \ifratio{43}{
+  \includegraphics[width=0.5\textwidth]{speedup_tbb}
+    } {
   \includegraphics[width=0.4\textwidth]{speedup_tbb}
+    }
   \end{center}

### 2019-10-21 writing/paper/paper.tex
Remove footnote for single author.
Fix spacing in author list.
Fix keywords.
Change PPAM paper to recommended citation style.

@@
 \titlerunning{A High-Order DG Solver to Simulate Cloud Formation Processes}
-\author{Lukas Krenz\inst{1} \and{} Leonhard Rannabauer\inst{1} \and{} Michael Bader\inst{1}}
+\author{Lukas Krenz \and Leonhard Rannabauer \and Michael Bader}
 \authorrunning{L.\ Krenz, L.\ Rannabauer, M.\ Bader}
@@
 \usepackage[autostyle, english = american]{csquotes}
-\usepackage[%
-  backend=biber,
-  url=false,
-  doi=false,
-  % style=alphabetic,
-  % backref=true,
-  % hyperref=true,
-  maxnames=3,
-  % minnames=3,
-  % maxbibnames=99,
-  firstinits=true,
-  % uniquename=init
-  ]{biblatex}
-\DefineBibliographyStrings{english}{%
-  backrefpage = {see p.},
-  backrefpages = {see pp.}
-}
-\addbibresource{../bibliography.bib}
+% \usepackage[%
+%   backend=biber,
+%   url=false,
+%   doi=false,
+%   % style=alphabetic,
+%   % backref=true,
+%   % hyperref=true,
+%   maxnames=3,
+%   % minnames=3,
+%   % maxbibnames=99,
+%   firstinits=true,
+%   % uniquename=init
+%   ]{biblatex}
+% \addbibresource{../bibliography.bib}
+\newcommand{\citeauthor}{???}
 
@@
 
-\keywords{\aderdg{}  \and Navier-Stokes \and Adaptive Mesh Refinement.}
+\keywords{\aderdg{}  \and Navier-Stokes \and Adaptive Mesh Refinement}
 \end{abstract}
@@
 Due to the viscous components of the Navier-Stokes equations, it is not straightforward to apply the \aderdg{} formalism of~\cite{dumbser2008unified}, which addresses hyperbolic systems of partial differentials equations (\pde{}s) in first-order formulation.
-To include viscosity, we use the numerical flux for the compressible Navier-Stokes equations of \citeauthor{gassner2008discontinuous}~\cite{gassner2008discontinuous}.
+To include viscosity, we use the numerical flux for the compressible Navier-Stokes equations of Gassner et al.~\cite{gassner2008discontinuous}.
 This flux has already been applied to the \aderdg{} method in~\cite{dumbser2010arbitrary}.
@@
 
+\todo{Mention simulation order for two bubbles!}
 We have two bubbles, with constants
@@
 
-\printbibliography{}
+%\bibliographystyle{plain}
+\bibliographystyle{spmpsci}
+\bibliography{../bibliography}{}
+%\printbibliography{}
 \end{document}

### 2019-10-23 writing/paper/paper.tex
State more clearly that Taylor-Green/ABC are not an exact solution.
Add draft for manufactured solution.

@@
 \section{Results}
+\todo{Introduction of chapter}
+\todo{Introduce need for MMS}
+Following~\cite{dumbser2010arbitrary}, we assume that
+\begin{align}\label{eq:manufactured-solution}
+\begin{split}
+  \pressure(\bm{x}, t) &= \pressure_0 \cos( \bm{k} \bm{x} - \omega t ) + \pressure_b, \\
+  \Qrho(\bm{x}, t) &= \Qrho_0 \sin (\bm{k} \bm{x} - \omega t) + \Qrho_b, \\
+  \Qv(\bm{x}, t) &= \bm{v_0} \sin(\bm{k} \bm{x} - \omega t),
+\end{split}
+\end{align}
+is our analytical solution.
+We use the constants
+\begin{equation}
+\begin{alignedat}{6}
+  & \pressure_u &&= \nicefrac{1}{10}, \qquad& \pressure_b &= \nicefrac{1}{\gamma}, \\
+  & \Qrho_0 &&= \nicefrac{1}{2}, \qquad& \Qrho_b &= 1, \\
+  & \bm{v_0} &&= \nicefrac{1}{4},
+  \begin{pmatrix}
+    1 \\
+    1
+  \end{pmatrix},
+  \qquad& \bm{k} &= \nicefrac{\pi}{5}
+  \begin{pmatrix}
+    1\\
+    1
+  \end{pmatrix},\\
+  & \omega &&= 2 \pi.
+  \end{alignedat}
+\end{equation}
+\Cref{eq:manufactured-solution} does not solver the compressible Navier-Stokes equations \cref{eq:equation-set} directly but rather our equation set with ann added source term.
+We derive this source term symbolically with a computer algebra system.
+
 We use a mix of various benchmarking scenarios that consist of standard \textsc{cfd} scenarios and atmospheric flows.
-%
+
 For the standard \textsc{cfd} testing scenarios, we use the following constants of fluids:
@@
 \end{equation}
+
 A simple scenario is the Taylor-Green vortex.
@@
 A comparison at time $t = 10.0$ of the analytical solution for the pressure with our approximation (\cref{fig:taylor-green}) shows excellent agreement.
+Note that we only show a qualitative analysis because this is not an exact solution for our equation set.
 We used an \aderdg{}-scheme of order $5$ with a grid of $25^2$ cells.
@@
 \end{align}
-again under the assumption of incompressibility.
+again under the assumption of incompressibility, i.e.\ it is also not an exact solution of our \pde{}.
 The constant $C = \nicefrac{100}{\gamma}$ is chosen as before.

### 2019-10-29 writing/paper/paper.tex
Add some improvements to paper.

--- 2019-10-21 writing/paper/paper.tex
@@
   While established methods use numerics tailored towards the specific simulation, our scheme works scenario independent.
-  All together, our method can be seen as a perfect candidate for large scale cloud simulation runs on current and future super computers.
+  All together, our method can be seen as a perfect candidate for large scale cloud simulation runs on current and future super computers.\todo{Less bragging!}
 
@@
 \section{Results}
-We use a mix of various benchmarking scenarios that consist of standard \textsc{cfd} scenarios and atmospheric flows.
-%
-For the standard \textsc{cfd} testing scenarios, we use the following constants of fluids:
+In this section, we evaluate the quality of the results of our numerical methods and the scalability of our implementation.
+We use a mix of various benchmarking scenarios.
+After investigating the numerical convergence rate, we look at three standard \textsc{cfd} scenarios: the Taylor-Green vortex, the three-dimensional Arnold-Beltrami-Childress scenario and a lid-driven cavity flow.
+Finally, we evaluate the performance for stratified flow scenarios both in two and three dimensions.
+
+\subsection{CDF Testing Scenarios}
+We begin with a manuactured solution scenario which we can use for a convergence test.
+\todo{Introduce need for MMS}
+Unless mentioned otherwise, we use the following constants of fluids:
 \begin{equation}
@@
 \end{equation}
+Our description of the manufactured solution follows~\cite{dumbser2010arbitrary}.
+To construct this solution, we assume that
+% \begin{align}\label{eq:manufactured-solution}
+% \begin{split}
+%   \pressure(\bm{x}, t) &= \pressure_0 \cos( \bm{k} \bm{x} - \omega t ) + \pressure_b, \\
+%   \Qrho(\bm{x}, t) &= \Qrho_0 \sin (\bm{k} \bm{x} - \omega t) + \Qrho_b, \\
+%   \Qv(\bm{x}, t) &= \bm{v_0} \sin(\bm{k} \bm{x} - \omega t),
+% \end{split}
+% \end{align}
+\begin{align}\label{eq:manufactured-solution}
+  \begin{split}
+    \pressure(\bm{x}, t) &= 0.1 \cos( \bm{k} \bm{x} - 2 \pi t ) + \gamma^{-1}, \\
+    \Qrho(\bm{x}, t) &= 0.5 \sin (\bm{k} \bm{x} - 2 \pi t) + 1, \\
+    \Qv(\bm{x}, t) &= \bm{v_0} \sin(\bm{k} \bm{x} - 2 \pi t),
+  \end{split}
+  \end{align}
+solves our \pde{}.
+We use the constants $\bm{v_0} = \nicefrac{1}{4} \left( 1, 1 \right)^\intercal$ and $\bm{k} = \nicefrac{\pi}{5} \left( 1, 1 \right)^\intercal$ 
+% \begin{equation}
+% \begin{alignedat}{6}
+%   & \pressure_u &&= \nicefrac{1}{10}, \qquad& \pressure_b &= \nicefrac{1}{\gamma}, \\
+%   & \Qrho_0 &&= \nicefrac{1}{2}, \qquad& \Qrho_b &= 1, \\
+%   & \bm{v_0} &&= \nicefrac{1}{4},
+%   \begin{pmatrix}
+%     1 \\
+%     1
+%   \end{pmatrix},
+%   \qquad& \bm{k} &= \nicefrac{\pi}{5}
+%   \begin{pmatrix}
+%     1\\
+%     1
+%   \end{pmatrix},\\
+%   & \omega &&= 2 \pi.
+%   \end{alignedat}
+% \end{equation}
+Note that \Cref{eq:manufactured-solution} does not solve the compressible Navier-Stokes equations \cref{eq:equation-set} directly.
+It rather solves our equation set with an added source term which can be derived with a computer algebra system.
+We ran this scenario for a grid of combinations of order $1, \ldots 6$ and mesh sizes of $??? $.
+For this scenario, we achieve high-order convergence (\ref{fig:convergence-test}) but notice some diminishing returns for very large orders.
+\begin{figure}[htb]
+  \centering
+  ??? 
+  \caption{\label{fig:convergence-test}Mesh size vs.\ error for various orders.
+  Dashed lines show the theoretical order of convergence.}
+\end{figure}
+
+After we have established that the implementation of our numerical method converges, we are going to investigate three established testing scenarios from the field of computational fluid mechanics.
 A simple scenario is the Taylor-Green vortex.
-It has an analytical solution in the incompressible limit which is given by
+Assuming an incompressible fluid, it can written as
 \begin{align}
@@
 
-We simulate on the domain $[0,2\pi]^2$ 
-%We use a domain of size 
-%$(\SI{2 \pi}{\m} \times \SI{2 \pi}{\m})$ 
-%% keine Meter-Angaben bei analytischen Testcases
-and impose the analytical solution at the boundary.
+We simulate on the domain $[0,2\pi]^2$ and impose the analytical solution at the boundary.
 A comparison at time $t = 10.0$ of the analytical solution for the pressure with our approximation (\cref{fig:taylor-green}) shows excellent agreement.
+Note that we only show a qualitative analysis because this is not an exact solution for our equation set as we do assume compressibility of the fluid.
+This is nevertheless a valid comparison because for very low Mach numbers, both incompressible and compressible equations behave in a very similar manner.
 We used an \aderdg{}-scheme of order $5$ with a grid of $25^2$ cells.
@@
 
-The Arnold-Beltrami-Childress (\textsc{abc}) flow is similar to the Taylor-Green vortex but possesses an analytical solution for three-dimensions as well~\cite{tavelli2016staggered}.
+The Arnold-Beltrami-Childress (\textsc{abc}) flow is similar to the Taylor-Green vortex but is an analytical solution for the three-dimensions incompressible Navier-Stokes equations~\cite{tavelli2016staggered}.
 It is defined in the domain \( \left[ -\pi, \pi \right]^3 \) as
@@
 \end{align}
-again under the assumption of incompressibility.
 The constant $C = \nicefrac{100}{\gamma}$ is chosen as before.
@@
 Our results (\cref{fig:abc-flow}) show a good agreement between the analytical solution and our approximation with an \aderdg{}-scheme of order $3$ with a mesh consisting of $27^3$ cells at time $t = \SI{0.1}{\s}$.
+Again, we do not perform a quantative analysis as the \textsc{abc}-flow only solves our equation set approximately.
 
@@
 
+\subsection{Stratified Flow Scenarios}
 With the constants
@@
 
-\todo{Mention simulation order for two bubbles!}
 We have two bubbles, with constants
@@
 Hence, it is difficult to compare the parametrization directly.
-We ran this scenario twice: once without \amr{} and a mesh of size $\SI{1000/81}{\m} = \SI{12.35}{\m}$ and 
-once with \amr{} with two adaptive refinement levels and parameters $\Trefine = 2.5$ and $\Tdelete = -0.5$.
+We ran this scenario twice:
+once without \amr{} and a mesh of size $\SI{1000/81}{\m} = \SI{12.35}{\m}$ and once with \amr{} with two adaptive refinement levels and parameters $\Trefine = 2.5$ and $\Tdelete = -0.5$.
+For both settings we used polynomials of order 6.
 We specialize the \amr{}-criterion~\pcref{eq:refinement-criterion} to our stratified flows by using the potential temperature.
@@
 We observe that the $L_2$ difference between the potential temperature of the \amr{} run, which uses 1953 cells, and the one of the fully refined run with 6561 cells, is only $1.87$.
-The relative error is \num{6.69e-6}.
+The relative error is \num{6.69e-6}\todo{Update these numbers}.
 We further emphasize that our \amr{}-criterion accurately tracks the position of the edges of the cloud instead of only its position.
@@
 We found that the parameters presented in the manuscript of~\cite{kelly2012continuous} only agree with the results, if we use the same parameters as for 2D simulations.}.
-For the 2D case, we use a constant viscosity of $\mu = 0.01$ and an \aderdg{}-method of order 5 with two levels of dynamic \amr{}, resulting again in cell sizes of roughly $\SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.34}{\m}$.
+For the 2D case, we use a constant viscosity of $\mu = 0.01$ and an \aderdg{}-method of order 6 with two levels of dynamic \amr{}, resulting again in cell sizes of roughly $\SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.34}{\m}$.
 We use slightly different \amr{} parameters of $\Trefine = 1.5$ and $\Tdelete = -0.5$ and let the simulation run for \SI{600}{\s}.
@@
 
+\subsection{Performance Results}
+\todo{1--2 days on workstation}
+\todo{tbb scalability in MDOF/s}
+\todo{Resolution low enough: weak scaling would be more interesting}
+All two-dimensional scenarios presented in this paper can be run on a single workstation in less than two days.
+Parallel scalability was thus not the primary goal of this paper.
+Nevertheless, our implementation allows us to scale to small to medium scale setups using a combined MPI/TBB parallelization strategy.
+
+\newcommand{\mdofs}{M\text{DOF}/s}%
+We typically first choose a number of MPI ranks that ensure an equal load balancing.
+For two-dimensional simulations this happens for $1, 10, 83, \ldots$ ranks, as our underlying framework uses a three-way splitting per dimension and an additional communication rank per level.
+Then, we choose the number of nodes that we want to use and divide the cores into shared-memory sections.
+These are then distributed among TBB ranks.
+We ran the two bubble scenario for a uniform grid for 30 timesteps and for multiple combinations of MPI ranks and TBB threads.
+This simulation was performed on the SuperMUC-NG system using computational kernels that are optimized for its Skylake architecture\todo{Cite opt. kernels?}.
+Using a single MPI rank, we have xxx x $10^x$ degrees of freedom updates ($\mdofs$) using two TBB threads and xxx $10^x \mdofs$ using xxx threads.
+When using 5 nodes, we achieve $x \mdofs$ for two threads and $x \mdofs$ for xxx threads, when using two ranks per node.
+
 \section{Conclusion}
@@
 We showed that our \amr{}-criterion is able to vastly reduce the number of grid cells while preserving the quality of the results.
+
+Future work should be directed towards improving the scalability.
+As mentioned in the results section, the resolution is sufficient for most numerical weather prediction purposed.
+With an improved \amr{} scaling and some fine tuning of the parallelization strategy, the numerical method presented here might be a good candidate for the small-scale simulation of clouds.
 

### 2019-10-29 src/collect_convergence.py
Add convergence plot scripts.

@@ -1,0 +1,41 @@
+#!/usr/bin/env python3
+import glob
+import pandas as pd
+from collections import defaultdict
+
+def main():
+    files = list(sorted(glob.glob('*/solution.csv')))
+    print(files)
+    # dicts are order : value
+    data = defaultdict(list)
+    results = []
+    for file in files:
+        df = pd.read_csv(file)
+        df = df[df['norm'] == 'l2']
+        #print(df.columns)
+        order = df['order'].values[0]
+        hmin = df['hmin'].values[0]
+        error = df['var3'].values[0]
+        #print(order, error)
+        data[order].append((hmin, error))
+        results.append([order, hmin, error])
+
+    df = pd.DataFrame(results)
+    df.columns = ['order', 'hmin', 'error']
+    print(df)
+    df.to_csv('errors.csv', index=None)
+
+    for order, values in data.items():
+        print("\n{}".format(order))
+        error_sum = 0.0
+        error_count = 0
+        for hmin, error in values:
+            print("{} {}".format(hmin, error))
+            error_sum += error
+            error_count +=1
+        error_mean = error_sum/error_count
+        print()
+        print(error_mean)
+
+if __name__ == '__main__':
+    main()

### 2019-10-29 src/plot_convergence.py

@@ -1,0 +1,59 @@
+#!/usr/bin/env python3
+import numpy as np
+
+import matplotlib.pyplot as plt
+import seaborn as sns
+from sklearn.linear_model import LinearRegression
+
+from plot_utils import *
+from dataset_utils import *
+
+from matplotlib import ticker
+
+def plot_convergence(fig_path, solution_path, target):
+    df = pd.read_csv(solution_path)
+    orders = np.unique(df['order'])
+    fig, ax = plt.subplots(figsize=figsize(1.0, target=target))
+    colors = sns.color_palette("Paired")
+
+    for i, order in enumerate(orders):
+        cur_color = colors[i % len(colors)]
+        df_sub = df.loc[df['order'] == order, :]
+        x = df_sub['hmin']
+        y = df_sub['error']**0.5 # TODO: Is this correct?
+        ax.loglog(x, y, label="$P={}$".format(order), c=cur_color)
+        ax.scatter(x, y, c=cur_color, marker='x', label=None)
+
+        model = LinearRegression(fit_intercept=True)
+        model.fit(np.log(x.values.reshape(-1, 1)), np.log(y))
+    
+        print("Emp. conv. {} for theoretical order {}".format(model.coef_[0], order+1))
+
+        model.coef_[0] = order + 1
+        y_pred = np.exp(model.predict(np.log(x.values.reshape(-1, 1))))
+        ax.loglog(x, y_pred, linestyle='dashed', c=cur_color, label=None)
+
+    ax.set_xticks(np.unique(df['hmin']))
+    ax.set_xticklabels(["$10/3^{}$".format(i+1) for i in range(1,5)][::-1])
+    fig.gca().invert_xaxis()
+    fig.legend(loc='lower left', bbox_to_anchor=(0.095,0.16))
+    ax.set_xlabel('Grid spacing')
+    ax.set_ylabel('$L_2$ error')
+    sns.despine(fig, ax)
+
+    #fig.subplots_adjust(left=0.2, bottom=0.31, top=0.95, right=0.95)
+    fig.subplots_adjust(left=0.1, bottom=0.175, right=0.98, top=0.97)
+    fig.savefig(fig_path + '{target}_convergence.pdf'.format(target=target),
+                transparent=True)
+    
+
+def main():
+    set_plot_defaults()
+
+    fig_path = 'output/'
+    plot_convergence(fig_path=fig_path,
[…]

### 2019-10-30 writing/paper/paper.tex
Draft for camera ready version PPAM paper.

@@
 \institute{Department of Informatics, Technical University of Munich\\
-  \email{lukas.krenz@in.tum.de}, \email{rannabauer@in.tum.de}, \email{bader@in.tum.de}
+  \email{lukas.krenz@in.tum.de}, \email{rannabau@in.tum.de}, \email{bader@in.tum.de}
 \vspace*{-0.2cm}
@@
 \begin{abstract}
+  \todo{Mention corresponding author}
   We present a high-order discontinuous Galerkin (\dg{}) solver of the compressible Navier-Stokes equations for cloud formation processes.
@@
 
-\section{Results}
+\section{Results}\label{sec:results}
 In this section, we evaluate the quality of the results of our numerical methods and the scalability of our implementation.
@@
 solves our \pde{}.
-We use the constants $\bm{v_0} = \nicefrac{1}{4} \left( 1, 1 \right)^\intercal$ and $\bm{k} = \nicefrac{\pi}{5} \left( 1, 1 \right)^\intercal$ 
+We use the constants $\bm{v_0} = \nicefrac{1}{4} \left( 1, 1 \right)^\intercal$, $\bm{k} = \nicefrac{\pi}{5} \left( 1, 1 \right)^\intercal$ and simulate a domain of size $\left[ 10 \times 10 \right]$ for $\SI{0.5}{\s}$.
+The viscosity is set to $\mu = 0.1$.
 % \begin{equation}
@@
 It rather solves our equation set with an added source term which can be derived with a computer algebra system.
-We ran this scenario for a grid of combinations of order $1, \ldots 6$ and mesh sizes of $??? $.
-For this scenario, we achieve high-order convergence (\ref{fig:convergence-test}) but notice some diminishing returns for very large orders.
-\begin{figure}[htb]
+We ran this for a a combination of orders $1, \ldots 6$ and multiple grid sizes.
+Note that by order we mean the polynomial order throughout the entire paper and not the theoretical convergence order.
+For this scenario, we achieve high-order convergence (\ref{fig:convergence-test}) but notice some diminishing returns for large orders\todo{Maybe note that Dumbser doesnt get perfect convergence either.}.
+\begin{figure}[tb]
   \centering
-  ??? 
-  \caption{\label{fig:convergence-test}Mesh size vs.\ error for various orders.
-  Dashed lines show the theoretical order of convergence.}
+  \includegraphics{paper_convergence}
+  \caption{\label{fig:convergence-test}Mesh size vs.\ error for various polynomial orders $P$.
+    Dashed lines show the theoretical convergence order of $P+1$.}
 \end{figure}
@@
 A simple scenario is the Taylor-Green vortex.
-Assuming an incompressible fluid, it can written as
+Assuming an incompressible fluid, it can be written as
 \begin{align}
@@
 \end{align}
-The constant $C = \nicefrac{100}{\gamma}$ governs the speed of sound and thus the Mach number $\text{Ma} = 0.1$~\cite{dumbser2016high}. The viscosity is set to $\mu = 0.1$.
+The constant $C = \nicefrac{100}{\gamma}$ governs the speed of sound and thus the Mach number $\text{Ma} = 0.1$~\cite{dumbser2016high}.
+The viscosity is set to $\mu = 0.1$.
 
@@
   \centering
-  \begin{subfigure}[t]{.473\textwidth}
-    \centering
-    \includegraphics{paper_lid_driven_cavity}
-    \caption{\label{fig:cavity-flow}Our approximation (solid lines) of the lid-driven cavity flow vs.\ reference solution (crosses) of~\cite{ghia1982high}.
-    The respective other coordinate is held constant at a value of 0.}
-  \end{subfigure}\quad%
   \begin{subfigure}[t]{0.473\textwidth}
@@
     The plot shows two velocity slices, the respective other coordinate is held constant at a value of $\pi$.}
-
+  \end{subfigure}\qquad%
+\begin{subfigure}[t]{.473\textwidth}
+  \centering
+    \includegraphics{paper_abc_flow_velocity}
+    \captionof{figure}{\label{fig:abc-flow}Our approximation (markers) of the \textsc{abc}-flow vs.\ analytical solution (lines, \cref{eq:abc-flow}).
+    All other axes are held constant at a value of 0. We show every 6th value.}
+\end{subfigure}
     %\includegraphics{paper_abc_flow_velocity}
@@
     %The analytical solution is represented by lines, the numerical results by markers.}
-  \end{subfigure}
   \caption{Two dimensional \textsc{cfd} scenarios}
@@
     \centering
-    \includegraphics{paper_abc_flow_velocity}
-    \captionof{figure}{\label{fig:abc-flow}Our approximation (markers) of the \textsc{abc}-flow vs.\ analytical solution (lines, \cref{eq:abc-flow}).
-    All other axes are held constant at a value of 0. We show every 6th value.}
-\end{minipage}\qquad%
+    \includegraphics{paper_lid_driven_cavity}
+    \caption{\label{fig:cavity-flow}Our approximation (solid lines) of the lid-driven cavity flow vs.\ reference solution (crosses) of~\cite{ghia1982high}.
+    The respective other coordinate is held constant at a value of 0.}
+  \end{minipage}\quad%
 \begin{minipage}[t]{.473\textwidth}
@@
     \captionof{figure}{\label{fig:two-bubbles-fv}%
-    Colliding bubbles with \muscl{}. Contour values for potential temperature perturbation are $-0.05, 0.05, 0.1, \ldots 0.45$.}
+    Colliding bubbles with \muscl{}. Contour values for potential temperature perturbation are $-0.05, 0.05, 0.1, \ldots 0.45$. TODO UPDATE!}
 \end{minipage}
@@
 \begin{equation}\label{eq:atmosphere-constants}
-    \gamma = 1.4 ,\quad \Pr =  0.71 ,\quad R = 287.058 ,\quad p_0 = \SI{10e5}{\Pa}, \quad g = \SI{9.8}{m/s^2},
+    \gamma = 1.4 ,\quad \Pr =  0.71 ,\quad R = 287.058 ,\quad p_0 = 10^5 \SI{}{\Pa}, \quad g = \SI{9.8}{m/s^2},
 \end{equation}
@@
 \end{equation}
-Similar to~\cite{muller2010adaptive}, we use a constant viscosity of $\mu = 0.01$ to regularize the solution.
+Similar to~\cite{muller2010adaptive}, we use a constant viscosity of $\mu = 0.001$ to regularize the solution.
 Note that we use a different implementation of viscosity than~\cite{muller2010adaptive}.
@@
 The resulting mesh can be seen in \cref{fig:two-bubbles-ader}.
+In addition, we ran a simulation with the same settings for a polynomial order of 3.
+We can see~\pcref{fig:two-bubbles-ader} that the lower resolution leads to spurious wave and does not capure the behavior of the cloud.
+
 We observe that the $L_2$ difference between the potential temperature of the \amr{} run, which uses 1953 cells, and the one of the fully refined run with 6561 cells, is only $1.87$.
-The relative error is \num{6.69e-6}\todo{Update these numbers}.
+The relative error is \num{2.56e-6}.
 We further emphasize that our \amr{}-criterion accurately tracks the position of the edges of the cloud instead of only its position.
@@
 We found that the parameters presented in the manuscript of~\cite{kelly2012continuous} only agree with the results, if we use the same parameters as for 2D simulations.}.
-For the 2D case, we use a constant viscosity of $\mu = 0.01$ and an \aderdg{}-method of order 6 with two levels of dynamic \amr{}, resulting again in cell sizes of roughly $\SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.34}{\m}$.
-We use slightly different \amr{} parameters of $\Trefine = 1.5$ and $\Tdelete = -0.5$ and let the simulation run for \SI{600}{\s}.
+For the 2D case, we use a constant viscosity of $\mu = 0.001$ and an \aderdg{}-method of order 6 with two levels of dynamic \amr{}, resulting again in cell sizes of roughly $\SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.34}{\m}$.
+We use slightly different \amr{} parameters of $\Trefine = 1.5$ and $\Tdelete = -0.5$ and let the simulation run for \SI{700}{\s}.
 Note that, as seen in \cref{fig:cosine-2d}, our \amr{}-criterion tracks the wavefront of the cloud accurately.
@@
 For the 3D case, we use an \aderdg{}-scheme of order 3 with a static mesh with cell sizes of \SI{40}{\m} and a shorter simulation duration of \SI{400}{\s}.
-Due to the relatively coarse resolution and the hence increased aliasing errors, we need to increase the viscosity to $\mu = 0.05$.
+Due to the relatively coarse resolution and the hence increased aliasing errors, we need to increase the viscosity to $\mu = 0.005$.
 This corresponds to a larger amount of smoothing.
@@
   \centering
-  \includegraphics[width=0.90\textwidth]{paper_two_bubbles}
-  \caption{\label{fig:two-bubbles-ader}Colliding Bubbles with \aderdg{}. Contour values for potential temperature perturbation are $-0.05, 0.05, 0.1, \ldots 0.45$.}
+  \includegraphics[width=1.0\textwidth]{paper_two_bubbles}
+  \caption{\label{fig:two-bubbles-ader}Colliding Bubbles with \aderdg{}. Contour values for potential temperature perturbation are $-0.05, 0.05, 0.1, \ldots 0.45$.
+  Right: Comparison of small scale structure between order 3 (top) and order 6 (bottom).}
 \end{figure}
@@
     \centering
-    \includegraphics[width=\textwidth, trim={0cm 0 23cm 0},clip]{paper_cosine_bubble_collage}
+    \includegraphics[scale=0.16, trim={0cm 0 32cm 0},clip]{paper_cosine_bubble_collage}
     %\includegraphics[width=\textwidth]{paper_cosine_bubble}
@@
     \centering
-    \includegraphics[width=\textwidth, trim={23cm 0 0cm 0},clip]{paper_cosine_bubble_collage}
-    %\includegraphics[width=\textwidth]{paper_cosine_bubble_3d}
+    \includegraphics[scale=0.16, trim={42cm 0 0cm 0},clip]{paper_cosine_bubble_collage}
     \caption{\label{fig:cosine-3d}3D Cosine Bubble}
   \end{subfigure}
-  \caption{\label{fig:cosine-bubbles-results}Cosine Bubble Scenario}
+  \caption{\label{fig:cosine-bubbles-results}Cosine Bubble Scenario.}
 \end{figure}
 
-\subsection{Performance Results}
-\todo{1--2 days on workstation}
-\todo{tbb scalability in MDOF/s}
-\todo{Resolution low enough: weak scaling would be more interesting}
+\subsection{Scalability}%
+\newcommand{\mdofs}{M\text{DOF}/s}%
 All two-dimensional scenarios presented in this paper can be run on a single workstation in less than two days.
 Parallel scalability was thus not the primary goal of this paper.
-Nevertheless, our implementation allows us to scale to small to medium scale setups using a combined MPI/TBB parallelization strategy.
-
-\newcommand{\mdofs}{M\text{DOF}/s}%
+Nevertheless, our implementation allows us to scale to small to medium scale setups using a combined \mpi{}~+~\tbb{} parallelization strategy, which works a follows:
 We typically first choose a number of MPI ranks that ensure an equal load balancing.
@@
 These are then distributed among TBB ranks.
-We ran the two bubble scenario for a uniform grid for 30 timesteps and for multiple combinations of MPI ranks and TBB threads.
+We ran the two bubble scenario for a uniform grid with a mesh size of $729 \times 729$ for 20 timesteps and for multiple combinations of \mpi{} ranks and \tbb{} threads.
 This simulation was performed on the SuperMUC-NG system using computational kernels that are optimized for its Skylake architecture\todo{Cite opt. kernels?}.
-Using a single MPI rank, we have xxx x $10^x$ degrees of freedom updates ($\mdofs$) using two TBB threads and xxx $10^x \mdofs$ using xxx threads.
-When using 5 nodes, we achieve $x \mdofs$ for two threads and $x \mdofs$ for xxx threads, when using two ranks per node.
+Using a single MPI rank, we have roughly $4.9$ millions degrees of freedom updates ($\mdofs$) using two TBB threads and $20.15 \mdofs$ using 24 threads (i.e.\ a half node).
+For a full node with 48 threads, we get a performance of $12 \mdofs$.
+When using 5 nodes with 10 \mpi{} ranks, we achieve $29.3 \mdofs$ for two threads and $137.3 \mdofs$ for 24 threads.
 
+We further note that for our scenarios weak scaling is more important than strong scaling, as we currently cover only a small area containing a single cloud, where in practical applications one would like to smilate more complex scenarios.
 \section{Conclusion}
-We presented an implementation of an \aderdg{}-method and a \muscl{}-scheme with \amr{} for the Navier-Stokes equations, based on the \exahypeengine.
+We presented an implementation of a \muscl{}-scheme and an \aderdg{}-method with \amr{} for the Navier-Stokes equations, based on the \exahypeengine.
 Our implementation is capable of simulating different scenarios:
@@
 Future work should be directed towards improving the scalability.
-As mentioned in the results section, the resolution is sufficient for most numerical weather prediction purposed.
-With an improved \amr{} scaling and some fine tuning of the parallelization strategy, the numerical method presented here might be a good candidate for the small-scale simulation of clouds.
+As mentioned in \cref{sec:results}, the resolution is sufficient for most numerical weather prediction purposes\todo{Actually mention this}.
+With an improved \amr{} scaling and some fine tuning of the parallelization strategy, the numerical method presented here might be a good candidate for the simulation of small scale convection processes that lead to cloud formation processes.
 

### 2019-10-30 src/plot_abc.py

@@ -93,9 +93,10 @@ def plot_abc(fig_path, solution_path, target, order=2):
 
 def main():
     set_plot_defaults()
-    fig_path='output/'
+    fig_path='output_cpc/'
     plot_abc(fig_path=fig_path,
-                      solution_path='/work_fast/krenz/abc_flow/solution_cartesian-0.vtu',
+		      solution_path='/work/krenz/cpc_paper/output/sol_cart-0-rank-0.vtu',
+                      #solution_path='/work_fast/krenz/abc_flow/solution_cartesian-0.vtu',
                       target='paper')
         
 if __name__ == '__main__':

### 2019-10-30 src/plot_convergence.py

@@ -13,7 +13,7 @@ from matplotlib import ticker
 def plot_convergence(fig_path, solution_path, target):
     df = pd.read_csv(solution_path)
     orders = np.unique(df['order'])
-    fig, ax = plt.subplots(figsize=figsize(1.0, target=target))
+    fig, ax = plt.subplots(figsize=figsize(0.9, target=target))
     colors = sns.color_palette("Paired")
 
     for i, order in enumerate(orders):
@@ -36,13 +36,14 @@ def plot_convergence(fig_path, solution_path, target):
     ax.set_xticks(np.unique(df['hmin']))
     ax.set_xticklabels(["$10/3^{}$".format(i+1) for i in range(1,5)][::-1])
     fig.gca().invert_xaxis()
-    fig.legend(loc='lower left', bbox_to_anchor=(0.095,0.16))
+    fig.legend(loc='lower left', bbox_to_anchor=(0.15,0.16),
+               handlelength=0.7, ncol=2)
     ax.set_xlabel('Grid spacing')
     ax.set_ylabel('$L_2$ error')
     sns.despine(fig, ax)
 
     #fig.subplots_adjust(left=0.2, bottom=0.31, top=0.95, right=0.95)
-    fig.subplots_adjust(left=0.1, bottom=0.175, right=0.98, top=0.97)
+    fig.subplots_adjust(left=0.15, bottom=0.175, right=0.98, top=0.97)
     fig.savefig(fig_path + '{target}_convergence.pdf'.format(target=target),
                 transparent=True)
     

### 2019-10-30 writing/paper/paper.tex
Add more grammar to paper.

@@
 \let\boundary\undefined%
-\crefformat{equation}{\eqA{}Eq.~\eqB #2#1#3)}
+\crefformat{equation}{\eqA{}eq.~\eqB #2#1#3)}
 % TODO: Fix for more than two equations!
@@
 \begin{abstract}
-  \todo{Mention corresponding author}
+  \todo{Corresp.\ author, ORCID next to authors}
   We present a high-order discontinuous Galerkin (\dg{}) solver of the compressible Navier-Stokes equations for cloud formation processes.
@@
 We use a mix of various benchmarking scenarios.
-After investigating the numerical convergence rate, we look at three standard \textsc{cfd} scenarios: the Taylor-Green vortex, the three-dimensional Arnold-Beltrami-Childress scenario and a lid-driven cavity flow.
-Finally, we evaluate the performance for stratified flow scenarios both in two and three dimensions.
+After investigating the numerical convergence rate, we look at three standard \textsc{cfd} scenarios: the Taylor-Green vortex, the three-dimensional Arnold-Beltrami-Childress flow and a lid-driven cavity flow.
+Finally, we evaluate the performance for stratified flow scenarios in both two and three dimensions.
 
 \subsection{CDF Testing Scenarios}
-We begin with a manuactured solution scenario which we can use for a convergence test.
-\todo{Introduce need for MMS}
-Unless mentioned otherwise, we use the following constants of fluids:
+We begin with a manufactured solution scenario which we can use for a convergence test.
+We use the following constants of fluids for all scenarios in this section:
 \begin{equation}
@@
   \begin{split}
-    \pressure(\bm{x}, t) &= 0.1 \cos( \bm{k} \bm{x} - 2 \pi t ) + \gamma^{-1}, \\
-    \Qrho(\bm{x}, t) &= 0.5 \sin (\bm{k} \bm{x} - 2 \pi t) + 1, \\
+    \pressure(\bm{x}, t) &= \nicefrac{1}{10} \cos( \bm{k} \bm{x} - 2 \pi t ) + \nicefrac{1}{\gamma}, \\
+    \Qrho(\bm{x}, t) &= \nicefrac{1}{2} \sin (\bm{k} \bm{x} - 2 \pi t) + 1, \\
     \Qv(\bm{x}, t) &= \bm{v_0} \sin(\bm{k} \bm{x} - 2 \pi t),
@@
 Note that by order we mean the polynomial order throughout the entire paper and not the theoretical convergence order.
-For this scenario, we achieve high-order convergence (\ref{fig:convergence-test}) but notice some diminishing returns for large orders\todo{Maybe note that Dumbser doesnt get perfect convergence either.}.
+For this scenario, we achieve high-order convergence (\cref{fig:convergence-test}) but notice some diminishing returns for large orders\todo{Maybe note that Dumbser doesnt get perfect convergence either.}.
 \begin{figure}[tb]
@@
 A comparison at time $t = 10.0$ of the analytical solution for the pressure with our approximation (\cref{fig:taylor-green}) shows excellent agreement.
-Note that we only show a qualitative analysis because this is not an exact solution for our equation set as we do assume compressibility of the fluid.
-This is nevertheless a valid comparison because for very low Mach numbers, both incompressible and compressible equations behave in a very similar manner.
+Note that we only show a qualitative analysis because this is not an exact solution for our equation set as we assume compressibility of the fluid.
+This is nevertheless a valid comparison because for very low Mach numbers, both incompressible and compressible equations behave in a very similarly.
 We used an \aderdg{}-scheme of order $5$ with a grid of $25^2$ cells.
-
+%
 \begin{figure}[tb]
@@
     %The analytical solution is represented by lines, the numerical results by markers.}
-  \caption{Two dimensional \textsc{cfd} scenarios}
-  \label{fig:cdf-results}
+  \caption{\label{fig:cdf-results}Two dimensional \textsc{cfd} scenarios}
 \end{figure}
 
-The Arnold-Beltrami-Childress (\textsc{abc}) flow is similar to the Taylor-Green vortex but is an analytical solution for the three-dimensions incompressible Navier-Stokes equations~\cite{tavelli2016staggered}.
+The Arnold-Beltrami-Childress (\textsc{abc}) flow is similar to the Taylor-Green vortex but is an analytical solution for the three-dimensional incompressible Navier-Stokes equations~\cite{tavelli2016staggered}.
 It is defined in the domain \( \left[ -\pi, \pi \right]^3 \) as
@@
 Our results (\cref{fig:abc-flow}) show a good agreement between the analytical solution and our approximation with an \aderdg{}-scheme of order $3$ with a mesh consisting of $27^3$ cells at time $t = \SI{0.1}{\s}$.
-Again, we do not perform a quantative analysis as the \textsc{abc}-flow only solves our equation set approximately.
+Again, we do not perform a quantitative analysis as the \textsc{abc}-flow only solves our equation set approximately.
 
@@
     \captionof{figure}{\label{fig:two-bubbles-fv}%
-    Colliding bubbles with \muscl{}. Contour values for potential temperature perturbation are $-0.05, 0.05, 0.1, \ldots 0.45$. TODO UPDATE!}
+    Colliding bubbles with \muscl{}. Contour values for potential temperature perturbation are $-0.05, 0.05, 0.1, \ldots 0.45$.}
 \end{minipage}
@@
 \subsection{Stratified Flow Scenarios}
+Our main focus is the simulation of stratified flow scenarios.
+In the following, we present bubble convection scenarios in both two and three dimensions.
 With the constants
@@
 \end{equation}
-all following stratified flow scenarios are described in terms of the potential temperature
+all following scenarios are described in terms of the potential temperature
 \begin{equation}
@@
 
+\begin{figure}[tb]
+  \centering
+  \includegraphics[width=1.0\textwidth]{paper_two_bubbles}
+  \caption{\label{fig:two-bubbles-ader}Left: Colliding Bubbles with \aderdg{}. Contour values for potential temperature perturbation are $-0.05, 0.05, 0.1, \ldots 0.45$.\\
+  Right: Comparison of small scale structure between order 3 (top) and order 6 (bottom).}
+\end{figure}
 We have two bubbles, with constants
@@
 In addition, we ran a simulation with the same settings for a polynomial order of 3.
-We can see~\pcref{fig:two-bubbles-ader} that the lower resolution leads to spurious wave and does not capure the behavior of the cloud.
+We can see~\pcref{fig:two-bubbles-ader} that the lower resolution leads to spurious wave and does not capture the behavior of the cloud.
 
@@
 \begin{equation}\label{eq:cosine-bubble}
-  A = \SI{0.5}{\K} \quad a = \SI{250}{\m} \quad x_c = \SI{500}{\m} \quad z_c = \SI{350}{\m}.
+  A = \SI{0.5}{\K}, \quad a = \SI{250}{\m}, \quad x_c = \SI{500}{\m}, \quad z_c = \SI{350}{\m}.
 \end{equation}
@@
 Our results (\cref{fig:cosine-3d}) capture the dynamics of the scenario well and agree with the reference solution of~\cite{kelly2012continuous}.
-
-\begin{figure}[tb]
-  \centering
-  \includegraphics[width=1.0\textwidth]{paper_two_bubbles}
-  \caption{\label{fig:two-bubbles-ader}Colliding Bubbles with \aderdg{}. Contour values for potential temperature perturbation are $-0.05, 0.05, 0.1, \ldots 0.45$.
-  Right: Comparison of small scale structure between order 3 (top) and order 6 (bottom).}
-\end{figure}
 
@@
 Nevertheless, our implementation allows us to scale to small to medium scale setups using a combined \mpi{}~+~\tbb{} parallelization strategy, which works a follows:
-We typically first choose a number of MPI ranks that ensure an equal load balancing.
-For two-dimensional simulations this happens for $1, 10, 83, \ldots$ ranks, as our underlying framework uses a three-way splitting per dimension and an additional communication rank per level.
+We typically first choose a number of \mpi{} ranks that ensure an equal load balancing.
+For two-dimensional simulations this happens for $1, 10, 83, \ldots$ ranks, as our underlying framework uses three-way splittings for each level and per dimension and an additional communication rank per level.
 Then, we choose the number of nodes that we want to use and divide the cores into shared-memory sections.
-These are then distributed among TBB ranks.
+These are then distributed among \tbb{} ranks.
+
 We ran the two bubble scenario for a uniform grid with a mesh size of $729 \times 729$ for 20 timesteps and for multiple combinations of \mpi{} ranks and \tbb{} threads.
 This simulation was performed on the SuperMUC-NG system using computational kernels that are optimized for its Skylake architecture\todo{Cite opt. kernels?}.
-Using a single MPI rank, we have roughly $4.9$ millions degrees of freedom updates ($\mdofs$) using two TBB threads and $20.15 \mdofs$ using 24 threads (i.e.\ a half node).
+Using a single \mpi{} rank, we get roughly $4.9$ millions degrees of freedom updates ($\mdofs$) using two \tbb{} threads and $20.15 \mdofs$ using 24 threads (i.e.\ a half node).
 For a full node with 48 threads, we get a performance of $12 \mdofs$.
@@
 
-We further note that for our scenarios weak scaling is more important than strong scaling, as we currently cover only a small area containing a single cloud, where in practical applications one would like to smilate more complex scenarios.
+We further note that for our scenarios weak scaling is more important than strong scaling, as we currently cover only a small area containing a single cloud, where in practical applications one would like to simulate more complex scenarios.
 \section{Conclusion}
@@
 Our implementation is capable of simulating different scenarios:
-We evaluated our method for standard \textsc{cfd} scenarios and achieved competitive results for all used scenarios.
-This is true for both two-dimensional scenarios (Taylor-Green vortex and lid-driven cavity) and for the three-dimensional \textsc{abc}-flow.
+We show that our method has high order convergence and we successfully evaluated our method for standard \textsc{cfd} scenarios:
+We have competitive results for both two-dimensional scenarios (Taylor-Green vortex and lid-driven cavity) and for the three-dimensional \textsc{abc}-flow.
 
@@
 Future work should be directed towards improving the scalability.
-As mentioned in \cref{sec:results}, the resolution is sufficient for most numerical weather prediction purposes\todo{Actually mention this}.
 With an improved \amr{} scaling and some fine tuning of the parallelization strategy, the numerical method presented here might be a good candidate for the simulation of small scale convection processes that lead to cloud formation processes.
@@
 No~823844 (ChEESE centre of excellence, \url{www.cheese-coe.eu}).
-Computing resources were provided by the Leibniz Supercomputing Centre (project pr83no).
+Computing resources were provided by the Leibniz Supercomputing Centre (project pr83no\todo{Mention other project?}).
 Special thanks go to Dominic E.\ Charrier for his support with the implementation in the \exahypeengine{}.

### 2019-10-31 writing/paper/paper.tex
Fix more stuff for PPAM 2019.

@@
 \titlerunning{A High-Order DG Solver to Simulate Cloud Formation Processes}
-\author{Lukas Krenz \and Leonhard Rannabauer \and Michael Bader}
+\author{Lukas Krenz\orcidID{0000-0001-6378-0778} \and Leonhard Rannabauer \and Michael Bader}
 \authorrunning{L.\ Krenz, L.\ Rannabauer, M.\ Bader}
@@
 % \addbibresource{../bibliography.bib}
+\usepackage{cite}
 \newcommand{\citeauthor}{???}
@@
 \usepackage{hyperref}
-\usepackage[]{cleveref}
+\usepackage[capitalise]{cleveref}
 \newcommand{\creflastconjunction}{, and\nobreakspace} % use Oxford comma
@@
 \let\boundary\undefined%
-\crefformat{equation}{\eqA{}eq.~\eqB #2#1#3)}
+\crefformat{equation}{\eqA{}Eq.~\eqB #2#1#3)}
 % TODO: Fix for more than two equations!
@@
 \begin{abstract}
-  \todo{Corresp.\ author, ORCID next to authors}
+  % We present a high-order discontinuous Galerkin (\dg{}) solver of the compressible Navier-Stokes equations for cloud formation processes.
+  % The scheme exploits an underlying parallelized implementation of the \aderdg{} method with dynamic adaptive mesh refinement. 
+  % We improve our method by a \pde{}-independent general refinement criterion, based on the local total variation of the numerical solution.
+  % Our generic scheme shows competitive results for both classical \textsc{cfd} and stratified scenarios.
+  % While established methods use numerics tailored towards the specific simulation, our scheme works scenario independent.
+  % All together, our method can be seen as a perfect candidate for large scale cloud simulation runs on current and future super computers.\todo{Less bragging!}
    We present a high-order discontinuous Galerkin (\dg{}) solver of the compressible Navier-Stokes equations for cloud formation processes.
@@
   We improve our method by a \pde{}-independent general refinement criterion, based on the local total variation of the numerical solution.
+  While established methods use numerics tailored towards the specific simulation, our scheme works scenario independent.
   Our generic scheme shows competitive results for both classical \textsc{cfd} and stratified scenarios.
-  While established methods use numerics tailored towards the specific simulation, our scheme works scenario independent.
-  All together, our method can be seen as a perfect candidate for large scale cloud simulation runs on current and future super computers.\todo{Less bragging!}
-
+  We focus on two dimensional simulations of two bubble convection scenarios over a background atmosphere.
+  The largest simulation here uses order 6 and 6561 cells which were reduced to 1953 cells by the refinement criterion.
+ \todo{Abstract---ideas for last two sentences. Note that adding one sentence leads to more pages.}
+% 
 \keywords{\aderdg{}  \and Navier-Stokes \and Adaptive Mesh Refinement}
@@
 Note that by order we mean the polynomial order throughout the entire paper and not the theoretical convergence order.
-For this scenario, we achieve high-order convergence (\cref{fig:convergence-test}) but notice some diminishing returns for large orders\todo{Maybe note that Dumbser doesnt get perfect convergence either.}.
+For this scenario, we achieve high-order convergence (\cref{fig:convergence-test}) but notice some diminishing returns for large orders\todo{Here a sentence regarding convergence would be nice---Dumbser got better results}.
 \begin{figure}[tb]
@@
 A simple scenario is the Taylor-Green vortex.
-Assuming an incompressible fluid, it can be written as
+Assuming an \textit{incompressible} fluid, it can be written as
 \begin{align}
@@
     %The analytical solution is represented by lines, the numerical results by markers.}
-  \caption{\label{fig:cdf-results}Two dimensional \textsc{cfd} scenarios}
+  \caption{\label{fig:cdf-results}Two-dimensional \textsc{cfd} scenarios}
 \end{figure}
 
-The Arnold-Beltrami-Childress (\textsc{abc}) flow is similar to the Taylor-Green vortex but is an analytical solution for the three-dimensional incompressible Navier-Stokes equations~\cite{tavelli2016staggered}.
+The Arnold-Beltrami-Childress (\textsc{abc}) flow is similar to the Taylor-Green vortex but is an analytical solution for the three-dimensional \textit{incompressible} Navier-Stokes equations~\cite{tavelli2016staggered}.
 It is defined in the domain \( \left[ -\pi, \pi \right]^3 \) as
@@
 The resulting mesh can be seen in \cref{fig:two-bubbles-ader}.
-In addition, we ran a simulation with the same settings for a polynomial order of 3.
-We can see~\pcref{fig:two-bubbles-ader} that the lower resolution leads to spurious wave and does not capture the behavior of the cloud.
 
 We observe that the $L_2$ difference between the potential temperature of the \amr{} run, which uses 1953 cells, and the one of the fully refined run with 6561 cells, is only $1.87$.
-The relative error is \num{2.56e-6}.
+The relative error is \num{2.6e-6}.
 We further emphasize that our \amr{}-criterion accurately tracks the position of the edges of the cloud instead of only its position.
@@
 Overall, our result for this benchmark shows an excellent agreement to the previous solutions of~\cite{muller2010adaptive}.
+In addition, we ran a simulation with the same settings for a polynomial order of 3.
+The lower resolution leads to spurious waves~(\cref{fig:two-bubbles-ader}) and does not capture the behavior of the cloud.
 
-In addition, we simulated the same scenario with our \muscl{} method, using $7^2$ patches with $90^2$ finite volume cells each.
+Furthermore, we simulated the same scenario with our \muscl{} method, using $7^2$ patches with $90^2$ finite volume cells each.
 As we use limiting, we do not need any viscosity.
@@
 \subsection{Scalability}%
-\newcommand{\mdofs}{M\text{DOF}/s}%
+\newcommand{\mdofs}{\text{MDOF/s}}%
 All two-dimensional scenarios presented in this paper can be run on a single workstation in less than two days.
 Parallel scalability was thus not the primary goal of this paper.
-Nevertheless, our implementation allows us to scale to small to medium scale setups using a combined \mpi{}~+~\tbb{} parallelization strategy, which works a follows:
+Nevertheless, our implementation allows us to scale to small to medium scale setups using a combined \mpi{}~+~Thread building blocks(\tbb{}) parallelization strategy, which works a follows:
 We typically first choose a number of \mpi{} ranks that ensure an equal load balancing.
-For two-dimensional simulations this happens for $1, 10, 83, \ldots$ ranks, as our underlying framework uses three-way splittings for each level and per dimension and an additional communication rank per level.
-Then, we choose the number of nodes that we want to use and divide the cores into shared-memory sections.
-These are then distributed among \tbb{} ranks.
+\exahype{} achieves best scalability for $1, 10, 83, \ldots$ ranks, as our underlying framework uses three-way splittings for each level and per dimension and an additional communication rank per level.
+For the desired number of compute nodes, we then determine the number of \tbb{} threads per rank to match the number of total available cores.
 
-We ran the two bubble scenario for a uniform grid with a mesh size of $729 \times 729$ for 20 timesteps and for multiple combinations of \mpi{} ranks and \tbb{} threads.
-This simulation was performed on the SuperMUC-NG system using computational kernels that are optimized for its Skylake architecture\todo{Cite opt. kernels?}.
-Using a single \mpi{} rank, we get roughly $4.9$ millions degrees of freedom updates ($\mdofs$) using two \tbb{} threads and $20.15 \mdofs$ using 24 threads (i.e.\ a half node).
+We ran the two bubble scenario for a uniform grid with a mesh size of $729 \times 729$ with order 6, resulting in roughly 104 million degrees of freedom (\textsc{dof}), for 20 timesteps and for multiple combinations of \mpi{} ranks and \tbb{} threads\todo{Check number of dofs?
+Should be $(6+1)^2 * 729^2$, right?}.
+This simulation was performed on the SuperMUC-NG system using computational kernels that are optimized for its Skylake architecture.
+Using a single \mpi{} rank, we get roughly $4.9$ millions \textsc{dof} updates ($\mdofs$) using two \tbb{} threads and $20.15 \mdofs$ using 24 threads (i.e.\ a half node).
 For a full node with 48 threads, we get a performance of $12 \mdofs$.
@@
 No~823844 (ChEESE centre of excellence, \url{www.cheese-coe.eu}).
-Computing resources were provided by the Leibniz Supercomputing Centre (project pr83no\todo{Mention other project?}).
+Computing resources were provided by the Leibniz Supercomputing Centre (project pr83no).
 Special thanks go to Dominic E.\ Charrier for his support with the implementation in the \exahypeengine{}.
 
-%\bibliographystyle{plain}
 \bibliographystyle{spmpsci}
 \bibliography{../bibliography}{}
-%\printbibliography{}
 \end{document}

### 2019-10-31 writing/paper/paper.tex
Preperations for camera ready (1).

@@
 \vspace*{-0.2cm}
-} % todo emails and stuff
+} 
 \usepackage[utf8]{inputenc}
@@
 \newcommand{\creflastconjunction}{, and\nobreakspace} % use Oxford comma
-\usepackage{todonotes}
+\usepackage{graphicx}
 \usepackage{multimedia}
-\graphicspath{{../figures/}}
+%\graphicspath{{../figures/}}
+\graphicspath{{.}}
 \let\boundary\undefined%
 \crefformat{equation}{\eqA{}Eq.~\eqB #2#1#3)}
-% TODO: Fix for more than two equations!
 \crefmultiformat{equation}{Eqs.~\eqMultiA#2#1#3\eqMultiB}%
@@
 \usepackage{bm}
-\input{../thesis/macros.tex}
+% Commands/Macros
+\newcommand{\muscl}{\textsc{muscl}-Hancock}
+\newcommand{\dg}{\textsc{dg}}
+\newcommand{\ader}{\textsc{ader}}
+\newcommand{\aderdg}{\textsc{ader-dg}}
+\newcommand{\amr}{\textsc{amr}}
+\newcommand{\pde}{\textsc{pde}}
+\newcommand{\tbb}{\textsc{tbb}}
+\newcommand{\mpi}{\textsc{mpi}}
+
+\newcommand{\softwareName}[1]{#1}
+\newcommand{\exahype}{\softwareName{ExaHyPE}}
+\newcommand{\exahypeengine}{\softwareName{ExaHyPE Engine}}
+
+% Variables and other equation stuff
+\newcommand{\Q}{\bm{Q}}
+\newcommand{\gradQ}{\gradient{\Q}}
+\newcommand{\Qrho}{\rho}
+\newcommand{\Qj}{\rho \bm{v}}
+\newcommand{\Qv}{\bm{v}}
+\newcommand{\QE}{\rho E}
+\newcommand{\potT}{\theta}
+\newcommand{\backgroundPotT}{\overline{\theta}}
+\newcommand{\pertubationPotT}{\theta'}
+\newcommand{\stressT}{\bm{\sigma}}
+\newcommand{\pressure}{p}
+
+% Cells
+\newcommand{\cell}[1][]{C_{#1}}
+
+% Bold if no index is supplied.
+\newcommand{\bmempty}[2]{
+\notblank{#2}{#1}{\bm{#1}}
+}
+
+% Equation parts
+\newcommand{\flux}{\bm{F}}
+\newcommand{\viscFlux}{\flux^{v}}
+\newcommand{\hyperFlux}{\flux^{h}}
+%\newcommand{\source}{\bm{S}}
+\newcommand{\source}[1][]{
+  \notblank{#1}{
+S_{#1}
+}{
+\bm{S}
+}
+}
+\newcommand{\intdcell}[1]{\int_{\cell} #1 \dd{\bm{x}}}
+\newcommand{\tv}{\operatorname{TV}}
 
@@
 \begin{abstract}
-  % We present a high-order discontinuous Galerkin (\dg{}) solver of the compressible Navier-Stokes equations for cloud formation processes.
-  % The scheme exploits an underlying parallelized implementation of the \aderdg{} method with dynamic adaptive mesh refinement. 
-  % We improve our method by a \pde{}-independent general refinement criterion, based on the local total variation of the numerical solution.
-  % Our generic scheme shows competitive results for both classical \textsc{cfd} and stratified scenarios.
-  % While established methods use numerics tailored towards the specific simulation, our scheme works scenario independent.
-  % All together, our method can be seen as a perfect candidate for large scale cloud simulation runs on current and future super computers.\todo{Less bragging!}
 We present a high-order discontinuous Galerkin (\dg{}) solver of the compressible Navier-Stokes equations for cloud formation processes.
@@
 The largest simulation here uses order 6 and 6561 cells which were reduced to 1953 cells by the refinement criterion.
- \todo{Abstract---ideas for last two sentences. Note that adding one sentence leads to more pages.}
 %
@@
 Note that by order we mean the polynomial order throughout the entire paper and not the theoretical convergence order.
-For this scenario, we achieve high-order convergence (\cref{fig:convergence-test}) but notice some diminishing returns for large orders\todo{Here a sentence regarding convergence would be nice---Dumbser got better results}.
+For this scenario, we achieve high-order convergence (\cref{fig:convergence-test}) but notice some diminishing returns for large orders.
 \begin{figure}[tb]
   \centering
-  \includegraphics{paper_convergence}
+  \includegraphics{CP032_convergence}
   \caption{\label{fig:convergence-test}Mesh size vs.\ error for various polynomial orders $P$.
@@
     \centering
-    \includegraphics{paper_taylor_green_vel}
+    \includegraphics{CP032_taylor_green_vel}
     \caption{\label{fig:taylor-green}Our result (markers) of the Taylor-Green vortex vs.\ the analytical solution (lines) \cref{eq:taylor-green}.
@@
   \centering
-    \includegraphics{paper_abc_flow_velocity}
+    \includegraphics{CP032_abc_flow_velocity}
     \captionof{figure}{\label{fig:abc-flow}Our approximation (markers) of the \textsc{abc}-flow vs.\ analytical solution (lines, \cref{eq:abc-flow}).
@@
     \centering
-    \includegraphics{paper_lid_driven_cavity}
+    \includegraphics{CP032_lid_driven_cavity}
     \caption{\label{fig:cavity-flow}Our approximation (solid lines) of the lid-driven cavity flow vs.\ reference solution (crosses) of~\cite{ghia1982high}.
@@
   \centering
-    \includegraphics[width=\textwidth]{paper_two_bubbles_fv}
+    \includegraphics[width=\textwidth]{CP032_two_bubbles_fv}
     \captionof{figure}{\label{fig:two-bubbles-fv}%
@@
   \centering
-  \includegraphics[width=1.0\textwidth]{paper_two_bubbles}
+  \includegraphics[width=1.0\textwidth]{CP032_two_bubbles}
   \caption{\label{fig:two-bubbles-ader}Left: Colliding Bubbles with \aderdg{}. Contour values for potential temperature perturbation are $-0.05, 0.05, 0.1, \ldots 0.45$.\\
@@
     \centering
-    \includegraphics[scale=0.16, trim={0cm 0 32cm 0},clip]{paper_cosine_bubble_collage}
+    \includegraphics[scale=0.16, trim={0cm 0 32cm 0},clip]{CP032_cosine_bubble_collage}
     %\includegraphics[width=\textwidth]{paper_cosine_bubble}
-    \caption{\label{fig:cosine-2d}2D Cosine Bubble.}%todo: Contour lines?
+    \caption{\label{fig:cosine-2d}2D Cosine Bubble.}%
   \end{subfigure}~%
@@
     \centering
-    \includegraphics[scale=0.16, trim={42cm 0 0cm 0},clip]{paper_cosine_bubble_collage}
+    \includegraphics[scale=0.16, trim={42cm 0 0cm 0},clip]{CP032_cosine_bubble_collage}
     \caption{\label{fig:cosine-3d}3D Cosine Bubble}
@@
 
-We ran the two bubble scenario for a uniform grid with a mesh size of $729 \times 729$ with order 6, resulting in roughly 104 million degrees of freedom (\textsc{dof}), for 20 timesteps and for multiple combinations of \mpi{} ranks and \tbb{} threads\todo{Check number of dofs?
-Should be $(6+1)^2 * 729^2$, right?}.
+We ran the two bubble scenario for a uniform grid with a mesh size of $729 \times 729$ with order 6, resulting in roughly 104 million degrees of freedom (\textsc{dof}), for 20 timesteps and for multiple combinations of \mpi{} ranks and \tbb{} threads.
 This simulation was performed on the SuperMUC-NG system using computational kernels that are optimized for its Skylake architecture.

### 2019-10-31 writing/paper/paper.tex
Fix typo.

@@
 We focus on two dimensional simulations of two bubble convection scenarios over a background atmosphere.
-The largest simulation here uses order 6 and 6561 cells which were reduced to 1953 cells by the refinement criterion.
+The largest simulation here uses order 6 and 6561 cells which were reduced to 1953 cells by our refinement criterion.
 %
@@
 
-\subsection{CDF Testing Scenarios}
+\subsection{CFD Testing Scenarios}
 We begin with a manufactured solution scenario which we can use for a convergence test.
@@
 It rather solves our equation set with an added source term which can be derived with a computer algebra system.
-We ran this for a a combination of orders $1, \ldots 6$ and multiple grid sizes.
+We ran this for a a combination of orders $1, \ldots, 6$ and multiple grid sizes.
 Note that by order we mean the polynomial order throughout the entire paper and not the theoretical convergence order.
@@
 Parallel scalability was thus not the primary goal of this paper.
-Nevertheless, our implementation allows us to scale to small to medium scale setups using a combined \mpi{}~+~Thread building blocks(\tbb{}) parallelization strategy, which works a follows:
+Nevertheless, our implementation allows us to scale to small to medium scale setups using a combined \mpi{}~+~Thread building blocks~(\tbb{}) parallelization strategy, which works as follows:
 We typically first choose a number of \mpi{} ranks that ensure an equal load balancing.
@@
 This simulation was performed on the SuperMUC-NG system using computational kernels that are optimized for its Skylake architecture.
-Using a single \mpi{} rank, we get roughly $4.9$ millions \textsc{dof} updates ($\mdofs$) using two \tbb{} threads and $20.15 \mdofs$ using 24 threads (i.e.\ a half node).
+Using a single \mpi{} rank, we get roughly $4.9$ millions \textsc{dof} updates ($\mdofs$) using two \tbb{} threads and $20.2 \mdofs$ using 24 threads (i.e.\ a half node).
 For a full node with 48 threads, we get a performance of $12 \mdofs$.

### 2019-10-31 writing/paper/CP032.tex
Fix spacing issue. Rename stuff.

--- 2019-10-31 writing/paper/paper.tex
@@
   \email{lukas.krenz@in.tum.de}, \email{rannabau@in.tum.de}, \email{bader@in.tum.de}
-\vspace*{-0.2cm}
 } 
@@
 \begin{itemize}%
-\item We extend the \exahypeengine{} to allow viscous terms following the aforementioned numerical scheme.
+\item We extend the \exahypeengine{} to allow viscous terms.
 \item We thus provide an implementation of the compressible Navier-Stokes equations.
@@
 
-\bibliographystyle{spmpsci}
-\bibliography{../bibliography}{}
+\bibliographystyle{CP032_spmpsci}
+\bibliography{CP032_bibliography}{}
 \end{document}

### 2022-06-21 writing/erratum/CP032.tex
Add initial draft of erratum

--- 2019-10-31 writing/paper/CP032.tex
@@
 \documentclass[runningheads]{llncs}
-\title{A High-Order Discontinuous Galerkin Solver with Dynamic Adaptive Mesh Refinement to Simulate Cloud Formation Processes }
+\title{Erratum: A High-Order Discontinuous Galerkin Solver with Dynamic Adaptive Mesh Refinement to Simulate Cloud Formation Processes }
 \titlerunning{A High-Order DG Solver to Simulate Cloud Formation Processes}
@@
 \begin{abstract}
-We present a high-order discontinuous Galerkin (\dg{}) solver of the compressible Navier-Stokes equations for cloud formation processes.
-The scheme exploits an underlying parallelized implementation of the \aderdg{} method with dynamic adaptive mesh refinement. 
-We improve our method by a \pde{}-independent general refinement criterion, based on the local total variation of the numerical solution.
-While established methods use numerics tailored towards the specific simulation, our scheme works scenario independent.
-Our generic scheme shows competitive results for both classical \textsc{cfd} and stratified scenarios.
-We focus on two dimensional simulations of two bubble convection scenarios over a background atmosphere.
-The largest simulation here uses order 6 and 6561 cells which were reduced to 1953 cells by our refinement criterion.
-%
+
 \keywords{\aderdg{}  \and Navier-Stokes \and Adaptive Mesh Refinement}
 \end{abstract}
-\section{Introduction}
-In this paper we address the resolution of basic cloud formation processes on modern super computer systems.
-The simulation of cloud formations, as part of convective processes, is expected to play an important role in future numerical weather prediction~\cite{bauer2015quiet}.
-This requires both suitable physical models and effective computational realizations. 
-Here we focus on the simulation of simple benchmark scenarios~\cite{giraldo2008study}.
-They contain relatively small scale effects which are well approximated with the compressible Navier-Stokes equations.
-We use the \aderdg{} method of~\cite{dumbser2008unified}, which allows us to simulate the Navier-Stokes equations with a space-time-discretization of arbitrary high order.
-In contrast to Runge-Kutta time integrators or semi-implicit methods, an increase of the order of \aderdg{} only results in larger computational kernels and does not affect the complexity of the scheme.
-Additionally, \aderdg{} is a communication avoiding scheme and reduces the overhead on larger scale.
-We see our scheme in the regime of already established methods for cloud simulations, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
 
-Due to the viscous components of the Navier-Stokes equations, it is not straightforward to apply the \aderdg{} formalism of~\cite{dumbser2008unified}, which addresses hyperbolic systems of partial differentials equations (\pde{}s) in first-order formulation.
-To include viscosity, we use the numerical flux for the compressible Navier-Stokes equations of Gassner et al.~\cite{gassner2008discontinuous}.
-This flux has already been applied to the \aderdg{} method in~\cite{dumbser2010arbitrary}.
-In contrast to this paper, we focus on the simulation of complex flows with a gravitational source term and a realistic background atmosphere.
-Additionally, we use adaptive mesh refinement (\textsc{amr}) to increase the spatial resolution in areas of interest.
-This has been shown to work well for the simulation of cloud dynamics~\cite{muller2010adaptive}.
-Regarding the issue of limiting in high-order \dg{} methods, we note that viscosity not only models the correct physics of the problem but also smooths oscillations and discontinuities, thus stabilizing the simulation.
+\subsection{Erratum}
+This is an erratum for \cite{krenz2019high}.
+When trying to reproduce the results, we noticed that we erronously computed the cloud scenarios with a different background pressure and viscosity as stated in the paper.
+As the former may result in different physical results, we here evaluated the simulations with the correct background pressure of $\ldots$.
+In our paper, while viscosity follows the Navier-Stokes equations, we use it additionally to stabilize the simulation.
+Neither classical CFD scenarios (Taylor-Green, Lid-driven cavity, 3D scenario) nor the convergence test are affected by this.
+We recomputed the key results with correct background pressure.
 
-We base our work on the \exahypeengine{} (\url{www.exahype.eu}), which is a framework that can solve arbitrary hyperbolic \pde\ systems.
-A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well-posed Cauchy problem for a system of hyperbolic \pde{}s of first order.
-The underlying \aderdg{} method, parallelization techniques and dynamic adaptive mesh refinement are available for simulations while the implementations are left as a black box to the user.
-An introduction to the communication-avoiding implementation of the whole numerical scheme can be found in~\cite{charrier2018stop}.
+The first scenario is the cosine bubble scenario with and without adaptive mesh refinement (AMR).
+We ran it as described in the paper but with the correct background pressure and a viscosity of $\mu = \ldots$. 
+%TODO Refinement settings.
+Figure XXX depicts the results.
+Both show an excellent agreement with the original results.
+The AMR simulation shows slight differences in the refinement; however, the refinement has the same quality as the original one.
 
-To summarize, we make the following contributions in this paper:%
-\begin{itemize}%
-\item We extend the \exahypeengine{} to allow viscous terms.
-\item We thus provide an implementation of the compressible Navier-Stokes equations.
-  In addition, we tailor the equation set to stratified flows with gravitational source term.
-  We emphasize that we use a standard formulation of the Navier-Stokes equations as seen in the field of computational fluid mechanics and only use small modifications of the governing equations, in contrast to a equation set that is tailored exactly to the application area.
-\item We present a general \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
-  Furthermore, we show how to utilize this criterion for stratified flows.
-\item We evaluate our implementation with standard \textsc{cfd} scenarios and atmospheric flows and inspect the effectiveness of our proposed \amr{}-criterion.
-  We thus inspect, whether our proposed general implementation can achieve results that are competitive with the state-of-the-art models that rely on heavily specified equations and numerics.
-\end{itemize}
-%
-\section{Equation Set}
-\newcommand{\diffCoeff}{\varepsilon}%
-\newcommand{\hyperFluxDef}{
-  \begin{pmatrix}
-    \Qj \\
-    \Qv  \otimes \Qj + \bm{I} \pressure  \\
-    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure)
-  \end{pmatrix}
-}%
-\newcommand{\viscFluxDef}{
-  \begin{pmatrix}
-    0\\
-     \stressT (\Q, \gradQ)  \\
-     \Qv \cdot \stressT (\Q, \gradQ) - \kappa \gradient{T}
-   \end{pmatrix}
-}%
-% \begin{equation}
-%   \label{eq:ns-short}
-%  \pdv{}{t} \bm{Q} + \divergence{\bm{F}(\bm{Q}, \gradient{\bm{Q}})} = \bm{S}(\bm{Q}) 
-% \end{equation}
-The compressible Navier-Stokes equations in the conservative form are given as% \pcref{eq:conservation-law-gradient}
-\begin{equation}
- \label{eq:equation-set} 
-%  \begin{array}{l}
-%  \text{mass cons.} \\
-%  \text{momentum cons.} \\
-%  \text{energy cons.} \\
-%  \text{cont.\ gas} 
-% \end{array}
-% :
-\quad
-  \pdv{}{t}
-  \underbrace{
-  \begin{pmatrix}
-    \Qrho\\
-    \Qj\\
-    \QE
-    \end{pmatrix}}_{\Q}
-  +
-  \divergence{
-  \underbrace{
-  \left(
-   \underbrace{\hyperFluxDef}_{\hyperFlux(\Q)}
-+
-\underbrace{\viscFluxDef}_{\viscFlux(\Q, \gradQ)}
-  \right)}_{\flux(\Q, \gradQ)}}
- =
-  \underbrace{
-  \begin{pmatrix}
-    \source[\Qrho\phantom{\Qrho}]\\
-    \source[\Qj]\\
-    \source[\QE]
-    \end{pmatrix}}_{\source(\Q, \bm{x}, t)}
-\end{equation}
-with the vector of conserved quantities $\Q$, flux $\flux(\Q, \gradQ)$ and source $\source(\Q)$.
-Note that the flux can be split into a hyperbolic part $\hyperFlux(\Q)$,
-which is identical to the flux of the Euler equations,
-and a viscous part $\viscFlux(\Q, \gradQ)$.
-The conserved quantities
-\(\Q\)
-% \begin{equation} 
-%   \label{eq:conserved-variables}
-%  \Q = \left( \Qrho, \Qj, \QE, \QZ \right),
-% \end{equation}
-are the density $\Qrho$, the two or three-dimensional momentum $\Qj$ and the energy density $\QE$.
-The rows of \cref{eq:equation-set} are the conservation of mass, the conservation of momentum and the conservation of energy.
+The second scenario is the colliding bubble scenario.
+We ran this with the Finite Volume method using a viscosity of $\mu=0$.
+The results (Figure xxx) agree with the original results.
+We also ran this with the ADER-DG method, with and without AMR (Figure XXX).
+Similarly to the cosine bubble, the results show an excellent agreement with the original results (with some small differences in the refinement).
 
-The pressure $\pressure$ is given by the equation of state of an ideal gas
-\begin{equation}
-  \label{eq:eos}
-  \pressure = (\gamma - 1) \left(\QE - \frac{1}{2} \left(\Qv \cdot \Qj \right) - gz \right).
-\end{equation}
-The term $gz$ is the geopotential height with the gravity of Earth $g$~\cite{giraldo2008study}.
-The temperature $T$ relates to the pressure by the thermal equation of state
-\begin{equation}
-  \label{eq:temperature}
-  \pressure = \Qrho R T,
-\end{equation}
-where $R$ is the specific gas constant of a fluid.
+The third scenario is the three-dimensional cosine bubble.
+We ran this with a viscosity of $\mu = \ldots$.
+The results (Figure XXX) agree with our original simulations.
 
-We model the diffusivity by the stress tensor
-\begin{equation}
-  \label{eq:stress-tensor}
-  \stressT(\Q, \gradQ) =
-  \mu
-  \bigl(
-  \left(\nicefrac{2}{3} \divergence{\Qv} \right) -
-  \left( \gradient{\Qv} + \gradient{\Qv}^\intercal \right)
-  \bigr),
-\end{equation}
-with constant viscosity $\mu$.
-The heat diffusion is governed by the coefficient
-\begin{equation}
-  \label{eq:heat-conduction-coeff}
-  \kappa = \frac{\mu \gamma}{\Pr} \frac{1}{\gamma - 1} R = \frac{\mu c_p}{\Pr},
-\end{equation}
-where the ratio of specific heats $\gamma$, the heat capacity at constant pressure $c_p$ and the Prandtl number $\Pr$ depend on the fluid.
-
-Many realistic atmospheric flows can be described by a perturbation over a background state that is in hydrostatic equilibrium
-\newcommand{\backgroundPressure}{\overline{\pressure}}
-\newcommand{\backgroundRho}{\overline{\Qrho}}
-\begin{equation}
-  \label{eq:hydrostatic-balance}
-  \pdv{}{z} \backgroundPressure{\left (z \right )} = -g \backgroundRho(z),
-\end{equation}
-i.e.\ a state, where the pressure gradient is exactly in balance with the gravitational source term $\source[\Qj] = - \bm{k} \Qrho g$.
-The vector $\bm{k}$ is the unit vector pointing in $z$-direction.
-The momentum equation is dominated by the background flow in this case.
-Because this can lead to numerical instabilities, problems of this kind are challenging and require some care.
-To lessen the impact of this, we split the pressure $\pressure = \backgroundPressure + \pressure'$ into a sum of the background pressure $\backgroundPressure(z)$ and perturbation $\pressure'(\bm{x}, t)$.
-We split the density $\Qrho = \backgroundRho + \Qrho'$ in the same manner and arrive at
-\begin{equation}
-  \label{eq:momentum-equation-split}
-  \pdv{\Qj}{t}+ \divergence{ \left(
-    \Qv \otimes \Qj + \bm{I} \pressure'
-    \right)
-  } + \viscFlux_\Qj
-  =
-  -g \bm{k} \Qrho'.
-\end{equation}
-Note that a similar and more complex splitting is performed in~\cite{muller2010adaptive,giraldo2008study}.
-In contrast to this, we use the true compressible Navier-Stokes equations with minimal modifications.
-
-\section{Numerics}
-The \exahypeengine{} implements an \aderdg{}-scheme and a \muscl{} finite volume method.
-Both can be considered as instances of the more general \textsc{PnPm} schemes of~\cite{dumbser2008unified}.
-We use a Rusanov-style flux that is adapted to \pde{}s with viscous terms~\cite{gassner2008discontinuous,fambri2017space}.
-The finite volume scheme is stabilized with the van Albada limiter~\cite{van1997comparative}.
-The user can state dynamic \amr{} rules by supplying custom criteria that are evaluated point-wise.
-Our criterion uses an element-local error estimate based on the total variation of the numerical solution.
-We exploit the fact that the total variation of a numerical solution is a perfect indicator for edges of a wavefront.
-Let $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ be a sufficiently smooth function that maps the discrete solution at a point $\bm{x}$ to an arbitrary indicator variable.
-The total variation (\textsc{tv}) of this function is defined by
-\begin{equation}
-  \label{eq:tv}
-  \tv \left[ f(\bm{x}) \right] =
-  \left\Vert
-\intdcell{ \vert \gradient{f \left( \bm{x} \right)} \vert }
-\right\Vert_1
-\end{equation}
-for each cell.
-The operator $\Vert \cdot \Vert_1$ denotes the discrete $L_1$ norm in this equation.
-We compute the integral efficiently with Gaussian quadrature over the collocated quadrature points.
-\newcommand{\mean}{\mu}%
-\newcommand{\std}{\sigma}%
-\newcommand{\variance}{\std^2}%
-\newcommand{\Trefine}{T_\text{refine}}%
-\newcommand{\Tdelete}{T_\text{coarsen}}%
-How can we decide whether a cell is important or not?
-To resolve this conundrum, we compute the mean and the population standard deviation of the total variation of all cells.
-It is important that we use the method of~\cite{chan1982updating} to compute the modes in a parallel and numerical stable manner.
-A cell is then considered to contain significant information if its deviates from the mean more than a given threshold.
-This criterion can be described formally by
-\begin{equation}
-  \label{eq:refinement-criterion}
-  \operatorname{evaluate-refinement}(\Q, \mu, \sigma) =
-  \begin{cases}
-    \text{refine} & \text{if } \tv(\Q) \geq \mu + \Trefine \sigma, \\
-    \text{coarsen} & \text{if } \tv(\Q) < \mu + \Tdelete \sigma, \\
-    \text{keep} & \text{otherwise}.
-    \end{cases}
-\end{equation}
-The parameters $\Trefine > \Tdelete$ can be chosen freely.
-Chebyshev's inequality
-\begin{equation}
-  \label{eq:chebychev}
-  \mathbb{P}\bigl(\vert X - \mu \vert \geq c \sigma \bigr) \leq \frac{1}{c^2},
-\end{equation}
-with probability $\mathbb{P}$ guarantees that we neither mark all cells for refinement nor for coarsening.
-This inequality holds for arbitrary distributions under the weak assumption that they have a finite mean $\mu$ and a finite standard deviation $\sigma$~\cite{wasserman2004all}.
-Note that subcells are coarsened only if all subcells belonging to the coarse cell are marked for coarsening.
-In contrast to already published criteria which are either designed solely for the simulation of clouds~\cite{muller2010adaptive} or computationally expensive~\cite{fambri2017space}, our criterion works for arbitrary \pde{}s and yet, is easy to compute and intuitive.
-
-\section{Results}\label{sec:results}
-In this section, we evaluate the quality of the results of our numerical methods and the scalability of our implementation.
-We use a mix of various benchmarking scenarios.
-After investigating the numerical convergence rate, we look at three standard \textsc{cfd} scenarios: the Taylor-Green vortex, the three-dimensional Arnold-Beltrami-Childress flow and a lid-driven cavity flow.
-Finally, we evaluate the performance for stratified flow scenarios in both two and three dimensions.
-
-\subsection{CFD Testing Scenarios}
-We begin with a manufactured solution scenario which we can use for a convergence test.
-We use the following constants of fluids for all scenarios in this section:
-\begin{equation}
-  \gamma = 1.4, \quad \Pr = 0.7, \quad c_v = 1.0.
-\end{equation}
-Our description of the manufactured solution follows~\cite{dumbser2010arbitrary}.
-To construct this solution, we assume that
-% \begin{align}\label{eq:manufactured-solution}
-% \begin{split}
-%   \pressure(\bm{x}, t) &= \pressure_0 \cos( \bm{k} \bm{x} - \omega t ) + \pressure_b, \\
-%   \Qrho(\bm{x}, t) &= \Qrho_0 \sin (\bm{k} \bm{x} - \omega t) + \Qrho_b, \\
-%   \Qv(\bm{x}, t) &= \bm{v_0} \sin(\bm{k} \bm{x} - \omega t),
-% \end{split}
-% \end{align}
-\begin{align}\label{eq:manufactured-solution}
-  \begin{split}
-    \pressure(\bm{x}, t) &= \nicefrac{1}{10} \cos( \bm{k} \bm{x} - 2 \pi t ) + \nicefrac{1}{\gamma}, \\
-    \Qrho(\bm{x}, t) &= \nicefrac{1}{2} \sin (\bm{k} \bm{x} - 2 \pi t) + 1, \\
-    \Qv(\bm{x}, t) &= \bm{v_0} \sin(\bm{k} \bm{x} - 2 \pi t),
-  \end{split}
-  \end{align}
-solves our \pde{}.
-We use the constants $\bm{v_0} = \nicefrac{1}{4} \left( 1, 1 \right)^\intercal$, $\bm{k} = \nicefrac{\pi}{5} \left( 1, 1 \right)^\intercal$ and simulate a domain of size $\left[ 10 \times 10 \right]$ for $\SI{0.5}{\s}$.
-The viscosity is set to $\mu = 0.1$.
-% \begin{equation}
-% \begin{alignedat}{6}
-%   & \pressure_u &&= \nicefrac{1}{10}, \qquad& \pressure_b &= \nicefrac{1}{\gamma}, \\
-%   & \Qrho_0 &&= \nicefrac{1}{2}, \qquad& \Qrho_b &= 1, \\
-%   & \bm{v_0} &&= \nicefrac{1}{4},
-%   \begin{pmatrix}
-%     1 \\
-%     1
-%   \end{pmatrix},
-%   \qquad& \bm{k} &= \nicefrac{\pi}{5}
-%   \begin{pmatrix}
-%     1\\
-%     1
-%   \end{pmatrix},\\
-%   & \omega &&= 2 \pi.
-%   \end{alignedat}
-% \end{equation}
-Note that \Cref{eq:manufactured-solution} does not solve the compressible Navier-Stokes equations \cref{eq:equation-set} directly.
-It rather solves our equation set with an added source term which can be derived with a computer algebra system.
-We ran this for a a combination of orders $1, \ldots, 6$ and multiple grid sizes.
-Note that by order we mean the polynomial order throughout the entire paper and not the theoretical convergence order.
-For this scenario, we achieve high-order convergence (\cref{fig:convergence-test}) but notice some diminishing returns for large orders.
-\begin{figure}[tb]
-  \centering
-  \includegraphics{CP032_convergence}
-  \caption{\label{fig:convergence-test}Mesh size vs.\ error for various polynomial orders $P$.
-    Dashed lines show the theoretical convergence order of $P+1$.}
-\end{figure}
-
-After we have established that the implementation of our numerical method converges, we are going to investigate three established testing scenarios from the field of computational fluid mechanics.
-A simple scenario is the Taylor-Green vortex.
-Assuming an \textit{incompressible} fluid, it can be written as
-\begin{align}
-  \label{eq:taylor-green}
-  \begin{split}
-  \Qrho(\bm{x}, t) &= 1,\\
-  \Qv(\bm{x}, t) &= \exp(-2 \mu t)
-  \begin{pmatrix}
-    \phantom{-}\sin(x) \cos(y) \\
-- \cos(x) \sin(y) 
-    \end{pmatrix}, \\
-  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \nicefrac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C.
-  \end{split}
-\end{align}
-The constant $C = \nicefrac{100}{\gamma}$ governs the speed of sound and thus the Mach number $\text{Ma} = 0.1$~\cite{dumbser2016high}.
-The viscosity is set to $\mu = 0.1$.
-
-We simulate on the domain $[0,2\pi]^2$ and impose the analytical solution at the boundary.
-A comparison at time $t = 10.0$ of the analytical solution for the pressure with our approximation (\cref{fig:taylor-green}) shows excellent agreement.
-Note that we only show a qualitative analysis because this is not an exact solution for our equation set as we assume compressibility of the fluid.
-This is nevertheless a valid comparison because for very low Mach numbers, both incompressible and compressible equations behave in a very similarly.
-We used an \aderdg{}-scheme of order $5$ with a grid of $25^2$ cells.
-%
-\begin{figure}[tb]
-  \centering
-  \begin{subfigure}[t]{0.473\textwidth}
-    \centering
-    \includegraphics{CP032_taylor_green_vel}
-    \caption{\label{fig:taylor-green}Our result (markers) of the Taylor-Green vortex vs.\ the analytical solution (lines) \cref{eq:taylor-green}.
-    The plot shows two velocity slices, the respective other coordinate is held constant at a value of $\pi$.}
-  \end{subfigure}\qquad%
-\begin{subfigure}[t]{.473\textwidth}
-  \centering
-    \includegraphics{CP032_abc_flow_velocity}
-    \captionof{figure}{\label{fig:abc-flow}Our approximation (markers) of the \textsc{abc}-flow vs.\ analytical solution (lines, \cref{eq:abc-flow}).
-    All other axes are held constant at a value of 0. We show every 6th value.}
-\end{subfigure}
-    %\includegraphics{paper_abc_flow_velocity}
-    %\caption{\label{fig:abc-flow}\textsc{abc}-flow. We show the velocity in $x$-direction for slices through the domain, where all but the mentioned coordinates are held constant at a value of zero.
-    %The analytical solution is represented by lines, the numerical results by markers.}
-  \caption{\label{fig:cdf-results}Two-dimensional \textsc{cfd} scenarios}
-\end{figure}
-
-The Arnold-Beltrami-Childress (\textsc{abc}) flow is similar to the Taylor-Green vortex but is an analytical solution for the three-dimensional \textit{incompressible} Navier-Stokes equations~\cite{tavelli2016staggered}.
-It is defined in the domain \( \left[ -\pi, \pi \right]^3 \) as
-\begin{align}
-  \label{eq:abc-flow}
-  \begin{split}
-  \Qrho(\bm{x}, t) &= 1,\\
-  \Qv(\bm{x}, t) &= \phantom{-} \exp(-1\mu t)
-  \begin{pmatrix}
-    \sin(z) + \cos(y)\\
-    \sin(x) + \cos(z)\\
-    \sin(y) + \cos(x)
-  \end{pmatrix}, \\
-  \pressure(\bm{x}, t) &= -\exp(-2 \mu t) \, \left(\cos(x)\sin(y) + \sin(x)\cos(z) + \sin(z)\cos(y)\right)
-  + C.
-  \end{split}
-\end{align}
-The constant $C = \nicefrac{100}{\gamma}$ is chosen as before.
-We use a viscosity of $\mu = 0.01$ and analytical boundary conditions.
-Our results (\cref{fig:abc-flow}) show a good agreement between the analytical solution and our approximation with an \aderdg{}-scheme of order $3$ with a mesh consisting of $27^3$ cells at time $t = \SI{0.1}{\s}$.
-Again, we do not perform a quantitative analysis as the \textsc{abc}-flow only solves our equation set approximately.
-
-\begin{figure}[tb]
-\centering
-% or .473 size each, and \\quad inbetween
-  \begin{minipage}[t]{.473\textwidth}
-    \centering
-    \includegraphics{CP032_lid_driven_cavity}
-    \caption{\label{fig:cavity-flow}Our approximation (solid lines) of the lid-driven cavity flow vs.\ reference solution (crosses) of~\cite{ghia1982high}.
-    The respective other coordinate is held constant at a value of 0.}
-  \end{minipage}\quad%
-\begin{minipage}[t]{.473\textwidth}
-  \centering
-    \includegraphics[width=\textwidth]{CP032_two_bubbles_fv}
-    \captionof{figure}{\label{fig:two-bubbles-fv}%
-    Colliding bubbles with \muscl{}. Contour values for potential temperature perturbation are $-0.05, 0.05, 0.1, \ldots 0.45$.}
-\end{minipage}
-\end{figure}
-
-As a final example of standard flow scenarios, we consider the lid-driven cavity flow where the fluid is initially at rest, with $\Qrho = 1$ and $ \pressure(\bm{x}) = \nicefrac{100}{\gamma}$.
-We consider a domain of size $\SI{1}{m} \times \SI{1}{\m}$ which is surrounded by no-slip walls.
-The flow is driven entirely by the upper wall which has a velocity of $v_x = \SI{1}{\m/\s}$.
-The simulation runs for $\SI{10}{\s}$.
-Again, our results (\cref{fig:cavity-flow}) have an excellent agreement with the reference solution of~\cite{ghia1982high}.
-We used an \aderdg{}-method of order $3$ with a mesh of size $27^2$.
-
-\subsection{Stratified Flow Scenarios}
-Our main focus is the simulation of stratified flow scenarios.
-In the following, we present bubble convection scenarios in both two and three dimensions.
-With the constants
-\begin{equation}\label{eq:atmosphere-constants}
-    \gamma = 1.4 ,\quad \Pr =  0.71 ,\quad R = 287.058 ,\quad p_0 = 10^5 \SI{}{\Pa}, \quad g = \SI{9.8}{m/s^2},
-\end{equation}
-all following scenarios are described in terms of the potential temperature
-\begin{equation}
-  \potT = T \left( \frac{p_0}{p} \right)^{R/c_p},
-\end{equation}
-with reference pressure $p_0$~\cite{muller2010adaptive,giraldo2008study}.
-%
-We compute the initial background density and pressure by inserting the assumption of a constant background energy in \cref{eq:hydrostatic-balance}.
-The background atmosphere is then perturbed.
-We set the density and energy at the boundary such that it corresponds to the background atmosphere.
-Furthermore, to ensure that the atmosphere stays in hydrostatic balance, we need to impose the viscous heat flux
-\begin{equation}
-  \label{eq:atmosphere-bc}
-  \viscFlux_{\QE} = \kappa \pdv{\overline{T}}{z}.% =
-\end{equation}
-at the boundary~\cite{giraldo2008study}.
-In this equation, $\overline{T}(z)$ is the background temperature at position $z$, which can be computed from \cref{eq:hydrostatic-balance,eq:eos}.
-
-Our first scenario is the colliding bubbles scenario~\cite{muller2010adaptive}.
-We use perturbations of the form
-\begin{equation}
-  \label{eq:bubbles-pertubation}
-  \pertubationPotT =
-  \begin{cases}
-    A & r \leq a, \\
-    A \exp \left( - \frac{(r-a)^2}{s^2} \right) & r > a,
-    \end{cases}
-\end{equation}
-where $s$ is the decay rate and $r$  is the radius to the center
-\begin{equation}
-  \label{eq:radius}
-  r^2 = \Vert \bm{x} - \bm{x_c} \Vert_2,
-\end{equation}
-i.e., $r$ denotes the Euclidean distance between the spatial positions $\bm{x} = (x, z)$ and the center of a bubble $\bm{x_c} = (x_c, z_c)$ -- for three-dimensional scenarios $\bm{x}$ and $\bm{x_c}$ also contain a $y$ coordinate.
-
-\begin{figure}[tb]
-  \centering
-  \includegraphics[width=1.0\textwidth]{CP032_two_bubbles}
-  \caption{\label{fig:two-bubbles-ader}Left: Colliding Bubbles with \aderdg{}. Contour values for potential temperature perturbation are $-0.05, 0.05, 0.1, \ldots 0.45$.\\
-  Right: Comparison of small scale structure between order 3 (top) and order 6 (bottom).}
-\end{figure}
-We have two bubbles, with constants
-\begin{equation}
-  \label{eq:bubbles-values}
-\begin{alignedat}{6}
-  & \text{warm:} \qquad && A = \SI{0.5}{\K}, \quad&& a = \SI{150}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{500}{\m,} \quad&& z_c = \SI{300}{\m},\\
-  & \text{cold:} \qquad && A = \SI{-0.15}{\K}, \quad&& a = \SI{0}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{560}{\m}, \quad&& z_c = \SI{640}{\m}.
-  \end{alignedat}
-\end{equation}
-Similar to~\cite{muller2010adaptive}, we use a constant viscosity of $\mu = 0.001$ to regularize the solution.
-Note that we use a different implementation of viscosity than~\cite{muller2010adaptive}.
-Hence, it is difficult to compare the parametrization directly.
-We ran this scenario twice:
-once without \amr{} and a mesh of size $\SI{1000/81}{\m} = \SI{12.35}{\m}$ and once with \amr{} with two adaptive refinement levels and parameters $\Trefine = 2.5$ and $\Tdelete = -0.5$.
-For both settings we used polynomials of order 6.
-We specialize the \amr{}-criterion~\pcref{eq:refinement-criterion} to our stratified flows by using the potential temperature.
-This resulted in a mesh with cell-size lengths of approx.\ \SI{111.1}{\m}, \SI{37.04}{\m}, and \SI{12.34}{\m}.
-The resulting mesh can be seen in \cref{fig:two-bubbles-ader}.
-
-We observe that the $L_2$ difference between the potential temperature of the \amr{} run, which uses 1953 cells, and the one of the fully refined run with 6561 cells, is only $1.87$.
-The relative error is \num{2.6e-6}.
-We further emphasize that our \amr{}-criterion accurately tracks the position of the edges of the cloud instead of only its position.
-This is the main advantage of our gradient-based method in contrast to methods working directly with the value of the solution, as for example~\cite{muller2010adaptive}.
-Overall, our result for this benchmark shows an excellent agreement to the previous solutions of~\cite{muller2010adaptive}.
-In addition, we ran a simulation with the same settings for a polynomial order of 3.
-The lower resolution leads to spurious waves~(\cref{fig:two-bubbles-ader}) and does not capture the behavior of the cloud.
-
-Furthermore, we simulated the same scenario with our \muscl{} method, using $7^2$ patches with $90^2$ finite volume cells each.
-As we use limiting, we do not need any viscosity.
-The results of this method (\cref{fig:two-bubbles-fv}) also agree with the reference but contain fewer details.
-Note that the numerical dissipativity of the finite volume scheme has a smoothing effect that is similar to the smoothing caused by viscosity.
-
-For our second scenario, the cosine bubble, we use a perturbation of the form
-\begin{align}
-  \label{eq:cos-pertubation}
-  \pertubationPotT &= \begin{cases}
-    \nicefrac{A}{2} \left[ 1 + \cos(\pi r) \right] & r \leq a, \\
-    0 & r > a,
-    \end{cases}
-\end{align}
-where $A$ denotes the maximal perturbation and $a$ is the size of the bubble.
-We use the constants
-\begin{equation}\label{eq:cosine-bubble}
-  A = \SI{0.5}{\K}, \quad a = \SI{250}{\m}, \quad x_c = \SI{500}{\m}, \quad z_c = \SI{350}{\m}.
-\end{equation}
-For the three-dimensional bubble, we set $y_c = x_c = \SI{500}{\m}$.
-This corresponds to the parameters used in~\cite{kelly2012continuous}\footnote{%
-We found that the parameters presented in the manuscript of~\cite{kelly2012continuous} only agree with the results, if we use the same parameters as for 2D simulations.}.
-For the 2D case, we use a constant viscosity of $\mu = 0.001$ and an \aderdg{}-method of order 6 with two levels of dynamic \amr{}, resulting again in cell sizes of roughly $\SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.34}{\m}$.
-We use slightly different \amr{} parameters of $\Trefine = 1.5$ and $\Tdelete = -0.5$ and let the simulation run for \SI{700}{\s}.
-Note that, as seen in \cref{fig:cosine-2d}, our \amr{}-criterion tracks the wavefront of the cloud accurately.
-This result shows an excellent agreement to the ones achieved in~\cite{giraldo2008study,muller2010adaptive}.
-
-For the 3D case, we use an \aderdg{}-scheme of order 3 with a static mesh with cell sizes of \SI{40}{\m} and a shorter simulation duration of \SI{400}{\s}.
-Due to the relatively coarse resolution and the hence increased aliasing errors, we need to increase the viscosity to $\mu = 0.005$.
-This corresponds to a larger amount of smoothing.
-Our results (\cref{fig:cosine-3d}) capture the dynamics of the scenario well and agree with the reference solution of~\cite{kelly2012continuous}.
-
-\begin{figure}[tb]
-  \centering
-  \begin{subfigure}[t]{0.5\textwidth}
-    \centering
-    \includegraphics[scale=0.16, trim={0cm 0 32cm 0},clip]{CP032_cosine_bubble_collage}
-    %\includegraphics[width=\textwidth]{paper_cosine_bubble}
-    \caption{\label{fig:cosine-2d}2D Cosine Bubble.}%
-  \end{subfigure}~%
-  \begin{subfigure}[t]{0.5\textwidth}
-    \centering
-    \includegraphics[scale=0.16, trim={42cm 0 0cm 0},clip]{CP032_cosine_bubble_collage}
-    \caption{\label{fig:cosine-3d}3D Cosine Bubble}
-  \end{subfigure}
-  \caption{\label{fig:cosine-bubbles-results}Cosine Bubble Scenario.}
-\end{figure}
-
-\subsection{Scalability}%
-\newcommand{\mdofs}{\text{MDOF/s}}%
-All two-dimensional scenarios presented in this paper can be run on a single workstation in less than two days.
-Parallel scalability was thus not the primary goal of this paper.
-Nevertheless, our implementation allows us to scale to small to medium scale setups using a combined \mpi{}~+~Thread building blocks~(\tbb{}) parallelization strategy, which works as follows:
-We typically first choose a number of \mpi{} ranks that ensure an equal load balancing.
-\exahype{} achieves best scalability for $1, 10, 83, \ldots$ ranks, as our underlying framework uses three-way splittings for each level and per dimension and an additional communication rank per level.
-For the desired number of compute nodes, we then determine the number of \tbb{} threads per rank to match the number of total available cores.
-
-We ran the two bubble scenario for a uniform grid with a mesh size of $729 \times 729$ with order 6, resulting in roughly 104 million degrees of freedom (\textsc{dof}), for 20 timesteps and for multiple combinations of \mpi{} ranks and \tbb{} threads.
-This simulation was performed on the SuperMUC-NG system using computational kernels that are optimized for its Skylake architecture.
-Using a single \mpi{} rank, we get roughly $4.9$ millions \textsc{dof} updates ($\mdofs$) using two \tbb{} threads and $20.2 \mdofs$ using 24 threads (i.e.\ a half node).
-For a full node with 48 threads, we get a performance of $12 \mdofs$.
-When using 5 nodes with 10 \mpi{} ranks, we achieve $29.3 \mdofs$ for two threads and $137.3 \mdofs$ for 24 threads.
-
-We further note that for our scenarios weak scaling is more important than strong scaling, as we currently cover only a small area containing a single cloud, where in practical applications one would like to simulate more complex scenarios.
-\section{Conclusion}
-We presented an implementation of a \muscl{}-scheme and an \aderdg{}-method with \amr{} for the Navier-Stokes equations, based on the \exahypeengine.
-Our implementation is capable of simulating different scenarios:
-We show that our method has high order convergence and we successfully evaluated our method for standard \textsc{cfd} scenarios:
-We have competitive results for both two-dimensional scenarios (Taylor-Green vortex and lid-driven cavity) and for the three-dimensional \textsc{abc}-flow.
-
-Furthermore, our method allows us to simulate flows in hydrostatic equilibrium correctly, as our results for the cosine and colliding bubble scenarios showed.
-We showed that our \amr{}-criterion is able to vastly reduce the number of grid cells while preserving the quality of the results.
-
-Future work should be directed towards improving the scalability.
-With an improved \amr{} scaling and some fine tuning of the parallelization strategy, the numerical method presented here might be a good candidate for the simulation of small scale convection processes that lead to cloud formation processes.
+To summarize, we reran the affected simulations with the correct background pressure.
+After adapting the viscosity, the new results agree well with the original results.
 

### 2022-06-22 writing/erratum/CP032.tex
Add parameters for simulations

@@
 We recomputed the key results with correct background pressure.
+All 2D scenarios were ran with a viscosity of $\mu=0.1$, the 3D scenario required a viscosity of $\mu=0.4$.
 
+% Settings: visc 0.1, refine: 1.5, coarse: -0.5
 The first scenario is the cosine bubble scenario with and without adaptive mesh refinement (AMR).
@@
 The second scenario is the colliding bubble scenario.
-We ran this with the Finite Volume method using a viscosity of $\mu=0$.
+We ran this with the Finite Volume method using a viscosity of $\mu=0.1$.
 The results (Figure xxx) agree with the original results.
+% Settings: visc: 0.1, refine: 1.5, coarse: -0.5
 We also ran this with the ADER-DG method, with and without AMR (Figure XXX).
@@
 The third scenario is the three-dimensional cosine bubble.
-We ran this with a viscosity of $\mu = \ldots$.
+We ran this with a viscosity of $\mu = 0.4$.
 The results (Figure XXX) agree with our original simulations.

### 2022-06-27 writing/erratum/CP032.tex
First draft erratum

@@
 When trying to reproduce the results, we noticed that we erronously computed the cloud scenarios with a different background pressure and viscosity as stated in the paper.
-As the former may result in different physical results, we here evaluated the simulations with the correct background pressure of $\ldots$.
+As the former may result in different physical results, we here evaluate the simulations with the correct background pressure of $\SI{100 000 }{\pascal}$.
 In our paper, while viscosity follows the Navier-Stokes equations, we use it additionally to stabilize the simulation.
 Neither classical CFD scenarios (Taylor-Green, Lid-driven cavity, 3D scenario) nor the convergence test are affected by this.
-We recomputed the key results with correct background pressure.
+We recomputed the key cloud scenarios with correct background pressure.
 All 2D scenarios were ran with a viscosity of $\mu=0.1$, the 3D scenario required a viscosity of $\mu=0.4$.
 
+\begin{figure}[htb]
+  \begin{subfigure}[t]{0.45\columnwidth}
+  \includegraphics[width=\textwidth]{screenshots/cosine_bubble_2d_dg.png}
+  \caption{\label{fig:cosine-bubble-2d-dg-amr}%
+  2D Cosine bubble with AMR, computed by ADER-DG method.
+  Contours are at $-0.05, 0.05, \ldots 0.45$.
+  }
+  \end{subfigure}\quad
+  \begin{subfigure}[t]{0.45\columnwidth}
+  \includegraphics[width=1\textwidth]{screenshots/cosine_bubble_3d_dg.png}
+  \caption{\label{fig:cosine-bubble-3d-dg-noamr}%
+  3D Cosine bubble without AMR, computed by ADER-DG method.}
+  \end{subfigure}
+
+\end{figure}
 % Settings: visc 0.1, refine: 1.5, coarse: -0.5
 The first scenario is the cosine bubble scenario with and without adaptive mesh refinement (AMR).
-We ran it as described in the paper but with the correct background pressure and a viscosity of $\mu = \ldots$. 
+We ran it as described in the paper but with the correct background pressure. 
 %TODO Refinement settings.
-Figure XXX depicts the results.
-Both show an excellent agreement with the original results.
-The AMR simulation shows slight differences in the refinement; however, the refinement has the same quality as the original one.
+The new result (\cref{fig:cosine-bubble-2d-dg-amr}) shows an excellent agreement with the original results.
+The adapted mesh of shows slight differences in the refinement; however, the refinement has the same quality as the original one.
+The third scenario is the three-dimensional cosine bubble.
+The results, as shown in \cref{fig:cosine-bubble-3d-dg-noamr} are similar to our original results.
 
-The second scenario is the colliding bubble scenario.
-We ran this with the Finite Volume method using a viscosity of $\mu=0.1$.
-The results (Figure xxx) agree with the original results.
+\begin{figure}[htb]
+  \begin{subfigure}[t]{0.45\columnwidth}
+  \includegraphics[width=\textwidth]{screenshots/two_bubbles_dg.png}
+  \caption{\label{fig:two-bubbles-2d-dg-amr}%
+  2D Cosine bubble with AMR, computed by ADER-DG method.
+  Contours are at $-0.05, 0.05, \ldots 0.45$.
+  }
+  \end{subfigure}\quad
+  \begin{subfigure}[t]{0.45\columnwidth}
+  \includegraphics[width=1\textwidth]{screenshots/two_bubbles_fv.png}
+  \caption{\label{fig:two-bubbles-2d-fv-noamr}%
+  2D colliding bubbles scenario, without AMR, computed with finite volume method.}
+  \end{subfigure}
+
+\end{figure}
+
+The final scenario is the colliding bubble scenario.
+We ran this first with the ADER-DG method and a viscosity of $\mu=0.1$.
+Similarly to the cosine bubble, the results (\cref{fig:two-bubbles-2d-dg-amr}) show an excellent agreement with the original results (with some small differences in the refinement).
+We ran this first with the Finite Volume method using a viscosity of $\mu=0.0$.
+The results (\cref{fig:two-bubbles-2d-fv-noamr}) agree with the original results.
 % Settings: visc: 0.1, refine: 1.5, coarse: -0.5
-We also ran this with the ADER-DG method, with and without AMR (Figure XXX).
-Similarly to the cosine bubble, the results show an excellent agreement with the original results (with some small differences in the refinement).
-
-The third scenario is the three-dimensional cosine bubble.
-We ran this with a viscosity of $\mu = 0.4$.
-The results (Figure XXX) agree with our original simulations.
 
@@
 Computing resources were provided by the Leibniz Supercomputing Centre (project pr83no).
-Special thanks go to Dominic E.\ Charrier for his support with the implementation in the \exahypeengine{}.
 

### 2022-07-13 writing/erratum/CP032.tex
Add todos, improve figure captions

@@
 \usepackage{cite}
-\newcommand{\citeauthor}{???}
+\usepackage{todonotes}
 
@@
 
-\subsection{Erratum}
+\todo[inline]{Make clearer, which sections which scenario corresponds to.}
+\todo[inline]{Maybe use same figure naming as in original paper.}
+%\subsection{Erratum}
+\paragraph{Background}
 This is an erratum for \cite{krenz2019high}.
+\todo[inline]{Zu verklausuliert:}
 When trying to reproduce the results, we noticed that we erronously computed the cloud scenarios with a different background pressure and viscosity as stated in the paper.
+\todo[inline]{Mention concrete parameters later}
 As the former may result in different physical results, we here evaluate the simulations with the correct background pressure of $\SI{100 000 }{\pascal}$.
+\todo[inline]{Make clearer that viscosity is both physical and stabilizing}
 In our paper, while viscosity follows the Navier-Stokes equations, we use it additionally to stabilize the simulation.
@@
   \end{subfigure}
-
+\caption{
+  This corresponds to figure 6 of the original paper.
+}
 \end{figure}
 % Settings: visc 0.1, refine: 1.5, coarse: -0.5
+\paragraph{Cosine Bubble}
 The first scenario is the cosine bubble scenario with and without adaptive mesh refinement (AMR).
@@
 
-\begin{figure}[htb]
-  \begin{subfigure}[t]{0.45\columnwidth}
+\begin{figure}[tb] 
+  \centering 
+  % or .473 size each, and \\quad inbetween 
+    \begin{minipage}[t]{.473\textwidth} 
+      \centering 
   \includegraphics[width=\textwidth]{screenshots/two_bubbles_dg.png}
+      %\caption{\label{fig:cavity-flow}Our approximation (solid lines) of the lid-driven cavity flow vs.\ reference solution (crosses) of~\cite{ghia1982high}. 
+      %The respective other coordinate is held constant at a value of 0.} 
   \caption{\label{fig:two-bubbles-2d-dg-amr}%
-  2D Cosine bubble with AMR, computed by ADER-DG method.
+  This corresponds to figure 5 in the original paper.
+  2D colliding bubble with AMR, computed by ADER-DG method.
   Contours are at $-0.05, 0.05, \ldots 0.45$.
   }
-  \end{subfigure}\quad
-  \begin{subfigure}[t]{0.45\columnwidth}
+
+    \end{minipage}\quad% 
+  \begin{minipage}[t]{.473\textwidth}
+    \centering
   \includegraphics[width=1\textwidth]{screenshots/two_bubbles_fv.png}
-  \caption{\label{fig:two-bubbles-2d-fv-noamr}%
+  \captionof{figure}{\label{fig:two-bubbles-2d-fv-noamr}%
+  This corresponds to figure 4 in the original paper.
   2D colliding bubbles scenario, without AMR, computed with finite volume method.}
-  \end{subfigure}
 
+  \end{minipage}
   \end{figure}
 
+\paragraph{Colliding Bubble}
 The final scenario is the colliding bubble scenario.

### 2022-07-18 writing/erratum/CP032.tex
Improved erratum

--- 2022-06-27 writing/erratum/CP032.tex
@@
 \maketitle 
-\begin{abstract}
+%\begin{abstract}
+%This is an erratum.
+%In the original paper, we computed our scenarios with incorrect parameters.
+%Here, we show that we get similar results with the corrected parameters.
+%%\keywords{\aderdg{}  \and Navier-Stokes \and Adaptive Mesh Refinement}
+%\end{abstract}
+\paragraph{Background}
+This is an erratum for~\cite{krenz2019high}.
+When trying to reproduce our results, we noticed that we erroneously computed the cloud scenarios (in section 4.2) with different parameters as stated in the papers.
+These scenarios simulate perturbations over a background field which is in hydrostatic equilibrium.
+We used an incorrect background pressure of \SI{10 000}{\pascal} instead of \SI{100 000 }{\pascal} to compute the background fields.
+In our paper, we use the viscosity given by the Navier-Stokes equations to stabilize our simulations.
+We stated a viscosity that is too small to ensure stable simulations, especially with the correct background pressure.
+Thus, we recomputed the key cloud scenarios with correct background pressure and modified viscosity.
+All other simulation parameters are as described in~\cite{krenz2019high}.
+Neither classical CFD scenarios (Taylor-Green, Lid-driven cavity, ABC-Vortex) nor the convergence test are affected.
 
-\keywords{\aderdg{}  \and Navier-Stokes \and Adaptive Mesh Refinement}
-\end{abstract}
-
-\subsection{Erratum}
-This is an erratum for \cite{krenz2019high}.
-When trying to reproduce the results, we noticed that we erronously computed the cloud scenarios with a different background pressure and viscosity as stated in the paper.
-As the former may result in different physical results, we here evaluate the simulations with the correct background pressure of $\SI{100 000 }{\pascal}$.
-In our paper, while viscosity follows the Navier-Stokes equations, we use it additionally to stabilize the simulation.
-Neither classical CFD scenarios (Taylor-Green, Lid-driven cavity, 3D scenario) nor the convergence test are affected by this.
-We recomputed the key cloud scenarios with correct background pressure.
-All 2D scenarios were ran with a viscosity of $\mu=0.1$, the 3D scenario required a viscosity of $\mu=0.4$.
-
-\begin{figure}[htb]
+\begin{figure}[tb]
   \begin{subfigure}[t]{0.45\columnwidth}
@@
   \caption{\label{fig:cosine-bubble-2d-dg-amr}%
-  2D Cosine bubble with AMR, computed by ADER-DG method.
+  2D Cosine bubble with AMR, computed by the ADER-DG method.
   Contours are at $-0.05, 0.05, \ldots 0.45$.
@@
   \caption{\label{fig:cosine-bubble-3d-dg-noamr}%
-  3D Cosine bubble without AMR, computed by ADER-DG method.}
+  3D Cosine bubble without AMR, computed by the ADER-DG method.}
   \end{subfigure}
-
+\caption{
+  Results for the cosine bubble scenario.
+  This figure corresponds to figure 6 of the original paper.
+}
 \end{figure}
 % Settings: visc 0.1, refine: 1.5, coarse: -0.5
-The first scenario is the cosine bubble scenario with and without adaptive mesh refinement (AMR).
-We ran it as described in the paper but with the correct background pressure. 
-%TODO Refinement settings.
+\paragraph{Cosine Bubble}
+The cosine bubble scenario with and without adaptive mesh refinement (AMR).
+We ran it as described in the paper but with the correct background pressure and a viscosity of $\mu=0.1$. 
 The new result (\cref{fig:cosine-bubble-2d-dg-amr}) shows an excellent agreement with the original results.
 The adapted mesh of shows slight differences in the refinement; however, the refinement has the same quality as the original one.
-The third scenario is the three-dimensional cosine bubble.
-The results, as shown in \cref{fig:cosine-bubble-3d-dg-noamr} are similar to our original results.
+Similar to the original results, the results obtained with a statically refined mesh are visually indistinguishable from the AMR results.
+We also simulated a three-dimensional cosine bubble.
+The results (\cref{fig:cosine-bubble-3d-dg-noamr}), computed with the correct background pressure and a viscosity of $\mu=0.4$, are similar to our original results.
 
-\begin{figure}[htb]
-  \begin{subfigure}[t]{0.45\columnwidth}
+\begin{figure}[tb] 
+  \centering 
+    \begin{minipage}[t]{.473\textwidth} 
+    \centering
+  \includegraphics[width=1\textwidth]{screenshots/two_bubbles_fv.png}
+  \captionof{figure}{\label{fig:two-bubbles-2d-fv-noamr}%
+  This corresponds to figure 4 in the original paper.
+  2D colliding bubbles scenario, without AMR, computed with finite volume method.}
+    \end{minipage}\quad% 
+  \begin{minipage}[t]{.473\textwidth}
+      \centering 
   \includegraphics[width=\textwidth]{screenshots/two_bubbles_dg.png}
-  \caption{\label{fig:two-bubbles-2d-dg-amr}%
-  2D Cosine bubble with AMR, computed by ADER-DG method.
+  \captionof{figure}{\label{fig:two-bubbles-2d-dg-amr}%
+  This corresponds to figure 5 in the original paper.
+  2D colliding bubble with AMR, computed by ADER-DG method.
   Contours are at $-0.05, 0.05, \ldots 0.45$.
   }
-  \end{subfigure}\quad
-  \begin{subfigure}[t]{0.45\columnwidth}
-  \includegraphics[width=1\textwidth]{screenshots/two_bubbles_fv.png}
-  \caption{\label{fig:two-bubbles-2d-fv-noamr}%
-  2D colliding bubbles scenario, without AMR, computed with finite volume method.}
-  \end{subfigure}
-
+  \end{minipage}
   \end{figure}
 
-The final scenario is the colliding bubble scenario.
-We ran this first with the ADER-DG method and a viscosity of $\mu=0.1$.
-Similarly to the cosine bubble, the results (\cref{fig:two-bubbles-2d-dg-amr}) show an excellent agreement with the original results (with some small differences in the refinement).
-We ran this first with the Finite Volume method using a viscosity of $\mu=0.0$.
+\paragraph{Colliding Bubble}
+We ran the colliding bubble scenario with the ADER-DG method and a viscosity of $\mu=0.1$.
+Similarly to the cosine bubble, the results with AMR (\cref{fig:two-bubbles-2d-dg-amr}) show an excellent agreement with the original results, with some small differences in the refinement.
+The simulation with AMR also agrees with our results.
+Additionally, we simulated this scenario with the Finite Volume method and a viscosity of $\mu=0.0$.
 The results (\cref{fig:two-bubbles-2d-fv-noamr}) agree with the original results.
-% Settings: visc: 0.1, refine: 1.5, coarse: -0.5
-
-To summarize, we reran the affected simulations with the correct background pressure.
-After adapting the viscosity, the new results agree well with the original results.
 

### 2022-07-21 writing/erratum/CP032.tex
next iteration erratum

@@
 In our paper, we use the viscosity given by the Navier-Stokes equations to stabilize our simulations.
-We stated a viscosity that is too small to ensure stable simulations, especially with the correct background pressure.
+We stated a viscosity that is too small to ensure stable simulations.
 Thus, we recomputed the key cloud scenarios with correct background pressure and modified viscosity.
@@
 \paragraph{Cosine Bubble}
-The cosine bubble scenario with and without adaptive mesh refinement (AMR).
-We ran it as described in the paper but with the correct background pressure and a viscosity of $\mu=0.1$. 
+We ran the cosine bubble scenario with and without adaptive mesh refinement (AMR) using the correct background pressure and a viscosity of $\mu=0.1$. 
 The new result (\cref{fig:cosine-bubble-2d-dg-amr}) shows an excellent agreement with the original results.
-The adapted mesh of shows slight differences in the refinement; however, the refinement has the same quality as the original one.
+The adapted mesh of the new results is slightly different; however, the refinement has the same quality as the original one.
 Similar to the original results, the results obtained with a statically refined mesh are visually indistinguishable from the AMR results.
@@
 The simulation with AMR also agrees with our results.
-Additionally, we simulated this scenario with the Finite Volume method and a viscosity of $\mu=0.0$.
+Additionally, we simulated this scenario with the Finite Volume method and a viscosity of $\mu=0$.
 The results (\cref{fig:two-bubbles-2d-fv-noamr}) agree with the original results.

### 2023-10-13 writing/erratum/CP032.tex
Include Michael's comments in erratum

@@
 When trying to reproduce our results, we noticed that we erroneously computed the cloud scenarios (in section 4.2) with different parameters as stated in the papers.
-These scenarios simulate perturbations over a background field which is in hydrostatic equilibrium.
-We used an incorrect background pressure of \SI{10 000}{\pascal} instead of \SI{100 000 }{\pascal} to compute the background fields.
+These scenarios simulate perturbations over a background state that is in hydrostatic equilibrium.
+We used an incorrect background pressure of \SI{10000}{\pascal} instead of \SI{100000 }{\pascal} to compute the background states.
 In our paper, we use the viscosity given by the Navier-Stokes equations to stabilize our simulations.
-We stated a viscosity that is too small to ensure stable simulations.
+We stated a viscosity that is too small to ensure stable simulations with the higher background pressure.
 Thus, we recomputed the key cloud scenarios with correct background pressure and modified viscosity.
@@
 
-\begin{figure}[tb]
+\begin{figure}[htb]
   \begin{subfigure}[t]{0.45\columnwidth}
@@
 \caption{
-  Results for the cosine bubble scenario.
-  This figure corresponds to figure 6 of the original paper.
+  Recomputed and corrected scenario to replace Figure 6 of~\cite{krenz2019high}.
 }
@@
 % Settings: visc 0.1, refine: 1.5, coarse: -0.5
-\paragraph{Cosine Bubble}
+\paragraph{Cosine Bubble (Sec. 4.2, Fig.~4 and~5 of~\cite{krenz2019high})}
 We ran the cosine bubble scenario with and without adaptive mesh refinement (AMR) using the correct background pressure and a viscosity of $\mu=0.1$. 
-The new result (\cref{fig:cosine-bubble-2d-dg-amr}) shows an excellent agreement with the original results.
-The adapted mesh of the new results is slightly different; however, the refinement has the same quality as the original one.
+The new result (\cref{fig:cosine-bubble-2d-dg-amr}) shows a very close agreement with the original results.
+The adapted mesh of the new results is slightly different.
+However, the mesh refinements for the two scenarios are of the same quality
 Similar to the original results, the results obtained with a statically refined mesh are visually indistinguishable from the AMR results.
@@
 
-\begin{figure}[tb] 
+\begin{figure}[htb] 
   \centering 
@@
   \captionof{figure}{\label{fig:two-bubbles-2d-fv-noamr}%
-  This corresponds to figure 4 in the original paper.
+  Recomputed and corrected scenario to replace Figure 4 in~\cite{krenz2019high}.
   2D colliding bubbles scenario, without AMR, computed with finite volume method.}
@@
   \captionof{figure}{\label{fig:two-bubbles-2d-dg-amr}%
-  This corresponds to figure 5 in the original paper.
+  Recomputed and corrected scenario to replace Figure 5 in~\cite{krenz2019high}.
   2D colliding bubble with AMR, computed by ADER-DG method.
@@
 
-\paragraph{Colliding Bubble}
+\paragraph{Colliding Bubble (Sec.~4.2. and Fig.~6 of\cite{krenz2019high})}
 We ran the colliding bubble scenario with the ADER-DG method and a viscosity of $\mu=0.1$.
-Similarly to the cosine bubble, the results with AMR (\cref{fig:two-bubbles-2d-dg-amr}) show an excellent agreement with the original results, with some small differences in the refinement.
+Similarly to the cosine bubble, the results with AMR (\cref{fig:two-bubbles-2d-dg-amr}) show a very close agreement with the original results, with some small differences in the refinement.
 The simulation with AMR also agrees with our results.

### 2023-11-24 writing/erratum/CP032.tex
Some minor edits to erratum

@@
 \authorrunning{L.\ Krenz, L.\ Rannabauer, M.\ Bader}
-\institute{Department of Informatics, Technical University of Munich\\
+\institute{TUM School of Computation, Information and Technology, Technical University of Munich\\
   \email{lukas.krenz@in.tum.de}, \email{rannabau@in.tum.de}, \email{bader@in.tum.de}
@@
 The new result (\cref{fig:cosine-bubble-2d-dg-amr}) shows a very close agreement with the original results.
-The adapted mesh of the new results is slightly different.
-However, the mesh refinements for the two scenarios are of the same quality
+The mesh refinements for the two scenarios are not identical but of the same quality
 Similar to the original results, the results obtained with a statically refined mesh are visually indistinguishable from the AMR results.
@@
   \captionof{figure}{\label{fig:two-bubbles-2d-fv-noamr}%
-  Recomputed and corrected scenario to replace Figure 4 in~\cite{krenz2019high}.
-  2D colliding bubbles scenario, without AMR, computed with finite volume method.}
+  2D colliding bubbles scenario, without AMR, computed with Finite Volume method.
+  Recomputed and corrected scenario to replace Figure 4 in~\cite{krenz2019high}.%
+  }
     \end{minipage}\quad% 
@@
   \captionof{figure}{\label{fig:two-bubbles-2d-dg-amr}%
-  Recomputed and corrected scenario to replace Figure 5 in~\cite{krenz2019high}.
   2D colliding bubble with AMR, computed by ADER-DG method.
   Contours are at $-0.05, 0.05, \ldots 0.45$.
+  Recomputed and corrected scenario to replace Figure 5 in~\cite{krenz2019high}.%
   }
@@
 
-\subsection*{Acknowledgments}
-This work was funded by the European Union’s Horizon 2020 Research and Innovation Programme under grant agreements 
-No~671698 (project ExaHyPE, \url{www.exahype.eu}) and 
-No~823844 (ChEESE centre of excellence, \url{www.cheese-coe.eu}).
-Computing resources were provided by the Leibniz Supercomputing Centre (project pr83no).
+%\subsection*{Acknowledgments}
+%This work was funded by the European Union’s Horizon 2020 Research and Innovation Programme under grant agreements 
+%No~671698 (project ExaHyPE, \url{www.exahype.eu}) and 
+%No~823844 (ChEESE centre of excellence, \url{www.cheese-coe.eu}).
+%Computing resources were provided by the Leibniz Supercomputing Centre (project pr83no).
 
